### 2020-06-22 chatbot_classification/sample/paper.tex
sample

%% LyX 2.3.1-1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass{article}
\usepackage[latin9]{inputenc}
\usepackage{array}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{graphicx}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}
%% A simple dot to overcome graphicx limitations
\newcommand{\lyxdot}{.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
% Template for GlobalSIP-2018 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\usepackage{spconf}

\def\x{{\mathbf x}}
\def\L{{\cal L}}

\makeatother

\begin{document}
\title{     
  An attention based deep neural network for \\
  automatic lexical stress detection   
}
\name{Tian Xia, Xianfeng Rui, Chien-Lin Huang, Iek Heng Chu, Shaojun Wang, Mei Han}   
\address{     
  \{SummerRainET2008, huntrui, chiccocl, iekhengchu0217, swang.usa, hanmei613\}@gmail.com   
}
\maketitle 
\begin{abstract}
Lexical stress detection is one of important tasks in self-directed
language learning application. We address this task by leveraging
two successful attention techniques in natural language processing,
\textbf{inner attention} and \textbf{self-attention}. First, combined
with LSTM to model time-series features, inner attention could extract
most important information and then convert length-varying input into
a fixed-length feature vector; Second, self-attention intrinsically
support as input words with \emph{different number of syllables} to
model contexture information. Besides, our model is straightforward
to expand to include hand-crafted features to improve performance,
and can be applied to similar tasks, such as pitch accent detector.
Experiments on LibriSpeech, TedLium and a third self-recored datasets
show the high performance of our proposed attention based neural network. 
\end{abstract}
\keywords{stress, detection, attention, neural network}

\section{Introduction}

\label{sec:intro}

Nowadays self-directed language learning has become more and more
popular, and computer-aided pronunciation training therefore has drawn
considerable attention. The research in this direction is focusing
on mispronunciation detection and diagnosis problems by using speech
recognition related technologies. These problems can be addressed
in segmental level and suprasegmental level. For example, segmental
level work involving phones and words \cite{li2015integrating,li2016mispronunciation},
suprasegmental level involving lexical stress \cite{li2011a,li2012perceptually,li2013lexical}
and pitch accent \cite{li2011a,zhao2013exploiting}, etc. This paper
targets at lexical stress detection problem, which is one of most
important factors for evaluating proficiency.

Lexical stress has a relation with the prominent syllables of a word.
As pointed in the work of \cite{li2018automatic}, in many cases the
position of syllable carries important information to disambiguate
word semantics. e.g., ``subject" vs. "sub'ject", "permit" vs.
"per'mit". Once we detect lexical stress for a word, and compare
with its typical lexical stress pattern from dictionary, we could
determine whether stress pronunciation is correct.

There are a line of related work. Such as the work in \cite{tepperman2005automatic}
uses Gaussian mixture models; Zhao et al. \cite{svm} adopted SVMs
to identify the vowels of L2 English speech carrying primary stress
or not. Other similar studies using SVMs to detect lexical stress
of English speech with Taiwanese accent were reported in Wang et al.
\cite{wang2009stress}, Chen and Wang \cite{chen2010automatic}, etc.
Ferrer et al. \cite{ferrer2015classification} introduced a system
for lexical stress detection using both prosodic (pitch, energy and
duration) and spectral MFCC features. Results showed that the MFCC
helped improve the experimental performance. The error rates of the
system for L1-English and L1-Japanese data were 11\% and 20\% respectively.

Another important work in \cite{li2018automatic} uses multi-distribution
deep neural networks (MD-DNN), which are constructed by stacking up
multiple Restricted Boltzmann Machines (RBMs). The work from Li et
al. work uses several hand-crafted syllable-based features with length
fixed. The main difference with our model is we do not hand-craft
features, but have the neural network learn itself. Moreover, our
model does not require the input to be of 5-syllable\footnote{They would fill short words to 5-syllable with special values, usually
0s.}, and prevent any approximation of input.

\begin{figure*}[t]
\begin{centering}
\includegraphics[scale=0.45]{picture\lyxdot 1} 
\par\end{centering}
\caption{Our neural network structure. For example, first, the word ``\textbf{projector}''
is partitioned into three syllables by linguistic rules, ``pro'',
``jec'' and ``tor''. Second, each syllable, represented as concatenation
of several time-series features in the frame level, e.g., MFCC, pitch
and energy, is encoded by the LSTM blocks, and then be converted into
a fixed-length feature vector by inner attention Third, all syllable-representing
feature vectors are interacting with each other via\textbf{ self-attention},
and finally be trained to fit their final labels. Note that, all LSTM
models are sharing the same parameters, and so are  all position-wise
Feed-Forward-Networks (FFN).}
\label{fig:framework}
\end{figure*}

\section{Attention based neural network}

\label{sec:att-nn}

\subsection{Time-series features}

Intuitively, pitch highly correlates with stress. Instead of extracting
mere one highest frequency, we extract several highest frequencies
in each frame, which empirically contribute to the performance moderately..

As stressed syllable usually exhibits higher energy than its neighboring
ones, thus energy is extracted in the frame level.

Besides, Mel Frequency Cepstral Coefficient (MFCC) features are found
to benefit stress detection ask in \cite{ferrer2015classification}.
Hence we adopt MFCC here, with Delta and Delta-Delta information included
as well. Empirically, we found large dimension of MFCC improves the
final performance. Thus we prefer large dimensions.

All the three kinds of features above are normalized in the word level
and in each feature dimension. Our normalization strategy has two
parts. First, lineally scale features into the range of minimum and
maximum, and second, subtract by the mean value. Adopting either part
separately hurts the performance.

\subsection{Syllable encoding module}

The logic level 2, 3, 4 in Fig. \ref{fig:framework} demonstrate the
internal structure of syllable encoding module. It consists of one
bidirectional LSTM, several blocks of uni-directional LSTM and residual
edge, and one inner attention layer \cite{inneratten}.

Based on the statistics of syllable duration, we limit the maximum
LSTM steps as 50, corresponding to 500 ms duration. This setting is
the same through logic level 2 and 3. In logic level 2, two frame-level
LSTMs runs from different directions and element-wisely sum together
to enrich both the left and right context for each frame state. This
is also the common doing when applying LSTM into a sequential data.

The neural network structure in logic level 3 is alike in that of
Google translation model \cite{wu2016googlemt}. It is made of multiple
identical blocks, each of which has a uni-directional LSTM and element-wisely
add its input into its output via a residual edge.

In the logic level 4, inner-attention part, which can be interpreted
as a special weighted-pooling strategy, the processing is a bit tricky.
Because the durations of syllables vary a lot, it is beneficial to
only weight those real frame information, and ignore those filled
frame information due to the maximum LSTMS steps or maximum frame
number\footnote{Based on statistics of syllable durations, we just set maximum frame
number as 50.}. See Equ. \ref{eq:weight}.

\begin{align}
\alpha_{i}= & \begin{cases}
\textrm{softmax}\{f(\mathbf{S_{i}},\mathbf{H})\} & i\in[0,\textrm{syllable\_length})\\
0 & i\in[\textrm{syllable\_length},50)
\end{cases}\label{eq:weight}\\
\mathbf{S}= & \sum\alpha_{i}\cdot\mathbf{S_{i}}
\end{align}
where $\mathbf{S_{i}}$ is the state vector of LSTM, corresponding
to each speech frame. $\mathbf{H}$ is a global and trainable vector,
shared by each syllable.The function $f$ defines how to compute the
importance of each state vector by its real content. The simplest
definition is the inner product.

\subsection{Syllable interaction module}

Pronunciation stress kinds of reflects the focused information of
a whole word, thus, it is natural to consider contextual information.
The work in \cite{li2018automatic} also take advantage of context
of a syllable, but they considers fixed four-syllable contextual information.
In comparison, we take a self-attention \cite{bert,transformer} based
network, which digests words with different number of syllables as
input. There is no need to expand input by filling empty positions.

The logic level 5 includes two parts, $\mathcal{O}(n^{2})$ operations
of self-attention, and $\mathcal{O}(n)$ operations of position-wise
feed forward network.

In the self-attention part, we adopt more efficient bi-linear formula
than inner product for the attention weight $\alpha_{i,j}$, and the
matrix $\mathbf{M}$ is a globally trainable parameter. There are
other alternatives to calculate the weight $\alpha_{i,j}$, such as
more powerful multi-head attention in BERT model \cite{bert,transformer}.
It is not difficult to replace with it, however, we adopt the bi-linear
formula due to two reasons, simple to implement and focused on the
whole network structure itself.

\begin{align}
\alpha_{i,j}= & \textrm{softmax}\{\mathbf{S_{i}}^{T}\mathbf{M}\mathbf{S_{j}}\}\label{eq:self-att-weight}\\
\mathbf{S_{i}}= & \sum_{j}\alpha_{i,j}\cdot\mathbf{S_{j}}
\end{align}

In the position-wise feed forward network part, we use the definition
in \cite{transformer}. It is actually equivalent to two dense networks,
with the first one having the relu activation function and the second
one not.

\begin{equation}
\textrm{FFN}(x)=\textrm{max}(0,xW_{1}+b_{1})W_{2}+b\label{eq:ffn}
\end{equation}

\subsection{Target label}

Generally, we assign scores of 1, 0.5, 0 \footnote{It is only based on experiences, and might not the optimal.}
as our target labels for primary stress, secondary stress, and no
stress respectively.We then use $l1$-norm to convert these label
scores into a probability distribution, and use in our cross-entropy
based loss function. We should note that one word might have more
than one primary stress, thus problem is a not multi-class problem,
but a multi-label problem.

\begin{equation}
\mathcal{L}=-\sum_{syl}p_{\textrm{syl}}^{\textrm{label}}\log P_{syl}^{\textrm{o}}
\end{equation}
where $p_{\textrm{syl}}^{\textrm{label}}$ is the normalized target
label probability of some syllable, and $P_{syl}^{\textrm{o}}$ is
the corresponding output probability from the self-attention blocks.

\section{Experiments}

\subsection{Datasets}

As there lack public datasets with enough wrong stress pronunciations,
we adopt two public datasets, which is usually used for ASR task,
to evaluate the performance of detected\textbf{ true stress }pronunciations;
we also recored a third dataset with one half of wrong stress pronunciation,
to evaluate the performance of detected \textbf{wrong stress} pronunciations.

In practical application, users are more concerned about the correctness
of the primary stress, so we do not predict and measure the \textbf{secondary
stress}, though our model is capable.

Besides, our model is end-to-end based to directly optimize the stress
prediction in the \textbf{word-level}, thus, we do not report measures
of syllable-level stress prediction. All reported results in the experiments
are F-values, which balances the precision rate and recall rate.
\begin{enumerate}
\item LibriSpeech \footnote{http://www.openslr.org/12} dataset, and we
use 360 hours clean read English speech for training, 50 hours for
testing.
\item TedLium dataset, which is talk set with a variety of speakers and
topics. We use 400 hours for training, 50 hours for testing.
\item dictionary based dataset. We have 10 teammates record 2000 vocabularies,
most of which have 3 syllable and 4 syllables \footnote{2-syllable words are much easier. See Table \ref{tbe:total}.},
and pronuciate each word for three time. Totally we have about 6000
word based samples, and a half is from female speakers.
\end{enumerate}
\begin{table*}
\begin{centering}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
Dataset & Model & \emph{\#syllable}=all & 2 & 3 & 4 & 5\tabularnewline
\hline 
\multirow{3}{*}{LibriSpeech} & SVM & 0.80 & 0.822 & 0.783 & 0.730 & 0.652\tabularnewline
\cline{2-7} 
 & Boosting & 0.85 & 0.874 & 0.834 & 0.784 & 0.708\tabularnewline
\cline{2-7} 
 & Ours(summer) & \textbf{0.95} & 0.9619 & 0.9138 & 0.8304 & 0.7232\tabularnewline
\hline 
\multirow{3}{*}{TedLium} & SVM & 0.812 & 0.834 & 0.779 & 0.739 & 0.661\tabularnewline
\cline{2-7} 
 & Boosting & 0.862 & 0.888 & 0.831 & 0.813 & 0.732\tabularnewline
\cline{2-7} 
 & Ours & \textbf{0.951} & 0.9669 & 0.9438 & 0.8804 & 0.7832\tabularnewline
\hline 
\multirow{3}{*}{dictionary} & SVM & 0.69 & 0.712 & 0.682 & 0.682 & 0.643\tabularnewline
\cline{2-7} 
 & Boosting & 0.726 & 0.734 & 0.721 & 0.712 & 0.654\tabularnewline
\cline{2-7} 
 & Ours & \textbf{0.788} & 0.821 & 0.777 & 0.762 & 0.723\tabularnewline
\hline 
\end{tabular}
\par\end{centering}
\caption{In LibriSpeech and TedLium datasets have its own training and testing
data, while as dictionary-data is limited, we just take the best model
trained in LibriSpeech data. Our model adopts the best configuration.
More details can be found in Table \ref{tbe:lstm-level} and \ref{tbe:self-att-level}.}

\label{tbe:total}
\end{table*}

\subsection{Features and systems}

All features used in our systems and baseline systems are based on
syllable. Here for our syllable feature extraction, we use the Maximal
Onset Principle (Pulgram, 1970) to extract syllables from the phoneme
sequence decoded from our automatic speech recognizer.

Four kinds of features are considered in baseline systems, and they
are duration, energy, pitches, and MFCC. Since the absolute duration
of the same syllable within one word can vary from people to people,
we actually measures the relative duration of each syllable within
one word. Regarding the other features, we process in the same way.
They are extracted in the frame level, and normalized at the word
boundary to compute its relative values. We chose 25\% percentile,50\%
percentile, 75\% percentile, minimum and maximum value within the
syllable window. Regarding MFCC, we observe higher dimension benefits
better results. Therefore, we set the dimension of MFCC to 40. Plus
additional delta and delta-delta information, we actually use 120
dimension MFCC related features.
\begin{enumerate}
\item The first baseline system is a SVM based system which is similar to
the one in \cite{svm}. We use Gaussian kernel and default parameter
settings.
\item The second baseline baseline system is gradient-boosting tree based,
sharing exact features with the first baseline. There are some tunable
parameters, such as tree depth, leave number. We report the best result. 
\item Our attention based network model is capable of direct processing
time series features, thus we take energy, pitches and MFCC in all
frames, but we do not use the duration feature. The model is implemented
in Tensorflow, and the optimizer is Adam with default hyper parameters.
The learning rate is 1e-3. We found 10 epoch of train is enough to
reach good performance.
\end{enumerate}

\subsection{Results}

We first look at the performances of all models on the whole datasets
in Table \ref{tbe:total}. Boosting tree based training performs consistently
better than SVM based, because boosting tree has more controllable
parameters to tune in practice. More, tree-based models have no requirement
in the data normalization, and it is hence more robust. Our attention
based network model performs significantly better than boosting tree
based. This is our model theoretically digests time-series features,
and they contains more information than the input feeding into SVM
and boosting tree based .

In LibriSpeech and TedLium datasets, our model has much better ability
to sufficiently fit the data. However, this advantages moderately
decrease in the self-recorded dictionary dataset. We consider there
are two reasons. The first one is different data distribution. The
dictionary dataset is from Chinese accent speakers, while LibriSpeech
data is American English, and TedLium is mixed with a variety of speakers
with different accent. The second one is, both LibriSpeech and TedLium
datasets are supposed to not include wrong stress pronunciations.
This might result in sort of memorizing vocabularies, as well as their
stresses, with any feature set. We could not exclude this possibility,
as it is hard to create a dataset with enough wrong stresses to verify
it. Anyway, our model still reveals better performance than baselines
comparatively. To construct a large dataset with wrong stresses to
improve our model is also our future work.

As the distribution of syllable number of words varies in datasets,
we further have a statistics of model performances on words with different
syllable number. In Table \ref{tbe:total}, generally, our model on
short words, which has no more than 3 syllables, performs quite well
with at least 0.90 F-values. On longer words, all models perform worse,
and our model still holds advance over other two baselines.

\begin{table}
\begin{centering}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
\emph{\#LSTM} & 1 & 2 & 3 & 4 & 5 & 6\tabularnewline
\hline 
\multirow{1}{*}{LibriSpeech} & 0.92 & 0.928 & 0.939 & 0.944 & \textbf{0.951} & 0.948\tabularnewline
\hline 
\multirow{1}{*}{dictionary} & 0.743 & 0.751 & 0.760 & 0.768 & \textbf{0.77} & 0.764\tabularnewline
\hline 
\end{tabular}
\par\end{centering}
\caption{We show the performances from different block numbers of LSTM in the
logic layer 3 in Figure \ref{fig:framework}, where the self-attention
block number is fixed to 1. See Table \ref{tbe:self-att-level}.}

\label{tbe:lstm-level}
\end{table}
In Table \ref{tbe:lstm-level}, we display the performances from different
number of LSTM blocks. Besides testing on the LibriSpeech data, we
also apply the best model into dictionary dataset for testing. We
observed that more LSTM layers strongly contributes to the final performance.
However, when the layer number reaches 6, the performance decreases.
Besides, more LSTM blocks make the training significantly slower.

\begin{table}
\begin{centering}
\begin{tabular}{|c|c|c|c|}
\hline 
\emph{\#self-att} & 0 & 1 & 2\tabularnewline
\hline 
\multirow{1}{*}{LibriSpeech} & 0.941 & \textbf{0.951} & 0.929\tabularnewline
\hline 
\multirow{1}{*}{dictionary} & 0.743 & \textbf{0.77} & 0.760\tabularnewline
\hline 
\end{tabular}
\par\end{centering}
\caption{We show the performances from different number of self-attention blocks
in the logic layer 5 in Figure \ref{fig:framework}, where the LSTM
block number is fixed to 5.}

\label{tbe:self-att-level}
\end{table}
In Table \ref{tbe:self-att-level}, we surprisingly find more self-attention
layers are not helpful to this task, which kind of differs from that
in machine translation experiments \cite{transformer}. We conjecture
our task is comparatively simpler than machine translation task, and
more self-attention layers lead to overfitting. We also tried other
position-wise activation function in Equ. \ref{eq:ffn}, such as one
layer linear network with relu or other activations, and they are
not helpful.

\section{Conclusion}

In this work, we successfully applied two widely used attention techniques
into lexical stress detection problem. Our proposed model directly
takes time series features as input that it could fully explore input
information; and the network structure instrinstically support words
with different number of syllables, without expanding short words,
to reduce input approximation. Experiments also demonstrate the improvements
over baselines systems.

\bibliographystyle{IEEEbib}
\bibliography{refs}

\end{document}

### 2020-06-22 bin/compile.sh

@@ -1,2 +1,2 @@
-pdflatex $1 
-open $1.pdf
+pdflatex paper 
+open paper.pdf

### 2020-06-22 chatbot_classification/aaai_2021/paper.tex
modified:   .gitignore

%% LyX 2.3.1-1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass{article}
\usepackage[latin9]{inputenc}
\usepackage{array}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{graphicx}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}
%% A simple dot to overcome graphicx limitations
\newcommand{\lyxdot}{.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
% Template for GlobalSIP-2018 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\usepackage{spconf}

\def\x{{\mathbf x}}
\def\L{{\cal L}}

\makeatother

\begin{document}
\title{     
  SFC: Few-Shot Text Classification via Similarity Fused with Classification System
}
\name{Jingwen Huang}   
\address{     
  \{hanmei613\}@gmail.com   
}
\maketitle

\begin{abstract}
  Building  conversational chatbot system has become a popular solution to sharing
  the  work  of customer service under various business scenarios. One of the most
  important  applications is the single-turn conversational chatbot aiming at user
  intent  detection, which essentially equals to short-text classification problem
  in  the  field  of  Natural  Language  Processing.  However, each time for a new
  service,  the  chatbot system often needs to perform well in few-shot setups due
  to  lack  of  domain-specific  data,  which  is  still quite hard even if we use
  powerful  pretrained  model  like  Roberta. Therefore, in this paper, we propose
  SFC,  a  system  fusion  of  both  similarity  model and classification model to
  overcome  this  challenge.  Our main contributions are: 1) transfer learning and
  negative  sampling  based  on  sentence-pair  are utilized as remedy for lack of
  data;  2)  multi-task  learning is involved to achieve faster training speed and
  better  performance;  3) model ensembling of classification and similarity model
  guarantees  inference  speed  while keeping high accuracy. Additionally, we also
  conduct  extensive  experiments on four public datasets in few-shot setup (i.e.,
  with  only  5 to 20 training data per class). The experimental results show that
  our system can steadily outperform several competitive baselines by 2 percent in
  average accuracy.
\end{abstract}
\keywords{stress, detection, attention, neural network}

\section{Introduction}
\label{sec:intro}

Single-turn  conversational  chatbots  are  designed to transform existing tasks
that  rely  on human agents, such as classifying customers' questions or queries
to  find  the  corresponding  answer,  into an automatic process based on intent
classification   model.  Since  user  queries  are  usually  much  shorter  than
paragraphs  or  documents,  the chatbot can actually be turned into a short-text
Classification  task  in  Natural  Language Processing. Moreover, at the initial
stage  of  building  chatbots, it's usually extremely hard to collect sufficient
data  for each class. In this way, building a single-turn conversational chatbot
become  a  short-text  classification  problem under few-shot setting(Yu et al.,
2018).

Short  texts are usually more ambiguous in comparison with long texts since they
don't contain enough contextual information, which poses a great challenge for
classification(Chen et al., 2019). In addition, the few-shot scenario(Yu et al.,
2018)  adds  even more difficulties to the classification task since there is no
enough  information  for  the  model  to  learn  for  each  class.  Comparing to
non-pre-trained neural network such as convolutional neural networks (CNNs)(Kim,
2014) and long short term memory networks (LSTMs)(Mousa and Schuller, 2017), the
recently introduced pre-trained language models on large corpus like BERT(Devlin
et  al.,  2019)  and  RoBERTa(Liu et al., 2019) has been proven more powerful in
solving  many  NLP  tasks  including  short-text  classification  for  deficient
data(Madabushi,  H.  T.,  2020).  Especially  for  few-shot  scenarios, transfer
learning  based  on  pre-trained  model  tends  to  do more help to the negative
effects brought by scarcity of training data. Due to the fact that RoBERTa is an
improved  version  of  BERT,  we  build  our SFC chatbot system using RoBERTa as
pre-trained  context-dependent  embeddings.  To  our  knowledge, the most common
approach  is  adding  a  softmax  classifier to the top of RoBERTa(i.e., RoBERTa
classifier),  which  turns  the  problem into a simple text classification task.
However,  despite  the  fact  that  RoBERTa has achieved amazing results in many
Natural  Language  Processing tasks, we still believe it has much more potential
under few-shot setting.

Therefore,  in  this  paper  we  propose  to  involve  similarity  model  (i.e.,
sentence-pair  classifier)  based  on  RoBERTa,  which  can  score  the semantic
similarity between two sentences by multiple cross-attention mechanism(Barkan et
al.,  2019).  A natural idea to enhance model performance in few-shot setting is
to  further  pre-train RoBERTa with target domain data for transfer learning(Sun
et  al.,  2019).  However, it's always not easy to find domain-specific data for
certain  service/product  if  we  try  to further pre-train a RoBERTa classifier
directly.  In  comparison,  it's  relatively  feasible  to  obtain  dataset  for
semantically duplicate sentence pair identification task. That is to say, we can
obtain a further pre-trained similarity model to identify the class with highest
semantic  similarity  level to each user query. Afterwards, we can fine-tune the
similarity  model using sentence pairs sampled from target task dataset based on
negative  sampling  strategy(Bamler  and Mandt, 2020), which can provide us with
more features to learn from limited amount of data.

We  also apply multi-task learning(Caruana, 1993; Collobert and Weston, 2008) in
training  process  to  enhance the training speed and performance. We set up two
different  objectives  for  training. The first one is the regular sentence-pair
similarity  score  which  help the model learn the semantic similarity between a
query  to each existing data point. The second target is to learn the similarity
score  between  a  query  and all the data points of a certain class as a whole.
Specific  knowledge contained in these two tasks can be fully explored to obtain
a faster training speed and higher accuracy.

Another  contribution of this work is that we ensemble the similarity model with
classification  model  at  the  inference  step.  In  contrast with common model
ensembling  methods,  the classification model are used as an auxiliary model in
our  system  to  select promising sentence-pair candidates for similarity model.
The  experiment  results  on  4  short-text  classification  datasets in various
few-shot  settings  show that our system can outperform single model baseline by
at  least  2 percent on average. Besides, we can also control the inference time
for one single query to be within 0.5 seconds, which makes the system applicable
in real-life single-turn chatbot scenario.

\section{Attention based neural network}

\section{Conclusion}

In this work, we successfully applied two widely used attention techniques
into lexical stress detection problem. Our proposed model directly
takes time series features as input that it could fully explore input
information; and the network structure instrinstically support words
with different number of syllables, without expanding short words,
to reduce input approximation. Experiments also demonstrate the improvements
over baselines systems.

\bibliographystyle{IEEEbib}
\bibliography{refs}

\end{document}

### 2020-07-02 chatbot_classification/aaai_2021/paper.tex
update sfc paper citation

@@
   Building  conversational chatbot system has become a popular solution to sharing
-  the  work  of customer service under various business scenarios. One of the most
-  important  applications is the single-turn conversational chatbot aiming at user
-  intent  detection, which essentially equals to short-text classification problem
+  the  work  of customer service under various business scenarios.
+A conversational chatbot needs to detect user's intent given a few words, which essentially equals to short-text classification problem
   in  the  field  of  Natural  Language  Processing.  However, each time for a new
-  service,  the  chatbot system often needs to perform well in few-shot setups due
+  service,  the  task-specific chatbot system often needs to perform well in few-shot setups due
   to  lack  of  domain-specific  data,  which  is  still quite hard even if we use
@@
 \end{abstract}
-\keywords{stress, detection, attention, neural network}
+%\keywords{}
 
@@
 paragraphs  or  documents,  the chatbot can actually be turned into a short-text
-Classification  task  in  Natural  Language Processing. Moreover, at the initial
+Classification\cite{phan2008learning,yan2009dynamic,hua2015short} task  in  Natural  Language Processing. Moreover, at the initial
 stage  of  building  chatbots, it's usually extremely hard to collect sufficient
 data  for each class. In this way, building a single-turn conversational chatbot
-become  a  short-text  classification  problem under few-shot setting(Yu et al.,
-2018).
+become  a  short-text  classification\cite{sriram2010short} problem under few-shot setting\cite{yu2018diverse}.
 
-Short  texts are usually more ambiguous in comparison with long texts since they
+Short  texts\cite{song2014short} are usually more ambiguous in comparison with long texts since they
 don't contain enough contextual information, which poses a great challenge for
-classification(Chen et al., 2019). In addition, the few-shot scenario(Yu et al.,
-2018)  adds  even more difficulties to the classification task since there is no
+classification\cite{chen2019deep}. In addition, the few-shot scenario\cite{yu2018diverse} adds  even more difficulties to the classification task since there is no
 enough  information  for  the  model  to  learn  for  each  class.  Comparing to
-non-pre-trained neural network such as convolutional neural networks (CNNs)(Kim,
-2014) and long short term memory networks (LSTMs)(Mousa and Schuller, 2017), the
-recently introduced pre-trained language models on large corpus like BERT(Devlin
-et  al.,  2019)  and  RoBERTa(Liu et al., 2019) has been proven more powerful in
+non-pre-trained neural network such as convolutional neural networks (CNNs)\cite{kim2014convolutional,zhang2015character,conneau2016very} and long short term memory networks (LSTMs)\cite{mousa2017contextual,liu2016recurrent}, the
+recently introduced pre-trained language models on large corpus like BERT\cite{devlin2018bert}  and  RoBERTa\cite{liu2019roberta} has been proven more powerful in
 solving  many  NLP  tasks  including  short-text  classification  for  deficient
-data(Madabushi,  H.  T.,  2020).  Especially  for  few-shot  scenarios, transfer
+data\cite{madabushi2020cost}.  Especially  for  few-shot  scenarios, transfer
 learning  based  on  pre-trained  model  tends  to  do more help to the negative
@@
 sentence-pair  classifier)  based  on  RoBERTa,  which  can  score  the semantic
-similarity between two sentences by multiple cross-attention mechanism(Barkan et
-al.,  2019).  A natural idea to enhance model performance in few-shot setting is
-to  further  pre-train RoBERTa with target domain data for transfer learning(Sun
-et  al.,  2019).  However, it's always not easy to find domain-specific data for
+similarity between two sentences by multiple cross-attention mechanism\cite{barkan2020scalable}.  A natural idea to enhance model performance in few-shot setting is
+to  further  pre-train RoBERTa with target domain data for transfer learning\cite{sun2019fine}.  However, it's always not easy to find domain-specific data for
 certain  service/product  if  we  try  to further pre-train a RoBERTa classifier
@@
 similarity  model using sentence pairs sampled from target task dataset based on
-negative  sampling  strategy(Bamler  and Mandt, 2020), which can provide us with
+negative  sampling  strategy\cite{bamler2020extreme}, which can provide us with
 more features to learn from limited amount of data.
 
-We  also apply multi-task learning(Caruana, 1993; Collobert and Weston, 2008) in
+We  also apply multi-task learning\cite{caruana1993multitask,collobert2008unified} in
 training  process  to  enhance the training speed and performance. We set up two
@@
 classification  model  at  the  inference  step.  In  contrast with common model
-ensembling  methods,  the classification model are used as an auxiliary model in
+ensembling  methods\cite{breiman1996stacked,schapire1998boosting},  the classification model are used as an auxiliary model in
 our  system  to  select promising sentence-pair candidates for similarity model.
@@
 
-\section{Attention based neural network}
+%\section{Attention based neural network}
 
-\section{Conclusion}
-
-In this work, we successfully applied two widely used attention techniques
-into lexical stress detection problem. Our proposed model directly
-takes time series features as input that it could fully explore input
-information; and the network structure instrinstically support words
-with different number of syllables, without expanding short words,
-to reduce input approximation. Experiments also demonstrate the improvements
-over baselines systems.
+%\section{Conclusion}
 

### 2020-07-25 chatbot_classification/aaai_2021/paper.tex
modified:   paper.pdf   modified:   paper.tex
update model structure figures and Abstract and Introduction Section

@@
 \usepackage{graphicx}
+\usepackage{float}
+\usepackage{subfigure}
 
@@
 \title{     
-  SFC: Few-Shot Text Classification via Similarity Fused with Classification System
+  %SFC: Few-Shot Text Classification via Similarity Fused with Classification System
+  Joint training of classification model and similarity model for low-resource
+  text classification in chatbot
 }
@@
 \begin{abstract}
-  Building  conversational chatbot system has become a popular solution to sharing
-  the  work  of customer service under various business scenarios.
-A conversational chatbot needs to detect user's intent given a few words, which essentially equals to short-text classification problem
-  in  the  field  of  Natural  Language  Processing.  However, each time for a new
-  service,  the  task-specific chatbot system often needs to perform well in few-shot setups due
-  to  lack  of  domain-specific  data,  which  is  still quite hard even if we use
-  powerful  pretrained  model  like  Roberta. Therefore, in this paper, we propose
-  SFC,  a  system  fusion  of  both  similarity  model and classification model to
-  overcome  this  challenge.  Our main contributions are: 1) transfer learning and
-  negative  sampling  based  on  sentence-pair  are utilized as remedy for lack of
-  data;  2)  multi-task  learning is involved to achieve faster training speed and
-  better  performance;  3) model ensembling of classification and similarity model
-  guarantees  inference  speed  while keeping high accuracy. Additionally, we also
-  conduct  extensive  experiments on four public datasets in few-shot setup (i.e.,
+  Building  conversational  chatbot  system  has  become  a  popular solution to customer  services  under various business scenarios. A
+  conversational  chatbot needs to detect user's intent given a few words, which
+  essentially  equals  to  short-text  classification  problem  in  the field of Natural  Language  Processing.
+Moreover,  each  time  for  a  new service, the task-specific  chatbot  system  often needs to perform well in few-shot setups due  to lack of domain-specific data, which is quite a challenge for single-model system such as text classification model system or sentence-pair semantic similarity model system under such a low-resource condition.
+Therefore, in this paper, we propose
+  SFC,  a 2-stage joint system with multi-task training technique for both text classification task and sentence-pair semantic similarity task to
+  overcome  this challenge.
+Furthermore, we additionally propose an improved version of SFC to allow text classification model and sentence-pair model be combined into a joint model organized in hierarchical structure.
+We also
+  conduct extensive experiments on 4 public and 1 private datasets in few-shot setup (i.e.,
   with only 5 to 20 training data per class). The experimental results show that
-  our system can steadily outperform several competitive baselines by 2 percent in
-  average accuracy.
+  our  system can steadily outperform several competitive single-model baselines by 2 percent
+  in average accuracy.
 \end{abstract}
@@
 \label{sec:intro}
+% latest version start
+Task-specific conversational chatbot\cite{wen2016network} are designed to share the working pressure of human customer service agents who are responsible for solving customers' questions or queries about certain products or services.
+Regardless of whether the conversation is single-turn or multi-turn, the essential technical solution behind the chatbot is intent classification model which can identify the correct intent behind user's input text and find the corresponding answer.
 
-Single-turn  conversational  chatbots  are  designed to transform existing tasks
-that  rely  on human agents, such as classifying customers' questions or queries
-to  find  the  corresponding  answer,  into an automatic process based on intent
-classification   model.  Since  user  queries  are  usually  much  shorter  than
-paragraphs  or  documents,  the chatbot can actually be turned into a short-text
-Classification\cite{phan2008learning,yan2009dynamic,hua2015short} task  in  Natural  Language Processing. Moreover, at the initial
-stage  of  building  chatbots, it's usually extremely hard to collect sufficient
-data  for each class. In this way, building a single-turn conversational chatbot
-become  a  short-text  classification\cite{sriram2010short} problem under few-shot setting\cite{yu2018diverse}.
+Although task-specific conversational chatbot already has a wide application in various business and industries, it's still a quite challenging task due to its natural properties of low-resource.
+First, customers' utterance within a conversation is usually quite short and completed in a few words.
+Short text\cite{song2014short} are generally more ambiguous in comparison with long texts such as paragraphs or documents since they don't contain enough contextual information, which poses a great challenge\cite{chen2019deep} for classification task\cite{phan2008learning,yan2009dynamic,hua2015short}.
+Second, at the initial stage of building a chatbot for specific task or service, it's often extremely hard to collect sufficient data samples for each class.
+The reason is that it's usually too expensive and time consuming to extract different ways of natural language expression for each intent class from history conversation log or even manually compose the corpus from nothing.
+Therefore, the key to building a task-specific chatbot with high performance becomes solving the challenge of short-text classification\cite{sriram2010short} problem under few-shot setting\cite{yu2018diverse}.
 
-Short  texts\cite{song2014short} are usually more ambiguous in comparison with long texts since they
-don't contain enough contextual information, which poses a great challenge for
-classification\cite{chen2019deep}. In addition, the few-shot scenario\cite{yu2018diverse} adds  even more difficulties to the classification task since there is no
-enough  information  for  the  model  to  learn  for  each  class.  Comparing to
-non-pre-trained neural network such as convolutional neural networks (CNNs)\cite{kim2014convolutional,zhang2015character,conneau2016very} and long short term memory networks (LSTMs)\cite{mousa2017contextual,liu2016recurrent}, the
-recently introduced pre-trained language models on large corpus like BERT\cite{devlin2018bert}  and  RoBERTa\cite{liu2019roberta} has been proven more powerful in
-solving  many  NLP  tasks  including  short-text  classification  for  deficient
-data\cite{madabushi2020cost}.  Especially  for  few-shot  scenarios, transfer
-learning  based  on  pre-trained  model  tends  to  do more help to the negative
-effects brought by scarcity of training data. Due to the fact that RoBERTa is an
-improved  version  of  BERT,  we  build  our SFC chatbot system using RoBERTa as
-pre-trained  context-dependent  embeddings.  To  our  knowledge, the most common
-approach  is  adding  a  softmax  classifier to the top of RoBERTa(i.e., RoBERTa
-classifier),  which  turns  the  problem into a simple text classification task.
-However,  despite  the  fact  that  RoBERTa has achieved amazing results in many
-Natural  Language  Processing tasks, we still believe it has much more potential
-under few-shot setting.
+\begin{figure}[htbp]
+\centering 
+\subfigure[text classification model structure based on pre-trained transformer]{
+\label{Fig.1.sub.1}
+\includegraphics[scale=0.6]{picture1.pdf}}
+\subfigure[sentence-pair model structure based on cross-attention mechanism]{
+\label{Fig.1.sub.2}
+\includegraphics[scale=0.55]{picture2.pdf}}
+\caption{Model Structure of 2 popular approach for building task-specific conversational chatbot}
+\label{Fig.1.main}
+\end{figure}
 
-Therefore,  in  this  paper  we  propose  to  involve  similarity  model  (i.e.,
-sentence-pair  classifier)  based  on  RoBERTa,  which  can  score  the semantic
-similarity between two sentences by multiple cross-attention mechanism\cite{barkan2020scalable}.  A natural idea to enhance model performance in few-shot setting is
-to  further  pre-train RoBERTa with target domain data for transfer learning\cite{sun2019fine}.  However, it's always not easy to find domain-specific data for
-certain  service/product  if  we  try  to further pre-train a RoBERTa classifier
-directly.  In  comparison,  it's  relatively  feasible  to  obtain  dataset  for
-semantically duplicate sentence pair identification task. That is to say, we can
-obtain a further pre-trained similarity model to identify the class with highest
-semantic  similarity  level to each user query. Afterwards, we can fine-tune the
-similarity  model using sentence pairs sampled from target task dataset based on
-negative  sampling  strategy\cite{bamler2020extreme}, which can provide us with
-more features to learn from limited amount of data.
+One of the most popular approach among existing work was text classification model based on neural network.
+Since the length of the text is quite short, many previous work\cite{wen2016network} choose neural network such as convolutional neural networks (CNNs)\cite{kim2014convolutional,zhang2015character,conneau2016very}
+or long short term memory networks
+(LSTMs)\cite{mousa2017contextual,liu2016recurrent} to accomplish the task of extracting semantic feature from limited amount of words.
+A common model structure is adding a softmax classifier to the top of the neural network.
+Afterwards, pre-trained language models on large corpus like BERT\cite{devlin2018bert} and
+RoBERTa\cite{liu2019roberta} has  been proven more powerful in solving many NLP
+tasks      including      short-text      classification\cite{madabushi2020cost}.
+Especially   for  few-shot  scenarios\cite{yu2018diverse}, pre-trained  model  based on transformers\cite{vaswani2017attention}, shown in Fig.
+\ref{Fig.1.sub.1}, tends  to  do more help to reducing the negative effects brought by scarcity of training data.
 
-We  also apply multi-task learning\cite{caruana1993multitask,collobert2008unified} in
-training  process  to  enhance the training speed and performance. We set up two
-different  objectives  for  training. The first one is the regular sentence-pair
-similarity  score  which  help the model learn the semantic similarity between a
-query  to each existing data point. The second target is to learn the similarity
-score  between  a  query  and all the data points of a certain class as a whole.
-Specific  knowledge contained in these two tasks can be fully explored to obtain
-a faster training speed and higher accuracy.
+Another popular approach among previous work was based on sentence-pair model.
+The motivation of this approach was started from the idea of Information Retrival (IR) based chatbot\cite{jafarpour2010filter, leuski2011npceditor}.
+Having a Q-A (Question-Answer) pairs dataset and user query Q, the IR based conversational system will look up in the Q-A dataset for the pair (Q', A') that best matches query Q through semantic analysis and returns A' as the answer to Q\cite{mnasri2019recent}.
+In this way, sentence-pair model pre-trained on large corpus of semantic similarity identification task can be applied for being used as a tool to identify the class with highest semantic similarity to customer's query.
+A common model structure of pre-trained\cite{devlin2018bert} sentence-pair model is based on multiple cross-attention mechanism\cite{barkan2020scalable}, shown in Fig.
+\ref{Fig.1.sub.2}.
+Due to the fact that many experiment results have shown that RoBERTa\cite{liu2019roberta} is an improved  version  of  BERT, and has achieved amazing results on both text classification and sentence-pairs semantic similarity tasks, we choose RoBERTa as an important baseline approach in this paper.
 
-Another  contribution of this work is that we ensemble the similarity model with
-classification  model  at  the  inference  step.  In  contrast with common model
-ensembling  methods\cite{breiman1996stacked,schapire1998boosting},  the classification model are used as an auxiliary model in
-our  system  to  select promising sentence-pair candidates for similarity model.
-The  experiment  results  on  4  short-text  classification  datasets in various
-few-shot  settings  show that our system can outperform single model baseline by
-at  least  2 percent on average. Besides, we can also control the inference time
-for one single query to be within 0.5 seconds, which makes the system applicable
-in real-life single-turn chatbot scenario.
+Despite the success of these 2 approaches, they still have some limitations in task-specific chatbot scenario.
+As for the text classification model approach, it's quite hard to use data augmentation method to solve the data insufficiency challenge since the it's usually unfeasible to get large amount of domain-specific data when facing a new task.
+With respect to the sentence-pair model approach, though we can obtain large amount of data in semantically duplicate sentence pair identification domain for transfer learning\cite{sun2019fine}, it's still quite hard to perform well on task-specific dataset because the training objective of sentence-pair model is semantic similarity, which is slightly different from the target of classification task.
+That is to say, there always exists some intent classes which cannot be distinguished by each other merely depending on semantic similarity.
+For example, we have 2 user query saying, A: What should I do if I want to change my password?
+B: What is the modification rule if I want to change my password?
+In this case, sentence A is semantically similar to B, since they both express the
+desire for changing password.
+However, it's still reasonable to classify them into 2 intent classes, since A is asking for the method for changing password, while B is asking for the rule to follow when creating a new password.
+
+\begin{figure}[htbp]
+\begin{centering}
+\includegraphics[scale=0.48]{picture3}
+\par\end{centering}
+\caption{\textbf{Network Structure of 2-stage SFC:} a joint system of multi-task for both text classification task and sentence-pair semantic similarity task.}
+\label{fig:ver.1.3}
+\end{figure}
+
+The above limitation motivates us to propose a joint system of both text classification task and sentence-pair semantic similarity task, named SFC here, shown in Fig.
+\ref{fig:ver.1.3}.
+Our goal is to utilize the advantage of the feasibility of transfer learning based on semantic similarity, while in the mean time, add the classification task's target into the training process of sentence-pair model for multi-task learning\cite{caruana1993multitask,collobert2008unified}.
+To obtain such a joint system, we first start with preparation work, which is pre-training a sentence-pair model on external corpus for sentence pair duplication identification, and then find an auxiliary model or tool which can help us sample out top-K most related intent classes.
+This auxiliary model or tool can either be searching engine such as elasticsearch\cite{divya2013elasticsearch} or a text classification model trained on task-specific chatbot data.
+Afterwards, we further fine-tune the sentence-pair model with 2 training tasks: 1) the regular sentence pair similarity tasks.
+Here we use the text classification model as an auxiliary model in this paper to sample sentence pairs for training based on negative sampling strategy\cite{bamler2020extreme}.
+The reason is that a task-specific chatbot often has hundreds of intent classes, which forms too many sentence pairs for training since any two sentences from two different classes can form a sentence-pair of negative sample.
+Besides, according to Bamler\cite{bamler2020extreme}, training on negative samples from most confusing wrong label can help model converge faster and obtain better performance.
+2) the classification task on top-K (here K is a hyperparameter) candidate classes provided by our auxiliary model or tool.
+Here we use the average pooling of the representation given by sentence-pair model for sentence pairs formed by the user input query and the corpus sentences in each class as the feature.
+We stack the task-specific layers on the top of the shared-parameter sentence-pair model structure, which is a classic parameter sharing mechanism\cite{collobert2008unified, subramanian2018learning,liu2019multi} for multi-task\cite{sun2019fine}.
+In this way, specific knowledge contained in these 2 tasks can be fully explored and deeply interact with each other to obtain better overall performance.
+
+However, since the auxiliary tool in joint system mentioned above works in a separate stage from sentence-pair model, we find the the quality of sampled candidate classes might limit the overall performance of SFC, since the candidate classes for each user query is always fixed during the multi-task training process.
+This observation motivates us to further improve SFC into a joint model of sentence-pair model and text classification model in a hierarchical architecture by putting different tasks at different network layers\cite{sogaard2016deep, hashimoto2016joint} and then training them together, shown in Fig \ref{fig:framework}.
+Here, the text classification model involved in joint training process replace the role of auxiliary tools.
+In this way, the sentence pairs selected from top-K classes becomes dynamic, which means the text classification model will also be further optimized to provide better top-K classes pooling result.
+
+We summarize our contributions as follow:
+
+1) We propose a novel joint system named SFC with multi-task training technique designed for task-specific conversational chatbot with low-resource, in which we make full utilization of the advantages brought by both the text classification task and sentence-pair semantic similarity task.
+
+2) To further improve the system performance of SFC, we also propose an innovative joint model structure, in which the text classification model and sentence-pair model are fused into one single model for joint training.
+
+3) Experiment results on 4 public and 1 private short-text classification datasets with respect to intent recognition tasks under conversational chatbot scenario all demonstrated that our proposed SFC joint system with multi-task, as well as the improved version of SFC, can both achieve remarkable improvement comparing to some powerful single-task and single-model baselines, especially under few-shot settings.
+
+\begin{figure*}[t]
+\begin{centering}
+\includegraphics[scale=0.72]{picture4} 
+\par\end{centering}
+\caption{\textbf{Network Structure of hierarchical SFC:} a joint model of sentence-pair model and text classification model organized in hierarchical structure by completing different tasks at different network layers.}
+\label{fig:framework}
+\end{figure*}
+
+% latest version end
 

### 2020-07-26 chatbot_classification/aaai_2021/paper.tex
modified:   paper.pdf   modified:   paper.tex   modified:   picture1.key   modified:   picture1.pdf   modified:   picture2.key

@@
 \centering 
-\subfigure[text classification model structure based on pre-trained transformer]{
+\subfigure[classification model]{
 \label{Fig.1.sub.1}
-\includegraphics[scale=0.6]{picture1.pdf}}
-\subfigure[sentence-pair model structure based on cross-attention mechanism]{
+\includegraphics[scale=0.7]{picture1.pdf}}
+\subfigure[similarity model]{
 \label{Fig.1.sub.2}
 \includegraphics[scale=0.55]{picture2.pdf}}
-\caption{Model Structure of 2 popular approach for building task-specific conversational chatbot}
+\caption{Two popular structures of building task-specific conversational chatbot}
 \label{Fig.1.main}

### 2020-07-30 chatbot_classification/aaai_2021/paper.tex
update

@@
 
+\section{Methodology}
+In this section, we will describe a system of similarity model fused with classification model, named as SFC, in detail.
+We come up with 2 different approaches for implementation of SFC system, in which hierarchical SFC is a further improvement of 2-stage SFC for better performance.
+\subsection{2-stage SFC with multi-task learning}
+The detailed network structure of 2-stage SFC is shown in Fig. \ref{fig:ver.1.3}. It is composed with 2 separate stages in charge of different jobs.
+In stage 1, we can use any auxiliary model or tool to provide top-K most related classes for sampling sentence pairs of both positive samples and negative samples for stage 2.
+Suppose we have a training data set $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$ of $N$ data points, in which $x_{i}$ is the user input query and $y_{i}$ is a single class label from a class label set of $C$ classes in total.
+If we want to generate sentence pair data set $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$, where $(x, x')_{j}$ is sentence pair grouped by 2 user input queries and $l_{j}\in\{0, 1\}$ is similarity class label, see Equ.
+\ref{eq:similarity label},
+\begin{align}
+l_{j}=\begin{cases} \label{eq:similarity label}
+0 & y_{s_1}\neq y_{s_2}\\
+1 & y_{s_1}=y_{s_2}
+\end{cases}
+\end{align}
+directly from original data set $\mathcal{D}$ without any sampling strategy, then $\mathcal{D'}$ will have $M=N^2$ data points of sentence pairs, which might be too time-consuming for the training process of stage 2 since we often have hundreds of class labels under task-specific chatbot scenario.
+Although we may only have a few data points for a single class label, $N$ is still quite a big number.
+
+Therefore, we adopt the idea of adversarial negative sampling strategy raised by \cite{bamler2020extreme}.
+The key idea of this sampling strategy is to train with negative samples that are hard to distinguish from positive samples.
+Now suppose we have a user input query $x_{i}$ as $s_{1}$ and top-K most related class labels set $\mathcal{C'}=\{c'_{1}, \dots, c'_{K}\}$ found by auxiliary model or tool in stage 1, where $K$ is a hyperparameter set by us that controls candidate class number, we apply the adversarial negative sampling strategy into our sentence pair sampling process by the following 2 steps:
+
+\textbf{1.
+positive sentence pair sampling}: During the training process, we have to first make sure that the ground truth class label $y_{i}$ for $x_{i}$ is within the candidate class label set $\mathcal{C'}$.
+If $y_{i}\notin \mathcal{C'}$, we will manually add $y_{i}$ into $\mathcal{C'}$ by replacing $c'_{K}$ with $y_{i}$.
+Afterwards, we will randomly sample $P$ sentences $\{x'_{0},x'_{1}, \dots, x'_{P}\}$ with the same class label as $y_{i}$ from data set $\mathcal{D}$ to form the set of sentence pairs with positive label $\mathcal{P'}_{i}=\{[(x_{i}, x'_{0}), 1], [(x_{i}, x'_{1}), 1], \dots, [(x_{i}, x'_{P}), 1]\}$, where $P$ is also a hyperparameter set by us that controls the number of sentences we should sample from each class.
+
+\textbf{2.
+negative sentence pair sampling}: As for negative sentence pairs, we will also randomly sample $P$ sentences for each class in the negative candidate class label set $\mathcal{C'}\backslash \{y_{i}\}$.
+The class labels in $\mathcal{C'}\backslash \{y_{i}\}$ are the set of most confusing classes comparing to the ground truth ${y_{i}}$, so we assume that the sentence pairs with negative label grouped by user input query $x_{i}$ and sentences with class labels in $\mathcal{C'}\backslash \{y_{i}\}$ are also strong adversarial negative samples that can help enhance the training speed and performance.
+According to the same method as positive sentence pair sampling, we can obtain the set of sentence pairs with negative label as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{0}), 0], [(x_{i}, x'_{1}), 0], ..., [(x_{i}, x'_{P\cdot (K-1)}), 0]\}$
+
+In this way, we can generate the sentence pair data set $\mathcal{D'}$ for stage 2 based on the top-K class label set $\mathcal{C'}$ provided by stage 1 as $\mathcal{D'}=\{\mathcal{P'}_{i}\cup \mathcal{N'}_{i}\}_{i=1}^{N}$, in which we will have $M=N\cdot K\cdot P$ data points of sentence pairs in total.
+
+After explaining the data sampling principle for sentence pairs and how the 2 stages in SFC system connect with each other, let's go deeper into model structure within these 2 stages respectively to see how it works.
+
+\subsubsection{stage 1: classification model for providing top-K classes}
+As for stage 1, our SFC system can adapt to any auxiliary model or even searching tool based on Term Frequency-Inverse
+Document Frequency (TF-IDF) retrieval.
+In this paper, however, we choose to fine-tune RoBERTa on our task-specific data set $\mathcal{D}$ by adding a softmax classifier on top of it, the same as the structure shown in Fig.
+\ref{Fig.1.sub.1}, for better overall performance.
+According to our experimental result, RoBERTa can guarantee that approximately 95\% ground truth label be included in top-5 candidate classes with highest probability after being fine-tuned on task-specific data set with top-1 weighted F score at around 0.75.
+So we use RoBERTa as encoder of classification model in our setting at stage 1 to ensure low limitation for the performance of stage 2.
+
+For single-sentence text classification tasks, given a data point $x_{i}$ with class label $y_{i}$ from data set $\mathcal{D}$, RoBERTa takes the final hidden state $h_{i}$ of the first token [CLS] as the representation for the whole sequence of $x_{i}$.
+Let's suppose we have a linear layer as ${\Phi}^C_{i}=W^Ch_{i}+b^C$, where $W^C$ and $b^C$ are trainable parameters, the probability score for $x_{i}$ can be calculated as $p^C_{i}=softmax(W^Ch_{i}+b^C)=softmax({\Phi}^C_{i})$.
+Then, the loss for stage 1 classification model is shown in Equ.
+\ref{eq:classification loss}, in which the first term $\varPhi_{i,y_{i}}^C$ encourages high probability for prediction of the correct label $y_{i}$.
+
+\begin{equation}
+\begin{aligned}
+\mathcal{L}^{C}&=\frac{1}{N}\sum_{i=1}^{N}-log(\frac{exp(\varPhi_{i,y_{i}}^C)}{\sum_{j=1}^{C}exp(\varPhi_{i,j}^C)}) \\&=\frac{1}{N}\sum_{i=1}^{N}-\varPhi_{i,y_{i}}^C+log(\sum_{j=1}^{C}exp(\varPhi_{i,j}^C))
+\label{eq:classification loss}
+\end{aligned}
+\end{equation}
+
+\subsubsection{stage 2: sentence-pair model for multi-task learning}
+As for stage 2, we also choose RoBERTa as the encoder for sentence pairs, as shown in Fig.
+\ref{fig:ver.1.3}.
+Before sending sentence pairs to Roberta, we pack sentence pairs into a single sequence and separate them with a special token [SEP].
+Roberta will also use a learned embedding to every token indicating whether it belongs to the first sentence or the second one.
+Then, we utilize the cross-attention mechanism inside RoBERTa, and then extract semantic relationship between 2 sentences from the output softmax layer, which is placed on top of the last hidden representation of the [CLS] token.
+
+Before we start to fine-tune our sentence-pair model on task-specific dataset, we first fine-tune RoBERTa on Quora dataset\cite{iyer2017first}, which contains 404,290 potential duplicate question pairs, for transfer learning.
+Then we continue to do multi-task training on sentence-pair dataset $\mathcal{D'}$ sampled from the top-K candidate classes provided by stage 1.
+
+The 2 tasks for stage 2 training process are listed below.
 % latest version end

### 2020-08-01 chatbot_classification/aaai_2021/paper.tex
update

@@
 The 2 tasks for stage 2 training process are listed below.
+
+$\bullet$ \textbf{Task 1: Regular sentence-pair similarity task}
+
+For sentence pair semantic similarity task, given a data point $(x, x')_{i}$ with similarity label $l_{i}$ from data set $\mathcal{D'}=\{[(x,x')_{i},l_{i}]\}_{i=1}^{M}$, Roberta takes the final hidden state $h_{i}$ of the first token [CLS] as the representation for the sequence of packed sentence pair $(x, x')_{i}$.
+Let's suppose we have a linear layer as ${\Phi}^S_{i}=W^Sh_{i}+b^S$, where $W^S$ and $b^S$ are trainable parameters, and the probability score for $(x, x')_{i}$ can be calculated as $p^S_{i}=softmax({\Phi}^S_{i})$.
+
+Due to the fact that sentence pairs within the same class is much less than sentence pairs from different classes, the data set $\mathcal{D'}$ is imbalanced.
+Therefore, we will accommodate a weight variable $w^S = [K-1, 1]$ to the loss to eliminate the bias brought by imbalanced data, shown in Equ.
+\ref{eq:similarity loss}.
+
+\begin{equation}
+\begin{aligned}
+\mathcal{L}^{S}&=\frac{1}{M}\sum_{i=1}^{M}-w^S_{l_i}\cdot log(\frac{exp(\varPhi_{i,l_{i}}^S)}{\sum_{j=0}^{1}exp(\varPhi_{i,j}^S)}) \\&=\frac{1}{M}\sum_{i=1}^{M}-w^S_{l_i}\cdot \varPhi_{i,l_{i}}^S+w^S_{l_i}\cdot log(\sum_{j=0}^{1}exp(\varPhi_{i,j}^S))
+\label{eq:similarity loss}
+\end{aligned}
+\end{equation}
+
+$\bullet$ \textbf{Task 2: Classification task on top-K classes based on sentence-pair model}
+
+As for top-K classification task, we share the same sentence-pair similarity model structure with task 1.
+The only difference is that we add a task-specific average pooling layer, shown in Fig.
+\ref{fig:ver.1.3} to implement the classification task based on sentence-pair model.
+
+We already know that the size of ${\Phi}^S$ in task 1 is $M\times 2=(N\cdot K\cdot P)\times 2$, where $N$ is the total number of data points in original training data $\mathcal{D}$, $K$ is a hyperparameter that controls the number of candidate classes provided by stage 1, and $P$ is also a hyperparameter that controls the number of sentences we should randomly sample from each candidate class.
+Now, for the average pooling layer, we first reshape ${\Phi}^S$ into the size of $N\times K\times P\times 2$, and then split it into ${\Phi}^{K,pos}$ and ${\Phi}^{K,neg}$, and both of them will have the size of $N\times K\times P$.
+In this way, ${\Phi}^{K,pos}$ can represent the level of similarity for each sentence pair, and in the mean time, ${\Phi}^{K,neg}$ can represent the level of dissimilarity for each sentence pair.
+Then, we can do average pooling for each candidate class among the top-K classes as shown in Equ.
+\ref{eq:average pooling:1} and Equ.
+\ref{eq:average pooling:2}.
+
+\begin{align}
+{\xi}_{i,j}^{K,pos} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,pos} \label{eq:average pooling:1}\\
+{\xi}_{i,j}^{K,neg} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,neg}
+\label{eq:average pooling:2}
+\end{align}
+
+With the average pooling result ${\xi}^{K,pos}$ and ${\xi}^{K,neg}$, we also generate a top-K class label $l^{K}_i\in [1,\dots,K]$ for each ${\xi}^{K,pos}_{i}$ and  ${\xi}^{K,neg}_{i}$.
+The loss for top-K classification task is shown in Equ.
+\ref{eq:top-k classification loss}.
+In Equ.
+\ref{eq: pos top-k loss} and Equ.
+\ref{eq: neg top-k loss}, the first term $\xi_{i,l^{K}_{i}}^{K,pos}$ and $\xi_{i,l^{K}_{i}}^{K,neg}$ encourage high level of similarity and low level of dissimilarity for prediction of the correct label $l^{K}_i$ within the top-K candidate classes.
+
+\begin{align}
+\mathcal{L}^{K} = \frac{1}{N}\sum_{i=1}^{N}(\mathcal{L}^{K,pos}_{i} - \mathcal{L}^{K,neg}_{i})
+\label{eq:top-k classification loss}
+\end{align}
+where,
+
+\begin{equation}
+\begin{aligned}
+\mathcal{L}^{K,pos}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,pos})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,pos})}) \\
+&= -\xi_{i,l^{K}_{i}}^{K,pos} + log(\sum_{j=1}^{K}exp(\xi_{i,j}^{K,pos}))
+\label{eq: pos top-k loss}
+\end{aligned}
+\end{equation}
+
+\begin{equation}
+\begin{aligned}
+\mathcal{L}^{K,neg}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,neg})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,neg})}) \\
+&= -\xi_{i,l^{K}_{i}}^{K,neg} + log(\sum_{j=1}^{K}exp(\xi_{i,j}^{K,neg}))
+\label{eq: neg top-k loss}
+\end{aligned}
+\end{equation}
+
+Therefore, the overall loss function for multi-task learning in stage 2 is shown in Equ.
+\ref{eq: 2-stage SFC loss}.
+The training objective of stage 2 is to minimize the weighted sum of task-specific losses.
+Here $\alpha_S$ and $\alpha_K$ are weights of task 1 and task 2 respectively, which are $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting.
+
+\begin{align}
+\mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K
+\label{eq: 2-stage SFC loss}
+\end{align}
+
+\subsection{hierarchical SFC with joint model structure}
+Despite the outstanding experimental result of 2-stage SFC on various tasks, we still find a limitation brought by the 2-stage system structure.
+In 2-stage SFC, Stage 1 and stage 2 are separate, so they do not interact with each other during training.
+In this case, the performance of stage 1 can limit the potential of stage 2, meanwhile, stage 2 also cannot give training feedback back to stage 1 for fine-tuning.
+
+Therefore, to further improve the overall performance of SFC, we proposed a hierarchical SFC joint model structure, shown in Fig.
+\ref{fig:framework}.
+In hierarchical SFC, classification model is being placed in lower level to dynamically provide top-K candidate classes for the sentence-pair similarity model placed in higher level through a top-K pooling layer.
+In this way, classification model and similarity model can be merged into one single joint-model for multi-task training, thus avoiding the limitation brought by 2 separate stage structure.
+
+There are 3 tasks in total during the training process of hierarchical SFC, shown in Fig.
+\ref{fig:framework}, and the overall loss is also the weighted sum of all the task-specific losses, shown in Equ.
+\ref{eq: hierachical SFC loss}.
+Here, $\alpha_S$, $\alpha_K$ and $\alpha_C$ are the weights for task 1: sentence-pair similarity, task 2: top-K classification and task 3: general single sentence classification respectively, which are $\alpha_S=0.25$,  $\alpha_K=0.25$ and $\alpha_C=0.5$ in our setting.
+
+\begin{align}
+\mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K + \alpha_C \mathcal{L}^C
+\label{eq: hierachical SFC loss}
+\end{align}
+
+Finally, when doing inference, for each user input query $x$, we will choose the class label that contains the sentence $x'$ with highest similarity score $\varPhi$, after being packed into a sentence pair $(x, x')$ with query $x$, as our final result for prediction.
 % latest version end

### 2020-08-03 chatbot_classification/aaai_2021/paper.tex
update

@@
 Finally, when doing inference, for each user input query $x$, we will choose the class label that contains the sentence $x'$ with highest similarity score $\varPhi$, after being packed into a sentence pair $(x, x')$ with query $x$, as our final result for prediction.
+
+\section{Experiments}
+In this section, we conduct extensive experiments over 5 task-specific dataset to evaluate the performance of our proposed SFC system and the effectiveness of the methodology of multi-task learning and hierachical joint-model structure under low-data settings.
+
+\subsection{Datasets}
+The dataset used in our experiments aims to help us study low-resource text classification problem under task-specific conversational chatbot scenario.
+Therefore, we keep all the dataset under low-resource chatbot corpus setting, which is a large number of class labels (50-250) with a few examples(5-20) in short text for each class, by sampling smaller subsets from the full scale when the raw datasets are oversized, see Table \ref{tbe:dataset statistic}.
+
+According to the task and domain, we categorize our experimental datasets into the following 3 categories:
+
+$\bullet$ \textbf{full-scale real-world task-specific faq chatbot dataset}
+
+\textbf{ITG} is a real-world FAQ chatbot dataset composed of question and answer pairs about online English teaching.
+It contains 3,938 sample questions for 228 class labels, where each class label corresponds to an unique answer for a bunch of similar sample questions.
+
+We divide the whole dataset into 3 folds randomly with approximately the same amount of data within each fold, and then choose 2 folds as the training set, the remaing 1 fold as the test set for our experiments.
+We can obtain 3 different combinations among the 3 folds, and we will use the average experimental results of these 3 combinations as the final evaluation result for this dataset.
+
+$\bullet$ \textbf{subset of customer review dataset for extreme classification}
+
+\begin{table*}
+\begin{centering}
+
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline 
+Dataset & Domain & \#Class & \#Samples & \#Samples/Class & Experimental Settings\tabularnewline
+\hline 
+ITG & FAQ chatbot & 228 & 3938 & 17 & 3-fold\tabularnewline
+\hline 
+Amazon-670k & Product review & 250 & 1942 & 8 & class sampling\tabularnewline
+\hline 
+HWU64 & Intent detection & 64 & [320, 640, 960, 1280] & [5, 10, 15, 20] & data sampling\tabularnewline
+\hline 
+CLINC150 & Intent detection & 150 & [750, 1500, 2250] & [5, 10, 15] & data sampling\tabularnewline
+\hline 
+BANKING77 & Intent detection & 77 & [385, 770, 1155, 1540] & [5, 10, 15, 20] & data sampling\tabularnewline
+\hline 
+\end{tabular}
+\par\end{centering}
+\caption{Key statistics for experimental datasets and few shot settings}
+
+\label{tbe:dataset statistic}
+\end{table*}
+
 % latest version end

### 2020-08-06 chatbot_classification/aaai_2021/paper.tex
update

@@
 l_{j}=\begin{cases} \label{eq:similarity label}
-0 & y_{s_1}\neq y_{s_2}\\
-1 & y_{s_1}=y_{s_2}
+0 & y_{x}\neq y_{x'}\\
+1 & y_{x}=y_{x'}
 \end{cases}
@@
 Therefore, we adopt the idea of adversarial negative sampling strategy raised by \cite{bamler2020extreme}.
-The key idea of this sampling strategy is to train with negative samples that are hard to distinguish from positive samples.
-Now suppose we have a user input query $x_{i}$ as $s_{1}$ and top-K most related class labels set $\mathcal{C'}=\{c'_{1}, \dots, c'_{K}\}$ found by auxiliary model or tool in stage 1, where $K$ is a hyperparameter set by us that controls candidate class number, we apply the adversarial negative sampling strategy into our sentence pair sampling process by the following 2 steps:
+The key idea of this sampling strategy is to train with negative samples that are hard to be distinguished from positive samples.
+Now suppose we have a user input query $x_{i}$ and top-K most related class labels set $\mathcal{C'}=\{c'_{1}, \dots, c'_{K}\}$ found by auxiliary model or tool in stage 1, where $K$ is a hyperparameter set by us that controls candidate class number, we apply the adversarial negative sampling strategy into our sentence pair sampling process by the following 2 steps:
 
@@
 negative sentence pair sampling}: As for negative sentence pairs, we will also randomly sample $P$ sentences for each class in the negative candidate class label set $\mathcal{C'}\backslash \{y_{i}\}$.
-The class labels in $\mathcal{C'}\backslash \{y_{i}\}$ are the set of most confusing classes comparing to the ground truth ${y_{i}}$, so we assume that the sentence pairs with negative label grouped by user input query $x_{i}$ and sentences with class labels in $\mathcal{C'}\backslash \{y_{i}\}$ are also strong adversarial negative samples that can help enhance the training speed and performance.
+The class labels in $\mathcal{C'}\backslash \{y_{i}\}$ are the set of most confusing classes comparing to the ground truth ${y_{i}}$, so we assume that the sentence pairs with negative label grouped by user input query $x_{i}$ and sentences with class labels in $\mathcal{C'}\backslash \{y_{i}\}$ are also strong adversarial negative samples for sentence-pair similarity model that can help enhance the training speed and performance.
 According to the same method as positive sentence pair sampling, we can obtain the set of sentence pairs with negative label as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{0}), 0], [(x_{i}, x'_{1}), 0], ..., [(x_{i}, x'_{P\cdot (K-1)}), 0]\}$
@@
 \ref{Fig.1.sub.1}, for better overall performance.
-According to our experimental result, RoBERTa can guarantee that approximately 95\% ground truth label be included in top-5 candidate classes with highest probability after being fine-tuned on task-specific data set with top-1 weighted F score at around 0.75.
+According to our experimental result, RoBERTa can guarantee that approximately 95\% ground truth label be included in top-5 candidate classes with highest probability after being fine-tuned on task-specific data set with experimental result measured by F-score at around 0.75.
 So we use RoBERTa as encoder of classification model in our setting at stage 1 to ensure low limitation for the performance of stage 2.
@@
 Before sending sentence pairs to Roberta, we pack sentence pairs into a single sequence and separate them with a special token [SEP].
-Roberta will also use a learned embedding to every token indicating whether it belongs to the first sentence or the second one.
+Roberta will also add a learned embedding to every token indicating whether it belongs to the first sentence or the second one.
 Then, we utilize the cross-attention mechanism inside RoBERTa, and then extract semantic relationship between 2 sentences from the output softmax layer, which is placed on top of the last hidden representation of the [CLS] token.
@@
 
+\begin{table*}
+\begin{centering}
+
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline 
+Dataset & Domain & \#Class & \#Samples & \#Samples/Class & Experimental Settings\tabularnewline
+\hline 
+ITG & FAQ chatbot & 228 & 3938 & 17 & 3-fold\tabularnewline
+\hline 
+Amazon-670k & Product review & 250 & 1942 & 8 & class sampling\tabularnewline
+\hline 
+HWU64 & Intent detection & 64 & [320, 640, 960, 1280] & [5, 10, 15, 20] & data sampling\tabularnewline
+\hline 
+CLINC150 & Intent detection & 150 & [750, 1500, 2250] & [5, 10, 15] & data sampling\tabularnewline
+\hline 
+BANKING77 & Intent detection & 77 & [385, 770, 1155, 1540] & [5, 10, 15, 20] & data sampling\tabularnewline
+\hline 
+\end{tabular}
+\par\end{centering}
+\caption{Key statistics for experimental datasets and few shot settings}
+
+\label{tbe:dataset statistic}
+\end{table*}
+
 \subsection{hierarchical SFC with joint model structure}
@@
 
-Therefore, to further improve the overall performance of SFC, we proposed a hierarchical SFC joint model structure, shown in Fig.
+Therefore, to further improve the overall performance of SFC, we proposed a hierarchical joint model structure, shown in Fig.
 \ref{fig:framework}.
-In hierarchical SFC, classification model is being placed in lower level to dynamically provide top-K candidate classes for the sentence-pair similarity model placed in higher level through a top-K pooling layer.
+In hierarchical SFC, classification model is being placed in lower layer level to dynamically provide top-K candidate classes for the sentence-pair similarity model placed in higher layer level through a top-K pooling layer.
 In this way, classification model and similarity model can be merged into one single joint-model for multi-task training, thus avoiding the limitation brought by 2 separate stage structure.
@@
 
+\textbf{Amazon-670K} is a customer product review dataset for text classification task from the extreme classification repository with full data containing 670,091 class labels, 285,176 training samples and 150875 test samples\cite{bhatia2016extreme}.
+As the data set contains multiple class labels per training sample, we keep only the first class label for each data point.
+Besides, we also randomly sampled 250 class labels from all the classes that contain only 5-15 data points.
+In this way, we simulate the low-resource chatbot corpus setting with the subset of 1,942 training samples and 716 test samples for 250 class labels.
+
+$\bullet$ \textbf{subset of recently-released intent detection datasets}.
+
+From our point of view, task-specific chatbot usually starts with small amount of data at the initial stage.
+As more and more customers start to communicate with the chatbot, more data can be extracted from conversation log.
+Base on these assumptions, we do experiments on the following 3 intent detection dataset under sampling method similar to the approach in \cite{casanueva2020efficient} but in more sophisticated few-shot settings, while keeping the same test sets for each experiment to see the change of the improvement scale with decreasing data amount.
+
+\textbf{HWU64} is a intent detection dataset designed for home robot scenario\cite{liu2019benchmarking}.
+It aims at the specific task of capturing the intent for different user requests to home robot and finding the corresponding answer.
+The raw dataset contains 25,716 data points for 64 class labels through crowdsourcing, which raises much more data than common real-world circumstances.
+Therefore, we experiment with the setups where only 5, 10, 15 and 20 training data points are available for each class label by random sampling.
+
+\textbf{CLINC150} is a dataset designed for task-oriented systems with 23,700 queries that are short and unstructured for 150 intents, in the same style made by real users through crowdsourcing\cite{larson2019evaluation}.
+Here, we sample 5, 10 and 15 training data points for each intent class label by random sampling for our experimental setup.
+
+\textbf{BANKING77} is a intent detection dataset for bank customer services.
+The raw dataset contains 13,084 data points for 77 class labels\cite{casanueva2020efficient}.
+Here, we sample 5, 10, 15, 20 training data points for each class label by random sampling for our experimental setup.
+
+\begin{table*}
+\begin{centering}
+\scalebox{0.8}{
+\begin{tabular}{|c|ccc|cccc|cccc|c|c|}
+\hline 
+\multicolumn{1}{|c|}{\multirow{2}*{\textbf{Models}} }& \multicolumn{3}{c|}{\textbf{CLINC150}}& \multicolumn{4}{c|}{\textbf{BANKING77}}& \multicolumn{4}{c|}{\textbf{HWU64}}& \ \ \ \textbf{ITG} \ \ \ & \textbf{Amazon-670k}\tabularnewline
+\cline{2-14}
+\multicolumn{1}{|c|}{} & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & \textbf{Full} & \textbf{Full}\tabularnewline
+\hline
+BERT-large & \multirow{2}*{$0.8080$} & \multirow{2}*{$0.8904$} & \multirow{2}*{$0.9265$} & \multirow{2}*{$0.578$} & \multirow{2}*{$0.8004$} & \multirow{2}*{$0.8518$} & \multirow{2}*{$0.8827$} & \multirow{2}*{$0.4711$} & \multirow{2}*{$0.5963$} & \multirow{2}*{$0.6342$} & \multirow{2}*{$0.7010$} & \multirow{2}*{$0.7485$} & \multirow{2}*{$0.6658$}\tabularnewline
+(classification) & & & & & & & & & & & & &\tabularnewline
+\hline
+ALBERT-xxlarge & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-}\tabularnewline
+(classification) & & & & & & & & & & & & &\tabularnewline
+\hline
+RoBERTa-base & \multirow{2}*{$0.8732$} & \multirow{2}*{$0.9254$} & \multirow{2}*{$0.9363$} & \multirow{2}*{$0.7305$} & \multirow{2}*{$0.8654$} & \multirow{2}*{$0.8808$} & \multirow{2}*{$0.9080$} & \multirow{2}*{$0.5831$} & \multirow{2}*{$0.6790$} & \multirow{2}*{$0.7064$} & \multirow{2}*{$0.7100$} & \multirow{2}*{$0.7734$} & \multirow{2}*{$0.6708$}\tabularnewline
+(classification) & & & & & & & & & & & & &\tabularnewline
+\hline
+RoBERTa-large & \multirow{2}*{$0.8974$} & \multirow{2}*{$0.9372$} & \multirow{2}*{$0.9508$} & \multirow{2}*{$0.7690$} & \multirow{2}*{$0.8728$} & \multirow{2}*{$0.8966$} & \multirow{2}*{$0.9099$} & \multirow{2}*{$0.6044$} & \multirow{2}*{$0.7002$} & \multirow{2}*{$0.7129$} & \multirow{2}*{$0.7436$} & \multirow{2}*{$0.7990$} & \multirow{2}*{$0.7156$}\tabularnewline
+(classification) & & & & & & & & & & & & &\tabularnewline
+\hline
+RoBERTa-large & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-}\tabularnewline
+(similarity) & & & & & & & & & & & & &\tabularnewline
+\hline
+2-stage SFC & \multirow{2}*{$0.8979$} & \multirow{2}*{$0.9457$} & \multirow{2}*{$0.9517$} & \multirow{2}*{$0.7975$} & \multirow{2}*{$0.8818$} & \multirow{2}*{$0.8962$} & \multirow{2}*{$0.9109$} & \multirow{2}*{$0.6477$} & \multirow{2}*{$0.7055$} & \multirow{2}*{$0.7200$} & \multirow{2}*{$0.7232$} & \multirow{2}*{$0.7972$} & \multirow{2}*{$0.7189$}\tabularnewline
+(task1 only) & & & & & & & & & & & & &\tabularnewline
+\hline
+2-stage SFC & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-}\tabularnewline
+(task2 only) & & & & & & & & & & & & &\tabularnewline
+\hline
+2-stage SFC & \multirow{2}*{$0.9167$} & \multirow{2}*{$0.9456$} & \multirow{2}*{$0.9571$} & \multirow{2}*{$0.7954$} & \multirow{2}*{$0.8854$} & \multirow{2}*{$0.8931$} & \multirow{2}*{$0.9192$} & \multirow{2}*{$0.6525$} & \multirow{2}*{$0.7001$} & \multirow{2}*{$0.7168$} & \multirow{2}*{$0.7476$} & \multirow{2}*{$\textbf{0.8124}$} & \multirow{2}*{$0.7364$}\tabularnewline
+(task1 + task2) & & & & & & & & & & & & &\tabularnewline
+\hline
+\multirow{2}*{Hierarchical SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline
+ & & & & & & & & & & & & &\tabularnewline
+\hline
+\end{tabular}
+}
+\par\end{centering}
+\caption{F-scores on five task-specific dataset for text classification in chatbot under low resource.
+For ITG, we keep the full dataset.
+For Amazon-670k, we randomly sampled 250 classes with training sample numbers within 5-15 samples per class.
+For CLINC150, BANKING77, HWU64, we set up various few-shot settings (5/10/15/20 samples per class) while keeping the test set to be fixed.
+The highest scores for each data setting are marked in bold.}
+
+\label{tbe:table2}
+\end{table*}
+
+\subsection{Baselines}
+We choose 3 groups of representative baselines:
+
+\textbf{Group 1: single-task classification model.} This group of baseline models are based on the network structure for classification model shown in \ref{Fig.1.sub.1}.
+As for the pretrained model, we choose RoBERTa, BERT and ALBERT, all of which are among the most powerful pretrained models that achieve outstanding results in many NLP tasks, in our experimental setting.
+Since we apply RoBERTa in our SFC system, we naturally adopt single-task classification model based on RoBERTa-large and RoBERTa-base as our baseline models.
+Besides, we also adopt the baseline pre-trained model BERT-large\cite{devlin2018bert} and recently released ALBERT-xxlarge\cite{lan2019albert} for comparison.
+Since we use different few-shot settings from \cite{casanueva2020efficient} for those intent detection datasets, we also use BERT-large tuned on our few-shot settings as an essential reference for experimental results.
+
+\textbf{Group 2: single-task similarity model.} This group of baseline models are based on network structure for similarity model shown in \ref{Fig.1.sub.2}.
+We choose RoBERTa-large for the pretrained model part as an powerful baseline.
+But during the evaluation step, we use elastic search to do a rough filter for candidate sentence pairs to guarantee a reasonable inference time for each user query.
+
+\textbf{Group 3: SFC system with ablation study.} This group of baseline is based on the network structure of 2-stage SFC shown in \ref{fig:ver.1.3}.
+We conduct ablation study by introducing single task SFC system with only Task 1 or Task 2 to investigate the influence of each component within the total loss.
+
+\subsection{Implementation Details}
+For our SFC system, we use RoBERTa-large as the pretrained model for both classification task and sentence-pair similarity task.
+We further fine-tune our SFC system on task-specific datasets with max sequence length of 128, learning rate of 1.5e-5 for RoBERTa-large pretrained model and learning rate of 5e-4 for task-specific layer with polynomial decay and Adam optimizer.
+Also, we set the max number of the epoch to 100 and save the best model on validation set based on test result in F-score.
+We also report the F-score as the main evaluation measure for all experimental results.
+
+For the experiments in Table \ref{tbe:table2}, we empirically set the hyperparameter to be $K=5$ and $P=10$ for all SFC variants.
+In Table \ref{tbe:table3}, we conduct extensive experiments to see the performance of SFC system under various hyperparameter settings.
+
+\subsection{Result Analysis}
+
+Table \ref{tbe:table2} presents the results for each experimental data and model set-up in detail.
+The performance of each model is measured in F-score on the fixed test set for each data set.
+The overall performance of SFC system is better than all the competitive single-model baseline models on five experimental datasets.
+This observation gives us a general idea that classification model and similarity model can actually provide each other with complementary information, and combining them together into a joint system can effectively enhance the overall capability based on richer extracted semantic information.
+However the relative performance among all the variants of SFC also seems to depend on some specific charateristic of each data set.
+Therefore, we did the following more detailed analysis from several different aspect.
+
 \begin{table*}
@@
 
-\begin{tabular}{|c|c|c|c|c|c|}
+\begin{tabular}{|c|c|c|c|c|c|c|}
 \hline 
-Dataset & Domain & \#Class & \#Samples & \#Samples/Class & Experimental Settings\tabularnewline
+\multicolumn{1}{|c|}{\multirow{2}*{Dataset}}&\multicolumn{1}{c|}{\multirow{2}*{Model}}& $K=3$ & $K=5$ & $K=10$ & $K=15$ & $K=20$\tabularnewline
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & $P=20$ & $P=10$ & $P=5$ & $P=4$ & $P=3$\tabularnewline
 \hline
-ITG & FAQ chatbot & 228 & 3938 & 17 & 3-fold\tabularnewline
+\multicolumn{1}{|c|}{\multirow{2}*{ITG}}& 2-stage SFC & 0.05 & 0.05 & 0.05 & 0.05 & 0.05\tabularnewline
+\cline{2-7}
+\multicolumn{1}{|c|}{} & Hierarchical SFC & 0.05 & 0.05 & 0.05 & 0.05 & 0.05\tabularnewline
 \hline
-Amazon-670k & Product review & 250 & 1942 & 8 & class sampling\tabularnewline
-\hline 
-HWU64 & Intent detection & 64 & [320, 640, 960, 1280] & [5, 10, 15, 20] & data sampling\tabularnewline
-\hline 
-CLINC150 & Intent detection & 150 & [750, 1500, 2250] & [5, 10, 15] & data sampling\tabularnewline
-\hline 
-BANKING77 & Intent detection & 77 & [385, 770, 1155, 1540] & [5, 10, 15, 20] & data sampling\tabularnewline
+\multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& 2-stage SFC & 0.05 & 0.05 & 0.05 & 0.05 & 0.05\tabularnewline
+\cline{2-7}
+\multicolumn{1}{|c|}{} & Hierarchical SFC & 0.05 & 0.05 & 0.05 & 0.05 & 0.05\tabularnewline
 \hline
@@
 \par\end{centering}
-\caption{Key statistics for experimental datasets and few shot settings}
+\caption{We show the performance of SFC from different settings of hyperparameters for $K$, the candidate class number, and $P$, the sample number for each class.}
 
-\label{tbe:dataset statistic}
+\label{tbe:table3}
 \end{table*}

### 2020-08-08 chatbot_classification/aaai_2021/paper.tex
update

@@
 \hline
-ALBERT-xxlarge & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-}\tabularnewline
+ALBERT-xxlarge & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{$0.1422$} & \multirow{2}*{$0.2057$} & \multirow{2}*{$0.5723$} & \multirow{2}*{$0.5912$} & \multirow{2}*{$0.6601$} & \multirow{2}*{$0.6893$}\tabularnewline
 (classification) & & & & & & & & & & & & &\tabularnewline
@@
 \hline
-RoBERTa-large & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-}\tabularnewline
+RoBERTa-large & \multirow{2}*{$0.8266$} & \multirow{2}*{$0.8861$} & \multirow{2}*{$0.9023$} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{$0.5425$} & \multirow{2}*{$0.6164$} & \multirow{2}*{$0.6503$} & \multirow{2}*{$0.6729$} & \multirow{2}*{$0.7418$} & \multirow{2}*{$0.6362$}\tabularnewline
 (similarity) & & & & & & & & & & & & &\tabularnewline
@@
 
+\begin{table*}
+\begin{centering}
+
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+\multicolumn{1}{|c|}{\multirow{2}*{Dataset}}&\multicolumn{1}{c|}{\multirow{2}*{Model}}& $K=3$ & $K=5$ & $K=10$ & $K=15$ & $K=20$\tabularnewline
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & $P=20$ & $P=10$ & $P=5$ & $P=4$ & $P=3$\tabularnewline
+\hline
+\multicolumn{1}{|c|}{\multirow{2}*{ITG}}& 2-stage SFC & 0.05 & $0.8124$ & 0.05 & 0.05 & 0.05\tabularnewline
+\cline{2-7}
+\multicolumn{1}{|c|}{} & Hierarchical SFC & 0.05 & $0.8114$ & 0.05 & 0.05 & 0.05\tabularnewline
+\hline
+\multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& 2-stage SFC & 0.05 & $0.7364$ & 0.05 & 0.05 & 0.05\tabularnewline
+\cline{2-7}
+\multicolumn{1}{|c|}{} & Hierarchical SFC & 0.05 & $0.7445$ & 0.05 & 0.05 & 0.05\tabularnewline
+\hline
+\end{tabular}
+\par\end{centering}
+\caption{We show the performance of SFC from different settings of hyperparameters for $K$, the candidate class number, and $P$, the sample number for each class.}
+
+\label{tbe:table3}
+\end{table*}
+
 \subsection{Result Analysis}
@@
 
-\begin{table*}
-\begin{centering}
+First, we turn to compare among the four SFC variants.
+We conduct ablation experiments to study the benefits brought by multi-task training by comparing multi-task 2-stage SFC with single-task 2-stage SFC.
+We can see from Table \ref{tbe:table2} that 2-stage SFC with only task 1 (sentence-pair similarity task) degrades by 0.65 percent on average and 2-stage SFC with only task 2 (top-K classification task) degrades by 0.3 percent on average.
+The degradation indicates that training with these 2 tasks together in SFC can effectively help the sentence-pair model extract more knowledge from the limited amount of data.
+Besides, task 2 degrades 0.35 percent less than task 1.
+This observation suggests that task 2 may play a relatively more important role in multi-task learning, which leads us to put larger weight $\alpha_{K}$ to the loss $\mathcal{L}^{K}$ of task 2 when calculating the total loss $\mathcal{L}$.
+Also, we can see that the hierachical SFC steadily outperforms 2-stage SFC on 5 diverse datasets by 2 percents on average.
+This observation supports the idea that the hierachical joint model structure can alleviate the limitation brought by the lack of interaction between similarity model and classification model in 2-stage SFC.
+Therefore, for the following analysis, we will focus on the comparison between hierachical SFC and the other baseline models.
 
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
-\multicolumn{1}{|c|}{\multirow{2}*{Dataset}}&\multicolumn{1}{c|}{\multirow{2}*{Model}}& $K=3$ & $K=5$ & $K=10$ & $K=15$ & $K=20$\tabularnewline
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & $P=20$ & $P=10$ & $P=5$ & $P=4$ & $P=3$\tabularnewline
-\hline
-\multicolumn{1}{|c|}{\multirow{2}*{ITG}}& 2-stage SFC & 0.05 & 0.05 & 0.05 & 0.05 & 0.05\tabularnewline
-\cline{2-7}
-\multicolumn{1}{|c|}{} & Hierarchical SFC & 0.05 & 0.05 & 0.05 & 0.05 & 0.05\tabularnewline
-\hline
-\multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& 2-stage SFC & 0.05 & 0.05 & 0.05 & 0.05 & 0.05\tabularnewline
-\cline{2-7}
-\multicolumn{1}{|c|}{} & Hierarchical SFC & 0.05 & 0.05 & 0.05 & 0.05 & 0.05\tabularnewline
-\hline
-\end{tabular}
-\par\end{centering}
-\caption{We show the performance of SFC from different settings of hyperparameters for $K$, the candidate class number, and $P$, the sample number for each class.}
+Next, we analyze the overall improvement trend of SFC under various few-shot settings.
+Our main focus is to study chatbot building in common situation during real-world application where only a few sample sentences are available for each class.
+The experimental results for the 3 diverse intent detection datasets under few-shot settings indicate that our proposed SFC can achieve +2.47 percents average improvement over one of the most powerful baseline models, which is RoBERTa-large classification model, on all these few-shot settings.
+Moreover, the improvement in F-score becomes more and more prominent with the decrease of data sample number per class.
+Our hierarchical SFC can achieve +4.97 percents average improvements over RoBERTa-large classification model in the most extreme few-shot setting with only 5 training samples per class.
 
-\label{tbe:table3}
-\end{table*}
+Then, we begin to compare the general performance of SFC with classification model and similarity model baselines.
+As for the classification model, hierarchical SFC outperforms BERT-large by +9.81 percents, ALBERT-xxlarge by 4 percents, RoBERTa-large by +2.47 percents, RoBERTa-base by +4.52 percents on average F-score for 5 datasets.
+In this way, we can see that RoBERTa is the best pre-trained model for the low-resource text classification task we are studying.
+As for the similarity model, we only choose the strongest pretrained model RoBERTa-large as our baseline, and hierarchical SFC achieves the improvement of 3 percents on average.
+Moreover, hierarchical SFC's result on 2 datasets without few-shot settings, which are ITG and Amazon-670k, are also 1.24 percents and 2.89 percents higher than Roberta-large classification model.
+These improvements illustrate that putting classification model and similarity model at different network layers to cooperate with each other is a successful design of hierarchical network structure for joint model, which enables these two models assist each other for better overall results.
+
+Finally, we analyze the effect brought by different settings of hyperparameters, see Table \ref{tbe:table3}.
+We conduct experiments on 5 different settings of hyperparameters, which are the number of candidate class number $K$ and the number of sentence pairs $P$ for each class, on ITG and Amazon-670K datasets to find the most suitable setting of these 2 hyperparameters.
+We control the total number of sentence pairs sampled for each user query into about the same level of amount(50-60).
+Through analyzing the experimenal results shown in Table \ref{tbe:table3}, we find that the best setting of hyperparameters might be slightly different for datasets of different data size.
+The class label number of ITG and Amazon-670k are similar in our experimental setting, which is around 250.
+However the total amount of data points of ITG is approximately 2 times larger than Amazon-670k.
+Therefore, the setting of $K=5$ and $P=10$ is good enough for ITG since most of the classes contains over 10 data points.
+However, for Amazon-670k, the amount of data sample for each class is scarce, thus, we may need more candidate classes to sample enough effective sentence pairs for sentence-pair model layer of SFC.
+In this way, the setting of $K=10$ and $P=5$ becomes a good choice.
+
+In conclusion, to the best of our knowledge, these results place SFC as the best performing model on 5 diverse experimental datasets for text classification task under low-resource task-specific conversational chatbot scenario.
+
+\section{Conclusion}
+In this work, we successfully proposed SFC, a joint system of classification model and sentence-pair similarity model with multi-task learning, which can effectively alleviate the limitation of classification model and similarity model for low-resource text classification tasks.
+Experimental results illustrate that our proposed system can achieve great improvement on 5 diverse datasets for task-specific chatbot system over several competitive single-task baseline models.
+Furthermore, we especially analyze the excellent performance of SFC when facing the challenge brought by few-shot scenarios, which is quite common in real-world application of chatbot system.
 

### 2020-08-10 chatbot_classification/aaai_2021/paper.tex
add subsections in Result Analysis

@@
 \label{Fig.1.sub.1}
-\includegraphics[scale=0.7]{picture1.pdf}}
+\includegraphics[scale=0.7]{picture/picture1.pdf}}
 \subfigure[similarity model]{
 \label{Fig.1.sub.2}
-\includegraphics[scale=0.55]{picture2.pdf}}
+\includegraphics[scale=0.55]{picture/picture2.pdf}}
 \caption{Two popular structures of building task-specific conversational chatbot}
@@
 \begin{centering}
-\includegraphics[scale=0.48]{picture3}
+\includegraphics[scale=0.48]{picture/picture3}
 \par\end{centering}
@@
 \begin{centering}
-\includegraphics[scale=0.72]{picture4} 
+\includegraphics[scale=0.72]{picture/picture4} 
 \par\end{centering}
@@
 
-$\bullet$ \textbf{full-scale real-world task-specific faq chatbot dataset}
+$\bullet$ \textbf{Full-scale real-world task-specific faq chatbot dataset}
 
@@
 
-$\bullet$ \textbf{subset of customer review dataset for extreme classification}
+$\bullet$ \textbf{Subset of customer review dataset for extreme classification}
 
@@
 
-$\bullet$ \textbf{subset of recently-released intent detection datasets}.
+$\bullet$ \textbf{Subset of recently-released intent detection datasets}.
 
@@
 
-First, we turn to compare among the four SFC variants.
+\textbf{Comparison among SFC variants.} First, we turn to compare among the four SFC variants shown in Table \ref{tbe:table2} to analyze the improvement brought by multi-task and hierarchical joint-model structure.
 We conduct ablation experiments to study the benefits brought by multi-task training by comparing multi-task 2-stage SFC with single-task 2-stage SFC.
@@
 
-Next, we analyze the overall improvement trend of SFC under various few-shot settings.
+\textbf{Analysis under few-shot scenarios.} Next, we analyze the overall improvement trend of SFC under various few-shot settings.
 Our main focus is to study chatbot building in common situation during real-world application where only a few sample sentences are available for each class.
@@
 
-Then, we begin to compare the general performance of SFC with classification model and similarity model baselines.
+\textbf{Fusion of classification and similarity model.} Then, we begin to compare the general performance of SFC with single-task classification and similarity baselines.
 As for the classification model, hierarchical SFC outperforms BERT-large by +9.81 percents, ALBERT-xxlarge by 4 percents, RoBERTa-large by +2.47 percents, RoBERTa-base by +4.52 percents on average F-score for 5 datasets.
@@
 
-Finally, we analyze the effect brought by different settings of hyperparameters, see Table \ref{tbe:table3}.
+\textbf{Settings of hyperparameters.} Finally, we analyze the effect brought by different settings of hyperparameters, see Table \ref{tbe:table3}.
 We conduct experiments on 5 different settings of hyperparameters, which are the number of candidate class number $K$ and the number of sentence pairs $P$ for each class, on ITG and Amazon-670K datasets to find the most suitable setting of these 2 hyperparameters.

### 2020-08-12 chatbot_classification/aaai_2021/paper.tex
modification based on ver_1 and update experimental results

@@
 The detailed network structure of 2-stage SFC is shown in Fig. \ref{fig:ver.1.3}. It is composed with 2 separate stages in charge of different jobs.
-In stage 1, we can use any auxiliary model or tool to provide top-K most related classes for sampling sentence pairs of both positive samples and negative samples for stage 2.
+In stage 1, we can use any auxiliary model or tool to provide top-K most related class labels for sampling sentence pairs of both positive samples and negative samples for stage 2.
 Suppose we have a training data set $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$ of $N$ data points, in which $x_{i}$ is the user input query and $y_{i}$ is a single class label from a class label set of $C$ classes in total.
@@
 directly from original data set $\mathcal{D}$ without any sampling strategy, then $\mathcal{D'}$ will have $M=N^2$ data points of sentence pairs, which might be too time-consuming for the training process of stage 2 since we often have hundreds of class labels under task-specific chatbot scenario.
-Although we may only have a few data points for a single class label, $N$ is still quite a big number.
+Although we may only have a few data points for a single class label, $M$ is still quite a big number.
 
@@
 The key idea of this sampling strategy is to train with negative samples that are hard to be distinguished from positive samples.
-Now suppose we have a user input query $x_{i}$ and top-K most related class labels set $\mathcal{C'}=\{c'_{1}, \dots, c'_{K}\}$ found by auxiliary model or tool in stage 1, where $K$ is a hyperparameter set by us that controls candidate class number, we apply the adversarial negative sampling strategy into our sentence pair sampling process by the following 2 steps:
+Now suppose we have a user input query $x_{i}$ and top-K most related class labels set $\mathcal{C'}=\{c'_{1}, \dots, c'_{K}\}$ provided by auxiliary model or tool in stage 1, where $K$ is a hyperparameter set by us that controls candidate class number, we apply the adversarial negative sampling strategy into our sentence pair sampling process by the following 2 steps:
 
@@
 positive sentence pair sampling}: During the training process, we have to first make sure that the ground truth class label $y_{i}$ for $x_{i}$ is within the candidate class label set $\mathcal{C'}$.
-If $y_{i}\notin \mathcal{C'}$, we will manually add $y_{i}$ into $\mathcal{C'}$ by replacing $c'_{K}$ with $y_{i}$.
+If $y_{i}\notin \mathcal{C'}$, we will manually add $y_{i}$ into $\mathcal{C'}$ by replacing $c'_{K}$ with $y_{i}$, since $c'_{K}$ is the least promising candidate label according to the auxiliary model in stage 1.
 Afterwards, we will randomly sample $P$ sentences $\{x'_{0},x'_{1}, \dots, x'_{P}\}$ with the same class label as $y_{i}$ from data set $\mathcal{D}$ to form the set of sentence pairs with positive label $\mathcal{P'}_{i}=\{[(x_{i}, x'_{0}), 1], [(x_{i}, x'_{1}), 1], \dots, [(x_{i}, x'_{P}), 1]\}$, where $P$ is also a hyperparameter set by us that controls the number of sentences we should sample from each class.
@@
 negative sentence pair sampling}: As for negative sentence pairs, we will also randomly sample $P$ sentences for each class in the negative candidate class label set $\mathcal{C'}\backslash \{y_{i}\}$.
-The class labels in $\mathcal{C'}\backslash \{y_{i}\}$ are the set of most confusing classes comparing to the ground truth ${y_{i}}$, so we assume that the sentence pairs with negative label grouped by user input query $x_{i}$ and sentences with class labels in $\mathcal{C'}\backslash \{y_{i}\}$ are also strong adversarial negative samples for sentence-pair similarity model that can help enhance the training speed and performance.
+The class labels in $\mathcal{C'}\backslash \{y_{i}\}$ are the set of most confusing class labels comparing to the ground truth ${y_{i}}$, so we assume that the sentence pairs with negative label grouped by user input query $x_{i}$ and sentences with class labels in $\mathcal{C'}\backslash \{y_{i}\}$ are strong adversarial negative samples for sentence-pair similarity model that can help enhance the training speed and performance.
 According to the same method as positive sentence pair sampling, we can obtain the set of sentence pairs with negative label as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{0}), 0], [(x_{i}, x'_{1}), 0], ..., [(x_{i}, x'_{P\cdot (K-1)}), 0]\}$
@@
 
-\subsubsection{stage 1: classification model for providing top-K classes}
+\subsubsection{stage 1: classification model for providing top-K candidate class labels}
 As for stage 1, our SFC system can adapt to any auxiliary model or even searching tool based on Term Frequency-Inverse
@@
 \ref{Fig.1.sub.1}, for better overall performance.
-According to our experimental result, RoBERTa can guarantee that approximately 95\% ground truth label be included in top-5 candidate classes with highest probability after being fine-tuned on task-specific data set with experimental result measured by F-score at around 0.75.
+According to our experimental result, RoBERTa can guarantee that approximately 95\% ground truth label be included in top-5 candidate class labels with highest probability after being fine-tuned on task-specific data set with experimental result measured by F-score at around 0.75.
 So we use RoBERTa as encoder of classification model in our setting at stage 1 to ensure low limitation for the performance of stage 2.
@@
 Before we start to fine-tune our sentence-pair model on task-specific dataset, we first fine-tune RoBERTa on Quora dataset\cite{iyer2017first}, which contains 404,290 potential duplicate question pairs, for transfer learning.
-Then we continue to do multi-task training on sentence-pair dataset $\mathcal{D'}$ sampled from the top-K candidate classes provided by stage 1.
+Then we continue to do multi-task training on sentence-pair dataset $\mathcal{D'}$ sampled from the top-K candidate class labels provided by stage 1.
 
@@
 
-As for top-K classification task, we share the same sentence-pair similarity model structure with task 1.
+As for top-K classification task, it shares the same sentence-pair similarity model structure with task 1.
 The only difference is that we add a task-specific average pooling layer, shown in Fig.
@@
 
-We already know that the size of ${\Phi}^S$ in task 1 is $M\times 2=(N\cdot K\cdot P)\times 2$, where $N$ is the total number of data points in original training data $\mathcal{D}$, $K$ is a hyperparameter that controls the number of candidate classes provided by stage 1, and $P$ is also a hyperparameter that controls the number of sentences we should randomly sample from each candidate class.
+We already know that the size of ${\Phi}^S$ in task 1 is $M\times 2=(N\cdot K\cdot P)\times 2$, where $N$ is the total number of data points in original training data $\mathcal{D}$, $K$ is a hyperparameter that controls the number of candidate class labels provided by stage 1, and $P$ is also a hyperparameter that controls the number of sentences we should randomly sample from each candidate class labels.
 Now, for the average pooling layer, we first reshape ${\Phi}^S$ into the size of $N\times K\times P\times 2$, and then split it into ${\Phi}^{K,pos}$ and ${\Phi}^{K,neg}$, and both of them will have the size of $N\times K\times P$.
@@
 \ref{fig:framework}.
-In hierarchical SFC, classification model is being placed in lower layer level to dynamically provide top-K candidate classes for the sentence-pair similarity model placed in higher layer level through a top-K pooling layer.
-In this way, classification model and similarity model can be merged into one single joint-model for multi-task training, thus avoiding the limitation brought by 2 separate stage structure.
+In hierarchical SFC, classification model is being placed in lower layer level to dynamically provide top-K candidate class labels for the sentence-pair similarity model placed in higher layer level through a top-K pooling layer.
+In this way, classification model and similarity model can be merged into one single joint-model for multi-task training with sentence pairs sampled from varying candidate class labels, thus avoiding the limitation brought by 2 separate stage structure.
 
@@
 \section{Experiments}
-In this section, we conduct extensive experiments over 5 task-specific dataset to evaluate the performance of our proposed SFC system and the effectiveness of the methodology of multi-task learning and hierachical joint-model structure under low-data settings.
+In this section, we conduct extensive experiments over 5 task-specific datasets to evaluate the performance of our proposed SFC system and the effectiveness of the methodology of multi-task learning and hierachical joint-model structure under low-data settings.
 
 \subsection{Datasets}
-The dataset used in our experiments aims to help us study low-resource text classification problem under task-specific conversational chatbot scenario.
+The datasets used in our experiments aims to help us study low-resource text classification problem under task-specific conversational chatbot scenario.
 Therefore, we keep all the dataset under low-resource chatbot corpus setting, which is a large number of class labels (50-250) with a few examples(5-20) in short text for each class, by sampling smaller subsets from the full scale when the raw datasets are oversized, see Table \ref{tbe:dataset statistic}.
@@
 \hline
+TextCNN & \multirow{2}*{$0.3539$} & \multirow{2}*{$0.5497$} & \multirow{2}*{$0.6246$} & \multirow{2}*{$0.2882$} & \multirow{2}*{$0.5187$} & \multirow{2}*{$0.6129$} & \multirow{2}*{$0.6554$} & \multirow{2}*{$0.2105$} & \multirow{2}*{$0.3202$} & \multirow{2}*{$0.4154$} & \multirow{2}*{$0.4529$} & \multirow{2}*{$0.5563$} & \multirow{2}*{$0.3333$}\tabularnewline
+(classification) & & & & & & & & & & & & &\tabularnewline
+\hline
 BERT-large & \multirow{2}*{$0.8080$} & \multirow{2}*{$0.8904$} & \multirow{2}*{$0.9265$} & \multirow{2}*{$0.578$} & \multirow{2}*{$0.8004$} & \multirow{2}*{$0.8518$} & \multirow{2}*{$0.8827$} & \multirow{2}*{$0.4711$} & \multirow{2}*{$0.5963$} & \multirow{2}*{$0.6342$} & \multirow{2}*{$0.7010$} & \multirow{2}*{$0.7485$} & \multirow{2}*{$0.6658$}\tabularnewline
@@
 \hline
-ALBERT-xxlarge & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{$0.1422$} & \multirow{2}*{$0.2057$} & \multirow{2}*{$0.5723$} & \multirow{2}*{$0.5912$} & \multirow{2}*{$0.6601$} & \multirow{2}*{$0.6893$}\tabularnewline
+ALBERT-xxlarge & \multirow{2}*{$0.6500$} & \multirow{2}*{$0.9008$} & \multirow{2}*{$0.9296$} & \multirow{2}*{$0.3608$} & \multirow{2}*{$0.614$} & \multirow{2}*{$0.809$} & \multirow{2}*{$0.853$} & \multirow{2}*{$0.1422$} & \multirow{2}*{$0.2735$} & \multirow{2}*{$0.5723$} & \multirow{2}*{$0.6217$} & \multirow{2}*{$0.7253$} & \multirow{2}*{$0.6893$}\tabularnewline
 (classification) & & & & & & & & & & & & &\tabularnewline
@@
 \hline
-RoBERTa-large & \multirow{2}*{$0.8266$} & \multirow{2}*{$0.8861$} & \multirow{2}*{$0.9023$} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{$0.5425$} & \multirow{2}*{$0.6164$} & \multirow{2}*{$0.6503$} & \multirow{2}*{$0.6729$} & \multirow{2}*{$0.7418$} & \multirow{2}*{$0.6362$}\tabularnewline
+RoBERTa-large & \multirow{2}*{$0.8266$} & \multirow{2}*{$0.8861$} & \multirow{2}*{$0.9023$} & \multirow{2}*{$0.757$} & \multirow{2}*{$0.8476$} & \multirow{2}*{$0.8614$} & \multirow{2}*{$0.8743$} & \multirow{2}*{$0.5425$} & \multirow{2}*{$0.6164$} & \multirow{2}*{$0.6503$} & \multirow{2}*{$0.6729$} & \multirow{2}*{$0.7418$} & \multirow{2}*{$0.6362$}\tabularnewline
 (similarity) & & & & & & & & & & & & &\tabularnewline
@@
 \hline
-2-stage SFC & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-}\tabularnewline
+2-stage SFC & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{$0.7997$} & \multirow{2}*{$0.8823$} & \multirow{2}*{$0.8945$} & \multirow{2}*{$0.9123$} & \multirow{2}*{$0.6498$} & \multirow{2}*{$0.6980$} & \multirow{2}*{$0.7202$} & \multirow{2}*{$0.7358$} & \multirow{2}*{$0.8020$} & \multirow{2}*{$0.7311$}\tabularnewline
 (task2 only) & & & & & & & & & & & & &\tabularnewline
@@
 \textbf{Group 1: single-task classification model.} This group of baseline models are based on the network structure for classification model shown in \ref{Fig.1.sub.1}.
+As for non-pretrained neural network, we choose TextCNN\cite{kim2014convolutional} as a representative baseline.
 As for the pretrained model, we choose RoBERTa, BERT and ALBERT, all of which are among the most powerful pretrained models that achieve outstanding results in many NLP tasks, in our experimental setting.
 Since we apply RoBERTa in our SFC system, we naturally adopt single-task classification model based on RoBERTa-large and RoBERTa-base as our baseline models.
-Besides, we also adopt the baseline pre-trained model BERT-large\cite{devlin2018bert} and recently released ALBERT-xxlarge\cite{lan2019albert} for comparison.
+Besides, we also adopt the recently released baseline pre-trained model ALBERT-xxlarge\cite{lan2019albert} for comparison.
 Since we use different few-shot settings from \cite{casanueva2020efficient} for those intent detection datasets, we also use BERT-large tuned on our few-shot settings as an essential reference for experimental results.
@@
 Our hierarchical SFC can achieve +4.97 percents average improvements over RoBERTa-large classification model in the most extreme few-shot setting with only 5 training samples per class.
+This observation indicates that SFC is especially suitable for being applied during the initial stage of building task-specific chatbot system, where the amount of data sample for each class label is extremely scarce.
 
 \textbf{Fusion of classification and similarity model.} Then, we begin to compare the general performance of SFC with single-task classification and similarity baselines.
-As for the classification model, hierarchical SFC outperforms BERT-large by +9.81 percents, ALBERT-xxlarge by 4 percents, RoBERTa-large by +2.47 percents, RoBERTa-base by +4.52 percents on average F-score for 5 datasets.
-In this way, we can see that RoBERTa is the best pre-trained model for the low-resource text classification task we are studying.
-As for the similarity model, we only choose the strongest pretrained model RoBERTa-large as our baseline, and hierarchical SFC achieves the improvement of 3 percents on average.
-Moreover, hierarchical SFC's result on 2 datasets without few-shot settings, which are ITG and Amazon-670k, are also 1.24 percents and 2.89 percents higher than Roberta-large classification model.
+As for the classification model, hierarchical SFC outperforms TextCNN by +37.99 percents, ALBERT-xxlarge by 10 percents, BERT-large by +9.81 percents, RoBERTa-base by +4.52 percents, RoBERTa-large by +2.47 percents on average F-score over 5 datasets.
+In this way, we can see that RoBERTa is the best baseline pre-trained model for the low-resource text classification task we are studying.
+As for the similarity model, we only choose the strongest pretrained model RoBERTa-large as our baseline, and hierarchical SFC achieves the improvement of +7.81 percents on average.
+Moreover, hierarchical SFC's result on 2 datasets without data sampling for few-shot settings, which are ITG and Amazon-670k, are also 1.24 and 2.89 percents higher than Roberta-large classification model, and are 6.96 and 10.77 percents higher than Roberta-large similarity model.
 These improvements illustrate that putting classification model and similarity model at different network layers to cooperate with each other is a successful design of hierarchical network structure for joint model, which enables these two models assist each other for better overall results.

### 2020-08-15 chatbot_classification/aaai_2021/paper.tex
modification based on ver_1 and update experimental results
update experimental results

@@
 
-\textbf{HWU64} is a intent detection dataset designed for home robot scenario\cite{liu2019benchmarking}.
-It aims at the specific task of capturing the intent for different user requests to home robot and finding the corresponding answer.
-The raw dataset contains 25,716 data points for 64 class labels through crowdsourcing, which raises much more data than common real-world circumstances.
-Therefore, we experiment with the setups where only 5, 10, 15 and 20 training data points are available for each class label by random sampling.
-
-\textbf{CLINC150} is a dataset designed for task-oriented systems with 23,700 queries that are short and unstructured for 150 intents, in the same style made by real users through crowdsourcing\cite{larson2019evaluation}.
-Here, we sample 5, 10 and 15 training data points for each intent class label by random sampling for our experimental setup.
-
-\textbf{BANKING77} is a intent detection dataset for bank customer services.
-The raw dataset contains 13,084 data points for 77 class labels\cite{casanueva2020efficient}.
-Here, we sample 5, 10, 15, 20 training data points for each class label by random sampling for our experimental setup.
-
 \begin{table*}
@@
 \hline
+LEAM & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-}\tabularnewline
+(classification) & & & & & & & & & & & & &\tabularnewline
+\hline
 BERT-large & \multirow{2}*{$0.8080$} & \multirow{2}*{$0.8904$} & \multirow{2}*{$0.9265$} & \multirow{2}*{$0.578$} & \multirow{2}*{$0.8004$} & \multirow{2}*{$0.8518$} & \multirow{2}*{$0.8827$} & \multirow{2}*{$0.4711$} & \multirow{2}*{$0.5963$} & \multirow{2}*{$0.6342$} & \multirow{2}*{$0.7010$} & \multirow{2}*{$0.7485$} & \multirow{2}*{$0.6658$}\tabularnewline
@@
 \hline
-ALBERT-xxlarge & \multirow{2}*{$0.6500$} & \multirow{2}*{$0.9008$} & \multirow{2}*{$0.9296$} & \multirow{2}*{$0.3608$} & \multirow{2}*{$0.614$} & \multirow{2}*{$0.809$} & \multirow{2}*{$0.853$} & \multirow{2}*{$0.1422$} & \multirow{2}*{$0.2735$} & \multirow{2}*{$0.5723$} & \multirow{2}*{$0.6217$} & \multirow{2}*{$0.7253$} & \multirow{2}*{$0.6893$}\tabularnewline
+ALBERT-xxlarge & \multirow{2}*{$0.6500$} & \multirow{2}*{$0.9008$} & \multirow{2}*{$0.9296$} & \multirow{2}*{$0.3608$} & \multirow{2}*{$0.6345$} & \multirow{2}*{$0.8090$} & \multirow{2}*{$0.8530$} & \multirow{2}*{$0.3549$} & \multirow{2}*{$0.3876$} & \multirow{2}*{$0.5808$} & \multirow{2}*{$0.6320$} & \multirow{2}*{$0.7253$} & \multirow{2}*{$0.6893$}\tabularnewline
 (classification) & & & & & & & & & & & & &\tabularnewline
@@
 \hline
-2-stage SFC & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{$0.7997$} & \multirow{2}*{$0.8823$} & \multirow{2}*{$0.8945$} & \multirow{2}*{$0.9123$} & \multirow{2}*{$0.6498$} & \multirow{2}*{$0.6980$} & \multirow{2}*{$0.7202$} & \multirow{2}*{$0.7358$} & \multirow{2}*{$0.8020$} & \multirow{2}*{$0.7311$}\tabularnewline
+2-stage SFC & \multirow{2}*{$0.9162$} & \multirow{2}*{$0.9424$} & \multirow{2}*{$0.9530$} & \multirow{2}*{$0.7997$} & \multirow{2}*{$0.8823$} & \multirow{2}*{$0.8945$} & \multirow{2}*{$0.9123$} & \multirow{2}*{$0.6498$} & \multirow{2}*{$0.6980$} & \multirow{2}*{$0.7202$} & \multirow{2}*{$0.7358$} & \multirow{2}*{$0.8020$} & \multirow{2}*{$0.7311$}\tabularnewline
 (task2 only) & & & & & & & & & & & & &\tabularnewline
@@
 \end{table*}
+
+\textbf{HWU64} is a intent detection dataset designed for home robot scenario\cite{liu2019benchmarking}.
+It aims at the specific task of capturing the intent for different user requests to home robot and finding the corresponding answer.
+The raw dataset contains 25,716 data points for 64 class labels through crowdsourcing, which raises much more data than common real-world circumstances.
+Therefore, we experiment with the setups where only 5, 10, 15 and 20 training data points are available for each class label by random sampling.
+
+\textbf{CLINC150} is a dataset designed for task-oriented systems with 23,700 queries that are short and unstructured for 150 intents, in the same style made by real users through crowdsourcing\cite{larson2019evaluation}.
+Here, we sample 5, 10 and 15 training data points for each intent class label by random sampling for our experimental setup.
+
+\textbf{BANKING77} is a intent detection dataset for bank customer services.
+The raw dataset contains 13,084 data points for 77 class labels\cite{casanueva2020efficient}.
+Here, we sample 5, 10, 15, 20 training data points for each class label by random sampling for our experimental setup.
 
@@
 \hline
-\multicolumn{1}{|c|}{\multirow{2}*{ITG}}& 2-stage SFC & 0.05 & $0.8124$ & 0.05 & 0.05 & 0.05\tabularnewline
+\multicolumn{1}{|c|}{\multirow{2}*{ITG}}& 2-stage SFC & - & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
 \cline{2-7}
-\multicolumn{1}{|c|}{} & Hierarchical SFC & 0.05 & $0.8114$ & 0.05 & 0.05 & 0.05\tabularnewline
+\multicolumn{1}{|c|}{} & Hierarchical SFC & - & $0.8114$ & - & - & $0.7826$\tabularnewline
 \hline
-\multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& 2-stage SFC & 0.05 & $0.7364$ & 0.05 & 0.05 & 0.05\tabularnewline
+\multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& 2-stage SFC & - & $0.7364$ & - & - & -\tabularnewline
 \cline{2-7}
-\multicolumn{1}{|c|}{} & Hierarchical SFC & 0.05 & $0.7445$ & 0.05 & 0.05 & 0.05\tabularnewline
+\multicolumn{1}{|c|}{} & Hierarchical SFC & - & $0.7445$ & - & - & -\tabularnewline
 \hline
@@
 \textbf{Fusion of classification and similarity model.} Then, we begin to compare the general performance of SFC with single-task classification and similarity baselines.
-As for the classification model, hierarchical SFC outperforms TextCNN by +37.99 percents, ALBERT-xxlarge by 10 percents, BERT-large by +9.81 percents, RoBERTa-base by +4.52 percents, RoBERTa-large by +2.47 percents on average F-score over 5 datasets.
+As for the classification model, hierarchical SFC outperforms TextCNN by +37.99 percents, ALBERT-xxlarge by +17.87 percents\footnote{We found that the performance of ALBERT.xxlarge is extremely unstable for classification task.
+Here, we did multiple run with different settings of parameters such as learning rate and batch size for each dataset, and record the best result we can obtain in Table \ref{tbe:table2}.}, BERT-large by +9.81 percents, RoBERTa-base by +4.52 percents, RoBERTa-large by +2.47 percents on average F-score over 5 datasets.
 In this way, we can see that RoBERTa is the best baseline pre-trained model for the low-resource text classification task we are studying.

### 2020-08-19 chatbot_classification/aaai_2021/paper.tex
update LEAM baseline and experimental results

@@
 A common model structure is adding a softmax classifier to the top of the neural network.
+Another common approach is text classification neural network based on label-word joint embedding, such as LEAM\cite{wang2018joint}.
+This approach involves label embedding when constructing the text-sequence representation, which poses requirements on label information.
+In our cases, since we have large amount of class labels without being well-defined, this approach can do only a few help to the low-resource chatbot scenario.
 Afterwards, pre-trained language models on large corpus like BERT\cite{devlin2018bert} and
@@
 \hline
-TextCNN & \multirow{2}*{$0.3539$} & \multirow{2}*{$0.5497$} & \multirow{2}*{$0.6246$} & \multirow{2}*{$0.2882$} & \multirow{2}*{$0.5187$} & \multirow{2}*{$0.6129$} & \multirow{2}*{$0.6554$} & \multirow{2}*{$0.2105$} & \multirow{2}*{$0.3202$} & \multirow{2}*{$0.4154$} & \multirow{2}*{$0.4529$} & \multirow{2}*{$0.5563$} & \multirow{2}*{$0.3333$}\tabularnewline
+TextCNN & \multirow{2}*{$0.5318$} & \multirow{2}*{$0.6963$} & \multirow{2}*{$0.7609$} & \multirow{2}*{$0.4408$} & \multirow{2}*{$0.6436$} & \multirow{2}*{$0.7366$} & \multirow{2}*{$0.7918$} & \multirow{2}*{$0.3112$} & \multirow{2}*{$0.4007$} & \multirow{2}*{$0.4823$} & \multirow{2}*{$0.5272$} & \multirow{2}*{$0.6624$} & \multirow{2}*{$0.4401$}\tabularnewline
 (classification) & & & & & & & & & & & & &\tabularnewline
 \hline
-LEAM & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-}\tabularnewline
+LEAM & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{$0.4545$} & \multirow{2}*{$0.5554$} & \multirow{2}*{$0.5936$} & \multirow{2}*{$0.6599$} & \multirow{2}*{$0.7086$} & \multirow{2}*{$0.6091$}\tabularnewline
 (classification) & & & & & & & & & & & & &\tabularnewline
@@
 \hline
-\multicolumn{1}{|c|}{\multirow{2}*{ITG}}& 2-stage SFC & - & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
+\multicolumn{1}{|c|}{\multirow{2}*{ITG}}& 2-stage SFC & $0.8034$ & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
 \cline{2-7}
-\multicolumn{1}{|c|}{} & Hierarchical SFC & - & $0.8114$ & - & - & $0.7826$\tabularnewline
+\multicolumn{1}{|c|}{} & Hierarchical SFC & $0.7882$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7826$\tabularnewline
 \hline
-\multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& 2-stage SFC & - & $0.7364$ & - & - & -\tabularnewline
+\multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& 2-stage SFC & $0.7278$ & $0.7364$ & $0.7366$ & $0.7328$ & $0.7204$\tabularnewline
 \cline{2-7}
-\multicolumn{1}{|c|}{} & Hierarchical SFC & - & $0.7445$ & - & - & -\tabularnewline
+\multicolumn{1}{|c|}{} & Hierarchical SFC & $0.7334$ & $0.7445$ & $0.7516$ & - & -\tabularnewline
 \hline

### 2020-08-23 chatbot_classification/aaai_2021/paper.ver_02.tex
version2.

--- 2020-08-19 chatbot_classification/aaai_2021/paper.tex
@@
 A common model structure is adding a softmax classifier to the top of the neural network.
-Another common approach is text classification neural network based on label-word joint embedding, such as LEAM\cite{wang2018joint}.
-This approach involves label embedding when constructing the text-sequence representation, which poses requirements on label information.
-In our cases, since we have large amount of class labels without being well-defined, this approach can do only a few help to the low-resource chatbot scenario.
 Afterwards, pre-trained language models on large corpus like BERT\cite{devlin2018bert} and
@@
 
-Another popular approach among previous work was based on sentence-pair model.
+Another common approach is text classification neural network based on label-word joint embedding, such as LEAM\cite{wang2018joint}, MTLE\cite{zhang2017multi} and EXAM\cite{du2019explicit}.
+This approach involves label embedding when constructing the text-sequence representation.
+Take LEAM as an example, the text classification model is implemented by jointly embedding the word and label in the same latent space\cite{wang2018joint}.
+Afterwards, the text representation are constructed based on text-label compatibility through attention mechanism.
+In this way, additional sources of semantic information from class labels can be fully leveraged, which is quite helpful especially under few-shot scenario.
+
+The third popular approach among previous work was based on sentence-pair model.
 The motivation of this approach was started from the idea of Information Retrival (IR) based chatbot\cite{jafarpour2010filter, leuski2011npceditor}.
@@
 
-Despite the success of these 2 approaches, they still have some limitations in task-specific chatbot scenario.
+Despite the success of these 3 approaches, they still have some limitations in task-specific chatbot scenario.
 As for the text classification model approach, it's quite hard to use data augmentation method to solve the data insufficiency challenge since the it's usually unfeasible to get large amount of domain-specific data when facing a new task.
+As for label-word joint embedding approach, it poses noticeable requirements on label information.
+However, in our cases, since we have large amount of class labels without being well-defined for question answering chatbot, the only thing we can do is to choose one of the user utterance as the class label to represent the key information of the whole class.
+In this way, the label will become not only prolix but also biased, which will bring some negative effect to label embedding.
 With respect to the sentence-pair model approach, though we can obtain large amount of data in semantically duplicate sentence pair identification domain for transfer learning\cite{sun2019fine}, it's still quite hard to perform well on task-specific dataset because the training objective of sentence-pair model is semantic similarity, which is slightly different from the target of classification task.
@@
 \hline
-LEAM & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{$0.4545$} & \multirow{2}*{$0.5554$} & \multirow{2}*{$0.5936$} & \multirow{2}*{$0.6599$} & \multirow{2}*{$0.7086$} & \multirow{2}*{$0.6091$}\tabularnewline
+LEAM & \multirow{2}*{$0.7514$} & \multirow{2}*{$0.8203$} & \multirow{2}*{$0.8612$} & \multirow{2}*{$0.5422$} & \multirow{2}*{$0.7812$} & \multirow{2}*{$0.8129$} & \multirow{2}*{$0.8280$} & \multirow{2}*{$0.4545$} & \multirow{2}*{$0.5554$} & \multirow{2}*{$0.5936$} & \multirow{2}*{$0.6599$} & \multirow{2}*{$0.7086$} & \multirow{2}*{$0.6091$}\tabularnewline
 (classification) & & & & & & & & & & & & &\tabularnewline
@@
 \cline{2-7}
-\multicolumn{1}{|c|}{} & Hierarchical SFC & $0.7334$ & $0.7445$ & $0.7516$ & - & -\tabularnewline
+\multicolumn{1}{|c|}{} & Hierarchical SFC & $0.7334$ & $0.7445$ & $0.7516$ & $0.7344$ & $0.7373$\tabularnewline
 \hline
@@
 This observation suggests that task 2 may play a relatively more important role in multi-task learning, which leads us to put larger weight $\alpha_{K}$ to the loss $\mathcal{L}^{K}$ of task 2 when calculating the total loss $\mathcal{L}$.
-Also, we can see that the hierachical SFC steadily outperforms 2-stage SFC on 5 diverse datasets by 2 percents on average.
+Also, we can see that the hierachical SFC steadily outperforms 2-stage SFC on 5 diverse datasets by 1.17 percents on average.
 This observation supports the idea that the hierachical joint model structure can alleviate the limitation brought by the lack of interaction between similarity model and classification model in 2-stage SFC.
@@
 Our main focus is to study chatbot building in common situation during real-world application where only a few sample sentences are available for each class.
-The experimental results for the 3 diverse intent detection datasets under few-shot settings indicate that our proposed SFC can achieve +2.47 percents average improvement over one of the most powerful baseline models, which is RoBERTa-large classification model, on all these few-shot settings.
+The experimental results for the 3 diverse intent detection datasets (ClINC150, BANKING77, HWU64) under few-shot settings indicate that our proposed
+hierarchical SFC can achieve 2.47 percents average improvement over one of the most powerful baseline models, which is RoBERTa-large classification model, on all these few-shot settings.
 Moreover, the improvement in F-score becomes more and more prominent with the decrease of data sample number per class.
-Our hierarchical SFC can achieve +4.97 percents average improvements over RoBERTa-large classification model in the most extreme few-shot setting with only 5 training samples per class.
+Our hierarchical SFC can achieve 4.97 percents average improvements over RoBERTa-large classification model in the most extreme few-shot setting with only 5 training samples per class.
 This observation indicates that SFC is especially suitable for being applied during the initial stage of building task-specific chatbot system, where the amount of data sample for each class label is extremely scarce.
 
+\textbf{Comparison between label embedding and sentence pair embedding.} Afterwards, we start to compare the performance of SFC with the text-label joint embedding baseline named as LEAM.
+As shown in Table \ref{tbe:table2}, hierarchical SFC outperforms LEAM by 14.25 percents on average F-score over 5 datasets.
+Besides, although the labels within the 3 diverse intent detection datasets (CLINC150, BANKING77, HWU64) are all being well-defined as the semantic summary of each intent, hierarchical SFC still outperforms LEAM by 14.69 percents on average F-score.
+This observation indicates that it's usually quite hard to use a fixed label with only a few words as the representative of all the sentences within a class since there are always plenty of ways for people to express questions or queries about the same topic during a conversation with chatbot.
+Therefore, learning the semantic similarity between user query and sample sentences through sentence pair embedding can be more reliable than making decision according to the semantic relationship between user query and class labels through label embedding.
+
 \textbf{Fusion of classification and similarity model.} Then, we begin to compare the general performance of SFC with single-task classification and similarity baselines.
-As for the classification model, hierarchical SFC outperforms TextCNN by +37.99 percents, ALBERT-xxlarge by +17.87 percents\footnote{We found that the performance of ALBERT.xxlarge is extremely unstable for classification task.
-Here, we did multiple run with different settings of parameters such as learning rate and batch size for each dataset, and record the best result we can obtain in Table \ref{tbe:table2}.}, BERT-large by +9.81 percents, RoBERTa-base by +4.52 percents, RoBERTa-large by +2.47 percents on average F-score over 5 datasets.
+As for the classification model, hierarchical SFC outperforms TextCNN by 26.19 percents, ALBERT-xxlarge by 17.87 percents\footnote{We found that the performance of ALBERT.xxlarge is extremely unstable for classification task.
+Here, we did multiple run with different settings of parameters such as learning rate and batch size for each dataset, and record the best result we can obtain in Table \ref{tbe:table2}.}, BERT-large by 9.81 percents, RoBERTa-base by 4.52 percents, RoBERTa-large by 2.47 percents on average F-score over 5 datasets.
 In this way, we can see that RoBERTa is the best baseline pre-trained model for the low-resource text classification task we are studying.
-As for the similarity model, we only choose the strongest pretrained model RoBERTa-large as our baseline, and hierarchical SFC achieves the improvement of +7.81 percents on average.
+As for the similarity model, we only choose the strongest pretrained model RoBERTa-large as our baseline, and hierarchical SFC achieves the improvement of 7.81 percents on average.
 Moreover, hierarchical SFC's result on 2 datasets without data sampling for few-shot settings, which are ITG and Amazon-670k, are also 1.24 and 2.89 percents higher than Roberta-large classification model, and are 6.96 and 10.77 percents higher than Roberta-large similarity model.

### 2020-08-23 chatbot_classification/aaai_2021/paper.ver_03.tex
Version 3. AAAI format.

--- 2020-08-23 chatbot_classification/aaai_2021/paper.ver_02.tex
@@
-%% LyX 2.3.1-1 created this file.  For more info, see http://www.lyx.org/.
-%% Do not edit unless you really know what you are doing.
-\documentclass{article}
-\usepackage[latin9]{inputenc}
+\def\year{2021}\relax
+%File: formatting-instructions-latex-2021.tex
+%release 2021.1
+\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
+\usepackage{aaai21}  % DO NOT CHANGE THIS
+\usepackage{times}  % DO NOT CHANGE THIS
+\usepackage{helvet} % DO NOT CHANGE THIS
+\usepackage{courier}  % DO NOT CHANGE THIS
+\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
+\usepackage{graphicx} % DO NOT CHANGE THIS
+\urlstyle{rm} % DO NOT CHANGE THIS
+\def\UrlFont{\rm}  % DO NOT CHANGE THIS
+\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
+\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
+\frenchspacing  % DO NOT CHANGE THIS
+\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
+\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
+%\nocopyright
+%PDF Info Is REQUIRED.
+% For /Author, add all authors within the parentheses, separated by commas. No accents or commands.
+% For /Title, add Title in Mixed Case. No accents or commands. Retain the parentheses.
+\pdfinfo{
+  /Title (AAAI Press Formatting Instructions for Authors Using LaTeX -- A Guide)
+  /Author (AAAI Press Staff, Pater Patel Schneider, Sunil Issar, J. Scott Penberthy, George Ferguson, Hans Guesgen, Francisco Cruz, Marc Pujol-Gonzalez)
+  /TemplateVersion (2021.1)
+}
+
 \usepackage{array}
@@
 \usepackage{subfigure}
+\usepackage{spconf}
 
-\makeatletter
+\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-% Template for GlobalSIP-2018 paper; to be used with:
-%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
-%          IEEEbib.bst - IEEE bibliography style file.
-% --------------------------------------------------------------------------
-\usepackage{spconf}
-
 \def\x{{\mathbf x}}
@@
 
-\makeatother
-
-\begin{document}
 \title{     
@@
 }
-\name{Jingwen Huang}   
-\address{     
-  \{hanmei613\}@gmail.com   
+
+\author{
+  %Authors
+  % All authors must be in the same font size and format.
+  Written by AAAI Press Staff\textsuperscript{\rm 1}\thanks{With help from the AAAI Publications Committee.}\\
+  AAAI Style Contributions by Pater Patel Schneider,
+  Sunil Issar,  \\
+  J. Scott Penberthy,
+  George Ferguson,
+  Hans Guesgen,
+  Francisco Cruz,
+  Marc Pujol-Gonzalez
+  \\
 }
+\affiliations{
+  %Afiliations
+
+  \textsuperscript{\rm 1}Association for the Advancement of Artificial Intelligence\\
+  %If you have multiple authors and multiple affiliations
+  % use superscripts in text and roman font to identify them.
+  %For example,
+
+  % Sunil Issar, \textsuperscript{\rm 2}
+  % J. Scott Penberthy, \textsuperscript{\rm 3}
+  % George Ferguson,\textsuperscript{\rm 4}
+  % Hans Guesgen, \textsuperscript{\rm 5}.
+  % Note that the comma should be placed BEFORE the superscript for optimum readability
+
+  2275 East Bayshore Road, Suite 160\\
+  Palo Alto, California 94303\\
+  % email address must be in roman text type, not monospace or sans serif
+  publications21@aaai.org
+
+  % See more examples next
+}
+
+\begin{document}
   \maketitle
@@
   \begin{abstract}
-  Building  conversational  chatbot  system  has  become  a  popular solution to customer  services  under various business scenarios. A
-  conversational  chatbot needs to detect user's intent given a few words, which
-  essentially  equals  to  short-text  classification  problem  in  the field of Natural  Language  Processing.
-Moreover,  each  time  for  a  new service, the task-specific  chatbot  system  often needs to perform well in few-shot setups due  to lack of domain-specific data, which is quite a challenge for single-model system such as text classification model system or sentence-pair semantic similarity model system under such a low-resource condition.
-Therefore, in this paper, we propose
-  SFC,  a 2-stage joint system with multi-task training technique for both text classification task and sentence-pair semantic similarity task to
-  overcome  this challenge.
-Furthermore, we additionally propose an improved version of SFC to allow text classification model and sentence-pair model be combined into a joint model organized in hierarchical structure.
-We also
-  conduct extensive experiments on 4 public and 1 private datasets in few-shot setup (i.e.,
-  with only 5 to 20 training data per class). The experimental results show that
-  our  system can steadily outperform several competitive single-model baselines by 2 percent
-  in average accuracy.
+    Building  conversational  chatbot  system  has  become a popular solution to
+    customer services under various business scenarios. A conversational chatbot
+    needs to detect user's intent given a few words, which essentially equals to
+    short-text   classification   problem  in  the  field  of  Natural  Language
+    Processing. Moreover, each time for a new service, the task-specific chatbot
+    system  often  needs  to  perform  well  in  few-shot  setups due to lack of
+    domain-specific  data,  which  is  quite a challenge for single-model system
+    such   as   text  classification  model  system  or  sentence-pair  semantic
+    similarity  model  system under such a low-resource condition. Therefore, in
+    this  paper, we propose SFC, a 2-stage joint system with multi-task training
+    technique  for  both  text  classification  task  and sentence-pair semantic
+    similarity  task  to  overcome  this challenge. Furthermore, we additionally
+    propose  an  improved  version of SFC to allow text classification model and
+    sentence-pair model be combined into a joint model organized in hierarchical
+    structure.  We  also conduct extensive experiments on 4 public and 1 private
+    datasets  in  few-shot  setup  (i.e.,  with  only  5 to 20 training data per
+    class).   The  experimental  results  show  that  our  system  can  steadily
+    outperform  several  competitive  single-model  baselines  by  2  percent in
+    average accuracy.
   \end{abstract}
-%\keywords{}
 
@@
   \label{sec:intro}
-% latest version start
-Task-specific conversational chatbot\cite{wen2016network} are designed to share the working pressure of human customer service agents who are responsible for solving customers' questions or queries about certain products or services.
-Regardless of whether the conversation is single-turn or multi-turn, the essential technical solution behind the chatbot is intent classification model which can identify the correct intent behind user's input text and find the corresponding answer.
+  Task-specific  conversational  chatbot\cite{wen2016network}  are  designed  to
+  share   the  working  pressure  of  human  customer  service  agents  who  are
+  responsible for solving customers' questions or queries about certain products
+  or  services.  Regardless  of  whether  the  conversation  is  single-turn  or
+  multi-turn,  the  essential  technical  solution  behind the chatbot is intent
+  classification model which can identify the correct intent behind user's input
+  text and find the corresponding answer.
 
-Although task-specific conversational chatbot already has a wide application in various business and industries, it's still a quite challenging task due to its natural properties of low-resource.
-First, customers' utterance within a conversation is usually quite short and completed in a few words.
-Short text\cite{song2014short} are generally more ambiguous in comparison with long texts such as paragraphs or documents since they don't contain enough contextual information, which poses a great challenge\cite{chen2019deep} for classification task\cite{phan2008learning,yan2009dynamic,hua2015short}.
-Second, at the initial stage of building a chatbot for specific task or service, it's often extremely hard to collect sufficient data samples for each class.
-The reason is that it's usually too expensive and time consuming to extract different ways of natural language expression for each intent class from history conversation log or even manually compose the corpus from nothing.
-Therefore, the key to building a task-specific chatbot with high performance becomes solving the challenge of short-text classification\cite{sriram2010short} problem under few-shot setting\cite{yu2018diverse}.
+  Although  task-specific  conversational chatbot already has a wide application
+  in various business and industries, it's still a quite challenging task due to
+  its  natural  properties of low-resource. First, customers' utterance within a
+  conversation  is  usually  quite  short  and  completed  in a few words. Short
+  text\cite{song2014short}  are generally more ambiguous in comparison with long
+  texts  such  as  paragraphs  or  documents  since  they  don't  contain enough
+  contextual  information,  which poses a great challenge\cite{chen2019deep} for
+  classification        task\cite{phan2008learning,yan2009dynamic,hua2015short}.
+  Second,  at  the  initial  stage  of  building  a chatbot for specific task or
+  service, it's often extremely hard to collect sufficient data samples for each
+  class.  The  reason  is  that it's usually too expensive and time consuming to
+  extract  different  ways  of natural language expression for each intent class
+  from  history  conversation  log  or  even  manually  compose  the corpus from
+  nothing.  Therefore,  the  key  to  building a task-specific chatbot with high
+  performance     becomes     solving     the     challenge     of    short-text
+  classification\cite{sriram2010short}        problem       under       few-shot
+  setting\cite{yu2018diverse}.
 
@@
       \label{Fig.1.sub.1}
-\includegraphics[scale=0.7]{picture/picture1.pdf}}
+      \includegraphics[scale=0.7]{picture/picture1.pdf}
+    }
     \subfigure[similarity model]{
       \label{Fig.1.sub.2}
-\includegraphics[scale=0.55]{picture/picture2.pdf}}
+      \includegraphics[scale=0.55]{picture/picture2.pdf}
+    }
     \caption{Two popular structures of building task-specific conversational chatbot}
@@
 
-One of the most popular approach among existing work was text classification model based on neural network.
-Since the length of the text is quite short, many previous work\cite{wen2016network} choose neural network such as convolutional neural networks (CNNs)\cite{kim2014convolutional,zhang2015character,conneau2016very}
-or long short term memory networks
-(LSTMs)\cite{mousa2017contextual,liu2016recurrent} to accomplish the task of extracting semantic feature from limited amount of words.
-A common model structure is adding a softmax classifier to the top of the neural network.
-Afterwards, pre-trained language models on large corpus like BERT\cite{devlin2018bert} and
-RoBERTa\cite{liu2019roberta} has  been proven more powerful in solving many NLP
-tasks      including      short-text      classification\cite{madabushi2020cost}.
-Especially   for  few-shot  scenarios\cite{yu2018diverse}, pre-trained  model  based on transformers\cite{vaswani2017attention}, shown in Fig.
-\ref{Fig.1.sub.1}, tends  to  do more help to reducing the negative effects brought by scarcity of training data.
+  One  of  the most popular approach among existing work was text classification
+  model  based  on  neural network. Since the length of the text is quite short,
+  many   previous   work\cite{wen2016network}  choose  neural  network  such  as
+  convolutional                          neural                         networks
+  (CNNs)\cite{kim2014convolutional,zhang2015character,conneau2016very}  or  long
+  short  term memory networks (LSTMs)\cite{mousa2017contextual,liu2016recurrent}
+  to  accomplish  the task of extracting semantic feature from limited amount of
+  words.  A  common model structure is adding a softmax classifier to the top of
+  the  neural  network.  Afterwards, pre-trained language models on large corpus
+  like   BERT\cite{devlin2018bert}  and  RoBERTa\cite{liu2019roberta}  has  been
+  proven   more   powerful  in  solving  many  NLP  tasks  including  short-text
+  classification\cite{madabushi2020cost}.      Especially      for      few-shot
+  scenarios\cite{yu2018diverse},       pre-trained      model      based      on
+  transformers\cite{vaswani2017attention},   shown  in  Fig.  \ref{Fig.1.sub.1},
+  tends  to do more help to reducing the negative effects brought by scarcity of
+  training data.
 
-Another common approach is text classification neural network based on label-word joint embedding, such as LEAM\cite{wang2018joint}, MTLE\cite{zhang2017multi} and EXAM\cite{du2019explicit}.
-This approach involves label embedding when constructing the text-sequence representation.
-Take LEAM as an example, the text classification model is implemented by jointly embedding the word and label in the same latent space\cite{wang2018joint}.
-Afterwards, the text representation are constructed based on text-label compatibility through attention mechanism.
-In this way, additional sources of semantic information from class labels can be fully leveraged, which is quite helpful especially under few-shot scenario.
+  Another  common  approach  is  text  classification  neural  network  based on
+  label-word     joint     embedding,    such    as    LEAM\cite{wang2018joint},
+  MTLE\cite{zhang2017multi}   and   EXAM\cite{du2019explicit}.   This   approach
+  involves  label  embedding when constructing the text-sequence representation.
+  Take  LEAM  as  an  example,  the  text classification model is implemented by
+  jointly    embedding    the    word    and    label   in   the   same   latent
+  space\cite{wang2018joint}. Afterwards, the text representation are constructed
+  based  on  text-label  compatibility through attention mechanism. In this way,
+  additional  sources  of  semantic  information  from class labels can be fully
+  leveraged, which is quite helpful especially under few-shot scenario.
 
-The third popular approach among previous work was based on sentence-pair model.
-The motivation of this approach was started from the idea of Information Retrival (IR) based chatbot\cite{jafarpour2010filter, leuski2011npceditor}.
-Having a Q-A (Question-Answer) pairs dataset and user query Q, the IR based conversational system will look up in the Q-A dataset for the pair (Q', A') that best matches query Q through semantic analysis and returns A' as the answer to Q\cite{mnasri2019recent}.
-In this way, sentence-pair model pre-trained on large corpus of semantic similarity identification task can be applied for being used as a tool to identify the class with highest semantic similarity to customer's query.
-A common model structure of pre-trained\cite{devlin2018bert} sentence-pair model is based on multiple cross-attention mechanism\cite{barkan2020scalable}, shown in Fig.
-\ref{Fig.1.sub.2}.
-Due to the fact that many experiment results have shown that RoBERTa\cite{liu2019roberta} is an improved  version  of  BERT, and has achieved amazing results on both text classification and sentence-pairs semantic similarity tasks, we choose RoBERTa as an important baseline approach in this paper.
+  The  third  popular  approach  among  previous work was based on sentence-pair
+  model.  The  motivation  of  this  approach  was  started  from  the  idea  of
+  Information     Retrival    (IR)    based    chatbot\cite{jafarpour2010filter,
+  leuski2011npceditor}.  Having  a  Q-A (Question-Answer) pairs dataset and user
+  query  Q,  the  IR based conversational system will look up in the Q-A dataset
+  for  the pair (Q', A') that best matches query Q through semantic analysis and
+  returns   A'   as   the  answer  to  Q\cite{mnasri2019recent}.  In  this  way,
+  sentence-pair  model  pre-trained  on  large  corpus  of  semantic  similarity
+  identification  task  can  be applied for being used as a tool to identify the
+  class  with  highest  semantic  similarity to customer's query. A common model
+  structure  of pre-trained\cite{devlin2018bert} sentence-pair model is based on
+  multiple  cross-attention  mechanism\cite{barkan2020scalable},  shown  in Fig.
+  \ref{Fig.1.sub.2}.  Due  to  the  fact that many experiment results have shown
+  that  RoBERTa\cite{liu2019roberta}  is  an  improved  version of BERT, and has
+  achieved  amazing  results  on  both  text  classification  and sentence-pairs
+  semantic similarity tasks, we choose RoBERTa as an important baseline approach
+  in this paper.
 
-Despite the success of these 3 approaches, they still have some limitations in task-specific chatbot scenario.
-As for the text classification model approach, it's quite hard to use data augmentation method to solve the data insufficiency challenge since the it's usually unfeasible to get large amount of domain-specific data when facing a new task.
-As for label-word joint embedding approach, it poses noticeable requirements on label information.
-However, in our cases, since we have large amount of class labels without being well-defined for question answering chatbot, the only thing we can do is to choose one of the user utterance as the class label to represent the key information of the whole class.
-In this way, the label will become not only prolix but also biased, which will bring some negative effect to label embedding.
-With respect to the sentence-pair model approach, though we can obtain large amount of data in semantically duplicate sentence pair identification domain for transfer learning\cite{sun2019fine}, it's still quite hard to perform well on task-specific dataset because the training objective of sentence-pair model is semantic similarity, which is slightly different from the target of classification task.
-That is to say, there always exists some intent classes which cannot be distinguished by each other merely depending on semantic similarity.
-For example, we have 2 user query saying, A: What should I do if I want to change my password?
-B: What is the modification rule if I want to change my password?
-In this case, sentence A is semantically similar to B, since they both express the
-desire for changing password.
-However, it's still reasonable to classify them into 2 intent classes, since A is asking for the method for changing password, while B is asking for the rule to follow when creating a new password.
+  Despite the success of these 3 approaches, they still have some limitations in
+  task-specific chatbot scenario. As for the text classification model approach,
+  it's   quite   hard  to  use  data  augmentation  method  to  solve  the  data
+  insufficiency  challenge since the it's usually unfeasible to get large amount
+  of  domain-specific  data  when  facing  a  new  task. As for label-word joint
+  embedding  approach,  it  poses  noticeable requirements on label information.
+  However,  in  our  cases,  since  we have large amount of class labels without
+  being well-defined for question answering chatbot, the only thing we can do is
+  to  choose  one  of the user utterance as the class label to represent the key
+  information  of  the  whole class. In this way, the label will become not only
+  prolix  but  also  biased,  which  will  bring  some  negative effect to label
+  embedding.  With  respect  to  the sentence-pair model approach, though we can
+  obtain   large   amount  of  data  in  semantically  duplicate  sentence  pair
+  identification  domain  for  transfer  learning\cite{sun2019fine},  it's still
+  quite  hard  to  perform  well  on  task-specific dataset because the training
+  objective  of  sentence-pair  model  is semantic similarity, which is slightly
+  different from the target of classification task. That is to say, there always
+  exists  some intent classes which cannot be distinguished by each other merely
+  depending on semantic similarity. For example, we have 2 user query saying, A:
+  What  should I do if I want to change my password? B: What is the modification
+  rule if I want to change my password? In this case, sentence A is semantically
+  similar  to  B,  since  they  both  express  the desire for changing password.
+  However, it's still reasonable to classify them into 2 intent classes, since A
+  is asking for the method for changing password, while B is asking for the rule
+  to follow when creating a new password.
 
@@
       \includegraphics[scale=0.48]{picture/picture3}
-\par\end{centering}
+      \par
+    \end{centering}
     \caption{\textbf{Network Structure of 2-stage SFC:} a joint system of multi-task for both text classification task and sentence-pair semantic similarity task.}
@@
 
-The above limitation motivates us to propose a joint system of both text classification task and sentence-pair semantic similarity task, named SFC here, shown in Fig.
-\ref{fig:ver.1.3}.
-Our goal is to utilize the advantage of the feasibility of transfer learning based on semantic similarity, while in the mean time, add the classification task's target into the training process of sentence-pair model for multi-task learning\cite{caruana1993multitask,collobert2008unified}.
-To obtain such a joint system, we first start with preparation work, which is pre-training a sentence-pair model on external corpus for sentence pair duplication identification, and then find an auxiliary model or tool which can help us sample out top-K most related intent classes.
-This auxiliary model or tool can either be searching engine such as elasticsearch\cite{divya2013elasticsearch} or a text classification model trained on task-specific chatbot data.
-Afterwards, we further fine-tune the sentence-pair model with 2 training tasks: 1) the regular sentence pair similarity tasks.
-Here we use the text classification model as an auxiliary model in this paper to sample sentence pairs for training based on negative sampling strategy\cite{bamler2020extreme}.
-The reason is that a task-specific chatbot often has hundreds of intent classes, which forms too many sentence pairs for training since any two sentences from two different classes can form a sentence-pair of negative sample.
-Besides, according to Bamler\cite{bamler2020extreme}, training on negative samples from most confusing wrong label can help model converge faster and obtain better performance.
-2) the classification task on top-K (here K is a hyperparameter) candidate classes provided by our auxiliary model or tool.
-Here we use the average pooling of the representation given by sentence-pair model for sentence pairs formed by the user input query and the corpus sentences in each class as the feature.
-We stack the task-specific layers on the top of the shared-parameter sentence-pair model structure, which is a classic parameter sharing mechanism\cite{collobert2008unified, subramanian2018learning,liu2019multi} for multi-task\cite{sun2019fine}.
-In this way, specific knowledge contained in these 2 tasks can be fully explored and deeply interact with each other to obtain better overall performance.
+  The  above  limitation  motivates  us  to  propose a joint system of both text
+  classification  task  and  sentence-pair  semantic  similarity task, named SFC
+  here, shown in Fig. \ref{fig:ver.1.3}. Our goal is to utilize the advantage of
+  the  feasibility  of  transfer learning based on semantic similarity, while in
+  the  mean time, add the classification task's target into the training process
+  of            sentence-pair           model           for           multi-task
+  learning\cite{caruana1993multitask,collobert2008unified}.  To  obtain  such  a
+  joint  system,  we  first start with preparation work, which is pre-training a
+  sentence-pair   model   on  external  corpus  for  sentence  pair  duplication
+  identification,  and  then  find  an auxiliary model or tool which can help us
+  sample out top-K most related intent classes. This auxiliary model or tool can
+  either  be searching engine such as elasticsearch\cite{divya2013elasticsearch}
+  or  a  text  classification  model  trained  on  task-specific  chatbot  data.
+  Afterwards,  we  further  fine-tune  the  sentence-pair  model with 2 training
+  tasks:  1)  the  regular  sentence pair similarity tasks. Here we use the text
+  classification  model  as  an auxiliary model in this paper to sample sentence
+  pairs       for       training       based      on      negative      sampling
+  strategy\cite{bamler2020extreme}.  The  reason is that a task-specific chatbot
+  often  has hundreds of intent classes, which forms too many sentence pairs for
+  training  since  any  two  sentences  from  two  different  classes can form a
+  sentence-pair     of     negative     sample.     Besides,     according    to
+  Bamler\cite{bamler2020extreme},   training   on  negative  samples  from  most
+  confusing  wrong  label  can  help  model  converge  faster  and obtain better
+  performance.  2) the classification task on top-K (here K is a hyperparameter)
+  candidate  classes  provided  by  our auxiliary model or tool. Here we use the
+  average  pooling  of  the  representation  given  by  sentence-pair  model for
+  sentence pairs formed by the user input query and the corpus sentences in each
+  class  as  the  feature.  We  stack the task-specific layers on the top of the
+  shared-parameter  sentence-pair  model structure, which is a classic parameter
+  sharing                                   mechanism\cite{collobert2008unified,
+  subramanian2018learning,liu2019multi}   for  multi-task\cite{sun2019fine}.  In
+  this  way, specific knowledge contained in these 2 tasks can be fully explored
+  and deeply interact with each other to obtain better overall performance.
 
-However, since the auxiliary tool in joint system mentioned above works in a separate stage from sentence-pair model, we find the the quality of sampled candidate classes might limit the overall performance of SFC, since the candidate classes for each user query is always fixed during the multi-task training process.
-This observation motivates us to further improve SFC into a joint model of sentence-pair model and text classification model in a hierarchical architecture by putting different tasks at different network layers\cite{sogaard2016deep, hashimoto2016joint} and then training them together, shown in Fig \ref{fig:framework}.
-Here, the text classification model involved in joint training process replace the role of auxiliary tools.
-In this way, the sentence pairs selected from top-K classes becomes dynamic, which means the text classification model will also be further optimized to provide better top-K classes pooling result.
+  However,  since  the auxiliary tool in joint system mentioned above works in a
+  separate  stage  from  sentence-pair model, we find the the quality of sampled
+  candidate  classes  might  limit  the  overall  performance  of SFC, since the
+  candidate  classes  for  each user query is always fixed during the multi-task
+  training  process. This observation motivates us to further improve SFC into a
+  joint  model  of  sentence-pair  model  and  text  classification  model  in a
+  hierarchical  architecture  by  putting  different  tasks at different network
+  layers\cite{sogaard2016deep,   hashimoto2016joint}   and  then  training  them
+  together,  shown  in  Fig  \ref{fig:framework}.  Here, the text classification
+  model  involved in joint training process replace the role of auxiliary tools.
+  In  this  way, the sentence pairs selected from top-K classes becomes dynamic,
+  which  means  the  text classification model will also be further optimized to
+  provide better top-K classes pooling result.
 
@@
 
-1) We propose a novel joint system named SFC with multi-task training technique designed for task-specific conversational chatbot with low-resource, in which we make full utilization of the advantages brought by both the text classification task and sentence-pair semantic similarity task.
+  1)  We  propose  a  novel  joint  system  named  SFC  with multi-task training
+  technique designed for task-specific conversational chatbot with low-resource,
+  in  which  we make full utilization of the advantages brought by both the text
+  classification task and sentence-pair semantic similarity task.
 
-2) To further improve the system performance of SFC, we also propose an innovative joint model structure, in which the text classification model and sentence-pair model are fused into one single model for joint training.
+  2)  To  further  improve  the  system  performance  of SFC, we also propose an
+  innovative  joint  model structure, in which the text classification model and
+  sentence-pair model are fused into one single model for joint training.
 
-3) Experiment results on 4 public and 1 private short-text classification datasets with respect to intent recognition tasks under conversational chatbot scenario all demonstrated that our proposed SFC joint system with multi-task, as well as the improved version of SFC, can both achieve remarkable improvement comparing to some powerful single-task and single-model baselines, especially under few-shot settings.
+  3)  Experiment  results  on  4  public and 1 private short-text classification
+  datasets with respect to intent recognition tasks under conversational chatbot
+  scenario  all demonstrated that our proposed SFC joint system with multi-task,
+  as  well  as  the  improved  version  of  SFC,  can  both  achieve  remarkable
+  improvement comparing to some powerful single-task and single-model baselines,
+  especially under few-shot settings.
 
@@
       \includegraphics[scale=0.72]{picture/picture4} 
-\par\end{centering}
-\caption{\textbf{Network Structure of hierarchical SFC:} a joint model of sentence-pair model and text classification model organized in hierarchical structure by completing different tasks at different network layers.}
+      \par
+    \end{centering}
+    \caption{
+      \textbf{Network   Structure   of  hierarchical  SFC:}  a  joint  model  of
+      sentence-pair   model   and   text   classification   model  organized  in
+      hierarchical  structure by completing different tasks at different network
+      layers.
+    }
     \label{fig:framework}
@@
   \section{Methodology}
-In this section, we will describe a system of similarity model fused with classification model, named as SFC, in detail.
-We come up with 2 different approaches for implementation of SFC system, in which hierarchical SFC is a further improvement of 2-stage SFC for better performance.
+  In  this  section,  we  will  describe a system of similarity model fused with
+  classification  model,  named  as  SFC, in detail. We come up with 2 different
+  approaches  for  implementation  of SFC system, in which hierarchical SFC is a
+  further improvement of 2-stage SFC for better performance.
+
   \subsection{2-stage SFC with multi-task learning}
-The detailed network structure of 2-stage SFC is shown in Fig. \ref{fig:ver.1.3}. It is composed with 2 separate stages in charge of different jobs.
-In stage 1, we can use any auxiliary model or tool to provide top-K most related class labels for sampling sentence pairs of both positive samples and negative samples for stage 2.
-Suppose we have a training data set $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$ of $N$ data points, in which $x_{i}$ is the user input query and $y_{i}$ is a single class label from a class label set of $C$ classes in total.
-If we want to generate sentence pair data set $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$, where $(x, x')_{j}$ is sentence pair grouped by 2 user input queries and $l_{j}\in\{0, 1\}$ is similarity class label, see Equ.
-\ref{eq:similarity label},
+
+  The   detailed   network   structure   of   2-stage   SFC  is  shown  in  Fig.
+  \ref{fig:ver.1.3}.  It  is  composed  with  2  separate  stages  in  charge of
+  different  jobs. In stage 1, we can use any auxiliary model or tool to provide
+  top-K  most  related class labels for sampling sentence pairs of both positive
+  samples  and negative samples for stage 2. Suppose we have a training data set
+  $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$  of  $N$ data points, in which $x_{i}$
+  is the user input query and $y_{i}$ is a single class label from a class label
+  set  of  $C$  classes  in total. If we want to generate sentence pair data set
+  $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$,   where   $(x,   x')_{j}$  is
+  sentence  pair  grouped  by  2  user  input  queries and $l_{j}\in\{0, 1\}$ is
+  similarity class label, see Equ. \ref{eq:similarity label},
   \begin{align}
-l_{j}=\begin{cases} \label{eq:similarity label}
+    l_{j}=
+    \begin{cases} \label{eq:similarity label}
       0 & y_{x}\neq y_{x'}\\
@@
   \end{align}
-directly from original data set $\mathcal{D}$ without any sampling strategy, then $\mathcal{D'}$ will have $M=N^2$ data points of sentence pairs, which might be too time-consuming for the training process of stage 2 since we often have hundreds of class labels under task-specific chatbot scenario.
-Although we may only have a few data points for a single class label, $M$ is still quite a big number.
+  directly  from  original data set $\mathcal{D}$ without any sampling strategy,
+  then  $\mathcal{D'}$  will  have  $M=N^2$ data points of sentence pairs, which
+  might be too time-consuming for the training process of stage 2 since we often
+  have  hundreds  of class labels under task-specific chatbot scenario. Although
+  we  may  only  have  a  few data points for a single class label, $M$ is still
+  quite a big number.
 
-Therefore, we adopt the idea of adversarial negative sampling strategy raised by \cite{bamler2020extreme}.
-The key idea of this sampling strategy is to train with negative samples that are hard to be distinguished from positive samples.
-Now suppose we have a user input query $x_{i}$ and top-K most related class labels set $\mathcal{C'}=\{c'_{1}, \dots, c'_{K}\}$ provided by auxiliary model or tool in stage 1, where $K$ is a hyperparameter set by us that controls candidate class number, we apply the adversarial negative sampling strategy into our sentence pair sampling process by the following 2 steps:
+  Therefore,  we adopt the idea of adversarial negative sampling strategy raised
+  by  \cite{bamler2020extreme}.  The  key  idea  of this sampling strategy is to
+  train  with  negative  samples that are hard to be distinguished from positive
+  samples. Now suppose we have a user input query $x_{i}$ and top-K most related
+  class   labels   set  $\mathcal{C'}=\{c'_{1},  \dots,  c'_{K}\}$  provided  by
+  auxiliary  model  or  tool in stage 1, where $K$ is a hyperparameter set by us
+  that  controls  candidate  class  number,  we  apply  the adversarial negative
+  sampling  strategy  into our sentence pair sampling process by the following 2
+  steps:
 
-\textbf{1.
-positive sentence pair sampling}: During the training process, we have to first make sure that the ground truth class label $y_{i}$ for $x_{i}$ is within the candidate class label set $\mathcal{C'}$.
-If $y_{i}\notin \mathcal{C'}$, we will manually add $y_{i}$ into $\mathcal{C'}$ by replacing $c'_{K}$ with $y_{i}$, since $c'_{K}$ is the least promising candidate label according to the auxiliary model in stage 1.
-Afterwards, we will randomly sample $P$ sentences $\{x'_{0},x'_{1}, \dots, x'_{P}\}$ with the same class label as $y_{i}$ from data set $\mathcal{D}$ to form the set of sentence pairs with positive label $\mathcal{P'}_{i}=\{[(x_{i}, x'_{0}), 1], [(x_{i}, x'_{1}), 1], \dots, [(x_{i}, x'_{P}), 1]\}$, where $P$ is also a hyperparameter set by us that controls the number of sentences we should sample from each class.
+  \textbf{1.  positive  sentence pair sampling}: During the training process, we
+  have  to first make sure that the ground truth class label $y_{i}$ for $x_{i}$
+  is  within  the  candidate  class  label  set  $\mathcal{C'}$. If $y_{i}\notin
+  \mathcal{C'}$,  we  will manually add $y_{i}$ into $\mathcal{C'}$ by replacing
+  $c'_{K}$  with  $y_{i}$, since $c'_{K}$ is the least promising candidate label
+  according  to  the  auxiliary  model  in stage 1. Afterwards, we will randomly
+  sample  $P$  sentences  $\{x'_{0},x'_{1}, \dots, x'_{P}\}$ with the same class
+  label as $y_{i}$ from data set $\mathcal{D}$ to form the set of sentence pairs
+  with   positive   label  $\mathcal{P'}_{i}=\{[(x_{i},  x'_{0}),  1],  [(x_{i},
+  x'_{1}),   1],   \dots,   [(x_{i},   x'_{P}),  1]\}$,  where  $P$  is  also  a
+  hyperparameter  set  by  us  that  controls  the number of sentences we should
+  sample from each class.
 
-\textbf{2.
-negative sentence pair sampling}: As for negative sentence pairs, we will also randomly sample $P$ sentences for each class in the negative candidate class label set $\mathcal{C'}\backslash \{y_{i}\}$.
-The class labels in $\mathcal{C'}\backslash \{y_{i}\}$ are the set of most confusing class labels comparing to the ground truth ${y_{i}}$, so we assume that the sentence pairs with negative label grouped by user input query $x_{i}$ and sentences with class labels in $\mathcal{C'}\backslash \{y_{i}\}$ are strong adversarial negative samples for sentence-pair similarity model that can help enhance the training speed and performance.
-According to the same method as positive sentence pair sampling, we can obtain the set of sentence pairs with negative label as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{0}), 0], [(x_{i}, x'_{1}), 0], ..., [(x_{i}, x'_{P\cdot (K-1)}), 0]\}$
+  \textbf{2.  negative  sentence pair sampling}: As for negative sentence pairs,
+  we  will  also  randomly  sample  $P$ sentences for each class in the negative
+  candidate class label set $\mathcal{C'}\backslash \{y_{i}\}$. The class labels
+  in  $\mathcal{C'}\backslash  \{y_{i}\}$  are  the  set of most confusing class
+  labels comparing to the ground truth ${y_{i}}$, so we assume that the sentence
+  pairs  with  negative  label grouped by user input query $x_{i}$ and sentences
+  with class labels in $\mathcal{C'}\backslash \{y_{i}\}$ are strong adversarial
+  negative  samples for sentence-pair similarity model that can help enhance the
+  training  speed  and  performance.  According  to  the same method as positive
+  sentence  pair sampling, we can obtain the set of sentence pairs with negative
+  label  as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{0}), 0], [(x_{i}, x'_{1}), 0], ...,
+  [(x_{i}, x'_{P\cdot (K-1)}), 0]\}$
 
-In this way, we can generate the sentence pair data set $\mathcal{D'}$ for stage 2 based on the top-K class label set $\mathcal{C'}$ provided by stage 1 as $\mathcal{D'}=\{\mathcal{P'}_{i}\cup \mathcal{N'}_{i}\}_{i=1}^{N}$, in which we will have $M=N\cdot K\cdot P$ data points of sentence pairs in total.
+  In  this  way,  we  can generate the sentence pair data set $\mathcal{D'}$ for
+  stage  2 based on the top-K class label set $\mathcal{C'}$ provided by stage 1
+  as   $\mathcal{D'}=\{\mathcal{P'}_{i}\cup   \mathcal{N'}_{i}\}_{i=1}^{N}$,  in
+  which we will have $M=N\cdot K\cdot P$ data points of sentence pairs in total.
 
-After explaining the data sampling principle for sentence pairs and how the 2 stages in SFC system connect with each other, let's go deeper into model structure within these 2 stages respectively to see how it works.
+  After  explaining the data sampling principle for sentence pairs and how the 2
+  stages  in  SFC  system  connect  with  each other, let's go deeper into model
+  structure within these 2 stages respectively to see how it works.
 
-\subsubsection{stage 1: classification model for providing top-K candidate class labels}
-As for stage 1, our SFC system can adapt to any auxiliary model or even searching tool based on Term Frequency-Inverse
-Document Frequency (TF-IDF) retrieval.
-In this paper, however, we choose to fine-tune RoBERTa on our task-specific data set $\mathcal{D}$ by adding a softmax classifier on top of it, the same as the structure shown in Fig.
-\ref{Fig.1.sub.1}, for better overall performance.
-According to our experimental result, RoBERTa can guarantee that approximately 95\% ground truth label be included in top-5 candidate class labels with highest probability after being fine-tuned on task-specific data set with experimental result measured by F-score at around 0.75.
-So we use RoBERTa as encoder of classification model in our setting at stage 1 to ensure low limitation for the performance of stage 2.
+  \subsubsection*{
+    stage 1: classification model for providing top-K candidate class labels
+  }
 
-For single-sentence text classification tasks, given a data point $x_{i}$ with class label $y_{i}$ from data set $\mathcal{D}$, RoBERTa takes the final hidden state $h_{i}$ of the first token [CLS] as the representation for the whole sequence of $x_{i}$.
-Let's suppose we have a linear layer as ${\Phi}^C_{i}=W^Ch_{i}+b^C$, where $W^C$ and $b^C$ are trainable parameters, the probability score for $x_{i}$ can be calculated as $p^C_{i}=softmax(W^Ch_{i}+b^C)=softmax({\Phi}^C_{i})$.
-Then, the loss for stage 1 classification model is shown in Equ.
-\ref{eq:classification loss}, in which the first term $\varPhi_{i,y_{i}}^C$ encourages high probability for prediction of the correct label $y_{i}$.
+  As for  stage  1,  our  SFC  system  can adapt to any auxiliary model or even
+  searching  tool  based  on  Term Frequency-Inverse Document Frequency (TF-IDF)
+  retrieval.  In  this  paper,  however,  we  choose to fine-tune RoBERTa on our
+  task-specific  data set $\mathcal{D}$ by adding a softmax classifier on top of
+  it,  the  same  as  the  structure shown in Fig. \ref{Fig.1.sub.1}, for better
+  overall  performance.  According  to  our  experimental  result,  RoBERTa  can
+  guarantee  that  approximately  95\%  ground  truth label be included in top-5
+  candidate  class  labels  with  highest  probability after being fine-tuned on
+  task-specific  data set with experimental result measured by F-score at around
+  0.75.  So  we use RoBERTa as encoder of classification model in our setting at
+  stage 1 to ensure low limitation for the performance of stage 2.
+
+  For single-sentence text classification tasks, given a data point $x_{i}$ with
+  class  label  $y_{i}$  from  data  set  $\mathcal{D}$, RoBERTa takes the final
+  hidden  state  $h_{i}$  of the first token [CLS] as the representation for the
+  whole   sequence  of  $x_{i}$.  Let's  suppose  we  have  a  linear  layer  as
+  ${\Phi}^C_{i}=W^Ch_{i}+b^C$,  where  $W^C$ and $b^C$ are trainable parameters,
+  the    probability    score    for    $x_{i}$    can    be    calculated    as
+  $p^C_{i}=softmax(W^Ch_{i}+b^C)=softmax({\Phi}^C_{i})$.   Then,  the  loss  for
+  stage 1 classification model is shown in Equ. \ref{eq:classification loss}, in
+  which  the  first  term  $\varPhi_{i,y_{i}}^C$ encourages high probability for
+  prediction of the correct label $y_{i}$.
 
@@
 
-\subsubsection{stage 2: sentence-pair model for multi-task learning}
-As for stage 2, we also choose RoBERTa as the encoder for sentence pairs, as shown in Fig.
-\ref{fig:ver.1.3}.
-Before sending sentence pairs to Roberta, we pack sentence pairs into a single sequence and separate them with a special token [SEP].
-Roberta will also add a learned embedding to every token indicating whether it belongs to the first sentence or the second one.
-Then, we utilize the cross-attention mechanism inside RoBERTa, and then extract semantic relationship between 2 sentences from the output softmax layer, which is placed on top of the last hidden representation of the [CLS] token.
+  \subsubsection*{
+    stage 2: sentence-pair model for multi-task learning
+  }
 
-Before we start to fine-tune our sentence-pair model on task-specific dataset, we first fine-tune RoBERTa on Quora dataset\cite{iyer2017first}, which contains 404,290 potential duplicate question pairs, for transfer learning.
-Then we continue to do multi-task training on sentence-pair dataset $\mathcal{D'}$ sampled from the top-K candidate class labels provided by stage 1.
+  As for  stage 2, we also choose RoBERTa as the encoder for sentence pairs, as
+  shown  in Fig. \ref{fig:ver.1.3}. Before sending sentence pairs to Roberta, we
+  pack  sentence  pairs  into a single sequence and separate them with a special
+  token  [SEP].  Roberta  will  also  add  a  learned  embedding  to every token
+  indicating  whether  it belongs to the first sentence or the second one. Then,
+  we  utilize  the  cross-attention  mechanism  inside RoBERTa, and then extract
+  semantic relationship between 2 sentences from the output softmax layer, which
+  is placed on top of the last hidden representation of the [CLS] token.
+
+  Before we start to fine-tune our sentence-pair model on task-specific dataset,
+  we   first  fine-tune  RoBERTa  on  Quora  dataset\cite{iyer2017first},  which
+  contains  404,290  potential  duplicate question pairs, for transfer learning.
+  Then   we   continue  to  do  multi-task  training  on  sentence-pair  dataset
+  $\mathcal{D'}$ sampled from the top-K candidate class labels provided by stage
+  1.
 
@@
 
-For sentence pair semantic similarity task, given a data point $(x, x')_{i}$ with similarity label $l_{i}$ from data set $\mathcal{D'}=\{[(x,x')_{i},l_{i}]\}_{i=1}^{M}$, Roberta takes the final hidden state $h_{i}$ of the first token [CLS] as the representation for the sequence of packed sentence pair $(x, x')_{i}$.
-Let's suppose we have a linear layer as ${\Phi}^S_{i}=W^Sh_{i}+b^S$, where $W^S$ and $b^S$ are trainable parameters, and the probability score for $(x, x')_{i}$ can be calculated as $p^S_{i}=softmax({\Phi}^S_{i})$.
+  For  sentence  pair semantic similarity task, given a data point $(x, x')_{i}$
+  with       similarity       label       $l_{i}$       from       data      set
+  $\mathcal{D'}=\{[(x,x')_{i},l_{i}]\}_{i=1}^{M}$,   Roberta   takes  the  final
+  hidden  state  $h_{i}$  of the first token [CLS] as the representation for the
+  sequence of packed sentence pair $(x, x')_{i}$. Let's suppose we have a linear
+  layer  as  ${\Phi}^S_{i}=W^Sh_{i}+b^S$,  where  $W^S$  and $b^S$ are trainable
+  parameters,  and  the probability score for $(x, x')_{i}$ can be calculated as
+  $p^S_{i}=softmax({\Phi}^S_{i})$.
 
-Due to the fact that sentence pairs within the same class is much less than sentence pairs from different classes, the data set $\mathcal{D'}$ is imbalanced.
-Therefore, we will accommodate a weight variable $w^S = [K-1, 1]$ to the loss to eliminate the bias brought by imbalanced data, shown in Equ.
+  Due  to  the  fact that sentence pairs within the same class is much less than
+  sentence  pairs  from  different  classes,  the  data  set  $\mathcal{D'}$  is
+  imbalanced.  Therefore, we will accommodate a weight variable $w^S = [K-1, 1]$
+  to  the  loss  to eliminate the bias brought by imbalanced data, shown in Equ.
   \ref{eq:similarity loss}.
@@
 
-As for top-K classification task, it shares the same sentence-pair similarity model structure with task 1.
-The only difference is that we add a task-specific average pooling layer, shown in Fig.
-\ref{fig:ver.1.3} to implement the classification task based on sentence-pair model.
+  As  for top-K classification task, it shares the same sentence-pair similarity
+  model   structure  with  task  1.  The  only  difference  is  that  we  add  a
+  task-specific  average  pooling  layer,  shown  in  Fig.  \ref{fig:ver.1.3} to
+  implement the classification task based on sentence-pair model.
 
-We already know that the size of ${\Phi}^S$ in task 1 is $M\times 2=(N\cdot K\cdot P)\times 2$, where $N$ is the total number of data points in original training data $\mathcal{D}$, $K$ is a hyperparameter that controls the number of candidate class labels provided by stage 1, and $P$ is also a hyperparameter that controls the number of sentences we should randomly sample from each candidate class labels.
-Now, for the average pooling layer, we first reshape ${\Phi}^S$ into the size of $N\times K\times P\times 2$, and then split it into ${\Phi}^{K,pos}$ and ${\Phi}^{K,neg}$, and both of them will have the size of $N\times K\times P$.
-In this way, ${\Phi}^{K,pos}$ can represent the level of similarity for each sentence pair, and in the mean time, ${\Phi}^{K,neg}$ can represent the level of dissimilarity for each sentence pair.
-Then, we can do average pooling for each candidate class among the top-K classes as shown in Equ.
-\ref{eq:average pooling:1} and Equ.
+  We  already  know  that the size of ${\Phi}^S$ in task 1 is $M\times 2=(N\cdot
+  K\cdot  P)\times  2$, where $N$ is the total number of data points in original
+  training  data $\mathcal{D}$, $K$ is a hyperparameter that controls the number
+  of   candidate   class  labels  provided  by  stage  1,  and  $P$  is  also  a
+  hyperparameter that controls the number of sentences we should randomly sample
+  from each candidate class labels. Now, for the average pooling layer, we first
+  reshape  ${\Phi}^S$  into  the  size  of $N\times K\times P\times 2$, and then
+  split  it  into  ${\Phi}^{K,pos}$  and ${\Phi}^{K,neg}$, and both of them will
+  have  the  size  of  $N\times  K\times  P$.  In this way, ${\Phi}^{K,pos}$ can
+  represent  the  level  of  similarity  for each sentence pair, and in the mean
+  time,  ${\Phi}^{K,neg}$  can  represent  the  level  of dissimilarity for each
+  sentence  pair. Then, we can do average pooling for each candidate class among
+  the  top-K  classes  as  shown  in  Equ.  \ref{eq:average  pooling:1} and Equ.
   \ref{eq:average pooling:2}.
@@
 
-With the average pooling result ${\xi}^{K,pos}$ and ${\xi}^{K,neg}$, we also generate a top-K class label $l^{K}_i\in [1,\dots,K]$ for each ${\xi}^{K,pos}_{i}$ and  ${\xi}^{K,neg}_{i}$.
-The loss for top-K classification task is shown in Equ.
-\ref{eq:top-k classification loss}.
-In Equ.
-\ref{eq: pos top-k loss} and Equ.
-\ref{eq: neg top-k loss}, the first term $\xi_{i,l^{K}_{i}}^{K,pos}$ and $\xi_{i,l^{K}_{i}}^{K,neg}$ encourage high level of similarity and low level of dissimilarity for prediction of the correct label $l^{K}_i$ within the top-K candidate classes.
+  With  the  average pooling result ${\xi}^{K,pos}$ and ${\xi}^{K,neg}$, we also
+  generate   a   top-K   class   label   $l^{K}_i\in   [1,\dots,K]$   for   each
+  ${\xi}^{K,pos}_{i}$ and ${\xi}^{K,neg}_{i}$. The loss for top-K classification
+  task is shown in Equ. \ref{eq:top-k classification loss}. In Equ. \ref{eq: pos
+  top-k   loss}   and   Equ.   \ref{eq:   neg   top-k   loss},  the  first  term
+  $\xi_{i,l^{K}_{i}}^{K,pos}$  and  $\xi_{i,l^{K}_{i}}^{K,neg}$  encourage  high
+  level  of  similarity  and  low  level  of dissimilarity for prediction of the
+  correct label $l^{K}_i$ within the top-K candidate classes.
 
@@
 
-Therefore, the overall loss function for multi-task learning in stage 2 is shown in Equ.
-\ref{eq: 2-stage SFC loss}.
-The training objective of stage 2 is to minimize the weighted sum of task-specific losses.
-Here $\alpha_S$ and $\alpha_K$ are weights of task 1 and task 2 respectively, which are $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting.
+  Therefore,  the  overall  loss  function for multi-task learning in stage 2 is
+  shown in Equ. \ref{eq: 2-stage SFC loss}. The training objective of stage 2 is
+  to  minimize  the  weighted  sum  of task-specific losses. Here $\alpha_S$ and
+  $\alpha_K$  are  weights  of  task  1  and  task  2  respectively,  which  are
+  $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting.
 
@@
       \end{tabular}
-\par\end{centering}
+      \par
+    \end{centering}
     \caption{Key statistics for experimental datasets and few shot settings}
@@
   \subsection{hierarchical SFC with joint model structure}
-Despite the outstanding experimental result of 2-stage SFC on various tasks, we still find a limitation brought by the 2-stage system structure.
-In 2-stage SFC, Stage 1 and stage 2 are separate, so they do not interact with each other during training.
-In this case, the performance of stage 1 can limit the potential of stage 2, meanwhile, stage 2 also cannot give training feedback back to stage 1 for fine-tuning.
+  Despite  the  outstanding experimental result of 2-stage SFC on various tasks,
+  we still find a limitation brought by the 2-stage system structure. In 2-stage
+  SFC, Stage 1 and stage 2 are separate, so they do not interact with each other
+  during  training.  In  this  case,  the  performance  of stage 1 can limit the
+  potential  of  stage  2, meanwhile, stage 2 also cannot give training feedback
+  back to stage 1 for fine-tuning.
 
-Therefore, to further improve the overall performance of SFC, we proposed a hierarchical joint model structure, shown in Fig.
-\ref{fig:framework}.
-In hierarchical SFC, classification model is being placed in lower layer level to dynamically provide top-K candidate class labels for the sentence-pair similarity model placed in higher layer level through a top-K pooling layer.
-In this way, classification model and similarity model can be merged into one single joint-model for multi-task training with sentence pairs sampled from varying candidate class labels, thus avoiding the limitation brought by 2 separate stage structure.
+  Therefore,  to  further  improve the overall performance of SFC, we proposed a
+  hierarchical  joint  model  structure,  shown  in Fig. \ref{fig:framework}. In
+  hierarchical SFC, classification model is being placed in lower layer level to
+  dynamically  provide  top-K  candidate  class  labels  for  the  sentence-pair
+  similarity  model  placed in higher layer level through a top-K pooling layer.
+  In  this way, classification model and similarity model can be merged into one
+  single  joint-model  for  multi-task training with sentence pairs sampled from
+  varying  candidate  class  labels,  thus  avoiding the limitation brought by 2
+  separate stage structure.
 
-There are 3 tasks in total during the training process of hierarchical SFC, shown in Fig.
-\ref{fig:framework}, and the overall loss is also the weighted sum of all the task-specific losses, shown in Equ.
-\ref{eq: hierachical SFC loss}.
-Here, $\alpha_S$, $\alpha_K$ and $\alpha_C$ are the weights for task 1: sentence-pair similarity, task 2: top-K classification and task 3: general single sentence classification respectively, which are $\alpha_S=0.25$,  $\alpha_K=0.25$ and $\alpha_C=0.5$ in our setting.
+  There  are  3  tasks in total during the training process of hierarchical SFC,
+  shown  in  Fig. \ref{fig:framework}, and the overall loss is also the weighted
+  sum  of  all  the task-specific losses, shown in Equ. \ref{eq: hierachical SFC
+  loss}. Here, $\alpha_S$, $\alpha_K$ and $\alpha_C$ are the weights for task 1:
+  sentence-pair  similarity,  task  2:  top-K classification and task 3: general
+  single   sentence  classification  respectively,  which  are  $\alpha_S=0.25$,
+  $\alpha_K=0.25$ and $\alpha_C=0.5$ in our setting.
 
@@
 
-Finally, when doing inference, for each user input query $x$, we will choose the class label that contains the sentence $x'$ with highest similarity score $\varPhi$, after being packed into a sentence pair $(x, x')$ with query $x$, as our final result for prediction.
+  Finally,  when  doing inference, for each user input query $x$, we will choose
+  the  class label that contains the sentence $x'$ with highest similarity score
+  $\varPhi$,  after  being packed into a sentence pair $(x, x')$ with query $x$,
+  as our final result for prediction.
 
   \section{Experiments}
-In this section, we conduct extensive experiments over 5 task-specific datasets to evaluate the performance of our proposed SFC system and the effectiveness of the methodology of multi-task learning and hierachical joint-model structure under low-data settings.
+  In  this  section,  we  conduct  extensive  experiments  over  5 task-specific
+  datasets  to  evaluate  the  performance  of  our  proposed SFC system and the
+  effectiveness  of  the  methodology  of  multi-task  learning  and hierachical
+  joint-model structure under low-data settings.
 
   \subsection{Datasets}
-The datasets used in our experiments aims to help us study low-resource text classification problem under task-specific conversational chatbot scenario.
-Therefore, we keep all the dataset under low-resource chatbot corpus setting, which is a large number of class labels (50-250) with a few examples(5-20) in short text for each class, by sampling smaller subsets from the full scale when the raw datasets are oversized, see Table \ref{tbe:dataset statistic}.
+  The  datasets  used in our experiments aims to help us study low-resource text
+  classification  problem  under  task-specific conversational chatbot scenario.
+  Therefore,  we keep all the dataset under low-resource chatbot corpus setting,
+  which  is a large number of class labels (50-250) with a few examples(5-20) in
+  short  text  for  each  class, by sampling smaller subsets from the full scale
+  when the raw datasets are oversized, see Table \ref{tbe:dataset statistic}.
 
-According to the task and domain, we categorize our experimental datasets into the following 3 categories:
+  According to the task and domain, we categorize our experimental datasets into
+  the following 3 categories:
 
@@
 
-\textbf{ITG} is a real-world FAQ chatbot dataset composed of question and answer pairs about online English teaching.
-It contains 3,938 sample questions for 228 class labels, where each class label corresponds to an unique answer for a bunch of similar sample questions.
+  \textbf{ITG}  is  a  real-world  FAQ  chatbot dataset composed of question and
+  answer pairs about online English teaching. It contains 3,938 sample questions
+  for  228  class labels, where each class label corresponds to an unique answer
+  for a bunch of similar sample questions.
 
-We divide the whole dataset into 3 folds randomly with approximately the same amount of data within each fold, and then choose 2 folds as the training set, the remaing 1 fold as the test set for our experiments.
-We can obtain 3 different combinations among the 3 folds, and we will use the average experimental results of these 3 combinations as the final evaluation result for this dataset.
+  We  divide the whole dataset into 3 folds randomly with approximately the same
+  amount  of data within each fold, and then choose 2 folds as the training set,
+  the  remaing  1  fold  as  the  test  set for our experiments. We can obtain 3
+  different  combinations  among  the  3  folds,  and  we  will  use the average
+  experimental  results  of  these 3 combinations as the final evaluation result
+  for this dataset.
 
@@
 
-\textbf{Amazon-670K} is a customer product review dataset for text classification task from the extreme classification repository with full data containing 670,091 class labels, 285,176 training samples and 150875 test samples\cite{bhatia2016extreme}.
-As the data set contains multiple class labels per training sample, we keep only the first class label for each data point.
-Besides, we also randomly sampled 250 class labels from all the classes that contain only 5-15 data points.
-In this way, we simulate the low-resource chatbot corpus setting with the subset of 1,942 training samples and 716 test samples for 250 class labels.
+  \textbf{Amazon-670K}   is   a   customer   product  review  dataset  for  text
+  classification  task from the extreme classification repository with full data
+  containing  670,091  class  labels,  285,176  training samples and 150875 test
+  samples\cite{bhatia2016extreme}.  As  the  data  set  contains  multiple class
+  labels  per  training sample, we keep only the first class label for each data
+  point. Besides, we also randomly sampled 250 class labels from all the classes
+  that  contain only 5-15 data points. In this way, we simulate the low-resource
+  chatbot  corpus setting with the subset of 1,942 training samples and 716 test
+  samples for 250 class labels.
 
@@
 
-From our point of view, task-specific chatbot usually starts with small amount of data at the initial stage.
-As more and more customers start to communicate with the chatbot, more data can be extracted from conversation log.
-Base on these assumptions, we do experiments on the following 3 intent detection dataset under sampling method similar to the approach in \cite{casanueva2020efficient} but in more sophisticated few-shot settings, while keeping the same test sets for each experiment to see the change of the improvement scale with decreasing data amount.
+  From our point of view, task-specific chatbot usually starts with small amount
+  of  data at the initial stage. As more and more customers start to communicate
+  with  the  chatbot,  more data can be extracted from conversation log. Base on
+  these  assumptions,  we  do  experiments  on  the following 3 intent detection
+  dataset    under    sampling    method    similar    to    the   approach   in
+  \cite{casanueva2020efficient}  but  in  more  sophisticated few-shot settings,
+  while  keeping the same test sets for each experiment to see the change of the
+  improvement scale with decreasing data amount.
 
@@
       }
-\par\end{centering}
-\caption{F-scores on five task-specific dataset for text classification in chatbot under low resource.
-For ITG, we keep the full dataset.
-For Amazon-670k, we randomly sampled 250 classes with training sample numbers within 5-15 samples per class.
-For CLINC150, BANKING77, HWU64, we set up various few-shot settings (5/10/15/20 samples per class) while keeping the test set to be fixed.
-The highest scores for each data setting are marked in bold.}
+      \par
+    \end{centering}
+    \caption{
+      F-scores  on five task-specific dataset for text classification in chatbot
+      under low resource. For ITG, we keep the full dataset. For Amazon-670k, we
+      randomly  sampled  250  classes  with  training sample numbers within 5-15
+      samples  per  class.  For  CLINC150,  BANKING77,  HWU64, we set up various
+      few-shot  settings  (5/10/15/20  samples per class) while keeping the test
+      set  to  be  fixed. The highest scores for each data setting are marked in
+      bold.
+    }
 
@@
 
-\textbf{HWU64} is a intent detection dataset designed for home robot scenario\cite{liu2019benchmarking}.
-It aims at the specific task of capturing the intent for different user requests to home robot and finding the corresponding answer.
-The raw dataset contains 25,716 data points for 64 class labels through crowdsourcing, which raises much more data than common real-world circumstances.
-Therefore, we experiment with the setups where only 5, 10, 15 and 20 training data points are available for each class label by random sampling.
+  \textbf{HWU64}   is  a  intent  detection  dataset  designed  for  home  robot
+  scenario\cite{liu2019benchmarking}.  It aims at the specific task of capturing
+  the  intent  for  different  user  requests  to  home  robot  and  finding the
+  corresponding answer. The raw dataset contains 25,716 data points for 64 class
+  labels  through  crowdsourcing,  which  raises  much  more  data  than  common
+  real-world  circumstances. Therefore, we experiment with the setups where only
+  5,  10,  15  and 20 training data points are available for each class label by
+  random sampling.
 
-\textbf{CLINC150} is a dataset designed for task-oriented systems with 23,700 queries that are short and unstructured for 150 intents, in the same style made by real users through crowdsourcing\cite{larson2019evaluation}.
-Here, we sample 5, 10 and 15 training data points for each intent class label by random sampling for our experimental setup.
+  \textbf{CLINC150}  is a dataset designed for task-oriented systems with 23,700
+  queries  that  are  short  and unstructured for 150 intents, in the same style
+  made  by real users through crowdsourcing\cite{larson2019evaluation}. Here, we
+  sample 5, 10 and 15 training data points for each intent class label by random
+  sampling for our experimental setup.
 
   \textbf{BANKING77}  is  a intent detection dataset for bank customer services.
-The raw dataset contains 13,084 data points for 77 class labels\cite{casanueva2020efficient}.
-Here, we sample 5, 10, 15, 20 training data points for each class label by random sampling for our experimental setup.
+  The    raw    dataset    contains    13,084   data   points   for   77   class
+  labels\cite{casanueva2020efficient}.  Here,  we  sample 5, 10, 15, 20 training
+  data  points  for  each  class  label  by random sampling for our experimental
+  setup.
 
@@
 
-\textbf{Group 1: single-task classification model.} This group of baseline models are based on the network structure for classification model shown in \ref{Fig.1.sub.1}.
-As for non-pretrained neural network, we choose TextCNN\cite{kim2014convolutional} as a representative baseline.
-As for the pretrained model, we choose RoBERTa, BERT and ALBERT, all of which are among the most powerful pretrained models that achieve outstanding results in many NLP tasks, in our experimental setting.
-Since we apply RoBERTa in our SFC system, we naturally adopt single-task classification model based on RoBERTa-large and RoBERTa-base as our baseline models.
-Besides, we also adopt the recently released baseline pre-trained model ALBERT-xxlarge\cite{lan2019albert} for comparison.
-Since we use different few-shot settings from \cite{casanueva2020efficient} for those intent detection datasets, we also use BERT-large tuned on our few-shot settings as an essential reference for experimental results.
+  \textbf{Group  1:  single-task  classification  model.} This group of baseline
+  models  are  based  on the network structure for classification model shown in
+  \ref{Fig.1.sub.1}.   As   for   non-pretrained   neural   network,  we  choose
+  TextCNN\cite{kim2014convolutional}  as  a  representative baseline. As for the
+  pretrained  model,  we choose RoBERTa, BERT and ALBERT, all of which are among
+  the  most  powerful pretrained models that achieve outstanding results in many
+  NLP  tasks,  in  our  experimental  setting. Since we apply RoBERTa in our SFC
+  system,   we   naturally  adopt  single-task  classification  model  based  on
+  RoBERTa-large  and RoBERTa-base as our baseline models. Besides, we also adopt
+  the       recently       released       baseline       pre-trained       model
+  ALBERT-xxlarge\cite{lan2019albert}  for  comparison.  Since  we  use different
+  few-shot   settings   from   \cite{casanueva2020efficient}  for  those  intent
+  detection  datasets,  we also use BERT-large tuned on our few-shot settings as
+  an essential reference for experimental results.
 
-\textbf{Group 2: single-task similarity model.} This group of baseline models are based on network structure for similarity model shown in \ref{Fig.1.sub.2}.
-We choose RoBERTa-large for the pretrained model part as an powerful baseline.
-But during the evaluation step, we use elastic search to do a rough filter for candidate sentence pairs to guarantee a reasonable inference time for each user query.
+  \textbf{Group  2: single-task similarity model.} This group of baseline models
+  are   based   on   network   structure   for   similarity   model   shown   in
+  \ref{Fig.1.sub.2}. We choose RoBERTa-large for the pretrained model part as an
+  powerful baseline. But during the evaluation step, we use elastic search to do
+  a  rough  filter  for  candidate  sentence  pairs  to  guarantee  a reasonable
+  inference time for each user query.
 
-\textbf{Group 3: SFC system with ablation study.} This group of baseline is based on the network structure of 2-stage SFC shown in \ref{fig:ver.1.3}.
-We conduct ablation study by introducing single task SFC system with only Task 1 or Task 2 to investigate the influence of each component within the total loss.
+  \textbf{Group  3:  SFC  system with ablation study.} This group of baseline is
+  based  on  the network structure of 2-stage SFC shown in \ref{fig:ver.1.3}. We
+  conduct  ablation study by introducing single task SFC system with only Task 1
+  or  Task  2  to  investigate  the influence of each component within the total
+  loss.
 
   \subsection{Implementation Details}
-For our SFC system, we use RoBERTa-large as the pretrained model for both classification task and sentence-pair similarity task.
-We further fine-tune our SFC system on task-specific datasets with max sequence length of 128, learning rate of 1.5e-5 for RoBERTa-large pretrained model and learning rate of 5e-4 for task-specific layer with polynomial decay and Adam optimizer.
-Also, we set the max number of the epoch to 100 and save the best model on validation set based on test result in F-score.
-We also report the F-score as the main evaluation measure for all experimental results.
+  For  our  SFC  system,  we  use RoBERTa-large as the pretrained model for both
+  classification  task  and  sentence-pair similarity task. We further fine-tune
+  our  SFC  system  on  task-specific  datasets with max sequence length of 128,
+  learning  rate  of 1.5e-5 for RoBERTa-large pretrained model and learning rate
+  of  5e-4  for  task-specific  layer  with polynomial decay and Adam optimizer.
+  Also,  we  set  the  max number of the epoch to 100 and save the best model on
+  validation  set based on test result in F-score. We also report the F-score as
+  the main evaluation measure for all experimental results.
 
-For the experiments in Table \ref{tbe:table2}, we empirically set the hyperparameter to be $K=5$ and $P=10$ for all SFC variants.
-In Table \ref{tbe:table3}, we conduct extensive experiments to see the performance of SFC system under various hyperparameter settings.
+  For  the  experiments  in  Table  \ref{tbe:table2},  we  empirically  set  the
+  hyperparameter  to  be  $K=5$  and  $P=10$  for  all  SFC  variants.  In Table
+  \ref{tbe:table3},  we  conduct extensive experiments to see the performance of
+  SFC system under various hyperparameter settings.
 
@@
       \end{tabular}
-\par\end{centering}
-\caption{We show the performance of SFC from different settings of hyperparameters for $K$, the candidate class number, and $P$, the sample number for each class.}
+      \par
+    \end{centering}
+    \caption{
+      We  show the performance of SFC from different settings of hyperparameters
+      for  $K$,  the candidate class number, and $P$, the sample number for each
+      class.
+    }
 
@@
 
-Table \ref{tbe:table2} presents the results for each experimental data and model set-up in detail.
-The performance of each model is measured in F-score on the fixed test set for each data set.
-The overall performance of SFC system is better than all the competitive single-model baseline models on five experimental datasets.
-This observation gives us a general idea that classification model and similarity model can actually provide each other with complementary information, and combining them together into a joint system can effectively enhance the overall capability based on richer extracted semantic information.
-However the relative performance among all the variants of SFC also seems to depend on some specific charateristic of each data set.
-Therefore, we did the following more detailed analysis from several different aspect.
+  Table  \ref{tbe:table2}  presents  the  results for each experimental data and
+  model  set-up  in detail. The performance of each model is measured in F-score
+  on the fixed test set for each data set. The overall performance of SFC system
+  is  better  than  all  the  competitive  single-model  baseline models on five
+  experimental   datasets.  This  observation  gives  us  a  general  idea  that
+  classification model and similarity model can actually provide each other with
+  complementary information, and combining them together into a joint system can
+  effectively  enhance the overall capability based on richer extracted semantic
+  information.  However  the  relative performance among all the variants of SFC
+  also  seems  to  depend  on  some  specific  charateristic  of  each data set.
+  Therefore,  we did the following more detailed analysis from several different
+  aspect.
 
-\textbf{Comparison among SFC variants.} First, we turn to compare among the four SFC variants shown in Table \ref{tbe:table2} to analyze the improvement brought by multi-task and hierarchical joint-model structure.
-We conduct ablation experiments to study the benefits brought by multi-task training by comparing multi-task 2-stage SFC with single-task 2-stage SFC.
-We can see from Table \ref{tbe:table2} that 2-stage SFC with only task 1 (sentence-pair similarity task) degrades by 0.65 percent on average and 2-stage SFC with only task 2 (top-K classification task) degrades by 0.3 percent on average.
-The degradation indicates that training with these 2 tasks together in SFC can effectively help the sentence-pair model extract more knowledge from the limited amount of data.
-Besides, task 2 degrades 0.35 percent less than task 1.
-This observation suggests that task 2 may play a relatively more important role in multi-task learning, which leads us to put larger weight $\alpha_{K}$ to the loss $\mathcal{L}^{K}$ of task 2 when calculating the total loss $\mathcal{L}$.
-Also, we can see that the hierachical SFC steadily outperforms 2-stage SFC on 5 diverse datasets by 1.17 percents on average.
-This observation supports the idea that the hierachical joint model structure can alleviate the limitation brought by the lack of interaction between similarity model and classification model in 2-stage SFC.
-Therefore, for the following analysis, we will focus on the comparison between hierachical SFC and the other baseline models.
+  \textbf{Comparison  among  SFC  variants.} First, we turn to compare among the
+  four  SFC  variants shown in Table \ref{tbe:table2} to analyze the improvement
+  brought  by  multi-task  and  hierarchical  joint-model  structure. We conduct
+  ablation  experiments  to study the benefits brought by multi-task training by
+  comparing multi-task 2-stage SFC with single-task 2-stage SFC. We can see from
+  Table  \ref{tbe:table2}  that  2-stage  SFC  with  only  task 1 (sentence-pair
+  similarity task) degrades by 0.65 percent on average and 2-stage SFC with only
+  task  2  (top-K  classification  task) degrades by 0.3 percent on average. The
+  degradation  indicates  that  training  with these 2 tasks together in SFC can
+  effectively  help  the  sentence-pair  model  extract  more knowledge from the
+  limited  amount  of data. Besides, task 2 degrades 0.35 percent less than task
+  1.  This observation suggests that task 2 may play a relatively more important
+  role  in multi-task learning, which leads us to put larger weight $\alpha_{K}$
+  to  the  loss  $\mathcal{L}^{K}$  of  task  2  when calculating the total loss
+  $\mathcal{L}$.  Also, we can see that the hierachical SFC steadily outperforms
+  2-stage  SFC  on  5  diverse  datasets  by  1.17  percents  on  average.  This
+  observation  supports  the idea that the hierachical joint model structure can
+  alleviate the limitation brought by the lack of interaction between similarity
+  model  and  classification  model in 2-stage SFC. Therefore, for the following
+  analysis,  we  will  focus  on  the comparison between hierachical SFC and the
+  other baseline models.
 
-\textbf{Analysis under few-shot scenarios.} Next, we analyze the overall improvement trend of SFC under various few-shot settings.
-Our main focus is to study chatbot building in common situation during real-world application where only a few sample sentences are available for each class.
-The experimental results for the 3 diverse intent detection datasets (ClINC150, BANKING77, HWU64) under few-shot settings indicate that our proposed
-hierarchical SFC can achieve 2.47 percents average improvement over one of the most powerful baseline models, which is RoBERTa-large classification model, on all these few-shot settings.
-Moreover, the improvement in F-score becomes more and more prominent with the decrease of data sample number per class.
-Our hierarchical SFC can achieve 4.97 percents average improvements over RoBERTa-large classification model in the most extreme few-shot setting with only 5 training samples per class.
-This observation indicates that SFC is especially suitable for being applied during the initial stage of building task-specific chatbot system, where the amount of data sample for each class label is extremely scarce.
+  \textbf{Analysis  under  few-shot  scenarios.}  Next,  we  analyze the overall
+  improvement trend of SFC under various few-shot settings. Our main focus is to
+  study chatbot building in common situation during real-world application where
+  only  a  few  sample  sentences are available for each class. The experimental
+  results  for  the  3  diverse  intent detection datasets (ClINC150, BANKING77,
+  HWU64) under few-shot settings indicate that our proposed hierarchical SFC can
+  achieve  2.47  percents  average  improvement  over  one  of the most powerful
+  baseline  models,  which  is  RoBERTa-large classification model, on all these
+  few-shot  settings. Moreover, the improvement in F-score becomes more and more
+  prominent  with the decrease of data sample number per class. Our hierarchical
+  SFC   can  achieve  4.97  percents  average  improvements  over  RoBERTa-large
+  classification model in the most extreme few-shot setting with only 5 training
+  samples  per class. This observation indicates that SFC is especially suitable
+  for  being  applied during the initial stage of building task-specific chatbot
+  system,  where  the  amount  of  data sample for each class label is extremely
+  scarce.
 
-\textbf{Comparison between label embedding and sentence pair embedding.} Afterwards, we start to compare the performance of SFC with the text-label joint embedding baseline named as LEAM.
-As shown in Table \ref{tbe:table2}, hierarchical SFC outperforms LEAM by 14.25 percents on average F-score over 5 datasets.
-Besides, although the labels within the 3 diverse intent detection datasets (CLINC150, BANKING77, HWU64) are all being well-defined as the semantic summary of each intent, hierarchical SFC still outperforms LEAM by 14.69 percents on average F-score.
-This observation indicates that it's usually quite hard to use a fixed label with only a few words as the representative of all the sentences within a class since there are always plenty of ways for people to express questions or queries about the same topic during a conversation with chatbot.
-Therefore, learning the semantic similarity between user query and sample sentences through sentence pair embedding can be more reliable than making decision according to the semantic relationship between user query and class labels through label embedding.
+  \textbf{Comparison  between  label  embedding  and  sentence  pair embedding.}
+  Afterwards,  we  start  to  compare the performance of SFC with the text-label
+  joint  embedding  baseline  named as LEAM. As shown in Table \ref{tbe:table2},
+  hierarchical  SFC outperforms LEAM by 14.25 percents on average F-score over 5
+  datasets.  Besides,  although the labels within the 3 diverse intent detection
+  datasets  (CLINC150,  BANKING77,  HWU64)  are  all  being  well-defined as the
+  semantic  summary  of  each intent, hierarchical SFC still outperforms LEAM by
+  14.69  percents  on  average  F-score.  This  observation  indicates that it's
+  usually  quite  hard  to  use  a  fixed  label  with  only  a few words as the
+  representative  of  all  the  sentences  within a class since there are always
+  plenty of ways for people to express questions or queries about the same topic
+  during   a   conversation  with  chatbot.  Therefore,  learning  the  semantic
+  similarity  between  user  query  and  sample  sentences through sentence pair
+  embedding  can be more reliable than making decision according to the semantic
+  relationship between user query and class labels through label embedding.
 
-\textbf{Fusion of classification and similarity model.} Then, we begin to compare the general performance of SFC with single-task classification and similarity baselines.
-As for the classification model, hierarchical SFC outperforms TextCNN by 26.19 percents, ALBERT-xxlarge by 17.87 percents\footnote{We found that the performance of ALBERT.xxlarge is extremely unstable for classification task.
-Here, we did multiple run with different settings of parameters such as learning rate and batch size for each dataset, and record the best result we can obtain in Table \ref{tbe:table2}.}, BERT-large by 9.81 percents, RoBERTa-base by 4.52 percents, RoBERTa-large by 2.47 percents on average F-score over 5 datasets.
-In this way, we can see that RoBERTa is the best baseline pre-trained model for the low-resource text classification task we are studying.
-As for the similarity model, we only choose the strongest pretrained model RoBERTa-large as our baseline, and hierarchical SFC achieves the improvement of 7.81 percents on average.
-Moreover, hierarchical SFC's result on 2 datasets without data sampling for few-shot settings, which are ITG and Amazon-670k, are also 1.24 and 2.89 percents higher than Roberta-large classification model, and are 6.96 and 10.77 percents higher than Roberta-large similarity model.
-These improvements illustrate that putting classification model and similarity model at different network layers to cooperate with each other is a successful design of hierarchical network structure for joint model, which enables these two models assist each other for better overall results.
+  \textbf{Fusion  of  classification  and  similarity  model.} Then, we begin to
+  compare  the  general  performance  of SFC with single-task classification and
+  similarity  baselines.  As  for  the  classification  model,  hierarchical SFC
+  outperforms    TextCNN    by   26.19   percents,   ALBERT-xxlarge   by   17.87
+  percents\footnote{We found that the performance of ALBERT.xxlarge is extremely
+  unstable  for  classification  task.  Here, we did multiple run with different
+  settings  of parameters such as learning rate and batch size for each dataset,
+  and  record  the  best  result  we  can  obtain  in  Table \ref{tbe:table2}.},
+  BERT-large  by  9.81 percents, RoBERTa-base by 4.52 percents, RoBERTa-large by
+  2.47 percents on average F-score over 5 datasets. In this way, we can see that
+  RoBERTa  is  the  best  baseline  pre-trained  model for the low-resource text
+  classification  task  we  are  studying.  As for the similarity model, we only
+  choose  the  strongest  pretrained  model  RoBERTa-large  as our baseline, and
+  hierarchical  SFC  achieves  the  improvement  of  7.81  percents  on average.
+  Moreover,  hierarchical  SFC's  result on 2 datasets without data sampling for
+  few-shot  settings,  which  are  ITG  and  Amazon-670k, are also 1.24 and 2.89
+  percents  higher  than  Roberta-large  classification  model, and are 6.96 and
+  10.77  percents higher than Roberta-large similarity model. These improvements
+  illustrate that putting classification model and similarity model at different
+  network  layers  to  cooperate  with  each  other  is  a  successful design of
+  hierarchical network structure for joint model, which enables these two models
+  assist each other for better overall results.
 
-\textbf{Settings of hyperparameters.} Finally, we analyze the effect brought by different settings of hyperparameters, see Table \ref{tbe:table3}.
-We conduct experiments on 5 different settings of hyperparameters, which are the number of candidate class number $K$ and the number of sentence pairs $P$ for each class, on ITG and Amazon-670K datasets to find the most suitable setting of these 2 hyperparameters.
-We control the total number of sentence pairs sampled for each user query into about the same level of amount(50-60).
-Through analyzing the experimenal results shown in Table \ref{tbe:table3}, we find that the best setting of hyperparameters might be slightly different for datasets of different data size.
-The class label number of ITG and Amazon-670k are similar in our experimental setting, which is around 250.
-However the total amount of data points of ITG is approximately 2 times larger than Amazon-670k.
-Therefore, the setting of $K=5$ and $P=10$ is good enough for ITG since most of the classes contains over 10 data points.
-However, for Amazon-670k, the amount of data sample for each class is scarce, thus, we may need more candidate classes to sample enough effective sentence pairs for sentence-pair model layer of SFC.
-In this way, the setting of $K=10$ and $P=5$ becomes a good choice.
+  \textbf{Settings  of  hyperparameters.} Finally, we analyze the effect brought
+  by  different  settings  of  hyperparameters,  see  Table \ref{tbe:table3}. We
+  conduct  experiments on 5 different settings of hyperparameters, which are the
+  number  of candidate class number $K$ and the number of sentence pairs $P$ for
+  each  class, on ITG and Amazon-670K datasets to find the most suitable setting
+  of  these  2  hyperparameters.  We  control the total number of sentence pairs
+  sampled  for  each  user  query  into  about  the same level of amount(50-60).
+  Through  analyzing the experimenal results shown in Table \ref{tbe:table3}, we
+  find  that the best setting of hyperparameters might be slightly different for
+  datasets of different data size. The class label number of ITG and Amazon-670k
+  are  similar  in  our  experimental  setting, which is around 250. However the
+  total  amount  of  data  points  of  ITG  is approximately 2 times larger than
+  Amazon-670k. Therefore, the setting of $K=5$ and $P=10$ is good enough for ITG
+  since  most  of  the  classes  contains  over  10  data  points.  However, for
+  Amazon-670k,  the amount of data sample for each class is scarce, thus, we may
+  need  more  candidate  classes  to  sample enough effective sentence pairs for
+  sentence-pair model layer of SFC. In this way, the setting of $K=10$ and $P=5$
+  becomes a good choice.
 
-In conclusion, to the best of our knowledge, these results place SFC as the best performing model on 5 diverse experimental datasets for text classification task under low-resource task-specific conversational chatbot scenario.
+  In  conclusion,  to  the best of our knowledge, these results place SFC as the
+  best   performing   model   on   5  diverse  experimental  datasets  for  text
+  classification  task  under  low-resource task-specific conversational chatbot
+  scenario.
 
   \section{Conclusion}
-In this work, we successfully proposed SFC, a joint system of classification model and sentence-pair similarity model with multi-task learning, which can effectively alleviate the limitation of classification model and similarity model for low-resource text classification tasks.
-Experimental results illustrate that our proposed system can achieve great improvement on 5 diverse datasets for task-specific chatbot system over several competitive single-task baseline models.
-Furthermore, we especially analyze the excellent performance of SFC when facing the challenge brought by few-shot scenarios, which is quite common in real-world application of chatbot system.
+  In  this  work, we successfully proposed SFC, a joint system of classification
+  model  and  sentence-pair similarity model with multi-task learning, which can
+  effectively  alleviate  the  limitation of classification model and similarity
+  model   for  low-resource  text  classification  tasks.  Experimental  results
+  illustrate that our proposed system can achieve great improvement on 5 diverse
+  datasets for task-specific chatbot system over several competitive single-task
+  baseline  models. Furthermore, we especially analyze the excellent performance
+  of SFC when facing the challenge brought by few-shot scenarios, which is quite
+  common in real-world application of chatbot system.
 
-% latest version end
-
-%\section{Attention based neural network}
-
-%\section{Conclusion}
-
-\bibliographystyle{IEEEbib}
+  \bibliographystyle{aaai21}
   \bibliography{refs}

### 2020-08-26 chatbot_classification/aaai_2021/paper.tex
modified:   chatbot_classification/aaai_2021/paper.pdf   modified:   chatbot_classification/aaai_2021/paper.tex

@@
 
-One of the most popular approach among existing work was text classification model based on neural network.
-Since the length of the text is quite short, many previous work\cite{wen2016network} choose neural network such as convolutional neural networks (CNNs)\cite{kim2014convolutional,zhang2015character,conneau2016very}
-or long short term memory networks
-(LSTMs)\cite{mousa2017contextual,liu2016recurrent} to accomplish the task of extracting semantic feature from limited amount of words.
-A common model structure is adding a softmax classifier to the top of the neural network.
-Another common approach is text classification neural network based on label-word joint embedding, such as LEAM\cite{wang2018joint}.
-This approach involves label embedding when constructing the text-sequence representation, which poses requirements on label information.
-In our cases, since we have large amount of class labels without being well-defined, this approach can do only a few help to the low-resource chatbot scenario.
-Afterwards, pre-trained language models on large corpus like BERT\cite{devlin2018bert} and
-RoBERTa\cite{liu2019roberta} has  been proven more powerful in solving many NLP
-tasks      including      short-text      classification\cite{madabushi2020cost}.
-Especially   for  few-shot  scenarios\cite{yu2018diverse}, pre-trained  model  based on transformers\cite{vaswani2017attention}, shown in Fig.
-\ref{Fig.1.sub.1}, tends  to  do more help to reducing the negative effects brought by scarcity of training data.
+  One  of  the most popular approach among existing work was text classification
+  model  based  on  neural network. Since the length of the text is quite short,
+  many   previous   work\cite{wen2016network}  choose  neural  network  such  as
+  convolutional                          neural                         networks
+  (CNNs)\cite{kim2014convolutional,zhang2015character,conneau2016very}  or  long
+  short  term memory networks (LSTMs)\cite{mousa2017contextual,liu2016recurrent}
+  to  accomplish  the task of extracting semantic feature from limited amount of
+  words.  A  common model structure is adding a softmax classifier to the top of
+  the  neural  network.  Afterwards, pre-trained language models on large corpus
+  like   BERT\cite{devlin2018bert}  and  RoBERTa\cite{liu2019roberta}  has  been
+  proven   more   powerful  in  solving  many  NLP  tasks  including  short-text
+  classification\cite{madabushi2020cost}.      Especially      for      few-shot
+  scenarios\cite{yu2018diverse},       pre-trained      model      based      on
+  transformers\cite{vaswani2017attention},   shown  in  Fig.  \ref{Fig.1.sub.1},
+  tends  to do more help to reducing the negative effects brought by scarcity of
+  training data.
 
-Another popular approach among previous work was based on sentence-pair model.
-The motivation of this approach was started from the idea of Information Retrival (IR) based chatbot\cite{jafarpour2010filter, leuski2011npceditor}.
-Having a Q-A (Question-Answer) pairs dataset and user query Q, the IR based conversational system will look up in the Q-A dataset for the pair (Q', A') that best matches query Q through semantic analysis and returns A' as the answer to Q\cite{mnasri2019recent}.
-In this way, sentence-pair model pre-trained on large corpus of semantic similarity identification task can be applied for being used as a tool to identify the class with highest semantic similarity to customer's query.
-A common model structure of pre-trained\cite{devlin2018bert} sentence-pair model is based on multiple cross-attention mechanism\cite{barkan2020scalable}, shown in Fig.
-\ref{Fig.1.sub.2}.
-Due to the fact that many experiment results have shown that RoBERTa\cite{liu2019roberta} is an improved  version  of  BERT, and has achieved amazing results on both text classification and sentence-pairs semantic similarity tasks, we choose RoBERTa as an important baseline approach in this paper.
+  Another  common  approach  is  text  classification  neural  network  based on
+  label-word     joint     embedding,    such    as    LEAM\cite{wang2018joint},
+  MTLE\cite{zhang2017multi}   and   EXAM\cite{du2019explicit}.   This   approach
+  involves  label  embedding when constructing the text-sequence representation.
+  Take  LEAM  as  an  example,  the  text classification model is implemented by
+  jointly    embedding    the    word    and    label   in   the   same   latent
+  space\cite{wang2018joint}. Afterwards, the text representation are constructed
+  based  on  text-label  compatibility through attention mechanism. In this way,
+  additional  sources  of  semantic  information  from class labels can be fully
+  leveraged, which is quite helpful especially under few-shot scenario.
 
-Despite the success of these 2 approaches, they still have some limitations in task-specific chatbot scenario.
-As for the text classification model approach, it's quite hard to use data augmentation method to solve the data insufficiency challenge since the it's usually unfeasible to get large amount of domain-specific data when facing a new task.
-With respect to the sentence-pair model approach, though we can obtain large amount of data in semantically duplicate sentence pair identification domain for transfer learning\cite{sun2019fine}, it's still quite hard to perform well on task-specific dataset because the training objective of sentence-pair model is semantic similarity, which is slightly different from the target of classification task.
-That is to say, there always exists some intent classes which cannot be distinguished by each other merely depending on semantic similarity.
-For example, we have 2 user query saying, A: What should I do if I want to change my password?
-B: What is the modification rule if I want to change my password?
-In this case, sentence A is semantically similar to B, since they both express the
-desire for changing password.
-However, it's still reasonable to classify them into 2 intent classes, since A is asking for the method for changing password, while B is asking for the rule to follow when creating a new password.
+  The  third  popular  approach  among  previous work was based on sentence-pair
+  model.  The  motivation  of  this  approach  was  started  from  the  idea  of
+  Information     Retrival    (IR)    based    chatbot\cite{jafarpour2010filter,
+  leuski2011npceditor}.  Having  a  Q-A (Question-Answer) pairs dataset and user
+  query  Q,  the  IR based conversational system will look up in the Q-A dataset
+  for  the pair (Q', A') that best matches query Q through semantic analysis and
+  returns   A'   as   the  answer  to  Q\cite{mnasri2019recent}.  In  this  way,
+  sentence-pair  model  pre-trained  on  large  corpus  of  semantic  similarity
+  identification  task  can  be applied for being used as a tool to identify the
+  class  with  highest  semantic  similarity to customer's query. A common model
+  structure  of pre-trained\cite{devlin2018bert} sentence-pair model is based on
+  multiple  cross-attention  mechanism\cite{barkan2020scalable},  shown  in Fig.
+  \ref{Fig.1.sub.2}.  Due  to  the  fact that many experiment results have shown
+  that  RoBERTa\cite{liu2019roberta}  is  an  improved  version of BERT, and has
+  achieved  amazing  results  on  both  text  classification  and sentence-pairs
+  semantic similarity tasks, we choose RoBERTa as an important baseline approach
+  in this paper.
+
+  Despite the success of these 3 approaches, they still have some limitations in
+  task-specific chatbot scenario. As for the text classification model approach,
+  it's   quite   hard  to  use  data  augmentation  method  to  solve  the  data
+  insufficiency  challenge since the it's usually unfeasible to get large amount
+  of  domain-specific  data  when  facing  a  new  task. As for label-word joint
+  embedding  approach,  it  poses  noticeable requirements on label information.
+  However,  in  our  cases,  since  we have large amount of class labels without
+  being well-defined for question answering chatbot, the only thing we can do is
+  to  choose  one  of the user utterance as the class label to represent the key
+  information  of  the  whole class. In this way, the label will become not only
+  prolix  but  also  biased,  which  will  bring  some  negative effect to label
+  embedding.  With  respect  to  the sentence-pair model approach, though we can
+  obtain   large   amount  of  data  in  semantically  duplicate  sentence  pair
+  identification  domain  for  transfer  learning\cite{sun2019fine},  it's still
+  quite  hard  to  perform  well  on  task-specific dataset because the training
+  objective  of  sentence-pair  model  is semantic similarity, which is slightly
+  different from the target of classification task. That is to say, there always
+  exists  some intent classes which cannot be distinguished by each other merely
+  depending on semantic similarity. For example, we have 2 user query saying, A:
+  What  should I do if I want to change my password? B: What is the modification
+  rule if I want to change my password? In this case, sentence A is semantically
+  similar  to  B,  since  they  both  express  the desire for changing password.
+  However, it's still reasonable to classify them into 2 intent classes, since A
+  is asking for the method for changing password, while B is asking for the rule
+  to follow when creating a new password.
 
@@
       \includegraphics[scale=0.48]{picture/picture3}
-\par\end{centering}
-\caption{\textbf{Network Structure of 2-stage SFC:} a joint system of multi-task for both text classification task and sentence-pair semantic similarity task.}
+      \par
+    \end{centering}
+    \caption{
+      \textbf{Network  Structure  of  2-stage SFC:} a joint system of multi-task
+      for  both  text  classification task and sentence-pair semantic similarity
+      task.
+    }
     \label{fig:ver.1.3}
@@
           \hline
-LEAM & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{$0.4545$} & \multirow{2}*{$0.5554$} & \multirow{2}*{$0.5936$} & \multirow{2}*{$0.6599$} & \multirow{2}*{$0.7086$} & \multirow{2}*{$0.6091$}\tabularnewline
+          LEAM & \multirow{2}*{$0.7514$} & \multirow{2}*{$0.8203$} & \multirow{2}*{$0.8612$} & \multirow{2}*{$0.5422$} & \multirow{2}*{$0.7812$} & \multirow{2}*{$0.8129$} & \multirow{2}*{$0.8280$} & \multirow{2}*{$0.4545$} & \multirow{2}*{$0.5554$} & \multirow{2}*{$0.5936$} & \multirow{2}*{$0.6599$} & \multirow{2}*{$0.7086$} & \multirow{2}*{$0.6091$}\tabularnewline
           (classification) & & & & & & & & & & & & &\tabularnewline
@@
         \cline{2-7}
-\multicolumn{1}{|c|}{} & Hierarchical SFC & $0.7334$ & $0.7445$ & $0.7516$ & - & -\tabularnewline
+        \multicolumn{1}{|c|}{} & Hierarchical SFC & $0.7334$ & $0.7445$ & $0.7516$ & $0.7344$ & $0.7373$\tabularnewline
         \hline
       \end{tabular}
-\par\end{centering}
-\caption{We show the performance of SFC from different settings of hyperparameters for $K$, the candidate class number, and $P$, the sample number for each class.}
+      \par
+    \end{centering}
+    \caption{
+      We  show the performance of SFC from different settings of hyperparameters
+      for  $K$,  the candidate class number, and $P$, the sample number for each
+      class.
+    }
 
@@
 
-Table \ref{tbe:table2} presents the results for each experimental data and model set-up in detail.
-The performance of each model is measured in F-score on the fixed test set for each data set.
-The overall performance of SFC system is better than all the competitive single-model baseline models on five experimental datasets.
-This observation gives us a general idea that classification model and similarity model can actually provide each other with complementary information, and combining them together into a joint system can effectively enhance the overall capability based on richer extracted semantic information.
-However the relative performance among all the variants of SFC also seems to depend on some specific charateristic of each data set.
-Therefore, we did the following more detailed analysis from several different aspect.
+  Table  \ref{tbe:table2}  presents  the  results for each experimental data and
+  model  set-up  in detail. The performance of each model is measured in F-score
+  on the fixed test set for each data set. The overall performance of SFC system
+  is  better  than  all  the  competitive  single-model  baseline models on five
+  experimental   datasets.  This  observation  gives  us  a  general  idea  that
+  classification model and similarity model can actually provide each other with
+  complementary information, and combining them together into a joint system can
+  effectively  enhance the overall capability based on richer extracted semantic
+  information.  However  the  relative performance among all the variants of SFC
+  also  seems  to  depend  on  some  specific  charateristic  of  each data set.
+  Therefore,  we did the following more detailed analysis from several different
+  aspect.
 
-\textbf{Comparison among SFC variants.} First, we turn to compare among the four SFC variants shown in Table \ref{tbe:table2} to analyze the improvement brought by multi-task and hierarchical joint-model structure.
-We conduct ablation experiments to study the benefits brought by multi-task training by comparing multi-task 2-stage SFC with single-task 2-stage SFC.
-We can see from Table \ref{tbe:table2} that 2-stage SFC with only task 1 (sentence-pair similarity task) degrades by 0.65 percent on average and 2-stage SFC with only task 2 (top-K classification task) degrades by 0.3 percent on average.
-The degradation indicates that training with these 2 tasks together in SFC can effectively help the sentence-pair model extract more knowledge from the limited amount of data.
-Besides, task 2 degrades 0.35 percent less than task 1.
-This observation suggests that task 2 may play a relatively more important role in multi-task learning, which leads us to put larger weight $\alpha_{K}$ to the loss $\mathcal{L}^{K}$ of task 2 when calculating the total loss $\mathcal{L}$.
-Also, we can see that the hierachical SFC steadily outperforms 2-stage SFC on 5 diverse datasets by 2 percents on average.
-This observation supports the idea that the hierachical joint model structure can alleviate the limitation brought by the lack of interaction between similarity model and classification model in 2-stage SFC.
-Therefore, for the following analysis, we will focus on the comparison between hierachical SFC and the other baseline models.
+  \textbf{Comparison  among  SFC  variants.} First, we turn to compare among the
+  four  SFC  variants shown in Table \ref{tbe:table2} to analyze the improvement
+  brought  by  multi-task  and  hierarchical  joint-model  structure. We conduct
+  ablation  experiments  to study the benefits brought by multi-task training by
+  comparing multi-task 2-stage SFC with single-task 2-stage SFC. We can see from
+  Table  \ref{tbe:table2}  that  2-stage  SFC  with  only  task 1 (sentence-pair
+  similarity task) degrades by 0.65 percent on average and 2-stage SFC with only
+  task  2  (top-K  classification  task) degrades by 0.3 percent on average. The
+  degradation  indicates  that  training  with these 2 tasks together in SFC can
+  effectively  help  the  sentence-pair  model  extract  more knowledge from the
+  limited  amount  of data. Besides, task 2 degrades 0.35 percent less than task
+  1.  This observation suggests that task 2 may play a relatively more important
+  role  in multi-task learning, which leads us to put larger weight $\alpha_{K}$
+  to  the  loss  $\mathcal{L}^{K}$  of  task  2  when calculating the total loss
+  $\mathcal{L}$.  Also, we can see that the hierachical SFC steadily outperforms
+  2-stage  SFC  on  5  diverse  datasets  by  1.17  percents  on  average.  This
+  observation  supports  the idea that the hierachical joint model structure can
+  alleviate the limitation brought by the lack of interaction between similarity
+  model  and  classification  model in 2-stage SFC. Therefore, for the following
+  analysis,  we  will  focus  on  the comparison between hierachical SFC and the
+  other baseline models.
 
-\textbf{Analysis under few-shot scenarios.} Next, we analyze the overall improvement trend of SFC under various few-shot settings.
-Our main focus is to study chatbot building in common situation during real-world application where only a few sample sentences are available for each class.
-The experimental results for the 3 diverse intent detection datasets under few-shot settings indicate that our proposed SFC can achieve +2.47 percents average improvement over one of the most powerful baseline models, which is RoBERTa-large classification model, on all these few-shot settings.
-Moreover, the improvement in F-score becomes more and more prominent with the decrease of data sample number per class.
-Our hierarchical SFC can achieve +4.97 percents average improvements over RoBERTa-large classification model in the most extreme few-shot setting with only 5 training samples per class.
-This observation indicates that SFC is especially suitable for being applied during the initial stage of building task-specific chatbot system, where the amount of data sample for each class label is extremely scarce.
+  \textbf{Analysis  under  few-shot  scenarios.}  Next,  we  analyze the overall
+  improvement trend of SFC under various few-shot settings. Our main focus is to
+  study chatbot building in common situation during real-world application where
+  only  a  few  sample  sentences are available for each class. The experimental
+  results  for  the  3  diverse  intent detection datasets (ClINC150, BANKING77,
+  HWU64) under few-shot settings indicate that our proposed hierarchical SFC can
+  achieve  2.47  percents  average  improvement  over  one  of the most powerful
+  baseline  models,  which  is  RoBERTa-large classification model, on all these
+  few-shot  settings. Moreover, the improvement in F-score becomes more and more
+  prominent  with the decrease of data sample number per class. Our hierarchical
+  SFC   can  achieve  4.97  percents  average  improvements  over  RoBERTa-large
+  classification model in the most extreme few-shot setting with only 5 training
+  samples  per class. This observation indicates that SFC is especially suitable
+  for  being  applied during the initial stage of building task-specific chatbot
+  system,  where  the  amount  of  data sample for each class label is extremely
+  scarce.
 
-\textbf{Fusion of classification and similarity model.} Then, we begin to compare the general performance of SFC with single-task classification and similarity baselines.
-As for the classification model, hierarchical SFC outperforms TextCNN by +37.99 percents, ALBERT-xxlarge by +17.87 percents\footnote{We found that the performance of ALBERT.xxlarge is extremely unstable for classification task.
-Here, we did multiple run with different settings of parameters such as learning rate and batch size for each dataset, and record the best result we can obtain in Table \ref{tbe:table2}.}, BERT-large by +9.81 percents, RoBERTa-base by +4.52 percents, RoBERTa-large by +2.47 percents on average F-score over 5 datasets.
-In this way, we can see that RoBERTa is the best baseline pre-trained model for the low-resource text classification task we are studying.
-As for the similarity model, we only choose the strongest pretrained model RoBERTa-large as our baseline, and hierarchical SFC achieves the improvement of +7.81 percents on average.
-Moreover, hierarchical SFC's result on 2 datasets without data sampling for few-shot settings, which are ITG and Amazon-670k, are also 1.24 and 2.89 percents higher than Roberta-large classification model, and are 6.96 and 10.77 percents higher than Roberta-large similarity model.
-These improvements illustrate that putting classification model and similarity model at different network layers to cooperate with each other is a successful design of hierarchical network structure for joint model, which enables these two models assist each other for better overall results.
+  \textbf{Comparison  between  label  embedding  and  sentence  pair embedding.}
+  Afterwards,  we  start  to  compare the performance of SFC with the text-label
+  joint  embedding  baseline  named as LEAM. As shown in Table \ref{tbe:table2},
+  hierarchical  SFC outperforms LEAM by 14.25 percents on average F-score over 5
+  datasets.  Besides,  although the labels within the 3 diverse intent detection
+  datasets  (CLINC150,  BANKING77,  HWU64)  are  all  being  well-defined as the
+  semantic  summary  of  each intent, hierarchical SFC still outperforms LEAM by
+  14.69  percents  on  average  F-score.  This  observation  indicates that it's
+  usually  quite  hard  to  use  a  fixed  label  with  only  a few words as the
+  representative  of  all  the  sentences  within a class since there are always
+  plenty of ways for people to express questions or queries about the same topic
+  during   a   conversation  with  chatbot.  Therefore,  learning  the  semantic
+  similarity  between  user  query  and  sample  sentences through sentence pair
+  embedding  can be more reliable than making decision according to the semantic
+  relationship between user query and class labels through label embedding.
 
-\textbf{Settings of hyperparameters.} Finally, we analyze the effect brought by different settings of hyperparameters, see Table \ref{tbe:table3}.
-We conduct experiments on 5 different settings of hyperparameters, which are the number of candidate class number $K$ and the number of sentence pairs $P$ for each class, on ITG and Amazon-670K datasets to find the most suitable setting of these 2 hyperparameters.
-We control the total number of sentence pairs sampled for each user query into about the same level of amount(50-60).
-Through analyzing the experimenal results shown in Table \ref{tbe:table3}, we find that the best setting of hyperparameters might be slightly different for datasets of different data size.
-The class label number of ITG and Amazon-670k are similar in our experimental setting, which is around 250.
-However the total amount of data points of ITG is approximately 2 times larger than Amazon-670k.
-Therefore, the setting of $K=5$ and $P=10$ is good enough for ITG since most of the classes contains over 10 data points.
-However, for Amazon-670k, the amount of data sample for each class is scarce, thus, we may need more candidate classes to sample enough effective sentence pairs for sentence-pair model layer of SFC.
-In this way, the setting of $K=10$ and $P=5$ becomes a good choice.
+  \textbf{Fusion  of  classification  and  similarity  model.} Then, we begin to
+  compare  the  general  performance  of SFC with single-task classification and
+  similarity  baselines.  As  for  the  classification  model,  hierarchical SFC
+  outperforms    TextCNN    by   26.19   percents,   ALBERT-xxlarge   by   17.87
+  percents\footnote{We found that the performance of ALBERT.xxlarge is extremely
+  unstable  for  classification  task.  Here, we did multiple run with different
+  settings  of parameters such as learning rate and batch size for each dataset,
+  and  record  the  best  result  we  can  obtain  in  Table \ref{tbe:table2}.},
+  BERT-large  by  9.81 percents, RoBERTa-base by 4.52 percents, RoBERTa-large by
+  2.47 percents on average F-score over 5 datasets. In this way, we can see that
+  RoBERTa  is  the  best  baseline  pre-trained  model for the low-resource text
+  classification  task  we  are  studying.  As for the similarity model, we only
+  choose  the  strongest  pretrained  model  RoBERTa-large  as our baseline, and
+  hierarchical  SFC  achieves  the  improvement  of  7.81  percents  on average.
+  Moreover,  hierarchical  SFC's  result on 2 datasets without data sampling for
+  few-shot  settings,  which  are  ITG  and  Amazon-670k, are also 1.24 and 2.89
+  percents  higher  than  Roberta-large  classification  model, and are 6.96 and
+  10.77  percents higher than Roberta-large similarity model. These improvements
+  illustrate that putting classification model and similarity model at different
+  network  layers  to  cooperate  with  each  other  is  a  successful design of
+  hierarchical network structure for joint model, which enables these two models
+  assist each other for better overall results.
 
-In conclusion, to the best of our knowledge, these results place SFC as the best performing model on 5 diverse experimental datasets for text classification task under low-resource task-specific conversational chatbot scenario.
+  \textbf{Settings  of  hyperparameters.} Finally, we analyze the effect brought
+  by  different  settings  of  hyperparameters,  see  Table \ref{tbe:table3}. We
+  conduct  experiments on 5 different settings of hyperparameters, which are the
+  number  of candidate class number $K$ and the number of sentence pairs $P$ for
+  each  class, on ITG and Amazon-670K datasets to find the most suitable setting
+  of  these  2  hyperparameters.  We  control the total number of sentence pairs
+  sampled  for  each  user  query  into  about  the same level of amount(50-60).
+  Through  analyzing the experimenal results shown in Table \ref{tbe:table3}, we
+  find  that the best setting of hyperparameters might be slightly different for
+  datasets of different data size. The class label number of ITG and Amazon-670k
+  are  similar  in  our  experimental  setting, which is around 250. However the
+  total  amount  of  data  points  of  ITG  is approximately 2 times larger than
+  Amazon-670k. Therefore, the setting of $K=5$ and $P=10$ is good enough for ITG
+  since  most  of  the  classes  contains  over  10  data  points.  However, for
+  Amazon-670k,  the amount of data sample for each class is scarce, thus, we may
+  need  more  candidate  classes  to  sample enough effective sentence pairs for
+  sentence-pair model layer of SFC. In this way, the setting of $K=10$ and $P=5$
+  becomes a good choice.
+
+  In  conclusion,  to  the best of our knowledge, these results place SFC as the
+  best   performing   model   on   5  diverse  experimental  datasets  for  text
+  classification  task  under  low-resource task-specific conversational chatbot
+  scenario.
 
   \section{Conclusion}
-In this work, we successfully proposed SFC, a joint system of classification model and sentence-pair similarity model with multi-task learning, which can effectively alleviate the limitation of classification model and similarity model for low-resource text classification tasks.
-Experimental results illustrate that our proposed system can achieve great improvement on 5 diverse datasets for task-specific chatbot system over several competitive single-task baseline models.
-Furthermore, we especially analyze the excellent performance of SFC when facing the challenge brought by few-shot scenarios, which is quite common in real-world application of chatbot system.
+  In  this  work, we successfully proposed SFC, a joint system of classification
+  model  and  sentence-pair similarity model with multi-task learning, which can
+  effectively  alleviate  the  limitation of classification model and similarity
+  model   for  low-resource  text  classification  tasks.  Experimental  results
+  illustrate that our proposed system can achieve great improvement on 5 diverse
+  datasets for task-specific chatbot system over several competitive single-task
+  baseline  models. Furthermore, we especially analyze the excellent performance
+  of SFC when facing the challenge brought by few-shot scenarios, which is quite
+  common in real-world application of chatbot system.
 
-% latest version end
-
-%\section{Attention based neural network}
-
-%\section{Conclusion}
-
-\bibliographystyle{IEEEbib}
+  \bibliographystyle{aaai21}
   \bibliography{refs}

### 2020-08-26 chatbot_classification/aaai_2021/paper.tex
modified:   paper.pdf   modified:   paper.tex

@@
   \begin{abstract}
-    Building  conversational  chatbot  system  has  become a popular solution to
-    customer services under various business scenarios. A conversational chatbot
-    needs to detect user's intent given a few words, which essentially equals to
-    short-text   classification   problem  in  the  field  of  Natural  Language
-    Processing. Moreover, each time for a new service, the task-specific chatbot
-    system  often  needs  to  perform  well  in  few-shot  setups due to lack of
-    domain-specific  data,  which  is  quite a challenge for single-model system
-    such   as   text  classification  model  system  or  sentence-pair  semantic
-    similarity  model  system under such a low-resource condition. Therefore, in
-    this  paper, we propose SFC, a 2-stage joint system with multi-task training
-    technique  for  both  text  classification  task  and sentence-pair semantic
-    similarity  task  to  overcome  this challenge. Furthermore, we additionally
-    propose  an  improved  version of SFC to allow text classification model and
-    sentence-pair model be combined into a joint model organized in hierarchical
-    structure.  We  also conduct extensive experiments on 4 public and 1 private
-    datasets  in  few-shot  setup  (i.e.,  with  only  5 to 20 training data per
-    class).   The  experimental  results  show  that  our  system  can  steadily
-    outperform  several  competitive  single-model  baselines  by  2  percent in
-    average accuracy.
+    Task-specific  chatbot  systems has gained many important applications, such
+    as  Siri, Google home, customer service systems to allievaite human's labor.
+    In  this  kind  of  systems, one of the core problems is the accurate detection of
+    intention  of  a  user's input. It is then mapped into a predefined chatting
+    logic  graph,  and the chatbot can return reasonable answers easily. This is
+    the  main  difference from a free chatbot. The intention detection, assuming
+    only  one  intention  in  a  sentence,  can  be  modeled  as  a  short  text
+    classification  problem.  In  practice,  the  number  of  intentions  can be
+    hundreads of thousands, as opposed to quite limited in the tradiational text
+    classification  problem,  and  the  labeled  data  is not trivial to acquire
+    plenty,  generally  10  to 20 per intention. Then, how to train an efficient
+    model  in such a resource-intensive practical application in a new domain is
+    critical.  In  this  work, we propose a novel model, called similairty model
+    fused with classification Model (SFC), which combines a classification model
+    and  a  similairty  model,  and  borrows the power of multi-task training as
+    well.  We  conduct extensive experiments on 4 public and 1 private datasets.
+    The  experimental  results  show  that our new model outperforms very strong
+    baselines, BERT, RoBERTa and ALBERT based pretrained models by 2 percentages
+    in average accuracy.
+
   \end{abstract}
@@
   \label{sec:intro}
-  Task-specific  conversational  chatbot\cite{wen2016network}  are  designed  to
+
+  todo: joint training of intention and NER.
+
+  Task-specific  conversational  chatbot  \cite{wen2016network}  are  designed  to
   share   the  working  pressure  of  human  customer  service  agents  who  are
@@
   conversation  is  usually  quite  short  and  completed  in a few words. Short
-  text\cite{song2014short}  are generally more ambiguous in comparison with long
+  text \cite{song2014short}  are generally more ambiguous in comparison with long
   texts  such  as  paragraphs  or  documents  since  they  don't  contain enough
-  contextual  information,  which poses a great challenge\cite{chen2019deep} for
-  classification        task\cite{phan2008learning,yan2009dynamic,hua2015short}.
+  contextual  information,  which poses a great challenge \cite{chen2019deep} for
+  classification        task \cite{phan2008learning,yan2009dynamic,hua2015short}.
   Second,  at  the  initial  stage  of  building  a chatbot for specific task or
@@
   performance     becomes     solving     the     challenge     of    short-text
-  classification\cite{sriram2010short}        problem       under       few-shot
-  setting\cite{yu2018diverse}.
+  classification \cite{sriram2010short}        problem       under       few-shot
+  setting \cite{yu2018diverse}.
 
@@
   model  based  on  neural network. Since the length of the text is quite short,
-  many   previous   work\cite{wen2016network}  choose  neural  network  such  as
+  many   previous   work \cite{wen2016network}  choose  neural  network  such  as
   convolutional                          neural                         networks
-  (CNNs)\cite{kim2014convolutional,zhang2015character,conneau2016very}  or  long
-  short  term memory networks (LSTMs)\cite{mousa2017contextual,liu2016recurrent}
+  (CNNs) \cite{kim2014convolutional,zhang2015character,conneau2016very}  or  long
+  short  term memory networks (LSTMs) \cite{mousa2017contextual,liu2016recurrent}
   to  accomplish  the task of extracting semantic feature from limited amount of
@@
   the  neural  network.  Afterwards, pre-trained language models on large corpus
-  like   BERT\cite{devlin2018bert}  and  RoBERTa\cite{liu2019roberta}  has  been
+  like   BERT \cite{devlin2018bert}  and  RoBERTa \cite{liu2019roberta}  has  been
   proven   more   powerful  in  solving  many  NLP  tasks  including  short-text
-  classification\cite{madabushi2020cost}.      Especially      for      few-shot
-  scenarios\cite{yu2018diverse},       pre-trained      model      based      on
-  transformers\cite{vaswani2017attention},   shown  in  Fig.  \ref{Fig.1.sub.1},
+  classification \cite{madabushi2020cost}.      Especially      for      few-shot
+  scenarios \cite{yu2018diverse},       pre-trained      model      based      on
+  transformers \cite{vaswani2017attention},   shown  in  Fig.  \ref{Fig.1.sub.1},
   tends  to do more help to reducing the negative effects brought by scarcity of
@@
   Another  common  approach  is  text  classification  neural  network  based on
-  label-word     joint     embedding,    such    as    LEAM\cite{wang2018joint},
-  MTLE\cite{zhang2017multi}   and   EXAM\cite{du2019explicit}.   This   approach
+  label-word     joint     embedding,    such    as    LEAM \cite{wang2018joint},
+  MTLE \cite{zhang2017multi}   and   EXAM \cite{du2019explicit}.   This   approach
   involves  label  embedding when constructing the text-sequence representation.
@@
   jointly    embedding    the    word    and    label   in   the   same   latent
-  space\cite{wang2018joint}. Afterwards, the text representation are constructed
+  space \cite{wang2018joint}. Afterwards, the text representation are constructed
   based  on  text-label  compatibility through attention mechanism. In this way,
@@
   model.  The  motivation  of  this  approach  was  started  from  the  idea  of
-  Information     Retrival    (IR)    based    chatbot\cite{jafarpour2010filter,
+  Information     Retrival    (IR)    based    chatbot \cite{jafarpour2010filter,
   leuski2011npceditor}.  Having  a  Q-A (Question-Answer) pairs dataset and user
@@
   for  the pair (Q', A') that best matches query Q through semantic analysis and
-  returns   A'   as   the  answer  to  Q\cite{mnasri2019recent}.  In  this  way,
+  returns   A'   as   the  answer  to  Q \cite{mnasri2019recent}.  In  this  way,
   sentence-pair  model  pre-trained  on  large  corpus  of  semantic  similarity
@@
   class  with  highest  semantic  similarity to customer's query. A common model
-  structure  of pre-trained\cite{devlin2018bert} sentence-pair model is based on
-  multiple  cross-attention  mechanism\cite{barkan2020scalable},  shown  in Fig.
+  structure  of pre-trained \cite{devlin2018bert} sentence-pair model is based on
+  multiple  cross-attention  mechanism \cite{barkan2020scalable},  shown  in Fig.
   \ref{Fig.1.sub.2}.  Due  to  the  fact that many experiment results have shown
-  that  RoBERTa\cite{liu2019roberta}  is  an  improved  version of BERT, and has
+  that  RoBERTa \cite{liu2019roberta}  is  an  improved  version of BERT, and has
   achieved  amazing  results  on  both  text  classification  and sentence-pairs
@@
   obtain   large   amount  of  data  in  semantically  duplicate  sentence  pair
-  identification  domain  for  transfer  learning\cite{sun2019fine},  it's still
+  identification  domain  for  transfer  learning \cite{sun2019fine},  it's still
   quite  hard  to  perform  well  on  task-specific dataset because the training
@@
   of            sentence-pair           model           for           multi-task
-  learning\cite{caruana1993multitask,collobert2008unified}.  To  obtain  such  a
+  learning \cite{caruana1993multitask,collobert2008unified}.  To  obtain  such  a
   joint  system,  we  first start with preparation work, which is pre-training a
@@
   sample out top-K most related intent classes. This auxiliary model or tool can
-  either  be searching engine such as elasticsearch\cite{divya2013elasticsearch}
+  either  be searching engine such as elasticsearch \cite{divya2013elasticsearch}
   or  a  text  classification  model  trained  on  task-specific  chatbot  data.
@@
   pairs       for       training       based      on      negative      sampling
-  strategy\cite{bamler2020extreme}.  The  reason is that a task-specific chatbot
+  strategy \cite{bamler2020extreme}.  The  reason is that a task-specific chatbot
   often  has hundreds of intent classes, which forms too many sentence pairs for
@@
   sentence-pair     of     negative     sample.     Besides,     according    to
-  Bamler\cite{bamler2020extreme},   training   on  negative  samples  from  most
+  Bamler \cite{bamler2020extreme},   training   on  negative  samples  from  most
   confusing  wrong  label  can  help  model  converge  faster  and obtain better
@@
   shared-parameter  sentence-pair  model structure, which is a classic parameter
-  sharing                                   mechanism\cite{collobert2008unified,
-  subramanian2018learning,liu2019multi}   for  multi-task\cite{sun2019fine}.  In
+  sharing                                   mechanism \cite{collobert2008unified,
+  subramanian2018learning,liu2019multi}   for  multi-task \cite{sun2019fine}.  In
   this  way, specific knowledge contained in these 2 tasks can be fully explored
@@
   hierarchical  architecture  by  putting  different  tasks at different network
-  layers\cite{sogaard2016deep,   hashimoto2016joint}   and  then  training  them
+  layers \cite{sogaard2016deep,   hashimoto2016joint}   and  then  training  them
   together,  shown  in  Fig  \ref{fig:framework}.  Here, the text classification
@@
   Before we start to fine-tune our sentence-pair model on task-specific dataset,
-  we   first  fine-tune  RoBERTa  on  Quora  dataset\cite{iyer2017first},  which
+  we   first  fine-tune  RoBERTa  on  Quora  dataset \cite{iyer2017first},  which
   contains  404,290  potential  duplicate question pairs, for transfer learning.
@@
   containing  670,091  class  labels,  285,176  training samples and 150875 test
-  samples\cite{bhatia2016extreme}.  As  the  data  set  contains  multiple class
+  samples \cite{bhatia2016extreme}.  As  the  data  set  contains  multiple class
   labels  per  training sample, we keep only the first class label for each data
@@
   \textbf{HWU64}   is  a  intent  detection  dataset  designed  for  home  robot
-  scenario\cite{liu2019benchmarking}.  It aims at the specific task of capturing
+  scenario \cite{liu2019benchmarking}.  It aims at the specific task of capturing
   the  intent  for  different  user  requests  to  home  robot  and  finding the
@@
   queries  that  are  short  and unstructured for 150 intents, in the same style
-  made  by real users through crowdsourcing\cite{larson2019evaluation}. Here, we
+  made  by real users through crowdsourcing \cite{larson2019evaluation}. Here, we
   sample 5, 10 and 15 training data points for each intent class label by random
@@
   The    raw    dataset    contains    13,084   data   points   for   77   class
-  labels\cite{casanueva2020efficient}.  Here,  we  sample 5, 10, 15, 20 training
+  labels \cite{casanueva2020efficient}.  Here,  we  sample 5, 10, 15, 20 training
   data  points  for  each  class  label  by random sampling for our experimental
@@
   \ref{Fig.1.sub.1}.   As   for   non-pretrained   neural   network,  we  choose
-  TextCNN\cite{kim2014convolutional}  as  a  representative baseline. As for the
+  TextCNN \cite{kim2014convolutional}  as  a  representative baseline. As for the
   pretrained  model,  we choose RoBERTa, BERT and ALBERT, all of which are among
@@
   the       recently       released       baseline       pre-trained       model
-  ALBERT-xxlarge\cite{lan2019albert}  for  comparison.  Since  we  use different
+  ALBERT-xxlarge \cite{lan2019albert}  for  comparison.  Since  we  use different
   few-shot   settings   from    \cite{casanueva2020efficient}  for  those  intent

### 2020-08-26 chatbot_classification/aaai_2021/paper.tex
modified:   paper.pdf   modified:   paper.tex   modified:   paper.ver_03.pdf

@@
 
-  todo: joint training of intention and NER.
-
   Task-specific  conversational  chatbot  \cite{wen2016network}  are  designed  to
@@
   setting \cite{yu2018diverse}.
-
-  \begin{figure}[htbp]
-    \centering 
-    \subfigure[classification model]{
-      \label{Fig.1.sub.1}
-      \includegraphics[scale=0.7]{picture/picture1.pdf}
-    }
-    \subfigure[similarity model]{
-      \label{Fig.1.sub.2}
-      \includegraphics[scale=0.55]{picture/picture2.pdf}
-    }
-    \caption{Two popular structures of building task-specific conversational chatbot}
-    \label{Fig.1.main}
-  \end{figure}
 
@@
 
-  \begin{figure}[htbp]
-    \begin{centering}
-      \includegraphics[scale=0.48]{picture/picture3}
-      \par
-    \end{centering}
-    \caption{
-      \textbf{Network  Structure  of  2-stage SFC:} a joint system of multi-task
-      for  both  text  classification task and sentence-pair semantic similarity
-      task.
-    }
-    \label{fig:ver.1.3}
-  \end{figure}
-
   The  above  limitation  motivates  us  to  propose a joint system of both text
@@
   joint  model  of  sentence-pair  model  and  text  classification  model  in a
-  hierarchical  architecture  by  putting  different  tasks at different network
+  joint  architecture  by  putting  different  tasks at different network
   layers \cite{sogaard2016deep,   hashimoto2016joint}   and  then  training  them
@@
     \caption{
-      \textbf{Network   Structure   of  hierarchical  SFC:}  a  joint  model  of
+      \textbf{Network   Structure   of  joint  SFC:}  a  joint  model  of
       sentence-pair   model   and   text   classification   model  organized  in
-      hierarchical  structure by completing different tasks at different network
+      joint  structure by completing different tasks at different network
       layers.
@@
   classification  model,  named  as  SFC, in detail. We come up with 2 different
-  approaches  for  implementation  of SFC system, in which hierarchical SFC is a
-  further improvement of 2-stage SFC for better performance.
+  approaches  for  implementation  of SFC system, in which joint SFC is a
+  further improvement of two-stage SFC for better performance.
 
-  \subsection{2-stage SFC with multi-task learning}
+  \subsection{two-stage SFC with multi-task learning}
 
-  The   detailed   network   structure   of   2-stage   SFC  is  shown  in  Fig.
+  The   detailed   network   structure   of   two-stage   SFC  is  shown  in  Fig.
   \ref{fig:ver.1.3}.  It  is  composed  with  2  separate  stages  in  charge of
@@
   stages  in  SFC  system  connect  with  each other, let's go deeper into model
-  structure within these 2 stages respectively to see how it works.
+  structure within these two stages respectively to see how it works.
 
@@
   Therefore,  the  overall  loss  function for multi-task learning in stage 2 is
-  shown in Equ. \ref{eq: 2-stage SFC loss}. The training objective of stage 2 is
+  shown in Equ. \ref{eq: two-stage SFC loss}. The training objective of stage 2 is
   to  minimize  the  weighted  sum  of task-specific losses. Here $\alpha_S$ and
@@
     \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K
-    \label{eq: 2-stage SFC loss}
+    \label{eq: two-stage SFC loss}
   \end{align}
@@
 
-  \subsection{hierarchical SFC with joint model structure}
-  Despite  the  outstanding experimental result of 2-stage SFC on various tasks,
-  we still find a limitation brought by the 2-stage system structure. In 2-stage
+  \subsection{joint SFC with joint model structure}
+  Despite  the  outstanding experimental result of two-stage SFC on various tasks,
+  we still find a limitation brought by the two-stage system structure. In two-stage
   SFC, Stage 1 and stage 2 are separate, so they do not interact with each other
@@
   Therefore,  to  further  improve the overall performance of SFC, we proposed a
-  hierarchical  joint  model  structure,  shown  in Fig. \ref{fig:framework}. In
-  hierarchical SFC, classification model is being placed in lower layer level to
+  joint  model  structure,  shown  in Fig. \ref{fig:framework}. In
+  joint SFC, classification model is being placed in lower layer level to
   dynamically  provide  top-K  candidate  class  labels  for  the  sentence-pair
@@
 
-  There  are  3  tasks in total during the training process of hierarchical SFC,
+  There  are  3  tasks in total during the training process of joint SFC,
   shown  in  Fig. \ref{fig:framework}, and the overall loss is also the weighted
@@
           \hline
-          2-stage SFC & \multirow{2}*{$0.8979$} & \multirow{2}*{$0.9457$} & \multirow{2}*{$0.9517$} & \multirow{2}*{$0.7975$} & \multirow{2}*{$0.8818$} & \multirow{2}*{$0.8962$} & \multirow{2}*{$0.9109$} & \multirow{2}*{$0.6477$} & \multirow{2}*{$0.7055$} & \multirow{2}*{$0.7200$} & \multirow{2}*{$0.7232$} & \multirow{2}*{$0.7972$} & \multirow{2}*{$0.7189$}\tabularnewline
+          two-stage SFC & \multirow{2}*{$0.8979$} & \multirow{2}*{$0.9457$} & \multirow{2}*{$0.9517$} & \multirow{2}*{$0.7975$} & \multirow{2}*{$0.8818$} & \multirow{2}*{$0.8962$} & \multirow{2}*{$0.9109$} & \multirow{2}*{$0.6477$} & \multirow{2}*{$0.7055$} & \multirow{2}*{$0.7200$} & \multirow{2}*{$0.7232$} & \multirow{2}*{$0.7972$} & \multirow{2}*{$0.7189$}\tabularnewline
           (task1 only) & & & & & & & & & & & & &\tabularnewline
           \hline
-          2-stage SFC & \multirow{2}*{$0.9162$} & \multirow{2}*{$0.9424$} & \multirow{2}*{$0.9530$} & \multirow{2}*{$0.7997$} & \multirow{2}*{$0.8823$} & \multirow{2}*{$0.8945$} & \multirow{2}*{$0.9123$} & \multirow{2}*{$0.6498$} & \multirow{2}*{$0.6980$} & \multirow{2}*{$0.7202$} & \multirow{2}*{$0.7358$} & \multirow{2}*{$0.8020$} & \multirow{2}*{$0.7311$}\tabularnewline
+          two-stage SFC & \multirow{2}*{$0.9162$} & \multirow{2}*{$0.9424$} & \multirow{2}*{$0.9530$} & \multirow{2}*{$0.7997$} & \multirow{2}*{$0.8823$} & \multirow{2}*{$0.8945$} & \multirow{2}*{$0.9123$} & \multirow{2}*{$0.6498$} & \multirow{2}*{$0.6980$} & \multirow{2}*{$0.7202$} & \multirow{2}*{$0.7358$} & \multirow{2}*{$0.8020$} & \multirow{2}*{$0.7311$}\tabularnewline
           (task2 only) & & & & & & & & & & & & &\tabularnewline
           \hline
-          2-stage SFC & \multirow{2}*{$0.9167$} & \multirow{2}*{$0.9456$} & \multirow{2}*{$0.9571$} & \multirow{2}*{$0.7954$} & \multirow{2}*{$0.8854$} & \multirow{2}*{$0.8931$} & \multirow{2}*{$0.9192$} & \multirow{2}*{$0.6525$} & \multirow{2}*{$0.7001$} & \multirow{2}*{$0.7168$} & \multirow{2}*{$0.7476$} & \multirow{2}*{$\textbf{0.8124}$} & \multirow{2}*{$0.7364$}\tabularnewline
+          two-stage SFC & \multirow{2}*{$0.9167$} & \multirow{2}*{$0.9456$} & \multirow{2}*{$0.9571$} & \multirow{2}*{$0.7954$} & \multirow{2}*{$0.8854$} & \multirow{2}*{$0.8931$} & \multirow{2}*{$0.9192$} & \multirow{2}*{$0.6525$} & \multirow{2}*{$0.7001$} & \multirow{2}*{$0.7168$} & \multirow{2}*{$0.7476$} & \multirow{2}*{$\textbf{0.8124}$} & \multirow{2}*{$0.7364$}\tabularnewline
           (task1 + task2) & & & & & & & & & & & & &\tabularnewline
           \hline
-          \multirow{2}*{Hierarchical SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline
+          \multirow{2}*{joint SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline
           & & & & & & & & & & & & &\tabularnewline
@@
   \textbf{Group  3:  SFC  system with ablation study.} This group of baseline is
-  based  on  the network structure of 2-stage SFC shown in \ref{fig:ver.1.3}. We
+  based  on  the network structure of two-stage SFC shown in \ref{fig:ver.1.3}. We
   conduct  ablation study by introducing single task SFC system with only Task 1
@@
         \hline
-        \multicolumn{1}{|c|}{\multirow{2}*{ITG}}& 2-stage SFC & $0.8034$ & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
+        \multicolumn{1}{|c|}{\multirow{2}*{ITG}}& two-stage SFC & $0.8034$ & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
         \cline{2-7}
-        \multicolumn{1}{|c|}{} & Hierarchical SFC & $0.7882$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7826$\tabularnewline
+        \multicolumn{1}{|c|}{} & joint SFC & $0.7882$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7826$\tabularnewline
         \hline
-        \multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& 2-stage SFC & $0.7278$ & $0.7364$ & $0.7366$ & $0.7328$ & $0.7204$\tabularnewline
+        \multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& two-stage SFC & $0.7278$ & $0.7364$ & $0.7366$ & $0.7328$ & $0.7204$\tabularnewline
         \cline{2-7}
-        \multicolumn{1}{|c|}{} & Hierarchical SFC & $0.7334$ & $0.7445$ & $0.7516$ & $0.7344$ & $0.7373$\tabularnewline
+        \multicolumn{1}{|c|}{} & joint SFC & $0.7334$ & $0.7445$ & $0.7516$ & $0.7344$ & $0.7373$\tabularnewline
         \hline
@@
   four  SFC  variants shown in Table \ref{tbe:table2} to analyze the improvement
-  brought  by  multi-task  and  hierarchical  joint-model  structure. We conduct
+  brought  by  multi-task  and  joint-model  structure. We conduct
   ablation  experiments  to study the benefits brought by multi-task training by
-  comparing multi-task 2-stage SFC with single-task 2-stage SFC. We can see from
-  Table  \ref{tbe:table2}  that  2-stage  SFC  with  only  task 1 (sentence-pair
-  similarity task) degrades by 0.65 percent on average and 2-stage SFC with only
+  comparing multi-task two-stage SFC with single-task two-stage SFC. We can see from
+  Table  \ref{tbe:table2}  that  two-stage  SFC  with  only  task 1 (sentence-pair
+  similarity task) degrades by 0.65 percent on average and two-stage SFC with only
   task  2  (top-K  classification  task) degrades by 0.3 percent on average. The
@@
   $\mathcal{L}$.  Also, we can see that the hierachical SFC steadily outperforms
-  2-stage  SFC  on  5  diverse  datasets  by  1.17  percents  on  average.  This
+  two-stage  SFC  on  5  diverse  datasets  by  1.17  percents  on  average.  This
   observation  supports  the idea that the hierachical joint model structure can
   alleviate the limitation brought by the lack of interaction between similarity
-  model  and  classification  model in 2-stage SFC. Therefore, for the following
+  model  and  classification  model in two-stage SFC. Therefore, for the following
   analysis,  we  will  focus  on  the comparison between hierachical SFC and the
@@
   results  for  the  3  diverse  intent detection datasets (ClINC150, BANKING77,
-  HWU64) under few-shot settings indicate that our proposed hierarchical SFC can
+  HWU64) under few-shot settings indicate that our proposed joint SFC can
   achieve  2.47  percents  average  improvement  over  one  of the most powerful
@@
   few-shot  settings. Moreover, the improvement in F-score becomes more and more
-  prominent  with the decrease of data sample number per class. Our hierarchical
+  prominent  with the decrease of data sample number per class. Our joint
   SFC   can  achieve  4.97  percents  average  improvements  over  RoBERTa-large
@@
   joint  embedding  baseline  named as LEAM. As shown in Table \ref{tbe:table2},
-  hierarchical  SFC outperforms LEAM by 14.25 percents on average F-score over 5
+  joint  SFC outperforms LEAM by 14.25 percents on average F-score over 5
   datasets.  Besides,  although the labels within the 3 diverse intent detection
   datasets  (CLINC150,  BANKING77,  HWU64)  are  all  being  well-defined as the
-  semantic  summary  of  each intent, hierarchical SFC still outperforms LEAM by
+  semantic  summary  of  each intent, joint SFC still outperforms LEAM by
   14.69  percents  on  average  F-score.  This  observation  indicates that it's
@@
   compare  the  general  performance  of SFC with single-task classification and
-  similarity  baselines.  As  for  the  classification  model,  hierarchical SFC
+  similarity  baselines.  As  for  the  classification  model,  joint SFC
   outperforms    TextCNN    by   26.19   percents,   ALBERT-xxlarge   by   17.87
@@
   choose  the  strongest  pretrained  model  RoBERTa-large  as our baseline, and
-  hierarchical  SFC  achieves  the  improvement  of  7.81  percents  on average.
-  Moreover,  hierarchical  SFC's  result on 2 datasets without data sampling for
+  joint  SFC  achieves  the  improvement  of  7.81  percents  on average.
+  Moreover,  joint  SFC's  result on 2 datasets without data sampling for
   few-shot  settings,  which  are  ITG  and  Amazon-670k, are also 1.24 and 2.89
@@
   network  layers  to  cooperate  with  each  other  is  a  successful design of
-  hierarchical network structure for joint model, which enables these two models
+  joint network structure for joint model, which enables these two models
   assist each other for better overall results.

### 2020-08-27 chatbot_classification/aaai_2021/paper.tex
update result analysis

@@
           \hline
-          ALBERT-xxlarge & \multirow{2}*{$0.6500$} & \multirow{2}*{$0.9008$} & \multirow{2}*{$0.9296$} & \multirow{2}*{$0.3608$} & \multirow{2}*{$0.6345$} & \multirow{2}*{$0.8090$} & \multirow{2}*{$0.8530$} & \multirow{2}*{$0.3549$} & \multirow{2}*{$0.3876$} & \multirow{2}*{$0.5808$} & \multirow{2}*{$0.6320$} & \multirow{2}*{$0.7253$} & \multirow{2}*{$0.6893$}\tabularnewline
+          ALBERT-xxlarge & \multirow{2}*{$0.8497$} & \multirow{2}*{$0.9008$} & \multirow{2}*{$0.9296$} & \multirow{2}*{$0.5549$} & \multirow{2}*{$0.7981$} & \multirow{2}*{$0.8231$} & \multirow{2}*{$0.8530$} & \multirow{2}*{$0.4879$} & \multirow{2}*{$0.6116$} & \multirow{2}*{$0.6135$} & \multirow{2}*{$0.6996$} & \multirow{2}*{$0.7253$} & \multirow{2}*{$0.6893$}\tabularnewline
           (classification) & & & & & & & & & & & & &\tabularnewline
@@
         \cline{2-7}
-        \multicolumn{1}{|c|}{} & joint SFC & $0.7882$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7826$\tabularnewline
+        \multicolumn{1}{|c|}{} & joint SFC & $0.7986$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7918$\tabularnewline
         \hline
@@
   similarity task) degrades by 0.65 percent on average and two-stage SFC with only
-  task  2  (top-K  classification  task) degrades by 0.3 percent on average. The
+  task  2  (top-K  classification  task) degrades by 0.32 percent on average. The
   degradation  indicates  that  training  with these 2 tasks together in SFC can
   effectively  help  the  sentence-pair  model  extract  more knowledge from the
-  limited  amount  of data. Besides, task 2 degrades 0.35 percent less than task
+  limited  amount  of data. Besides, task 2 degrades 0.33 percent less than task
   1.  This observation suggests that task 2 may play a relatively more important
@@
   to  the  loss  $\mathcal{L}^{K}$  of  task  2  when calculating the total loss
-  $\mathcal{L}$.  Also, we can see that the hierachical SFC steadily outperforms
+  $\mathcal{L}$.  Also, we can see that the joint SFC steadily outperforms
   two-stage  SFC  on  5  diverse  datasets  by  1.17  percents  on  average.  This
-  observation  supports  the idea that the hierachical joint model structure can
+  observation  supports  the idea that the joint model structure can
   alleviate the limitation brought by the lack of interaction between similarity
   model  and  classification  model in two-stage SFC. Therefore, for the following
-  analysis,  we  will  focus  on  the comparison between hierachical SFC and the
+  analysis,  we  will  focus  on  the comparison between joint SFC and the
   other baseline models.
@@
   similarity  baselines.  As  for  the  classification  model,  joint SFC
-  outperforms    TextCNN    by   26.19   percents,   ALBERT-xxlarge   by   17.87
+  outperforms    TextCNN    by   26.19   percents,   ALBERT-xxlarge   by   9.95
   percents\footnote{We found that the performance of ALBERT.xxlarge is extremely
@@
   becomes a good choice.
+However, in spite of the effect on evaluation performance brought by different settings of hyperparameters, joint SFC still steadily outperforms two-stage SFC by 0.41 percents in overall average F-score on ITG and Amazon-670k datasets.
 
-  In  conclusion,  to  the best of our knowledge, these results place SFC as the
+  In  conclusion,  to  the best of our knowledge, these experimental results place joint SFC as the
   best   performing   model   on   5  diverse  experimental  datasets  for  text

### 2020-08-28 chatbot_classification/aaai_2021/paper.tex
modified:   paper.pdf   modified:   paper.tex

--- 2020-08-26 chatbot_classification/aaai_2021/paper.tex
@@
 
-  Task-specific  conversational  chatbot  \cite{wen2016network}  are  designed  to
-  share   the  working  pressure  of  human  customer  service  agents  who  are
-  responsible for solving customers' questions or queries about certain products
-  or  services.  Regardless  of  whether  the  conversation  is  single-turn  or
-  multi-turn,  the  essential  technical  solution  behind the chatbot is intent
-  classification model which can identify the correct intent behind user's input
-  text and find the corresponding answer.
+  Task-specific  conversational  chatbots  \cite{wen2016network}  can be applied
+  into  many practical products. For example, it can share the working burden of
+  human  customer  service  agents  responsible  for  customers' questions about
+  certain  products  or services. Another example is the speech-based control in
+  devices  like  intelligent  speakers, such as Siri, Google home, Baidu Xiaodu,
+  and smart home equipments. Regardless of whether these conversations belong to
+  single-turn or multi-turn, an essential technique underlying the chatbot is to
+  identify  the  real  intention  behind  a  user's  question or reply. Then the
+  chatbot  is caple of conducting expected action, text reply or accomplish some
+  operations.
 
@@
   class.  The  reason  is  that it's usually too expensive and time consuming to
-  extract  different  ways  of natural language expression for each intent class
+  extract  different  ways  of natural language expression for each intention class
   from  history  conversation  log  or  even  manually  compose  the corpus from
@@
   different from the target of classification task. That is to say, there always
-  exists  some intent classes which cannot be distinguished by each other merely
+  exists  some intention classes which cannot be distinguished by each other merely
   depending on semantic similarity. For example, we have 2 user query saying, A:
@@
   similar  to  B,  since  they  both  express  the desire for changing password.
-  However, it's still reasonable to classify them into 2 intent classes, since A
+  However, it's still reasonable to classify them into 2 intention classes, since A
   is asking for the method for changing password, while B is asking for the rule
@@
   identification,  and  then  find  an auxiliary model or tool which can help us
-  sample out top-K most related intent classes. This auxiliary model or tool can
+  sample out top-K most related intention classes. This auxiliary model or tool can
   either  be searching engine such as elasticsearch \cite{divya2013elasticsearch}
@@
   strategy \cite{bamler2020extreme}.  The  reason is that a task-specific chatbot
-  often  has hundreds of intent classes, which forms too many sentence pairs for
+  often  has hundreds of intention classes, which forms too many sentence pairs for
   training  since  any  two  sentences  from  two  different  classes can form a
@@
   3)  Experiment  results  on  4  public and 1 private short-text classification
-  datasets with respect to intent recognition tasks under conversational chatbot
+  datasets with respect to intention recognition tasks under conversational chatbot
   scenario  all demonstrated that our proposed SFC joint system with multi-task,
@@
         \hline 
-        HWU64 & Intent detection & 64 & [320, 640, 960, 1280] & [5, 10, 15, 20] & data sampling\tabularnewline
+        HWU64 & intention detection & 64 & [320, 640, 960, 1280] & [5, 10, 15, 20] & data sampling\tabularnewline
         \hline 
-        CLINC150 & Intent detection & 150 & [750, 1500, 2250] & [5, 10, 15] & data sampling\tabularnewline
+        CLINC150 & intention detection & 150 & [750, 1500, 2250] & [5, 10, 15] & data sampling\tabularnewline
         \hline 
-        BANKING77 & Intent detection & 77 & [385, 770, 1155, 1540] & [5, 10, 15, 20] & data sampling\tabularnewline
+        BANKING77 & intention detection & 77 & [385, 770, 1155, 1540] & [5, 10, 15, 20] & data sampling\tabularnewline
         \hline 
@@
 
-  $\bullet$ \textbf{Subset of recently-released intent detection datasets}.
+  $\bullet$ \textbf{Subset of recently-released intention detection datasets}.
 
@@
   with  the  chatbot,  more data can be extracted from conversation log. Base on
-  these  assumptions,  we  do  experiments  on  the following 3 intent detection
+  these  assumptions,  we  do  experiments  on  the following 3 intention detection
   dataset    under    sampling    method    similar    to    the   approach   in
@@
 
-  \textbf{HWU64}   is  a  intent  detection  dataset  designed  for  home  robot
+  \textbf{HWU64}   is  a  intention  detection  dataset  designed  for  home  robot
   scenario \cite{liu2019benchmarking}.  It aims at the specific task of capturing
-  the  intent  for  different  user  requests  to  home  robot  and  finding the
+  the  intention  for  different  user  requests  to  home  robot  and  finding the
   corresponding answer. The raw dataset contains 25,716 data points for 64 class
@@
   made  by real users through crowdsourcing \cite{larson2019evaluation}. Here, we
-  sample 5, 10 and 15 training data points for each intent class label by random
+  sample 5, 10 and 15 training data points for each intention class label by random
   sampling for our experimental setup.
 
-  \textbf{BANKING77}  is  a intent detection dataset for bank customer services.
+  \textbf{BANKING77}  is  a intention detection dataset for bank customer services.
   The    raw    dataset    contains    13,084   data   points   for   77   class
@@
   ALBERT-xxlarge \cite{lan2019albert}  for  comparison.  Since  we  use different
-  few-shot   settings   from    \cite{casanueva2020efficient}  for  those  intent
+  few-shot   settings   from    \cite{casanueva2020efficient}  for  those
+  intention
   detection  datasets,  we also use BERT-large tuned on our few-shot settings as
@@
   only  a  few  sample  sentences are available for each class. The experimental
-  results  for  the  3  diverse  intent detection datasets (ClINC150, BANKING77,
+  results  for  the  3  diverse  intention detection datasets (ClINC150, BANKING77,
   HWU64) under few-shot settings indicate that our proposed joint SFC can
@@
   joint  SFC outperforms LEAM by 14.25 percents on average F-score over 5
-  datasets.  Besides,  although the labels within the 3 diverse intent detection
+  datasets.  Besides,  although the labels within the 3 diverse intention detection
   datasets  (CLINC150,  BANKING77,  HWU64)  are  all  being  well-defined as the
-  semantic  summary  of  each intent, joint SFC still outperforms LEAM by
+  semantic  summary  of  each intention, joint SFC still outperforms LEAM by
   14.69  percents  on  average  F-score.  This  observation  indicates that it's

### 2020-08-30 chatbot_classification/aaai_2021/paper.ver_04.tex
version 4.   modified:   paper.tex
  new file:   paper.ver_04.pdf
  new file:   paper.ver_04.tex

--- 2020-08-28 chatbot_classification/aaai_2021/paper.tex
@@
 
-  Task-specific  conversational  chatbots  \cite{wen2016network}  can be applied
+  Task-specific  conversational  chatbot  \cite{wen2016network}  has been applied
   into  many practical products. For example, it can share the working burden of
@@
   identify  the  real  intention  behind  a  user's  question or reply. Then the
-  chatbot  is caple of conducting expected action, text reply or accomplish some
+  chatbot  is caple of conducting expected actions, text reply or accomplish some
   operations.
 
-  Although  task-specific  conversational chatbot already has a wide application
-  in various business and industries, it's still a quite challenging task due to
-  its  natural  properties of low-resource. First, customers' utterance within a
-  conversation  is  usually  quite  short  and  completed  in a few words. Short
-  text \cite{song2014short}  are generally more ambiguous in comparison with long
-  texts  such  as  paragraphs  or  documents  since  they  don't  contain enough
-  contextual  information,  which poses a great challenge \cite{chen2019deep} for
-  classification        task \cite{phan2008learning,yan2009dynamic,hua2015short}.
-  Second,  at  the  initial  stage  of  building  a chatbot for specific task or
-  service, it's often extremely hard to collect sufficient data samples for each
-  class.  The  reason  is  that it's usually too expensive and time consuming to
-  extract  different  ways  of natural language expression for each intention class
-  from  history  conversation  log  or  even  manually  compose  the corpus from
-  nothing.  Therefore,  the  key  to  building a task-specific chatbot with high
-  performance     becomes     solving     the     challenge     of    short-text
-  classification \cite{sriram2010short}        problem       under       few-shot
-  setting \cite{yu2018diverse}.
+  It  is  a  challenging task due to some inherent properties. First,
+  a customer's  utterance  within  a conversation is usually quite short. Since it
+  does  not  contain  enough  information,  short  text \cite{song2014short} are
+  thought  to  be  more  ambiguous  compared to long texts such as paragraphs or
+  documents,  poseing  a  great challenge \cite{chen2019deep} for classification
+  task   \cite{phan2008learning,yan2009dynamic,hua2015short}.   Second,  in  the
+  initial  stage  of  building  a  chatbot  , it is often rather hard to collect
+  sufficient  labeled  data  to  train  a good model. Because developers have to
+  examine tons of real system logs for typical user's utterances, and then label
+  them  with expected intentions. Therefore, the key to building a task-specific
+  chatbot  with  high  performance  becomes  solving the challenge of short-text
+  classification   \cite{sriram2010short}   problem   under   few-shot   setting
+  \cite{yu2018diverse}.
 
-  One  of  the most popular approach among existing work was text classification
-  model  based  on  neural network. Since the length of the text is quite short,
-  many   previous   work \cite{wen2016network}  choose  neural  network  such  as
-  convolutional                          neural                         networks
-  (CNNs) \cite{kim2014convolutional,zhang2015character,conneau2016very}  or  long
-  short  term memory networks (LSTMs) \cite{mousa2017contextual,liu2016recurrent}
-  to  accomplish  the task of extracting semantic feature from limited amount of
-  words.  A  common model structure is adding a softmax classifier to the top of
-  the  neural  network.  Afterwards, pre-trained language models on large corpus
-  like   BERT \cite{devlin2018bert}  and  RoBERTa \cite{liu2019roberta}  has  been
-  proven   more   powerful  in  solving  many  NLP  tasks  including  short-text
-  classification \cite{madabushi2020cost}.      Especially      for      few-shot
-  scenarios \cite{yu2018diverse},       pre-trained      model      based      on
-  transformers \cite{vaswani2017attention},   shown  in  Fig.  \ref{Fig.1.sub.1},
-  tends  to do more help to reducing the negative effects brought by scarcity of
-  training data.
+  Generally  there  are  two  kinds  of  approaches  to  address  this  problem,
+  classification model that directly maps an input into a most likely label, and
+  similarity  model  that searches a label whose associated data is most similar to
+  an input.
 
-  Another  common  approach  is  text  classification  neural  network  based on
-  label-word     joint     embedding,    such    as    LEAM \cite{wang2018joint},
-  MTLE \cite{zhang2017multi}   and   EXAM \cite{du2019explicit}.   This   approach
-  involves  label  embedding when constructing the text-sequence representation.
-  Take  LEAM  as  an  example,  the  text classification model is implemented by
-  jointly    embedding    the    word    and    label   in   the   same   latent
-  space \cite{wang2018joint}. Afterwards, the text representation are constructed
-  based  on  text-label  compatibility through attention mechanism. In this way,
-  additional  sources  of  semantic  information  from class labels can be fully
-  leveraged, which is quite helpful especially under few-shot scenario.
+  The   first  one,  \emph{text  classification},  includes  classic  long  text
+  classification  and  short  text  classification  in  this  scenario.  Besides
+  traditional  machine  learning  models  like  SVM,  boosting  tree,  many work
+  \cite{wen2016network}  choose  neural  network  such  as  convolutional neural
+  networks (CNNs) \cite{kim2014convolutional,zhang2015character,conneau2016very}
+  and       long       short       term       memory       networks      (LSTMs)
+  \cite{mousa2017contextual,liu2016recurrent}   to   accomplish   the   task  of
+  extracting  semantic  feature from limited amount of words. Their common model
+  structure  is  adding  a  softmax classifier as the final layer and mapping to
+  labels.  Another  two  interesting lines of work, label-word joint models, and
+  joint  NER  and  classification  are  discussed  in  the related work section.
+  Afterwards,   pre-trained   language   models   on   large  corpus  like  BERT
+  \cite{devlin2018bert}  and  RoBERTa \cite{liu2019roberta} has been proven more
+  powerful  in  solving  many  NLP  tasks  including  short-text  classification
+  \cite{madabushi2020cost}.      Especially      for      few-shot     scenarios
+  \cite{yu2018diverse},     pre-trained     model    based    on    transformers
+  \cite{vaswani2017attention}, shown in Fig. \ref{Fig.1.sub.1}, tends to do more
+  help to reducing the negative effects brought by scarcity of training data.
 
-  The  third  popular  approach  among  previous work was based on sentence-pair
-  model.  The  motivation  of  this  approach  was  started  from  the  idea  of
-  Information     Retrival    (IR)    based    chatbot \cite{jafarpour2010filter,
-  leuski2011npceditor}.  Having  a  Q-A (Question-Answer) pairs dataset and user
-  query  Q,  the  IR based conversational system will look up in the Q-A dataset
-  for  the pair (Q', A') that best matches query Q through semantic analysis and
-  returns   A'   as   the  answer  to  Q \cite{mnasri2019recent}.  In  this  way,
-  sentence-pair  model  pre-trained  on  large  corpus  of  semantic  similarity
-  identification  task  can  be applied for being used as a tool to identify the
-  class  with  highest  semantic  similarity to customer's query. A common model
-  structure  of pre-trained \cite{devlin2018bert} sentence-pair model is based on
-  multiple  cross-attention  mechanism \cite{barkan2020scalable},  shown  in Fig.
-  \ref{Fig.1.sub.2}.  Due  to  the  fact that many experiment results have shown
-  that  RoBERTa \cite{liu2019roberta}  is  an  improved  version of BERT, and has
-  achieved  amazing  results  on  both  text  classification  and sentence-pairs
-  semantic similarity tasks, we choose RoBERTa as an important baseline approach
-  in this paper.
+  The  second  one,  \emph{similarity model} is also called sentence-pair model.
+  Its  motivation  originates  from  the idea of Information Retrival (IR) based
+  chatbot   \cite{jafarpour2010filter,   leuski2011npceditor}.   Having   a  Q-A
+  (Question-Answer)  pairs dataset and user query Q, the IR based conversational
+  system will look up in the Q-A dataset for the pair (Q', A') that best matches
+  query  Q  through  semantic  analysis  and  returns  A'  as  the  answer  to Q
+  \cite{mnasri2019recent}. In this way, sentence-pair model pre-trained on large
+  corpus  of  semantic  similarity  identification task can be applied for being
+  used  as  a  tool  to  identify  the class with highest semantic similarity to
+  customer's    query.    A    common    model    structure    of    pre-trained
+  \cite{devlin2018bert} sentence-pair model is based on multiple cross-attention
+  mechanism  \cite{barkan2020scalable},  shown in Fig. \ref{Fig.1.sub.2}. Due to
+  the   fact   that   many   experiment   results   have   shown   that  RoBERTa
+  \cite{liu2019roberta} is an improved version of BERT, and has achieved amazing
+  results  on  both  text  classification and sentence-pairs semantic similarity
+  tasks, we choose RoBERTa as an important baseline approach in this paper.
 
-  Despite the success of these 3 approaches, they still have some limitations in
-  task-specific chatbot scenario. As for the text classification model approach,
-  it's   quite   hard  to  use  data  augmentation  method  to  solve  the  data
-  insufficiency  challenge since the it's usually unfeasible to get large amount
-  of  domain-specific  data  when  facing  a  new  task. As for label-word joint
-  embedding  approach,  it  poses  noticeable requirements on label information.
-  However,  in  our  cases,  since  we have large amount of class labels without
-  being well-defined for question answering chatbot, the only thing we can do is
-  to  choose  one  of the user utterance as the class label to represent the key
-  information  of  the  whole class. In this way, the label will become not only
-  prolix  but  also  biased,  which  will  bring  some  negative effect to label
-  embedding.  With  respect  to  the sentence-pair model approach, though we can
-  obtain   large   amount  of  data  in  semantically  duplicate  sentence  pair
-  identification  domain  for  transfer  learning \cite{sun2019fine},  it's still
-  quite  hard  to  perform  well  on  task-specific dataset because the training
-  objective  of  sentence-pair  model  is semantic similarity, which is slightly
-  different from the target of classification task. That is to say, there always
-  exists  some intention classes which cannot be distinguished by each other merely
-  depending on semantic similarity. For example, we have 2 user query saying, A:
-  What  should I do if I want to change my password? B: What is the modification
-  rule if I want to change my password? In this case, sentence A is semantically
-  similar  to  B,  since  they  both  express  the desire for changing password.
-  However, it's still reasonable to classify them into 2 intention classes, since A
-  is asking for the method for changing password, while B is asking for the rule
-  to follow when creating a new password.
+  Despite  the  success  of  these two kinds of approaches, they still have some
+  limitations   in   task-specific  chatbot  scenario.  As  for  the  \emph{text
+  classification  model},  it  is  quite hard to use data augmentation method to
+  solve  the  data insufficiency challenge since the it is usually unfeasible to
+  get  large amount of domain-specific data when facing a new task. With respect
+  to  the  \emph{similarity model}, though we can obtain a large amount of data
+  from semantically  duplicate  sentence  pair identification domain for transfer
+  learning  \cite{sun2019fine},  it  is  still  quite  hard  to  perform well on
+  a new task-specific dataset,  since their objective losses are totally different.
 
-  The  above  limitation  motivates  us  to  propose a joint system of both text
-  classification  task  and  sentence-pair  semantic  similarity task, named SFC
-  here, shown in Fig. \ref{fig:ver.1.3}. Our goal is to utilize the advantage of
-  the  feasibility  of  transfer learning based on semantic similarity, while in
-  the  mean time, add the classification task's target into the training process
-  of            sentence-pair           model           for           multi-task
-  learning \cite{caruana1993multitask,collobert2008unified}.  To  obtain  such  a
-  joint  system,  we  first start with preparation work, which is pre-training a
-  sentence-pair   model   on  external  corpus  for  sentence  pair  duplication
-  identification,  and  then  find  an auxiliary model or tool which can help us
-  sample out top-K most related intention classes. This auxiliary model or tool can
-  either  be searching engine such as elasticsearch \cite{divya2013elasticsearch}
-  or  a  text  classification  model  trained  on  task-specific  chatbot  data.
-  Afterwards,  we  further  fine-tune  the  sentence-pair  model with 2 training
-  tasks:  1)  the  regular  sentence pair similarity tasks. Here we use the text
-  classification  model  as  an auxiliary model in this paper to sample sentence
-  pairs       for       training       based      on      negative      sampling
-  strategy \cite{bamler2020extreme}.  The  reason is that a task-specific chatbot
-  often  has hundreds of intention classes, which forms too many sentence pairs for
-  training  since  any  two  sentences  from  two  different  classes can form a
-  sentence-pair     of     negative     sample.     Besides,     according    to
-  Bamler \cite{bamler2020extreme},   training   on  negative  samples  from  most
-  confusing  wrong  label  can  help  model  converge  faster  and obtain better
-  performance.  2) the classification task on top-K (here K is a hyperparameter)
-  candidate  classes  provided  by  our auxiliary model or tool. Here we use the
-  average  pooling  of  the  representation  given  by  sentence-pair  model for
-  sentence pairs formed by the user input query and the corpus sentences in each
-  class  as  the  feature.  We  stack the task-specific layers on the top of the
-  shared-parameter  sentence-pair  model structure, which is a classic parameter
-  sharing                                   mechanism \cite{collobert2008unified,
-  subramanian2018learning,liu2019multi}   for  multi-task \cite{sun2019fine}.  In
-  this  way, specific knowledge contained in these 2 tasks can be fully explored
-  and deeply interact with each other to obtain better overall performance.
-
-  However,  since  the auxiliary tool in joint system mentioned above works in a
-  separate  stage  from  sentence-pair model, we find the the quality of sampled
-  candidate  classes  might  limit  the  overall  performance  of SFC, since the
-  candidate  classes  for  each user query is always fixed during the multi-task
-  training  process. This observation motivates us to further improve SFC into a
-  joint  model  of  sentence-pair  model  and  text  classification  model  in a
-  joint  architecture  by  putting  different  tasks at different network
-  layers \cite{sogaard2016deep,   hashimoto2016joint}   and  then  training  them
-  together,  shown  in  Fig  \ref{fig:framework}.  Here, the text classification
-  model  involved in joint training process replace the role of auxiliary tools.
-  In  this  way, the sentence pairs selected from top-K classes becomes dynamic,
-  which  means  the  text classification model will also be further optimized to
-  provide better top-K classes pooling result.
+  The  above limitation motivates us to propose a joint system that is capble of
+  taking  advantagges  from  both  classification model and similarity model. We
+  calle  it  SFC,  short  for  similairty model fused with classification Model,
+  shown  in  Fig.  \ref{fig:ver.1.3}.  To  better train SFC, we further bring in
+  multi-task   learning   \cite{caruana1993multitask,collobert2008unified}.  Our
+  basic  idea  cames  from  two  stages. In the first stage, we use an auxiliary
+  model  to  select top-K most possible labels for a input. This model can be an
+  elasticsearch  \cite{divya2013elasticsearch}  or  a  text classification model
+  trained on current task-specific chatbot data. In the second stage, we build a
+  classification  model  whose  main modules are similarity models. Then, this
+  structure  derives two goals to train towards, the classification loss for our
+  application,  and the similarity loss for the main modules. When the two stages
+  are  independently  optimized,  we call \emph{two-stage SFC}. We further find,
+  the  the  quality  of  output  from  the  first  stage  might  limit the final
+  performance  of  system,  since  the  candidate  labels for each user query is
+  always  fixed  in  the  whole  multi-task  training  process. This observation
+  motivates  us  to  further  improve  the  two-stage SFC into a joint training,
+  called  \emph{joint  SFC}. In this way, the sentence pairs associated with the
+  top-K  classes  also  become dynamic, and the text classification model in the
+  first  stage  will also be further optimized to provide better top-K result by
+  the final training loss.
 
   We summarize our contributions as follow:
+  \begin{enumerate}
+    \item We propose a novel joint system to makes full utilization of
+    the advantages from both text classification model and similarity model.
 
-  1)  We  propose  a  novel  joint  system  named  SFC  with multi-task training
-  technique designed for task-specific conversational chatbot with low-resource,
-  in  which  we make full utilization of the advantages brought by both the text
-  classification task and sentence-pair semantic similarity task.
+    \item To  better  train such a system, we bring in multi-task training to obtain
+    expected performance.
 
-  2)  To  further  improve  the  system  performance  of SFC, we also propose an
-  innovative  joint  model structure, in which the text classification model and
-  sentence-pair model are fused into one single model for joint training.
-
-  3)  Experiment  results  on  4  public and 1 private short-text classification
-  datasets with respect to intention recognition tasks under conversational chatbot
-  scenario  all demonstrated that our proposed SFC joint system with multi-task,
-  as  well  as  the  improved  version  of  SFC,  can  both  achieve  remarkable
-  improvement comparing to some powerful single-task and single-model baselines,
-  especially under few-shot settings.
+    \item Experiment  results  from 4 public and 1 private short-text classification
+    datasets,  show  that  our  proposed  SFC joint system can achieve significant
+    improvements over strong baselines, especially in the low resource settings.
+  \end{enumerate}
 
@@
   \end{figure*}
+
+  \section{Related work}
+
+  Another  common  approach  is  text  classification  neural  network  based on
+  label-word     joint     embedding,    such    as    LEAM \cite{wang2018joint},
+  MTLE \cite{zhang2017multi}   and   EXAM \cite{du2019explicit}.   This   approach
+  involves  label  embedding when constructing the text-sequence representation.
+  Take  LEAM  as  an  example,  the  text classification model is implemented by
+  jointly    embedding    the    word    and    label   in   the   same   latent
+  space \cite{wang2018joint}. Afterwards, the text representation are constructed
+  based  on  text-label  compatibility through attention mechanism. In this way,
+  additional  sources  of  semantic  information  from class labels can be fully
+  leveraged, which is quite helpful especially under few-shot scenario.
+
+  As for \emph{label-word joint
+  embedding  approach},  it  poses  noticeable requirements on label information.
+  However,  in  our  cases,  since  we have large amount of class labels without
+  being well-defined for question answering chatbot, the only thing we can do is
+  to  choose  one  of the user utterance as the class label to represent the key
+  information  of  the  whole class. In this way, the label will become not only
+  prolix  but  also  biased,  which  will  bring  some  negative effect to label
+  embedding.
+
+  {Add joint NER and classification problem here.}
 
@@
   semantic  summary  of  each intention, joint SFC still outperforms LEAM by
-  14.69  percents  on  average  F-score.  This  observation  indicates that it's
+  14.69  percents  on  average  F-score.  This  observation  indicates that it is
   usually  quite  hard  to  use  a  fixed  label  with  only  a few words as the
@@
   Through  analyzing the experimenal results shown in Table \ref{tbe:table3}, we
-  find  that the best setting of hyperparameters might be slightly different for
+  find  that the best setting of hyperparameters might be different for
   datasets of different data size. The class label number of ITG and Amazon-670k

### 2020-08-30 chatbot_classification/aaai_2021/versions/paper.ver_01.tex
Reorganized.

--- 2020-08-15 chatbot_classification/aaai_2021/paper.tex
@@
 The detailed network structure of 2-stage SFC is shown in Fig. \ref{fig:ver.1.3}. It is composed with 2 separate stages in charge of different jobs.
-In stage 1, we can use any auxiliary model or tool to provide top-K most related class labels for sampling sentence pairs of both positive samples and negative samples for stage 2.
+In stage 1, we can use any auxiliary model or tool to provide top-K most related classes for sampling sentence pairs of both positive samples and negative samples for stage 2.
 Suppose we have a training data set $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$ of $N$ data points, in which $x_{i}$ is the user input query and $y_{i}$ is a single class label from a class label set of $C$ classes in total.
@@
 directly from original data set $\mathcal{D}$ without any sampling strategy, then $\mathcal{D'}$ will have $M=N^2$ data points of sentence pairs, which might be too time-consuming for the training process of stage 2 since we often have hundreds of class labels under task-specific chatbot scenario.
-Although we may only have a few data points for a single class label, $M$ is still quite a big number.
+Although we may only have a few data points for a single class label, $N$ is still quite a big number.
 
@@
 The key idea of this sampling strategy is to train with negative samples that are hard to be distinguished from positive samples.
-Now suppose we have a user input query $x_{i}$ and top-K most related class labels set $\mathcal{C'}=\{c'_{1}, \dots, c'_{K}\}$ provided by auxiliary model or tool in stage 1, where $K$ is a hyperparameter set by us that controls candidate class number, we apply the adversarial negative sampling strategy into our sentence pair sampling process by the following 2 steps:
+Now suppose we have a user input query $x_{i}$ and top-K most related class labels set $\mathcal{C'}=\{c'_{1}, \dots, c'_{K}\}$ found by auxiliary model or tool in stage 1, where $K$ is a hyperparameter set by us that controls candidate class number, we apply the adversarial negative sampling strategy into our sentence pair sampling process by the following 2 steps:
 
@@
 positive sentence pair sampling}: During the training process, we have to first make sure that the ground truth class label $y_{i}$ for $x_{i}$ is within the candidate class label set $\mathcal{C'}$.
-If $y_{i}\notin \mathcal{C'}$, we will manually add $y_{i}$ into $\mathcal{C'}$ by replacing $c'_{K}$ with $y_{i}$, since $c'_{K}$ is the least promising candidate label according to the auxiliary model in stage 1.
+If $y_{i}\notin \mathcal{C'}$, we will manually add $y_{i}$ into $\mathcal{C'}$ by replacing $c'_{K}$ with $y_{i}$.
 Afterwards, we will randomly sample $P$ sentences $\{x'_{0},x'_{1}, \dots, x'_{P}\}$ with the same class label as $y_{i}$ from data set $\mathcal{D}$ to form the set of sentence pairs with positive label $\mathcal{P'}_{i}=\{[(x_{i}, x'_{0}), 1], [(x_{i}, x'_{1}), 1], \dots, [(x_{i}, x'_{P}), 1]\}$, where $P$ is also a hyperparameter set by us that controls the number of sentences we should sample from each class.
@@
 negative sentence pair sampling}: As for negative sentence pairs, we will also randomly sample $P$ sentences for each class in the negative candidate class label set $\mathcal{C'}\backslash \{y_{i}\}$.
-The class labels in $\mathcal{C'}\backslash \{y_{i}\}$ are the set of most confusing class labels comparing to the ground truth ${y_{i}}$, so we assume that the sentence pairs with negative label grouped by user input query $x_{i}$ and sentences with class labels in $\mathcal{C'}\backslash \{y_{i}\}$ are strong adversarial negative samples for sentence-pair similarity model that can help enhance the training speed and performance.
+The class labels in $\mathcal{C'}\backslash \{y_{i}\}$ are the set of most confusing classes comparing to the ground truth ${y_{i}}$, so we assume that the sentence pairs with negative label grouped by user input query $x_{i}$ and sentences with class labels in $\mathcal{C'}\backslash \{y_{i}\}$ are also strong adversarial negative samples for sentence-pair similarity model that can help enhance the training speed and performance.
 According to the same method as positive sentence pair sampling, we can obtain the set of sentence pairs with negative label as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{0}), 0], [(x_{i}, x'_{1}), 0], ..., [(x_{i}, x'_{P\cdot (K-1)}), 0]\}$
@@
 
-\subsubsection{stage 1: classification model for providing top-K candidate class labels}
+\subsubsection{stage 1: classification model for providing top-K classes}
 As for stage 1, our SFC system can adapt to any auxiliary model or even searching tool based on Term Frequency-Inverse
@@
 \ref{Fig.1.sub.1}, for better overall performance.
-According to our experimental result, RoBERTa can guarantee that approximately 95\% ground truth label be included in top-5 candidate class labels with highest probability after being fine-tuned on task-specific data set with experimental result measured by F-score at around 0.75.
+According to our experimental result, RoBERTa can guarantee that approximately 95\% ground truth label be included in top-5 candidate classes with highest probability after being fine-tuned on task-specific data set with experimental result measured by F-score at around 0.75.
 So we use RoBERTa as encoder of classification model in our setting at stage 1 to ensure low limitation for the performance of stage 2.
@@
 Before we start to fine-tune our sentence-pair model on task-specific dataset, we first fine-tune RoBERTa on Quora dataset\cite{iyer2017first}, which contains 404,290 potential duplicate question pairs, for transfer learning.
-Then we continue to do multi-task training on sentence-pair dataset $\mathcal{D'}$ sampled from the top-K candidate class labels provided by stage 1.
+Then we continue to do multi-task training on sentence-pair dataset $\mathcal{D'}$ sampled from the top-K candidate classes provided by stage 1.
 
@@
 
-As for top-K classification task, it shares the same sentence-pair similarity model structure with task 1.
+As for top-K classification task, we share the same sentence-pair similarity model structure with task 1.
 The only difference is that we add a task-specific average pooling layer, shown in Fig.
@@
 
-We already know that the size of ${\Phi}^S$ in task 1 is $M\times 2=(N\cdot K\cdot P)\times 2$, where $N$ is the total number of data points in original training data $\mathcal{D}$, $K$ is a hyperparameter that controls the number of candidate class labels provided by stage 1, and $P$ is also a hyperparameter that controls the number of sentences we should randomly sample from each candidate class labels.
+We already know that the size of ${\Phi}^S$ in task 1 is $M\times 2=(N\cdot K\cdot P)\times 2$, where $N$ is the total number of data points in original training data $\mathcal{D}$, $K$ is a hyperparameter that controls the number of candidate classes provided by stage 1, and $P$ is also a hyperparameter that controls the number of sentences we should randomly sample from each candidate class.
 Now, for the average pooling layer, we first reshape ${\Phi}^S$ into the size of $N\times K\times P\times 2$, and then split it into ${\Phi}^{K,pos}$ and ${\Phi}^{K,neg}$, and both of them will have the size of $N\times K\times P$.
@@
 \ref{fig:framework}.
-In hierarchical SFC, classification model is being placed in lower layer level to dynamically provide top-K candidate class labels for the sentence-pair similarity model placed in higher layer level through a top-K pooling layer.
-In this way, classification model and similarity model can be merged into one single joint-model for multi-task training with sentence pairs sampled from varying candidate class labels, thus avoiding the limitation brought by 2 separate stage structure.
+In hierarchical SFC, classification model is being placed in lower layer level to dynamically provide top-K candidate classes for the sentence-pair similarity model placed in higher layer level through a top-K pooling layer.
+In this way, classification model and similarity model can be merged into one single joint-model for multi-task training, thus avoiding the limitation brought by 2 separate stage structure.
 
@@
 \section{Experiments}
-In this section, we conduct extensive experiments over 5 task-specific datasets to evaluate the performance of our proposed SFC system and the effectiveness of the methodology of multi-task learning and hierachical joint-model structure under low-data settings.
+In this section, we conduct extensive experiments over 5 task-specific dataset to evaluate the performance of our proposed SFC system and the effectiveness of the methodology of multi-task learning and hierachical joint-model structure under low-data settings.
 
 \subsection{Datasets}
-The datasets used in our experiments aims to help us study low-resource text classification problem under task-specific conversational chatbot scenario.
+The dataset used in our experiments aims to help us study low-resource text classification problem under task-specific conversational chatbot scenario.
 Therefore, we keep all the dataset under low-resource chatbot corpus setting, which is a large number of class labels (50-250) with a few examples(5-20) in short text for each class, by sampling smaller subsets from the full scale when the raw datasets are oversized, see Table \ref{tbe:dataset statistic}.
@@
 
-$\bullet$ \textbf{Full-scale real-world task-specific faq chatbot dataset}
+$\bullet$ \textbf{full-scale real-world task-specific faq chatbot dataset}
 
@@
 
-$\bullet$ \textbf{Subset of customer review dataset for extreme classification}
+$\bullet$ \textbf{subset of customer review dataset for extreme classification}
 
@@
 
-$\bullet$ \textbf{Subset of recently-released intent detection datasets}.
+$\bullet$ \textbf{subset of recently-released intent detection datasets}.
 
@@
 Base on these assumptions, we do experiments on the following 3 intent detection dataset under sampling method similar to the approach in \cite{casanueva2020efficient} but in more sophisticated few-shot settings, while keeping the same test sets for each experiment to see the change of the improvement scale with decreasing data amount.
+
+\textbf{HWU64} is a intent detection dataset designed for home robot scenario\cite{liu2019benchmarking}.
+It aims at the specific task of capturing the intent for different user requests to home robot and finding the corresponding answer.
+The raw dataset contains 25,716 data points for 64 class labels through crowdsourcing, which raises much more data than common real-world circumstances.
+Therefore, we experiment with the setups where only 5, 10, 15 and 20 training data points are available for each class label by random sampling.
+
+\textbf{CLINC150} is a dataset designed for task-oriented systems with 23,700 queries that are short and unstructured for 150 intents, in the same style made by real users through crowdsourcing\cite{larson2019evaluation}.
+Here, we sample 5, 10 and 15 training data points for each intent class label by random sampling for our experimental setup.
+
+\textbf{BANKING77} is a intent detection dataset for bank customer services.
+The raw dataset contains 13,084 data points for 77 class labels\cite{casanueva2020efficient}.
+Here, we sample 5, 10, 15, 20 training data points for each class label by random sampling for our experimental setup.
 
@@
 \hline
-TextCNN & \multirow{2}*{$0.3539$} & \multirow{2}*{$0.5497$} & \multirow{2}*{$0.6246$} & \multirow{2}*{$0.2882$} & \multirow{2}*{$0.5187$} & \multirow{2}*{$0.6129$} & \multirow{2}*{$0.6554$} & \multirow{2}*{$0.2105$} & \multirow{2}*{$0.3202$} & \multirow{2}*{$0.4154$} & \multirow{2}*{$0.4529$} & \multirow{2}*{$0.5563$} & \multirow{2}*{$0.3333$}\tabularnewline
-(classification) & & & & & & & & & & & & &\tabularnewline
-\hline
-LEAM & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-}\tabularnewline
-(classification) & & & & & & & & & & & & &\tabularnewline
-\hline
 BERT-large & \multirow{2}*{$0.8080$} & \multirow{2}*{$0.8904$} & \multirow{2}*{$0.9265$} & \multirow{2}*{$0.578$} & \multirow{2}*{$0.8004$} & \multirow{2}*{$0.8518$} & \multirow{2}*{$0.8827$} & \multirow{2}*{$0.4711$} & \multirow{2}*{$0.5963$} & \multirow{2}*{$0.6342$} & \multirow{2}*{$0.7010$} & \multirow{2}*{$0.7485$} & \multirow{2}*{$0.6658$}\tabularnewline
@@
 \hline
-ALBERT-xxlarge & \multirow{2}*{$0.6500$} & \multirow{2}*{$0.9008$} & \multirow{2}*{$0.9296$} & \multirow{2}*{$0.3608$} & \multirow{2}*{$0.6345$} & \multirow{2}*{$0.8090$} & \multirow{2}*{$0.8530$} & \multirow{2}*{$0.3549$} & \multirow{2}*{$0.3876$} & \multirow{2}*{$0.5808$} & \multirow{2}*{$0.6320$} & \multirow{2}*{$0.7253$} & \multirow{2}*{$0.6893$}\tabularnewline
+ALBERT-xxlarge & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{$0.1422$} & \multirow{2}*{$0.2057$} & \multirow{2}*{$0.5723$} & \multirow{2}*{$0.5912$} & \multirow{2}*{$0.6601$} & \multirow{2}*{$0.6893$}\tabularnewline
 (classification) & & & & & & & & & & & & &\tabularnewline
@@
 \hline
-RoBERTa-large & \multirow{2}*{$0.8266$} & \multirow{2}*{$0.8861$} & \multirow{2}*{$0.9023$} & \multirow{2}*{$0.757$} & \multirow{2}*{$0.8476$} & \multirow{2}*{$0.8614$} & \multirow{2}*{$0.8743$} & \multirow{2}*{$0.5425$} & \multirow{2}*{$0.6164$} & \multirow{2}*{$0.6503$} & \multirow{2}*{$0.6729$} & \multirow{2}*{$0.7418$} & \multirow{2}*{$0.6362$}\tabularnewline
+RoBERTa-large & \multirow{2}*{$0.8266$} & \multirow{2}*{$0.8861$} & \multirow{2}*{$0.9023$} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{$0.5425$} & \multirow{2}*{$0.6164$} & \multirow{2}*{$0.6503$} & \multirow{2}*{$0.6729$} & \multirow{2}*{$0.7418$} & \multirow{2}*{$0.6362$}\tabularnewline
 (similarity) & & & & & & & & & & & & &\tabularnewline
@@
 \hline
-2-stage SFC & \multirow{2}*{$0.9162$} & \multirow{2}*{$0.9424$} & \multirow{2}*{$0.9530$} & \multirow{2}*{$0.7997$} & \multirow{2}*{$0.8823$} & \multirow{2}*{$0.8945$} & \multirow{2}*{$0.9123$} & \multirow{2}*{$0.6498$} & \multirow{2}*{$0.6980$} & \multirow{2}*{$0.7202$} & \multirow{2}*{$0.7358$} & \multirow{2}*{$0.8020$} & \multirow{2}*{$0.7311$}\tabularnewline
+2-stage SFC & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-}\tabularnewline
 (task2 only) & & & & & & & & & & & & &\tabularnewline
@@
 
-\textbf{HWU64} is a intent detection dataset designed for home robot scenario\cite{liu2019benchmarking}.
-It aims at the specific task of capturing the intent for different user requests to home robot and finding the corresponding answer.
-The raw dataset contains 25,716 data points for 64 class labels through crowdsourcing, which raises much more data than common real-world circumstances.
-Therefore, we experiment with the setups where only 5, 10, 15 and 20 training data points are available for each class label by random sampling.
-
-\textbf{CLINC150} is a dataset designed for task-oriented systems with 23,700 queries that are short and unstructured for 150 intents, in the same style made by real users through crowdsourcing\cite{larson2019evaluation}.
-Here, we sample 5, 10 and 15 training data points for each intent class label by random sampling for our experimental setup.
-
-\textbf{BANKING77} is a intent detection dataset for bank customer services.
-The raw dataset contains 13,084 data points for 77 class labels\cite{casanueva2020efficient}.
-Here, we sample 5, 10, 15, 20 training data points for each class label by random sampling for our experimental setup.
-
 \subsection{Baselines}
@@
 \textbf{Group 1: single-task classification model.} This group of baseline models are based on the network structure for classification model shown in \ref{Fig.1.sub.1}.
-As for non-pretrained neural network, we choose TextCNN\cite{kim2014convolutional} as a representative baseline.
 As for the pretrained model, we choose RoBERTa, BERT and ALBERT, all of which are among the most powerful pretrained models that achieve outstanding results in many NLP tasks, in our experimental setting.
 Since we apply RoBERTa in our SFC system, we naturally adopt single-task classification model based on RoBERTa-large and RoBERTa-base as our baseline models.
-Besides, we also adopt the recently released baseline pre-trained model ALBERT-xxlarge\cite{lan2019albert} for comparison.
+Besides, we also adopt the baseline pre-trained model BERT-large\cite{devlin2018bert} and recently released ALBERT-xxlarge\cite{lan2019albert} for comparison.
 Since we use different few-shot settings from \cite{casanueva2020efficient} for those intent detection datasets, we also use BERT-large tuned on our few-shot settings as an essential reference for experimental results.
@@
 \hline
-\multicolumn{1}{|c|}{\multirow{2}*{ITG}}& 2-stage SFC & - & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
+\multicolumn{1}{|c|}{\multirow{2}*{ITG}}& 2-stage SFC & 0.05 & $0.8124$ & 0.05 & 0.05 & 0.05\tabularnewline
 \cline{2-7}
-\multicolumn{1}{|c|}{} & Hierarchical SFC & - & $0.8114$ & - & - & $0.7826$\tabularnewline
+\multicolumn{1}{|c|}{} & Hierarchical SFC & 0.05 & $0.8114$ & 0.05 & 0.05 & 0.05\tabularnewline
 \hline
-\multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& 2-stage SFC & - & $0.7364$ & - & - & -\tabularnewline
+\multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& 2-stage SFC & 0.05 & $0.7364$ & 0.05 & 0.05 & 0.05\tabularnewline
 \cline{2-7}
-\multicolumn{1}{|c|}{} & Hierarchical SFC & - & $0.7445$ & - & - & -\tabularnewline
+\multicolumn{1}{|c|}{} & Hierarchical SFC & 0.05 & $0.7445$ & 0.05 & 0.05 & 0.05\tabularnewline
 \hline
@@
 
-\textbf{Comparison among SFC variants.} First, we turn to compare among the four SFC variants shown in Table \ref{tbe:table2} to analyze the improvement brought by multi-task and hierarchical joint-model structure.
+First, we turn to compare among the four SFC variants.
 We conduct ablation experiments to study the benefits brought by multi-task training by comparing multi-task 2-stage SFC with single-task 2-stage SFC.
@@
 
-\textbf{Analysis under few-shot scenarios.} Next, we analyze the overall improvement trend of SFC under various few-shot settings.
+Next, we analyze the overall improvement trend of SFC under various few-shot settings.
 Our main focus is to study chatbot building in common situation during real-world application where only a few sample sentences are available for each class.
@@
 Our hierarchical SFC can achieve +4.97 percents average improvements over RoBERTa-large classification model in the most extreme few-shot setting with only 5 training samples per class.
-This observation indicates that SFC is especially suitable for being applied during the initial stage of building task-specific chatbot system, where the amount of data sample for each class label is extremely scarce.
 
-\textbf{Fusion of classification and similarity model.} Then, we begin to compare the general performance of SFC with single-task classification and similarity baselines.
-As for the classification model, hierarchical SFC outperforms TextCNN by +37.99 percents, ALBERT-xxlarge by +17.87 percents\footnote{We found that the performance of ALBERT.xxlarge is extremely unstable for classification task.
-Here, we did multiple run with different settings of parameters such as learning rate and batch size for each dataset, and record the best result we can obtain in Table \ref{tbe:table2}.}, BERT-large by +9.81 percents, RoBERTa-base by +4.52 percents, RoBERTa-large by +2.47 percents on average F-score over 5 datasets.
-In this way, we can see that RoBERTa is the best baseline pre-trained model for the low-resource text classification task we are studying.
-As for the similarity model, we only choose the strongest pretrained model RoBERTa-large as our baseline, and hierarchical SFC achieves the improvement of +7.81 percents on average.
-Moreover, hierarchical SFC's result on 2 datasets without data sampling for few-shot settings, which are ITG and Amazon-670k, are also 1.24 and 2.89 percents higher than Roberta-large classification model, and are 6.96 and 10.77 percents higher than Roberta-large similarity model.
+Then, we begin to compare the general performance of SFC with classification model and similarity model baselines.
+As for the classification model, hierarchical SFC outperforms BERT-large by +9.81 percents, ALBERT-xxlarge by 4 percents, RoBERTa-large by +2.47 percents, RoBERTa-base by +4.52 percents on average F-score for 5 datasets.
+In this way, we can see that RoBERTa is the best pre-trained model for the low-resource text classification task we are studying.
+As for the similarity model, we only choose the strongest pretrained model RoBERTa-large as our baseline, and hierarchical SFC achieves the improvement of 3 percents on average.
+Moreover, hierarchical SFC's result on 2 datasets without few-shot settings, which are ITG and Amazon-670k, are also 1.24 percents and 2.89 percents higher than Roberta-large classification model.
 These improvements illustrate that putting classification model and similarity model at different network layers to cooperate with each other is a successful design of hierarchical network structure for joint model, which enables these two models assist each other for better overall results.
 
-\textbf{Settings of hyperparameters.} Finally, we analyze the effect brought by different settings of hyperparameters, see Table \ref{tbe:table3}.
+Finally, we analyze the effect brought by different settings of hyperparameters, see Table \ref{tbe:table3}.
 We conduct experiments on 5 different settings of hyperparameters, which are the number of candidate class number $K$ and the number of sentence pairs $P$ for each class, on ITG and Amazon-670K datasets to find the most suitable setting of these 2 hyperparameters.

### 2020-09-01 chatbot_classification/aaai_2021/paper.tex
modified:   paper.tex

@@
   \begin{abstract}
-    Task-specific  chatbot  systems has gained many important applications, such
-    as  Siri, Google home, customer service systems to allievaite human's labor.
-    In  this  kind  of  systems, one of the core problems is the accurate detection of
-    intention  of  a  user's input. It is then mapped into a predefined chatting
-    logic  graph,  and the chatbot can return reasonable answers easily. This is
-    the  main  difference from a free chatbot. The intention detection, assuming
-    only  one  intention  in  a  sentence,  can  be  modeled  as  a  short  text
-    classification  problem.  In  practice,  the  number  of  intentions  can be
-    hundreads of thousands, as opposed to quite limited in the tradiational text
-    classification  problem,  and  the  labeled  data  is not trivial to acquire
-    plenty,  generally  10  to 20 per intention. Then, how to train an efficient
-    model  in such a resource-intensive practical application in a new domain is
-    critical.  In  this  work, we propose a novel model, called similairty model
-    fused with classification Model (SFC), which combines a classification model
-    and  a  similairty  model,  and  borrows the power of multi-task training as
-    well.  We  conduct extensive experiments on 4 public and 1 private datasets.
-    The  experimental  results  show  that our new model outperforms very strong
-    baselines, BERT, RoBERTa and ALBERT based pretrained models by 2 percentages
-    in average accuracy.
+    Task-specific  chatbot systems have gained many important applications, such
+    as  Siri,  Google home, and customer service systems. In these applications,
+    one  of  the  core  problems is the intention detection from a user's input.
+    Then,  the  intention  with  its  associated  information  is  mapped into a
+    predefined dialog logic graph, and the chatbot returns corresponding answer.
+    This  is  the  main  difference  from  a  free chatbot system. The intention
+    detection,  assuming  only  one  intention  in  a  user's input here, can be
+    modeled  as  a  short  text  classification.  In  practice,  the  number  of
+    intentions  can  be hundreds of thousands, as opposed to a few number in the
+    traditional text classification problem; enough training data is not trivial
+    to be filtered out and labeled from tons of raw user logs with miscellaneous
+    information, and generally only 10 to 20 samples per intention are available
+    in  the  early  stage.  Then,  how  to  train  an  efficient model in such a
+    practical  and important application is critical. In this work, we propose a
+    novel  model, called similarity model fused with classification Model (SFC),
+    which  combines  a  classification  model  and  a similarity model, and also
+    borrows  the  power  of  multi-task  training  as well. We conduct extensive
+    experiments  on  4  public  and 1 private datasets. The experimental results
+    show that our new model outperforms very strong baselines, BERT, RoBERTa and
+    ALBERT based pretrained models by 2 percentages in average accuracy.
 

### 2020-09-05 chatbot_classification/aaai_2021/paper.tex
update experimental results and analysis

@@
   \begin{abstract}
-    Task-specific  chatbot systems have gained many important applications, such
-    as  Siri,  Google home, and customer service systems. In these applications,
-    one  of  the  core  problems is the intention detection from a user's input.
-    Then,  the  intention  with  its  associated  information  is  mapped into a
-    predefined dialog logic graph, and the chatbot returns corresponding answer.
-    This  is  the  main  difference  from  a  free chatbot system. The intention
-    detection,  assuming  only  one  intention  in  a  user's input here, can be
-    modeled  as  a  short  text  classification.  In  practice,  the  number  of
-    intentions  can  be hundreds of thousands, as opposed to a few number in the
-    traditional text classification problem; enough training data is not trivial
-    to be filtered out and labeled from tons of raw user logs with miscellaneous
-    information, and generally only 10 to 20 samples per intention are available
-    in  the  early  stage.  Then,  how  to  train  an  efficient model in such a
-    practical  and important application is critical. In this work, we propose a
-    novel  model, called similarity model fused with classification Model (SFC),
-    which  combines  a  classification  model  and  a similarity model, and also
-    borrows  the  power  of  multi-task  training  as well. We conduct extensive
-    experiments  on  4  public  and 1 private datasets. The experimental results
-    show that our new model outperforms very strong baselines, BERT, RoBERTa and
-    ALBERT based pretrained models by 2 percentages in average accuracy.
+    Task-specific  chatbot  systems has gained many important applications, such
+    as  Siri, Google home, customer service systems to allievaite human's labor.
+    In  this  kind  of  systems, one of the core problems is the accurate detection of
+    intention  of  a  user's input. It is then mapped into a predefined chatting
+    logic  graph,  and the chatbot can return reasonable answers easily. This is
+    the  main  difference from a free chatbot. The intention detection, assuming
+    only  one  intention  in  a  sentence,  can  be  modeled  as  a  short  text
+    classification  problem.  In  practice,  the  number  of  intentions  can be
+    hundreads of thousands, as opposed to quite limited in the tradiational text
+    classification  problem,  and  the  labeled  data  is not trivial to acquire
+    plenty,  generally  10  to 20 per intention. Then, how to train an efficient
+    model  in such a resource-intensive practical application in a new domain is
+    critical.  In  this  work, we propose a novel model, called similairty model
+    fused with classification Model (SFC), which combines a classification model
+    and  a  similairty  model,  and  borrows the power of multi-task training as
+    well.  We  conduct extensive experiments on 4 public and 1 private datasets.
+    The  experimental  results  show  that our new model outperforms very strong
+    baselines, BERT, RoBERTa and ALBERT based pretrained models by 2 percentages
+    in average accuracy.
 
@@
   \section{Methodology}
-  In  this  section,  we  will  describe a system of similarity model fused with
+  In  this  section,  we  will  describe our proposed system of similarity model fused with
   classification  model,  named  as  SFC, in detail. We come up with 2 different
@@
 
-  The   detailed   network   structure   of   two-stage   SFC  is  shown  in  Fig.
-  \ref{fig:ver.1.3}.  It  is  composed  with  2  separate  stages  in  charge of
-  different  jobs. In stage 1, we can use any auxiliary model or tool to provide
-  top-K  most  related class labels for sampling sentence pairs of both positive
-  samples  and negative samples for stage 2. Suppose we have a training data set
+  The network   structure   of   two-stage   SFC  is  composed  with  2  separate  stages  in  charge of
+  different  jobs. In stage 1, we can use any auxiliary text classification model or tool to provide
+  top-K  most  related class labels. These selected class labels will later be used to sample sentence pairs of both positive
+  samples  and negative samples for stage 2.
+Then, in stage 2, we will use sentence pair similarity model to identify the class label with strongest semantic similarity to the user input sentence.
+Suppose we have a training dataset
   $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$  of  $N$ data points, in which $x_{i}$
   is the user input query and $y_{i}$ is a single class label from a class label
-  set  of  $C$  classes  in total. If we want to generate sentence pair data set
+  set  of  $C$  classes  in total. If we want to generate sentence pair dataset
   $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$,   where   $(x,   x')_{j}$  is
@@
   \end{align}
-  directly  from  original data set $\mathcal{D}$ without any sampling strategy,
+  directly  from  original dataset $\mathcal{D}$ without any sampling strategy,
   then  $\mathcal{D'}$  will  have  $M=N^2$ data points of sentence pairs, which
@@
   sample  $P$  sentences  $\{x'_{0},x'_{1}, \dots, x'_{P}\}$ with the same class
-  label as $y_{i}$ from data set $\mathcal{D}$ to form the set of sentence pairs
+  label as $y_{i}$ from dataset $\mathcal{D}$ to form the set of sentence pairs
   with   positive   label  $\mathcal{P'}_{i}=\{[(x_{i},  x'_{0}),  1],  [(x_{i},
@@
 
-  In  this  way,  we  can generate the sentence pair data set $\mathcal{D'}$ for
+  In  this  way,  we  can generate the sentence pair dataset $\mathcal{D'}$ for
   stage  2 based on the top-K class label set $\mathcal{C'}$ provided by stage 1
@@
 
-  As for  stage  1,  our  SFC  system  can adapt to any auxiliary model or even
+  As for  stage  1,  our  two-stage SFC  system  can adapt to any auxiliary model or even
   searching  tool  based  on  Term Frequency-Inverse Document Frequency (TF-IDF)
-  retrieval.  In  this  paper,  however,  we  choose to fine-tune RoBERTa on our
-  task-specific  data set $\mathcal{D}$ by adding a softmax classifier on top of
-  it,  the  same  as  the  structure shown in Fig. \ref{Fig.1.sub.1}, for better
+  retrieval.  In  this  paper,  however,  we  choose to fine-tune pretrained model such as RoBERTa on our
+  task-specific  dataset $\mathcal{D}$ by adding a softmax classifier on top of
+  it for better
   overall  performance.  According  to  our  experimental  result,  RoBERTa  can
-  guarantee  that  approximately  95\%  ground  truth label be included in top-5
-  candidate  class  labels  with  highest  probability after being fine-tuned on
-  task-specific  data set with experimental result measured by F-score at around
-  0.75.  So  we use RoBERTa as encoder of classification model in our setting at
+  guarantee  that  approximately  95\%  ground  truth labels be included in top-5
+  candidate  class  labels  with  highest  probability if it has been fine-tuned on
+  task-specific  dataset and can obtain a well performance measured by F-score over
+  0.75 on this dataset.  So  we use RoBERTa as the encoder of classification model in our setting at
   stage 1 to ensure low limitation for the performance of stage 2.
@@
   For single-sentence text classification tasks, given a data point $x_{i}$ with
-  class  label  $y_{i}$  from  data  set  $\mathcal{D}$, RoBERTa takes the final
+  class  label  $y_{i}$  from  dataset  $\mathcal{D}$, RoBERTa takes the final
   hidden  state  $h_{i}$  of the first token [CLS] as the representation for the
@@
 
-  As for  stage 2, we also choose RoBERTa as the encoder for sentence pairs, as
-  shown  in Fig. \ref{fig:ver.1.3}. Before sending sentence pairs to Roberta, we
+  As for  stage 2, we also choose RoBERTa as the encoder for the sentence pair similarity model. Before sending sentence pairs to Roberta, we
   pack  sentence  pairs  into a single sequence and separate them with a special
@@
   Due  to  the  fact that sentence pairs within the same class is much less than
-  sentence  pairs  from  different  classes,  the  data  set  $\mathcal{D'}$  is
+  sentence  pairs  from  different  classes,  the  dataset  $\mathcal{D'}$  is
   imbalanced.  Therefore, we will accommodate a weight variable $w^S = [K-1, 1]$
@@
 
-  As  for top-K classification task, it shares the same sentence-pair similarity
+  As  for top-K classification task, it shares the same sentence pair similarity
   model   structure  with  task  1.  The  only  difference  is  that  we  add  a
-  task-specific  average  pooling  layer,  shown  in  Fig.  \ref{fig:ver.1.3} to
+  task-specific  average  pooling  layer,  shown  in  Fig.  \ref{fig:framework} to
   implement the classification task based on sentence-pair model.
@@
   $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting.
+The reason for giving task 2 relatively more weights is that according to the ablation experiments we did in Section \ref{sec:exp}, task 2 contributes more to the overall performance.
 
@@
     \begin{centering}
-
+      \scalebox{0.9}{
       \begin{tabular}{|c|c|c|c|c|c|}
         \hline 
-        Dataset & Domain & \#Class & \#Samples & \#Samples/Class & Experimental Settings\tabularnewline
+        \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} & \textbf{\#Samples} & \textbf{\#Samples/Class} & \textbf{Experimental Settings}\tabularnewline
         \hline 
@@
         \hline 
-        HWU64 & intention detection & 64 & [320, 640, 960, 1280] & [5, 10, 15, 20] & data sampling\tabularnewline
+        HWU64 & intention detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
         \hline 
-        CLINC150 & intention detection & 150 & [750, 1500, 2250] & [5, 10, 15] & data sampling\tabularnewline
+        CLINC150 & intention detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
         \hline 
-        BANKING77 & intention detection & 77 & [385, 770, 1155, 1540] & [5, 10, 15, 20] & data sampling\tabularnewline
+        BANKING77 & intention detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
         \hline 
       \end{tabular}
+      }
     \par
@@
   \section{Experiments}
+  \label{sec:exp}
+
   In  this  section,  we  conduct  extensive  experiments  over  5 task-specific
   datasets  to  evaluate  the  performance  of  our  proposed SFC system and the
-  effectiveness  of  the  methodology  of  multi-task  learning  and hierachical
+  effectiveness  of  the  methodology  of  multi-task  learning  and
   joint-model structure under low-data settings.
@@
   classification  problem  under  task-specific conversational chatbot scenario.
-  Therefore,  we keep all the dataset under low-resource chatbot corpus setting,
+  Therefore,  we did experiments on datasets under low-resource chatbot corpus setting,
   which  is a large number of class labels (50-250) with a few examples(5-20) in
@@
   when the raw datasets are oversized, see Table \ref{tbe:dataset statistic}.
+Besides, we also did extensive experiments with larger scale datasets with 30-50 examples per class to test the stability of our proposed SFC system under normal-size data settings, also see Table \ref{tbe:dataset statistic}.
 
@@
   containing  670,091  class  labels,  285,176  training samples and 150875 test
-  samples \cite{bhatia2016extreme}.  As  the  data  set  contains  multiple class
+  samples \cite{bhatia2016extreme}.  As  the  dataset  contains  multiple class
   labels  per  training sample, we keep only the first class label for each data
@@
     \begin{centering}
-      \scalebox{0.8}{
-        \begin{tabular}{|c|ccc|cccc|cccc|c|c|}
+      \scalebox{0.55}{
+        \begin{tabular}{|c|cccccc|cccccc|cccccc|c|c|}
           \hline 
-          \multicolumn{1}{|c|}{\multirow{2}*{\textbf{Models}} }& \multicolumn{3}{c|}{\textbf{CLINC150}}& \multicolumn{4}{c|}{\textbf{BANKING77}}& \multicolumn{4}{c|}{\textbf{HWU64}}& \ \ \ \textbf{ITG} \ \ \ & \textbf{Amazon-670k}\tabularnewline
-          \cline{2-14}
-          \multicolumn{1}{|c|}{} & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & \textbf{Full} & \textbf{Full}\tabularnewline
+          \multicolumn{1}{|c|}{\multirow{2}*{\textbf{Models}} }& \multicolumn{6}{c|}{\textbf{CLINC150}}& \multicolumn{6}{c|}{\textbf{BANKING77}}& \multicolumn{6}{c|}{\textbf{HWU64}}& \ \ \ \textbf{ITG} \ \ \ & \textbf{Amazon-670k}\tabularnewline
+          \cline{2-21}
+          \multicolumn{1}{|c|}{} & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & \textbf{Full} & \textbf{Full}\tabularnewline
           \hline
-          TextCNN & \multirow{2}*{$0.5318$} & \multirow{2}*{$0.6963$} & \multirow{2}*{$0.7609$} & \multirow{2}*{$0.4408$} & \multirow{2}*{$0.6436$} & \multirow{2}*{$0.7366$} & \multirow{2}*{$0.7918$} & \multirow{2}*{$0.3112$} & \multirow{2}*{$0.4007$} & \multirow{2}*{$0.4823$} & \multirow{2}*{$0.5272$} & \multirow{2}*{$0.6624$} & \multirow{2}*{$0.4401$}\tabularnewline
-          (classification) & & & & & & & & & & & & &\tabularnewline
+          TextCNN & \multirow{2}*{$0.5318$} & \multirow{2}*{$0.6963$} & \multirow{2}*{$0.7609$} & \multirow{2}*{$0.8142$} & \multirow{2}*{$0.8526$} & \multirow{2}*{$0.8867$} & \multirow{2}*{$0.4408$} & \multirow{2}*{$0.6436$} & \multirow{2}*{$0.7366$} & \multirow{2}*{$0.7918$} & \multirow{2}*{$0.8228$} & \multirow{2}*{$0.8619$} & \multirow{2}*{$0.3112$} & \multirow{2}*{$0.4007$} & \multirow{2}*{$0.4823$} & \multirow{2}*{$0.5272$} & \multirow{2}*{$0.5782$} & \multirow{2}*{$0.6262$} & \multirow{2}*{$0.6624$} & \multirow{2}*{$0.4401$}\tabularnewline
+          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
           \hline
-          LEAM & \multirow{2}*{$0.7514$} & \multirow{2}*{$0.8203$} & \multirow{2}*{$0.8612$} & \multirow{2}*{$0.5422$} & \multirow{2}*{$0.7812$} & \multirow{2}*{$0.8129$} & \multirow{2}*{$0.8280$} & \multirow{2}*{$0.4545$} & \multirow{2}*{$0.5554$} & \multirow{2}*{$0.5936$} & \multirow{2}*{$0.6599$} & \multirow{2}*{$0.7086$} & \multirow{2}*{$0.6091$}\tabularnewline
-          (classification) & & & & & & & & & & & & &\tabularnewline
+          LEAM & \multirow{2}*{$0.7514$} & \multirow{2}*{$0.8203$} & \multirow{2}*{$0.8612$} & \multirow{2}*{$0.8802$} & \multirow{2}*{$0.9010$} & \multirow{2}*{$0.9180$} & \multirow{2}*{$0.5422$} & \multirow{2}*{$0.7812$} & \multirow{2}*{$0.8129$} & \multirow{2}*{$0.8280$} & \multirow{2}*{$0.8610$} & \multirow{2}*{$0.8727$} & \multirow{2}*{$0.4545$} & \multirow{2}*{$0.5554$} & \multirow{2}*{$0.5936$} & \multirow{2}*{$0.6599$} & \multirow{2}*{$0.6855$} & \multirow{2}*{$0.7046$} & \multirow{2}*{$0.7086$} & \multirow{2}*{$0.6091$}\tabularnewline
+          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
           \hline
-          BERT-large & \multirow{2}*{$0.8080$} & \multirow{2}*{$0.8904$} & \multirow{2}*{$0.9265$} & \multirow{2}*{$0.578$} & \multirow{2}*{$0.8004$} & \multirow{2}*{$0.8518$} & \multirow{2}*{$0.8827$} & \multirow{2}*{$0.4711$} & \multirow{2}*{$0.5963$} & \multirow{2}*{$0.6342$} & \multirow{2}*{$0.7010$} & \multirow{2}*{$0.7485$} & \multirow{2}*{$0.6658$}\tabularnewline
-          (classification) & & & & & & & & & & & & &\tabularnewline
+          BERT-large & \multirow{2}*{$0.8080$} & \multirow{2}*{$0.8904$} & \multirow{2}*{$0.9265$} & \multirow{2}*{$0.9334$} & \multirow{2}*{$0.9497$} & \multirow{2}*{$0.9595$} & \multirow{2}*{$0.5780$} & \multirow{2}*{$0.8004$} & \multirow{2}*{$0.8518$} & \multirow{2}*{$0.8827$} & \multirow{2}*{$0.8858$} & \multirow{2}*{$0.8982$} & \multirow{2}*{$0.4711$} & \multirow{2}*{$0.5963$} & \multirow{2}*{$0.6342$} & \multirow{2}*{$0.7010$} & \multirow{2}*{$0.7117$} & \multirow{2}*{$0.7424$} & \multirow{2}*{$0.7485$} & \multirow{2}*{$0.6658$}\tabularnewline
+          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
           \hline
-          ALBERT-xxlarge & \multirow{2}*{$0.8497$} & \multirow{2}*{$0.9008$} & \multirow{2}*{$0.9296$} & \multirow{2}*{$0.5549$} & \multirow{2}*{$0.7981$} & \multirow{2}*{$0.8231$} & \multirow{2}*{$0.8530$} & \multirow{2}*{$0.4879$} & \multirow{2}*{$0.6116$} & \multirow{2}*{$0.6135$} & \multirow{2}*{$0.6996$} & \multirow{2}*{$0.7253$} & \multirow{2}*{$0.6893$}\tabularnewline
-          (classification) & & & & & & & & & & & & &\tabularnewline
+          ALBERT-xxlarge & \multirow{2}*{$0.8497$} & \multirow{2}*{$0.9008$} & \multirow{2}*{$0.9296$} & \multirow{2}*{$0.9297$} & \multirow{2}*{$0.9466$} & \multirow{2}*{$0.9578$} & \multirow{2}*{$0.5549$} & \multirow{2}*{$0.7981$} & \multirow{2}*{$0.8231$} & \multirow{2}*{$0.8530$} & \multirow{2}*{$0.8571$} & \multirow{2}*{$0.9096$} & \multirow{2}*{$0.4879$} & \multirow{2}*{$0.6116$} & \multirow{2}*{$0.6135$} & \multirow{2}*{$0.6996$} & \multirow{2}*{$0.7094$} & \multirow{2}*{$0.7376$} & \multirow{2}*{$0.7253$} & \multirow{2}*{$0.6893$}\tabularnewline
+          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
           \hline
-          RoBERTa-base & \multirow{2}*{$0.8732$} & \multirow{2}*{$0.9254$} & \multirow{2}*{$0.9363$} & \multirow{2}*{$0.7305$} & \multirow{2}*{$0.8654$} & \multirow{2}*{$0.8808$} & \multirow{2}*{$0.9080$} & \multirow{2}*{$0.5831$} & \multirow{2}*{$0.6790$} & \multirow{2}*{$0.7064$} & \multirow{2}*{$0.7100$} & \multirow{2}*{$0.7734$} & \multirow{2}*{$0.6708$}\tabularnewline
-          (classification) & & & & & & & & & & & & &\tabularnewline
+          RoBERTa-base & \multirow{2}*{$0.8732$} & \multirow{2}*{$0.9254$} & \multirow{2}*{$0.9363$} & \multirow{2}*{$0.9482$} & \multirow{2}*{$0.9558$} & \multirow{2}*{$0.9637$} & \multirow{2}*{$0.7305$} & \multirow{2}*{$0.8654$} & \multirow{2}*{$0.8808$} & \multirow{2}*{$0.9080$} & \multirow{2}*{$0.9061$} & \multirow{2}*{$0.9293$} & \multirow{2}*{$0.5831$} & \multirow{2}*{$0.6790$} & \multirow{2}*{$0.7064$} & \multirow{2}*{$0.7100$} & \multirow{2}*{$0.7320$} & \multirow{2}*{$0.7472$} & \multirow{2}*{$0.7734$} & \multirow{2}*{$0.6708$}\tabularnewline
+          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
           \hline
-          RoBERTa-large & \multirow{2}*{$0.8974$} & \multirow{2}*{$0.9372$} & \multirow{2}*{$0.9508$} & \multirow{2}*{$0.7690$} & \multirow{2}*{$0.8728$} & \multirow{2}*{$0.8966$} & \multirow{2}*{$0.9099$} & \multirow{2}*{$0.6044$} & \multirow{2}*{$0.7002$} & \multirow{2}*{$0.7129$} & \multirow{2}*{$0.7436$} & \multirow{2}*{$0.7990$} & \multirow{2}*{$0.7156$}\tabularnewline
-          (classification) & & & & & & & & & & & & &\tabularnewline
+          RoBERTa-large & \multirow{2}*{$0.8974$} & \multirow{2}*{$0.9372$} & \multirow{2}*{$0.9508$} & \multirow{2}*{$0.9584$} & \multirow{2}*{$0.9621$} & \multirow{2}*{$0.9733$} & \multirow{2}*{$0.7690$} & \multirow{2}*{$0.8728$} & \multirow{2}*{$0.8966$} & \multirow{2}*{$0.9099$} & \multirow{2}*{$0.9227$} & \multirow{2}*{$0.9313$} & \multirow{2}*{$0.6044$} & \multirow{2}*{$0.7002$} & \multirow{2}*{$0.7129$} & \multirow{2}*{$0.7436$} & \multirow{2}*{$0.7493$} & \multirow{2}*{$0.7678$} & \multirow{2}*{$0.7990$} & \multirow{2}*{$0.7156$}\tabularnewline
+          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
           \hline
-          RoBERTa-large & \multirow{2}*{$0.8266$} & \multirow{2}*{$0.8861$} & \multirow{2}*{$0.9023$} & \multirow{2}*{$0.757$} & \multirow{2}*{$0.8476$} & \multirow{2}*{$0.8614$} & \multirow{2}*{$0.8743$} & \multirow{2}*{$0.5425$} & \multirow{2}*{$0.6164$} & \multirow{2}*{$0.6503$} & \multirow{2}*{$0.6729$} & \multirow{2}*{$0.7418$} & \multirow{2}*{$0.6362$}\tabularnewline
-          (similarity) & & & & & & & & & & & & &\tabularnewline
+          RoBERTa-large & \multirow{2}*{$0.8266$} & \multirow{2}*{$0.8861$} & \multirow{2}*{$0.9023$} & \multirow{2}*{$0.9084$} & \multirow{2}*{$0.9090$} & \multirow{2}*{$0.9407$} & \multirow{2}*{$0.757$} & \multirow{2}*{$0.8476$} & \multirow{2}*{$0.8614$} & \multirow{2}*{$0.8743$} & \multirow{2}*{$0.8749$} & \multirow{2}*{$0.8980$} & \multirow{2}*{$0.5425$} & \multirow{2}*{$0.6164$} & \multirow{2}*{$0.6503$} & \multirow{2}*{$0.6729$} & \multirow{2}*{$0.6947$} & \multirow{2}*{$0.7231$} & \multirow{2}*{$0.7418$} & \multirow{2}*{$0.6362$}\tabularnewline
+          (similarity) & & & & & & & & & & & & & & & & & & & &\tabularnewline
           \hline
-          two-stage SFC & \multirow{2}*{$0.8979$} & \multirow{2}*{$0.9457$} & \multirow{2}*{$0.9517$} & \multirow{2}*{$0.7975$} & \multirow{2}*{$0.8818$} & \multirow{2}*{$0.8962$} & \multirow{2}*{$0.9109$} & \multirow{2}*{$0.6477$} & \multirow{2}*{$0.7055$} & \multirow{2}*{$0.7200$} & \multirow{2}*{$0.7232$} & \multirow{2}*{$0.7972$} & \multirow{2}*{$0.7189$}\tabularnewline
-          (task1 only) & & & & & & & & & & & & &\tabularnewline
+          2-stage SFC & \multirow{2}*{$0.8979$} & \multirow{2}*{$0.9457$} & \multirow{2}*{$0.9517$} & \multirow{2}*{$0.9591$} & \multirow{2}*{$0.9610$} & \multirow{2}*{$0.9664$} & \multirow{2}*{$0.7975$} & \multirow{2}*{$0.8818$} & \multirow{2}*{$0.8962$} & \multirow{2}*{$0.9109$} & \multirow{2}*{$0.9187$} & \multirow{2}*{$0.9198$} & \multirow{2}*{$0.6477$} & \multirow{2}*{$0.7055$} & \multirow{2}*{$0.7200$} & \multirow{2}*{$0.7232$} & \multirow{2}*{$0.7484$} & \multirow{2}*{$0.7653$} & \multirow{2}*{$0.7972$} & \multirow{2}*{$0.7189$}\tabularnewline
+          (task1 only) & & & & & & & & & & & & & & & & & & & &\tabularnewline
           \hline
-          two-stage SFC & \multirow{2}*{$0.9162$} & \multirow{2}*{$0.9424$} & \multirow{2}*{$0.9530$} & \multirow{2}*{$0.7997$} & \multirow{2}*{$0.8823$} & \multirow{2}*{$0.8945$} & \multirow{2}*{$0.9123$} & \multirow{2}*{$0.6498$} & \multirow{2}*{$0.6980$} & \multirow{2}*{$0.7202$} & \multirow{2}*{$0.7358$} & \multirow{2}*{$0.8020$} & \multirow{2}*{$0.7311$}\tabularnewline
-          (task2 only) & & & & & & & & & & & & &\tabularnewline
+          2-stage SFC & \multirow{2}*{$0.9162$} & \multirow{2}*{$0.9424$} & \multirow{2}*{$0.9530$} & \multirow{2}*{$0.9617$} & \multirow{2}*{$0.9633$} & \multirow{2}*{$0.9690$} & \multirow{2}*{$0.7997$} & \multirow{2}*{$0.8823$} & \multirow{2}*{$0.8945$} & \multirow{2}*{$0.9123$} & \multirow{2}*{$0.9236$} & \multirow{2}*{$0.9317$} & \multirow{2}*{$0.6498$} & \multirow{2}*{$0.6980$} & \multirow{2}*{$0.7202$} & \multirow{2}*{$0.7358$} & \multirow{2}*{$0.7498$} & \multirow{2}*{$0.7657$} & \multirow{2}*{$0.8020$} & \multirow{2}*{$0.7311$}\tabularnewline
+          (task2 only) & & & & & & & & & & & & & & & & & & & &\tabularnewline
           \hline
-          two-stage SFC & \multirow{2}*{$0.9167$} & \multirow{2}*{$0.9456$} & \multirow{2}*{$0.9571$} & \multirow{2}*{$0.7954$} & \multirow{2}*{$0.8854$} & \multirow{2}*{$0.8931$} & \multirow{2}*{$0.9192$} & \multirow{2}*{$0.6525$} & \multirow{2}*{$0.7001$} & \multirow{2}*{$0.7168$} & \multirow{2}*{$0.7476$} & \multirow{2}*{$\textbf{0.8124}$} & \multirow{2}*{$0.7364$}\tabularnewline
-          (task1 + task2) & & & & & & & & & & & & &\tabularnewline
+          2-stage SFC & \multirow{2}*{$0.9167$} & \multirow{2}*{$0.9456$} & \multirow{2}*{$0.9571$} & \multirow{2}*{$0.9638$} & \multirow{2}*{$0.9658$} & \multirow{2}*{$0.9753$} & \multirow{2}*{$0.8135$} & \multirow{2}*{$0.8854$} & \multirow{2}*{$0.8931$} & \multirow{2}*{$0.9192$} & \multirow{2}*{$0.9257$} & \multirow{2}*{$0.9339$} & \multirow{2}*{$0.6525$} & \multirow{2}*{$0.7092$} & \multirow{2}*{$0.7168$} & \multirow{2}*{$0.7476$} & \multirow{2}*{$0.7519$} & \multirow{2}*{$0.7696$} & \multirow{2}*{$\textbf{0.8124}$} & \multirow{2}*{$0.7364$}\tabularnewline
+          (task1 + task2) & & & & & & & & & & & & & & & & & & & &\tabularnewline
           \hline
-          \multirow{2}*{joint SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline
-          & & & & & & & & & & & & &\tabularnewline
+          \multirow{2}*{Joint SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.9669}$} & \multirow{2}*{$\textbf{0.9712}$} & \multirow{2}*{$\textbf{0.9821}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.9323}$} & \multirow{2}*{$\textbf{0.9463}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$\textbf{0.7593}$} & \multirow{2}*{$\textbf{0.7772}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline
+          & & & & & & & & & & & & & & & & & & & &\tabularnewline
           \hline
@@
     \caption{
-      F-scores  on five task-specific dataset for text classification in chatbot
-      under low resource. For ITG, we keep the full dataset. For Amazon-670k, we
-      randomly  sampled  250  classes  with  training sample numbers within 5-15
-      samples  per  class.  For  CLINC150,  BANKING77,  HWU64, we set up various
-      few-shot  settings  (5/10/15/20  samples per class) while keeping the test
-      set  to  be  fixed. The highest scores for each data setting are marked in
-      bold.
+        F-scores on five task-specific dataset for text classification in chatbot under low resource.
+For ITG, we keep the full dataset.
+For Amazon-670k, we randomly sampled 250 classes with training sample numbers within 5-15 samples per class.
+For CLINC150, BANKING77, HWU64, we set up various few-shot settings (5/10/15/20/30/50 samples per class) while keeping the test set to be fixed.
+The highest scores for each data setting are marked in bold.
     }
-
     \label{tbe:table2}
@@
   real-world  circumstances. Therefore, we experiment with the setups where only
-  5,  10,  15  and 20 training data points are available for each class label by
+  5,  10,  15, 20, 30 and 50 training data points are available for each class label by
   random sampling.
@@
   made  by real users through crowdsourcing \cite{larson2019evaluation}. Here, we
-  sample 5, 10 and 15 training data points for each intention class label by random
+  sample 5, 10, 15, 20, 30 and 50 training data points for each intention class label by random
   sampling for our experimental setup.
@@
   The    raw    dataset    contains    13,084   data   points   for   77   class
-  labels \cite{casanueva2020efficient}.  Here,  we  sample 5, 10, 15, 20 training
+  labels \cite{casanueva2020efficient}.  Here,  we  sample 5, 10, 15, 20, 30, and 50 training
   data  points  for  each  class  label  by random sampling for our experimental
@@
   \textbf{Group  1:  single-task  classification  model.} This group of baseline
-  models  are  based  on the network structure for classification model shown in
-  \ref{Fig.1.sub.1}.   As   for   non-pretrained   neural   network,  we  choose
+  models  are  based  on the network structure for classification model.   As   for   non-pretrained   neural   network,  we  choose
   TextCNN \cite{kim2014convolutional}  as  a  representative baseline. As for the
@@
   the       recently       released       baseline       pre-trained       model
-  ALBERT-xxlarge \cite{lan2019albert}  for  comparison.  Since  we  use different
-  few-shot   settings   from    \cite{casanueva2020efficient}  for  those
+  ALBERT-xxlarge \cite{lan2019albert}  for  comparison.  Since  we  use few-shot   settings   different from    that of \cite{casanueva2020efficient}  for  those
   intention
   detection  datasets,  we also use BERT-large tuned on our few-shot settings as
-  an essential reference for experimental results.
+  an essential reference baseline for experimental results.
 
   \textbf{Group  2: single-task similarity model.} This group of baseline models
-  are   based   on   network   structure   for   similarity   model   shown   in
-  \ref{Fig.1.sub.2}. We choose RoBERTa-large for the pretrained model part as an
+  are   based   on   network   structure   for   sentence pair similarity   model. We choose RoBERTa-large for the pretrained model part as an
   powerful baseline. But during the evaluation step, we use elastic search to do
   a  rough  filter  for  candidate  sentence  pairs  to  guarantee  a reasonable
-  inference time for each user query.
+  inference time for each user input query.
 
   \textbf{Group  3:  SFC  system with ablation study.} This group of baseline is
-  based  on  the network structure of two-stage SFC shown in \ref{fig:ver.1.3}. We
+  based  on  the network structure of two-stage SFC. We
   conduct  ablation study by introducing single task SFC system with only Task 1
@@
   model  set-up  in detail. The performance of each model is measured in F-score
-  on the fixed test set for each data set. The overall performance of SFC system
+  on the fixed test set for each dataset. The overall performance of SFC system
   is  better  than  all  the  competitive  single-model  baseline models on five
@@
   effectively  enhance the overall capability based on richer extracted semantic
-  information.  However  the  relative performance among all the variants of SFC
-  also  seems  to  depend  on  some  specific  charateristic  of  each data set.
-  Therefore,  we did the following more detailed analysis from several different
+  information.
+Furthermore, we also studied  the  relative performance among all the variants of SFC on  different data settings to explore the benefits brought by multi-task training and the joint-model structure.
+  With all the experimental results shown in Table \ref{tbe:table2},  we did the following more detailed analysis from several different
   aspect.
@@
   Table  \ref{tbe:table2}  that  two-stage  SFC  with  only  task 1 (sentence-pair
-  similarity task) degrades by 0.65 percent on average and two-stage SFC with only
-  task  2  (top-K  classification  task) degrades by 0.32 percent on average. The
+  similarity task) degrades by 0.80 percent on average and two-stage SFC with only
+  task  2  (top-K  classification  task) degrades by 0.45 percent on average. The
   degradation  indicates  that  training  with these 2 tasks together in SFC can
   effectively  help  the  sentence-pair  model  extract  more knowledge from the
-  limited  amount  of data. Besides, task 2 degrades 0.33 percent less than task
+  limited  amount  of data. Besides, task 2 degrades 0.35 percent less than task
   1.  This observation suggests that task 2 may play a relatively more important
@@
   $\mathcal{L}$.  Also, we can see that the joint SFC steadily outperforms
-  two-stage  SFC  on  5  diverse  datasets  by  1.17  percents  on  average.  This
+  two-stage  SFC  on  5  diverse  datasets  by  0.95  percents  on  average.  This
   observation  supports  the idea that the joint model structure can
@@
   results  for  the  3  diverse  intention detection datasets (ClINC150, BANKING77,
-  HWU64) under few-shot settings indicate that our proposed joint SFC can
+  HWU64) under few-shot settings(5-20 samples per class) indicate that our proposed joint SFC can
   achieve  2.47  percents  average  improvement  over  one  of the most powerful
-  baseline  models,  which  is  RoBERTa-large classification model, on all these
-  few-shot  settings. Moreover, the improvement in F-score becomes more and more
+  baseline  models,  which  is  RoBERTa-large classification model. Moreover, the improvement in F-score becomes more and more
   prominent  with the decrease of data sample number per class. Our joint
@@
   classification model in the most extreme few-shot setting with only 5 training
-  samples  per class. This observation indicates that SFC is especially suitable
-  for  being  applied during the initial stage of building task-specific chatbot
-  system,  where  the  amount  of  data sample for each class label is extremely
-  scarce.
+  samples  per class. This observation indicates that SFC is especially well-performed
+  when  being  applied during the initial stage of building task-specific chatbot
+  system,  where  the  amount  of  data sample for each class label is extremely scarce.
+Furthermore, our proposed joint SFC can also achieve 2.04 percents average improvement over RoBERTa-large classification model on all the data settings including the ones with large scale (30-50 samples per class).
+This experimental result indicates that joint SFC can still steadily outperforms single-task pretrained model baseline even if the data size grows bigger.
+But the improvement is still more prominent when the data is scarce, which makes SFC an excellent model for low-resource chatbot scenario.
 
@@
   joint  embedding  baseline  named as LEAM. As shown in Table \ref{tbe:table2},
-  joint  SFC outperforms LEAM by 14.25 percents on average F-score over 5
+  joint  SFC outperforms LEAM by 11.90 percents on average F-score over 5
   datasets.  Besides,  although the labels within the 3 diverse intention detection
@@
   semantic  summary  of  each intention, joint SFC still outperforms LEAM by
-  14.69  percents  on  average  F-score.  This  observation  indicates that it is
+  10.71  percents  on  average  F-score.  This  observation  indicates that it is
   usually  quite  hard  to  use  a  fixed  label  with  only  a few words as the
@@
   similarity  baselines.  As  for  the  classification  model,  joint SFC
-  outperforms    TextCNN    by   26.19   percents,   ALBERT-xxlarge   by   9.95
+  outperforms    TextCNN    by   21.52   percents,   ALBERT-xxlarge   by   7.99
   percents\footnote{We found that the performance of ALBERT.xxlarge is extremely
@@
   and  record  the  best  result  we  can  obtain  in  Table \ref{tbe:table2}.},
-  BERT-large  by  9.81 percents, RoBERTa-base by 4.52 percents, RoBERTa-large by
-  2.47 percents on average F-score over 5 datasets. In this way, we can see that
+  BERT-large  by  7.73 percents, RoBERTa-base by 3.79 percents, RoBERTa-large by
+  2.04 percents on average F-score over 5 datasets. In this way, we can see that
   RoBERTa  is  the  best  baseline  pre-trained  model for the low-resource text
@@
   choose  the  strongest  pretrained  model  RoBERTa-large  as our baseline, and
-  joint  SFC  achieves  the  improvement  of  7.81  percents  on average.
+  joint  SFC  achieves  the  improvement  of  7.09  percents  on average.
   Moreover,  joint  SFC's  result on 2 datasets without data sampling for
@@
   best   performing   model   on   5  diverse  experimental  datasets  for  text
-  classification  task  under  low-resource task-specific conversational chatbot
+  classification  task, especially when it's under  low-resource task-specific conversational chatbot
   scenario.

### 2020-09-05 chatbot_classification/aaai_2021/paper.tex
modified:   paper.tex   modified:   picture/picture4.key   modified:   picture/picture4.pdf

@@
   model  to  select top-K most possible labels for a input. This model can be an
-  elasticsearch  \cite{divya2013elasticsearch}  or  a  text classification model
+  elastic search  \cite{divya2013elasticsearch}  or  a  text classification model
   trained on current task-specific chatbot data. In the second stage, we build a
@@
     \item To  better  train such a system, we bring in multi-task training to obtain
-    expected performance.
+    reasonable performance.
 
@@
     datasets,  show  that  our  proposed  SFC joint system can achieve significant
-    improvements over strong baselines, especially in the low resource settings.
+    and consistent improvements over strong baselines, especially in the low resource settings.
   \end{enumerate}
@@
   \section{Methodology}
-  In  this  section,  we  will  describe our proposed system of similarity model fused with
-  classification  model,  named  as  SFC, in detail. We come up with 2 different
-  approaches  for  implementation  of SFC system, in which joint SFC is a
-  further improvement of two-stage SFC for better performance.
+  In  this  section,  we  will  describe our proposed system of similarity model
+  fused  with  classification  model,  named  as  SFC, in detail. We propose two
+  approaches  to  implement  the  SFC idea, two-stageg SFC, and its more compact
+  version called joint-SFC.
 
-  \subsection{two-stage SFC with multi-task learning}
+  \subsection{Two-stage SFC}
 
@@
 
-  \textbf{1.  positive  sentence pair sampling}: During the training process, we
-  have  to first make sure that the ground truth class label $y_{i}$ for $x_{i}$
-  is  within  the  candidate  class  label  set  $\mathcal{C'}$. If $y_{i}\notin
-  \mathcal{C'}$,  we  will manually add $y_{i}$ into $\mathcal{C'}$ by replacing
-  $c'_{K}$  with  $y_{i}$, since $c'_{K}$ is the least promising candidate label
-  according  to  the  auxiliary  model  in stage 1. Afterwards, we will randomly
-  sample  $P$  sentences  $\{x'_{0},x'_{1}, \dots, x'_{P}\}$ with the same class
-  label as $y_{i}$ from dataset $\mathcal{D}$ to form the set of sentence pairs
-  with   positive   label  $\mathcal{P'}_{i}=\{[(x_{i},  x'_{0}),  1],  [(x_{i},
-  x'_{1}),   1],   \dots,   [(x_{i},   x'_{P}),  1]\}$,  where  $P$  is  also  a
+  The  first step is \emph{positive sentence pair sampling}. During the training
+  process,  we have to first make sure that the ground truth class label $y_{i}$
+  for  $x_{i}$  is  within  the  candidate  class  label  set $\mathcal{C'}$. If
+  $y_{i}\notin  \mathcal{C'}$,  we will manually add $y_{i}$ into $\mathcal{C'}$
+  by  replacing  $c'_{K}$  with  $y_{i}$,  since $c'_{K}$ is the least promising
+  candidate  label  according  to the auxiliary model in stage 1. Afterwards, we
+  will randomly sample $P$ sentences $\{x'_{0},x'_{1}, \dots, x'_{P}\}$ with the
+  same  class  label  as  $y_{i}$  from dataset $\mathcal{D}$ to form the set of
+  sentence  pairs  with positive label $\mathcal{P'}_{i}=\{[(x_{i}, x'_{0}), 1],
+  [(x_{i},  x'_{1}),  1],  \dots,  [(x_{i},  x'_{P}), 1]\}$, where $P$ is also a
   hyperparameter  set  by  us  that  controls  the number of sentences we should
@@
 
-  \textbf{2.  negative  sentence pair sampling}: As for negative sentence pairs,
-  we  will  also  randomly  sample  $P$ sentences for each class in the negative
-  candidate class label set $\mathcal{C'}\backslash \{y_{i}\}$. The class labels
-  in  $\mathcal{C'}\backslash  \{y_{i}\}$  are  the  set of most confusing class
-  labels comparing to the ground truth ${y_{i}}$, so we assume that the sentence
-  pairs  with  negative  label grouped by user input query $x_{i}$ and sentences
-  with class labels in $\mathcal{C'}\backslash \{y_{i}\}$ are strong adversarial
-  negative  samples for sentence-pair similarity model that can help enhance the
-  training  speed  and  performance.  According  to  the same method as positive
-  sentence  pair sampling, we can obtain the set of sentence pairs with negative
-  label  as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{0}), 0], [(x_{i}, x'_{1}), 0], ...,
-  [(x_{i}, x'_{P\cdot (K-1)}), 0]\}$
+  The  second  step  is  \emph{negative sentence pair sampling}: As for negative
+  sentence  pairs,  we will also randomly sample $P$ sentences for each class in
+  the negative candidate class label set $\mathcal{C'}\backslash \{y_{i}\}$. The
+  class  labels  in  $\mathcal{C'}\backslash  \{y_{i}\}$  are  the  set  of most
+  confusing  class  labels comparing to the ground truth ${y_{i}}$, so we assume
+  that  the  sentence  pairs  with  negative  label  grouped by user input query
+  $x_{i}$  and sentences with class labels in $\mathcal{C'}\backslash \{y_{i}\}$
+  are  strong  adversarial  negative  samples for sentence-pair similarity model
+  that  can  help  enhance  the training speed and performance. According to the
+  same  method  as  positive  sentence  pair  sampling, we can obtain the set of
+  sentence  pairs  with  negative label as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{0}),
+  0], [(x_{i}, x'_{1}), 0], ..., [(x_{i}, x'_{P\cdot (K-1)}), 0]\}$
 
@@
   \subsubsection*{
-    stage 1: classification model for providing top-K candidate class labels
+    Stage 1: classification model for providing top-K candidate class labels
   }
@@
 
-  \subsubsection*{
-    stage 2: sentence-pair model for multi-task learning
-  }
+  \subsubsection*{Stage 2: sentence-pair model for multi-task learning}
 
@@
 
+  \subsection{Multitask based training}
   The 2 tasks for stage 2 training process are listed below.
 
-  $\bullet$ \textbf{Task 1: Regular sentence-pair similarity task}
+  \subsubsection*{Task 1: Regular sentence-pair similarity task}
 
@@
 
-  $\bullet$ \textbf{Task 2: Classification task on top-K classes based on sentence-pair model}
+  \subsubsection*{Task   2:  Classification  task  on  top-K  classes  based  on
+  sentence-pair model}
 
@@
   Therefore,  the  overall  loss  function for multi-task learning in stage 2 is
-  shown in Equ. \ref{eq: two-stage SFC loss}. The training objective of stage 2 is
+  shown in Equ. \ref{eq:two-stage_SFC_loss}. The training objective of stage 2 is
   to  minimize  the  weighted  sum  of task-specific losses. Here $\alpha_S$ and
-  $\alpha_K$  are  weights  of  task  1  and  task  2  respectively,  which  are
+  $\alpha_K$  are  weights  of  task  1  and  task  2  respectively.
+  which  are
   $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting.
-The reason for giving task 2 relatively more weights is that according to the ablation experiments we did in Section \ref{sec:exp}, task 2 contributes more to the overall performance.
 
@@
     \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K
-    \label{eq: two-stage SFC loss}
+    \label{eq:two-stage_SFC_loss}
   \end{align}
@@
     \end{centering}
-    \caption{Key statistics for experimental datasets and few shot settings}
+    \caption{Statistics for all datasets and few shot settings\footnote{All
+    settings of four public datasets would be released to github soon}.}
 
@@
 
-  \subsection{joint SFC with joint model structure}
-  Despite  the  outstanding experimental result of two-stage SFC on various tasks,
-  we still find a limitation brought by the two-stage system structure. In two-stage
-  SFC, Stage 1 and stage 2 are separate, so they do not interact with each other
-  during  training.  In  this  case,  the  performance  of stage 1 can limit the
-  potential  of  stage  2, meanwhile, stage 2 also cannot give training feedback
-  back to stage 1 for fine-tuning.
+  \subsection{Joint SFC with joint model structure}
+  In  two-stage  SFC,  Stage 1 and stage 2 are separate, so they do not interact
+  with  each other during training. In this case, the performance of stage 1 can
+  limit  the  potential of stage 2, meanwhile, stage 2 also cannot give training
+  feedback back to stage 1 for fine-tuning.
 
@@
 
-  There  are  3  tasks in total during the training process of joint SFC,
-  shown  in  Fig. \ref{fig:framework}, and the overall loss is also the weighted
-  sum  of  all  the task-specific losses, shown in Equ. \ref{eq: hierachical SFC
-  loss}. Here, $\alpha_S$, $\alpha_K$ and $\alpha_C$ are the weights for task 1:
+  There  are 3 tasks in total during the training process of joint SFC, shown in
+  Fig. \ref{fig:framework}, and the overall loss is also the weighted sum of all
+  the   task-specific  losses,  shown  in  Equ.  \ref{eq:joint_SFC_loss}.  Here,
+  $\alpha_S$,   $\alpha_K$   and   $\alpha_C$   are  the  weights  for  task  1:
   sentence-pair  similarity,  task  2:  top-K classification and task 3: general
-  single   sentence  classification  respectively,  which  are  $\alpha_S=0.25$,
-  $\alpha_K=0.25$ and $\alpha_C=0.5$ in our setting.
-
+  single sentence classification respectively.
   \begin{align}
     \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K + \alpha_C \mathcal{L}^C
-    \label{eq: hierachical SFC loss}
+    \label{eq:joint_SFC_loss}
   \end{align}
@@
 
-  $\bullet$ \textbf{Full-scale real-world task-specific faq chatbot dataset}
+  \textbf{Real-world task-specific faq chatbot dataset}
 
@@
 
-  $\bullet$ \textbf{Subset of customer review dataset for extreme classification}
+  \textbf{Customer review dataset for extreme classification}
 
@@
 
-  $\bullet$ \textbf{Subset of recently-released intention detection datasets}.
+  \textbf{Recently-released intention detection datasets}.
 
@@
   \subsection{Baselines}
-  We choose 3 groups of representative baselines:
+  We choose 3 groups of typical baselines:
 
   \textbf{Group  1:  single-task  classification  model.} This group of baseline
-  models  are  based  on the network structure for classification model.   As   for   non-pretrained   neural   network,  we  choose
-  TextCNN \cite{kim2014convolutional}  as  a  representative baseline. As for the
-  pretrained  model,  we choose RoBERTa, BERT and ALBERT, all of which are among
-  the  most  powerful pretrained models that achieve outstanding results in many
-  NLP  tasks,  in  our  experimental  setting. Since we apply RoBERTa in our SFC
-  system,   we   naturally  adopt  single-task  classification  model  based  on
-  RoBERTa-large  and RoBERTa-base as our baseline models. Besides, we also adopt
-  the       recently       released       baseline       pre-trained       model
-  ALBERT-xxlarge \cite{lan2019albert}  for  comparison.  Since  we  use few-shot   settings   different from    that of \cite{casanueva2020efficient}  for  those
-  intention
-  detection  datasets,  we also use BERT-large tuned on our few-shot settings as
-  an essential reference baseline for experimental results.
+  models  are  based  on  the network structure for classification model. As for
+  non-pretrained  neural  network, we choose TextCNN \cite{kim2014convolutional}
+  as  a representative baseline. As for the pretrained model, we choose RoBERTa,
+  BERT  and  ALBERT,  all of which are among the most powerful pretrained models
+  that  achieve  outstanding  results  in  many  NLP  tasks, in our experimental
+  setting.  Since  we  apply  RoBERTa  in  our  SFC  system,  we naturally adopt
+  single-task  classification  model  based on RoBERTa-large and RoBERTa-base as
+  our  baseline  models.  Besides,  we also adopt the recently released baseline
+  pre-trained model ALBERT-xxlarge \cite{lan2019albert} for comparison. Since we
+  use few-shot settings different from that of \cite{casanueva2020efficient} for
+  those  intention  detection  datasets,  we  also  use  BERT-large tuned on our
+  few-shot settings as an essential reference baseline for experimental results.
 
@@
   the main evaluation measure for all experimental results.
+
+  In  two-stage  SFC, in equ. \ref{eq:two-stage_SFC_loss} the  weights of two tasks are set as $\alpha_S=0.125$ and
+  $\alpha_K=0.875$  in our setting. The reason for giving task 2 relatively more
+  weights  is  that  according  to  the  ablation  experiments we did in Section
+  \ref{sec:exp},  task  2  contributes more to the overall performance. In joint
+  SFC,  in equ. \ref{eq:joint_SFC_loss}, the  weights  of three tasks are set as $\alpha_S=0.25$, $\alpha_K=0.25$
+  and $\alpha_C=0.5$ in our setting.
 

### 2020-09-05 chatbot_classification/aaai_2021/paper.tex
version 1.   modified:   paper.tex   new file:   paper.ver01.pdf

@@
     \caption{
-      \textbf{Network   Structure   of  joint  SFC:}  a  joint  model  of
-      sentence-pair   model   and   text   classification   model  organized  in
-      joint  structure by completing different tasks at different network
-      layers.
+      \textbf{Network Structure of SFC:} two-stage SFC and joint-SFC are sharing
+      the  same  network  from  stage  1  and  stage 2, with the only difference
+      whether two stages being jointly trained.
     }
@@
           (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
           LEAM & \multirow{2}*{$0.7514$} & \multirow{2}*{$0.8203$} & \multirow{2}*{$0.8612$} & \multirow{2}*{$0.8802$} & \multirow{2}*{$0.9010$} & \multirow{2}*{$0.9180$} & \multirow{2}*{$0.5422$} & \multirow{2}*{$0.7812$} & \multirow{2}*{$0.8129$} & \multirow{2}*{$0.8280$} & \multirow{2}*{$0.8610$} & \multirow{2}*{$0.8727$} & \multirow{2}*{$0.4545$} & \multirow{2}*{$0.5554$} & \multirow{2}*{$0.5936$} & \multirow{2}*{$0.6599$} & \multirow{2}*{$0.6855$} & \multirow{2}*{$0.7046$} & \multirow{2}*{$0.7086$} & \multirow{2}*{$0.6091$}\tabularnewline
@@
           \hline
+          \hline
           BERT-large & \multirow{2}*{$0.8080$} & \multirow{2}*{$0.8904$} & \multirow{2}*{$0.9265$} & \multirow{2}*{$0.9334$} & \multirow{2}*{$0.9497$} & \multirow{2}*{$0.9595$} & \multirow{2}*{$0.5780$} & \multirow{2}*{$0.8004$} & \multirow{2}*{$0.8518$} & \multirow{2}*{$0.8827$} & \multirow{2}*{$0.8858$} & \multirow{2}*{$0.8982$} & \multirow{2}*{$0.4711$} & \multirow{2}*{$0.5963$} & \multirow{2}*{$0.6342$} & \multirow{2}*{$0.7010$} & \multirow{2}*{$0.7117$} & \multirow{2}*{$0.7424$} & \multirow{2}*{$0.7485$} & \multirow{2}*{$0.6658$}\tabularnewline
           (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
           ALBERT-xxlarge & \multirow{2}*{$0.8497$} & \multirow{2}*{$0.9008$} & \multirow{2}*{$0.9296$} & \multirow{2}*{$0.9297$} & \multirow{2}*{$0.9466$} & \multirow{2}*{$0.9578$} & \multirow{2}*{$0.5549$} & \multirow{2}*{$0.7981$} & \multirow{2}*{$0.8231$} & \multirow{2}*{$0.8530$} & \multirow{2}*{$0.8571$} & \multirow{2}*{$0.9096$} & \multirow{2}*{$0.4879$} & \multirow{2}*{$0.6116$} & \multirow{2}*{$0.6135$} & \multirow{2}*{$0.6996$} & \multirow{2}*{$0.7094$} & \multirow{2}*{$0.7376$} & \multirow{2}*{$0.7253$} & \multirow{2}*{$0.6893$}\tabularnewline
           (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
           RoBERTa-base & \multirow{2}*{$0.8732$} & \multirow{2}*{$0.9254$} & \multirow{2}*{$0.9363$} & \multirow{2}*{$0.9482$} & \multirow{2}*{$0.9558$} & \multirow{2}*{$0.9637$} & \multirow{2}*{$0.7305$} & \multirow{2}*{$0.8654$} & \multirow{2}*{$0.8808$} & \multirow{2}*{$0.9080$} & \multirow{2}*{$0.9061$} & \multirow{2}*{$0.9293$} & \multirow{2}*{$0.5831$} & \multirow{2}*{$0.6790$} & \multirow{2}*{$0.7064$} & \multirow{2}*{$0.7100$} & \multirow{2}*{$0.7320$} & \multirow{2}*{$0.7472$} & \multirow{2}*{$0.7734$} & \multirow{2}*{$0.6708$}\tabularnewline
           (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
           RoBERTa-large & \multirow{2}*{$0.8974$} & \multirow{2}*{$0.9372$} & \multirow{2}*{$0.9508$} & \multirow{2}*{$0.9584$} & \multirow{2}*{$0.9621$} & \multirow{2}*{$0.9733$} & \multirow{2}*{$0.7690$} & \multirow{2}*{$0.8728$} & \multirow{2}*{$0.8966$} & \multirow{2}*{$0.9099$} & \multirow{2}*{$0.9227$} & \multirow{2}*{$0.9313$} & \multirow{2}*{$0.6044$} & \multirow{2}*{$0.7002$} & \multirow{2}*{$0.7129$} & \multirow{2}*{$0.7436$} & \multirow{2}*{$0.7493$} & \multirow{2}*{$0.7678$} & \multirow{2}*{$0.7990$} & \multirow{2}*{$0.7156$}\tabularnewline
           (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
           RoBERTa-large & \multirow{2}*{$0.8266$} & \multirow{2}*{$0.8861$} & \multirow{2}*{$0.9023$} & \multirow{2}*{$0.9084$} & \multirow{2}*{$0.9090$} & \multirow{2}*{$0.9407$} & \multirow{2}*{$0.757$} & \multirow{2}*{$0.8476$} & \multirow{2}*{$0.8614$} & \multirow{2}*{$0.8743$} & \multirow{2}*{$0.8749$} & \multirow{2}*{$0.8980$} & \multirow{2}*{$0.5425$} & \multirow{2}*{$0.6164$} & \multirow{2}*{$0.6503$} & \multirow{2}*{$0.6729$} & \multirow{2}*{$0.6947$} & \multirow{2}*{$0.7231$} & \multirow{2}*{$0.7418$} & \multirow{2}*{$0.6362$}\tabularnewline
@@
           \hline
+          \hline
           2-stage SFC & \multirow{2}*{$0.8979$} & \multirow{2}*{$0.9457$} & \multirow{2}*{$0.9517$} & \multirow{2}*{$0.9591$} & \multirow{2}*{$0.9610$} & \multirow{2}*{$0.9664$} & \multirow{2}*{$0.7975$} & \multirow{2}*{$0.8818$} & \multirow{2}*{$0.8962$} & \multirow{2}*{$0.9109$} & \multirow{2}*{$0.9187$} & \multirow{2}*{$0.9198$} & \multirow{2}*{$0.6477$} & \multirow{2}*{$0.7055$} & \multirow{2}*{$0.7200$} & \multirow{2}*{$0.7232$} & \multirow{2}*{$0.7484$} & \multirow{2}*{$0.7653$} & \multirow{2}*{$0.7972$} & \multirow{2}*{$0.7189$}\tabularnewline
-          (task1 only) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
+          (task1) & & & & & & & & & & & & & & & & & & & &\tabularnewline
           2-stage SFC & \multirow{2}*{$0.9162$} & \multirow{2}*{$0.9424$} & \multirow{2}*{$0.9530$} & \multirow{2}*{$0.9617$} & \multirow{2}*{$0.9633$} & \multirow{2}*{$0.9690$} & \multirow{2}*{$0.7997$} & \multirow{2}*{$0.8823$} & \multirow{2}*{$0.8945$} & \multirow{2}*{$0.9123$} & \multirow{2}*{$0.9236$} & \multirow{2}*{$0.9317$} & \multirow{2}*{$0.6498$} & \multirow{2}*{$0.6980$} & \multirow{2}*{$0.7202$} & \multirow{2}*{$0.7358$} & \multirow{2}*{$0.7498$} & \multirow{2}*{$0.7657$} & \multirow{2}*{$0.8020$} & \multirow{2}*{$0.7311$}\tabularnewline
-          (task2 only) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
+          (task2) & & & & & & & & & & & & & & & & & & & &\tabularnewline
           2-stage SFC & \multirow{2}*{$0.9167$} & \multirow{2}*{$0.9456$} & \multirow{2}*{$0.9571$} & \multirow{2}*{$0.9638$} & \multirow{2}*{$0.9658$} & \multirow{2}*{$0.9753$} & \multirow{2}*{$0.8135$} & \multirow{2}*{$0.8854$} & \multirow{2}*{$0.8931$} & \multirow{2}*{$0.9192$} & \multirow{2}*{$0.9257$} & \multirow{2}*{$0.9339$} & \multirow{2}*{$0.6525$} & \multirow{2}*{$0.7092$} & \multirow{2}*{$0.7168$} & \multirow{2}*{$0.7476$} & \multirow{2}*{$0.7519$} & \multirow{2}*{$0.7696$} & \multirow{2}*{$\textbf{0.8124}$} & \multirow{2}*{$0.7364$}\tabularnewline
           (task1 + task2) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
           \multirow{2}*{Joint SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.9669}$} & \multirow{2}*{$\textbf{0.9712}$} & \multirow{2}*{$\textbf{0.9821}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.9323}$} & \multirow{2}*{$\textbf{0.9463}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$\textbf{0.7593}$} & \multirow{2}*{$\textbf{0.7772}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline

### 2020-09-06 chatbot_classification/aaai_2021/paper.tex
modified:   paper.tex   modified:   picture/picture4.key   modified:   picture/picture4.pdf

@@
 %File: formatting-instructions-latex-2021.tex
-%release 2021.1
 \documentclass[letterpaper]{article} % DO NOT CHANGE THIS
@@
 \usepackage{graphicx} % DO NOT CHANGE THIS
-\urlstyle{rm} % DO NOT CHANGE THIS
-\def\UrlFont{\rm}  % DO NOT CHANGE THIS
-\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\frenchspacing  % DO NOT CHANGE THIS
-\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
-\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
-%\nocopyright
-%PDF Info Is REQUIRED.
-% For /Author, add all authors within the parentheses, separated by commas. No accents or commands.
-% For /Title, add Title in Mixed Case. No accents or commands. Retain the parentheses.
-\pdfinfo{
-  /Title (AAAI Press Formatting Instructions for Authors Using LaTeX -- A Guide)
-  /Author (AAAI Press Staff, Pater Patel Schneider, Sunil Issar, J. Scott Penberthy, George Ferguson, Hans Guesgen, Francisco Cruz, Marc Pujol-Gonzalez)
-  /TemplateVersion (2021.1)
-}
-
 \usepackage{array}
@@
 \usepackage{spconf}
+\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
+\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
 
-\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.
+\urlstyle{rm} % DO NOT CHANGE THIS
+\def\UrlFont{\rm}  % DO NOT CHANGE THIS
+\frenchspacing  % DO NOT CHANGE THIS
+\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
+\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
-%% Because html converters don't know tabularnewline
 \providecommand{\tabularnewline}{\\}
@@
 
+%\nocopyright
+%PDF Info Is REQUIRED.
+% For /Author, add all authors within the parentheses, separated by commas. No accents or commands.
+% For /Title, add Title in Mixed Case. No accents or commands. Retain the parentheses.
+\pdfinfo{
+  /title (Joint training of classification model and similarity model for
+  low-resource text classification in chatbot)
+  /Author (no author informmation)
+  /TemplateVersion (2021.1)
+}
+
+\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
+%% Because html converters don't know tabularnewline
 \title{     
@@
   text classification in chatbot
-}
-
-\author{
-  %Authors
-  % All authors must be in the same font size and format.
-  Written by AAAI Press Staff\textsuperscript{\rm 1}\thanks{With help from the AAAI Publications Committee.}\\
-  AAAI Style Contributions by Pater Patel Schneider,
-  Sunil Issar,  \\
-  J. Scott Penberthy,
-  George Ferguson,
-  Hans Guesgen,
-  Francisco Cruz,
-  Marc Pujol-Gonzalez
-  \\
-}
-\affiliations{
-  %Afiliations
-
-  \textsuperscript{\rm 1}Association for the Advancement of Artificial Intelligence\\
-  %If you have multiple authors and multiple affiliations
-  % use superscripts in text and roman font to identify them.
-  %For example,
-
-  % Sunil Issar, \textsuperscript{\rm 2}
-  % J. Scott Penberthy, \textsuperscript{\rm 3}
-  % George Ferguson,\textsuperscript{\rm 4}
-  % Hans Guesgen, \textsuperscript{\rm 5}.
-  % Note that the comma should be placed BEFORE the superscript for optimum readability
-
-  2275 East Bayshore Road, Suite 160\\
-  Palo Alto, California 94303\\
-  % email address must be in roman text type, not monospace or sans serif
-  publications21@aaai.org
-
-  % See more examples next
 }

### 2020-09-06 chatbot_classification/aaai_2021/paper.tex
Version 2.

@@
   \section{Methodology}
-  In  this  section,  we  will  describe our proposed system of similarity model
-  fused  with  classification  model,  named  as  SFC, in detail. We propose two
-  approaches  to  implement  the  SFC idea, two-stageg SFC, and its more compact
-  version called joint-SFC.
+  In  this section, we describe our proposed system, similarity model fused with
+  classification  model (SFC). We propose two approaches to implement this idea,
+  two-stageg SFC, and its more unified version joint-SFC.
 
@@
 
-  The network   structure   of   two-stage   SFC  is  composed  with  2  separate  stages  in  charge of
-  different  jobs. In stage 1, we can use any auxiliary text classification model or tool to provide
-  top-K  most  related class labels. These selected class labels will later be used to sample sentence pairs of both positive
-  samples  and negative samples for stage 2.
-Then, in stage 2, we will use sentence pair similarity model to identify the class label with strongest semantic similarity to the user input sentence.
-Suppose we have a training dataset
-  $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$  of  $N$ data points, in which $x_{i}$
-  is the user input query and $y_{i}$ is a single class label from a class label
-  set  of  $C$  classes  in total. If we want to generate sentence pair dataset
-  $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$,   where   $(x,   x')_{j}$  is
-  sentence  pair  grouped  by  2  user  input  queries and $l_{j}\in\{0, 1\}$ is
-  similarity class label, see Equ. \ref{eq:similarity label},
-  \begin{align}
-    l_{j}=
-    \begin{cases} \label{eq:similarity label}
-      0 & y_{x}\neq y_{x'}\\
-      1 & y_{x}=y_{x'}
-    \end{cases}
-  \end{align}
-  directly  from  original dataset $\mathcal{D}$ without any sampling strategy,
-  then  $\mathcal{D'}$  will  have  $M=N^2$ data points of sentence pairs, which
-  might be too time-consuming for the training process of stage 2 since we often
-  have  hundreds  of class labels under task-specific chatbot scenario. Although
-  we  may  only  have  a  few data points for a single class label, $M$ is still
-  quite a big number.
-
-  Therefore,  we adopt the idea of adversarial negative sampling strategy raised
-  by   \cite{bamler2020extreme}.  The  key  idea  of this sampling strategy is to
-  train  with  negative  samples that are hard to be distinguished from positive
-  samples. Now suppose we have a user input query $x_{i}$ and top-K most related
-  class   labels   set  $\mathcal{C'}=\{c'_{1},  \dots,  c'_{K}\}$  provided  by
-  auxiliary  model  or  tool in stage 1, where $K$ is a hyperparameter set by us
-  that  controls  candidate  class  number,  we  apply  the adversarial negative
-  sampling  strategy  into our sentence pair sampling process by the following 2
-  steps:
-
-  The  first step is \emph{positive sentence pair sampling}. During the training
-  process,  we have to first make sure that the ground truth class label $y_{i}$
-  for  $x_{i}$  is  within  the  candidate  class  label  set $\mathcal{C'}$. If
-  $y_{i}\notin  \mathcal{C'}$,  we will manually add $y_{i}$ into $\mathcal{C'}$
-  by  replacing  $c'_{K}$  with  $y_{i}$,  since $c'_{K}$ is the least promising
-  candidate  label  according  to the auxiliary model in stage 1. Afterwards, we
-  will randomly sample $P$ sentences $\{x'_{0},x'_{1}, \dots, x'_{P}\}$ with the
-  same  class  label  as  $y_{i}$  from dataset $\mathcal{D}$ to form the set of
-  sentence  pairs  with positive label $\mathcal{P'}_{i}=\{[(x_{i}, x'_{0}), 1],
-  [(x_{i},  x'_{1}),  1],  \dots,  [(x_{i},  x'_{P}), 1]\}$, where $P$ is also a
-  hyperparameter  set  by  us  that  controls  the number of sentences we should
-  sample from each class.
-
-  The  second  step  is  \emph{negative sentence pair sampling}: As for negative
-  sentence  pairs,  we will also randomly sample $P$ sentences for each class in
-  the negative candidate class label set $\mathcal{C'}\backslash \{y_{i}\}$. The
-  class  labels  in  $\mathcal{C'}\backslash  \{y_{i}\}$  are  the  set  of most
-  confusing  class  labels comparing to the ground truth ${y_{i}}$, so we assume
-  that  the  sentence  pairs  with  negative  label  grouped by user input query
-  $x_{i}$  and sentences with class labels in $\mathcal{C'}\backslash \{y_{i}\}$
-  are  strong  adversarial  negative  samples for sentence-pair similarity model
-  that  can  help  enhance  the training speed and performance. According to the
-  same  method  as  positive  sentence  pair  sampling, we can obtain the set of
-  sentence  pairs  with  negative label as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{0}),
-  0], [(x_{i}, x'_{1}), 0], ..., [(x_{i}, x'_{P\cdot (K-1)}), 0]\}$
-
-  In  this  way,  we  can generate the sentence pair dataset $\mathcal{D'}$ for
-  stage  2 based on the top-K class label set $\mathcal{C'}$ provided by stage 1
-  as   $\mathcal{D'}=\{\mathcal{P'}_{i}\cup   \mathcal{N'}_{i}\}_{i=1}^{N}$,  in
-  which we will have $M=N\cdot K\cdot P$ data points of sentence pairs in total.
-
-  After  explaining the data sampling principle for sentence pairs and how the 2
-  stages  in  SFC  system  connect  with  each other, let's go deeper into model
-  structure within these two stages respectively to see how it works.
+  Two-stage   SFC  is  composed  with  two  independent stages  in  charge of
+  different  jobs.
 
@@
 
-  As for  stage  1,  our  two-stage SFC  system  can adapt to any auxiliary model or even
-  searching  tool  based  on  Term Frequency-Inverse Document Frequency (TF-IDF)
-  retrieval.  In  this  paper,  however,  we  choose to fine-tune pretrained model such as RoBERTa on our
-  task-specific  dataset $\mathcal{D}$ by adding a softmax classifier on top of
-  it for better
-  overall  performance.  According  to  our  experimental  result,  RoBERTa  can
-  guarantee  that  approximately  95\%  ground  truth labels be included in top-5
-  candidate  class  labels  with  highest  probability if it has been fine-tuned on
-  task-specific  dataset and can obtain a well performance measured by F-score over
-  0.75 on this dataset.  So  we use RoBERTa as the encoder of classification model in our setting at
-  stage 1 to ensure low limitation for the performance of stage 2.
+  In  stage  1,  we  can  use any auxiliary text classification model or tool,
+  such as Term Frequency-Inverse Document Frequency (TF-IDF)retrieval, to
+  provide  top-K  most  related  class  labels. These selected class labels will
+  later  be  used to sample sentence pairs of both positive samples and negative
+  samples  for  stage  2.
 
-  For single-sentence text classification tasks, given a data point $x_{i}$ with
+  In  this  work,  we  choose pretrained models to fine tune on our data $\mathcal{D}$.
+  Due to the excellent performance of RoBERTa in this task, compared to other pretrained
+  models, we use RoBERTa as the encoder of classification model in our setting.
+
+  In this stage, given a data point $x_{i}$ with
   class  label  $y_{i}$  from  dataset  $\mathcal{D}$, RoBERTa takes the final
@@
 
-  As for  stage 2, we also choose RoBERTa as the encoder for the sentence pair similarity model. Before sending sentence pairs to Roberta, we
-  pack  sentence  pairs  into a single sequence and separate them with a special
-  token  [SEP].  Roberta  will  also  add  a  learned  embedding  to every token
-  indicating  whether  it belongs to the first sentence or the second one. Then,
-  we  utilize  the  cross-attention  mechanism  inside RoBERTa, and then extract
-  semantic relationship between 2 sentences from the output softmax layer, which
-  is placed on top of the last hidden representation of the [CLS] token.
+  We continue choosing RoBERTa as the main module in the sentence pair
+  similarity  model.
 
-  Before we start to fine-tune our sentence-pair model on task-specific dataset,
+  Then, in stage 2, we will use sentence pair similarity
+  model  to  identify  the class label with strongest semantic similarity to the
+  user    input    sentence.    Suppose    we    have    a    training   dataset
+  $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$  of  $N$ data points, in which $x_{i}$
+  is the user input query and $y_{i}$ is a single class label from a class label
+  set  of  $C$  classes  in  total. If we want to generate sentence pair dataset
+  $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$,   where   $(x,   x')_{j}$  is
+  sentence  pair  grouped  by  2  user  input  queries and $l_{j}\in\{0, 1\}$
+  denotes the similarity label, see Equ. \ref{eq:similarity label},
+  \begin{align}
+    l_{j}=
+    \begin{cases} \label{eq:similarity label}
+      0 & y_{x}\neq y_{x'}\\
+      1 & y_{x}=y_{x'}
+    \end{cases}
+  \end{align}
+  directly  from  original dataset $\mathcal{D}$ without any sampling strategy,
+  then  $\mathcal{D'}$  will  have  $M=N^2$ data points of sentence pairs, which
+  might be too time-consuming for the training process of stage 2 since we often
+  have  hundreds  of class labels under task-specific chatbot scenario. Although
+  we  may  only  have  a  few data points for a single class label, $M$ is still
+  prohibitively large.
+
+  Therefore,  we adopt the idea of adversarial negative sampling strategy from
+  the work \cite{bamler2020extreme}.  The  key  idea  is to
+  train  with  negative  samples that are hard to be distinguished from positive
+  samples. Now suppose we have a user input query $x_{i}$ and top-K most related
+  class   labels   set  $\mathcal{C'}=\{c'_{1},  \dots,  c'_{K}\}$  provided  by
+  auxiliary  model  or  tool in stage 1, where $K$ is a hyperparameter 
+  to control  candidate  class  number,  we  apply  the adversarial negative
+  sampling  strategy  into our sentence pair sampling process by the following 2
+  steps:
+
+  The  first step is \emph{positive sentence pair sampling}. During the training
+  process,  we first make sure the ground truth class label $y_{i}$
+  for  $x_{i}$  is  within  the  candidate  class  label  set $\mathcal{C'}$. If
+  $y_{i}\notin  \mathcal{C'}$,  we manually add $y_{i}$ into $\mathcal{C'}$
+  by  replacing  $c'_{K}$  with  $y_{i}$,  since $c'_{K}$ is the least promising
+  candidate  label  according  to the auxiliary model in stage 1. Afterwards, we
+  will randomly sample $P$ sentences $\{x'_{0},x'_{1}, \dots, x'_{P}\}$ with the
+  same  class  label  as  $y_{i}$  from dataset $\mathcal{D}$ to form the set of
+  sentence  pairs  with positive label $\mathcal{P'}_{i}=\{[(x_{i}, x'_{0}), 1],
+  [(x_{i},  x'_{1}),  1],  \dots,  [(x_{i},  x'_{P}), 1]\}$, where $P$ is also a
+  hyperparameter  set  to control  the number of sentences we should
+  sample from each class.
+
+  The  second  step  is  \emph{negative sentence pair sampling}: As for negative
+  sentence  pairs,  we will also randomly sample $P$ sentences for each class in
+  the negative candidate class label set $\mathcal{C'}\backslash \{y_{i}\}$. The
+  class  labels  in  $\mathcal{C'}\backslash  \{y_{i}\}$  are  the  set  of most
+  confusing  class  labels comparing to the ground truth ${y_{i}}$, so we assume
+  that  the  sentence  pairs  with  negative  label  grouped by user input query
+  $x_{i}$  and sentences with class labels in $\mathcal{C'}\backslash \{y_{i}\}$
+  are  strong  adversarial  negative  samples for sentence-pair similarity model
+  that  can  help  enhance  the training speed and performance. According to the
+  same  method  as  positive  sentence  pair  sampling, we can obtain the set of
+  sentence  pairs  with  negative label as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{0}),
+  0], [(x_{i}, x'_{1}), 0], ..., [(x_{i}, x'_{P\cdot (K-1)}), 0]\}$
+
+  In  this  way,  we  generate the sentence pair dataset $\mathcal{D'}$ for
+  stage  2 based on the top-K class label set $\mathcal{C'}$ provided by stage 1
+  as   $\mathcal{D'}=\{\mathcal{P'}_{i}\cup   \mathcal{N'}_{i}\}_{i=1}^{N}$,  in
+  which we have $M=N\cdot K\cdot P$ data points of sentence pairs in total.
+
+  Before starting to fine-tune our sentence-pair model on task-specific dataset,
   we   first  fine-tune  RoBERTa  on  Quora  dataset \cite{iyer2017first},  which
@@
 
-  \subsection{Multitask based training}
+  \subsubsection*{Multi-task based training}
   The 2 tasks for stage 2 training process are listed below.
 
-  \subsubsection*{Task 1: Regular sentence-pair similarity task}
-
+  The first task is \emph{regular sentence-pair similarity task}.
   For  sentence  pair semantic similarity task, given a data point $(x, x')_{i}$
@@
 
-  \subsubsection*{Task   2:  Classification  task  on  top-K  classes  based  on
-  sentence-pair model}
+  The second task is \emph{classification  task  on  top-K  classes  based  on
+  sentence-pair model}.
 
@@
 
-  \subsection{Joint SFC with joint model structure}
-  In  two-stage  SFC,  Stage 1 and stage 2 are separate, so they do not interact
+  \subsection{Joint SFC}
+  In  two-stage  SFC,  Stage 1 and stage 2 are separate that there is no deep
+  interaction
   with  each other during training. In this case, the performance of stage 1 can
@@
   the   task-specific  losses,  shown  in  Equ.  \ref{eq:joint_SFC_loss}.  Here,
-  $\alpha_S$,   $\alpha_K$   and   $\alpha_C$   are  the  weights  for  task  1:
-  sentence-pair  similarity,  task  2:  top-K classification and task 3: general
+  $\alpha_S$,   $\alpha_K$   and   $\alpha_C$   represent the  weights  for  task  1,
+  sentence-pair  similarity,  task  2,  top-K classification and task 3, general
   single sentence classification respectively.
@@
   \end{align}
-
-  Finally,  when  doing inference, for each user input query $x$, we will choose
-  the  class label that contains the sentence $x'$ with highest similarity score
-  $\varPhi$,  after  being packed into a sentence pair $(x, x')$ with query $x$,
-  as our final result for prediction.
 

### 2020-09-06 chatbot_classification/aaai_2021/paper.tex
version 03.   modified:   paper.tex   new file:   paper.ver03.pdf

@@
   } 
-
-  In  stage  1,  we  can  use any auxiliary text classification model or tool,
+  We  can  use any auxiliary text classification model or tool,
   such as Term Frequency-Inverse Document Frequency (TF-IDF)retrieval, to
@@
 
-  In  this  work,  we  choose pretrained models to fine tune on our data $\mathcal{D}$.
+  In  this  work,  we  choose pretrained models to fine tune on our data.
   Due to the excellent performance of RoBERTa in this task, compared to other pretrained
@@
 
-  In this stage, given a data point $x_{i}$ with
-  class  label  $y_{i}$  from  dataset  $\mathcal{D}$, RoBERTa takes the final
-  hidden  state  $h_{i}$  of the first token [CLS] as the representation for the
-  whole   sequence  of  $x_{i}$.  Let's  suppose  we  have  a  linear  layer  as
-  ${\Phi}^C_{i}=W^Ch_{i}+b^C$,  where  $W^C$ and $b^C$ are trainable parameters,
-  the    probability    score    for    $x_{i}$    can    be    calculated    as
-  $p^C_{i}=softmax(W^Ch_{i}+b^C)=softmax({\Phi}^C_{i})$.   Then,  the  loss  for
-  stage 1 classification model is shown in Equ. \ref{eq:classification loss}, in
-  which  the  first  term  $\varPhi_{i,y_{i}}^C$ encourages high probability for
-  prediction of the correct label $y_{i}$.
+  Given   a   data   point   $x_{i}$  with  class  label  $y_{i}$  from  dataset
+  $\mathcal{D}$, we take the final hidden state $h_{i}$ of the first token [CLS]
+  encoded  by  RoBERTa  as the representation for the whole sequence of $x_{i}$.
+  Then  a linear layer is followed to output probabilistic distribution of class
+  labels,  $softmax(W^Ch_{i}+b^C)=softmax({\Phi}^C_{i})$,  where $W^C$ and $b^C$
+  are  trainable  parameters.  Then, the loss in stage 1 classification model is
+  shown in Equ. \ref{eq:classification loss},
 
@@
     \begin{aligned}
-      \mathcal{L}^{C}&=\frac{1}{N}\sum_{i=1}^{N}-log(\frac{exp(\varPhi_{i,y_{i}}^C)}{\sum_{j=1}^{C}exp(\varPhi_{i,j}^C)}) \\&=\frac{1}{N}\sum_{i=1}^{N}-\varPhi_{i,y_{i}}^C+log(\sum_{j=1}^{C}exp(\varPhi_{i,j}^C))
+      \mathcal{L}^{C}&=\frac{1}{N}\sum_{i=1}^{N}-log(\frac{exp(\varPhi_{i,y_{i}}^C)}{\sum_{j=1}^{C}exp(\varPhi_{i,j}^C)}) \\
       \label{eq:classification loss}
@@
 
-  \subsubsection*{Stage 2: sentence-pair model for multi-task learning}
+  \subsubsection*{
+    Stage 2: sentence-pair similarity model based classification with multi-task
+    learning
+  }
+  We  continue choosing RoBERTa as the main module in this stage that identifies
+  the class label with strongest semantic similarity to the user input sentence.
 
-  We continue choosing RoBERTa as the main module in the sentence pair
-  similarity  model.
-
-  Then, in stage 2, we will use sentence pair similarity
-  model  to  identify  the class label with strongest semantic similarity to the
-  user    input    sentence.    Suppose    we    have    a    training   dataset
-  $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$  of  $N$ data points, in which $x_{i}$
-  is the user input query and $y_{i}$ is a single class label from a class label
-  set  of  $C$  classes  in  total. If we want to generate sentence pair dataset
+  Suppose  we have a training dataset $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$ of
+  $N$  data  points,  in  which $x_{i}$ is the user input query and $y_{i}$ is a
+  single  class label from a class label set of $C$ classes in total. If we want
+  to             generate            sentence            pair            dataset
   $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$,   where   $(x,   x')_{j}$  is
-  sentence  pair  grouped  by  2  user  input  queries and $l_{j}\in\{0, 1\}$
-  denotes the similarity label, see Equ. \ref{eq:similarity label},
+  generated  from two user history queries \footnote{For simplicty, we use query
+  to denote a user's question or a response.} and $l_{j}\in\{0, 1\}$ denotes the
+  similarity label, see Equ. \ref{eq:similarity label},
   \begin{align}
@@
   directly  from  original  dataset $\mathcal{D}$ without any sampling strategy,
-  then  $\mathcal{D'}$  will  have  $M=N^2$ data points of sentence pairs, which
-  might be too time-consuming for the training process of stage 2 since we often
-  have  hundreds  of class labels under task-specific chatbot scenario. Although
-  we  may  only  have  a  few data points for a single class label, $M$ is still
-  prohibitively large.
+  then  $\mathcal{D'}$  will have $M=N^2$ data points of sentence pairs. That is
+  time-consuming  for  the  training  in stage 2 since we often have hundreds of
+  class  labels  under task-specific chatbot scenario. Though we may only have a
+  few data points for a single class label, $M$ is still prohibitively large.
 
   Therefore,  we  adopt  the idea of adversarial negative sampling strategy from
-  the work \cite{bamler2020extreme}.  The  key  idea  is to
-  train  with  negative  samples that are hard to be distinguished from positive
-  samples. Now suppose we have a user input query $x_{i}$ and top-K most related
-  class   labels   set  $\mathcal{C'}=\{c'_{1},  \dots,  c'_{K}\}$  provided  by
-  auxiliary  model  or  tool in stage 1, where $K$ is a hyperparameter 
-  to control  candidate  class  number,  we  apply  the adversarial negative
-  sampling  strategy  into our sentence pair sampling process by the following 2
-  steps:
+  the  work  \cite{bamler2020extreme}.  The  key  idea is to train with negative
+  samples  that  are hard to be distinguished from positive samples. Now suppose
+  we  have  a  user  input query $x_{i}$ and top-K most related class labels set
+  $\mathcal{C'}=\{c'_{1},  \dots,  c'_{K}\}$ provided by auxiliary model or tool
+  in  stage  1, where $K$ is a hyperparameter to control candidate class number,
+  we  apply  the  adversarial  negative sampling strategy into our sentence pair
+  sampling process by the following two steps:
 
@@
   contains  404,290  potential  duplicate question pairs, for transfer learning.
-  Then   we   continue  to  do  multi-task  training  on  sentence-pair  dataset
-  $\mathcal{D'}$ sampled from the top-K candidate class labels provided by stage
-  1.
+  This is also the merit of similarity based model, as labeled task-specific
+  classification data is hard to acquire, yet general sentence pairs with
+  similar semantics can be much easier to acquire.
 
   \subsubsection*{Multi-task based training}
-  The 2 tasks for stage 2 training process are listed below.
+  We   continue  to  do  multi-task  training  on  sentence-pair  dataset
+  $\mathcal{D'}$ sampled from the top-K candidate class labels provided by stage
+  1. In stage 2, we have two tasks tuning our system.
 
@@
 
-  Due  to  the  fact that sentence pairs within the same class is much less than
-  sentence  pairs  from  different  classes,  the  dataset  $\mathcal{D'}$  is
-  imbalanced.  Therefore, we will accommodate a weight variable $w^S = [K-1, 1]$
-  to  the  loss  to eliminate the bias brought by imbalanced data, shown in Equ.
+  Due  to  the  fact that sentence pairs within the same class is much fewer than
+  that from  different  classes,  the  dataset  $\mathcal{D'}$  is
+  quite imbalanced.  Therefore, we will accommodate a weight variable $w^S = [K-1, 1]$
+  to  the  loss  to eliminate the bias brought by data imbalance, shown in Equ.
   \ref{eq:similarity loss}.
@@
     \begin{aligned}
-      \mathcal{L}^{S}&=\frac{1}{M}\sum_{i=1}^{M}-w^S_{l_i}\cdot log(\frac{exp(\varPhi_{i,l_{i}}^S)}{\sum_{j=0}^{1}exp(\varPhi_{i,j}^S)}) \\&=\frac{1}{M}\sum_{i=1}^{M}-w^S_{l_i}\cdot \varPhi_{i,l_{i}}^S+w^S_{l_i}\cdot log(\sum_{j=0}^{1}exp(\varPhi_{i,j}^S))
+      \mathcal{L}^{S}&=\frac{1}{M}\sum_{i=1}^{M}-w^S_{l_i}\cdot log(\frac{exp(\varPhi_{i,l_{i}}^S)}{\sum_{j=0}^{1}exp(\varPhi_{i,j}^S)}) \\
       \label{eq:similarity loss}
@@
 
-  The second task is \emph{classification  task  on  top-K  classes  based  on
-  sentence-pair model}.
-
-  As  for top-K classification task, it shares the same sentence pair similarity
-  model   structure  with  task  1.  The  only  difference  is  that  we  add  a
+  The  second  task  is  \emph{classification  on  top-K classes}. As minimizing
+  similarity  loss  is  not  our  final goal in the intention classification, we
+  bring  back  classification  loss again. In this task, the network is based on
+  sentence  pair  similarity  modules.  The  only  difference  is  that we add a
   task-specific  average  pooling  layer,  shown  in Fig. \ref{fig:framework} to
-  implement the classification task based on sentence-pair model.
+  accomplish the classification task based on sentence-pair model.
 
@@
   \end{align}
-  where,
+  where
 
@@
     \begin{aligned}
-      \mathcal{L}^{K,pos}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,pos})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,pos})}) \\
-      &= -\xi_{i,l^{K}_{i}}^{K,pos} + log(\sum_{j=1}^{K}exp(\xi_{i,j}^{K,pos}))
+      \mathcal{L}^{K,pos}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,pos})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,pos})})
       \label{eq: pos top-k loss}
@@
       \mathcal{L}^{K,neg}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,neg})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,neg})}) \\
-      &= -\xi_{i,l^{K}_{i}}^{K,neg} + log(\sum_{j=1}^{K}exp(\xi_{i,j}^{K,neg}))
       \label{eq: neg top-k loss}
@@
 
-  Therefore,  the  overall  loss  function for multi-task learning in stage 2 is
+  Finally,  the  overall  loss  function for multi-task learning in stage 2 is
   shown in Equ. \ref{eq:two-stage_SFC_loss}. The training objective of stage 2 is
@@
   In  two-stage  SFC,  Stage  1  and  stage 2 are separate that there is no deep
-  interaction
-  with  each other during training. In this case, the performance of stage 1 can
-  limit  the  potential of stage 2, meanwhile, stage 2 also cannot give training
-  feedback back to stage 1 for fine-tuning.
+  interaction  with each other during training. In this case, the performance of
+  stage  1  may  limit  the potential of stage 2; meanwhile, stage 2 also cannot
+  give  training feedback back to stage 1 for fine-tuning. Therefore, to further
+  improve  the  overall performance of SFC, we proposed a joint model structure,
+  shown in Fig. \ref{fig:framework}.
 
-  Therefore,  to  further  improve the overall performance of SFC, we proposed a
-  joint  model  structure,  shown  in Fig. \ref{fig:framework}. In
-  joint SFC, classification model is being placed in lower layer level to
+  In  joint  SFC,  classification  model is being placed in lower layer level to
   dynamically  provide  top-K  candidate  class  labels  for  the  sentence-pair

### 2020-09-08 chatbot_classification/aaai_2021/paper.tex
version 04.   modified:   paper.tex   new file:   paper.ver04.pdf

@@
 
-  {Add joint NER and classification problem here.}
+  {todo: Add joint NER and classification problem here.}
 
@@
 
-  In  this  section,  we  conduct  extensive  experiments  over  5 task-specific
-  datasets  to  evaluate  the  performance  of  our  proposed SFC system and the
-  effectiveness  of  the  methodology  of  multi-task  learning  and
-  joint-model structure under low-data settings.
-
   \subsection{Datasets}
-  The  datasets  used in our experiments aims to help us study low-resource text
-  classification  problem  under  task-specific conversational chatbot scenario.
-  Therefore,  we did experiments on datasets under low-resource chatbot corpus setting,
-  which  is a large number of class labels (50-250) with a few examples(5-20) in
-  short  text  for  each  class, by sampling smaller subsets from the full scale
-  when the raw datasets are oversized, see Table \ref{tbe:dataset statistic}.
-Besides, we also did extensive experiments with larger scale datasets with 30-50 examples per class to test the stability of our proposed SFC system under normal-size data settings, also see Table \ref{tbe:dataset statistic}.
-
-  According to the task and domain, we categorize our experimental datasets into
-  the following 3 categories:
-
-  \textbf{Real-world task-specific faq chatbot dataset}
-
-  \textbf{ITG}  is  a  real-world  FAQ  chatbot dataset composed of question and
-  answer pairs about online English teaching. It contains 3,938 sample questions
-  for  228  class labels, where each class label corresponds to an unique answer
-  for a bunch of similar sample questions.
-
-  We  divide the whole dataset into 3 folds randomly with approximately the same
-  amount  of data within each fold, and then choose 2 folds as the training set,
-  the  remaing  1  fold  as  the  test  set for our experiments. We can obtain 3
-  different  combinations  among  the  3  folds,  and  we  will  use the average
-  experimental  results  of  these 3 combinations as the final evaluation result
-  for this dataset.
-
-  \textbf{Customer review dataset for extreme classification}
-
-  \textbf{Amazon-670K}   is   a   customer   product  review  dataset  for  text
-  classification  task from the extreme classification repository with full data
-  containing  670,091  class  labels,  285,176  training samples and 150875 test
-  samples \cite{bhatia2016extreme}.  As  the  dataset  contains  multiple class
-  labels  per  training sample, we keep only the first class label for each data
-  point. Besides, we also randomly sampled 250 class labels from all the classes
-  that  contain only 5-15 data points. In this way, we simulate the low-resource
-  chatbot  corpus setting with the subset of 1,942 training samples and 716 test
-  samples for 250 class labels.
-
-  \textbf{Recently-released intention detection datasets}.
-
-  From our point of view, task-specific chatbot usually starts with small amount
-  of  data at the initial stage. As more and more customers start to communicate
-  with  the  chatbot,  more data can be extracted from conversation log. Base on
-  these  assumptions,  we  do  experiments  on  the following 3 intention detection
-  dataset    under    sampling    method    similar    to    the   approach   in
-  \cite{casanueva2020efficient}  but  in  more  sophisticated few-shot settings,
-  while  keeping the same test sets for each experiment to see the change of the
-  improvement scale with decreasing data amount.
+  Our experiments aim to study the short text classification in the low-resource
+  environment  popular  in  the  task-specific conversional chatbot application.
+  Hence we choose and configure set datasets to serve this study. Different from
+  the  datasets from other short text classification research, such as semantics
+  classification  with  very  limited  semantics labels and several sentences as
+  input,   the   datasets  adopted  in  our  experiments  are  typically  having
+  comparatively  large  number  of  class labels, ranging from several dozens to
+  hundreds,  and  each  class  label  is  associated  with  a handful of labeled
+  queries,  and  each  query  is  usually  one  sentence. Table \ref{tbe:dataset
+  statistic} displays their statistics.
 
@@
           \hline
-          \hline
           BERT-large & \multirow{2}*{$0.8080$} & \multirow{2}*{$0.8904$} & \multirow{2}*{$0.9265$} & \multirow{2}*{$0.9334$} & \multirow{2}*{$0.9497$} & \multirow{2}*{$0.9595$} & \multirow{2}*{$0.5780$} & \multirow{2}*{$0.8004$} & \multirow{2}*{$0.8518$} & \multirow{2}*{$0.8827$} & \multirow{2}*{$0.8858$} & \multirow{2}*{$0.8982$} & \multirow{2}*{$0.4711$} & \multirow{2}*{$0.5963$} & \multirow{2}*{$0.6342$} & \multirow{2}*{$0.7010$} & \multirow{2}*{$0.7117$} & \multirow{2}*{$0.7424$} & \multirow{2}*{$0.7485$} & \multirow{2}*{$0.6658$}\tabularnewline
@@
           \hline
-          \hline
           2-stage SFC & \multirow{2}*{$0.8979$} & \multirow{2}*{$0.9457$} & \multirow{2}*{$0.9517$} & \multirow{2}*{$0.9591$} & \multirow{2}*{$0.9610$} & \multirow{2}*{$0.9664$} & \multirow{2}*{$0.7975$} & \multirow{2}*{$0.8818$} & \multirow{2}*{$0.8962$} & \multirow{2}*{$0.9109$} & \multirow{2}*{$0.9187$} & \multirow{2}*{$0.9198$} & \multirow{2}*{$0.6477$} & \multirow{2}*{$0.7055$} & \multirow{2}*{$0.7200$} & \multirow{2}*{$0.7232$} & \multirow{2}*{$0.7484$} & \multirow{2}*{$0.7653$} & \multirow{2}*{$0.7972$} & \multirow{2}*{$0.7189$}\tabularnewline
@@
           (task1 + task2) & & & & & & & & & & & & & & & & & & & &\tabularnewline
+          \hline
           \multirow{2}*{Joint SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.9669}$} & \multirow{2}*{$\textbf{0.9712}$} & \multirow{2}*{$\textbf{0.9821}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.9323}$} & \multirow{2}*{$\textbf{0.9463}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$\textbf{0.7593}$} & \multirow{2}*{$\textbf{0.7772}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline
@@
 
-  \textbf{HWU64}   is  a  intention  detection  dataset  designed  for  home  robot
-  scenario \cite{liu2019benchmarking}.  It aims at the specific task of capturing
-  the  intention  for  different  user  requests  to  home  robot  and  finding the
-  corresponding answer. The raw dataset contains 25,716 data points for 64 class
-  labels  through  crowdsourcing,  which  raises  much  more  data  than  common
-  real-world  circumstances. Therefore, we experiment with the setups where only
-  5,  10,  15, 20, 30 and 50 training data points are available for each class label by
-  random sampling.
+  \begin{enumerate}
+    \item \emph{ITG},  is  a proprietory FAQ dataset from real-world
+    chatbot  project,  which is composed of question and answer pairs about online
+    English teaching. It contains 3,938 sample questions for 228 class labels, and
+    each class label corresponds to a unique answer.
 
-  \textbf{CLINC150}  is a dataset designed for task-oriented systems with 23,700
-  queries  that  are  short  and unstructured for 150 intents, in the same style
-  made  by real users through crowdsourcing \cite{larson2019evaluation}. Here, we
-  sample 5, 10, 15, 20, 30 and 50 training data points for each intention class label by random
-  sampling for our experimental setup.
+    \item \emph{Amazon-670K}, is a customer product review dataset for
+    text  classification  task  from  the  extreme  classification repository. The
+    complete  dataset  contains 670,091 class labels, 285,176 training samples and
+    150,875   testing   samples   \cite{bhatia2016extreme}.  As  each  sample  may
+    correspond  to  multiple  class labels, we keep only the first one. We further
+    filter  out the class labels that each one is associated with 5 to 15 samples,
+    or  reviews,  to  mimic  the  chatbot scenario. From them, we sample 250 class
+    labels as well as their samples to form a subset with 1,942 + 716 samples.
 
-  \textbf{BANKING77}  is  a intention detection dataset for bank customer services.
-  The    raw    dataset    contains    13,084   data   points   for   77   class
-  labels \cite{casanueva2020efficient}.  Here,  we  sample 5, 10, 15, 20, 30, and 50 training
-  data  points  for  each  class  label  by random sampling for our experimental
-  setup.
+    \item \emph{HWU64}, is a intention detection dataset designed for
+    home  robot  scenario \cite{liu2019benchmarking}. It aims at the specific task
+    of  capturing  the  intention  for  different  user requests to home robot and
+    finding  the corresponding answer. The raw dataset contains 25,716 data points
+    for 64 class labels through crowdsourcing.
 
-  \subsection{Baselines}
-  We choose 3 groups of typical baselines:
+    \item \emph{CLINC150},  is  a dataset designed for task-oriented
+    systems  with  23,700 queries that are short and unstructured for 150 intents,
+    in    the    same   style   made   by   real   users   through   crowdsourcing
+    \cite{larson2019evaluation}.
 
-  \textbf{Group  1:  single-task  classification  model.} This group of baseline
-  models  are  based  on  the network structure for classification model. As for
-  non-pretrained  neural  network, we choose TextCNN \cite{kim2014convolutional}
-  as  a representative baseline. As for the pretrained model, we choose RoBERTa,
-  BERT  and  ALBERT,  all of which are among the most powerful pretrained models
-  that  achieve  outstanding  results  in  many  NLP  tasks, in our experimental
-  setting.  Since  we  apply  RoBERTa  in  our  SFC  system,  we naturally adopt
-  single-task  classification  model  based on RoBERTa-large and RoBERTa-base as
-  our  baseline  models.  Besides,  we also adopt the recently released baseline
-  pre-trained model ALBERT-xxlarge \cite{lan2019albert} for comparison. Since we
-  use few-shot settings different from that of \cite{casanueva2020efficient} for
-  those  intention  detection  datasets,  we  also  use  BERT-large tuned on our
-  few-shot settings as an essential reference baseline for experimental results.
+    \item \emph{BANKING77}, is a intention detection dataset for bank
+    customer  services.  The  raw dataset contains 13,084 data points for 77 class
+    labels \cite{casanueva2020efficient}.
+  \end{enumerate}
 
-  \textbf{Group  2: single-task similarity model.} This group of baseline models
-  are   based   on   network   structure   for   sentence pair similarity   model. We choose RoBERTa-large for the pretrained model part as an
-  powerful baseline. But during the evaluation step, we use elastic search to do
-  a  rough  filter  for  candidate  sentence  pairs  to  guarantee  a reasonable
-  inference time for each user input query.
+  Regarding  the first two datasets, we conduct 3-fold cross validata experients
+  that   70   percent   as  training,  15  percent  as  validation  and  testing
+  respectively,  and  report  the  averaged  testing results. Regarding the last
+  three datasets, we conduct experiments using a sampling method similar to that
+  in   \cite{casanueva2020efficient}   yet  in  a  more  sophisticated  few-shot
+  settings.  We  fix  a  test  data for each one, and examine their performances
+  using  5,  10,  15,  20,  30,  and 50 samples per class label respectively for
+  training.  This  is important, as in practice, a task-specific chatbot usually
+  starts  with  merely  a  handful of labeled data available in the early stage.
+  Besides,  in  the  active  learning framework, building an effective anxiliary
+  system  with limited resource is also quite important to help developers label
+  data more efficiently.
 
-  \textbf{Group  3:  SFC  system with ablation study.} This group of baseline is
-  based  on  the network structure of two-stage SFC. We
-  conduct  ablation study by introducing single task SFC system with only Task 1
-  or  Task  2  to  investigate  the influence of each component within the total
-  loss.
+  \subsection{System description}
+  We choose three kinds of system to construct our baselines.
+
+  \begin{enumerate}
+    \item \emph{Pretrained model based classification system}, which consists of
+    BERT,  RoBERTa,  and  ALBERT  \cite{lan2019albert}  based.  These pretrained
+    models  are  practically  proven  to  achieve  outstanding  performances  in
+    classification task and other NLP tasks.
+
+    \item   \emph{Non-pretrained   model  based  classification  system},  which
+    consists  of  a popular CNN based TextCNN \cite{kim2014convolutional}, and a
+    recently  proposed label-embedding based LEAM (todo: reference). Empircally,
+    a  non-pretrained  model  based  system  are  not  performing  as  well as a
+    pretrained  models  based,  if  both is applicable in some task. Our listing
+    these  non-pretrained model based systems here is to provide a comprehensive
+    performance comparison on our datasets.
+
+    \item   \emph{Pre-trained   model   based   similarity   model}.  We  choose
+    RoBERTa-large  as  our  fundermental  module as our SFC systems are based on
+    RoBERTa  too, and RoBERTa is empircally more effective than other pretrained
+    models  in  the  short  text  classification  task  in  our  experiments. In
+    inference,  we  use  an  elastic search to find a set of potential candidate
+    labels for the similarity model, to guarantee a reasonable running time.
+  \end{enumerate}
+
+  Our SFC systems include two-stage SFC with ablation, trained with two tasks
+  sperately and both, and joint SFC with all three tasks.
 
   \subsection{Implementation Details}
-  For  our  SFC  system,  we  use RoBERTa-large as the pretrained model for both
-  classification  task  and  sentence-pair similarity task. We further fine-tune
-  our  SFC  system  on  task-specific  datasets with max sequence length of 128,
+  For  our  SFC  systems,  we  use RoBERTa-large as the pretrained model for both
+  classification  task  and  sentence-pair similarity task. We fine-tune
+  our  SFC  system  on  our datasets with max sequence length of 128,
   learning  rate  of 1.5e-5 for RoBERTa-large pretrained model and learning rate
   of  5e-4  for  task-specific  layer  with polynomial decay and Adam optimizer.
-  Also,  we  set  the  max number of the epoch to 100 and save the best model on
-  validation  set based on test result in F-score. We also report the F-score as
-  the main evaluation measure for all experimental results.
+  Besides,  we  set  the  max number of the epoch to 100 and save the best model on
+  validation  set based on testing result in weighted F-score (todo: reference). 
+  We report the F-score as the main evaluation measure for all experiments.
 
-  In  two-stage  SFC, in equ. \ref{eq:two-stage_SFC_loss} the  weights of two tasks are set as $\alpha_S=0.125$ and
-  $\alpha_K=0.875$  in our setting. The reason for giving task 2 relatively more
-  weights  is  that  according  to  the  ablation  experiments we did in Section
-  \ref{sec:exp},  task  2  contributes more to the overall performance. In joint
-  SFC,  in equ. \ref{eq:joint_SFC_loss}, the  weights  of three tasks are set as $\alpha_S=0.25$, $\alpha_K=0.25$
-  and $\alpha_C=0.5$ in our setting.
+  In two-stage SFC, in equ. \ref{eq:two-stage_SFC_loss} the weights of two tasks
+  are  set  as  $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting. The reason
+  for  giving  task  2 relatively more weights is that according to the ablation
+  experiments  we  did  in Section \ref{sec:exp}, task 2 contributes more to the
+  overall  performance.  In  joint  SFC,  in  equ.  \ref{eq:joint_SFC_loss}, the
+  weights  of  three  tasks  are  set  as  $\alpha_S=0.25$,  $\alpha_K=0.25$ and
+  $\alpha_C=0.5$  in  our setting. Overrall, the task weights are less sensitive
+  in Joint SFC than in two-stage SFC.
 
@@
 
-  Table  \ref{tbe:table2}  presents  the  results for each experimental data and
+  Table  \ref{tbe:table2}  presents  all results on the five datasets 
   model  set-up  in detail. The performance of each model is measured in F-score
-  on the fixed test set for each dataset. The overall performance of SFC system
-  is  better  than  all  the  competitive  single-model  baseline models on five
-  experimental   datasets.  This  observation  gives  us  a  general  idea  that
-  classification model and similarity model can actually provide each other with
-  complementary information, and combining them together into a joint system can
-  effectively  enhance the overall capability based on richer extracted semantic
-  information.
-Furthermore, we also studied  the  relative performance among all the variants of SFC on  different data settings to explore the benefits brought by multi-task training and the joint-model structure.
-  With all the experimental results shown in Table \ref{tbe:table2},  we did the following more detailed analysis from several different
-  aspect.
+  on the fixed test set for each dataset. 
+  Overall,  two-stage SFC systems show moderate improvements over all  baseline
+  systems.  This  observation  gives  us  a  general  idea  that
+  classification model and similarity model can actually provide complementary information
+  to each other, and combining them together can enhance the overall capability 
+  based on richer extracted semantic information.  
+  Furthermore, we also studied  the  performance among all the variants of SFCs on  
+  different data settings to explore the benefits brought by multi-task training 
+  and the joint-model structure.
 

### 2020-09-08 chatbot_classification/aaai_2021/paper.tex
version 05.   modified:   paper.tex   new file:   paper.ver05.pdf

@@
     consists  of  a popular CNN based TextCNN \cite{kim2014convolutional}, and a
-    recently  proposed label-embedding based LEAM (todo: reference). Empircally,
+    recently  proposed label-embedding based LEAM (todo: reference and its label
+    setting). Empircally,
     a  non-pretrained  model  based  system  are  not  performing  as  well as a
@@
 
-  Table  \ref{tbe:table2}  presents  all results on the five datasets 
-  model  set-up  in detail. The performance of each model is measured in F-score
-  on the fixed test set for each dataset. 
-  Overall,  two-stage SFC systems show moderate improvements over all  baseline
-  systems.  This  observation  gives  us  a  general  idea  that
-  classification model and similarity model can actually provide complementary information
-  to each other, and combining them together can enhance the overall capability 
-  based on richer extracted semantic information.  
+  Table  \ref{tbe:table2} presents all results on the five datasets model set-up
+  in  detail.  The performance of each model is measured in F-score on the fixed
+  test  set  for  each  dataset.  Overall,  two-stage  SFC systems show moderate
+  improvements  over  all  baseline systems. This observation gives us a general
+  idea  that  classification  model  and  similarity  model can actually provide
+  complementary  information  to  each  other,  and  combining them together can
+  enhance the overall capability based on richer extracted semantic information.
   Furthermore, we also studied the performance among all the variants of SFCs on
@@
 
-  \textbf{Comparison  among  SFC  variants.} First, we turn to compare among the
-  four  SFC  variants shown in Table \ref{tbe:table2} to analyze the improvement
-  brought  by  multi-task  and  joint-model  structure. We conduct
-  ablation  experiments  to study the benefits brought by multi-task training by
-  comparing multi-task two-stage SFC with single-task two-stage SFC. We can see from
-  Table  \ref{tbe:table2}  that  two-stage  SFC  with  only  task 1 (sentence-pair
-  similarity task) degrades by 0.80 percent on average and two-stage SFC with only
-  task  2  (top-K  classification  task) degrades by 0.45 percent on average. The
-  degradation  indicates  that  training  with these 2 tasks together in SFC can
-  effectively  help  the  sentence-pair  model  extract  more knowledge from the
-  limited  amount  of data. Besides, task 2 degrades 0.35 percent less than task
-  1.  This observation suggests that task 2 may play a relatively more important
-  role  in multi-task learning, which leads us to put larger weight $\alpha_{K}$
-  to  the  loss  $\mathcal{L}^{K}$  of  task  2  when calculating the total loss
-  $\mathcal{L}$.  Also, we can see that the joint SFC steadily outperforms
-  two-stage  SFC  on  5  diverse  datasets  by  0.95  percents  on  average.  This
-  observation  supports  the idea that the joint model structure can
-  alleviate the limitation brought by the lack of interaction between similarity
-  model  and  classification  model in two-stage SFC. Therefore, for the following
-  analysis,  we  will  focus  on  the comparison between joint SFC and the
-  other baseline models.
+  \subsubsection*{Which SFC variant performs best?} 
+  First, we compare the four  SFC  variants to analyze the improvement
+  brought  by  multi-task  and  joint-model  structure.
 
-  \textbf{Analysis  under  few-shot  scenarios.}  Next,  we  analyze the overall
-  improvement trend of SFC under various few-shot settings. Our main focus is to
-  study chatbot building in common situation during real-world application where
-  only  a  few  sample  sentences are available for each class. The experimental
-  results  for  the  3  diverse  intention detection datasets (ClINC150, BANKING77,
-  HWU64) under few-shot settings(5-20 samples per class) indicate that our proposed joint SFC can
-  achieve  2.47  percents  average  improvement  over  one  of the most powerful
-  baseline  models,  which  is  RoBERTa-large classification model. Moreover, the improvement in F-score becomes more and more
-  prominent  with the decrease of data sample number per class. Our joint
-  SFC   can  achieve  4.97  percents  average  improvements  over  RoBERTa-large
-  classification model in the most extreme few-shot setting with only 5 training
-  samples  per class. This observation indicates that SFC is especially well-performed
-  when  being  applied during the initial stage of building task-specific chatbot
-  system,  where  the  amount  of  data sample for each class label is extremely scarce.
-Furthermore, our proposed joint SFC can also achieve 2.04 percents average improvement over RoBERTa-large classification model on all the data settings including the ones with large scale (30-50 samples per class).
-This experimental result indicates that joint SFC can still steadily outperforms single-task pretrained model baseline even if the data size grows bigger.
-But the improvement is still more prominent when the data is scarce, which makes SFC an excellent model for low-resource chatbot scenario.
+  Comparing with training two-stage SFC with multi-task, training with only task
+  1,  corresponding  to  sentence pair similarity model, degrades by 0.8 percent
+  point  on average, and training with only task 2, corresponding to top-K based
+  classification  task,  degrades  by  0.45  percent  point  on  average.  These
+  degradation  indicates  multi-task training in two-stage SFC is helpful for the
+  system  performance.  Besides, task 2 play a relatively more important role in
+  multi-task learning, and this aligns with their optimal weight settings.
 
-  \textbf{Comparison  between  label  embedding  and  sentence  pair embedding.}
-  Afterwards,  we  start  to  compare the performance of SFC with the text-label
-  joint  embedding  baseline  named as LEAM. As shown in Table \ref{tbe:table2},
-  joint  SFC outperforms LEAM by 11.90 percents on average F-score over 5
-  datasets.  Besides,  although the labels within the 3 diverse intention detection
-  datasets  (CLINC150,  BANKING77,  HWU64)  are  all  being  well-defined as the
-  semantic  summary  of  each intention, joint SFC still outperforms LEAM by
-  10.71  percents  on  average  F-score.  This  observation  indicates that it is
-  usually  quite  hard  to  use  a  fixed  label  with  only  a few words as the
-  representative  of  all  the  sentences  within a class since there are always
-  plenty of ways for people to express questions or queries about the same topic
-  during   a   conversation  with  chatbot.  Therefore,  learning  the  semantic
-  similarity  between  user  query  and  sample  sentences through sentence pair
-  embedding  can be more reliable than making decision according to the semantic
-  relationship between user query and class labels through label embedding.
+  Joint SFC consistently outperforms two-stage SFC on 5 diverse datasets by 0.95
+  percents  on  average. This observation supports the idea that the joint model
+  structure  can  alleviate  the  limitation  brought by the lack of interaction
+  between  two  stages.  In  following analysis, we will focus on the comparison
+  between joint SFC and the other baseline models.
 
-  \textbf{Fusion  of  classification  and  similarity  model.} Then, we begin to
-  compare  the  general  performance  of SFC with single-task classification and
-  similarity  baselines.  As  for  the  classification  model,  joint SFC
-  outperforms    TextCNN    by   21.52   percents,   ALBERT-xxlarge   by   7.99
-  percents\footnote{We found that the performance of ALBERT.xxlarge is extremely
-  unstable  for  classification  task.  Here, we did multiple run with different
-  settings  of parameters such as learning rate and batch size for each dataset,
-  and  record  the  best  result  we  can  obtain  in  Table \ref{tbe:table2}.},
-  BERT-large  by  7.73 percents, RoBERTa-base by 3.79 percents, RoBERTa-large by
-  2.04 percents on average F-score over 5 datasets. In this way, we can see that
-  RoBERTa  is  the  best  baseline  pre-trained  model for the low-resource text
-  classification  task  we  are  studying.  As for the similarity model, we only
-  choose  the  strongest  pretrained  model  RoBERTa-large  as our baseline, and
-  joint  SFC  achieves  the  improvement  of  7.09  percents  on average.
-  Moreover,  joint  SFC's  result on 2 datasets without data sampling for
-  few-shot  settings,  which  are  ITG  and  Amazon-670k, are also 1.24 and 2.89
-  percents  higher  than  Roberta-large  classification  model, and are 6.96 and
-  10.77  percents higher than Roberta-large similarity model. These improvements
-  illustrate that putting classification model and similarity model at different
-  network  layers  to  cooperate  with  each  other  is  a  successful design of
-  joint network structure for joint model, which enables these two models
-  assist each other for better overall results.
+  \subsubsection*{Is  the  fusion of a classification model and similarity model
+  helpful?}  We  compare  the performance of joint SFC with classification based
+  and similarity based baselines.
 
-  \textbf{Settings  of  hyperparameters.} Finally, we analyze the effect brought
-  by  different  settings  of  hyperparameters,  see  Table \ref{tbe:table3}. We
-  conduct  experiments on 5 different settings of hyperparameters, which are the
-  number  of candidate class number $K$ and the number of sentence pairs $P$ for
-  each  class, on ITG and Amazon-670K datasets to find the most suitable setting
-  of  these  2  hyperparameters.  We  control the total number of sentence pairs
-  sampled  for  each  user  query  into  about  the same level of amount(50-60).
+  Regarding the  classification  models,  joint SFC
+  outperforms    TextCNN    by   21.52   percent points,   ALBERT-xxlarge   by   7.99
+  percent points, BERT-large  by  7.73 percent points, RoBERTa-base by 3.79 
+  percent points, RoBERTa-large by 2.04 percents on average F-score over 5 datasets.  
+  Especially, ALBERT.xxlarge based is much more  unstable  in our senario. Thus, 
+  we did multiple run with different settings, e.g.,  learning rate and batch size 
+  for each dataset, and  report the  best  result  here. Comparatively,  
+  RoBERTa  based is  the  most stable and has the best performance among
+  all baselines and all experiment settings.
+
+  Regarding  the  similarity  model,  as  analyzed  above,  we  only  choose the
+  RoBERTa-large based as our baseline. Our joint SFC achieves the improvement of
+  7.09  percents  on average. Moreover, joint SFC's result on 2 datasets without
+  data  sampling  for few-shot settings, which are ITG and Amazon-670k, are also
+  1.24 and 2.89 percents higher than Roberta-large classification model, and are
+  6.96 and 10.77 percents higher than Roberta-large similarity model (todo:
+  meaning?).
+
+  The above analysises illustrate that suitable fusing the classification model and the 
+  similarity model to make them cooperate with each other is helpful to better
+  performance.
+
+  \subsubsection*{How does joint SFC interact with the classfication in stage
+  1?}
+  {todo: content}
+
+  \subsubsection*{How does SFC perform with different  training  data  size} 
+  We analyze the
+  overall  improvement  trend  of  SFC under various few-shot settings.
+
+  Our main
+  focus  is  to  study  chatbot  building  in common situation during real-world
+  application  where  only  a few sample sentences are available for each class.
+  The  experimental  results  for  the  3  diverse  intention detection datasets
+  (ClINC150,  BANKING77,  HWU64)  under  few-shot  settings, 5 to 20 samples per
+  class,  indicate that our proposed joint SFC can achieve 2.47 percents average
+  improvement   over  one  of  the  most  powerful  baseline  models,  which  is
+  RoBERTa-large  classification  model.  Moreover,  the  improvement  in F-score
+  becomes  more  and  more prominent with the decrease of data sample number per
+  class.
+
+  Especially,  in the most extreme few-shot setting with only 5 training samples
+  per  class  our joint SFC achieves 4.97 percent points improvements on average
+  over  RoBERTa-large classification model . This observation indicates that SFC
+  is  especially  well-performed  when being applied during the initial stage of
+  building  task-specific  chatbot  system,  where the amount of data sample for
+  each class label is extremely scarce.
+
+  Furthermore,  our  proposed  joint  SFC can also achieve 2.04 percents average
+  improvement  over  RoBERTa-large classification model on all the data settings
+  including  the  ones  with  large  scale,  30  to  50  samples per class. This
+  indicates that joint SFC can still steadily outperforms pretrained model based
+  baseline even if the data size grows bigger. However, the improvement is still
+  more prominent when the data is scarce, which makes SFC an excellent model for
+  low-resource chatbot scenario.
+
+  \subsubsection*{How is joint SFC related to the label  embedding based  LEAM?}
+  LEAM performs consistently better than TextCNN by a large margin in all
+  datasets. TextCNN is practically efficiently in task-specific chat
+  applications, and LEAM shows its power in modeling labeling information.
+
+  LEAM  does not perform as well as SFCs, since the first intuitive reason is it
+  does  not use pretrained model as encoding module; and another critical reason
+  is  in  task-specific  chat applications, it is common to have many intentions
+  that are close to some others with a minor difference, and it is hard and even
+  impossible  to  name  each  intention  with  a short clear name. One candidate
+  solution  is  setting  a most standard sample as the label of that class. When
+  using  non-pretrained  models  base  LEAM,  this is applicable. Yet when using
+  pretrained  model  based, as the all labels can be hundreds of thousands, then
+  this  can not be accommodated in a poplar 32 G Tesla V100 GPU. Actually, joint
+  SFC  can  be  kind  of  understood  as  a  generalization form of LEAM. In the
+  scenario when there is no clear class label, the relationship between a sample
+  and  a class lable is implicatily encoded as that between a sample and another
+  sample  from  the  same  class, and this turns into a sentence pair similarity
+  model.
+
+  \subsubsection*{Settings  of  hyperparameters} 
+  Finally, we analyze the effect brought
+  by  different  settings  of  hyperparameters,  see  Table \ref{tbe:table3}.
+
+  We  conduct  experiments on 5 different settings of hyperparameters, which are
+  the  number of candidate class number $K$ and the number of sentence pairs $P$
+  for  each  class,  on  ITG  and Amazon-670K datasets to find the most suitable
+  setting  of  these  2 hyperparameters. We control the total number of sentence
+  pairs  sampled for each user query into about the same level of amount(50-60).
   Through  analyzing the experimenal results shown in Table \ref{tbe:table3}, we
-  find  that the best setting of hyperparameters might be different for
-  datasets of different data size. The class label number of ITG and Amazon-670k
-  are  similar  in  our  experimental  setting, which is around 250. However the
-  total  amount  of  data  points  of  ITG  is approximately 2 times larger than
-  Amazon-670k. Therefore, the setting of $K=5$ and $P=10$ is good enough for ITG
-  since  most  of  the  classes  contains  over  10  data  points.  However, for
-  Amazon-670k,  the amount of data sample for each class is scarce, thus, we may
-  need  more  candidate  classes  to  sample enough effective sentence pairs for
-  sentence-pair model layer of SFC. In this way, the setting of $K=10$ and $P=5$
-  becomes a good choice.
-However, in spite of the effect on evaluation performance brought by different settings of hyperparameters, joint SFC still steadily outperforms two-stage SFC by 0.41 percents in overall average F-score on ITG and Amazon-670k datasets.
+  find  that the best setting of hyperparameters might be different for datasets
+  of  different  data  size.  The  class label number of ITG and Amazon-670k are
+  similar  in  our  experimental setting, which is around 250. However the total
+  amount of data points of ITG is approximately 2 times larger than Amazon-670k.
+  Therefore,  the  setting of $K=5$ and $P=10$ is good enough for ITG since most
+  of  the  classes  contains  over 10 data points. However, for Amazon-670k, the
+  amount  of  data  sample  for  each  class  is  scarce, thus, we may need more
+  candidate  classes to sample enough effective sentence pairs for sentence-pair
+  model  layer  of  SFC.  In this way, the setting of $K=10$ and $P=5$ becomes a
+  good choice. However, in spite of the effect on evaluation performance brought
+  by different settings of hyperparameters, joint SFC still steadily outperforms
+  two-stage  SFC  by  0.41  percents  in  overall  average  F-score  on  ITG and
+  Amazon-670k datasets.
 
-  In  conclusion,  to  the best of our knowledge, these experimental results place joint SFC as the
-  best   performing   model   on   5  diverse  experimental  datasets  for  text
-  classification  task, especially when it's under  low-resource task-specific conversational chatbot
-  scenario.
+  In  conclusion, to the best of our knowledge, these experimental results place
+  joint  SFC as the best performing model on 5 diverse experimental datasets for
+  text   classification   task,   especially   when   it's   under  low-resource
+  task-specific conversational chatbot scenario.
 

### 2020-09-09 chatbot_classification/aaai_2021/paper.tex
modified:   paper.tex

@@
   are  trainable  parameters.  Then, the loss in stage 1 classification model is
-  shown in Equ. \ref{eq:classification loss},
+  shown in Equ. \ref{eq:classification_loss},
 
@@
       \mathcal{L}^{C}&=\frac{1}{N}\sum_{i=1}^{N}-log(\frac{exp(\varPhi_{i,y_{i}}^C)}{\sum_{j=1}^{C}exp(\varPhi_{i,j}^C)}) \\
-      \label{eq:classification loss}
+      \label{eq:classification_loss}
     \end{aligned}
@@
   $N$  data  points,  in  which $x_{i}$ is the user input query and $y_{i}$ is a
-  single  class label from a class label set of $C$ classes in total. If we want
-  to             generate            sentence            pair            dataset
-  $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$,   where   $(x,   x')_{j}$  is
-  generated  from two user history queries \footnote{For simplicty, we use query
-  to denote a user's question or a response.} and $l_{j}\in\{0, 1\}$ denotes the
-  similarity label, see Equ. \ref{eq:similarity label},
-  \begin{align}
-    l_{j}=
-    \begin{cases} \label{eq:similarity label}
-      0 & y_{x}\neq y_{x'}\\
-      1 & y_{x}=y_{x'}
-    \end{cases}
-  \end{align}
-  directly  from  original  dataset $\mathcal{D}$ without any sampling strategy,
-  then  $\mathcal{D'}$  will have $M=N^2$ data points of sentence pairs. That is
-  time-consuming  for  the  training  in stage 2 since we often have hundreds of
-  class  labels  under task-specific chatbot scenario. Though we may only have a
-  few data points for a single class label, $M$ is still prohibitively large.
+  single  class label from a class label set of $C$ classes in total. We 
+  generate            a sentence            pair            dataset
+  $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$ from $\mathcal{D}$,   where   $(x,   x')_{j}$  is
+  a pair of two history queries \footnote{For simplicty, we use query
+  to denote a user's question or a response.}, and $l_{j}\in\{0, 1\}$ denotes the
+  similarity label that the ones from the same class label are considered
+  similar. The size of $\mathcal{D'}$  would be up to $O(N^2)$ if no any
+  sampling strategy is used.  This is quite time-consuming  for the  training
+  in stage 2 because $N$ can be several hundreds or thousands even under 
+  few shot setting in task-specific chatbot scenario.
 
@@
   The  first step is \emph{positive sentence pair sampling}. During the training
-  process,  we first make sure the ground truth class label $y_{i}$
-  for  $x_{i}$  is  within  the  candidate  class  label  set $\mathcal{C'}$. If
-  $y_{i}\notin  \mathcal{C'}$,  we manually add $y_{i}$ into $\mathcal{C'}$
-  by  replacing  $c'_{K}$  with  $y_{i}$,  since $c'_{K}$ is the least promising
-  candidate  label  according  to the auxiliary model in stage 1. Afterwards, we
-  will randomly sample $P$ sentences $\{x'_{0},x'_{1}, \dots, x'_{P}\}$ with the
-  same  class  label  as  $y_{i}$  from dataset $\mathcal{D}$ to form the set of
-  sentence  pairs  with positive label $\mathcal{P'}_{i}=\{[(x_{i}, x'_{0}), 1],
-  [(x_{i},  x'_{1}),  1],  \dots,  [(x_{i},  x'_{P}), 1]\}$, where $P$ is also a
-  hyperparameter  set  to control  the number of sentences we should
-  sample from each class.
+  process,  we  first make sure the ground truth class label $y_{i}$ for $x_{i}$
+  is  within  the  candidate  class  label  set  $\mathcal{C'}$. If $y_{i}\notin
+  \mathcal{C'}$,  we  manually  add  $y_{i}$  into  $\mathcal{C'}$  by replacing
+  $c'_{K}$  with  $y_{i}$, since $c'_{K}$ is the least promising candidate label
+  according  to  the  auxiliary  model  in stage 1. Afterwards, we will randomly
+  sample  $P$ sentences $\{x'_{1}, \dots, x'_{P}\}$ with the same class label as
+  $y_{i}$  from  dataset  $\mathcal{D}$  to  form the set of sentence pairs with
+  positive  label  $\mathcal{P'}_{i}=\{[(x_{i},  x'_{1}),  1],  \dots,  [(x_{i},
+  x'_{P}),  1]\}$,  where $P$ is also a hyperparameter set to control the number
+  of sentences we should sample from each class.
 
@@
   same  method  as  positive  sentence  pair  sampling, we can obtain the set of
-  sentence  pairs  with  negative label as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{0}),
-  0], [(x_{i}, x'_{1}), 0], ..., [(x_{i}, x'_{P\cdot (K-1)}), 0]\}$
+  sentence  pairs  with  negative label as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{1}),
+  0], ..., [(x_{i}, x'_{P\cdot K}), 0]\}$
 
-  In  this  way,  we  generate the sentence pair dataset $\mathcal{D'}$ for
-  stage  2 based on the top-K class label set $\mathcal{C'}$ provided by stage 1
-  as   $\mathcal{D'}=\{\mathcal{P'}_{i}\cup   \mathcal{N'}_{i}\}_{i=1}^{N}$,  in
-  which we have $M=N\cdot K\cdot P$ data points of sentence pairs in total.
+  In  this way, we generate the sentence pair dataset $\mathcal{D'}$ for stage 2
+  based  on  the  top-K  class  label  set $\mathcal{C'}$ provided by stage 1 as
+  $\mathcal{D'}=\{\mathcal{P'}_{i}\cup  \mathcal{N'}_{i}\}_{i=1}^{N}$,  in which
+  we have $M=N\cdot K\cdot P$ data points of sentence pairs in total.
 
@@
   to  the  loss  to eliminate the bias brought by data imbalance, shown in Equ.
-  \ref{eq:similarity loss}.
+  \ref{eq:similarity_loss}.
 
@@
       \mathcal{L}^{S}&=\frac{1}{M}\sum_{i=1}^{M}-w^S_{l_i}\cdot log(\frac{exp(\varPhi_{i,l_{i}}^S)}{\sum_{j=0}^{1}exp(\varPhi_{i,j}^S)}) \\
-      \label{eq:similarity loss}
+      \label{eq:similarity_loss}
     \end{aligned}
@@
   ${\xi}^{K,pos}_{i}$ and ${\xi}^{K,neg}_{i}$. The loss for top-K classification
-  task is shown in Equ. \ref{eq:top-k classification loss}. In Equ. \ref{eq: pos
+  task is shown in Equ. \ref{eq:top-k_classification_loss}. In Equ. \ref{eq: pos
   top-k   loss}   and   Equ.   \ref{eq:   neg   top-k   loss},  the  first  term
@@
     \mathcal{L}^{K} = \frac{1}{N}\sum_{i=1}^{N}(\mathcal{L}^{K,pos}_{i} - \mathcal{L}^{K,neg}_{i})
-    \label{eq:top-k classification loss}
+    \label{eq:top-k_classification_loss}
   \end{align}
@@
   $\alpha_K$  are  weights  of  task  1  and  task  2  respectively.
-  which  are
-  $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting.
 
@@
           \hline 
-        \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} & \textbf{\#Samples} & \textbf{\#Samples/Class} & \textbf{Experimental Settings}\tabularnewline
+          \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} &
+          \textbf{\#Training Samples} & \textbf{\#Samples/Class} & \textbf{Experimental Settings}\tabularnewline
           \hline 
@@
           \hline 
-        Amazon-670k & Product review & 250 & 1942 & 8 & class sampling\tabularnewline
+          Amazon-670k & Product review & 250 & 1942 & 8 & 3-fold\tabularnewline
           \hline 
@@
     \label{tbe:dataset statistic}
+  \end{table*}
+
+  \begin{table*}
+    \begin{centering}
+      \scalebox{0.55}{
+        \begin{tabular}{|c|cccccc|cccccc|cccccc|c|c|}
+          \hline 
+          \multicolumn{1}{|c|}{\multirow{2}*{\textbf{Models}} }& \multicolumn{6}{c|}{\textbf{CLINC150}}& \multicolumn{6}{c|}{\textbf{BANKING77}}& \multicolumn{6}{c|}{\textbf{HWU64}}& \ \ \ \textbf{ITG} \ \ \ & \textbf{Amazon-670k}\tabularnewline
+          \cline{2-21}
+          \multicolumn{1}{|c|}{} & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$
+          & $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & $\textbf{5}$ &
+          $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{30}$ &
+          $\textbf{50}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ &
+          $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & \textbf{3-fold} &
+          \textbf{3-fold}\tabularnewline
+          \hline
+          TextCNN & \multirow{2}*{$0.5318$} & \multirow{2}*{$0.6963$} & \multirow{2}*{$0.7609$} & \multirow{2}*{$0.8142$} & \multirow{2}*{$0.8526$} & \multirow{2}*{$0.8867$} & \multirow{2}*{$0.4408$} & \multirow{2}*{$0.6436$} & \multirow{2}*{$0.7366$} & \multirow{2}*{$0.7918$} & \multirow{2}*{$0.8228$} & \multirow{2}*{$0.8619$} & \multirow{2}*{$0.3112$} & \multirow{2}*{$0.4007$} & \multirow{2}*{$0.4823$} & \multirow{2}*{$0.5272$} & \multirow{2}*{$0.5782$} & \multirow{2}*{$0.6262$} & \multirow{2}*{$0.6624$} & \multirow{2}*{$0.4401$}\tabularnewline
+          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
+          LEAM & \multirow{2}*{$0.7514$} & \multirow{2}*{$0.8203$} & \multirow{2}*{$0.8612$} & \multirow{2}*{$0.8802$} & \multirow{2}*{$0.9010$} & \multirow{2}*{$0.9180$} & \multirow{2}*{$0.5422$} & \multirow{2}*{$0.7812$} & \multirow{2}*{$0.8129$} & \multirow{2}*{$0.8280$} & \multirow{2}*{$0.8610$} & \multirow{2}*{$0.8727$} & \multirow{2}*{$0.4545$} & \multirow{2}*{$0.5554$} & \multirow{2}*{$0.5936$} & \multirow{2}*{$0.6599$} & \multirow{2}*{$0.6855$} & \multirow{2}*{$0.7046$} & \multirow{2}*{$0.7086$} & \multirow{2}*{$0.6091$}\tabularnewline
+          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
+          \hline
+          BERT-large & \multirow{2}*{$0.8080$} & \multirow{2}*{$0.8904$} & \multirow{2}*{$0.9265$} & \multirow{2}*{$0.9334$} & \multirow{2}*{$0.9497$} & \multirow{2}*{$0.9595$} & \multirow{2}*{$0.5780$} & \multirow{2}*{$0.8004$} & \multirow{2}*{$0.8518$} & \multirow{2}*{$0.8827$} & \multirow{2}*{$0.8858$} & \multirow{2}*{$0.8982$} & \multirow{2}*{$0.4711$} & \multirow{2}*{$0.5963$} & \multirow{2}*{$0.6342$} & \multirow{2}*{$0.7010$} & \multirow{2}*{$0.7117$} & \multirow{2}*{$0.7424$} & \multirow{2}*{$0.7485$} & \multirow{2}*{$0.6658$}\tabularnewline
+          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
+          ALBERT-xxlarge & \multirow{2}*{$0.8497$} & \multirow{2}*{$0.9008$} & \multirow{2}*{$0.9296$} & \multirow{2}*{$0.9297$} & \multirow{2}*{$0.9466$} & \multirow{2}*{$0.9578$} & \multirow{2}*{$0.5549$} & \multirow{2}*{$0.7981$} & \multirow{2}*{$0.8231$} & \multirow{2}*{$0.8530$} & \multirow{2}*{$0.8571$} & \multirow{2}*{$0.9096$} & \multirow{2}*{$0.4879$} & \multirow{2}*{$0.6116$} & \multirow{2}*{$0.6135$} & \multirow{2}*{$0.6996$} & \multirow{2}*{$0.7094$} & \multirow{2}*{$0.7376$} & \multirow{2}*{$0.7253$} & \multirow{2}*{$0.6893$}\tabularnewline
+          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
+          RoBERTa-base & \multirow{2}*{$0.8732$} & \multirow{2}*{$0.9254$} & \multirow{2}*{$0.9363$} & \multirow{2}*{$0.9482$} & \multirow{2}*{$0.9558$} & \multirow{2}*{$0.9637$} & \multirow{2}*{$0.7305$} & \multirow{2}*{$0.8654$} & \multirow{2}*{$0.8808$} & \multirow{2}*{$0.9080$} & \multirow{2}*{$0.9061$} & \multirow{2}*{$0.9293$} & \multirow{2}*{$0.5831$} & \multirow{2}*{$0.6790$} & \multirow{2}*{$0.7064$} & \multirow{2}*{$0.7100$} & \multirow{2}*{$0.7320$} & \multirow{2}*{$0.7472$} & \multirow{2}*{$0.7734$} & \multirow{2}*{$0.6708$}\tabularnewline
+          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
+          \hline
+          RoBERTa-large & \multirow{2}*{$\textbf{0.8974i}$} &
+          \multirow{2}*{$\textbf{0.9372}$} & \multirow{2}*{$\textbf{0.9508}$} &
+          \multirow{2}*{$\textbf{0.9584}$} & \multirow{2}*{$\textbf{0.9621}$} & 
+          \multirow{2}*{$\textbf{0.9733}$} & \multirow{2}*{$\textbf{0.7690}$} & 
+          \multirow{2}*{$\textbf{0.8728}$} & \multirow{2}*{$\textbf{0.8966}$} & 
+          \multirow{2}*{$\textbf{0.9099}$} & \multirow{2}*{$i\textbf{0.9227}$} & 
+          \multirow{2}*{$\textbf{0.9313}$} & \multirow{2}*{$\textbf{0.6044}$} & 
+          \multirow{2}*{$\textbf{0.7002}$} & \multirow{2}*{$\textbf{0.7129}$} & 
+          \multirow{2}*{$\textbf{0.7436}$} & \multirow{2}*{$\textbf{0.7493}$} & 
+          \multirow{2}*{$\textbf{0.7678}$} & \multirow{2}*{$\textbf{0.7990}$} & 
+          \multirow{2}*{$\textbf{0.7156}$}\tabularnewline
+          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
+          RoBERTa-large & \multirow{2}*{$0.8266$} & \multirow{2}*{$0.8861$} & \multirow{2}*{$0.9023$} & \multirow{2}*{$0.9084$} & \multirow{2}*{$0.9090$} & \multirow{2}*{$0.9407$} & \multirow{2}*{$0.757$} & \multirow{2}*{$0.8476$} & \multirow{2}*{$0.8614$} & \multirow{2}*{$0.8743$} & \multirow{2}*{$0.8749$} & \multirow{2}*{$0.8980$} & \multirow{2}*{$0.5425$} & \multirow{2}*{$0.6164$} & \multirow{2}*{$0.6503$} & \multirow{2}*{$0.6729$} & \multirow{2}*{$0.6947$} & \multirow{2}*{$0.7231$} & \multirow{2}*{$0.7418$} & \multirow{2}*{$0.6362$}\tabularnewline
+          (similarity) & & & & & & & & & & & & & & & & & & & &\tabularnewline
+          \hline
+          2-stage SFC & \multirow{2}*{$0.8979$} & \multirow{2}*{$0.9457$} & \multirow{2}*{$0.9517$} & \multirow{2}*{$0.9591$} & \multirow{2}*{$0.9610$} & \multirow{2}*{$0.9664$} & \multirow{2}*{$0.7975$} & \multirow{2}*{$0.8818$} & \multirow{2}*{$0.8962$} & \multirow{2}*{$0.9109$} & \multirow{2}*{$0.9187$} & \multirow{2}*{$0.9198$} & \multirow{2}*{$0.6477$} & \multirow{2}*{$0.7055$} & \multirow{2}*{$0.7200$} & \multirow{2}*{$0.7232$} & \multirow{2}*{$0.7484$} & \multirow{2}*{$0.7653$} & \multirow{2}*{$0.7972$} & \multirow{2}*{$0.7189$}\tabularnewline
+          (task1) & & & & & & & & & & & & & & & & & & & &\tabularnewline
+          2-stage SFC & \multirow{2}*{$0.9162$} & \multirow{2}*{$0.9424$} & \multirow{2}*{$0.9530$} & \multirow{2}*{$0.9617$} & \multirow{2}*{$0.9633$} & \multirow{2}*{$0.9690$} & \multirow{2}*{$0.7997$} & \multirow{2}*{$0.8823$} & \multirow{2}*{$0.8945$} & \multirow{2}*{$0.9123$} & \multirow{2}*{$0.9236$} & \multirow{2}*{$0.9317$} & \multirow{2}*{$0.6498$} & \multirow{2}*{$0.6980$} & \multirow{2}*{$0.7202$} & \multirow{2}*{$0.7358$} & \multirow{2}*{$0.7498$} & \multirow{2}*{$0.7657$} & \multirow{2}*{$0.8020$} & \multirow{2}*{$0.7311$}\tabularnewline
+          (task2) & & & & & & & & & & & & & & & & & & & &\tabularnewline
+          2-stage SFC & \multirow{2}*{$0.9167$} & \multirow{2}*{$0.9456$} & \multirow{2}*{$0.9571$} & \multirow{2}*{$0.9638$} & \multirow{2}*{$0.9658$} & \multirow{2}*{$0.9753$} & \multirow{2}*{$0.8135$} & \multirow{2}*{$0.8854$} & \multirow{2}*{$0.8931$} & \multirow{2}*{$0.9192$} & \multirow{2}*{$0.9257$} & \multirow{2}*{$0.9339$} & \multirow{2}*{$0.6525$} & \multirow{2}*{$0.7092$} & \multirow{2}*{$0.7168$} & \multirow{2}*{$0.7476$} & \multirow{2}*{$0.7519$} & \multirow{2}*{$0.7696$} & \multirow{2}*{$\textbf{0.8124}$} & \multirow{2}*{$0.7364$}\tabularnewline
+          (task1 + task2) & & & & & & & & & & & & & & & & & & & &\tabularnewline
+          \hline
+          \multirow{2}*{Joint SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.9669}$} & \multirow{2}*{$\textbf{0.9712}$} & \multirow{2}*{$\textbf{0.9821}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.9323}$} & \multirow{2}*{$\textbf{0.9463}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$\textbf{0.7593}$} & \multirow{2}*{$\textbf{0.7772}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline
+          & & & & & & & & & & & & & & & & & & & &\tabularnewline
+          \hline
+        \end{tabular}
+      }
+      \par
+    \end{centering}
+    \caption{
+      F-scores  on  five  task-specific  datasets text classification in chatbot
+      under low resource. For ITG, we keep the full dataset. For Amazon-670k, we
+      randomly  sampled  250  classes  with  training sample numbers within 5-15
+      samples  per  class.  For  CLINC150,  BANKING77,  HWU64, we set up various
+      few-shot  settings  (5/10/15/20/30/50 samples per class) while keeping the
+      test  set to be fixed. The highest scores for each data setting are marked
+      in bold.
+    }
+    \label{tbe:table2}
   \end{table*}
@@
   the   task-specific  losses,  shown  in  Equ.  \ref{eq:joint_SFC_loss}.  Here,
-  $\alpha_S$,   $\alpha_K$   and   $\alpha_C$   represent the  weights  for  task  1,
-  sentence-pair  similarity,  task  2,  top-K classification and task 3, general
-  single sentence classification respectively.
+  $\alpha_S$,  $\alpha_K$  and  $\alpha_C$  represent  the  weights  for  task 1
+  sentence-pair  similarity  in  Equ.  \ref{eq:similarity_loss},  task  2  top-K
+  classification  in Equ. \ref{eq:top-k_classification_loss}, and task 3 general
+  single       sentence       classification      respectively      in      Equ.
+  \ref{eq:classification_loss}.
+
   \begin{align}
@@
   the  datasets from other short text classification research, such as semantics
-  classification  with  very  limited  semantics labels and several sentences as
+  classification  with  very  limited  semantics labels and relatively longer
   input,   the   datasets  adopted  in  our  experiments  are  typically  having
@@
   hundreds,  and  each  class  label  is  associated  with  a handful of labeled
-  queries,  and  each  query  is  usually  one  sentence. Table \ref{tbe:dataset
+  queries with each  query  being usually  one  sentence. Table \ref{tbe:dataset
   statistic} displays their statistics.
-
-  \begin{table*}
-    \begin{centering}
-      \scalebox{0.55}{
-        \begin{tabular}{|c|cccccc|cccccc|cccccc|c|c|}
-          \hline 
-          \multicolumn{1}{|c|}{\multirow{2}*{\textbf{Models}} }& \multicolumn{6}{c|}{\textbf{CLINC150}}& \multicolumn{6}{c|}{\textbf{BANKING77}}& \multicolumn{6}{c|}{\textbf{HWU64}}& \ \ \ \textbf{ITG} \ \ \ & \textbf{Amazon-670k}\tabularnewline
-          \cline{2-21}
-          \multicolumn{1}{|c|}{} & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & \textbf{Full} & \textbf{Full}\tabularnewline
-          \hline
-          TextCNN & \multirow{2}*{$0.5318$} & \multirow{2}*{$0.6963$} & \multirow{2}*{$0.7609$} & \multirow{2}*{$0.8142$} & \multirow{2}*{$0.8526$} & \multirow{2}*{$0.8867$} & \multirow{2}*{$0.4408$} & \multirow{2}*{$0.6436$} & \multirow{2}*{$0.7366$} & \multirow{2}*{$0.7918$} & \multirow{2}*{$0.8228$} & \multirow{2}*{$0.8619$} & \multirow{2}*{$0.3112$} & \multirow{2}*{$0.4007$} & \multirow{2}*{$0.4823$} & \multirow{2}*{$0.5272$} & \multirow{2}*{$0.5782$} & \multirow{2}*{$0.6262$} & \multirow{2}*{$0.6624$} & \multirow{2}*{$0.4401$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          LEAM & \multirow{2}*{$0.7514$} & \multirow{2}*{$0.8203$} & \multirow{2}*{$0.8612$} & \multirow{2}*{$0.8802$} & \multirow{2}*{$0.9010$} & \multirow{2}*{$0.9180$} & \multirow{2}*{$0.5422$} & \multirow{2}*{$0.7812$} & \multirow{2}*{$0.8129$} & \multirow{2}*{$0.8280$} & \multirow{2}*{$0.8610$} & \multirow{2}*{$0.8727$} & \multirow{2}*{$0.4545$} & \multirow{2}*{$0.5554$} & \multirow{2}*{$0.5936$} & \multirow{2}*{$0.6599$} & \multirow{2}*{$0.6855$} & \multirow{2}*{$0.7046$} & \multirow{2}*{$0.7086$} & \multirow{2}*{$0.6091$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-          BERT-large & \multirow{2}*{$0.8080$} & \multirow{2}*{$0.8904$} & \multirow{2}*{$0.9265$} & \multirow{2}*{$0.9334$} & \multirow{2}*{$0.9497$} & \multirow{2}*{$0.9595$} & \multirow{2}*{$0.5780$} & \multirow{2}*{$0.8004$} & \multirow{2}*{$0.8518$} & \multirow{2}*{$0.8827$} & \multirow{2}*{$0.8858$} & \multirow{2}*{$0.8982$} & \multirow{2}*{$0.4711$} & \multirow{2}*{$0.5963$} & \multirow{2}*{$0.6342$} & \multirow{2}*{$0.7010$} & \multirow{2}*{$0.7117$} & \multirow{2}*{$0.7424$} & \multirow{2}*{$0.7485$} & \multirow{2}*{$0.6658$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          ALBERT-xxlarge & \multirow{2}*{$0.8497$} & \multirow{2}*{$0.9008$} & \multirow{2}*{$0.9296$} & \multirow{2}*{$0.9297$} & \multirow{2}*{$0.9466$} & \multirow{2}*{$0.9578$} & \multirow{2}*{$0.5549$} & \multirow{2}*{$0.7981$} & \multirow{2}*{$0.8231$} & \multirow{2}*{$0.8530$} & \multirow{2}*{$0.8571$} & \multirow{2}*{$0.9096$} & \multirow{2}*{$0.4879$} & \multirow{2}*{$0.6116$} & \multirow{2}*{$0.6135$} & \multirow{2}*{$0.6996$} & \multirow{2}*{$0.7094$} & \multirow{2}*{$0.7376$} & \multirow{2}*{$0.7253$} & \multirow{2}*{$0.6893$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          RoBERTa-base & \multirow{2}*{$0.8732$} & \multirow{2}*{$0.9254$} & \multirow{2}*{$0.9363$} & \multirow{2}*{$0.9482$} & \multirow{2}*{$0.9558$} & \multirow{2}*{$0.9637$} & \multirow{2}*{$0.7305$} & \multirow{2}*{$0.8654$} & \multirow{2}*{$0.8808$} & \multirow{2}*{$0.9080$} & \multirow{2}*{$0.9061$} & \multirow{2}*{$0.9293$} & \multirow{2}*{$0.5831$} & \multirow{2}*{$0.6790$} & \multirow{2}*{$0.7064$} & \multirow{2}*{$0.7100$} & \multirow{2}*{$0.7320$} & \multirow{2}*{$0.7472$} & \multirow{2}*{$0.7734$} & \multirow{2}*{$0.6708$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          RoBERTa-large & \multirow{2}*{$0.8974$} & \multirow{2}*{$0.9372$} & \multirow{2}*{$0.9508$} & \multirow{2}*{$0.9584$} & \multirow{2}*{$0.9621$} & \multirow{2}*{$0.9733$} & \multirow{2}*{$0.7690$} & \multirow{2}*{$0.8728$} & \multirow{2}*{$0.8966$} & \multirow{2}*{$0.9099$} & \multirow{2}*{$0.9227$} & \multirow{2}*{$0.9313$} & \multirow{2}*{$0.6044$} & \multirow{2}*{$0.7002$} & \multirow{2}*{$0.7129$} & \multirow{2}*{$0.7436$} & \multirow{2}*{$0.7493$} & \multirow{2}*{$0.7678$} & \multirow{2}*{$0.7990$} & \multirow{2}*{$0.7156$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          RoBERTa-large & \multirow{2}*{$0.8266$} & \multirow{2}*{$0.8861$} & \multirow{2}*{$0.9023$} & \multirow{2}*{$0.9084$} & \multirow{2}*{$0.9090$} & \multirow{2}*{$0.9407$} & \multirow{2}*{$0.757$} & \multirow{2}*{$0.8476$} & \multirow{2}*{$0.8614$} & \multirow{2}*{$0.8743$} & \multirow{2}*{$0.8749$} & \multirow{2}*{$0.8980$} & \multirow{2}*{$0.5425$} & \multirow{2}*{$0.6164$} & \multirow{2}*{$0.6503$} & \multirow{2}*{$0.6729$} & \multirow{2}*{$0.6947$} & \multirow{2}*{$0.7231$} & \multirow{2}*{$0.7418$} & \multirow{2}*{$0.6362$}\tabularnewline
-          (similarity) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-          2-stage SFC & \multirow{2}*{$0.8979$} & \multirow{2}*{$0.9457$} & \multirow{2}*{$0.9517$} & \multirow{2}*{$0.9591$} & \multirow{2}*{$0.9610$} & \multirow{2}*{$0.9664$} & \multirow{2}*{$0.7975$} & \multirow{2}*{$0.8818$} & \multirow{2}*{$0.8962$} & \multirow{2}*{$0.9109$} & \multirow{2}*{$0.9187$} & \multirow{2}*{$0.9198$} & \multirow{2}*{$0.6477$} & \multirow{2}*{$0.7055$} & \multirow{2}*{$0.7200$} & \multirow{2}*{$0.7232$} & \multirow{2}*{$0.7484$} & \multirow{2}*{$0.7653$} & \multirow{2}*{$0.7972$} & \multirow{2}*{$0.7189$}\tabularnewline
-          (task1) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          2-stage SFC & \multirow{2}*{$0.9162$} & \multirow{2}*{$0.9424$} & \multirow{2}*{$0.9530$} & \multirow{2}*{$0.9617$} & \multirow{2}*{$0.9633$} & \multirow{2}*{$0.9690$} & \multirow{2}*{$0.7997$} & \multirow{2}*{$0.8823$} & \multirow{2}*{$0.8945$} & \multirow{2}*{$0.9123$} & \multirow{2}*{$0.9236$} & \multirow{2}*{$0.9317$} & \multirow{2}*{$0.6498$} & \multirow{2}*{$0.6980$} & \multirow{2}*{$0.7202$} & \multirow{2}*{$0.7358$} & \multirow{2}*{$0.7498$} & \multirow{2}*{$0.7657$} & \multirow{2}*{$0.8020$} & \multirow{2}*{$0.7311$}\tabularnewline
-          (task2) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          2-stage SFC & \multirow{2}*{$0.9167$} & \multirow{2}*{$0.9456$} & \multirow{2}*{$0.9571$} & \multirow{2}*{$0.9638$} & \multirow{2}*{$0.9658$} & \multirow{2}*{$0.9753$} & \multirow{2}*{$0.8135$} & \multirow{2}*{$0.8854$} & \multirow{2}*{$0.8931$} & \multirow{2}*{$0.9192$} & \multirow{2}*{$0.9257$} & \multirow{2}*{$0.9339$} & \multirow{2}*{$0.6525$} & \multirow{2}*{$0.7092$} & \multirow{2}*{$0.7168$} & \multirow{2}*{$0.7476$} & \multirow{2}*{$0.7519$} & \multirow{2}*{$0.7696$} & \multirow{2}*{$\textbf{0.8124}$} & \multirow{2}*{$0.7364$}\tabularnewline
-          (task1 + task2) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-          \multirow{2}*{Joint SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.9669}$} & \multirow{2}*{$\textbf{0.9712}$} & \multirow{2}*{$\textbf{0.9821}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.9323}$} & \multirow{2}*{$\textbf{0.9463}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$\textbf{0.7593}$} & \multirow{2}*{$\textbf{0.7772}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline
-          & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-        \end{tabular}
-      }
-      \par
-    \end{centering}
-    \caption{
-        F-scores on five task-specific dataset for text classification in chatbot under low resource.
-For ITG, we keep the full dataset.
-For Amazon-670k, we randomly sampled 250 classes with training sample numbers within 5-15 samples per class.
-For CLINC150, BANKING77, HWU64, we set up various few-shot settings (5/10/15/20/30/50 samples per class) while keeping the test set to be fixed.
-The highest scores for each data setting are marked in bold.
-    }
-    \label{tbe:table2}
-  \end{table*}
 
@@
 
-  \subsection{System description}
+  \subsection{Baselines}
   We choose three kinds of system to construct our baselines.
@@
     \item   \emph{Non-pretrained   model  based  classification  system},  which
-    consists  of  a popular CNN based TextCNN \cite{kim2014convolutional}, and a
-    recently  proposed label-embedding based LEAM (todo: reference and its label
-    setting). Empircally,
+    consists  of  a typical CNN based TextCNN \cite{kim2014convolutional}, and a
+    label-embedding based LEAM \cite{wang2018joint}. Regarding TextCNN, the
+    model is based on output from RoBERTa tokenization, and the kernels are set
+    as 1, 2, 3, 4, 5. Regarding LEAM, a literal class label is required, which
+    is available only in HWU64, CLINC150, BANKING77. Thus, for other two
+    datasets, we have to use its class number instead.  Empircally,
     a  non-pretrained  model  based  system  are  not  performing  as  well as a
@@
 
+  \subsection{Result Analysis}
+  All results in F-score (todo: reference) on the five datasets with different models and configurations are
+  showed in Table  \ref{tbe:table2}.
+
+  The performance of each model is measured in F-score on the fixed
+  test  set  for  each  dataset.  
+  Overall,  two-stage  SFC systems in multi-task training deliver  moderate 
+  improvements  over  corresponding baselines, and joint SFC deliver more
+  significant and consistent improvements over the best baseline, RoBERTa based
+  classification. In following content, we dive into more details.
+
+  \subsubsection*{Is multi-task and joint training working?} 
+  First, we compare the four  SFC  variants to analyze the improvement
+  brought  by  multi-task  and  joint-model  structure.
+
+  Comparing with training two-stage SFC with multi-task, training with only task
+  1,  corresponding  to  sentence pair similarity model, degrades by 0.8 percent
+  point  on average, and training with only task 2, corresponding to top-K based
+  classification  task,  degrades  by  0.45  percent  point  on  average.  These
+  degradation  indicates  multi-task training in two-stage SFC is helpful for the
+  system  performance.  Besides, task 2 play a relatively more important role in
+  multi-task learning, and this aligns with their optimal weight settings.
+
+  Joint SFC consistently outperforms two-stage SFC on 5 diverse datasets by 0.95
+  percents  on  average. This observation supports the idea that the joint model
+  structure  can  alleviate  the  limitation  brought by the lack of interaction
+  between  two  stages.  In  following analysis, we will focus on the comparison
+  between joint SFC and the other baseline models.
+
+  \subsubsection*{Is  the  fusion of a classification model and similarity model
+  helpful?}  We  compare  the performance of joint SFC with classification based
+  and similarity based baselines.
+
   \begin{table*}
@@
     \caption{
-      We  show the performance of SFC from different settings of hyperparameters
-      for  $K$,  the candidate class number, and $P$, the sample number for each
-      class.
+      We  show the performances of SFC from different settings of
+      hyperparameters, $K$  denoting the candidate class number from stage 1,
+      $P$ denoting the number of sampled sententence pair in stage 2. 
     }
-
     \label{tbe:table3}
   \end{table*}
-
-  \subsection{Result Analysis}
-
-  Table  \ref{tbe:table2} presents all results on the five datasets model set-up
-  in  detail.  The performance of each model is measured in F-score on the fixed
-  test  set  for  each  dataset.  Overall,  two-stage  SFC systems show moderate
-  improvements  over  all  baseline systems. This observation gives us a general
-  idea  that  classification  model  and  similarity  model can actually provide
-  complementary  information  to  each  other,  and  combining them together can
-  enhance the overall capability based on richer extracted semantic information.
-  Furthermore, we also studied the performance among all the variants of SFCs on
-  different data settings to explore the benefits brought by multi-task training
-  and the joint-model structure.
-
-  \subsubsection*{Which SFC variant performs best?} 
-  First, we compare the four  SFC  variants to analyze the improvement
-  brought  by  multi-task  and  joint-model  structure.
-
-  Comparing with training two-stage SFC with multi-task, training with only task
-  1,  corresponding  to  sentence pair similarity model, degrades by 0.8 percent
-  point  on average, and training with only task 2, corresponding to top-K based
-  classification  task,  degrades  by  0.45  percent  point  on  average.  These
-  degradation  indicates  multi-task training in two-stage SFC is helpful for the
-  system  performance.  Besides, task 2 play a relatively more important role in
-  multi-task learning, and this aligns with their optimal weight settings.
-
-  Joint SFC consistently outperforms two-stage SFC on 5 diverse datasets by 0.95
-  percents  on  average. This observation supports the idea that the joint model
-  structure  can  alleviate  the  limitation  brought by the lack of interaction
-  between  two  stages.  In  following analysis, we will focus on the comparison
-  between joint SFC and the other baseline models.
-
-  \subsubsection*{Is  the  fusion of a classification model and similarity model
-  helpful?}  We  compare  the performance of joint SFC with classification based
-  and similarity based baselines.
 
@@
 
-  \subsubsection*{How does joint SFC interact with the classfication in stage
-  1?}
+  \subsubsection*{Does joint SFC improve the classfication in stage 1?}
   {todo: content}
 
-  \subsubsection*{How does SFC perform with different  training  data  size} 
+  \subsubsection*{How does training sample size influence SFC?} 
   We analyze the
@@
 
-  \subsubsection*{How is joint SFC related to the label  embedding based  LEAM?}
+  \subsubsection*{How does joint SFC relate to the label  embedding based  LEAM?}
   LEAM performs consistently better than TextCNN by a large margin in all

### 2020-09-09 chatbot_classification/aaai_2021/paper.tex
modified:   paper.tex   new file:   paper.ver06.pdf

@@
 
-  {todo: Add joint NER and classification problem here.}
+  Another   line   of  interesting  work  is  the  joint  training  of  sentence
+  classification   and  NER  (todo:  reference).  If  both  the  city  and  date
+  information  are  recognized,  then  they  are good indicators that this query
+  might  be  booking  an  ticket. This work can also be combined in our proposed
+  framework.
 
@@
   of sentences we should sample from each class.
+
+\begin{table*}
+    \begin{centering}
+      \scalebox{0.9}{
+        \begin{tabular}{|c|c|c|c|c|c|}
+          \hline 
+          \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} &
+          \textbf{\#Training Samples} & \textbf{\#Samples/Class} & \textbf{Experimental Settings}\tabularnewline
+          \hline 
+          ITG & FAQ chatbot & 228 & 3938 & 17 & 3-fold\tabularnewline
+          \hline 
+          Amazon-670k & Product review & 250 & 1942 & 8 & 3-fold\tabularnewline
+          \hline 
+          HWU64 & intention detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
+          \hline 
+          CLINC150 & intention detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
+          \hline 
+          BANKING77 & intention detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
+          \hline 
+        \end{tabular}
+      }
+      \par
+    \end{centering}
+    \caption{Statistics for all datasets and few shot settings\footnote{All
+    settings of four public datasets would be released to github soon}.}
+
+    \label{tbe:dataset statistic}
+  \end{table*}
 
@@
     \begin{centering}
-      \scalebox{0.9}{
-        \begin{tabular}{|c|c|c|c|c|c|}
-          \hline 
-          \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} &
-          \textbf{\#Training Samples} & \textbf{\#Samples/Class} & \textbf{Experimental Settings}\tabularnewline
-          \hline 
-          ITG & FAQ chatbot & 228 & 3938 & 17 & 3-fold\tabularnewline
-          \hline 
-          Amazon-670k & Product review & 250 & 1942 & 8 & 3-fold\tabularnewline
-          \hline 
-          HWU64 & intention detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
-          \hline 
-          CLINC150 & intention detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
-          \hline 
-          BANKING77 & intention detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
-          \hline 
-        \end{tabular}
-      }
-      \par
-    \end{centering}
-    \caption{Statistics for all datasets and few shot settings\footnote{All
-    settings of four public datasets would be released to github soon}.}
-
-    \label{tbe:dataset statistic}
-  \end{table*}
-
-  \begin{table*}
-    \begin{centering}
       \scalebox{0.55}{
@@
     \caption{
-      F-scores  on  five  task-specific  datasets text classification in chatbot
+      F1 scores  on  five  task-specific  datasets text classification in chatbot
       under low resource. For ITG, we keep the full dataset. For Amazon-670k, we
@@
   Besides,  we  set  the  max number of the epoch to 100 and save the best model on
-  validation  set based on testing result in weighted F-score (todo: reference). 
-  We report the F-score as the main evaluation measure for all experiments.
+  validation  set based on testing result in weighted F1 score (todo: reference). 
+  We report the F1 score as the main evaluation measure for all experiments.
 
@@
   \subsection{Result Analysis}
-  All results in F-score (todo: reference) on the five datasets with different models and configurations are
+  All results in F1 score (todo: reference) on the five datasets with different models and configurations are
   showed in Table  \ref{tbe:table2}.
 
-  The performance of each model is measured in F-score on the fixed
+  The performance of each model is measured in F1 score on the fixed
   test  set  for  each  dataset.  
@@
 
-  \subsubsection*{Is multi-task and joint training working?} 
+  \subsubsection*{Are multi-task and joint training working?} 
   First, we compare the four  SFC  variants to analyze the improvement
@@
   Comparing with training two-stage SFC with multi-task, training with only task
-  1,  corresponding  to  sentence pair similarity model, degrades by 0.8 percent
-  point  on average, and training with only task 2, corresponding to top-K based
+  1,  namely the sentence pair similarity model, degrades by 0.8 percent
+  point  on average, and training with only task 2, namely the top-K based
   classification  task,  degrades  by  0.45  percent  point  on  average.  These
   degradation  indicates  multi-task training in two-stage SFC is helpful for the
-  system  performance.  Besides, task 2 play a relatively more important role in
+  system  performance.  Besides, task 2 plays a relatively more important role in
   multi-task learning, and this aligns with their optimal weight settings.
 
-  Joint SFC consistently outperforms two-stage SFC on 5 diverse datasets by 0.95
-  percents  on  average. This observation supports the idea that the joint model
+  Joint SFC consistently outperforms two-stage SFC with multi-task training  
+  on 5 diverse datasets by 0.95 percents  on  average. 
+  This observation supports the idea that the joint model
   structure  can  alleviate  the  limitation  brought by the lack of interaction
@@
 
-  \subsubsection*{Is  the  fusion of a classification model and similarity model
+  \subsubsection*{Is  the  fusion of a classification model and a similarity model
   helpful?}  We  compare  the performance of joint SFC with classification based
@@
   percent points, BERT-large  by  7.73 percent points, RoBERTa-base by 3.79 
-  percent points, RoBERTa-large by 2.04 percents on average F-score over 5 datasets.  
+  percent points, RoBERTa-large by 2.04 percents on average F1 score over 5 datasets.  
   Especially, ALBERT.xxlarge based is much more  unstable  in our senario. Thus, 
@@
   \subsubsection*{Does joint SFC improve the classfication in stage 1?}
-  {todo: content}
+  We  compare  the  top  1  predition and top 5 candidate labels in stage 1 from
+  two-stage SFC and joint SFC in Table \ref{tbe:top1_5_accuracy}. We should note
+  that  two-stage  SFC  does not optimize the stage 1 result, which is a RoBERTa
+  based classification model.
+
+  \begin{table}
+    \begin{centering}
+      \begin{tabular}{|c|c|c|c|c|}
+        \hline
+        F1 score & Two-stage SFC & Joint SFC & Gap & \tabularnewline
+        \hline
+        top-1 accuracy  & \textbf{81.50} & 81.07 & -0.47 & \tabularnewline
+        top-5 accuracy & 94.01 & \textbf{94.30} & +0.29 & \tabularnewline
+        \hline
+      \end{tabular}
+      \par
+    \end{centering}
+    \caption{The average classification accuracy in stage 1 on all five dataset.}
+    \label{tbe:top1_5_accuracy}
+  \end{table}
+
+  The joint training does not improve the classification performance in stage 1,
+  measured  by  top  1  accuracy.  However,  it  improves  the  quality of top 5
+  candidate  class  labels.  It  can  be  explained that, a classification model
+  inherently optimizes the objective loss, 0-1 error of top 1 here; the sentence
+  pair similairity model in the joint SFC poses positive effect in optimizing the 
+  candidate labels.
 
@@
   improvement   over  one  of  the  most  powerful  baseline  models,  which  is
-  RoBERTa-large  classification  model.  Moreover,  the  improvement  in F-score
+  RoBERTa-large  classification  model.  Moreover,  the  improvement  in F1 score
   becomes  more  and  more prominent with the decrease of data sample number per
@@
   by different settings of hyperparameters, joint SFC still steadily outperforms
-  two-stage  SFC  by  0.41  percents  in  overall  average  F-score  on  ITG and
+  two-stage  SFC  by  0.41  percents  in  overall  average  F1 score  on  ITG and
   Amazon-670k datasets.

### 2020-09-10 chatbot_classification/aaai_2021/paper.tex
modified:   paper.tex   new file:   picture/improvement_trend.jpg

@@
 
+  \begin{table}
+    \begin{centering}
+      \begin{tabular}{|c|c|c|c|c|}
+        \hline
+        F1 score & Two-stage SFC & Joint SFC & Gap & \tabularnewline
+        \hline
+        top-1 accuracy  & \textbf{81.50} & 81.07 & -0.47 & \tabularnewline
+        top-5 accuracy & 94.01 & \textbf{94.30} & +0.29 & \tabularnewline
+        \hline
+      \end{tabular}
+      \par
+    \end{centering}
+    \caption{The average classification accuracy in stage 1 on all five dataset.}
+    \label{tbe:top1_5_accuracy}
+  \end{table}
+
   Comparing with training two-stage SFC with multi-task, training with only task
@@
 
-  \begin{table}
-    \begin{centering}
-      \begin{tabular}{|c|c|c|c|c|}
-        \hline
-        F1 score & Two-stage SFC & Joint SFC & Gap & \tabularnewline
-        \hline
-        top-1 accuracy  & \textbf{81.50} & 81.07 & -0.47 & \tabularnewline
-        top-5 accuracy & 94.01 & \textbf{94.30} & +0.29 & \tabularnewline
-        \hline
-      \end{tabular}
-      \par
-    \end{centering}
-    \caption{The average classification accuracy in stage 1 on all five dataset.}
-    \label{tbe:top1_5_accuracy}
-  \end{table}
-
   The joint training does not improve the classification performance in stage 1,
@@
   \subsubsection*{How does training sample size influence SFC?} 
-  We analyze the
-  overall  improvement  trend  of  SFC under various few-shot settings.
+  We analyze the overall  improvement  trend  of  SFC under various few-shot
+  settings, and show results in Fig. \ref{fig:trend}.
 
-  Our main
-  focus  is  to  study  chatbot  building  in common situation during real-world
+  Our main focus  is  to  study  chatbot  building  in common situation during real-world
   application  where  only  a few sample sentences are available for each class.
   The  experimental  results  for  the  3  diverse  intention detection datasets
-  (ClINC150,  BANKING77,  HWU64)  under  few-shot  settings, 5 to 20 samples per
+  (ClINC150,  BANKING77,  HWU64)  under  few-shot  settings, 5 to 50 samples per
   class,  indicate that our proposed joint SFC can achieve 2.47 percents average
@@
   class.
+
+  \begin{figure}[t]
+    \begin{centering}
+      \includegraphics[scale=0.2]{picture/improvement_trend.jpg} 
+      \par
+    \end{centering}
+    \caption{
+      Improvements with different size of training data.
+    }
+    \label{fig:trend}
+  \end{figure}
 

### 2020-09-10 chatbot_classification/aaai_2021/paper.tex
update citation

@@
   classification  and  short  text  classification  in  this  scenario.  Besides
-  traditional  machine  learning  models  like  SVM,  boosting  tree,  many work
+  traditional  machine  learning  models  like  SVM \cite{suykens1999least},  boosting  tree \cite{tu2005probabilistic},  many work
   \cite{wen2016network}  choose  neural  network  such  as  convolutional neural
@@
   \cite{yu2018diverse},     pre-trained     model    based    on    transformers
-  \cite{vaswani2017attention}, shown in Fig. \ref{Fig.1.sub.1}, tends to do more
+  \cite{vaswani2017attention} tends to do more
   help to reducing the negative effects brought by scarcity of training data.
@@
   used  as  a  tool  to  identify  the class with highest semantic similarity to
-  customer's    query.    A    common    model    structure    of    pre-trained
-  \cite{devlin2018bert} sentence-pair model is based on multiple cross-attention
-  mechanism  \cite{barkan2020scalable},  shown in Fig. \ref{Fig.1.sub.2}. Due to
+  customer's    query.    A    common    model    structure    of    pre-trained sentence-pair model is based on multiple cross-attention
+  mechanism  \cite{barkan2020scalable}. Due to
   the   fact   that   many   experiment   results   have   shown   that  RoBERTa
-  \cite{liu2019roberta} is an improved version of BERT, and has achieved amazing
+  \cite{liu2019roberta} is an improved version of BERT \cite{devlin2018bert}, and has achieved amazing
   results  on  both  text  classification and sentence-pairs semantic similarity
@@
   calle  it  SFC,  short  for  similairty model fused with classification Model,
-  shown  in  Fig.  \ref{fig:ver.1.3}.  To  better train SFC, we further bring in
-  multi-task   learning   \cite{caruana1993multitask,collobert2008unified}.  Our
+  shown  in  Fig.  \ref{fig:framework}.  To  better train SFC, we further bring in
+  multi-task   learning   \cite{caruana1993multitask,collobert2008unified, liu2019multi}.  Our
   basic  idea  cames  from  two  stages. In the first stage, we use an auxiliary
@@
   sentence  pairs  with  negative label as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{1}),
-  0], ..., [(x_{i}, x'_{P\cdot K}), 0]\}$
+  0], ..., [(x_{i}, x'_{P\cdot (K-1)}), 0]\}$
 
@@
   sentence  pair. Then, we can do average pooling for each candidate class among
-  the  top-K  classes  as  shown  in  Equ.  \ref{eq:average  pooling:1} and Equ.
-  \ref{eq:average pooling:2}.
+  the  top-K  classes  as  shown  in  Equ.  \ref{eq:average  pooling}.
 
   \begin{align}
-    {\xi}_{i,j}^{K,pos} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,pos} \label{eq:average pooling:1}\\
+    {\xi}_{i,j}^{K,pos} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,pos} \ \ \ \ \ \ \ 
     {\xi}_{i,j}^{K,neg} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,neg}
-    \label{eq:average pooling:2}
+    \label{eq:average pooling}
   \end{align}
@@
           \hline
-          RoBERTa-large & \multirow{2}*{$\textbf{0.8974i}$} &
+          RoBERTa-large & \multirow{2}*{$\textbf{0.8974}$} &
           \multirow{2}*{$\textbf{0.9372}$} & \multirow{2}*{$\textbf{0.9508}$} &
@@
           \multirow{2}*{$\textbf{0.8728}$} & \multirow{2}*{$\textbf{0.8966}$} & 
-          \multirow{2}*{$\textbf{0.9099}$} & \multirow{2}*{$i\textbf{0.9227}$} & 
+          \multirow{2}*{$\textbf{0.9099}$} & \multirow{2}*{$\textbf{0.9227}$} & 
           \multirow{2}*{$\textbf{0.9313}$} & \multirow{2}*{$\textbf{0.6044}$} & 
@@
       few-shot  settings  (5/10/15/20/30/50 samples per class) while keeping the
-      test  set to be fixed. The highest scores for each data setting are marked
+      test  set to be fixed. The highest scores among all the baseline models and SFC variants for each data setting are both marked
       in bold.
@@
     \item \emph{Pretrained model based classification system}, which consists of
-    BERT,  RoBERTa,  and  ALBERT  \cite{lan2019albert}  based.  These pretrained
+    BERT \cite{devlin2018bert},  RoBERTa \cite{liu2019roberta},  and  ALBERT  \cite{lan2019albert}  based.  These pretrained
     models  are  practically  proven  to  achieve  outstanding  performances  in
@@
     is available only in HWU64, CLINC150, BANKING77. Thus, for other two
-    datasets, we have to use its class number instead.  Empircally,
+    datasets, we have to use its class number instead.  Empirically,
     a  non-pretrained  model  based  system  are  not  performing  as  well as a
@@
     \item   \emph{Pre-trained   model   based   similarity   model}.  We  choose
-    RoBERTa-large  as  our  fundermental  module as our SFC systems are based on
-    RoBERTa  too, and RoBERTa is empircally more effective than other pretrained
+    RoBERTa-large  as  our  fundamental  module as our SFC systems are based on
+    RoBERTa  too, and RoBERTa is empirically more effective than other pretrained
     models  in  the  short  text  classification  task  in  our  experiments. In

### 2020-09-10 chatbot_classification/aaai_2021/paper.tex
fix typo

@@
   identify  the  real  intention  behind  a  user's  question or reply. Then the
-  chatbot  is caple of conducting expected actions, text reply or accomplish some
+  chatbot  is capable of conducting expected actions, text reply or accomplish some
   operations.
@@
   thought  to  be  more  ambiguous  compared to long texts such as paragraphs or
-  documents,  poseing  a  great challenge \cite{chen2019deep} for classification
+  documents,  posing  a  great challenge \cite{chen2019deep} for classification
   task   \cite{phan2008learning,yan2009dynamic,hua2015short}.   Second,  in  the
@@
   The  second  one,  \emph{similarity model} is also called sentence-pair model.
-  Its  motivation  originates  from  the idea of Information Retrival (IR) based
+  Its  motivation  originates  from  the idea of Information Retrieval (IR) based
   chatbot   \cite{jafarpour2010filter,   leuski2011npceditor}.   Having   a  Q-A
@@
 
-  The  above limitation motivates us to propose a joint system that is capble of
-  taking  advantagges  from  both  classification model and similarity model. We
-  calle  it  SFC,  short  for  similairty model fused with classification Model,
+  The  above limitation motivates us to propose a joint system that is capable of
+  taking  advantages  from  both  classification model and similarity model. We
+  call  it  SFC,  short  for  similairty model fused with classification Model,
   shown  in  Fig.  \ref{fig:framework}.  To  better train SFC, we further bring in
   multi-task   learning   \cite{caruana1993multitask,collobert2008unified, liu2019multi}.  Our
-  basic  idea  cames  from  two  stages. In the first stage, we use an auxiliary
+  basic  idea  came  from  two  stages. In the first stage, we use an auxiliary
   model  to  select top-K most possible labels for a input. This model can be an
@@
   classification  model (SFC). We propose two approaches to implement this idea,
-  two-stageg SFC, and its more unified version joint-SFC.
+  two-stage SFC, and its more unified version joint-SFC.
 
@@
   $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$ from $\mathcal{D}$,   where   $(x,   x')_{j}$  is
-  a pair of two history queries \footnote{For simplicty, we use query
+  a pair of two history queries \footnote{For simplicity, we use query
   to denote a user's question or a response.}, and $l_{j}\in\{0, 1\}$ denotes the
@@
   Our experiments aim to study the short text classification in the low-resource
-  environment  popular  in  the  task-specific conversional chatbot application.
+  environment  popular  in  the  task-specific conversational chatbot application.
   Hence we choose and configure set datasets to serve this study. Different from
@@
 
-  Regarding  the first two datasets, we conduct 3-fold cross validata experients
+  Regarding  the first two datasets, we conduct 3-fold cross validation experiments
   that   70   percent   as  training,  15  percent  as  validation  and  testing
@@
   starts  with  merely  a  handful of labeled data available in the early stage.
-  Besides,  in  the  active  learning framework, building an effective anxiliary
+  Besides,  in  the  active  learning framework, building an effective auxiliary
   system  with limited resource is also quite important to help developers label
@@
   Our SFC systems include two-stage SFC with ablation, trained with two tasks
-  sperately and both, and joint SFC with all three tasks.
+  separately and both, and joint SFC with all three tasks.
 
@@
   weights  of  three  tasks  are  set  as  $\alpha_S=0.25$,  $\alpha_K=0.25$ and
-  $\alpha_C=0.5$  in  our setting. Overrall, the task weights are less sensitive
+  $\alpha_C=0.5$  in  our setting. Overall, the task weights are less sensitive
   in Joint SFC than in two-stage SFC.
@@
 
-  The above analysises illustrate that suitable fusing the classification model and the 
+  The above analysis illustrate that suitable fusing the classification model and the 
   similarity model to make them cooperate with each other is helpful to better
@@
 
-  \subsubsection*{Does joint SFC improve the classfication in stage 1?}
-  We  compare  the  top  1  predition and top 5 candidate labels in stage 1 from
+  \subsubsection*{Does joint SFC improve the classification in stage 1?}
+  We  compare  the  top  1  prediction and top 5 candidate labels in stage 1 from
   two-stage SFC and joint SFC in Table \ref{tbe:top1_5_accuracy}. We should note
@@
   scenario when there is no clear class label, the relationship between a sample
-  and  a class lable is implicatily encoded as that between a sample and another
+  and  a class label is implicitly encoded as that between a sample and another
   sample  from  the  same  class, and this turns into a sentence pair similarity
@@
   pairs  sampled for each user query into about the same level of amount(50-60).
-  Through  analyzing the experimenal results shown in Table \ref{tbe:table3}, we
+  Through  analyzing the experimental results shown in Table \ref{tbe:table3}, we
   find  that the best setting of hyperparameters might be different for datasets

### 2020-09-10 chatbot_classification/aaai_2021/paper.tex
from Zongcheng Ji.   modified:   paper.tex

@@
   Task-specific  conversational  chatbot  \cite{wen2016network}  has been applied
-  into  many practical products. For example, it can share the working burden of
+  into  many practical products. One typical example is to share the working burden of
   human  customer  service  agents  responsible  for  customers' questions about
-  certain  products  or services. Another example is the speech-based control in
+  certain  products  or services. Another one is the speech-based control in
   devices  like  intelligent  speakers, such as Siri, Google home, Baidu Xiaodu,
-  and smart home equipments. Regardless of whether these conversations belong to
-  single-turn or multi-turn, an essential technique underlying the chatbot is to
+  and smart home equipments, to name a few. Regardless of whether these conversations belong to
+  single or  multi-round, an essential technique underlying the chatbot is to
   identify  the  real  intention  behind  a  user's  question or reply. Then the
-  chatbot  is capable of conducting expected actions, text reply or accomplish some
+  chatbot  is capable of conducting expected actions, replying texts or accomplishing some
   operations.
 
-  It  is  a  challenging task due to some inherent properties. First,
+  Identifying intention  is  a  challenging task due to some inherent properties. First,
   a customer's  utterance  within  a conversation is usually quite short. Since it
-  does  not  contain  enough  information,  short  text \cite{song2014short} are
+  does  not  contain  enough  information,  short  texts \cite{song2014short} are
   thought  to  be  more  ambiguous  compared to long texts such as paragraphs or
@@
   examine tons of real system logs for typical user's utterances, and then label
-  them  with expected intentions. Therefore, the key to building a task-specific
-  chatbot  with  high  performance  becomes  solving the challenge of short-text
+  them  with expected intentions. Therefore, to build a task-specific chatbot with
+  high  performance, it is essential to solve the challenge of short-text
   classification   \cite{sriram2010short}   problem   under   few-shot   setting
@@
   Generally  there  are  two  kinds  of  approaches  to  address  this  problem,
-  classification model that directly maps an input into a most likely label, and
-  similarity  model  that searches a label whose associated data is most similar to
+  one is the classification model that directly maps an input into a most likely label, and
+  the other one is the similarity  model  that searches a label whose associated data is most similar to
   an input.
@@
   classification  and  short  text  classification  in  this  scenario.  Besides
-  traditional  machine  learning  models  like  SVM \cite{suykens1999least},  boosting  tree \cite{tu2005probabilistic},  many work
+  traditional  machine  learning  models  like  SVM \cite{suykens1999least},  
+  boosting  tree \cite{tu2005probabilistic},  many work
   \cite{wen2016network}  choose  neural  network  such  as  convolutional neural
@@
   used  as  a  tool  to  identify  the class with highest semantic similarity to
-  customer's    query.    A    common    model    structure    of    pre-trained sentence-pair model is based on multiple cross-attention
+  customer's    query.    A    common    model    structure    of    pre-trained 
+  sentence-pair model is based on multiple cross-attention
   mechanism  \cite{barkan2020scalable}. Due to
@@
   sentence  pairs  with  negative label as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{1}),
-  0], ..., [(x_{i}, x'_{P\cdot (K-1)}), 0]\}$
+  0], ..., [(x_{i}, x'_{P\cdot K}), 0]\}$
 

### 2020-09-10 chatbot_classification/aaai_2021/paper.tex
modify title
version 7
modified:   paper.tex

@@
 \usepackage{subfigure}
+\usepackage[switch]{lineno}
 \usepackage{spconf}
@@
   %SFC: Few-Shot Text Classification via Similarity Fused with Classification System
-  Joint training of classification model and similarity model for low-resource
-  text classification in chatbot
+  Joint Training of Classification and Similarity Models for \\ 
+  Intention Detection in Task-specific Chatbot
 }
@@
   \maketitle
+  \linenumbers
 
@@
     \end{centering}
-    \caption{Statistics for all datasets and few shot settings\footnote{All
-    settings of four public datasets would be released to github soon}.}
+    \caption{Statistics for all datasets and few shot settings.}
 
@@
   queries with each  query  being usually  one  sentence. Table \ref{tbe:dataset
-  statistic} displays their statistics.
+  statistic} displays their statistics.  All settings of four public datasets would 
+  be released to github soon.
 
@@
   Besides,  we  set  the  max number of the epoch to 100 and save the best model on
-  validation  set based on testing result in weighted F1 score (todo: reference). 
+  validation  set based on testing result in weighted F1 score
+  \footnote{In the multi-class and multi-label case, this is the average of the
+  F1 score of each class with weighting depending on the numbers in each class.}.
   We report the F1 score as the main evaluation measure for all experiments.
@@
   \subsection{Result Analysis}
-  All results in F1 score (todo: reference) on the five datasets with different models and configurations are
-  showed in Table  \ref{tbe:table2}.
+  All  results  in  F1  score  on  the  five  datasets with different models and
+  configurations are showed in Table \ref{tbe:table2}.
 

### 2020-09-10 chatbot_classification/aaai_2021/paper.tex
modified:   paper.tex

@@
           (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
           RoBERTa-large & \multirow{2}*{$\textbf{0.8974}$} &
@@
           (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
+          \hline
           RoBERTa-large & \multirow{2}*{$0.8266$} & \multirow{2}*{$0.8861$} & \multirow{2}*{$0.9023$} & \multirow{2}*{$0.9084$} & \multirow{2}*{$0.9090$} & \multirow{2}*{$0.9407$} & \multirow{2}*{$0.757$} & \multirow{2}*{$0.8476$} & \multirow{2}*{$0.8614$} & \multirow{2}*{$0.8743$} & \multirow{2}*{$0.8749$} & \multirow{2}*{$0.8980$} & \multirow{2}*{$0.5425$} & \multirow{2}*{$0.6164$} & \multirow{2}*{$0.6503$} & \multirow{2}*{$0.6729$} & \multirow{2}*{$0.6947$} & \multirow{2}*{$0.7231$} & \multirow{2}*{$0.7418$} & \multirow{2}*{$0.6362$}\tabularnewline
@@
     \end{centering}
-    \caption{The average classification accuracy in stage 1 on all five dataset.}
+    \caption{The average classification accuracy in percentage in stage 1 on all five dataset.}
     \label{tbe:top1_5_accuracy}
@@
 
-  \subsubsection*{Is  the  fusion of a classification model and a similarity model
-  helpful?}  We  compare  the performance of joint SFC with classification based
-  and similarity based baselines.
+  \subsubsection*{Is  the  fusion of classification and similarity models
+  helpful?}  We  compare  joint SFC with classification and similarity based
+  baselines respectively.
 
@@
   Regarding the  classification  models,  joint SFC
-  outperforms    TextCNN    by   21.52   percent points,   ALBERT-xxlarge   by   7.99
-  percent points, BERT-large  by  7.73 percent points, RoBERTa-base by 3.79 
-  percent points, RoBERTa-large by 2.04 percents on average F1 score over 5 datasets.  
-  Especially, ALBERT.xxlarge based is much more  unstable  in our senario. Thus, 
-  we did multiple run with different settings, e.g.,  learning rate and batch size 
-  for each dataset, and  report the  best  result  here. Comparatively,  
-  RoBERTa  based is  the  most stable and has the best performance among
-  all baselines and all experiment settings.
+  outperforms RoBERTa-large based, the strongest among all baselines, 
+  by 2.04 percent points on average F1 score over 5 datasets.  
+  Especially, ALBERT.xxlarge based is rather unstable  in this senario. Thus, 
+  we did multiple run with different settings and  report the  best  ones here. 
+  Comparatively,  RoBERTa  based is  the  most stable and has the best performance 
+  n almost all experiment settings.
 
   Regarding  the  similarity  model,  as  analyzed  above,  we  only  choose the
-  RoBERTa-large based as our baseline. Our joint SFC achieves the improvement of
-  7.09  percents  on average. Moreover, joint SFC's result on 2 datasets without
-  data  sampling  for few-shot settings, which are ITG and Amazon-670k, are also
-  1.24 and 2.89 percents higher than Roberta-large classification model, and are
-  6.96 and 10.77 percents higher than Roberta-large similarity model (todo:
-  meaning?).
+  RoBERTa-large based implementation as our baseline. Joint SFC achieves more improvement of
+  7.09  percent points  on average F1 score.
 
-  The above analysis illustrate that suitable fusing the classification model and the 
-  similarity model to make them cooperate with each other is helpful to better
-  performance.
+  The above analysis illustrates that suitable fusing the two kinds of models
+  can take their advantages.
 
   \subsubsection*{Does joint SFC improve the classification in stage 1?}
-  We  compare  the  top  1  prediction and top 5 candidate labels in stage 1 from
+  We  compare  the  top-1  prediction and top-5 candidate labels in stage 1 from
   two-stage SFC and joint SFC in Table \ref{tbe:top1_5_accuracy}. We should note
-  that  two-stage  SFC  does not optimize the stage 1 result, which is a RoBERTa
+  that  two-stage  SFC  does not optimize the stage 1 model, which is a RoBERTa
   based classification model.
@@
   The joint training does not improve the classification performance in stage 1,
-  measured  by  top  1  accuracy.  However,  it  improves  the  quality of top 5
+  measured  by  top-1  accuracy.  However,  it  improves  the  quality of top-5
   candidate  class  labels.  It  can  be  explained that, a classification model
-  inherently optimizes the objective loss, 0-1 error of top 1 here; the sentence
-  pair similairity model in the joint SFC poses positive effect in optimizing the 
+  inherently optimizes the objective loss, 0-1 error of top-1 here; the sentence
+  pair similairity model in the joint SFC poses more positive effect in optimizing the 
   candidate labels.
@@
   \subsubsection*{How does training sample size influence SFC?} 
-  We analyze the overall  improvement  trend  of  SFC under various few-shot
+  We analyze the overall  improvement  trend  of  joint SFC under various few-shot
   settings, and show results in Fig. \ref{fig:trend}.
@@
     \caption{
-      Improvements with different size of training data.
+      Improvements  from  Joint  SFC  over  RoBERTa  based  classification  with
+      different size of training data.
     }
@@
   per  class  our joint SFC achieves 4.97 percent points improvements on average
-  over  RoBERTa-large classification model . This observation indicates that SFC
+  over  RoBERTa-large classification model. This observation indicates that SFC
   is  especially  well-performed  when being applied during the initial stage of

### 2020-09-10 chatbot_classification/aaai_2021/paper.tex
modify abstract and introduction

--- 2020-09-10 chatbot_classification/aaai_2021/paper.tex
@@
     Task-specific  chatbot systems have gained many important applications, such
-    as  Siri,  Google home, and customer service systems. In these applications,
-    one  of  the  core  problems is the intention detection from a user's input.
-    Then,  the  intention  with  its  associated  information  is  mapped into a
-    predefined dialog logic graph, and the chatbot returns corresponding answer.
-    This  is  the  main  difference  from  a  free chatbot system. The intention
-    detection,  assuming  only  one  intention  in  a  user's input here, can be
-    modeled  as  a  short  text  classification.  In  practice,  the  number  of
+    as  Siri,  Google home, and customer service systems, etc. One essential technique 
+    underlying these applications  is to detect the real intention behind a user's input.
+    The intention detection,  assuming  only  one  intention  in  a  user's input here, can be
+    regarded  as  a  short  text  classification problem.  In  practice,  the  number  of
     intentions  can  be hundreds of thousands, as opposed to a few number in the
-    traditional text classification problem; enough training data is not trivial
-    to be filtered out and labeled from tons of raw user logs with miscellaneous
-    information, and generally only 10 to 20 samples per intention are available
-    in  the  early  stage.  Then,  how  to  train  an  efficient model in such a
-    practical  and important application is critical. In this work, we propose a
-    novel  model, called similarity model fused with classification Model (SFC),
+    traditional text classification problem; creating enough training data from tons of 
+    raw user logs with miscellaneous information is not trivial, 
+    and generally only 10 to 20 samples per intention are available in  the  early  stage.  
+    Thus,  how  to  train  an  effective short-text classification model with limited training
+    example in such a practical  and important application is critical. In this work, we propose a
+    novel  model, called similarity model fused with classification model (SFC),
     which  combines  a  classification  model  and  a similarity model, and also
     borrows  the  power  of  multi-task  training  as well. We conduct extensive
-    experiments  on  4  public  and 1 private datasets. The experimental results
-    show that our new model outperforms very strong baselines, BERT, RoBERTa and
-    ALBERT based pretrained models by 2 percentages in average accuracy.
+    experiments  on  4  public  and 1 private datasets. Experimental results
+    show that our new model outperforms very strong baselines (i.e., BERT, RoBERTa and
+    ALBERT based pretrained models) by 2 percentages in average accuracy.
 
@@
   Task-specific  conversational  chatbot  \cite{wen2016network}  has been applied
-  into  many practical products. One typical example is to share the working burden of
+  into  many practical products. One typical example is the chatbot that shares the working burden of
   human  customer  service  agents  responsible  for  customers' questions about
@@
   and smart home equipments, to name a few. Regardless of whether these conversations belong to
-  single or  multi-round, an essential technique underlying the chatbot is to
-  identify  the  real  intention  behind  a  user's  question or reply. Then the
-  chatbot  is capable of conducting expected actions, replying texts or accomplishing some
-  operations.
+  single or  multi-round, an essential technique underlying this type of chatbot is to
+  identify  the  real  intention  behind  a  user's  question or reply. 
+  The detected intention  with  its  associated  information  is then mapped into a
+  predefined dialog logic graph, from which a suitable response (e.g., conducting 
+  expected actions, replying texts or accomplishing some operations, etc)  is returned.
+  This  is  the  main  difference  from  a  free chatbot.
 
-  Identifying intention  is  a  challenging task due to some inherent properties. First,
+  Intention detection in task-specific chatbot  is  a  challenging task due to some inherent properties. First,
   a customer's  utterance  within  a conversation is usually quite short. Since it

### 2020-09-10 chatbot_classification/aaai_2021/paper.tex
modified:   paper.tex

@@
     and generally only 10 to 20 samples per intention are available in  the  early  stage.  
-    Thus,  how  to  train  an  effective short-text classification model with limited training
-    example in such a practical  and important application is critical. In this work, we propose a
+    Thus,  how  to  train  an  effective short-text classification model with
+    limited labeled data  in such a practical  and important application is critical. In this work, we propose a
     novel  model, called similarity model fused with classification model (SFC),
@@
     show that our new model outperforms very strong baselines (i.e., BERT, RoBERTa and
-    ALBERT based pretrained models) by 2 percentages in average accuracy.
+    ALBERT based pretrained models) by over 2 percentages in average F1 score.
 

### 2020-09-10 chatbot_classification/aaai_2021/paper.tex
modified:   paper.tex

@@
   \section{Methodology}
-  In  this section, we describe our proposed system, similarity model fused with
-  classification  model (SFC). We propose two approaches to implement this idea,
-  two-stage SFC, and its more unified version joint-SFC.
+  In  this section, we describe our proposed system, a similarity model fused with
+  a classification  model (SFC). We propose two approaches to implement this idea,
+  two-stage SFC, and its more compact version joint SFC.
 
@@
   to denote a user's question or a response.}, and $l_{j}\in\{0, 1\}$ denotes the
-  similarity label that the ones from the same class label are considered
+  similarity label that only the ones from the same class label are considered
   similar. The size of $\mathcal{D'}$  would be up to $O(N^2)$ if no any
@@
 
-  \section{Conclusion}
-  In  this  work, we successfully proposed SFC, a joint system of classification
-  model  and  sentence-pair similarity model with multi-task learning, which can
-  effectively  alleviate  the  limitation of classification model and similarity
-  model   for  low-resource  text  classification  tasks.  Experimental  results
-  illustrate that our proposed system can achieve great improvement on 5 diverse
-  datasets for task-specific chatbot system over several competitive single-task
-  baseline  models. Furthermore, we especially analyze the excellent performance
-  of SFC when facing the challenge brought by few-shot scenarios, which is quite
-  common in real-world application of chatbot system.
-
   \bibliographystyle{aaai21}

### 2020-09-10 chatbot_classification/aaai_2021/abstract.tex
Reorganized.   modified:   paper.tex
  new file:   abstract.tex
  new file:   introduction.tex
  new file:   related_work.tex
  new file:   methodology.tex
  new file:   experiments.tex
  new file:   conclusion.tex

--- 2020-09-10 chatbot_classification/aaai_2021/paper.tex
@@
-\def\year{2021}\relax
-%File: formatting-instructions-latex-2021.tex
-\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
-\usepackage{aaai21}  % DO NOT CHANGE THIS
-\usepackage{times}  % DO NOT CHANGE THIS
-\usepackage{helvet} % DO NOT CHANGE THIS
-\usepackage{courier}  % DO NOT CHANGE THIS
-\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
-\usepackage{graphicx} % DO NOT CHANGE THIS
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{float}
-\usepackage{subfigure}
-\usepackage[switch]{lineno}
-\usepackage{spconf}
-\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-
-\urlstyle{rm} % DO NOT CHANGE THIS
-\def\UrlFont{\rm}  % DO NOT CHANGE THIS
-\frenchspacing  % DO NOT CHANGE THIS
-\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
-\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
-
-\providecommand{\tabularnewline}{\\}
-%% A simple dot to overcome graphicx limitations
-\newcommand{\lyxdot}{.}
-
-\def\x{{\mathbf x}}
-\def\L{{\cal L}}
-
-%\nocopyright
-%PDF Info Is REQUIRED.
-% For /Author, add all authors within the parentheses, separated by commas. No accents or commands.
-% For /Title, add Title in Mixed Case. No accents or commands. Retain the parentheses.
-\pdfinfo{
-  /title (Joint training of classification model and similarity model for
-  low-resource text classification in chatbot)
-  /Author (no author informmation)
-  /TemplateVersion (2021.1)
-}
-
-\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
-%% Because html converters don't know tabularnewline
-\title{     
-  %SFC: Few-Shot Text Classification via Similarity Fused with Classification System
-  Joint Training of Classification and Similarity Models for \\ 
-  Intention Detection in Task-specific Chatbot
-}
-
-\begin{document}
-  \maketitle
-  \linenumbers
-
 \begin{abstract}
@@
 \end{abstract}
-
-  \section{Introduction}
-  \label{sec:intro}
-
-  Task-specific  conversational  chatbot  \cite{wen2016network}  has been applied
-  into  many practical products. One typical example is the chatbot that shares the working burden of
-  human  customer  service  agents  responsible  for  customers' questions about
-  certain  products  or services. Another one is the speech-based control in
-  devices  like  intelligent  speakers, such as Siri, Google home, Baidu Xiaodu,
-  and smart home equipments, to name a few. Regardless of whether these conversations belong to
-  single or  multi-round, an essential technique underlying this type of chatbot is to
-  identify  the  real  intention  behind  a  user's  question or reply. 
-  The detected intention  with  its  associated  information  is then mapped into a
-  predefined dialog logic graph, from which a suitable response (e.g., conducting 
-  expected actions, replying texts or accomplishing some operations, etc)  is returned.
-  This  is  the  main  difference  from  a  free chatbot.
-
-  Intention detection in task-specific chatbot  is  a  challenging task due to some inherent properties. First,
-  a customer's  utterance  within  a conversation is usually quite short. Since it
-  does  not  contain  enough  information,  short  texts \cite{song2014short} are
-  thought  to  be  more  ambiguous  compared to long texts such as paragraphs or
-  documents,  posing  a  great challenge \cite{chen2019deep} for classification
-  task   \cite{phan2008learning,yan2009dynamic,hua2015short}.   Second,  in  the
-  initial  stage  of  building  a  chatbot  , it is often rather hard to collect
-  sufficient  labeled  data  to  train  a good model. Because developers have to
-  examine tons of real system logs for typical user's utterances, and then label
-  them  with expected intentions. Therefore, to build a task-specific chatbot with
-  high  performance, it is essential to solve the challenge of short-text
-  classification   \cite{sriram2010short}   problem   under   few-shot   setting
-  \cite{yu2018diverse}.
-
-  Generally  there  are  two  kinds  of  approaches  to  address  this  problem,
-  one is the classification model that directly maps an input into a most likely label, and
-  the other one is the similarity  model  that searches a label whose associated data is most similar to
-  an input.
-
-  The   first  one,  \emph{text  classification},  includes  classic  long  text
-  classification  and  short  text  classification  in  this  scenario.  Besides
-  traditional  machine  learning  models  like  SVM \cite{suykens1999least},  
-  boosting  tree \cite{tu2005probabilistic},  many work
-  \cite{wen2016network}  choose  neural  network  such  as  convolutional neural
-  networks (CNNs) \cite{kim2014convolutional,zhang2015character,conneau2016very}
-  and       long       short       term       memory       networks      (LSTMs)
-  \cite{mousa2017contextual,liu2016recurrent}   to   accomplish   the   task  of
-  extracting  semantic  feature from limited amount of words. Their common model
-  structure  is  adding  a  softmax classifier as the final layer and mapping to
-  labels.  Another  two  interesting lines of work, label-word joint models, and
-  joint  NER  and  classification  are  discussed  in  the related work section.
-  Afterwards,   pre-trained   language   models   on   large  corpus  like  BERT
-  \cite{devlin2018bert}  and  RoBERTa \cite{liu2019roberta} has been proven more
-  powerful  in  solving  many  NLP  tasks  including  short-text  classification
-  \cite{madabushi2020cost}.      Especially      for      few-shot     scenarios
-  \cite{yu2018diverse},     pre-trained     model    based    on    transformers
-  \cite{vaswani2017attention} tends to do more
-  help to reducing the negative effects brought by scarcity of training data.
-
-  The  second  one,  \emph{similarity model} is also called sentence-pair model.
-  Its  motivation  originates  from  the idea of Information Retrieval (IR) based
-  chatbot   \cite{jafarpour2010filter,   leuski2011npceditor}.   Having   a  Q-A
-  (Question-Answer)  pairs dataset and user query Q, the IR based conversational
-  system will look up in the Q-A dataset for the pair (Q', A') that best matches
-  query  Q  through  semantic  analysis  and  returns  A'  as  the  answer  to Q
-  \cite{mnasri2019recent}. In this way, sentence-pair model pre-trained on large
-  corpus  of  semantic  similarity  identification task can be applied for being
-  used  as  a  tool  to  identify  the class with highest semantic similarity to
-  customer's    query.    A    common    model    structure    of    pre-trained 
-  sentence-pair model is based on multiple cross-attention
-  mechanism  \cite{barkan2020scalable}. Due to
-  the   fact   that   many   experiment   results   have   shown   that  RoBERTa
-  \cite{liu2019roberta} is an improved version of BERT \cite{devlin2018bert}, and has achieved amazing
-  results  on  both  text  classification and sentence-pairs semantic similarity
-  tasks, we choose RoBERTa as an important baseline approach in this paper.
-
-  Despite  the  success  of  these two kinds of approaches, they still have some
-  limitations   in   task-specific  chatbot  scenario.  As  for  the  \emph{text
-  classification  model},  it  is  quite hard to use data augmentation method to
-  solve  the  data insufficiency challenge since the it is usually unfeasible to
-  get  large amount of domain-specific data when facing a new task. With respect
-  to  the  \emph{similarity model}, though we can obtain a large amount of data
-  from semantically  duplicate  sentence  pair identification domain for transfer
-  learning  \cite{sun2019fine},  it  is  still  quite  hard  to  perform well on
-  a new task-specific dataset,  since their objective losses are totally different.
-
-  The  above limitation motivates us to propose a joint system that is capable of
-  taking  advantages  from  both  classification model and similarity model. We
-  call  it  SFC,  short  for  similairty model fused with classification Model,
-  shown  in  Fig.  \ref{fig:framework}.  To  better train SFC, we further bring in
-  multi-task   learning   \cite{caruana1993multitask,collobert2008unified, liu2019multi}.  Our
-  basic  idea  came  from  two  stages. In the first stage, we use an auxiliary
-  model  to  select top-K most possible labels for a input. This model can be an
-  elastic search  \cite{divya2013elasticsearch}  or  a  text classification model
-  trained on current task-specific chatbot data. In the second stage, we build a
-  classification  model  whose  main modules are similarity models. Then, this
-  structure  derives two goals to train towards, the classification loss for our
-  application,  and the similarity loss for the main modules. When the two stages
-  are  independently  optimized,  we call \emph{two-stage SFC}. We further find,
-  the  the  quality  of  output  from  the  first  stage  might  limit the final
-  performance  of  system,  since  the  candidate  labels for each user query is
-  always  fixed  in  the  whole  multi-task  training  process. This observation
-  motivates  us  to  further  improve  the  two-stage SFC into a joint training,
-  called  \emph{joint  SFC}. In this way, the sentence pairs associated with the
-  top-K  classes  also  become dynamic, and the text classification model in the
-  first  stage  will also be further optimized to provide better top-K result by
-  the final training loss.
-
-  We summarize our contributions as follow:
-  \begin{enumerate}
-    \item We propose a novel joint system to makes full utilization of
-    the advantages from both text classification model and similarity model.
-
-    \item To  better  train such a system, we bring in multi-task training to obtain
-    reasonable performance.
-
-    \item Experiment  results  from 4 public and 1 private short-text classification
-    datasets,  show  that  our  proposed  SFC joint system can achieve significant
-    and consistent improvements over strong baselines, especially in the low resource settings.
-  \end{enumerate}
-
-  \begin{figure*}[t]
-    \begin{centering}
-      \includegraphics[scale=0.72]{picture/picture4} 
-      \par
-    \end{centering}
-    \caption{
-      \textbf{Network Structure of SFC:} two-stage SFC and joint-SFC are sharing
-      the  same  network  from  stage  1  and  stage 2, with the only difference
-      whether two stages being jointly trained.
-    }
-    \label{fig:framework}
-  \end{figure*}
-
-  \section{Related work}
-
-  Another  common  approach  is  text  classification  neural  network  based on
-  label-word     joint     embedding,    such    as    LEAM \cite{wang2018joint},
-  MTLE \cite{zhang2017multi}   and   EXAM \cite{du2019explicit}.   This   approach
-  involves  label  embedding when constructing the text-sequence representation.
-  Take  LEAM  as  an  example,  the  text classification model is implemented by
-  jointly    embedding    the    word    and    label   in   the   same   latent
-  space \cite{wang2018joint}. Afterwards, the text representation are constructed
-  based  on  text-label  compatibility through attention mechanism. In this way,
-  additional  sources  of  semantic  information  from class labels can be fully
-  leveraged, which is quite helpful especially under few-shot scenario.
-
-  As for \emph{label-word joint
-  embedding  approach},  it  poses  noticeable requirements on label information.
-  However,  in  our  cases,  since  we have large amount of class labels without
-  being well-defined for question answering chatbot, the only thing we can do is
-  to  choose  one  of the user utterance as the class label to represent the key
-  information  of  the  whole class. In this way, the label will become not only
-  prolix  but  also  biased,  which  will  bring  some  negative effect to label
-  embedding.
-
-  Another   line   of  interesting  work  is  the  joint  training  of  sentence
-  classification   and  NER  (todo:  reference).  If  both  the  city  and  date
-  information  are  recognized,  then  they  are good indicators that this query
-  might  be  booking  an  ticket. This work can also be combined in our proposed
-  framework.
-
-  \section{Methodology}
-  In  this section, we describe our proposed system, a similarity model fused with
-  a classification  model (SFC). We propose two approaches to implement this idea,
-  two-stage SFC, and its more compact version joint SFC.
-
-  \subsection{Two-stage SFC}
-
-  Two-stage   SFC  is  composed  with  two  independent stages  in  charge of
-  different  jobs.
-
-  \subsubsection*{
-    Stage 1: classification model for providing top-K candidate class labels
-  } 
-  We  can  use any auxiliary text classification model or tool,
-  such as Term Frequency-Inverse Document Frequency (TF-IDF)retrieval, to
-  provide  top-K  most  related  class  labels. These selected class labels will
-  later  be  used to sample sentence pairs of both positive samples and negative
-  samples  for  stage  2.
-
-  In  this  work,  we  choose pretrained models to fine tune on our data.
-  Due to the excellent performance of RoBERTa in this task, compared to other pretrained
-  models, we use RoBERTa as the encoder of classification model in our setting.
-
-  Given   a   data   point   $x_{i}$  with  class  label  $y_{i}$  from  dataset
-  $\mathcal{D}$, we take the final hidden state $h_{i}$ of the first token [CLS]
-  encoded  by  RoBERTa  as the representation for the whole sequence of $x_{i}$.
-  Then  a linear layer is followed to output probabilistic distribution of class
-  labels,  $softmax(W^Ch_{i}+b^C)=softmax({\Phi}^C_{i})$,  where $W^C$ and $b^C$
-  are  trainable  parameters.  Then, the loss in stage 1 classification model is
-  shown in Equ. \ref{eq:classification_loss},
-
-  \begin{equation}
-    \begin{aligned}
-      \mathcal{L}^{C}&=\frac{1}{N}\sum_{i=1}^{N}-log(\frac{exp(\varPhi_{i,y_{i}}^C)}{\sum_{j=1}^{C}exp(\varPhi_{i,j}^C)}) \\
-      \label{eq:classification_loss}
-    \end{aligned}
-  \end{equation}
-
-  \subsubsection*{
-    Stage 2: sentence-pair similarity model based classification with multi-task
-    learning
-  }
-  We  continue choosing RoBERTa as the main module in this stage that identifies
-  the class label with strongest semantic similarity to the user input sentence.
-
-  Suppose  we have a training dataset $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$ of
-  $N$  data  points,  in  which $x_{i}$ is the user input query and $y_{i}$ is a
-  single  class label from a class label set of $C$ classes in total. We 
-  generate            a sentence            pair            dataset
-  $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$ from $\mathcal{D}$,   where   $(x,   x')_{j}$  is
-  a pair of two history queries \footnote{For simplicity, we use query
-  to denote a user's question or a response.}, and $l_{j}\in\{0, 1\}$ denotes the
-  similarity label that only the ones from the same class label are considered
-  similar. The size of $\mathcal{D'}$  would be up to $O(N^2)$ if no any
-  sampling strategy is used.  This is quite time-consuming  for the  training
-  in stage 2 because $N$ can be several hundreds or thousands even under 
-  few shot setting in task-specific chatbot scenario.
-
-  Therefore,  we  adopt  the idea of adversarial negative sampling strategy from
-  the  work  \cite{bamler2020extreme}.  The  key  idea is to train with negative
-  samples  that  are hard to be distinguished from positive samples. Now suppose
-  we  have  a  user  input query $x_{i}$ and top-K most related class labels set
-  $\mathcal{C'}=\{c'_{1},  \dots,  c'_{K}\}$ provided by auxiliary model or tool
-  in  stage  1, where $K$ is a hyperparameter to control candidate class number,
-  we  apply  the  adversarial  negative sampling strategy into our sentence pair
-  sampling process by the following two steps:
-
-  The  first step is \emph{positive sentence pair sampling}. During the training
-  process,  we  first make sure the ground truth class label $y_{i}$ for $x_{i}$
-  is  within  the  candidate  class  label  set  $\mathcal{C'}$. If $y_{i}\notin
-  \mathcal{C'}$,  we  manually  add  $y_{i}$  into  $\mathcal{C'}$  by replacing
-  $c'_{K}$  with  $y_{i}$, since $c'_{K}$ is the least promising candidate label
-  according  to  the  auxiliary  model  in stage 1. Afterwards, we will randomly
-  sample  $P$ sentences $\{x'_{1}, \dots, x'_{P}\}$ with the same class label as
-  $y_{i}$  from  dataset  $\mathcal{D}$  to  form the set of sentence pairs with
-  positive  label  $\mathcal{P'}_{i}=\{[(x_{i},  x'_{1}),  1],  \dots,  [(x_{i},
-  x'_{P}),  1]\}$,  where $P$ is also a hyperparameter set to control the number
-  of sentences we should sample from each class.
-
-  \begin{table*}
-    \begin{centering}
-      \scalebox{0.9}{
-        \begin{tabular}{|c|c|c|c|c|c|}
-          \hline 
-          \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} &
-          \textbf{\#Training Samples} & \textbf{\#Samples/Class} & \textbf{Experimental Settings}\tabularnewline
-          \hline 
-          ITG & FAQ chatbot & 228 & 3938 & 17 & 3-fold\tabularnewline
-          \hline 
-          Amazon-670k & Product review & 250 & 1942 & 8 & 3-fold\tabularnewline
-          \hline 
-          HWU64 & intention detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
-          \hline 
-          CLINC150 & intention detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
-          \hline 
-          BANKING77 & intention detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
-          \hline 
-        \end{tabular}
-      }
-      \par
-    \end{centering}
-    \caption{Statistics for all datasets and few shot settings.}
-
-    \label{tbe:dataset statistic}
-  \end{table*}
-
-  The  second  step  is  \emph{negative sentence pair sampling}: As for negative
-  sentence  pairs,  we will also randomly sample $P$ sentences for each class in
-  the negative candidate class label set $\mathcal{C'}\backslash \{y_{i}\}$. The
-  class  labels  in  $\mathcal{C'}\backslash  \{y_{i}\}$  are  the  set  of most
-  confusing  class  labels comparing to the ground truth ${y_{i}}$, so we assume
-  that  the  sentence  pairs  with  negative  label  grouped by user input query
-  $x_{i}$  and sentences with class labels in $\mathcal{C'}\backslash \{y_{i}\}$
-  are  strong  adversarial  negative  samples for sentence-pair similarity model
-  that  can  help  enhance  the training speed and performance. According to the
-  same  method  as  positive  sentence  pair  sampling, we can obtain the set of
-  sentence  pairs  with  negative label as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{1}),
-  0], ..., [(x_{i}, x'_{P\cdot K}), 0]\}$
-
-  In  this way, we generate the sentence pair dataset $\mathcal{D'}$ for stage 2
-  based  on  the  top-K  class  label  set $\mathcal{C'}$ provided by stage 1 as
-  $\mathcal{D'}=\{\mathcal{P'}_{i}\cup  \mathcal{N'}_{i}\}_{i=1}^{N}$,  in which
-  we have $M=N\cdot K\cdot P$ data points of sentence pairs in total.
-
-  Before starting to fine-tune our sentence-pair model on task-specific dataset,
-  we  first  fine-tune  RoBERTa  on  Quora  dataset  \cite{iyer2017first}, which
-  contains  404,290  potential  duplicate question pairs, for transfer learning.
-  This  is  also  the  merit of similarity based model, as labeled task-specific
-  classification  data  is  hard  to  acquire,  yet  general sentence pairs with
-  similar semantics can be much easier to acquire.
-
-  \subsubsection*{Multi-task based training}
-  We   continue  to  do  multi-task  training  on  sentence-pair  dataset
-  $\mathcal{D'}$ sampled from the top-K candidate class labels provided by stage
-  1. In stage 2, we have two tasks tuning our system.
-
-  The first task is \emph{regular sentence-pair similarity task}.
-  For  sentence  pair semantic similarity task, given a data point $(x, x')_{i}$
-  with       similarity       label       $l_{i}$       from       data      set
-  $\mathcal{D'}=\{[(x,x')_{i},l_{i}]\}_{i=1}^{M}$,   Roberta   takes  the  final
-  hidden  state  $h_{i}$  of the first token [CLS] as the representation for the
-  sequence of packed sentence pair $(x, x')_{i}$. Let's suppose we have a linear
-  layer  as  ${\Phi}^S_{i}=W^Sh_{i}+b^S$,  where  $W^S$  and $b^S$ are trainable
-  parameters,  and  the probability score for $(x, x')_{i}$ can be calculated as
-  $p^S_{i}=softmax({\Phi}^S_{i})$.
-
-  Due  to  the  fact that sentence pairs within the same class is much fewer than
-  that from  different  classes,  the  dataset  $\mathcal{D'}$  is
-  quite imbalanced.  Therefore, we will accommodate a weight variable $w^S = [K-1, 1]$
-  to  the  loss  to eliminate the bias brought by data imbalance, shown in Equ.
-  \ref{eq:similarity_loss}.
-
-  \begin{equation}
-    \begin{aligned}
-      \mathcal{L}^{S}&=\frac{1}{M}\sum_{i=1}^{M}-w^S_{l_i}\cdot log(\frac{exp(\varPhi_{i,l_{i}}^S)}{\sum_{j=0}^{1}exp(\varPhi_{i,j}^S)}) \\
-      \label{eq:similarity_loss}
-    \end{aligned}
-  \end{equation}
-
-  The  second  task  is  \emph{classification  on  top-K classes}. As minimizing
-  similarity  loss  is  not  our  final goal in the intention classification, we
-  bring  back  classification  loss again. In this task, the network is based on
-  sentence  pair  similarity  modules.  The  only  difference  is  that we add a
-  task-specific  average  pooling  layer,  shown  in Fig. \ref{fig:framework} to
-  accomplish the classification task based on sentence-pair model.
-
-  We  already  know  that the size of ${\Phi}^S$ in task 1 is $M\times 2=(N\cdot
-  K\cdot  P)\times  2$, where $N$ is the total number of data points in original
-  training  data $\mathcal{D}$, $K$ is a hyperparameter that controls the number
-  of   candidate   class  labels  provided  by  stage  1,  and  $P$  is  also  a
-  hyperparameter that controls the number of sentences we should randomly sample
-  from each candidate class labels. Now, for the average pooling layer, we first
-  reshape  ${\Phi}^S$  into  the  size  of $N\times K\times P\times 2$, and then
-  split  it  into  ${\Phi}^{K,pos}$  and ${\Phi}^{K,neg}$, and both of them will
-  have  the  size  of  $N\times  K\times  P$.  In this way, ${\Phi}^{K,pos}$ can
-  represent  the  level  of  similarity  for each sentence pair, and in the mean
-  time,  ${\Phi}^{K,neg}$  can  represent  the  level  of dissimilarity for each
-  sentence  pair. Then, we can do average pooling for each candidate class among
-  the  top-K  classes  as  shown  in  Equ.  \ref{eq:average  pooling}.
-
-  \begin{align}
-    {\xi}_{i,j}^{K,pos} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,pos} \ \ \ \ \ \ \ 
-    {\xi}_{i,j}^{K,neg} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,neg}
-    \label{eq:average pooling}
-  \end{align}
-
-  With  the  average pooling result ${\xi}^{K,pos}$ and ${\xi}^{K,neg}$, we also
-  generate   a   top-K   class   label   $l^{K}_i\in   [1,\dots,K]$   for   each
-  ${\xi}^{K,pos}_{i}$ and ${\xi}^{K,neg}_{i}$. The loss for top-K classification
-  task is shown in Equ. \ref{eq:top-k_classification_loss}. In Equ. \ref{eq: pos
-  top-k   loss}   and   Equ.   \ref{eq:   neg   top-k   loss},  the  first  term
-  $\xi_{i,l^{K}_{i}}^{K,pos}$  and  $\xi_{i,l^{K}_{i}}^{K,neg}$  encourage  high
-  level  of  similarity  and  low  level  of dissimilarity for prediction of the
-  correct label $l^{K}_i$ within the top-K candidate classes.
-
-  \begin{align}
-    \mathcal{L}^{K} = \frac{1}{N}\sum_{i=1}^{N}(\mathcal{L}^{K,pos}_{i} - \mathcal{L}^{K,neg}_{i})
-    \label{eq:top-k_classification_loss}
-  \end{align}
-  where
-
-  \begin{equation}
-    \begin{aligned}
-      \mathcal{L}^{K,pos}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,pos})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,pos})})
-      \label{eq: pos top-k loss}
-    \end{aligned}
-  \end{equation}
-
-  \begin{equation}
-    \begin{aligned}
-      \mathcal{L}^{K,neg}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,neg})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,neg})}) \\
-      \label{eq: neg top-k loss}
-    \end{aligned}
-  \end{equation}
-
-  Finally,  the  overall  loss  function for multi-task learning in stage 2 is
-  shown in Equ. \ref{eq:two-stage_SFC_loss}. The training objective of stage 2 is
-  to  minimize  the  weighted  sum  of task-specific losses. Here $\alpha_S$ and
-  $\alpha_K$  are  weights  of  task  1  and  task  2  respectively.
-
-  \begin{align}
-    \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K
-    \label{eq:two-stage_SFC_loss}
-  \end{align}
-
-  \begin{table*}
-    \begin{centering}
-      \scalebox{0.55}{
-        \begin{tabular}{|c|cccccc|cccccc|cccccc|c|c|}
-          \hline 
-          \multicolumn{1}{|c|}{\multirow{2}*{\textbf{Models}} }& \multicolumn{6}{c|}{\textbf{CLINC150}}& \multicolumn{6}{c|}{\textbf{BANKING77}}& \multicolumn{6}{c|}{\textbf{HWU64}}& \ \ \ \textbf{ITG} \ \ \ & \textbf{Amazon-670k}\tabularnewline
-          \cline{2-21}
-          \multicolumn{1}{|c|}{} & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$
-          & $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & $\textbf{5}$ &
-          $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{30}$ &
-          $\textbf{50}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ &
-          $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & \textbf{3-fold} &
-          \textbf{3-fold}\tabularnewline
-          \hline
-          TextCNN & \multirow{2}*{$0.5318$} & \multirow{2}*{$0.6963$} & \multirow{2}*{$0.7609$} & \multirow{2}*{$0.8142$} & \multirow{2}*{$0.8526$} & \multirow{2}*{$0.8867$} & \multirow{2}*{$0.4408$} & \multirow{2}*{$0.6436$} & \multirow{2}*{$0.7366$} & \multirow{2}*{$0.7918$} & \multirow{2}*{$0.8228$} & \multirow{2}*{$0.8619$} & \multirow{2}*{$0.3112$} & \multirow{2}*{$0.4007$} & \multirow{2}*{$0.4823$} & \multirow{2}*{$0.5272$} & \multirow{2}*{$0.5782$} & \multirow{2}*{$0.6262$} & \multirow{2}*{$0.6624$} & \multirow{2}*{$0.4401$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          LEAM & \multirow{2}*{$0.7514$} & \multirow{2}*{$0.8203$} & \multirow{2}*{$0.8612$} & \multirow{2}*{$0.8802$} & \multirow{2}*{$0.9010$} & \multirow{2}*{$0.9180$} & \multirow{2}*{$0.5422$} & \multirow{2}*{$0.7812$} & \multirow{2}*{$0.8129$} & \multirow{2}*{$0.8280$} & \multirow{2}*{$0.8610$} & \multirow{2}*{$0.8727$} & \multirow{2}*{$0.4545$} & \multirow{2}*{$0.5554$} & \multirow{2}*{$0.5936$} & \multirow{2}*{$0.6599$} & \multirow{2}*{$0.6855$} & \multirow{2}*{$0.7046$} & \multirow{2}*{$0.7086$} & \multirow{2}*{$0.6091$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-          BERT-large & \multirow{2}*{$0.8080$} & \multirow{2}*{$0.8904$} & \multirow{2}*{$0.9265$} & \multirow{2}*{$0.9334$} & \multirow{2}*{$0.9497$} & \multirow{2}*{$0.9595$} & \multirow{2}*{$0.5780$} & \multirow{2}*{$0.8004$} & \multirow{2}*{$0.8518$} & \multirow{2}*{$0.8827$} & \multirow{2}*{$0.8858$} & \multirow{2}*{$0.8982$} & \multirow{2}*{$0.4711$} & \multirow{2}*{$0.5963$} & \multirow{2}*{$0.6342$} & \multirow{2}*{$0.7010$} & \multirow{2}*{$0.7117$} & \multirow{2}*{$0.7424$} & \multirow{2}*{$0.7485$} & \multirow{2}*{$0.6658$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          ALBERT-xxlarge & \multirow{2}*{$0.8497$} & \multirow{2}*{$0.9008$} & \multirow{2}*{$0.9296$} & \multirow{2}*{$0.9297$} & \multirow{2}*{$0.9466$} & \multirow{2}*{$0.9578$} & \multirow{2}*{$0.5549$} & \multirow{2}*{$0.7981$} & \multirow{2}*{$0.8231$} & \multirow{2}*{$0.8530$} & \multirow{2}*{$0.8571$} & \multirow{2}*{$0.9096$} & \multirow{2}*{$0.4879$} & \multirow{2}*{$0.6116$} & \multirow{2}*{$0.6135$} & \multirow{2}*{$0.6996$} & \multirow{2}*{$0.7094$} & \multirow{2}*{$0.7376$} & \multirow{2}*{$0.7253$} & \multirow{2}*{$0.6893$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          RoBERTa-base & \multirow{2}*{$0.8732$} & \multirow{2}*{$0.9254$} & \multirow{2}*{$0.9363$} & \multirow{2}*{$0.9482$} & \multirow{2}*{$0.9558$} & \multirow{2}*{$0.9637$} & \multirow{2}*{$0.7305$} & \multirow{2}*{$0.8654$} & \multirow{2}*{$0.8808$} & \multirow{2}*{$0.9080$} & \multirow{2}*{$0.9061$} & \multirow{2}*{$0.9293$} & \multirow{2}*{$0.5831$} & \multirow{2}*{$0.6790$} & \multirow{2}*{$0.7064$} & \multirow{2}*{$0.7100$} & \multirow{2}*{$0.7320$} & \multirow{2}*{$0.7472$} & \multirow{2}*{$0.7734$} & \multirow{2}*{$0.6708$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          RoBERTa-large & \multirow{2}*{$\textbf{0.8974}$} &
-          \multirow{2}*{$\textbf{0.9372}$} & \multirow{2}*{$\textbf{0.9508}$} &
-          \multirow{2}*{$\textbf{0.9584}$} & \multirow{2}*{$\textbf{0.9621}$} & 
-          \multirow{2}*{$\textbf{0.9733}$} & \multirow{2}*{$\textbf{0.7690}$} & 
-          \multirow{2}*{$\textbf{0.8728}$} & \multirow{2}*{$\textbf{0.8966}$} & 
-          \multirow{2}*{$\textbf{0.9099}$} & \multirow{2}*{$\textbf{0.9227}$} & 
-          \multirow{2}*{$\textbf{0.9313}$} & \multirow{2}*{$\textbf{0.6044}$} & 
-          \multirow{2}*{$\textbf{0.7002}$} & \multirow{2}*{$\textbf{0.7129}$} & 
-          \multirow{2}*{$\textbf{0.7436}$} & \multirow{2}*{$\textbf{0.7493}$} & 
-          \multirow{2}*{$\textbf{0.7678}$} & \multirow{2}*{$\textbf{0.7990}$} & 
-          \multirow{2}*{$\textbf{0.7156}$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-          RoBERTa-large & \multirow{2}*{$0.8266$} & \multirow{2}*{$0.8861$} & \multirow{2}*{$0.9023$} & \multirow{2}*{$0.9084$} & \multirow{2}*{$0.9090$} & \multirow{2}*{$0.9407$} & \multirow{2}*{$0.757$} & \multirow{2}*{$0.8476$} & \multirow{2}*{$0.8614$} & \multirow{2}*{$0.8743$} & \multirow{2}*{$0.8749$} & \multirow{2}*{$0.8980$} & \multirow{2}*{$0.5425$} & \multirow{2}*{$0.6164$} & \multirow{2}*{$0.6503$} & \multirow{2}*{$0.6729$} & \multirow{2}*{$0.6947$} & \multirow{2}*{$0.7231$} & \multirow{2}*{$0.7418$} & \multirow{2}*{$0.6362$}\tabularnewline
-          (similarity) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-          2-stage SFC & \multirow{2}*{$0.8979$} & \multirow{2}*{$0.9457$} & \multirow{2}*{$0.9517$} & \multirow{2}*{$0.9591$} & \multirow{2}*{$0.9610$} & \multirow{2}*{$0.9664$} & \multirow{2}*{$0.7975$} & \multirow{2}*{$0.8818$} & \multirow{2}*{$0.8962$} & \multirow{2}*{$0.9109$} & \multirow{2}*{$0.9187$} & \multirow{2}*{$0.9198$} & \multirow{2}*{$0.6477$} & \multirow{2}*{$0.7055$} & \multirow{2}*{$0.7200$} & \multirow{2}*{$0.7232$} & \multirow{2}*{$0.7484$} & \multirow{2}*{$0.7653$} & \multirow{2}*{$0.7972$} & \multirow{2}*{$0.7189$}\tabularnewline
-          (task1) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          2-stage SFC & \multirow{2}*{$0.9162$} & \multirow{2}*{$0.9424$} & \multirow{2}*{$0.9530$} & \multirow{2}*{$0.9617$} & \multirow{2}*{$0.9633$} & \multirow{2}*{$0.9690$} & \multirow{2}*{$0.7997$} & \multirow{2}*{$0.8823$} & \multirow{2}*{$0.8945$} & \multirow{2}*{$0.9123$} & \multirow{2}*{$0.9236$} & \multirow{2}*{$0.9317$} & \multirow{2}*{$0.6498$} & \multirow{2}*{$0.6980$} & \multirow{2}*{$0.7202$} & \multirow{2}*{$0.7358$} & \multirow{2}*{$0.7498$} & \multirow{2}*{$0.7657$} & \multirow{2}*{$0.8020$} & \multirow{2}*{$0.7311$}\tabularnewline
-          (task2) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          2-stage SFC & \multirow{2}*{$0.9167$} & \multirow{2}*{$0.9456$} & \multirow{2}*{$0.9571$} & \multirow{2}*{$0.9638$} & \multirow{2}*{$0.9658$} & \multirow{2}*{$0.9753$} & \multirow{2}*{$0.8135$} & \multirow{2}*{$0.8854$} & \multirow{2}*{$0.8931$} & \multirow{2}*{$0.9192$} & \multirow{2}*{$0.9257$} & \multirow{2}*{$0.9339$} & \multirow{2}*{$0.6525$} & \multirow{2}*{$0.7092$} & \multirow{2}*{$0.7168$} & \multirow{2}*{$0.7476$} & \multirow{2}*{$0.7519$} & \multirow{2}*{$0.7696$} & \multirow{2}*{$\textbf{0.8124}$} & \multirow{2}*{$0.7364$}\tabularnewline
-          (task1 + task2) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-          \multirow{2}*{Joint SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.9669}$} & \multirow{2}*{$\textbf{0.9712}$} & \multirow{2}*{$\textbf{0.9821}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.9323}$} & \multirow{2}*{$\textbf{0.9463}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$\textbf{0.7593}$} & \multirow{2}*{$\textbf{0.7772}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline
-          & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-        \end{tabular}
-      }
-      \par
-    \end{centering}
-    \caption{
-      F1 scores  on  five  task-specific  datasets text classification in chatbot
-      under low resource. For ITG, we keep the full dataset. For Amazon-670k, we
-      randomly  sampled  250  classes  with  training sample numbers within 5-15
-      samples  per  class.  For  CLINC150,  BANKING77,  HWU64, we set up various
-      few-shot  settings  (5/10/15/20/30/50 samples per class) while keeping the
-      test  set to be fixed. The highest scores among all the baseline models and SFC variants for each data setting are both marked
-      in bold.
-    }
-    \label{tbe:table2}
-  \end{table*}
-
-  \subsection{Joint SFC}
-  In  two-stage  SFC,  Stage  1  and  stage 2 are separate that there is no deep
-  interaction  with each other during training. In this case, the performance of
-  stage  1  may  limit  the potential of stage 2; meanwhile, stage 2 also cannot
-  give  training feedback back to stage 1 for fine-tuning. Therefore, to further
-  improve  the  overall performance of SFC, we proposed a joint model structure,
-  shown in Fig. \ref{fig:framework}.
-
-  In  joint  SFC,  classification  model is being placed in lower layer level to
-  dynamically  provide  top-K  candidate  class  labels  for  the  sentence-pair
-  similarity  model  placed in higher layer level through a top-K pooling layer.
-  In  this way, classification model and similarity model can be merged into one
-  single  joint-model  for  multi-task training with sentence pairs sampled from
-  varying  candidate  class  labels,  thus  avoiding the limitation brought by 2
-  separate stage structure.
-
-  There  are 3 tasks in total during the training process of joint SFC, shown in
-  Fig. \ref{fig:framework}, and the overall loss is also the weighted sum of all
-  the   task-specific  losses,  shown  in  Equ.  \ref{eq:joint_SFC_loss}.  Here,
-  $\alpha_S$,  $\alpha_K$  and  $\alpha_C$  represent  the  weights  for  task 1
-  sentence-pair  similarity  in  Equ.  \ref{eq:similarity_loss},  task  2  top-K
-  classification  in Equ. \ref{eq:top-k_classification_loss}, and task 3 general
-  single       sentence       classification      respectively      in      Equ.
-  \ref{eq:classification_loss}.
-
-  \begin{align}
-    \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K + \alpha_C \mathcal{L}^C
-    \label{eq:joint_SFC_loss}
-  \end{align}
-
-  \section{Experiments}
-  \label{sec:exp}
-
-  \subsection{Datasets}
-  Our experiments aim to study the short text classification in the low-resource
-  environment  popular  in  the  task-specific conversational chatbot application.
-  Hence we choose and configure set datasets to serve this study. Different from
-  the  datasets from other short text classification research, such as semantics
-  classification  with  very  limited  semantics labels and relatively longer
-  input,   the   datasets  adopted  in  our  experiments  are  typically  having
-  comparatively  large  number  of  class labels, ranging from several dozens to
-  hundreds,  and  each  class  label  is  associated  with  a handful of labeled
-  queries with each  query  being usually  one  sentence. Table \ref{tbe:dataset
-  statistic} displays their statistics.  All settings of four public datasets would 
-  be released to github soon.
-
-  \begin{enumerate}
-    \item \emph{ITG},  is  a proprietory FAQ dataset from real-world
-    chatbot  project,  which is composed of question and answer pairs about online
-    English teaching. It contains 3,938 sample questions for 228 class labels, and
-    each class label corresponds to a unique answer.
-
-    \item \emph{Amazon-670K}, is a customer product review dataset for
-    text  classification  task  from  the  extreme  classification repository. The
-    complete  dataset  contains 670,091 class labels, 285,176 training samples and
-    150,875   testing   samples   \cite{bhatia2016extreme}.  As  each  sample  may
-    correspond  to  multiple  class labels, we keep only the first one. We further
-    filter  out the class labels that each one is associated with 5 to 15 samples,
-    or  reviews,  to  mimic  the  chatbot scenario. From them, we sample 250 class
-    labels as well as their samples to form a subset with 1,942 + 716 samples.
-
-    \item \emph{HWU64}, is a intention detection dataset designed for
-    home  robot  scenario \cite{liu2019benchmarking}. It aims at the specific task
-    of  capturing  the  intention  for  different  user requests to home robot and
-    finding  the corresponding answer. The raw dataset contains 25,716 data points
-    for 64 class labels through crowdsourcing.
-
-    \item \emph{CLINC150},  is  a dataset designed for task-oriented
-    systems  with  23,700 queries that are short and unstructured for 150 intents,
-    in    the    same   style   made   by   real   users   through   crowdsourcing
-    \cite{larson2019evaluation}.
-
-    \item \emph{BANKING77}, is a intention detection dataset for bank
-    customer  services.  The  raw dataset contains 13,084 data points for 77 class
-    labels \cite{casanueva2020efficient}.
-  \end{enumerate}
-
-  Regarding  the first two datasets, we conduct 3-fold cross validation experiments
-  that   70   percent   as  training,  15  percent  as  validation  and  testing
-  respectively,  and  report  the  averaged  testing results. Regarding the last
-  three datasets, we conduct experiments using a sampling method similar to that
-  in   \cite{casanueva2020efficient}   yet  in  a  more  sophisticated  few-shot
-  settings.  We  fix  a  test  data for each one, and examine their performances
-  using  5,  10,  15,  20,  30,  and 50 samples per class label respectively for
-  training.  This  is important, as in practice, a task-specific chatbot usually
-  starts  with  merely  a  handful of labeled data available in the early stage.
-  Besides,  in  the  active  learning framework, building an effective auxiliary
-  system  with limited resource is also quite important to help developers label
-  data more efficiently.
-
-  \subsection{Baselines}
-  We choose three kinds of system to construct our baselines.
-
-  \begin{enumerate}
-    \item \emph{Pretrained model based classification system}, which consists of
-    BERT \cite{devlin2018bert},  RoBERTa \cite{liu2019roberta},  and  ALBERT  \cite{lan2019albert}  based.  These pretrained
-    models  are  practically  proven  to  achieve  outstanding  performances  in
-    classification task and other NLP tasks.
-
-    \item   \emph{Non-pretrained   model  based  classification  system},  which
-    consists  of  a typical CNN based TextCNN \cite{kim2014convolutional}, and a
-    label-embedding based LEAM \cite{wang2018joint}. Regarding TextCNN, the
-    model is based on output from RoBERTa tokenization, and the kernels are set
-    as 1, 2, 3, 4, 5. Regarding LEAM, a literal class label is required, which
-    is available only in HWU64, CLINC150, BANKING77. Thus, for other two
-    datasets, we have to use its class number instead.  Empirically,
-    a  non-pretrained  model  based  system  are  not  performing  as  well as a
-    pretrained  models  based,  if  both is applicable in some task. Our listing
-    these  non-pretrained model based systems here is to provide a comprehensive
-    performance comparison on our datasets.
-
-    \item   \emph{Pre-trained   model   based   similarity   model}.  We  choose
-    RoBERTa-large  as  our  fundamental  module as our SFC systems are based on
-    RoBERTa  too, and RoBERTa is empirically more effective than other pretrained
-    models  in  the  short  text  classification  task  in  our  experiments. In
-    inference,  we  use  an  elastic search to find a set of potential candidate
-    labels for the similarity model, to guarantee a reasonable running time.
-  \end{enumerate}
-
-  Our SFC systems include two-stage SFC with ablation, trained with two tasks
-  separately and both, and joint SFC with all three tasks.
-
-  \subsection{Implementation Details}
-  For  our  SFC  systems,  we  use RoBERTa-large as the pretrained model for both
-  classification  task  and  sentence-pair similarity task. We fine-tune
-  our  SFC  system  on  our datasets with max sequence length of 128,
-  learning  rate  of 1.5e-5 for RoBERTa-large pretrained model and learning rate
-  of  5e-4  for  task-specific  layer  with polynomial decay and Adam optimizer.
-  Besides,  we  set  the  max number of the epoch to 100 and save the best model on
-  validation  set based on testing result in weighted F1 score
-  \footnote{In the multi-class and multi-label case, this is the average of the
-  F1 score of each class with weighting depending on the numbers in each class.}.
-  We report the F1 score as the main evaluation measure for all experiments.
-
-  In two-stage SFC, in equ. \ref{eq:two-stage_SFC_loss} the weights of two tasks
-  are  set  as  $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting. The reason
-  for  giving  task  2 relatively more weights is that according to the ablation
-  experiments  we  did  in Section \ref{sec:exp}, task 2 contributes more to the
-  overall  performance.  In  joint  SFC,  in  equ.  \ref{eq:joint_SFC_loss}, the
-  weights  of  three  tasks  are  set  as  $\alpha_S=0.25$,  $\alpha_K=0.25$ and
-  $\alpha_C=0.5$  in  our setting. Overall, the task weights are less sensitive
-  in Joint SFC than in two-stage SFC.
-
-  For  the  experiments  in  Table  \ref{tbe:table2},  we  empirically  set  the
-  hyperparameter  to  be  $K=5$  and  $P=10$  for  all  SFC  variants.  In Table
-  \ref{tbe:table3},  we  conduct extensive experiments to see the performance of
-  SFC system under various hyperparameter settings.
-
-  \subsection{Result Analysis}
-  All  results  in  F1  score  on  the  five  datasets with different models and
-  configurations are showed in Table \ref{tbe:table2}.
-
-  The performance of each model is measured in F1 score on the fixed
-  test  set  for  each  dataset.  
-  Overall,  two-stage  SFC systems in multi-task training deliver  moderate 
-  improvements  over  corresponding baselines, and joint SFC deliver more
-  significant and consistent improvements over the best baseline, RoBERTa based
-  classification. In following content, we dive into more details.
-
-  \subsubsection*{Are multi-task and joint training working?} 
-  First, we compare the four  SFC  variants to analyze the improvement
-  brought  by  multi-task  and  joint-model  structure.
-
-  \begin{table}
-    \begin{centering}
-      \begin{tabular}{|c|c|c|c|c|}
-        \hline
-        F1 score & Two-stage SFC & Joint SFC & Gap & \tabularnewline
-        \hline
-        top-1 accuracy  & \textbf{81.50} & 81.07 & -0.47 & \tabularnewline
-        top-5 accuracy & 94.01 & \textbf{94.30} & +0.29 & \tabularnewline
-        \hline
-      \end{tabular}
-      \par
-    \end{centering}
-    \caption{The average classification accuracy in percentage in stage 1 on all five dataset.}
-    \label{tbe:top1_5_accuracy}
-  \end{table}
-
-  Comparing with training two-stage SFC with multi-task, training with only task
-  1,  namely the sentence pair similarity model, degrades by 0.8 percent
-  point  on average, and training with only task 2, namely the top-K based
-  classification  task,  degrades  by  0.45  percent  point  on  average.  These
-  degradation  indicates  multi-task training in two-stage SFC is helpful for the
-  system  performance.  Besides, task 2 plays a relatively more important role in
-  multi-task learning, and this aligns with their optimal weight settings.
-
-  Joint SFC consistently outperforms two-stage SFC with multi-task training  
-  on 5 diverse datasets by 0.95 percents  on  average. 
-  This observation supports the idea that the joint model
-  structure  can  alleviate  the  limitation  brought by the lack of interaction
-  between  two  stages.  In  following analysis, we will focus on the comparison
-  between joint SFC and the other baseline models.
-
-  \subsubsection*{Is  the  fusion of classification and similarity models
-  helpful?}  We  compare  joint SFC with classification and similarity based
-  baselines respectively.
-
-  \begin{table*}
-    \begin{centering}
-
-      \begin{tabular}{|c|c|c|c|c|c|c|}
-        \hline 
-        \multicolumn{1}{|c|}{\multirow{2}*{Dataset}}&\multicolumn{1}{c|}{\multirow{2}*{Model}}& $K=3$ & $K=5$ & $K=10$ & $K=15$ & $K=20$\tabularnewline
-        \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & $P=20$ & $P=10$ & $P=5$ & $P=4$ & $P=3$\tabularnewline
-        \hline
-        \multicolumn{1}{|c|}{\multirow{2}*{ITG}}& two-stage SFC & $0.8034$ & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
-        \cline{2-7}
-        \multicolumn{1}{|c|}{} & joint SFC & $0.7986$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7918$\tabularnewline
-        \hline
-        \multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& two-stage SFC & $0.7278$ & $0.7364$ & $0.7366$ & $0.7328$ & $0.7204$\tabularnewline
-        \cline{2-7}
-        \multicolumn{1}{|c|}{} & joint SFC & $0.7334$ & $0.7445$ & $0.7516$ & $0.7344$ & $0.7373$\tabularnewline
-        \hline
-      \end{tabular}
-      \par
-    \end{centering}
-    \caption{
-      We  show the performances of SFC from different settings of
-      hyperparameters, $K$  denoting the candidate class number from stage 1,
-      $P$ denoting the number of sampled sententence pair in stage 2. 
-    }
-    \label{tbe:table3}
-  \end{table*}
-
-  Regarding the  classification  models,  joint SFC
-  outperforms RoBERTa-large based, the strongest among all baselines, 
-  by 2.04 percent points on average F1 score over 5 datasets.  
-  Especially, ALBERT.xxlarge based is rather unstable  in this senario. Thus, 
-  we did multiple run with different settings and  report the  best  ones here. 
-  Comparatively,  RoBERTa  based is  the  most stable and has the best performance 
-  n almost all experiment settings.
-
-  Regarding  the  similarity  model,  as  analyzed  above,  we  only  choose the
-  RoBERTa-large based implementation as our baseline. Joint SFC achieves more improvement of
-  7.09  percent points  on average F1 score.
-
-  The above analysis illustrates that suitable fusing the two kinds of models
-  can take their advantages.
-
-  \subsubsection*{Does joint SFC improve the classification in stage 1?}
-  We  compare  the  top-1  prediction and top-5 candidate labels in stage 1 from
-  two-stage SFC and joint SFC in Table \ref{tbe:top1_5_accuracy}. We should note
-  that  two-stage  SFC  does not optimize the stage 1 model, which is a RoBERTa
-  based classification model.
-
-  The joint training does not improve the classification performance in stage 1,
-  measured  by  top-1  accuracy.  However,  it  improves  the  quality of top-5
-  candidate  class  labels.  It  can  be  explained that, a classification model
-  inherently optimizes the objective loss, 0-1 error of top-1 here; the sentence
-  pair similairity model in the joint SFC poses more positive effect in optimizing the 
-  candidate labels.
-
-  \subsubsection*{How does training sample size influence SFC?} 
-  We analyze the overall  improvement  trend  of  joint SFC under various few-shot
-  settings, and show results in Fig. \ref{fig:trend}.
-
-  Our main focus  is  to  study  chatbot  building  in common situation during real-world
-  application  where  only  a few sample sentences are available for each class.
-  The  experimental  results  for  the  3  diverse  intention detection datasets
-  (ClINC150,  BANKING77,  HWU64)  under  few-shot  settings, 5 to 50 samples per
-  class,  indicate that our proposed joint SFC can achieve 2.47 percents average
-  improvement   over  one  of  the  most  powerful  baseline  models,  which  is
-  RoBERTa-large  classification  model.  Moreover,  the  improvement  in F1 score
-  becomes  more  and  more prominent with the decrease of data sample number per
-  class.
-
-  \begin{figure}[t]
-    \begin{centering}
-      \includegraphics[scale=0.2]{picture/improvement_trend.jpg} 
-      \par
-    \end{centering}
-    \caption{
-      Improvements  from  Joint  SFC  over  RoBERTa  based  classification  with
-      different size of training data.
-    }
-    \label{fig:trend}
-  \end{figure}
-
-  Especially,  in the most extreme few-shot setting with only 5 training samples
-  per  class  our joint SFC achieves 4.97 percent points improvements on average
-  over  RoBERTa-large classification model. This observation indicates that SFC
-  is  especially  well-performed  when being applied during the initial stage of
-  building  task-specific  chatbot  system,  where the amount of data sample for
-  each class label is extremely scarce.
-
-  Furthermore,  our  proposed  joint  SFC can also achieve 2.04 percents average
-  improvement  over  RoBERTa-large classification model on all the data settings
-  including  the  ones  with  large  scale,  30  to  50  samples per class. This
-  indicates that joint SFC can still steadily outperforms pretrained model based
-  baseline even if the data size grows bigger. However, the improvement is still
-  more prominent when the data is scarce, which makes SFC an excellent model for
-  low-resource chatbot scenario.
-
-  \subsubsection*{How does joint SFC relate to the label  embedding based  LEAM?}
-  LEAM performs consistently better than TextCNN by a large margin in all
-  datasets. TextCNN is practically efficiently in task-specific chat
-  applications, and LEAM shows its power in modeling labeling information.
-
-  LEAM  does not perform as well as SFCs, since the first intuitive reason is it
-  does  not use pretrained model as encoding module; and another critical reason
-  is  in  task-specific  chat applications, it is common to have many intentions
-  that are close to some others with a minor difference, and it is hard and even
-  impossible  to  name  each  intention  with  a short clear name. One candidate
-  solution  is  setting  a most standard sample as the label of that class. When
-  using  non-pretrained  models  base  LEAM,  this is applicable. Yet when using
-  pretrained  model  based, as the all labels can be hundreds of thousands, then
-  this  can not be accommodated in a poplar 32 G Tesla V100 GPU. Actually, joint
-  SFC  can  be  kind  of  understood  as  a  generalization form of LEAM. In the
-  scenario when there is no clear class label, the relationship between a sample
-  and  a class label is implicitly encoded as that between a sample and another
-  sample  from  the  same  class, and this turns into a sentence pair similarity
-  model.
-
-  \subsubsection*{Settings  of  hyperparameters} 
-  Finally, we analyze the effect brought
-  by  different  settings  of  hyperparameters,  see  Table \ref{tbe:table3}.
-
-  We  conduct  experiments on 5 different settings of hyperparameters, which are
-  the  number of candidate class number $K$ and the number of sentence pairs $P$
-  for  each  class,  on  ITG  and Amazon-670K datasets to find the most suitable
-  setting  of  these  2 hyperparameters. We control the total number of sentence
-  pairs  sampled for each user query into about the same level of amount(50-60).
-  Through  analyzing the experimental results shown in Table \ref{tbe:table3}, we
-  find  that the best setting of hyperparameters might be different for datasets
-  of  different  data  size.  The  class label number of ITG and Amazon-670k are
-  similar  in  our  experimental setting, which is around 250. However the total
-  amount of data points of ITG is approximately 2 times larger than Amazon-670k.
-  Therefore,  the  setting of $K=5$ and $P=10$ is good enough for ITG since most
-  of  the  classes  contains  over 10 data points. However, for Amazon-670k, the
-  amount  of  data  sample  for  each  class  is  scarce, thus, we may need more
-  candidate  classes to sample enough effective sentence pairs for sentence-pair
-  model  layer  of  SFC.  In this way, the setting of $K=10$ and $P=5$ becomes a
-  good choice. However, in spite of the effect on evaluation performance brought
-  by different settings of hyperparameters, joint SFC still steadily outperforms
-  two-stage  SFC  by  0.41  percents  in  overall  average  F1 score  on  ITG and
-  Amazon-670k datasets.
-
-  In  conclusion, to the best of our knowledge, these experimental results place
-  joint  SFC as the best performing model on 5 diverse experimental datasets for
-  text   classification   task,   especially   when   it's   under  low-resource
-  task-specific conversational chatbot scenario.
-
-  \bibliographystyle{aaai21}
-  \bibliography{refs}
-
-\end{document}

### 2020-09-10 chatbot_classification/aaai_2021/conclusion.tex
Reorganized.   modified:   paper.tex
  new file:   abstract.tex
  new file:   introduction.tex
  new file:   related_work.tex
  new file:   methodology.tex
  new file:   experiments.tex
  new file:   conclusion.tex

--- 2020-08-30 chatbot_classification/aaai_2021/versions/paper.ver_01.tex
@@
-%% LyX 2.3.1-1 created this file.  For more info, see http://www.lyx.org/.
-%% Do not edit unless you really know what you are doing.
-\documentclass{article}
-\usepackage[latin9]{inputenc}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{float}
-\usepackage{subfigure}
+\section{Experiments}
+\label{sec:conclusion}
 
-\makeatletter
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
-%% Because html converters don't know tabularnewline
-\providecommand{\tabularnewline}{\\}
-%% A simple dot to overcome graphicx limitations
-\newcommand{\lyxdot}{.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-% Template for GlobalSIP-2018 paper; to be used with:
-%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
-%          IEEEbib.bst - IEEE bibliography style file.
-% --------------------------------------------------------------------------
-\usepackage{spconf}
-
-\def\x{{\mathbf x}}
-\def\L{{\cal L}}
-
-\makeatother
-
-\begin{document}
-\title{     
-  %SFC: Few-Shot Text Classification via Similarity Fused with Classification System
-  Joint training of classification model and similarity model for low-resource
-  text classification in chatbot
-}
-\name{Jingwen Huang}   
-\address{     
-  \{hanmei613\}@gmail.com   
-}
-\maketitle
-
-\begin{abstract}
-  Building  conversational  chatbot  system  has  become  a  popular solution to customer  services  under various business scenarios. A
-  conversational  chatbot needs to detect user's intent given a few words, which
-  essentially  equals  to  short-text  classification  problem  in  the field of Natural  Language  Processing.
-Moreover,  each  time  for  a  new service, the task-specific  chatbot  system  often needs to perform well in few-shot setups due  to lack of domain-specific data, which is quite a challenge for single-model system such as text classification model system or sentence-pair semantic similarity model system under such a low-resource condition.
-Therefore, in this paper, we propose
-  SFC,  a 2-stage joint system with multi-task training technique for both text classification task and sentence-pair semantic similarity task to
-  overcome  this challenge.
-Furthermore, we additionally propose an improved version of SFC to allow text classification model and sentence-pair model be combined into a joint model organized in hierarchical structure.
-We also
-  conduct extensive experiments on 4 public and 1 private datasets in few-shot setup (i.e.,
-  with only 5 to 20 training data per class). The experimental results show that
-  our  system can steadily outperform several competitive single-model baselines by 2 percent
-  in average accuracy.
-\end{abstract}
-%\keywords{}
-
-\section{Introduction}
-\label{sec:intro}
-% latest version start
-Task-specific conversational chatbot\cite{wen2016network} are designed to share the working pressure of human customer service agents who are responsible for solving customers' questions or queries about certain products or services.
-Regardless of whether the conversation is single-turn or multi-turn, the essential technical solution behind the chatbot is intent classification model which can identify the correct intent behind user's input text and find the corresponding answer.
-
-Although task-specific conversational chatbot already has a wide application in various business and industries, it's still a quite challenging task due to its natural properties of low-resource.
-First, customers' utterance within a conversation is usually quite short and completed in a few words.
-Short text\cite{song2014short} are generally more ambiguous in comparison with long texts such as paragraphs or documents since they don't contain enough contextual information, which poses a great challenge\cite{chen2019deep} for classification task\cite{phan2008learning,yan2009dynamic,hua2015short}.
-Second, at the initial stage of building a chatbot for specific task or service, it's often extremely hard to collect sufficient data samples for each class.
-The reason is that it's usually too expensive and time consuming to extract different ways of natural language expression for each intent class from history conversation log or even manually compose the corpus from nothing.
-Therefore, the key to building a task-specific chatbot with high performance becomes solving the challenge of short-text classification\cite{sriram2010short} problem under few-shot setting\cite{yu2018diverse}.
-
-\begin{figure}[htbp]
-\centering 
-\subfigure[classification model]{
-\label{Fig.1.sub.1}
-\includegraphics[scale=0.7]{picture/picture1.pdf}}
-\subfigure[similarity model]{
-\label{Fig.1.sub.2}
-\includegraphics[scale=0.55]{picture/picture2.pdf}}
-\caption{Two popular structures of building task-specific conversational chatbot}
-\label{Fig.1.main}
-\end{figure}
-
-One of the most popular approach among existing work was text classification model based on neural network.
-Since the length of the text is quite short, many previous work\cite{wen2016network} choose neural network such as convolutional neural networks (CNNs)\cite{kim2014convolutional,zhang2015character,conneau2016very}
-or long short term memory networks
-(LSTMs)\cite{mousa2017contextual,liu2016recurrent} to accomplish the task of extracting semantic feature from limited amount of words.
-A common model structure is adding a softmax classifier to the top of the neural network.
-Afterwards, pre-trained language models on large corpus like BERT\cite{devlin2018bert} and
-RoBERTa\cite{liu2019roberta} has  been proven more powerful in solving many NLP
-tasks      including      short-text      classification\cite{madabushi2020cost}.
-Especially   for  few-shot  scenarios\cite{yu2018diverse}, pre-trained  model  based on transformers\cite{vaswani2017attention}, shown in Fig.
-\ref{Fig.1.sub.1}, tends  to  do more help to reducing the negative effects brought by scarcity of training data.
-
-Another popular approach among previous work was based on sentence-pair model.
-The motivation of this approach was started from the idea of Information Retrival (IR) based chatbot\cite{jafarpour2010filter, leuski2011npceditor}.
-Having a Q-A (Question-Answer) pairs dataset and user query Q, the IR based conversational system will look up in the Q-A dataset for the pair (Q', A') that best matches query Q through semantic analysis and returns A' as the answer to Q\cite{mnasri2019recent}.
-In this way, sentence-pair model pre-trained on large corpus of semantic similarity identification task can be applied for being used as a tool to identify the class with highest semantic similarity to customer's query.
-A common model structure of pre-trained\cite{devlin2018bert} sentence-pair model is based on multiple cross-attention mechanism\cite{barkan2020scalable}, shown in Fig.
-\ref{Fig.1.sub.2}.
-Due to the fact that many experiment results have shown that RoBERTa\cite{liu2019roberta} is an improved  version  of  BERT, and has achieved amazing results on both text classification and sentence-pairs semantic similarity tasks, we choose RoBERTa as an important baseline approach in this paper.
-
-Despite the success of these 2 approaches, they still have some limitations in task-specific chatbot scenario.
-As for the text classification model approach, it's quite hard to use data augmentation method to solve the data insufficiency challenge since the it's usually unfeasible to get large amount of domain-specific data when facing a new task.
-With respect to the sentence-pair model approach, though we can obtain large amount of data in semantically duplicate sentence pair identification domain for transfer learning\cite{sun2019fine}, it's still quite hard to perform well on task-specific dataset because the training objective of sentence-pair model is semantic similarity, which is slightly different from the target of classification task.
-That is to say, there always exists some intent classes which cannot be distinguished by each other merely depending on semantic similarity.
-For example, we have 2 user query saying, A: What should I do if I want to change my password?
-B: What is the modification rule if I want to change my password?
-In this case, sentence A is semantically similar to B, since they both express the
-desire for changing password.
-However, it's still reasonable to classify them into 2 intent classes, since A is asking for the method for changing password, while B is asking for the rule to follow when creating a new password.
-
-\begin{figure}[htbp]
-\begin{centering}
-\includegraphics[scale=0.48]{picture/picture3}
-\par\end{centering}
-\caption{\textbf{Network Structure of 2-stage SFC:} a joint system of multi-task for both text classification task and sentence-pair semantic similarity task.}
-\label{fig:ver.1.3}
-\end{figure}
-
-The above limitation motivates us to propose a joint system of both text classification task and sentence-pair semantic similarity task, named SFC here, shown in Fig.
-\ref{fig:ver.1.3}.
-Our goal is to utilize the advantage of the feasibility of transfer learning based on semantic similarity, while in the mean time, add the classification task's target into the training process of sentence-pair model for multi-task learning\cite{caruana1993multitask,collobert2008unified}.
-To obtain such a joint system, we first start with preparation work, which is pre-training a sentence-pair model on external corpus for sentence pair duplication identification, and then find an auxiliary model or tool which can help us sample out top-K most related intent classes.
-This auxiliary model or tool can either be searching engine such as elasticsearch\cite{divya2013elasticsearch} or a text classification model trained on task-specific chatbot data.
-Afterwards, we further fine-tune the sentence-pair model with 2 training tasks: 1) the regular sentence pair similarity tasks.
-Here we use the text classification model as an auxiliary model in this paper to sample sentence pairs for training based on negative sampling strategy\cite{bamler2020extreme}.
-The reason is that a task-specific chatbot often has hundreds of intent classes, which forms too many sentence pairs for training since any two sentences from two different classes can form a sentence-pair of negative sample.
-Besides, according to Bamler\cite{bamler2020extreme}, training on negative samples from most confusing wrong label can help model converge faster and obtain better performance.
-2) the classification task on top-K (here K is a hyperparameter) candidate classes provided by our auxiliary model or tool.
-Here we use the average pooling of the representation given by sentence-pair model for sentence pairs formed by the user input query and the corpus sentences in each class as the feature.
-We stack the task-specific layers on the top of the shared-parameter sentence-pair model structure, which is a classic parameter sharing mechanism\cite{collobert2008unified, subramanian2018learning,liu2019multi} for multi-task\cite{sun2019fine}.
-In this way, specific knowledge contained in these 2 tasks can be fully explored and deeply interact with each other to obtain better overall performance.
-
-However, since the auxiliary tool in joint system mentioned above works in a separate stage from sentence-pair model, we find the the quality of sampled candidate classes might limit the overall performance of SFC, since the candidate classes for each user query is always fixed during the multi-task training process.
-This observation motivates us to further improve SFC into a joint model of sentence-pair model and text classification model in a hierarchical architecture by putting different tasks at different network layers\cite{sogaard2016deep, hashimoto2016joint} and then training them together, shown in Fig \ref{fig:framework}.
-Here, the text classification model involved in joint training process replace the role of auxiliary tools.
-In this way, the sentence pairs selected from top-K classes becomes dynamic, which means the text classification model will also be further optimized to provide better top-K classes pooling result.
-
-We summarize our contributions as follow:
-
-1) We propose a novel joint system named SFC with multi-task training technique designed for task-specific conversational chatbot with low-resource, in which we make full utilization of the advantages brought by both the text classification task and sentence-pair semantic similarity task.
-
-2) To further improve the system performance of SFC, we also propose an innovative joint model structure, in which the text classification model and sentence-pair model are fused into one single model for joint training.
-
-3) Experiment results on 4 public and 1 private short-text classification datasets with respect to intent recognition tasks under conversational chatbot scenario all demonstrated that our proposed SFC joint system with multi-task, as well as the improved version of SFC, can both achieve remarkable improvement comparing to some powerful single-task and single-model baselines, especially under few-shot settings.
-
-\begin{figure*}[t]
-\begin{centering}
-\includegraphics[scale=0.72]{picture/picture4} 
-\par\end{centering}
-\caption{\textbf{Network Structure of hierarchical SFC:} a joint model of sentence-pair model and text classification model organized in hierarchical structure by completing different tasks at different network layers.}
-\label{fig:framework}
-\end{figure*}
-
-\section{Methodology}
-In this section, we will describe a system of similarity model fused with classification model, named as SFC, in detail.
-We come up with 2 different approaches for implementation of SFC system, in which hierarchical SFC is a further improvement of 2-stage SFC for better performance.
-\subsection{2-stage SFC with multi-task learning}
-The detailed network structure of 2-stage SFC is shown in Fig. \ref{fig:ver.1.3}. It is composed with 2 separate stages in charge of different jobs.
-In stage 1, we can use any auxiliary model or tool to provide top-K most related classes for sampling sentence pairs of both positive samples and negative samples for stage 2.
-Suppose we have a training data set $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$ of $N$ data points, in which $x_{i}$ is the user input query and $y_{i}$ is a single class label from a class label set of $C$ classes in total.
-If we want to generate sentence pair data set $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$, where $(x, x')_{j}$ is sentence pair grouped by 2 user input queries and $l_{j}\in\{0, 1\}$ is similarity class label, see Equ.
-\ref{eq:similarity label},
-\begin{align}
-l_{j}=\begin{cases} \label{eq:similarity label}
-0 & y_{x}\neq y_{x'}\\
-1 & y_{x}=y_{x'}
-\end{cases}
-\end{align}
-directly from original data set $\mathcal{D}$ without any sampling strategy, then $\mathcal{D'}$ will have $M=N^2$ data points of sentence pairs, which might be too time-consuming for the training process of stage 2 since we often have hundreds of class labels under task-specific chatbot scenario.
-Although we may only have a few data points for a single class label, $N$ is still quite a big number.
-
-Therefore, we adopt the idea of adversarial negative sampling strategy raised by \cite{bamler2020extreme}.
-The key idea of this sampling strategy is to train with negative samples that are hard to be distinguished from positive samples.
-Now suppose we have a user input query $x_{i}$ and top-K most related class labels set $\mathcal{C'}=\{c'_{1}, \dots, c'_{K}\}$ found by auxiliary model or tool in stage 1, where $K$ is a hyperparameter set by us that controls candidate class number, we apply the adversarial negative sampling strategy into our sentence pair sampling process by the following 2 steps:
-
-\textbf{1.
-positive sentence pair sampling}: During the training process, we have to first make sure that the ground truth class label $y_{i}$ for $x_{i}$ is within the candidate class label set $\mathcal{C'}$.
-If $y_{i}\notin \mathcal{C'}$, we will manually add $y_{i}$ into $\mathcal{C'}$ by replacing $c'_{K}$ with $y_{i}$.
-Afterwards, we will randomly sample $P$ sentences $\{x'_{0},x'_{1}, \dots, x'_{P}\}$ with the same class label as $y_{i}$ from data set $\mathcal{D}$ to form the set of sentence pairs with positive label $\mathcal{P'}_{i}=\{[(x_{i}, x'_{0}), 1], [(x_{i}, x'_{1}), 1], \dots, [(x_{i}, x'_{P}), 1]\}$, where $P$ is also a hyperparameter set by us that controls the number of sentences we should sample from each class.
-
-\textbf{2.
-negative sentence pair sampling}: As for negative sentence pairs, we will also randomly sample $P$ sentences for each class in the negative candidate class label set $\mathcal{C'}\backslash \{y_{i}\}$.
-The class labels in $\mathcal{C'}\backslash \{y_{i}\}$ are the set of most confusing classes comparing to the ground truth ${y_{i}}$, so we assume that the sentence pairs with negative label grouped by user input query $x_{i}$ and sentences with class labels in $\mathcal{C'}\backslash \{y_{i}\}$ are also strong adversarial negative samples for sentence-pair similarity model that can help enhance the training speed and performance.
-According to the same method as positive sentence pair sampling, we can obtain the set of sentence pairs with negative label as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{0}), 0], [(x_{i}, x'_{1}), 0], ..., [(x_{i}, x'_{P\cdot (K-1)}), 0]\}$
-
-In this way, we can generate the sentence pair data set $\mathcal{D'}$ for stage 2 based on the top-K class label set $\mathcal{C'}$ provided by stage 1 as $\mathcal{D'}=\{\mathcal{P'}_{i}\cup \mathcal{N'}_{i}\}_{i=1}^{N}$, in which we will have $M=N\cdot K\cdot P$ data points of sentence pairs in total.
-
-After explaining the data sampling principle for sentence pairs and how the 2 stages in SFC system connect with each other, let's go deeper into model structure within these 2 stages respectively to see how it works.
-
-\subsubsection{stage 1: classification model for providing top-K classes}
-As for stage 1, our SFC system can adapt to any auxiliary model or even searching tool based on Term Frequency-Inverse
-Document Frequency (TF-IDF) retrieval.
-In this paper, however, we choose to fine-tune RoBERTa on our task-specific data set $\mathcal{D}$ by adding a softmax classifier on top of it, the same as the structure shown in Fig.
-\ref{Fig.1.sub.1}, for better overall performance.
-According to our experimental result, RoBERTa can guarantee that approximately 95\% ground truth label be included in top-5 candidate classes with highest probability after being fine-tuned on task-specific data set with experimental result measured by F-score at around 0.75.
-So we use RoBERTa as encoder of classification model in our setting at stage 1 to ensure low limitation for the performance of stage 2.
-
-For single-sentence text classification tasks, given a data point $x_{i}$ with class label $y_{i}$ from data set $\mathcal{D}$, RoBERTa takes the final hidden state $h_{i}$ of the first token [CLS] as the representation for the whole sequence of $x_{i}$.
-Let's suppose we have a linear layer as ${\Phi}^C_{i}=W^Ch_{i}+b^C$, where $W^C$ and $b^C$ are trainable parameters, the probability score for $x_{i}$ can be calculated as $p^C_{i}=softmax(W^Ch_{i}+b^C)=softmax({\Phi}^C_{i})$.
-Then, the loss for stage 1 classification model is shown in Equ.
-\ref{eq:classification loss}, in which the first term $\varPhi_{i,y_{i}}^C$ encourages high probability for prediction of the correct label $y_{i}$.
-
-\begin{equation}
-\begin{aligned}
-\mathcal{L}^{C}&=\frac{1}{N}\sum_{i=1}^{N}-log(\frac{exp(\varPhi_{i,y_{i}}^C)}{\sum_{j=1}^{C}exp(\varPhi_{i,j}^C)}) \\&=\frac{1}{N}\sum_{i=1}^{N}-\varPhi_{i,y_{i}}^C+log(\sum_{j=1}^{C}exp(\varPhi_{i,j}^C))
-\label{eq:classification loss}
-\end{aligned}
-\end{equation}
-
-\subsubsection{stage 2: sentence-pair model for multi-task learning}
-As for stage 2, we also choose RoBERTa as the encoder for sentence pairs, as shown in Fig.
-\ref{fig:ver.1.3}.
-Before sending sentence pairs to Roberta, we pack sentence pairs into a single sequence and separate them with a special token [SEP].
-Roberta will also add a learned embedding to every token indicating whether it belongs to the first sentence or the second one.
-Then, we utilize the cross-attention mechanism inside RoBERTa, and then extract semantic relationship between 2 sentences from the output softmax layer, which is placed on top of the last hidden representation of the [CLS] token.
-
-Before we start to fine-tune our sentence-pair model on task-specific dataset, we first fine-tune RoBERTa on Quora dataset\cite{iyer2017first}, which contains 404,290 potential duplicate question pairs, for transfer learning.
-Then we continue to do multi-task training on sentence-pair dataset $\mathcal{D'}$ sampled from the top-K candidate classes provided by stage 1.
-
-The 2 tasks for stage 2 training process are listed below.
-
-$\bullet$ \textbf{Task 1: Regular sentence-pair similarity task}
-
-For sentence pair semantic similarity task, given a data point $(x, x')_{i}$ with similarity label $l_{i}$ from data set $\mathcal{D'}=\{[(x,x')_{i},l_{i}]\}_{i=1}^{M}$, Roberta takes the final hidden state $h_{i}$ of the first token [CLS] as the representation for the sequence of packed sentence pair $(x, x')_{i}$.
-Let's suppose we have a linear layer as ${\Phi}^S_{i}=W^Sh_{i}+b^S$, where $W^S$ and $b^S$ are trainable parameters, and the probability score for $(x, x')_{i}$ can be calculated as $p^S_{i}=softmax({\Phi}^S_{i})$.
-
-Due to the fact that sentence pairs within the same class is much less than sentence pairs from different classes, the data set $\mathcal{D'}$ is imbalanced.
-Therefore, we will accommodate a weight variable $w^S = [K-1, 1]$ to the loss to eliminate the bias brought by imbalanced data, shown in Equ.
-\ref{eq:similarity loss}.
-
-\begin{equation}
-\begin{aligned}
-\mathcal{L}^{S}&=\frac{1}{M}\sum_{i=1}^{M}-w^S_{l_i}\cdot log(\frac{exp(\varPhi_{i,l_{i}}^S)}{\sum_{j=0}^{1}exp(\varPhi_{i,j}^S)}) \\&=\frac{1}{M}\sum_{i=1}^{M}-w^S_{l_i}\cdot \varPhi_{i,l_{i}}^S+w^S_{l_i}\cdot log(\sum_{j=0}^{1}exp(\varPhi_{i,j}^S))
-\label{eq:similarity loss}
-\end{aligned}
-\end{equation}
-
-$\bullet$ \textbf{Task 2: Classification task on top-K classes based on sentence-pair model}
-
-As for top-K classification task, we share the same sentence-pair similarity model structure with task 1.
-The only difference is that we add a task-specific average pooling layer, shown in Fig.
-\ref{fig:ver.1.3} to implement the classification task based on sentence-pair model.
-
-We already know that the size of ${\Phi}^S$ in task 1 is $M\times 2=(N\cdot K\cdot P)\times 2$, where $N$ is the total number of data points in original training data $\mathcal{D}$, $K$ is a hyperparameter that controls the number of candidate classes provided by stage 1, and $P$ is also a hyperparameter that controls the number of sentences we should randomly sample from each candidate class.
-Now, for the average pooling layer, we first reshape ${\Phi}^S$ into the size of $N\times K\times P\times 2$, and then split it into ${\Phi}^{K,pos}$ and ${\Phi}^{K,neg}$, and both of them will have the size of $N\times K\times P$.
-In this way, ${\Phi}^{K,pos}$ can represent the level of similarity for each sentence pair, and in the mean time, ${\Phi}^{K,neg}$ can represent the level of dissimilarity for each sentence pair.
-Then, we can do average pooling for each candidate class among the top-K classes as shown in Equ.
-\ref{eq:average pooling:1} and Equ.
-\ref{eq:average pooling:2}.
-
-\begin{align}
-{\xi}_{i,j}^{K,pos} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,pos} \label{eq:average pooling:1}\\
-{\xi}_{i,j}^{K,neg} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,neg}
-\label{eq:average pooling:2}
-\end{align}
-
-With the average pooling result ${\xi}^{K,pos}$ and ${\xi}^{K,neg}$, we also generate a top-K class label $l^{K}_i\in [1,\dots,K]$ for each ${\xi}^{K,pos}_{i}$ and  ${\xi}^{K,neg}_{i}$.
-The loss for top-K classification task is shown in Equ.
-\ref{eq:top-k classification loss}.
-In Equ.
-\ref{eq: pos top-k loss} and Equ.
-\ref{eq: neg top-k loss}, the first term $\xi_{i,l^{K}_{i}}^{K,pos}$ and $\xi_{i,l^{K}_{i}}^{K,neg}$ encourage high level of similarity and low level of dissimilarity for prediction of the correct label $l^{K}_i$ within the top-K candidate classes.
-
-\begin{align}
-\mathcal{L}^{K} = \frac{1}{N}\sum_{i=1}^{N}(\mathcal{L}^{K,pos}_{i} - \mathcal{L}^{K,neg}_{i})
-\label{eq:top-k classification loss}
-\end{align}
-where,
-
-\begin{equation}
-\begin{aligned}
-\mathcal{L}^{K,pos}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,pos})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,pos})}) \\
-&= -\xi_{i,l^{K}_{i}}^{K,pos} + log(\sum_{j=1}^{K}exp(\xi_{i,j}^{K,pos}))
-\label{eq: pos top-k loss}
-\end{aligned}
-\end{equation}
-
-\begin{equation}
-\begin{aligned}
-\mathcal{L}^{K,neg}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,neg})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,neg})}) \\
-&= -\xi_{i,l^{K}_{i}}^{K,neg} + log(\sum_{j=1}^{K}exp(\xi_{i,j}^{K,neg}))
-\label{eq: neg top-k loss}
-\end{aligned}
-\end{equation}
-
-Therefore, the overall loss function for multi-task learning in stage 2 is shown in Equ.
-\ref{eq: 2-stage SFC loss}.
-The training objective of stage 2 is to minimize the weighted sum of task-specific losses.
-Here $\alpha_S$ and $\alpha_K$ are weights of task 1 and task 2 respectively, which are $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting.
-
-\begin{align}
-\mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K
-\label{eq: 2-stage SFC loss}
-\end{align}
-
-\begin{table*}
-\begin{centering}
-
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline 
-Dataset & Domain & \#Class & \#Samples & \#Samples/Class & Experimental Settings\tabularnewline
-\hline 
-ITG & FAQ chatbot & 228 & 3938 & 17 & 3-fold\tabularnewline
-\hline 
-Amazon-670k & Product review & 250 & 1942 & 8 & class sampling\tabularnewline
-\hline 
-HWU64 & Intent detection & 64 & [320, 640, 960, 1280] & [5, 10, 15, 20] & data sampling\tabularnewline
-\hline 
-CLINC150 & Intent detection & 150 & [750, 1500, 2250] & [5, 10, 15] & data sampling\tabularnewline
-\hline 
-BANKING77 & Intent detection & 77 & [385, 770, 1155, 1540] & [5, 10, 15, 20] & data sampling\tabularnewline
-\hline 
-\end{tabular}
-\par\end{centering}
-\caption{Key statistics for experimental datasets and few shot settings}
-
-\label{tbe:dataset statistic}
-\end{table*}
-
-\subsection{hierarchical SFC with joint model structure}
-Despite the outstanding experimental result of 2-stage SFC on various tasks, we still find a limitation brought by the 2-stage system structure.
-In 2-stage SFC, Stage 1 and stage 2 are separate, so they do not interact with each other during training.
-In this case, the performance of stage 1 can limit the potential of stage 2, meanwhile, stage 2 also cannot give training feedback back to stage 1 for fine-tuning.
-
-Therefore, to further improve the overall performance of SFC, we proposed a hierarchical joint model structure, shown in Fig.
-\ref{fig:framework}.
-In hierarchical SFC, classification model is being placed in lower layer level to dynamically provide top-K candidate classes for the sentence-pair similarity model placed in higher layer level through a top-K pooling layer.
-In this way, classification model and similarity model can be merged into one single joint-model for multi-task training, thus avoiding the limitation brought by 2 separate stage structure.
-
-There are 3 tasks in total during the training process of hierarchical SFC, shown in Fig.
-\ref{fig:framework}, and the overall loss is also the weighted sum of all the task-specific losses, shown in Equ.
-\ref{eq: hierachical SFC loss}.
-Here, $\alpha_S$, $\alpha_K$ and $\alpha_C$ are the weights for task 1: sentence-pair similarity, task 2: top-K classification and task 3: general single sentence classification respectively, which are $\alpha_S=0.25$,  $\alpha_K=0.25$ and $\alpha_C=0.5$ in our setting.
-
-\begin{align}
-\mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K + \alpha_C \mathcal{L}^C
-\label{eq: hierachical SFC loss}
-\end{align}
-
-Finally, when doing inference, for each user input query $x$, we will choose the class label that contains the sentence $x'$ with highest similarity score $\varPhi$, after being packed into a sentence pair $(x, x')$ with query $x$, as our final result for prediction.
-
-\section{Experiments}
-In this section, we conduct extensive experiments over 5 task-specific dataset to evaluate the performance of our proposed SFC system and the effectiveness of the methodology of multi-task learning and hierachical joint-model structure under low-data settings.
-
-\subsection{Datasets}
-The dataset used in our experiments aims to help us study low-resource text classification problem under task-specific conversational chatbot scenario.
-Therefore, we keep all the dataset under low-resource chatbot corpus setting, which is a large number of class labels (50-250) with a few examples(5-20) in short text for each class, by sampling smaller subsets from the full scale when the raw datasets are oversized, see Table \ref{tbe:dataset statistic}.
-
-According to the task and domain, we categorize our experimental datasets into the following 3 categories:
-
-$\bullet$ \textbf{full-scale real-world task-specific faq chatbot dataset}
-
-\textbf{ITG} is a real-world FAQ chatbot dataset composed of question and answer pairs about online English teaching.
-It contains 3,938 sample questions for 228 class labels, where each class label corresponds to an unique answer for a bunch of similar sample questions.
-
-We divide the whole dataset into 3 folds randomly with approximately the same amount of data within each fold, and then choose 2 folds as the training set, the remaing 1 fold as the test set for our experiments.
-We can obtain 3 different combinations among the 3 folds, and we will use the average experimental results of these 3 combinations as the final evaluation result for this dataset.
-
-$\bullet$ \textbf{subset of customer review dataset for extreme classification}
-
-\textbf{Amazon-670K} is a customer product review dataset for text classification task from the extreme classification repository with full data containing 670,091 class labels, 285,176 training samples and 150875 test samples\cite{bhatia2016extreme}.
-As the data set contains multiple class labels per training sample, we keep only the first class label for each data point.
-Besides, we also randomly sampled 250 class labels from all the classes that contain only 5-15 data points.
-In this way, we simulate the low-resource chatbot corpus setting with the subset of 1,942 training samples and 716 test samples for 250 class labels.
-
-$\bullet$ \textbf{subset of recently-released intent detection datasets}.
-
-From our point of view, task-specific chatbot usually starts with small amount of data at the initial stage.
-As more and more customers start to communicate with the chatbot, more data can be extracted from conversation log.
-Base on these assumptions, we do experiments on the following 3 intent detection dataset under sampling method similar to the approach in \cite{casanueva2020efficient} but in more sophisticated few-shot settings, while keeping the same test sets for each experiment to see the change of the improvement scale with decreasing data amount.
-
-\textbf{HWU64} is a intent detection dataset designed for home robot scenario\cite{liu2019benchmarking}.
-It aims at the specific task of capturing the intent for different user requests to home robot and finding the corresponding answer.
-The raw dataset contains 25,716 data points for 64 class labels through crowdsourcing, which raises much more data than common real-world circumstances.
-Therefore, we experiment with the setups where only 5, 10, 15 and 20 training data points are available for each class label by random sampling.
-
-\textbf{CLINC150} is a dataset designed for task-oriented systems with 23,700 queries that are short and unstructured for 150 intents, in the same style made by real users through crowdsourcing\cite{larson2019evaluation}.
-Here, we sample 5, 10 and 15 training data points for each intent class label by random sampling for our experimental setup.
-
-\textbf{BANKING77} is a intent detection dataset for bank customer services.
-The raw dataset contains 13,084 data points for 77 class labels\cite{casanueva2020efficient}.
-Here, we sample 5, 10, 15, 20 training data points for each class label by random sampling for our experimental setup.
-
-\begin{table*}
-\begin{centering}
-\scalebox{0.8}{
-\begin{tabular}{|c|ccc|cccc|cccc|c|c|}
-\hline 
-\multicolumn{1}{|c|}{\multirow{2}*{\textbf{Models}} }& \multicolumn{3}{c|}{\textbf{CLINC150}}& \multicolumn{4}{c|}{\textbf{BANKING77}}& \multicolumn{4}{c|}{\textbf{HWU64}}& \ \ \ \textbf{ITG} \ \ \ & \textbf{Amazon-670k}\tabularnewline
-\cline{2-14}
-\multicolumn{1}{|c|}{} & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & \textbf{Full} & \textbf{Full}\tabularnewline
-\hline
-BERT-large & \multirow{2}*{$0.8080$} & \multirow{2}*{$0.8904$} & \multirow{2}*{$0.9265$} & \multirow{2}*{$0.578$} & \multirow{2}*{$0.8004$} & \multirow{2}*{$0.8518$} & \multirow{2}*{$0.8827$} & \multirow{2}*{$0.4711$} & \multirow{2}*{$0.5963$} & \multirow{2}*{$0.6342$} & \multirow{2}*{$0.7010$} & \multirow{2}*{$0.7485$} & \multirow{2}*{$0.6658$}\tabularnewline
-(classification) & & & & & & & & & & & & &\tabularnewline
-\hline
-ALBERT-xxlarge & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{$0.1422$} & \multirow{2}*{$0.2057$} & \multirow{2}*{$0.5723$} & \multirow{2}*{$0.5912$} & \multirow{2}*{$0.6601$} & \multirow{2}*{$0.6893$}\tabularnewline
-(classification) & & & & & & & & & & & & &\tabularnewline
-\hline
-RoBERTa-base & \multirow{2}*{$0.8732$} & \multirow{2}*{$0.9254$} & \multirow{2}*{$0.9363$} & \multirow{2}*{$0.7305$} & \multirow{2}*{$0.8654$} & \multirow{2}*{$0.8808$} & \multirow{2}*{$0.9080$} & \multirow{2}*{$0.5831$} & \multirow{2}*{$0.6790$} & \multirow{2}*{$0.7064$} & \multirow{2}*{$0.7100$} & \multirow{2}*{$0.7734$} & \multirow{2}*{$0.6708$}\tabularnewline
-(classification) & & & & & & & & & & & & &\tabularnewline
-\hline
-RoBERTa-large & \multirow{2}*{$0.8974$} & \multirow{2}*{$0.9372$} & \multirow{2}*{$0.9508$} & \multirow{2}*{$0.7690$} & \multirow{2}*{$0.8728$} & \multirow{2}*{$0.8966$} & \multirow{2}*{$0.9099$} & \multirow{2}*{$0.6044$} & \multirow{2}*{$0.7002$} & \multirow{2}*{$0.7129$} & \multirow{2}*{$0.7436$} & \multirow{2}*{$0.7990$} & \multirow{2}*{$0.7156$}\tabularnewline
-(classification) & & & & & & & & & & & & &\tabularnewline
-\hline
-RoBERTa-large & \multirow{2}*{$0.8266$} & \multirow{2}*{$0.8861$} & \multirow{2}*{$0.9023$} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{$0.5425$} & \multirow{2}*{$0.6164$} & \multirow{2}*{$0.6503$} & \multirow{2}*{$0.6729$} & \multirow{2}*{$0.7418$} & \multirow{2}*{$0.6362$}\tabularnewline
-(similarity) & & & & & & & & & & & & &\tabularnewline
-\hline
-2-stage SFC & \multirow{2}*{$0.8979$} & \multirow{2}*{$0.9457$} & \multirow{2}*{$0.9517$} & \multirow{2}*{$0.7975$} & \multirow{2}*{$0.8818$} & \multirow{2}*{$0.8962$} & \multirow{2}*{$0.9109$} & \multirow{2}*{$0.6477$} & \multirow{2}*{$0.7055$} & \multirow{2}*{$0.7200$} & \multirow{2}*{$0.7232$} & \multirow{2}*{$0.7972$} & \multirow{2}*{$0.7189$}\tabularnewline
-(task1 only) & & & & & & & & & & & & &\tabularnewline
-\hline
-2-stage SFC & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-} & \multirow{2}*{-}\tabularnewline
-(task2 only) & & & & & & & & & & & & &\tabularnewline
-\hline
-2-stage SFC & \multirow{2}*{$0.9167$} & \multirow{2}*{$0.9456$} & \multirow{2}*{$0.9571$} & \multirow{2}*{$0.7954$} & \multirow{2}*{$0.8854$} & \multirow{2}*{$0.8931$} & \multirow{2}*{$0.9192$} & \multirow{2}*{$0.6525$} & \multirow{2}*{$0.7001$} & \multirow{2}*{$0.7168$} & \multirow{2}*{$0.7476$} & \multirow{2}*{$\textbf{0.8124}$} & \multirow{2}*{$0.7364$}\tabularnewline
-(task1 + task2) & & & & & & & & & & & & &\tabularnewline
-\hline
-\multirow{2}*{Hierarchical SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline
- & & & & & & & & & & & & &\tabularnewline
-\hline
-\end{tabular}
-}
-\par\end{centering}
-\caption{F-scores on five task-specific dataset for text classification in chatbot under low resource.
-For ITG, we keep the full dataset.
-For Amazon-670k, we randomly sampled 250 classes with training sample numbers within 5-15 samples per class.
-For CLINC150, BANKING77, HWU64, we set up various few-shot settings (5/10/15/20 samples per class) while keeping the test set to be fixed.
-The highest scores for each data setting are marked in bold.}
-
-\label{tbe:table2}
-\end{table*}
-
-\subsection{Baselines}
-We choose 3 groups of representative baselines:
-
-\textbf{Group 1: single-task classification model.} This group of baseline models are based on the network structure for classification model shown in \ref{Fig.1.sub.1}.
-As for the pretrained model, we choose RoBERTa, BERT and ALBERT, all of which are among the most powerful pretrained models that achieve outstanding results in many NLP tasks, in our experimental setting.
-Since we apply RoBERTa in our SFC system, we naturally adopt single-task classification model based on RoBERTa-large and RoBERTa-base as our baseline models.
-Besides, we also adopt the baseline pre-trained model BERT-large\cite{devlin2018bert} and recently released ALBERT-xxlarge\cite{lan2019albert} for comparison.
-Since we use different few-shot settings from \cite{casanueva2020efficient} for those intent detection datasets, we also use BERT-large tuned on our few-shot settings as an essential reference for experimental results.
-
-\textbf{Group 2: single-task similarity model.} This group of baseline models are based on network structure for similarity model shown in \ref{Fig.1.sub.2}.
-We choose RoBERTa-large for the pretrained model part as an powerful baseline.
-But during the evaluation step, we use elastic search to do a rough filter for candidate sentence pairs to guarantee a reasonable inference time for each user query.
-
-\textbf{Group 3: SFC system with ablation study.} This group of baseline is based on the network structure of 2-stage SFC shown in \ref{fig:ver.1.3}.
-We conduct ablation study by introducing single task SFC system with only Task 1 or Task 2 to investigate the influence of each component within the total loss.
-
-\subsection{Implementation Details}
-For our SFC system, we use RoBERTa-large as the pretrained model for both classification task and sentence-pair similarity task.
-We further fine-tune our SFC system on task-specific datasets with max sequence length of 128, learning rate of 1.5e-5 for RoBERTa-large pretrained model and learning rate of 5e-4 for task-specific layer with polynomial decay and Adam optimizer.
-Also, we set the max number of the epoch to 100 and save the best model on validation set based on test result in F-score.
-We also report the F-score as the main evaluation measure for all experimental results.
-
-For the experiments in Table \ref{tbe:table2}, we empirically set the hyperparameter to be $K=5$ and $P=10$ for all SFC variants.
-In Table \ref{tbe:table3}, we conduct extensive experiments to see the performance of SFC system under various hyperparameter settings.
-
-\begin{table*}
-\begin{centering}
-
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline 
-\multicolumn{1}{|c|}{\multirow{2}*{Dataset}}&\multicolumn{1}{c|}{\multirow{2}*{Model}}& $K=3$ & $K=5$ & $K=10$ & $K=15$ & $K=20$\tabularnewline
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & $P=20$ & $P=10$ & $P=5$ & $P=4$ & $P=3$\tabularnewline
-\hline
-\multicolumn{1}{|c|}{\multirow{2}*{ITG}}& 2-stage SFC & 0.05 & $0.8124$ & 0.05 & 0.05 & 0.05\tabularnewline
-\cline{2-7}
-\multicolumn{1}{|c|}{} & Hierarchical SFC & 0.05 & $0.8114$ & 0.05 & 0.05 & 0.05\tabularnewline
-\hline
-\multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& 2-stage SFC & 0.05 & $0.7364$ & 0.05 & 0.05 & 0.05\tabularnewline
-\cline{2-7}
-\multicolumn{1}{|c|}{} & Hierarchical SFC & 0.05 & $0.7445$ & 0.05 & 0.05 & 0.05\tabularnewline
-\hline
-\end{tabular}
-\par\end{centering}
-\caption{We show the performance of SFC from different settings of hyperparameters for $K$, the candidate class number, and $P$, the sample number for each class.}
-
-\label{tbe:table3}
-\end{table*}
-
-\subsection{Result Analysis}
-
-Table \ref{tbe:table2} presents the results for each experimental data and model set-up in detail.
-The performance of each model is measured in F-score on the fixed test set for each data set.
-The overall performance of SFC system is better than all the competitive single-model baseline models on five experimental datasets.
-This observation gives us a general idea that classification model and similarity model can actually provide each other with complementary information, and combining them together into a joint system can effectively enhance the overall capability based on richer extracted semantic information.
-However the relative performance among all the variants of SFC also seems to depend on some specific charateristic of each data set.
-Therefore, we did the following more detailed analysis from several different aspect.
-
-First, we turn to compare among the four SFC variants.
-We conduct ablation experiments to study the benefits brought by multi-task training by comparing multi-task 2-stage SFC with single-task 2-stage SFC.
-We can see from Table \ref{tbe:table2} that 2-stage SFC with only task 1 (sentence-pair similarity task) degrades by 0.65 percent on average and 2-stage SFC with only task 2 (top-K classification task) degrades by 0.3 percent on average.
-The degradation indicates that training with these 2 tasks together in SFC can effectively help the sentence-pair model extract more knowledge from the limited amount of data.
-Besides, task 2 degrades 0.35 percent less than task 1.
-This observation suggests that task 2 may play a relatively more important role in multi-task learning, which leads us to put larger weight $\alpha_{K}$ to the loss $\mathcal{L}^{K}$ of task 2 when calculating the total loss $\mathcal{L}$.
-Also, we can see that the hierachical SFC steadily outperforms 2-stage SFC on 5 diverse datasets by 2 percents on average.
-This observation supports the idea that the hierachical joint model structure can alleviate the limitation brought by the lack of interaction between similarity model and classification model in 2-stage SFC.
-Therefore, for the following analysis, we will focus on the comparison between hierachical SFC and the other baseline models.
-
-Next, we analyze the overall improvement trend of SFC under various few-shot settings.
-Our main focus is to study chatbot building in common situation during real-world application where only a few sample sentences are available for each class.
-The experimental results for the 3 diverse intent detection datasets under few-shot settings indicate that our proposed SFC can achieve +2.47 percents average improvement over one of the most powerful baseline models, which is RoBERTa-large classification model, on all these few-shot settings.
-Moreover, the improvement in F-score becomes more and more prominent with the decrease of data sample number per class.
-Our hierarchical SFC can achieve +4.97 percents average improvements over RoBERTa-large classification model in the most extreme few-shot setting with only 5 training samples per class.
-
-Then, we begin to compare the general performance of SFC with classification model and similarity model baselines.
-As for the classification model, hierarchical SFC outperforms BERT-large by +9.81 percents, ALBERT-xxlarge by 4 percents, RoBERTa-large by +2.47 percents, RoBERTa-base by +4.52 percents on average F-score for 5 datasets.
-In this way, we can see that RoBERTa is the best pre-trained model for the low-resource text classification task we are studying.
-As for the similarity model, we only choose the strongest pretrained model RoBERTa-large as our baseline, and hierarchical SFC achieves the improvement of 3 percents on average.
-Moreover, hierarchical SFC's result on 2 datasets without few-shot settings, which are ITG and Amazon-670k, are also 1.24 percents and 2.89 percents higher than Roberta-large classification model.
-These improvements illustrate that putting classification model and similarity model at different network layers to cooperate with each other is a successful design of hierarchical network structure for joint model, which enables these two models assist each other for better overall results.
-
-Finally, we analyze the effect brought by different settings of hyperparameters, see Table \ref{tbe:table3}.
-We conduct experiments on 5 different settings of hyperparameters, which are the number of candidate class number $K$ and the number of sentence pairs $P$ for each class, on ITG and Amazon-670K datasets to find the most suitable setting of these 2 hyperparameters.
-We control the total number of sentence pairs sampled for each user query into about the same level of amount(50-60).
-Through analyzing the experimenal results shown in Table \ref{tbe:table3}, we find that the best setting of hyperparameters might be slightly different for datasets of different data size.
-The class label number of ITG and Amazon-670k are similar in our experimental setting, which is around 250.
-However the total amount of data points of ITG is approximately 2 times larger than Amazon-670k.
-Therefore, the setting of $K=5$ and $P=10$ is good enough for ITG since most of the classes contains over 10 data points.
-However, for Amazon-670k, the amount of data sample for each class is scarce, thus, we may need more candidate classes to sample enough effective sentence pairs for sentence-pair model layer of SFC.
-In this way, the setting of $K=10$ and $P=5$ becomes a good choice.
-
-In conclusion, to the best of our knowledge, these results place SFC as the best performing model on 5 diverse experimental datasets for text classification task under low-resource task-specific conversational chatbot scenario.
-
-\section{Conclusion}
-In this work, we successfully proposed SFC, a joint system of classification model and sentence-pair similarity model with multi-task learning, which can effectively alleviate the limitation of classification model and similarity model for low-resource text classification tasks.
-Experimental results illustrate that our proposed system can achieve great improvement on 5 diverse datasets for task-specific chatbot system over several competitive single-task baseline models.
-Furthermore, we especially analyze the excellent performance of SFC when facing the challenge brought by few-shot scenarios, which is quite common in real-world application of chatbot system.
-
-% latest version end
-
-%\section{Attention based neural network}
-
-%\section{Conclusion}
-
-\bibliographystyle{IEEEbib}
-\bibliography{refs}
-
-\end{document}
+In  this  work,  we  successfully proposed SFC, a joint system of classification
+model  and  sentence-pair  similarity  model with multi-task learning, which can
+effectively  alleviate  the  limitation  of  classification model and similarity
+model   for  low-  resource  text  classification  tasks.  Experimental  results
+illustrate  that  our proposed system can achieve great improvement on 5 diverse
+datasets  for  task-specific chatbot system over several competitive single-task
+baseline models. Furthermore, we especially analyze the excellent performance of
+SFC  when  facing  the  challenge  brought by few-shot scenarios, which is quite
+common in real-world application of chatbot system.

### 2020-09-10 chatbot_classification/aaai_2021/experiments.tex
Reorganized.   modified:   paper.tex
  new file:   abstract.tex
  new file:   introduction.tex
  new file:   related_work.tex
  new file:   methodology.tex
  new file:   experiments.tex
  new file:   conclusion.tex

--- 2020-09-10 chatbot_classification/aaai_2021/paper.tex
@@
-\def\year{2021}\relax
-%File: formatting-instructions-latex-2021.tex
-\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
-\usepackage{aaai21}  % DO NOT CHANGE THIS
-\usepackage{times}  % DO NOT CHANGE THIS
-\usepackage{helvet} % DO NOT CHANGE THIS
-\usepackage{courier}  % DO NOT CHANGE THIS
-\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
-\usepackage{graphicx} % DO NOT CHANGE THIS
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{float}
-\usepackage{subfigure}
-\usepackage[switch]{lineno}
-\usepackage{spconf}
-\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-
-\urlstyle{rm} % DO NOT CHANGE THIS
-\def\UrlFont{\rm}  % DO NOT CHANGE THIS
-\frenchspacing  % DO NOT CHANGE THIS
-\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
-\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
-
-\providecommand{\tabularnewline}{\\}
-%% A simple dot to overcome graphicx limitations
-\newcommand{\lyxdot}{.}
-
-\def\x{{\mathbf x}}
-\def\L{{\cal L}}
-
-%\nocopyright
-%PDF Info Is REQUIRED.
-% For /Author, add all authors within the parentheses, separated by commas. No accents or commands.
-% For /Title, add Title in Mixed Case. No accents or commands. Retain the parentheses.
-\pdfinfo{
-  /title (Joint training of classification model and similarity model for
-  low-resource text classification in chatbot)
-  /Author (no author informmation)
-  /TemplateVersion (2021.1)
-}
-
-\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
-%% Because html converters don't know tabularnewline
-\title{     
-  %SFC: Few-Shot Text Classification via Similarity Fused with Classification System
-  Joint Training of Classification and Similarity Models for \\ 
-  Intention Detection in Task-specific Chatbot
-}
-
-\begin{document}
-  \maketitle
-  \linenumbers
-
-  \begin{abstract}
-    Task-specific  chatbot systems have gained many important applications, such
-    as  Siri,  Google home, and customer service systems, etc. One essential technique 
-    underlying these applications  is to detect the real intention behind a user's input.
-    The intention detection,  assuming  only  one  intention  in  a  user's input here, can be
-    regarded  as  a  short  text  classification problem.  In  practice,  the  number  of
-    intentions  can  be hundreds of thousands, as opposed to a few number in the
-    traditional text classification problem; creating enough training data from tons of 
-    raw user logs with miscellaneous information is not trivial, 
-    and generally only 10 to 20 samples per intention are available in  the  early  stage.  
-    Thus,  how  to  train  an  effective short-text classification model with
-    limited labeled data  in such a practical  and important application is critical. In this work, we propose a
-    novel  model, called similarity model fused with classification model (SFC),
-    which  combines  a  classification  model  and  a similarity model, and also
-    borrows  the  power  of  multi-task  training  as well. We conduct extensive
-    experiments  on  4  public  and 1 private datasets. Experimental results
-    show that our new model outperforms very strong baselines (i.e., BERT, RoBERTa and
-    ALBERT based pretrained models) by over 2 percentages in average F1 score.
-
-  \end{abstract}
-
-  \section{Introduction}
-  \label{sec:intro}
-
-  Task-specific  conversational  chatbot  \cite{wen2016network}  has been applied
-  into  many practical products. One typical example is the chatbot that shares the working burden of
-  human  customer  service  agents  responsible  for  customers' questions about
-  certain  products  or services. Another one is the speech-based control in
-  devices  like  intelligent  speakers, such as Siri, Google home, Baidu Xiaodu,
-  and smart home equipments, to name a few. Regardless of whether these conversations belong to
-  single or  multi-round, an essential technique underlying this type of chatbot is to
-  identify  the  real  intention  behind  a  user's  question or reply. 
-  The detected intention  with  its  associated  information  is then mapped into a
-  predefined dialog logic graph, from which a suitable response (e.g., conducting 
-  expected actions, replying texts or accomplishing some operations, etc)  is returned.
-  This  is  the  main  difference  from  a  free chatbot.
-
-  Intention detection in task-specific chatbot  is  a  challenging task due to some inherent properties. First,
-  a customer's  utterance  within  a conversation is usually quite short. Since it
-  does  not  contain  enough  information,  short  texts \cite{song2014short} are
-  thought  to  be  more  ambiguous  compared to long texts such as paragraphs or
-  documents,  posing  a  great challenge \cite{chen2019deep} for classification
-  task   \cite{phan2008learning,yan2009dynamic,hua2015short}.   Second,  in  the
-  initial  stage  of  building  a  chatbot  , it is often rather hard to collect
-  sufficient  labeled  data  to  train  a good model. Because developers have to
-  examine tons of real system logs for typical user's utterances, and then label
-  them  with expected intentions. Therefore, to build a task-specific chatbot with
-  high  performance, it is essential to solve the challenge of short-text
-  classification   \cite{sriram2010short}   problem   under   few-shot   setting
-  \cite{yu2018diverse}.
-
-  Generally  there  are  two  kinds  of  approaches  to  address  this  problem,
-  one is the classification model that directly maps an input into a most likely label, and
-  the other one is the similarity  model  that searches a label whose associated data is most similar to
-  an input.
-
-  The   first  one,  \emph{text  classification},  includes  classic  long  text
-  classification  and  short  text  classification  in  this  scenario.  Besides
-  traditional  machine  learning  models  like  SVM \cite{suykens1999least},  
-  boosting  tree \cite{tu2005probabilistic},  many work
-  \cite{wen2016network}  choose  neural  network  such  as  convolutional neural
-  networks (CNNs) \cite{kim2014convolutional,zhang2015character,conneau2016very}
-  and       long       short       term       memory       networks      (LSTMs)
-  \cite{mousa2017contextual,liu2016recurrent}   to   accomplish   the   task  of
-  extracting  semantic  feature from limited amount of words. Their common model
-  structure  is  adding  a  softmax classifier as the final layer and mapping to
-  labels.  Another  two  interesting lines of work, label-word joint models, and
-  joint  NER  and  classification  are  discussed  in  the related work section.
-  Afterwards,   pre-trained   language   models   on   large  corpus  like  BERT
-  \cite{devlin2018bert}  and  RoBERTa \cite{liu2019roberta} has been proven more
-  powerful  in  solving  many  NLP  tasks  including  short-text  classification
-  \cite{madabushi2020cost}.      Especially      for      few-shot     scenarios
-  \cite{yu2018diverse},     pre-trained     model    based    on    transformers
-  \cite{vaswani2017attention} tends to do more
-  help to reducing the negative effects brought by scarcity of training data.
-
-  The  second  one,  \emph{similarity model} is also called sentence-pair model.
-  Its  motivation  originates  from  the idea of Information Retrieval (IR) based
-  chatbot   \cite{jafarpour2010filter,   leuski2011npceditor}.   Having   a  Q-A
-  (Question-Answer)  pairs dataset and user query Q, the IR based conversational
-  system will look up in the Q-A dataset for the pair (Q', A') that best matches
-  query  Q  through  semantic  analysis  and  returns  A'  as  the  answer  to Q
-  \cite{mnasri2019recent}. In this way, sentence-pair model pre-trained on large
-  corpus  of  semantic  similarity  identification task can be applied for being
-  used  as  a  tool  to  identify  the class with highest semantic similarity to
-  customer's    query.    A    common    model    structure    of    pre-trained 
-  sentence-pair model is based on multiple cross-attention
-  mechanism  \cite{barkan2020scalable}. Due to
-  the   fact   that   many   experiment   results   have   shown   that  RoBERTa
-  \cite{liu2019roberta} is an improved version of BERT \cite{devlin2018bert}, and has achieved amazing
-  results  on  both  text  classification and sentence-pairs semantic similarity
-  tasks, we choose RoBERTa as an important baseline approach in this paper.
-
-  Despite  the  success  of  these two kinds of approaches, they still have some
-  limitations   in   task-specific  chatbot  scenario.  As  for  the  \emph{text
-  classification  model},  it  is  quite hard to use data augmentation method to
-  solve  the  data insufficiency challenge since the it is usually unfeasible to
-  get  large amount of domain-specific data when facing a new task. With respect
-  to  the  \emph{similarity model}, though we can obtain a large amount of data
-  from semantically  duplicate  sentence  pair identification domain for transfer
-  learning  \cite{sun2019fine},  it  is  still  quite  hard  to  perform well on
-  a new task-specific dataset,  since their objective losses are totally different.
-
-  The  above limitation motivates us to propose a joint system that is capable of
-  taking  advantages  from  both  classification model and similarity model. We
-  call  it  SFC,  short  for  similairty model fused with classification Model,
-  shown  in  Fig.  \ref{fig:framework}.  To  better train SFC, we further bring in
-  multi-task   learning   \cite{caruana1993multitask,collobert2008unified, liu2019multi}.  Our
-  basic  idea  came  from  two  stages. In the first stage, we use an auxiliary
-  model  to  select top-K most possible labels for a input. This model can be an
-  elastic search  \cite{divya2013elasticsearch}  or  a  text classification model
-  trained on current task-specific chatbot data. In the second stage, we build a
-  classification  model  whose  main modules are similarity models. Then, this
-  structure  derives two goals to train towards, the classification loss for our
-  application,  and the similarity loss for the main modules. When the two stages
-  are  independently  optimized,  we call \emph{two-stage SFC}. We further find,
-  the  the  quality  of  output  from  the  first  stage  might  limit the final
-  performance  of  system,  since  the  candidate  labels for each user query is
-  always  fixed  in  the  whole  multi-task  training  process. This observation
-  motivates  us  to  further  improve  the  two-stage SFC into a joint training,
-  called  \emph{joint  SFC}. In this way, the sentence pairs associated with the
-  top-K  classes  also  become dynamic, and the text classification model in the
-  first  stage  will also be further optimized to provide better top-K result by
-  the final training loss.
-
-  We summarize our contributions as follow:
-  \begin{enumerate}
-    \item We propose a novel joint system to makes full utilization of
-    the advantages from both text classification model and similarity model.
-
-    \item To  better  train such a system, we bring in multi-task training to obtain
-    reasonable performance.
-
-    \item Experiment  results  from 4 public and 1 private short-text classification
-    datasets,  show  that  our  proposed  SFC joint system can achieve significant
-    and consistent improvements over strong baselines, especially in the low resource settings.
-  \end{enumerate}
-
-  \begin{figure*}[t]
-    \begin{centering}
-      \includegraphics[scale=0.72]{picture/picture4} 
-      \par
-    \end{centering}
-    \caption{
-      \textbf{Network Structure of SFC:} two-stage SFC and joint-SFC are sharing
-      the  same  network  from  stage  1  and  stage 2, with the only difference
-      whether two stages being jointly trained.
-    }
-    \label{fig:framework}
-  \end{figure*}
-
-  \section{Related work}
-
-  Another  common  approach  is  text  classification  neural  network  based on
-  label-word     joint     embedding,    such    as    LEAM \cite{wang2018joint},
-  MTLE \cite{zhang2017multi}   and   EXAM \cite{du2019explicit}.   This   approach
-  involves  label  embedding when constructing the text-sequence representation.
-  Take  LEAM  as  an  example,  the  text classification model is implemented by
-  jointly    embedding    the    word    and    label   in   the   same   latent
-  space \cite{wang2018joint}. Afterwards, the text representation are constructed
-  based  on  text-label  compatibility through attention mechanism. In this way,
-  additional  sources  of  semantic  information  from class labels can be fully
-  leveraged, which is quite helpful especially under few-shot scenario.
-
-  As for \emph{label-word joint
-  embedding  approach},  it  poses  noticeable requirements on label information.
-  However,  in  our  cases,  since  we have large amount of class labels without
-  being well-defined for question answering chatbot, the only thing we can do is
-  to  choose  one  of the user utterance as the class label to represent the key
-  information  of  the  whole class. In this way, the label will become not only
-  prolix  but  also  biased,  which  will  bring  some  negative effect to label
-  embedding.
-
-  Another   line   of  interesting  work  is  the  joint  training  of  sentence
-  classification   and  NER  (todo:  reference).  If  both  the  city  and  date
-  information  are  recognized,  then  they  are good indicators that this query
-  might  be  booking  an  ticket. This work can also be combined in our proposed
-  framework.
-
-  \section{Methodology}
-  In  this section, we describe our proposed system, a similarity model fused with
-  a classification  model (SFC). We propose two approaches to implement this idea,
-  two-stage SFC, and its more compact version joint SFC.
-
-  \subsection{Two-stage SFC}
-
-  Two-stage   SFC  is  composed  with  two  independent stages  in  charge of
-  different  jobs.
-
-  \subsubsection*{
-    Stage 1: classification model for providing top-K candidate class labels
-  } 
-  We  can  use any auxiliary text classification model or tool,
-  such as Term Frequency-Inverse Document Frequency (TF-IDF)retrieval, to
-  provide  top-K  most  related  class  labels. These selected class labels will
-  later  be  used to sample sentence pairs of both positive samples and negative
-  samples  for  stage  2.
-
-  In  this  work,  we  choose pretrained models to fine tune on our data.
-  Due to the excellent performance of RoBERTa in this task, compared to other pretrained
-  models, we use RoBERTa as the encoder of classification model in our setting.
-
-  Given   a   data   point   $x_{i}$  with  class  label  $y_{i}$  from  dataset
-  $\mathcal{D}$, we take the final hidden state $h_{i}$ of the first token [CLS]
-  encoded  by  RoBERTa  as the representation for the whole sequence of $x_{i}$.
-  Then  a linear layer is followed to output probabilistic distribution of class
-  labels,  $softmax(W^Ch_{i}+b^C)=softmax({\Phi}^C_{i})$,  where $W^C$ and $b^C$
-  are  trainable  parameters.  Then, the loss in stage 1 classification model is
-  shown in Equ. \ref{eq:classification_loss},
-
-  \begin{equation}
-    \begin{aligned}
-      \mathcal{L}^{C}&=\frac{1}{N}\sum_{i=1}^{N}-log(\frac{exp(\varPhi_{i,y_{i}}^C)}{\sum_{j=1}^{C}exp(\varPhi_{i,j}^C)}) \\
-      \label{eq:classification_loss}
-    \end{aligned}
-  \end{equation}
-
-  \subsubsection*{
-    Stage 2: sentence-pair similarity model based classification with multi-task
-    learning
-  }
-  We  continue choosing RoBERTa as the main module in this stage that identifies
-  the class label with strongest semantic similarity to the user input sentence.
-
-  Suppose  we have a training dataset $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$ of
-  $N$  data  points,  in  which $x_{i}$ is the user input query and $y_{i}$ is a
-  single  class label from a class label set of $C$ classes in total. We 
-  generate            a sentence            pair            dataset
-  $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$ from $\mathcal{D}$,   where   $(x,   x')_{j}$  is
-  a pair of two history queries \footnote{For simplicity, we use query
-  to denote a user's question or a response.}, and $l_{j}\in\{0, 1\}$ denotes the
-  similarity label that only the ones from the same class label are considered
-  similar. The size of $\mathcal{D'}$  would be up to $O(N^2)$ if no any
-  sampling strategy is used.  This is quite time-consuming  for the  training
-  in stage 2 because $N$ can be several hundreds or thousands even under 
-  few shot setting in task-specific chatbot scenario.
-
-  Therefore,  we  adopt  the idea of adversarial negative sampling strategy from
-  the  work  \cite{bamler2020extreme}.  The  key  idea is to train with negative
-  samples  that  are hard to be distinguished from positive samples. Now suppose
-  we  have  a  user  input query $x_{i}$ and top-K most related class labels set
-  $\mathcal{C'}=\{c'_{1},  \dots,  c'_{K}\}$ provided by auxiliary model or tool
-  in  stage  1, where $K$ is a hyperparameter to control candidate class number,
-  we  apply  the  adversarial  negative sampling strategy into our sentence pair
-  sampling process by the following two steps:
-
-  The  first step is \emph{positive sentence pair sampling}. During the training
-  process,  we  first make sure the ground truth class label $y_{i}$ for $x_{i}$
-  is  within  the  candidate  class  label  set  $\mathcal{C'}$. If $y_{i}\notin
-  \mathcal{C'}$,  we  manually  add  $y_{i}$  into  $\mathcal{C'}$  by replacing
-  $c'_{K}$  with  $y_{i}$, since $c'_{K}$ is the least promising candidate label
-  according  to  the  auxiliary  model  in stage 1. Afterwards, we will randomly
-  sample  $P$ sentences $\{x'_{1}, \dots, x'_{P}\}$ with the same class label as
-  $y_{i}$  from  dataset  $\mathcal{D}$  to  form the set of sentence pairs with
-  positive  label  $\mathcal{P'}_{i}=\{[(x_{i},  x'_{1}),  1],  \dots,  [(x_{i},
-  x'_{P}),  1]\}$,  where $P$ is also a hyperparameter set to control the number
-  of sentences we should sample from each class.
-
-  \begin{table*}
-    \begin{centering}
-      \scalebox{0.9}{
-        \begin{tabular}{|c|c|c|c|c|c|}
-          \hline 
-          \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} &
-          \textbf{\#Training Samples} & \textbf{\#Samples/Class} & \textbf{Experimental Settings}\tabularnewline
-          \hline 
-          ITG & FAQ chatbot & 228 & 3938 & 17 & 3-fold\tabularnewline
-          \hline 
-          Amazon-670k & Product review & 250 & 1942 & 8 & 3-fold\tabularnewline
-          \hline 
-          HWU64 & intention detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
-          \hline 
-          CLINC150 & intention detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
-          \hline 
-          BANKING77 & intention detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
-          \hline 
-        \end{tabular}
-      }
-      \par
-    \end{centering}
-    \caption{Statistics for all datasets and few shot settings.}
-
-    \label{tbe:dataset statistic}
-  \end{table*}
-
-  The  second  step  is  \emph{negative sentence pair sampling}: As for negative
-  sentence  pairs,  we will also randomly sample $P$ sentences for each class in
-  the negative candidate class label set $\mathcal{C'}\backslash \{y_{i}\}$. The
-  class  labels  in  $\mathcal{C'}\backslash  \{y_{i}\}$  are  the  set  of most
-  confusing  class  labels comparing to the ground truth ${y_{i}}$, so we assume
-  that  the  sentence  pairs  with  negative  label  grouped by user input query
-  $x_{i}$  and sentences with class labels in $\mathcal{C'}\backslash \{y_{i}\}$
-  are  strong  adversarial  negative  samples for sentence-pair similarity model
-  that  can  help  enhance  the training speed and performance. According to the
-  same  method  as  positive  sentence  pair  sampling, we can obtain the set of
-  sentence  pairs  with  negative label as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{1}),
-  0], ..., [(x_{i}, x'_{P\cdot K}), 0]\}$
-
-  In  this way, we generate the sentence pair dataset $\mathcal{D'}$ for stage 2
-  based  on  the  top-K  class  label  set $\mathcal{C'}$ provided by stage 1 as
-  $\mathcal{D'}=\{\mathcal{P'}_{i}\cup  \mathcal{N'}_{i}\}_{i=1}^{N}$,  in which
-  we have $M=N\cdot K\cdot P$ data points of sentence pairs in total.
-
-  Before starting to fine-tune our sentence-pair model on task-specific dataset,
-  we  first  fine-tune  RoBERTa  on  Quora  dataset  \cite{iyer2017first}, which
-  contains  404,290  potential  duplicate question pairs, for transfer learning.
-  This  is  also  the  merit of similarity based model, as labeled task-specific
-  classification  data  is  hard  to  acquire,  yet  general sentence pairs with
-  similar semantics can be much easier to acquire.
-
-  \subsubsection*{Multi-task based training}
-  We   continue  to  do  multi-task  training  on  sentence-pair  dataset
-  $\mathcal{D'}$ sampled from the top-K candidate class labels provided by stage
-  1. In stage 2, we have two tasks tuning our system.
-
-  The first task is \emph{regular sentence-pair similarity task}.
-  For  sentence  pair semantic similarity task, given a data point $(x, x')_{i}$
-  with       similarity       label       $l_{i}$       from       data      set
-  $\mathcal{D'}=\{[(x,x')_{i},l_{i}]\}_{i=1}^{M}$,   Roberta   takes  the  final
-  hidden  state  $h_{i}$  of the first token [CLS] as the representation for the
-  sequence of packed sentence pair $(x, x')_{i}$. Let's suppose we have a linear
-  layer  as  ${\Phi}^S_{i}=W^Sh_{i}+b^S$,  where  $W^S$  and $b^S$ are trainable
-  parameters,  and  the probability score for $(x, x')_{i}$ can be calculated as
-  $p^S_{i}=softmax({\Phi}^S_{i})$.
-
-  Due  to  the  fact that sentence pairs within the same class is much fewer than
-  that from  different  classes,  the  dataset  $\mathcal{D'}$  is
-  quite imbalanced.  Therefore, we will accommodate a weight variable $w^S = [K-1, 1]$
-  to  the  loss  to eliminate the bias brought by data imbalance, shown in Equ.
-  \ref{eq:similarity_loss}.
-
-  \begin{equation}
-    \begin{aligned}
-      \mathcal{L}^{S}&=\frac{1}{M}\sum_{i=1}^{M}-w^S_{l_i}\cdot log(\frac{exp(\varPhi_{i,l_{i}}^S)}{\sum_{j=0}^{1}exp(\varPhi_{i,j}^S)}) \\
-      \label{eq:similarity_loss}
-    \end{aligned}
-  \end{equation}
-
-  The  second  task  is  \emph{classification  on  top-K classes}. As minimizing
-  similarity  loss  is  not  our  final goal in the intention classification, we
-  bring  back  classification  loss again. In this task, the network is based on
-  sentence  pair  similarity  modules.  The  only  difference  is  that we add a
-  task-specific  average  pooling  layer,  shown  in Fig. \ref{fig:framework} to
-  accomplish the classification task based on sentence-pair model.
-
-  We  already  know  that the size of ${\Phi}^S$ in task 1 is $M\times 2=(N\cdot
-  K\cdot  P)\times  2$, where $N$ is the total number of data points in original
-  training  data $\mathcal{D}$, $K$ is a hyperparameter that controls the number
-  of   candidate   class  labels  provided  by  stage  1,  and  $P$  is  also  a
-  hyperparameter that controls the number of sentences we should randomly sample
-  from each candidate class labels. Now, for the average pooling layer, we first
-  reshape  ${\Phi}^S$  into  the  size  of $N\times K\times P\times 2$, and then
-  split  it  into  ${\Phi}^{K,pos}$  and ${\Phi}^{K,neg}$, and both of them will
-  have  the  size  of  $N\times  K\times  P$.  In this way, ${\Phi}^{K,pos}$ can
-  represent  the  level  of  similarity  for each sentence pair, and in the mean
-  time,  ${\Phi}^{K,neg}$  can  represent  the  level  of dissimilarity for each
-  sentence  pair. Then, we can do average pooling for each candidate class among
-  the  top-K  classes  as  shown  in  Equ.  \ref{eq:average  pooling}.
-
-  \begin{align}
-    {\xi}_{i,j}^{K,pos} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,pos} \ \ \ \ \ \ \ 
-    {\xi}_{i,j}^{K,neg} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,neg}
-    \label{eq:average pooling}
-  \end{align}
-
-  With  the  average pooling result ${\xi}^{K,pos}$ and ${\xi}^{K,neg}$, we also
-  generate   a   top-K   class   label   $l^{K}_i\in   [1,\dots,K]$   for   each
-  ${\xi}^{K,pos}_{i}$ and ${\xi}^{K,neg}_{i}$. The loss for top-K classification
-  task is shown in Equ. \ref{eq:top-k_classification_loss}. In Equ. \ref{eq: pos
-  top-k   loss}   and   Equ.   \ref{eq:   neg   top-k   loss},  the  first  term
-  $\xi_{i,l^{K}_{i}}^{K,pos}$  and  $\xi_{i,l^{K}_{i}}^{K,neg}$  encourage  high
-  level  of  similarity  and  low  level  of dissimilarity for prediction of the
-  correct label $l^{K}_i$ within the top-K candidate classes.
-
-  \begin{align}
-    \mathcal{L}^{K} = \frac{1}{N}\sum_{i=1}^{N}(\mathcal{L}^{K,pos}_{i} - \mathcal{L}^{K,neg}_{i})
-    \label{eq:top-k_classification_loss}
-  \end{align}
-  where
-
-  \begin{equation}
-    \begin{aligned}
-      \mathcal{L}^{K,pos}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,pos})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,pos})})
-      \label{eq: pos top-k loss}
-    \end{aligned}
-  \end{equation}
-
-  \begin{equation}
-    \begin{aligned}
-      \mathcal{L}^{K,neg}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,neg})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,neg})}) \\
-      \label{eq: neg top-k loss}
-    \end{aligned}
-  \end{equation}
-
-  Finally,  the  overall  loss  function for multi-task learning in stage 2 is
-  shown in Equ. \ref{eq:two-stage_SFC_loss}. The training objective of stage 2 is
-  to  minimize  the  weighted  sum  of task-specific losses. Here $\alpha_S$ and
-  $\alpha_K$  are  weights  of  task  1  and  task  2  respectively.
-
-  \begin{align}
-    \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K
-    \label{eq:two-stage_SFC_loss}
-  \end{align}
-
-  \begin{table*}
-    \begin{centering}
-      \scalebox{0.55}{
-        \begin{tabular}{|c|cccccc|cccccc|cccccc|c|c|}
-          \hline 
-          \multicolumn{1}{|c|}{\multirow{2}*{\textbf{Models}} }& \multicolumn{6}{c|}{\textbf{CLINC150}}& \multicolumn{6}{c|}{\textbf{BANKING77}}& \multicolumn{6}{c|}{\textbf{HWU64}}& \ \ \ \textbf{ITG} \ \ \ & \textbf{Amazon-670k}\tabularnewline
-          \cline{2-21}
-          \multicolumn{1}{|c|}{} & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$
-          & $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & $\textbf{5}$ &
-          $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{30}$ &
-          $\textbf{50}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ &
-          $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & \textbf{3-fold} &
-          \textbf{3-fold}\tabularnewline
-          \hline
-          TextCNN & \multirow{2}*{$0.5318$} & \multirow{2}*{$0.6963$} & \multirow{2}*{$0.7609$} & \multirow{2}*{$0.8142$} & \multirow{2}*{$0.8526$} & \multirow{2}*{$0.8867$} & \multirow{2}*{$0.4408$} & \multirow{2}*{$0.6436$} & \multirow{2}*{$0.7366$} & \multirow{2}*{$0.7918$} & \multirow{2}*{$0.8228$} & \multirow{2}*{$0.8619$} & \multirow{2}*{$0.3112$} & \multirow{2}*{$0.4007$} & \multirow{2}*{$0.4823$} & \multirow{2}*{$0.5272$} & \multirow{2}*{$0.5782$} & \multirow{2}*{$0.6262$} & \multirow{2}*{$0.6624$} & \multirow{2}*{$0.4401$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          LEAM & \multirow{2}*{$0.7514$} & \multirow{2}*{$0.8203$} & \multirow{2}*{$0.8612$} & \multirow{2}*{$0.8802$} & \multirow{2}*{$0.9010$} & \multirow{2}*{$0.9180$} & \multirow{2}*{$0.5422$} & \multirow{2}*{$0.7812$} & \multirow{2}*{$0.8129$} & \multirow{2}*{$0.8280$} & \multirow{2}*{$0.8610$} & \multirow{2}*{$0.8727$} & \multirow{2}*{$0.4545$} & \multirow{2}*{$0.5554$} & \multirow{2}*{$0.5936$} & \multirow{2}*{$0.6599$} & \multirow{2}*{$0.6855$} & \multirow{2}*{$0.7046$} & \multirow{2}*{$0.7086$} & \multirow{2}*{$0.6091$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-          BERT-large & \multirow{2}*{$0.8080$} & \multirow{2}*{$0.8904$} & \multirow{2}*{$0.9265$} & \multirow{2}*{$0.9334$} & \multirow{2}*{$0.9497$} & \multirow{2}*{$0.9595$} & \multirow{2}*{$0.5780$} & \multirow{2}*{$0.8004$} & \multirow{2}*{$0.8518$} & \multirow{2}*{$0.8827$} & \multirow{2}*{$0.8858$} & \multirow{2}*{$0.8982$} & \multirow{2}*{$0.4711$} & \multirow{2}*{$0.5963$} & \multirow{2}*{$0.6342$} & \multirow{2}*{$0.7010$} & \multirow{2}*{$0.7117$} & \multirow{2}*{$0.7424$} & \multirow{2}*{$0.7485$} & \multirow{2}*{$0.6658$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          ALBERT-xxlarge & \multirow{2}*{$0.8497$} & \multirow{2}*{$0.9008$} & \multirow{2}*{$0.9296$} & \multirow{2}*{$0.9297$} & \multirow{2}*{$0.9466$} & \multirow{2}*{$0.9578$} & \multirow{2}*{$0.5549$} & \multirow{2}*{$0.7981$} & \multirow{2}*{$0.8231$} & \multirow{2}*{$0.8530$} & \multirow{2}*{$0.8571$} & \multirow{2}*{$0.9096$} & \multirow{2}*{$0.4879$} & \multirow{2}*{$0.6116$} & \multirow{2}*{$0.6135$} & \multirow{2}*{$0.6996$} & \multirow{2}*{$0.7094$} & \multirow{2}*{$0.7376$} & \multirow{2}*{$0.7253$} & \multirow{2}*{$0.6893$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          RoBERTa-base & \multirow{2}*{$0.8732$} & \multirow{2}*{$0.9254$} & \multirow{2}*{$0.9363$} & \multirow{2}*{$0.9482$} & \multirow{2}*{$0.9558$} & \multirow{2}*{$0.9637$} & \multirow{2}*{$0.7305$} & \multirow{2}*{$0.8654$} & \multirow{2}*{$0.8808$} & \multirow{2}*{$0.9080$} & \multirow{2}*{$0.9061$} & \multirow{2}*{$0.9293$} & \multirow{2}*{$0.5831$} & \multirow{2}*{$0.6790$} & \multirow{2}*{$0.7064$} & \multirow{2}*{$0.7100$} & \multirow{2}*{$0.7320$} & \multirow{2}*{$0.7472$} & \multirow{2}*{$0.7734$} & \multirow{2}*{$0.6708$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          RoBERTa-large & \multirow{2}*{$\textbf{0.8974}$} &
-          \multirow{2}*{$\textbf{0.9372}$} & \multirow{2}*{$\textbf{0.9508}$} &
-          \multirow{2}*{$\textbf{0.9584}$} & \multirow{2}*{$\textbf{0.9621}$} & 
-          \multirow{2}*{$\textbf{0.9733}$} & \multirow{2}*{$\textbf{0.7690}$} & 
-          \multirow{2}*{$\textbf{0.8728}$} & \multirow{2}*{$\textbf{0.8966}$} & 
-          \multirow{2}*{$\textbf{0.9099}$} & \multirow{2}*{$\textbf{0.9227}$} & 
-          \multirow{2}*{$\textbf{0.9313}$} & \multirow{2}*{$\textbf{0.6044}$} & 
-          \multirow{2}*{$\textbf{0.7002}$} & \multirow{2}*{$\textbf{0.7129}$} & 
-          \multirow{2}*{$\textbf{0.7436}$} & \multirow{2}*{$\textbf{0.7493}$} & 
-          \multirow{2}*{$\textbf{0.7678}$} & \multirow{2}*{$\textbf{0.7990}$} & 
-          \multirow{2}*{$\textbf{0.7156}$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-          RoBERTa-large & \multirow{2}*{$0.8266$} & \multirow{2}*{$0.8861$} & \multirow{2}*{$0.9023$} & \multirow{2}*{$0.9084$} & \multirow{2}*{$0.9090$} & \multirow{2}*{$0.9407$} & \multirow{2}*{$0.757$} & \multirow{2}*{$0.8476$} & \multirow{2}*{$0.8614$} & \multirow{2}*{$0.8743$} & \multirow{2}*{$0.8749$} & \multirow{2}*{$0.8980$} & \multirow{2}*{$0.5425$} & \multirow{2}*{$0.6164$} & \multirow{2}*{$0.6503$} & \multirow{2}*{$0.6729$} & \multirow{2}*{$0.6947$} & \multirow{2}*{$0.7231$} & \multirow{2}*{$0.7418$} & \multirow{2}*{$0.6362$}\tabularnewline
-          (similarity) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-          2-stage SFC & \multirow{2}*{$0.8979$} & \multirow{2}*{$0.9457$} & \multirow{2}*{$0.9517$} & \multirow{2}*{$0.9591$} & \multirow{2}*{$0.9610$} & \multirow{2}*{$0.9664$} & \multirow{2}*{$0.7975$} & \multirow{2}*{$0.8818$} & \multirow{2}*{$0.8962$} & \multirow{2}*{$0.9109$} & \multirow{2}*{$0.9187$} & \multirow{2}*{$0.9198$} & \multirow{2}*{$0.6477$} & \multirow{2}*{$0.7055$} & \multirow{2}*{$0.7200$} & \multirow{2}*{$0.7232$} & \multirow{2}*{$0.7484$} & \multirow{2}*{$0.7653$} & \multirow{2}*{$0.7972$} & \multirow{2}*{$0.7189$}\tabularnewline
-          (task1) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          2-stage SFC & \multirow{2}*{$0.9162$} & \multirow{2}*{$0.9424$} & \multirow{2}*{$0.9530$} & \multirow{2}*{$0.9617$} & \multirow{2}*{$0.9633$} & \multirow{2}*{$0.9690$} & \multirow{2}*{$0.7997$} & \multirow{2}*{$0.8823$} & \multirow{2}*{$0.8945$} & \multirow{2}*{$0.9123$} & \multirow{2}*{$0.9236$} & \multirow{2}*{$0.9317$} & \multirow{2}*{$0.6498$} & \multirow{2}*{$0.6980$} & \multirow{2}*{$0.7202$} & \multirow{2}*{$0.7358$} & \multirow{2}*{$0.7498$} & \multirow{2}*{$0.7657$} & \multirow{2}*{$0.8020$} & \multirow{2}*{$0.7311$}\tabularnewline
-          (task2) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          2-stage SFC & \multirow{2}*{$0.9167$} & \multirow{2}*{$0.9456$} & \multirow{2}*{$0.9571$} & \multirow{2}*{$0.9638$} & \multirow{2}*{$0.9658$} & \multirow{2}*{$0.9753$} & \multirow{2}*{$0.8135$} & \multirow{2}*{$0.8854$} & \multirow{2}*{$0.8931$} & \multirow{2}*{$0.9192$} & \multirow{2}*{$0.9257$} & \multirow{2}*{$0.9339$} & \multirow{2}*{$0.6525$} & \multirow{2}*{$0.7092$} & \multirow{2}*{$0.7168$} & \multirow{2}*{$0.7476$} & \multirow{2}*{$0.7519$} & \multirow{2}*{$0.7696$} & \multirow{2}*{$\textbf{0.8124}$} & \multirow{2}*{$0.7364$}\tabularnewline
-          (task1 + task2) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-          \multirow{2}*{Joint SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.9669}$} & \multirow{2}*{$\textbf{0.9712}$} & \multirow{2}*{$\textbf{0.9821}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.9323}$} & \multirow{2}*{$\textbf{0.9463}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$\textbf{0.7593}$} & \multirow{2}*{$\textbf{0.7772}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline
-          & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-        \end{tabular}
-      }
-      \par
-    \end{centering}
-    \caption{
-      F1 scores  on  five  task-specific  datasets text classification in chatbot
-      under low resource. For ITG, we keep the full dataset. For Amazon-670k, we
-      randomly  sampled  250  classes  with  training sample numbers within 5-15
-      samples  per  class.  For  CLINC150,  BANKING77,  HWU64, we set up various
-      few-shot  settings  (5/10/15/20/30/50 samples per class) while keeping the
-      test  set to be fixed. The highest scores among all the baseline models and SFC variants for each data setting are both marked
-      in bold.
-    }
-    \label{tbe:table2}
-  \end{table*}
-
-  \subsection{Joint SFC}
-  In  two-stage  SFC,  Stage  1  and  stage 2 are separate that there is no deep
-  interaction  with each other during training. In this case, the performance of
-  stage  1  may  limit  the potential of stage 2; meanwhile, stage 2 also cannot
-  give  training feedback back to stage 1 for fine-tuning. Therefore, to further
-  improve  the  overall performance of SFC, we proposed a joint model structure,
-  shown in Fig. \ref{fig:framework}.
-
-  In  joint  SFC,  classification  model is being placed in lower layer level to
-  dynamically  provide  top-K  candidate  class  labels  for  the  sentence-pair
-  similarity  model  placed in higher layer level through a top-K pooling layer.
-  In  this way, classification model and similarity model can be merged into one
-  single  joint-model  for  multi-task training with sentence pairs sampled from
-  varying  candidate  class  labels,  thus  avoiding the limitation brought by 2
-  separate stage structure.
-
-  There  are 3 tasks in total during the training process of joint SFC, shown in
-  Fig. \ref{fig:framework}, and the overall loss is also the weighted sum of all
-  the   task-specific  losses,  shown  in  Equ.  \ref{eq:joint_SFC_loss}.  Here,
-  $\alpha_S$,  $\alpha_K$  and  $\alpha_C$  represent  the  weights  for  task 1
-  sentence-pair  similarity  in  Equ.  \ref{eq:similarity_loss},  task  2  top-K
-  classification  in Equ. \ref{eq:top-k_classification_loss}, and task 3 general
-  single       sentence       classification      respectively      in      Equ.
-  \ref{eq:classification_loss}.
-
-  \begin{align}
-    \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K + \alpha_C \mathcal{L}^C
-    \label{eq:joint_SFC_loss}
-  \end{align}
-
 \section{Experiments}
@@
 task-specific conversational chatbot scenario.
-
-  \bibliographystyle{aaai21}
-  \bibliography{refs}
-
-\end{document}

### 2020-09-10 chatbot_classification/aaai_2021/introduction.tex
Reorganized.   modified:   paper.tex
  new file:   abstract.tex
  new file:   introduction.tex
  new file:   related_work.tex
  new file:   methodology.tex
  new file:   experiments.tex
  new file:   conclusion.tex

--- 2020-09-10 chatbot_classification/aaai_2021/paper.tex
@@
-\def\year{2021}\relax
-%File: formatting-instructions-latex-2021.tex
-\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
-\usepackage{aaai21}  % DO NOT CHANGE THIS
-\usepackage{times}  % DO NOT CHANGE THIS
-\usepackage{helvet} % DO NOT CHANGE THIS
-\usepackage{courier}  % DO NOT CHANGE THIS
-\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
-\usepackage{graphicx} % DO NOT CHANGE THIS
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{float}
-\usepackage{subfigure}
-\usepackage[switch]{lineno}
-\usepackage{spconf}
-\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-
-\urlstyle{rm} % DO NOT CHANGE THIS
-\def\UrlFont{\rm}  % DO NOT CHANGE THIS
-\frenchspacing  % DO NOT CHANGE THIS
-\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
-\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
-
-\providecommand{\tabularnewline}{\\}
-%% A simple dot to overcome graphicx limitations
-\newcommand{\lyxdot}{.}
-
-\def\x{{\mathbf x}}
-\def\L{{\cal L}}
-
-%\nocopyright
-%PDF Info Is REQUIRED.
-% For /Author, add all authors within the parentheses, separated by commas. No accents or commands.
-% For /Title, add Title in Mixed Case. No accents or commands. Retain the parentheses.
-\pdfinfo{
-  /title (Joint training of classification model and similarity model for
-  low-resource text classification in chatbot)
-  /Author (no author informmation)
-  /TemplateVersion (2021.1)
-}
-
-\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
-%% Because html converters don't know tabularnewline
-\title{     
-  %SFC: Few-Shot Text Classification via Similarity Fused with Classification System
-  Joint Training of Classification and Similarity Models for \\ 
-  Intention Detection in Task-specific Chatbot
-}
-
-\begin{document}
-  \maketitle
-  \linenumbers
-
-  \begin{abstract}
-    Task-specific  chatbot systems have gained many important applications, such
-    as  Siri,  Google home, and customer service systems, etc. One essential technique 
-    underlying these applications  is to detect the real intention behind a user's input.
-    The intention detection,  assuming  only  one  intention  in  a  user's input here, can be
-    regarded  as  a  short  text  classification problem.  In  practice,  the  number  of
-    intentions  can  be hundreds of thousands, as opposed to a few number in the
-    traditional text classification problem; creating enough training data from tons of 
-    raw user logs with miscellaneous information is not trivial, 
-    and generally only 10 to 20 samples per intention are available in  the  early  stage.  
-    Thus,  how  to  train  an  effective short-text classification model with
-    limited labeled data  in such a practical  and important application is critical. In this work, we propose a
-    novel  model, called similarity model fused with classification model (SFC),
-    which  combines  a  classification  model  and  a similarity model, and also
-    borrows  the  power  of  multi-task  training  as well. We conduct extensive
-    experiments  on  4  public  and 1 private datasets. Experimental results
-    show that our new model outperforms very strong baselines (i.e., BERT, RoBERTa and
-    ALBERT based pretrained models) by over 2 percentages in average F1 score.
-
-  \end{abstract}
-
 \section{Introduction}
@@
 The  above  limitation motivates us to propose a joint system that is capable of
-  taking  advantages  from  both  classification model and similarity model. We
-  call  it  SFC,  short  for  similairty model fused with classification Model,
-  shown  in  Fig.  \ref{fig:framework}.  To  better train SFC, we further bring in
-  multi-task   learning   \cite{caruana1993multitask,collobert2008unified, liu2019multi}.  Our
-  basic  idea  came  from  two  stages. In the first stage, we use an auxiliary
-  model  to  select top-K most possible labels for a input. This model can be an
-  elastic search  \cite{divya2013elasticsearch}  or  a  text classification model
-  trained on current task-specific chatbot data. In the second stage, we build a
+taking  advantages  from both classification model and similarity model. We call
+it  SFC,  short  for  similairty model fused with classification Model, shown in
+Fig.  \ref{fig:framework}.  To  better train SFC, we further bring in multi-task
+learning   \cite{caruana1993multitask,collobert2008unified,  liu2019multi}.  Our
+basic  idea  came from two stages. In the first stage, we use an auxiliary model
+to  select  top-K most possible labels for a input. This model can be an elastic
+search  \cite{divya2013elasticsearch}  or a text classification model trained on
+current   task-specific   chatbot   data.  In  the  second  stage,  we  build  a
 classification  model  whose  main  modules  are  similarity  models. Then, this
@@
 application,  and  the similarity loss for the main modules. When the two stages
-  are  independently  optimized,  we call \emph{two-stage SFC}. We further find,
-  the  the  quality  of  output  from  the  first  stage  might  limit the final
-  performance  of  system,  since  the  candidate  labels for each user query is
-  always  fixed  in  the  whole  multi-task  training  process. This observation
-  motivates  us  to  further  improve  the  two-stage SFC into a joint training,
-  called  \emph{joint  SFC}. In this way, the sentence pairs associated with the
-  top-K  classes  also  become dynamic, and the text classification model in the
-  first  stage  will also be further optimized to provide better top-K result by
-  the final training loss.
+are  independently optimized, we call \emph{two-stage SFC}. We further find, the
+the  quality of output from the first stage might limit the final performance of
+system,  since  the  candidate labels for each user query is always fixed in the
+whole  multi-task  training  process.  This  observation motivates us to further
+improve  the  two-stage  SFC  into a joint training, called \emph{joint SFC}. In
+this  way,  the  sentence  pairs  associated  with the top-K classes also become
+dynamic,  and  the  text  classification  model  in the first stage will also be
+further optimized to provide better top-K result by the final training loss.
 
@@
 \end{figure*}
-
-  \section{Related work}
-
-  Another  common  approach  is  text  classification  neural  network  based on
-  label-word     joint     embedding,    such    as    LEAM \cite{wang2018joint},
-  MTLE \cite{zhang2017multi}   and   EXAM \cite{du2019explicit}.   This   approach
-  involves  label  embedding when constructing the text-sequence representation.
-  Take  LEAM  as  an  example,  the  text classification model is implemented by
-  jointly    embedding    the    word    and    label   in   the   same   latent
-  space \cite{wang2018joint}. Afterwards, the text representation are constructed
-  based  on  text-label  compatibility through attention mechanism. In this way,
-  additional  sources  of  semantic  information  from class labels can be fully
-  leveraged, which is quite helpful especially under few-shot scenario.
-
-  As for \emph{label-word joint
-  embedding  approach},  it  poses  noticeable requirements on label information.
-  However,  in  our  cases,  since  we have large amount of class labels without
-  being well-defined for question answering chatbot, the only thing we can do is
-  to  choose  one  of the user utterance as the class label to represent the key
-  information  of  the  whole class. In this way, the label will become not only
-  prolix  but  also  biased,  which  will  bring  some  negative effect to label
-  embedding.
-
-  Another   line   of  interesting  work  is  the  joint  training  of  sentence
-  classification   and  NER  (todo:  reference).  If  both  the  city  and  date
-  information  are  recognized,  then  they  are good indicators that this query
-  might  be  booking  an  ticket. This work can also be combined in our proposed
-  framework.
-
-  \section{Methodology}
-  In  this section, we describe our proposed system, a similarity model fused with
-  a classification  model (SFC). We propose two approaches to implement this idea,
-  two-stage SFC, and its more compact version joint SFC.
-
-  \subsection{Two-stage SFC}
-
-  Two-stage   SFC  is  composed  with  two  independent stages  in  charge of
-  different  jobs.
-
-  \subsubsection*{
-    Stage 1: classification model for providing top-K candidate class labels
-  } 
-  We  can  use any auxiliary text classification model or tool,
-  such as Term Frequency-Inverse Document Frequency (TF-IDF)retrieval, to
-  provide  top-K  most  related  class  labels. These selected class labels will
-  later  be  used to sample sentence pairs of both positive samples and negative
-  samples  for  stage  2.
-
-  In  this  work,  we  choose pretrained models to fine tune on our data.
-  Due to the excellent performance of RoBERTa in this task, compared to other pretrained
-  models, we use RoBERTa as the encoder of classification model in our setting.
-
-  Given   a   data   point   $x_{i}$  with  class  label  $y_{i}$  from  dataset
-  $\mathcal{D}$, we take the final hidden state $h_{i}$ of the first token [CLS]
-  encoded  by  RoBERTa  as the representation for the whole sequence of $x_{i}$.
-  Then  a linear layer is followed to output probabilistic distribution of class
-  labels,  $softmax(W^Ch_{i}+b^C)=softmax({\Phi}^C_{i})$,  where $W^C$ and $b^C$
-  are  trainable  parameters.  Then, the loss in stage 1 classification model is
-  shown in Equ. \ref{eq:classification_loss},
-
-  \begin{equation}
-    \begin{aligned}
-      \mathcal{L}^{C}&=\frac{1}{N}\sum_{i=1}^{N}-log(\frac{exp(\varPhi_{i,y_{i}}^C)}{\sum_{j=1}^{C}exp(\varPhi_{i,j}^C)}) \\
-      \label{eq:classification_loss}
-    \end{aligned}
-  \end{equation}
-
-  \subsubsection*{
-    Stage 2: sentence-pair similarity model based classification with multi-task
-    learning
-  }
-  We  continue choosing RoBERTa as the main module in this stage that identifies
-  the class label with strongest semantic similarity to the user input sentence.
-
-  Suppose  we have a training dataset $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$ of
-  $N$  data  points,  in  which $x_{i}$ is the user input query and $y_{i}$ is a
-  single  class label from a class label set of $C$ classes in total. We 
-  generate            a sentence            pair            dataset
-  $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$ from $\mathcal{D}$,   where   $(x,   x')_{j}$  is
-  a pair of two history queries \footnote{For simplicity, we use query
-  to denote a user's question or a response.}, and $l_{j}\in\{0, 1\}$ denotes the
-  similarity label that only the ones from the same class label are considered
-  similar. The size of $\mathcal{D'}$  would be up to $O(N^2)$ if no any
-  sampling strategy is used.  This is quite time-consuming  for the  training
-  in stage 2 because $N$ can be several hundreds or thousands even under 
-  few shot setting in task-specific chatbot scenario.
-
-  Therefore,  we  adopt  the idea of adversarial negative sampling strategy from
-  the  work  \cite{bamler2020extreme}.  The  key  idea is to train with negative
-  samples  that  are hard to be distinguished from positive samples. Now suppose
-  we  have  a  user  input query $x_{i}$ and top-K most related class labels set
-  $\mathcal{C'}=\{c'_{1},  \dots,  c'_{K}\}$ provided by auxiliary model or tool
-  in  stage  1, where $K$ is a hyperparameter to control candidate class number,
-  we  apply  the  adversarial  negative sampling strategy into our sentence pair
-  sampling process by the following two steps:
-
-  The  first step is \emph{positive sentence pair sampling}. During the training
-  process,  we  first make sure the ground truth class label $y_{i}$ for $x_{i}$
-  is  within  the  candidate  class  label  set  $\mathcal{C'}$. If $y_{i}\notin
-  \mathcal{C'}$,  we  manually  add  $y_{i}$  into  $\mathcal{C'}$  by replacing
-  $c'_{K}$  with  $y_{i}$, since $c'_{K}$ is the least promising candidate label
-  according  to  the  auxiliary  model  in stage 1. Afterwards, we will randomly
-  sample  $P$ sentences $\{x'_{1}, \dots, x'_{P}\}$ with the same class label as
-  $y_{i}$  from  dataset  $\mathcal{D}$  to  form the set of sentence pairs with
-  positive  label  $\mathcal{P'}_{i}=\{[(x_{i},  x'_{1}),  1],  \dots,  [(x_{i},
-  x'_{P}),  1]\}$,  where $P$ is also a hyperparameter set to control the number
-  of sentences we should sample from each class.
-
-  \begin{table*}
-    \begin{centering}
-      \scalebox{0.9}{
-        \begin{tabular}{|c|c|c|c|c|c|}
-          \hline 
-          \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} &
-          \textbf{\#Training Samples} & \textbf{\#Samples/Class} & \textbf{Experimental Settings}\tabularnewline
-          \hline 
-          ITG & FAQ chatbot & 228 & 3938 & 17 & 3-fold\tabularnewline
-          \hline 
-          Amazon-670k & Product review & 250 & 1942 & 8 & 3-fold\tabularnewline
-          \hline 
-          HWU64 & intention detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
-          \hline 
-          CLINC150 & intention detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
-          \hline 
-          BANKING77 & intention detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
-          \hline 
-        \end{tabular}
-      }
-      \par
-    \end{centering}
-    \caption{Statistics for all datasets and few shot settings.}
-
-    \label{tbe:dataset statistic}
-  \end{table*}
-
-  The  second  step  is  \emph{negative sentence pair sampling}: As for negative
-  sentence  pairs,  we will also randomly sample $P$ sentences for each class in
-  the negative candidate class label set $\mathcal{C'}\backslash \{y_{i}\}$. The
-  class  labels  in  $\mathcal{C'}\backslash  \{y_{i}\}$  are  the  set  of most
-  confusing  class  labels comparing to the ground truth ${y_{i}}$, so we assume
-  that  the  sentence  pairs  with  negative  label  grouped by user input query
-  $x_{i}$  and sentences with class labels in $\mathcal{C'}\backslash \{y_{i}\}$
-  are  strong  adversarial  negative  samples for sentence-pair similarity model
-  that  can  help  enhance  the training speed and performance. According to the
-  same  method  as  positive  sentence  pair  sampling, we can obtain the set of
-  sentence  pairs  with  negative label as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{1}),
-  0], ..., [(x_{i}, x'_{P\cdot K}), 0]\}$
-
-  In  this way, we generate the sentence pair dataset $\mathcal{D'}$ for stage 2
-  based  on  the  top-K  class  label  set $\mathcal{C'}$ provided by stage 1 as
-  $\mathcal{D'}=\{\mathcal{P'}_{i}\cup  \mathcal{N'}_{i}\}_{i=1}^{N}$,  in which
-  we have $M=N\cdot K\cdot P$ data points of sentence pairs in total.
-
-  Before starting to fine-tune our sentence-pair model on task-specific dataset,
-  we  first  fine-tune  RoBERTa  on  Quora  dataset  \cite{iyer2017first}, which
-  contains  404,290  potential  duplicate question pairs, for transfer learning.
-  This  is  also  the  merit of similarity based model, as labeled task-specific
-  classification  data  is  hard  to  acquire,  yet  general sentence pairs with
-  similar semantics can be much easier to acquire.
-
-  \subsubsection*{Multi-task based training}
-  We   continue  to  do  multi-task  training  on  sentence-pair  dataset
-  $\mathcal{D'}$ sampled from the top-K candidate class labels provided by stage
-  1. In stage 2, we have two tasks tuning our system.
-
-  The first task is \emph{regular sentence-pair similarity task}.
-  For  sentence  pair semantic similarity task, given a data point $(x, x')_{i}$
-  with       similarity       label       $l_{i}$       from       data      set
-  $\mathcal{D'}=\{[(x,x')_{i},l_{i}]\}_{i=1}^{M}$,   Roberta   takes  the  final
-  hidden  state  $h_{i}$  of the first token [CLS] as the representation for the
-  sequence of packed sentence pair $(x, x')_{i}$. Let's suppose we have a linear
-  layer  as  ${\Phi}^S_{i}=W^Sh_{i}+b^S$,  where  $W^S$  and $b^S$ are trainable
-  parameters,  and  the probability score for $(x, x')_{i}$ can be calculated as
-  $p^S_{i}=softmax({\Phi}^S_{i})$.
-
-  Due  to  the  fact that sentence pairs within the same class is much fewer than
-  that from  different  classes,  the  dataset  $\mathcal{D'}$  is
-  quite imbalanced.  Therefore, we will accommodate a weight variable $w^S = [K-1, 1]$
-  to  the  loss  to eliminate the bias brought by data imbalance, shown in Equ.
-  \ref{eq:similarity_loss}.
-
-  \begin{equation}
-    \begin{aligned}
-      \mathcal{L}^{S}&=\frac{1}{M}\sum_{i=1}^{M}-w^S_{l_i}\cdot log(\frac{exp(\varPhi_{i,l_{i}}^S)}{\sum_{j=0}^{1}exp(\varPhi_{i,j}^S)}) \\
-      \label{eq:similarity_loss}
-    \end{aligned}
-  \end{equation}
-
-  The  second  task  is  \emph{classification  on  top-K classes}. As minimizing
-  similarity  loss  is  not  our  final goal in the intention classification, we
-  bring  back  classification  loss again. In this task, the network is based on
-  sentence  pair  similarity  modules.  The  only  difference  is  that we add a
-  task-specific  average  pooling  layer,  shown  in Fig. \ref{fig:framework} to
-  accomplish the classification task based on sentence-pair model.
-
-  We  already  know  that the size of ${\Phi}^S$ in task 1 is $M\times 2=(N\cdot
-  K\cdot  P)\times  2$, where $N$ is the total number of data points in original
-  training  data $\mathcal{D}$, $K$ is a hyperparameter that controls the number
-  of   candidate   class  labels  provided  by  stage  1,  and  $P$  is  also  a
-  hyperparameter that controls the number of sentences we should randomly sample
-  from each candidate class labels. Now, for the average pooling layer, we first
-  reshape  ${\Phi}^S$  into  the  size  of $N\times K\times P\times 2$, and then
-  split  it  into  ${\Phi}^{K,pos}$  and ${\Phi}^{K,neg}$, and both of them will
-  have  the  size  of  $N\times  K\times  P$.  In this way, ${\Phi}^{K,pos}$ can
-  represent  the  level  of  similarity  for each sentence pair, and in the mean
-  time,  ${\Phi}^{K,neg}$  can  represent  the  level  of dissimilarity for each
-  sentence  pair. Then, we can do average pooling for each candidate class among
-  the  top-K  classes  as  shown  in  Equ.  \ref{eq:average  pooling}.
-
-  \begin{align}
-    {\xi}_{i,j}^{K,pos} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,pos} \ \ \ \ \ \ \ 
-    {\xi}_{i,j}^{K,neg} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,neg}
-    \label{eq:average pooling}
-  \end{align}
-
-  With  the  average pooling result ${\xi}^{K,pos}$ and ${\xi}^{K,neg}$, we also
-  generate   a   top-K   class   label   $l^{K}_i\in   [1,\dots,K]$   for   each
-  ${\xi}^{K,pos}_{i}$ and ${\xi}^{K,neg}_{i}$. The loss for top-K classification
-  task is shown in Equ. \ref{eq:top-k_classification_loss}. In Equ. \ref{eq: pos
-  top-k   loss}   and   Equ.   \ref{eq:   neg   top-k   loss},  the  first  term
-  $\xi_{i,l^{K}_{i}}^{K,pos}$  and  $\xi_{i,l^{K}_{i}}^{K,neg}$  encourage  high
-  level  of  similarity  and  low  level  of dissimilarity for prediction of the
-  correct label $l^{K}_i$ within the top-K candidate classes.
-
-  \begin{align}
-    \mathcal{L}^{K} = \frac{1}{N}\sum_{i=1}^{N}(\mathcal{L}^{K,pos}_{i} - \mathcal{L}^{K,neg}_{i})
-    \label{eq:top-k_classification_loss}
-  \end{align}
-  where
-
-  \begin{equation}
-    \begin{aligned}
-      \mathcal{L}^{K,pos}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,pos})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,pos})})
-      \label{eq: pos top-k loss}
-    \end{aligned}
-  \end{equation}
-
-  \begin{equation}
-    \begin{aligned}
-      \mathcal{L}^{K,neg}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,neg})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,neg})}) \\
-      \label{eq: neg top-k loss}
-    \end{aligned}
-  \end{equation}
-
-  Finally,  the  overall  loss  function for multi-task learning in stage 2 is
-  shown in Equ. \ref{eq:two-stage_SFC_loss}. The training objective of stage 2 is
-  to  minimize  the  weighted  sum  of task-specific losses. Here $\alpha_S$ and
-  $\alpha_K$  are  weights  of  task  1  and  task  2  respectively.
-
-  \begin{align}
-    \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K
-    \label{eq:two-stage_SFC_loss}
-  \end{align}
-
-  \begin{table*}
-    \begin{centering}
-      \scalebox{0.55}{
-        \begin{tabular}{|c|cccccc|cccccc|cccccc|c|c|}
-          \hline 
-          \multicolumn{1}{|c|}{\multirow{2}*{\textbf{Models}} }& \multicolumn{6}{c|}{\textbf{CLINC150}}& \multicolumn{6}{c|}{\textbf{BANKING77}}& \multicolumn{6}{c|}{\textbf{HWU64}}& \ \ \ \textbf{ITG} \ \ \ & \textbf{Amazon-670k}\tabularnewline
-          \cline{2-21}
-          \multicolumn{1}{|c|}{} & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$
-          & $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & $\textbf{5}$ &
-          $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{30}$ &
-          $\textbf{50}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ &
-          $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & \textbf{3-fold} &
-          \textbf{3-fold}\tabularnewline
-          \hline
-          TextCNN & \multirow{2}*{$0.5318$} & \multirow{2}*{$0.6963$} & \multirow{2}*{$0.7609$} & \multirow{2}*{$0.8142$} & \multirow{2}*{$0.8526$} & \multirow{2}*{$0.8867$} & \multirow{2}*{$0.4408$} & \multirow{2}*{$0.6436$} & \multirow{2}*{$0.7366$} & \multirow{2}*{$0.7918$} & \multirow{2}*{$0.8228$} & \multirow{2}*{$0.8619$} & \multirow{2}*{$0.3112$} & \multirow{2}*{$0.4007$} & \multirow{2}*{$0.4823$} & \multirow{2}*{$0.5272$} & \multirow{2}*{$0.5782$} & \multirow{2}*{$0.6262$} & \multirow{2}*{$0.6624$} & \multirow{2}*{$0.4401$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          LEAM & \multirow{2}*{$0.7514$} & \multirow{2}*{$0.8203$} & \multirow{2}*{$0.8612$} & \multirow{2}*{$0.8802$} & \multirow{2}*{$0.9010$} & \multirow{2}*{$0.9180$} & \multirow{2}*{$0.5422$} & \multirow{2}*{$0.7812$} & \multirow{2}*{$0.8129$} & \multirow{2}*{$0.8280$} & \multirow{2}*{$0.8610$} & \multirow{2}*{$0.8727$} & \multirow{2}*{$0.4545$} & \multirow{2}*{$0.5554$} & \multirow{2}*{$0.5936$} & \multirow{2}*{$0.6599$} & \multirow{2}*{$0.6855$} & \multirow{2}*{$0.7046$} & \multirow{2}*{$0.7086$} & \multirow{2}*{$0.6091$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-          BERT-large & \multirow{2}*{$0.8080$} & \multirow{2}*{$0.8904$} & \multirow{2}*{$0.9265$} & \multirow{2}*{$0.9334$} & \multirow{2}*{$0.9497$} & \multirow{2}*{$0.9595$} & \multirow{2}*{$0.5780$} & \multirow{2}*{$0.8004$} & \multirow{2}*{$0.8518$} & \multirow{2}*{$0.8827$} & \multirow{2}*{$0.8858$} & \multirow{2}*{$0.8982$} & \multirow{2}*{$0.4711$} & \multirow{2}*{$0.5963$} & \multirow{2}*{$0.6342$} & \multirow{2}*{$0.7010$} & \multirow{2}*{$0.7117$} & \multirow{2}*{$0.7424$} & \multirow{2}*{$0.7485$} & \multirow{2}*{$0.6658$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          ALBERT-xxlarge & \multirow{2}*{$0.8497$} & \multirow{2}*{$0.9008$} & \multirow{2}*{$0.9296$} & \multirow{2}*{$0.9297$} & \multirow{2}*{$0.9466$} & \multirow{2}*{$0.9578$} & \multirow{2}*{$0.5549$} & \multirow{2}*{$0.7981$} & \multirow{2}*{$0.8231$} & \multirow{2}*{$0.8530$} & \multirow{2}*{$0.8571$} & \multirow{2}*{$0.9096$} & \multirow{2}*{$0.4879$} & \multirow{2}*{$0.6116$} & \multirow{2}*{$0.6135$} & \multirow{2}*{$0.6996$} & \multirow{2}*{$0.7094$} & \multirow{2}*{$0.7376$} & \multirow{2}*{$0.7253$} & \multirow{2}*{$0.6893$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          RoBERTa-base & \multirow{2}*{$0.8732$} & \multirow{2}*{$0.9254$} & \multirow{2}*{$0.9363$} & \multirow{2}*{$0.9482$} & \multirow{2}*{$0.9558$} & \multirow{2}*{$0.9637$} & \multirow{2}*{$0.7305$} & \multirow{2}*{$0.8654$} & \multirow{2}*{$0.8808$} & \multirow{2}*{$0.9080$} & \multirow{2}*{$0.9061$} & \multirow{2}*{$0.9293$} & \multirow{2}*{$0.5831$} & \multirow{2}*{$0.6790$} & \multirow{2}*{$0.7064$} & \multirow{2}*{$0.7100$} & \multirow{2}*{$0.7320$} & \multirow{2}*{$0.7472$} & \multirow{2}*{$0.7734$} & \multirow{2}*{$0.6708$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          RoBERTa-large & \multirow{2}*{$\textbf{0.8974}$} &
-          \multirow{2}*{$\textbf{0.9372}$} & \multirow{2}*{$\textbf{0.9508}$} &
-          \multirow{2}*{$\textbf{0.9584}$} & \multirow{2}*{$\textbf{0.9621}$} & 
-          \multirow{2}*{$\textbf{0.9733}$} & \multirow{2}*{$\textbf{0.7690}$} & 
-          \multirow{2}*{$\textbf{0.8728}$} & \multirow{2}*{$\textbf{0.8966}$} & 
-          \multirow{2}*{$\textbf{0.9099}$} & \multirow{2}*{$\textbf{0.9227}$} & 
-          \multirow{2}*{$\textbf{0.9313}$} & \multirow{2}*{$\textbf{0.6044}$} & 
-          \multirow{2}*{$\textbf{0.7002}$} & \multirow{2}*{$\textbf{0.7129}$} & 
-          \multirow{2}*{$\textbf{0.7436}$} & \multirow{2}*{$\textbf{0.7493}$} & 
-          \multirow{2}*{$\textbf{0.7678}$} & \multirow{2}*{$\textbf{0.7990}$} & 
-          \multirow{2}*{$\textbf{0.7156}$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-          RoBERTa-large & \multirow{2}*{$0.8266$} & \multirow{2}*{$0.8861$} & \multirow{2}*{$0.9023$} & \multirow{2}*{$0.9084$} & \multirow{2}*{$0.9090$} & \multirow{2}*{$0.9407$} & \multirow{2}*{$0.757$} & \multirow{2}*{$0.8476$} & \multirow{2}*{$0.8614$} & \multirow{2}*{$0.8743$} & \multirow{2}*{$0.8749$} & \multirow{2}*{$0.8980$} & \multirow{2}*{$0.5425$} & \multirow{2}*{$0.6164$} & \multirow{2}*{$0.6503$} & \multirow{2}*{$0.6729$} & \multirow{2}*{$0.6947$} & \multirow{2}*{$0.7231$} & \multirow{2}*{$0.7418$} & \multirow{2}*{$0.6362$}\tabularnewline
-          (similarity) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-          2-stage SFC & \multirow{2}*{$0.8979$} & \multirow{2}*{$0.9457$} & \multirow{2}*{$0.9517$} & \multirow{2}*{$0.9591$} & \multirow{2}*{$0.9610$} & \multirow{2}*{$0.9664$} & \multirow{2}*{$0.7975$} & \multirow{2}*{$0.8818$} & \multirow{2}*{$0.8962$} & \multirow{2}*{$0.9109$} & \multirow{2}*{$0.9187$} & \multirow{2}*{$0.9198$} & \multirow{2}*{$0.6477$} & \multirow{2}*{$0.7055$} & \multirow{2}*{$0.7200$} & \multirow{2}*{$0.7232$} & \multirow{2}*{$0.7484$} & \multirow{2}*{$0.7653$} & \multirow{2}*{$0.7972$} & \multirow{2}*{$0.7189$}\tabularnewline
-          (task1) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          2-stage SFC & \multirow{2}*{$0.9162$} & \multirow{2}*{$0.9424$} & \multirow{2}*{$0.9530$} & \multirow{2}*{$0.9617$} & \multirow{2}*{$0.9633$} & \multirow{2}*{$0.9690$} & \multirow{2}*{$0.7997$} & \multirow{2}*{$0.8823$} & \multirow{2}*{$0.8945$} & \multirow{2}*{$0.9123$} & \multirow{2}*{$0.9236$} & \multirow{2}*{$0.9317$} & \multirow{2}*{$0.6498$} & \multirow{2}*{$0.6980$} & \multirow{2}*{$0.7202$} & \multirow{2}*{$0.7358$} & \multirow{2}*{$0.7498$} & \multirow{2}*{$0.7657$} & \multirow{2}*{$0.8020$} & \multirow{2}*{$0.7311$}\tabularnewline
-          (task2) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          2-stage SFC & \multirow{2}*{$0.9167$} & \multirow{2}*{$0.9456$} & \multirow{2}*{$0.9571$} & \multirow{2}*{$0.9638$} & \multirow{2}*{$0.9658$} & \multirow{2}*{$0.9753$} & \multirow{2}*{$0.8135$} & \multirow{2}*{$0.8854$} & \multirow{2}*{$0.8931$} & \multirow{2}*{$0.9192$} & \multirow{2}*{$0.9257$} & \multirow{2}*{$0.9339$} & \multirow{2}*{$0.6525$} & \multirow{2}*{$0.7092$} & \multirow{2}*{$0.7168$} & \multirow{2}*{$0.7476$} & \multirow{2}*{$0.7519$} & \multirow{2}*{$0.7696$} & \multirow{2}*{$\textbf{0.8124}$} & \multirow{2}*{$0.7364$}\tabularnewline
-          (task1 + task2) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-          \multirow{2}*{Joint SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.9669}$} & \multirow{2}*{$\textbf{0.9712}$} & \multirow{2}*{$\textbf{0.9821}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.9323}$} & \multirow{2}*{$\textbf{0.9463}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$\textbf{0.7593}$} & \multirow{2}*{$\textbf{0.7772}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline
-          & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-        \end{tabular}
-      }
-      \par
-    \end{centering}
-    \caption{
-      F1 scores  on  five  task-specific  datasets text classification in chatbot
-      under low resource. For ITG, we keep the full dataset. For Amazon-670k, we
-      randomly  sampled  250  classes  with  training sample numbers within 5-15
-      samples  per  class.  For  CLINC150,  BANKING77,  HWU64, we set up various
-      few-shot  settings  (5/10/15/20/30/50 samples per class) while keeping the
-      test  set to be fixed. The highest scores among all the baseline models and SFC variants for each data setting are both marked
-      in bold.
-    }
-    \label{tbe:table2}
-  \end{table*}
-
-  \subsection{Joint SFC}
-  In  two-stage  SFC,  Stage  1  and  stage 2 are separate that there is no deep
-  interaction  with each other during training. In this case, the performance of
-  stage  1  may  limit  the potential of stage 2; meanwhile, stage 2 also cannot
-  give  training feedback back to stage 1 for fine-tuning. Therefore, to further
-  improve  the  overall performance of SFC, we proposed a joint model structure,
-  shown in Fig. \ref{fig:framework}.
-
-  In  joint  SFC,  classification  model is being placed in lower layer level to
-  dynamically  provide  top-K  candidate  class  labels  for  the  sentence-pair
-  similarity  model  placed in higher layer level through a top-K pooling layer.
-  In  this way, classification model and similarity model can be merged into one
-  single  joint-model  for  multi-task training with sentence pairs sampled from
-  varying  candidate  class  labels,  thus  avoiding the limitation brought by 2
-  separate stage structure.
-
-  There  are 3 tasks in total during the training process of joint SFC, shown in
-  Fig. \ref{fig:framework}, and the overall loss is also the weighted sum of all
-  the   task-specific  losses,  shown  in  Equ.  \ref{eq:joint_SFC_loss}.  Here,
-  $\alpha_S$,  $\alpha_K$  and  $\alpha_C$  represent  the  weights  for  task 1
-  sentence-pair  similarity  in  Equ.  \ref{eq:similarity_loss},  task  2  top-K
-  classification  in Equ. \ref{eq:top-k_classification_loss}, and task 3 general
-  single       sentence       classification      respectively      in      Equ.
-  \ref{eq:classification_loss}.
-
-  \begin{align}
-    \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K + \alpha_C \mathcal{L}^C
-    \label{eq:joint_SFC_loss}
-  \end{align}
-
-  \section{Experiments}
-  \label{sec:exp}
-
-  \subsection{Datasets}
-  Our experiments aim to study the short text classification in the low-resource
-  environment  popular  in  the  task-specific conversational chatbot application.
-  Hence we choose and configure set datasets to serve this study. Different from
-  the  datasets from other short text classification research, such as semantics
-  classification  with  very  limited  semantics labels and relatively longer
-  input,   the   datasets  adopted  in  our  experiments  are  typically  having
-  comparatively  large  number  of  class labels, ranging from several dozens to
-  hundreds,  and  each  class  label  is  associated  with  a handful of labeled
-  queries with each  query  being usually  one  sentence. Table \ref{tbe:dataset
-  statistic} displays their statistics.  All settings of four public datasets would 
-  be released to github soon.
-
-  \begin{enumerate}
-    \item \emph{ITG},  is  a proprietory FAQ dataset from real-world
-    chatbot  project,  which is composed of question and answer pairs about online
-    English teaching. It contains 3,938 sample questions for 228 class labels, and
-    each class label corresponds to a unique answer.
-
-    \item \emph{Amazon-670K}, is a customer product review dataset for
-    text  classification  task  from  the  extreme  classification repository. The
-    complete  dataset  contains 670,091 class labels, 285,176 training samples and
-    150,875   testing   samples   \cite{bhatia2016extreme}.  As  each  sample  may
-    correspond  to  multiple  class labels, we keep only the first one. We further
-    filter  out the class labels that each one is associated with 5 to 15 samples,
-    or  reviews,  to  mimic  the  chatbot scenario. From them, we sample 250 class
-    labels as well as their samples to form a subset with 1,942 + 716 samples.
-
-    \item \emph{HWU64}, is a intention detection dataset designed for
-    home  robot  scenario \cite{liu2019benchmarking}. It aims at the specific task
-    of  capturing  the  intention  for  different  user requests to home robot and
-    finding  the corresponding answer. The raw dataset contains 25,716 data points
-    for 64 class labels through crowdsourcing.
-
-    \item \emph{CLINC150},  is  a dataset designed for task-oriented
-    systems  with  23,700 queries that are short and unstructured for 150 intents,
-    in    the    same   style   made   by   real   users   through   crowdsourcing
-    \cite{larson2019evaluation}.
-
-    \item \emph{BANKING77}, is a intention detection dataset for bank
-    customer  services.  The  raw dataset contains 13,084 data points for 77 class
-    labels \cite{casanueva2020efficient}.
-  \end{enumerate}
-
-  Regarding  the first two datasets, we conduct 3-fold cross validation experiments
-  that   70   percent   as  training,  15  percent  as  validation  and  testing
-  respectively,  and  report  the  averaged  testing results. Regarding the last
-  three datasets, we conduct experiments using a sampling method similar to that
-  in   \cite{casanueva2020efficient}   yet  in  a  more  sophisticated  few-shot
-  settings.  We  fix  a  test  data for each one, and examine their performances
-  using  5,  10,  15,  20,  30,  and 50 samples per class label respectively for
-  training.  This  is important, as in practice, a task-specific chatbot usually
-  starts  with  merely  a  handful of labeled data available in the early stage.
-  Besides,  in  the  active  learning framework, building an effective auxiliary
-  system  with limited resource is also quite important to help developers label
-  data more efficiently.
-
-  \subsection{Baselines}
-  We choose three kinds of system to construct our baselines.
-
-  \begin{enumerate}
-    \item \emph{Pretrained model based classification system}, which consists of
-    BERT \cite{devlin2018bert},  RoBERTa \cite{liu2019roberta},  and  ALBERT  \cite{lan2019albert}  based.  These pretrained
-    models  are  practically  proven  to  achieve  outstanding  performances  in
-    classification task and other NLP tasks.
-
-    \item   \emph{Non-pretrained   model  based  classification  system},  which
-    consists  of  a typical CNN based TextCNN \cite{kim2014convolutional}, and a
-    label-embedding based LEAM \cite{wang2018joint}. Regarding TextCNN, the
-    model is based on output from RoBERTa tokenization, and the kernels are set
-    as 1, 2, 3, 4, 5. Regarding LEAM, a literal class label is required, which
-    is available only in HWU64, CLINC150, BANKING77. Thus, for other two
-    datasets, we have to use its class number instead.  Empirically,
-    a  non-pretrained  model  based  system  are  not  performing  as  well as a
-    pretrained  models  based,  if  both is applicable in some task. Our listing
-    these  non-pretrained model based systems here is to provide a comprehensive
-    performance comparison on our datasets.
-
-    \item   \emph{Pre-trained   model   based   similarity   model}.  We  choose
-    RoBERTa-large  as  our  fundamental  module as our SFC systems are based on
-    RoBERTa  too, and RoBERTa is empirically more effective than other pretrained
-    models  in  the  short  text  classification  task  in  our  experiments. In
-    inference,  we  use  an  elastic search to find a set of potential candidate
-    labels for the similarity model, to guarantee a reasonable running time.
-  \end{enumerate}
-
-  Our SFC systems include two-stage SFC with ablation, trained with two tasks
-  separately and both, and joint SFC with all three tasks.
-
-  \subsection{Implementation Details}
-  For  our  SFC  systems,  we  use RoBERTa-large as the pretrained model for both
-  classification  task  and  sentence-pair similarity task. We fine-tune
-  our  SFC  system  on  our datasets with max sequence length of 128,
-  learning  rate  of 1.5e-5 for RoBERTa-large pretrained model and learning rate
-  of  5e-4  for  task-specific  layer  with polynomial decay and Adam optimizer.
-  Besides,  we  set  the  max number of the epoch to 100 and save the best model on
-  validation  set based on testing result in weighted F1 score
-  \footnote{In the multi-class and multi-label case, this is the average of the
-  F1 score of each class with weighting depending on the numbers in each class.}.
-  We report the F1 score as the main evaluation measure for all experiments.
-
-  In two-stage SFC, in equ. \ref{eq:two-stage_SFC_loss} the weights of two tasks
-  are  set  as  $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting. The reason
-  for  giving  task  2 relatively more weights is that according to the ablation
-  experiments  we  did  in Section \ref{sec:exp}, task 2 contributes more to the
-  overall  performance.  In  joint  SFC,  in  equ.  \ref{eq:joint_SFC_loss}, the
-  weights  of  three  tasks  are  set  as  $\alpha_S=0.25$,  $\alpha_K=0.25$ and
-  $\alpha_C=0.5$  in  our setting. Overall, the task weights are less sensitive
-  in Joint SFC than in two-stage SFC.
-
-  For  the  experiments  in  Table  \ref{tbe:table2},  we  empirically  set  the
-  hyperparameter  to  be  $K=5$  and  $P=10$  for  all  SFC  variants.  In Table
-  \ref{tbe:table3},  we  conduct extensive experiments to see the performance of
-  SFC system under various hyperparameter settings.
-
-  \subsection{Result Analysis}
-  All  results  in  F1  score  on  the  five  datasets with different models and
-  configurations are showed in Table \ref{tbe:table2}.
-
-  The performance of each model is measured in F1 score on the fixed
-  test  set  for  each  dataset.  
-  Overall,  two-stage  SFC systems in multi-task training deliver  moderate 
-  improvements  over  corresponding baselines, and joint SFC deliver more
-  significant and consistent improvements over the best baseline, RoBERTa based
-  classification. In following content, we dive into more details.
-
-  \subsubsection*{Are multi-task and joint training working?} 
-  First, we compare the four  SFC  variants to analyze the improvement
-  brought  by  multi-task  and  joint-model  structure.
-
-  \begin{table}
-    \begin{centering}
-      \begin{tabular}{|c|c|c|c|c|}
-        \hline
-        F1 score & Two-stage SFC & Joint SFC & Gap & \tabularnewline
-        \hline
-        top-1 accuracy  & \textbf{81.50} & 81.07 & -0.47 & \tabularnewline
-        top-5 accuracy & 94.01 & \textbf{94.30} & +0.29 & \tabularnewline
-        \hline
-      \end{tabular}
-      \par
-    \end{centering}
-    \caption{The average classification accuracy in percentage in stage 1 on all five dataset.}
-    \label{tbe:top1_5_accuracy}
-  \end{table}
-
-  Comparing with training two-stage SFC with multi-task, training with only task
-  1,  namely the sentence pair similarity model, degrades by 0.8 percent
-  point  on average, and training with only task 2, namely the top-K based
-  classification  task,  degrades  by  0.45  percent  point  on  average.  These
-  degradation  indicates  multi-task training in two-stage SFC is helpful for the
-  system  performance.  Besides, task 2 plays a relatively more important role in
-  multi-task learning, and this aligns with their optimal weight settings.
-
-  Joint SFC consistently outperforms two-stage SFC with multi-task training  
-  on 5 diverse datasets by 0.95 percents  on  average. 
-  This observation supports the idea that the joint model
-  structure  can  alleviate  the  limitation  brought by the lack of interaction
-  between  two  stages.  In  following analysis, we will focus on the comparison
-  between joint SFC and the other baseline models.
-
-  \subsubsection*{Is  the  fusion of classification and similarity models
-  helpful?}  We  compare  joint SFC with classification and similarity based
-  baselines respectively.
-
-  \begin{table*}
-    \begin{centering}
-
-      \begin{tabular}{|c|c|c|c|c|c|c|}
-        \hline 
-        \multicolumn{1}{|c|}{\multirow{2}*{Dataset}}&\multicolumn{1}{c|}{\multirow{2}*{Model}}& $K=3$ & $K=5$ & $K=10$ & $K=15$ & $K=20$\tabularnewline
-        \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & $P=20$ & $P=10$ & $P=5$ & $P=4$ & $P=3$\tabularnewline
-        \hline
-        \multicolumn{1}{|c|}{\multirow{2}*{ITG}}& two-stage SFC & $0.8034$ & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
-        \cline{2-7}
-        \multicolumn{1}{|c|}{} & joint SFC & $0.7986$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7918$\tabularnewline
-        \hline
-        \multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& two-stage SFC & $0.7278$ & $0.7364$ & $0.7366$ & $0.7328$ & $0.7204$\tabularnewline
-        \cline{2-7}
-        \multicolumn{1}{|c|}{} & joint SFC & $0.7334$ & $0.7445$ & $0.7516$ & $0.7344$ & $0.7373$\tabularnewline
-        \hline
-      \end{tabular}
-      \par
-    \end{centering}
-    \caption{
-      We  show the performances of SFC from different settings of
-      hyperparameters, $K$  denoting the candidate class number from stage 1,
-      $P$ denoting the number of sampled sententence pair in stage 2. 
-    }
-    \label{tbe:table3}
-  \end{table*}
-
-  Regarding the  classification  models,  joint SFC
-  outperforms RoBERTa-large based, the strongest among all baselines, 
-  by 2.04 percent points on average F1 score over 5 datasets.  
-  Especially, ALBERT.xxlarge based is rather unstable  in this senario. Thus, 
-  we did multiple run with different settings and  report the  best  ones here. 
-  Comparatively,  RoBERTa  based is  the  most stable and has the best performance 
-  n almost all experiment settings.
-
-  Regarding  the  similarity  model,  as  analyzed  above,  we  only  choose the
-  RoBERTa-large based implementation as our baseline. Joint SFC achieves more improvement of
-  7.09  percent points  on average F1 score.
-
-  The above analysis illustrates that suitable fusing the two kinds of models
-  can take their advantages.
-
-  \subsubsection*{Does joint SFC improve the classification in stage 1?}
-  We  compare  the  top-1  prediction and top-5 candidate labels in stage 1 from
-  two-stage SFC and joint SFC in Table \ref{tbe:top1_5_accuracy}. We should note
-  that  two-stage  SFC  does not optimize the stage 1 model, which is a RoBERTa
-  based classification model.
-
-  The joint training does not improve the classification performance in stage 1,
-  measured  by  top-1  accuracy.  However,  it  improves  the  quality of top-5
-  candidate  class  labels.  It  can  be  explained that, a classification model
-  inherently optimizes the objective loss, 0-1 error of top-1 here; the sentence
-  pair similairity model in the joint SFC poses more positive effect in optimizing the 
-  candidate labels.
-
-  \subsubsection*{How does training sample size influence SFC?} 
-  We analyze the overall  improvement  trend  of  joint SFC under various few-shot
-  settings, and show results in Fig. \ref{fig:trend}.
-
-  Our main focus  is  to  study  chatbot  building  in common situation during real-world
-  application  where  only  a few sample sentences are available for each class.
-  The  experimental  results  for  the  3  diverse  intention detection datasets
-  (ClINC150,  BANKING77,  HWU64)  under  few-shot  settings, 5 to 50 samples per
-  class,  indicate that our proposed joint SFC can achieve 2.47 percents average
-  improvement   over  one  of  the  most  powerful  baseline  models,  which  is
-  RoBERTa-large  classification  model.  Moreover,  the  improvement  in F1 score
-  becomes  more  and  more prominent with the decrease of data sample number per
-  class.
-
-  \begin{figure}[t]
-    \begin{centering}
-      \includegraphics[scale=0.2]{picture/improvement_trend.jpg} 
-      \par
-    \end{centering}
-    \caption{
-      Improvements  from  Joint  SFC  over  RoBERTa  based  classification  with
-      different size of training data.
-    }
-    \label{fig:trend}
-  \end{figure}
-
-  Especially,  in the most extreme few-shot setting with only 5 training samples
-  per  class  our joint SFC achieves 4.97 percent points improvements on average
-  over  RoBERTa-large classification model. This observation indicates that SFC
-  is  especially  well-performed  when being applied during the initial stage of
-  building  task-specific  chatbot  system,  where the amount of data sample for
-  each class label is extremely scarce.
-
-  Furthermore,  our  proposed  joint  SFC can also achieve 2.04 percents average
-  improvement  over  RoBERTa-large classification model on all the data settings
-  including  the  ones  with  large  scale,  30  to  50  samples per class. This
-  indicates that joint SFC can still steadily outperforms pretrained model based
-  baseline even if the data size grows bigger. However, the improvement is still
-  more prominent when the data is scarce, which makes SFC an excellent model for
-  low-resource chatbot scenario.
-
-  \subsubsection*{How does joint SFC relate to the label  embedding based  LEAM?}
-  LEAM performs consistently better than TextCNN by a large margin in all
-  datasets. TextCNN is practically efficiently in task-specific chat
-  applications, and LEAM shows its power in modeling labeling information.
-
-  LEAM  does not perform as well as SFCs, since the first intuitive reason is it
-  does  not use pretrained model as encoding module; and another critical reason
-  is  in  task-specific  chat applications, it is common to have many intentions
-  that are close to some others with a minor difference, and it is hard and even
-  impossible  to  name  each  intention  with  a short clear name. One candidate
-  solution  is  setting  a most standard sample as the label of that class. When
-  using  non-pretrained  models  base  LEAM,  this is applicable. Yet when using
-  pretrained  model  based, as the all labels can be hundreds of thousands, then
-  this  can not be accommodated in a poplar 32 G Tesla V100 GPU. Actually, joint
-  SFC  can  be  kind  of  understood  as  a  generalization form of LEAM. In the
-  scenario when there is no clear class label, the relationship between a sample
-  and  a class label is implicitly encoded as that between a sample and another
-  sample  from  the  same  class, and this turns into a sentence pair similarity
-  model.
-
-  \subsubsection*{Settings  of  hyperparameters} 
-  Finally, we analyze the effect brought
-  by  different  settings  of  hyperparameters,  see  Table \ref{tbe:table3}.
-
-  We  conduct  experiments on 5 different settings of hyperparameters, which are
-  the  number of candidate class number $K$ and the number of sentence pairs $P$
-  for  each  class,  on  ITG  and Amazon-670K datasets to find the most suitable
-  setting  of  these  2 hyperparameters. We control the total number of sentence
-  pairs  sampled for each user query into about the same level of amount(50-60).
-  Through  analyzing the experimental results shown in Table \ref{tbe:table3}, we
-  find  that the best setting of hyperparameters might be different for datasets
-  of  different  data  size.  The  class label number of ITG and Amazon-670k are
-  similar  in  our  experimental setting, which is around 250. However the total
-  amount of data points of ITG is approximately 2 times larger than Amazon-670k.
-  Therefore,  the  setting of $K=5$ and $P=10$ is good enough for ITG since most
-  of  the  classes  contains  over 10 data points. However, for Amazon-670k, the
-  amount  of  data  sample  for  each  class  is  scarce, thus, we may need more
-  candidate  classes to sample enough effective sentence pairs for sentence-pair
-  model  layer  of  SFC.  In this way, the setting of $K=10$ and $P=5$ becomes a
-  good choice. However, in spite of the effect on evaluation performance brought
-  by different settings of hyperparameters, joint SFC still steadily outperforms
-  two-stage  SFC  by  0.41  percents  in  overall  average  F1 score  on  ITG and
-  Amazon-670k datasets.
-
-  In  conclusion, to the best of our knowledge, these experimental results place
-  joint  SFC as the best performing model on 5 diverse experimental datasets for
-  text   classification   task,   especially   when   it's   under  low-resource
-  task-specific conversational chatbot scenario.
-
-  \bibliographystyle{aaai21}
-  \bibliography{refs}
-
-\end{document}

### 2020-09-10 chatbot_classification/aaai_2021/methodology.tex
Reorganized.   modified:   paper.tex
  new file:   abstract.tex
  new file:   introduction.tex
  new file:   related_work.tex
  new file:   methodology.tex
  new file:   experiments.tex
  new file:   conclusion.tex

--- 2020-09-10 chatbot_classification/aaai_2021/paper.tex
@@
-\def\year{2021}\relax
-%File: formatting-instructions-latex-2021.tex
-\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
-\usepackage{aaai21}  % DO NOT CHANGE THIS
-\usepackage{times}  % DO NOT CHANGE THIS
-\usepackage{helvet} % DO NOT CHANGE THIS
-\usepackage{courier}  % DO NOT CHANGE THIS
-\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
-\usepackage{graphicx} % DO NOT CHANGE THIS
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{float}
-\usepackage{subfigure}
-\usepackage[switch]{lineno}
-\usepackage{spconf}
-\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-
-\urlstyle{rm} % DO NOT CHANGE THIS
-\def\UrlFont{\rm}  % DO NOT CHANGE THIS
-\frenchspacing  % DO NOT CHANGE THIS
-\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
-\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
-
-\providecommand{\tabularnewline}{\\}
-%% A simple dot to overcome graphicx limitations
-\newcommand{\lyxdot}{.}
-
-\def\x{{\mathbf x}}
-\def\L{{\cal L}}
-
-%\nocopyright
-%PDF Info Is REQUIRED.
-% For /Author, add all authors within the parentheses, separated by commas. No accents or commands.
-% For /Title, add Title in Mixed Case. No accents or commands. Retain the parentheses.
-\pdfinfo{
-  /title (Joint training of classification model and similarity model for
-  low-resource text classification in chatbot)
-  /Author (no author informmation)
-  /TemplateVersion (2021.1)
-}
-
-\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
-%% Because html converters don't know tabularnewline
-\title{     
-  %SFC: Few-Shot Text Classification via Similarity Fused with Classification System
-  Joint Training of Classification and Similarity Models for \\ 
-  Intention Detection in Task-specific Chatbot
-}
-
-\begin{document}
-  \maketitle
-  \linenumbers
-
-  \begin{abstract}
-    Task-specific  chatbot systems have gained many important applications, such
-    as  Siri,  Google home, and customer service systems, etc. One essential technique 
-    underlying these applications  is to detect the real intention behind a user's input.
-    The intention detection,  assuming  only  one  intention  in  a  user's input here, can be
-    regarded  as  a  short  text  classification problem.  In  practice,  the  number  of
-    intentions  can  be hundreds of thousands, as opposed to a few number in the
-    traditional text classification problem; creating enough training data from tons of 
-    raw user logs with miscellaneous information is not trivial, 
-    and generally only 10 to 20 samples per intention are available in  the  early  stage.  
-    Thus,  how  to  train  an  effective short-text classification model with
-    limited labeled data  in such a practical  and important application is critical. In this work, we propose a
-    novel  model, called similarity model fused with classification model (SFC),
-    which  combines  a  classification  model  and  a similarity model, and also
-    borrows  the  power  of  multi-task  training  as well. We conduct extensive
-    experiments  on  4  public  and 1 private datasets. Experimental results
-    show that our new model outperforms very strong baselines (i.e., BERT, RoBERTa and
-    ALBERT based pretrained models) by over 2 percentages in average F1 score.
-
-  \end{abstract}
-
-  \section{Introduction}
-  \label{sec:intro}
-
-  Task-specific  conversational  chatbot  \cite{wen2016network}  has been applied
-  into  many practical products. One typical example is the chatbot that shares the working burden of
-  human  customer  service  agents  responsible  for  customers' questions about
-  certain  products  or services. Another one is the speech-based control in
-  devices  like  intelligent  speakers, such as Siri, Google home, Baidu Xiaodu,
-  and smart home equipments, to name a few. Regardless of whether these conversations belong to
-  single or  multi-round, an essential technique underlying this type of chatbot is to
-  identify  the  real  intention  behind  a  user's  question or reply. 
-  The detected intention  with  its  associated  information  is then mapped into a
-  predefined dialog logic graph, from which a suitable response (e.g., conducting 
-  expected actions, replying texts or accomplishing some operations, etc)  is returned.
-  This  is  the  main  difference  from  a  free chatbot.
-
-  Intention detection in task-specific chatbot  is  a  challenging task due to some inherent properties. First,
-  a customer's  utterance  within  a conversation is usually quite short. Since it
-  does  not  contain  enough  information,  short  texts \cite{song2014short} are
-  thought  to  be  more  ambiguous  compared to long texts such as paragraphs or
-  documents,  posing  a  great challenge \cite{chen2019deep} for classification
-  task   \cite{phan2008learning,yan2009dynamic,hua2015short}.   Second,  in  the
-  initial  stage  of  building  a  chatbot  , it is often rather hard to collect
-  sufficient  labeled  data  to  train  a good model. Because developers have to
-  examine tons of real system logs for typical user's utterances, and then label
-  them  with expected intentions. Therefore, to build a task-specific chatbot with
-  high  performance, it is essential to solve the challenge of short-text
-  classification   \cite{sriram2010short}   problem   under   few-shot   setting
-  \cite{yu2018diverse}.
-
-  Generally  there  are  two  kinds  of  approaches  to  address  this  problem,
-  one is the classification model that directly maps an input into a most likely label, and
-  the other one is the similarity  model  that searches a label whose associated data is most similar to
-  an input.
-
-  The   first  one,  \emph{text  classification},  includes  classic  long  text
-  classification  and  short  text  classification  in  this  scenario.  Besides
-  traditional  machine  learning  models  like  SVM \cite{suykens1999least},  
-  boosting  tree \cite{tu2005probabilistic},  many work
-  \cite{wen2016network}  choose  neural  network  such  as  convolutional neural
-  networks (CNNs) \cite{kim2014convolutional,zhang2015character,conneau2016very}
-  and       long       short       term       memory       networks      (LSTMs)
-  \cite{mousa2017contextual,liu2016recurrent}   to   accomplish   the   task  of
-  extracting  semantic  feature from limited amount of words. Their common model
-  structure  is  adding  a  softmax classifier as the final layer and mapping to
-  labels.  Another  two  interesting lines of work, label-word joint models, and
-  joint  NER  and  classification  are  discussed  in  the related work section.
-  Afterwards,   pre-trained   language   models   on   large  corpus  like  BERT
-  \cite{devlin2018bert}  and  RoBERTa \cite{liu2019roberta} has been proven more
-  powerful  in  solving  many  NLP  tasks  including  short-text  classification
-  \cite{madabushi2020cost}.      Especially      for      few-shot     scenarios
-  \cite{yu2018diverse},     pre-trained     model    based    on    transformers
-  \cite{vaswani2017attention} tends to do more
-  help to reducing the negative effects brought by scarcity of training data.
-
-  The  second  one,  \emph{similarity model} is also called sentence-pair model.
-  Its  motivation  originates  from  the idea of Information Retrieval (IR) based
-  chatbot   \cite{jafarpour2010filter,   leuski2011npceditor}.   Having   a  Q-A
-  (Question-Answer)  pairs dataset and user query Q, the IR based conversational
-  system will look up in the Q-A dataset for the pair (Q', A') that best matches
-  query  Q  through  semantic  analysis  and  returns  A'  as  the  answer  to Q
-  \cite{mnasri2019recent}. In this way, sentence-pair model pre-trained on large
-  corpus  of  semantic  similarity  identification task can be applied for being
-  used  as  a  tool  to  identify  the class with highest semantic similarity to
-  customer's    query.    A    common    model    structure    of    pre-trained 
-  sentence-pair model is based on multiple cross-attention
-  mechanism  \cite{barkan2020scalable}. Due to
-  the   fact   that   many   experiment   results   have   shown   that  RoBERTa
-  \cite{liu2019roberta} is an improved version of BERT \cite{devlin2018bert}, and has achieved amazing
-  results  on  both  text  classification and sentence-pairs semantic similarity
-  tasks, we choose RoBERTa as an important baseline approach in this paper.
-
-  Despite  the  success  of  these two kinds of approaches, they still have some
-  limitations   in   task-specific  chatbot  scenario.  As  for  the  \emph{text
-  classification  model},  it  is  quite hard to use data augmentation method to
-  solve  the  data insufficiency challenge since the it is usually unfeasible to
-  get  large amount of domain-specific data when facing a new task. With respect
-  to  the  \emph{similarity model}, though we can obtain a large amount of data
-  from semantically  duplicate  sentence  pair identification domain for transfer
-  learning  \cite{sun2019fine},  it  is  still  quite  hard  to  perform well on
-  a new task-specific dataset,  since their objective losses are totally different.
-
-  The  above limitation motivates us to propose a joint system that is capable of
-  taking  advantages  from  both  classification model and similarity model. We
-  call  it  SFC,  short  for  similairty model fused with classification Model,
-  shown  in  Fig.  \ref{fig:framework}.  To  better train SFC, we further bring in
-  multi-task   learning   \cite{caruana1993multitask,collobert2008unified, liu2019multi}.  Our
-  basic  idea  came  from  two  stages. In the first stage, we use an auxiliary
-  model  to  select top-K most possible labels for a input. This model can be an
-  elastic search  \cite{divya2013elasticsearch}  or  a  text classification model
-  trained on current task-specific chatbot data. In the second stage, we build a
-  classification  model  whose  main modules are similarity models. Then, this
-  structure  derives two goals to train towards, the classification loss for our
-  application,  and the similarity loss for the main modules. When the two stages
-  are  independently  optimized,  we call \emph{two-stage SFC}. We further find,
-  the  the  quality  of  output  from  the  first  stage  might  limit the final
-  performance  of  system,  since  the  candidate  labels for each user query is
-  always  fixed  in  the  whole  multi-task  training  process. This observation
-  motivates  us  to  further  improve  the  two-stage SFC into a joint training,
-  called  \emph{joint  SFC}. In this way, the sentence pairs associated with the
-  top-K  classes  also  become dynamic, and the text classification model in the
-  first  stage  will also be further optimized to provide better top-K result by
-  the final training loss.
-
-  We summarize our contributions as follow:
-  \begin{enumerate}
-    \item We propose a novel joint system to makes full utilization of
-    the advantages from both text classification model and similarity model.
-
-    \item To  better  train such a system, we bring in multi-task training to obtain
-    reasonable performance.
-
-    \item Experiment  results  from 4 public and 1 private short-text classification
-    datasets,  show  that  our  proposed  SFC joint system can achieve significant
-    and consistent improvements over strong baselines, especially in the low resource settings.
-  \end{enumerate}
-
-  \begin{figure*}[t]
-    \begin{centering}
-      \includegraphics[scale=0.72]{picture/picture4} 
-      \par
-    \end{centering}
-    \caption{
-      \textbf{Network Structure of SFC:} two-stage SFC and joint-SFC are sharing
-      the  same  network  from  stage  1  and  stage 2, with the only difference
-      whether two stages being jointly trained.
-    }
-    \label{fig:framework}
-  \end{figure*}
-
-  \section{Related work}
-
-  Another  common  approach  is  text  classification  neural  network  based on
-  label-word     joint     embedding,    such    as    LEAM \cite{wang2018joint},
-  MTLE \cite{zhang2017multi}   and   EXAM \cite{du2019explicit}.   This   approach
-  involves  label  embedding when constructing the text-sequence representation.
-  Take  LEAM  as  an  example,  the  text classification model is implemented by
-  jointly    embedding    the    word    and    label   in   the   same   latent
-  space \cite{wang2018joint}. Afterwards, the text representation are constructed
-  based  on  text-label  compatibility through attention mechanism. In this way,
-  additional  sources  of  semantic  information  from class labels can be fully
-  leveraged, which is quite helpful especially under few-shot scenario.
-
-  As for \emph{label-word joint
-  embedding  approach},  it  poses  noticeable requirements on label information.
-  However,  in  our  cases,  since  we have large amount of class labels without
-  being well-defined for question answering chatbot, the only thing we can do is
-  to  choose  one  of the user utterance as the class label to represent the key
-  information  of  the  whole class. In this way, the label will become not only
-  prolix  but  also  biased,  which  will  bring  some  negative effect to label
-  embedding.
-
-  Another   line   of  interesting  work  is  the  joint  training  of  sentence
-  classification   and  NER  (todo:  reference).  If  both  the  city  and  date
-  information  are  recognized,  then  they  are good indicators that this query
-  might  be  booking  an  ticket. This work can also be combined in our proposed
-  framework.
-
 \section{Methodology}
@@
 \end{align}
-
-  \section{Experiments}
-  \label{sec:exp}
-
-  \subsection{Datasets}
-  Our experiments aim to study the short text classification in the low-resource
-  environment  popular  in  the  task-specific conversational chatbot application.
-  Hence we choose and configure set datasets to serve this study. Different from
-  the  datasets from other short text classification research, such as semantics
-  classification  with  very  limited  semantics labels and relatively longer
-  input,   the   datasets  adopted  in  our  experiments  are  typically  having
-  comparatively  large  number  of  class labels, ranging from several dozens to
-  hundreds,  and  each  class  label  is  associated  with  a handful of labeled
-  queries with each  query  being usually  one  sentence. Table \ref{tbe:dataset
-  statistic} displays their statistics.  All settings of four public datasets would 
-  be released to github soon.
-
-  \begin{enumerate}
-    \item \emph{ITG},  is  a proprietory FAQ dataset from real-world
-    chatbot  project,  which is composed of question and answer pairs about online
-    English teaching. It contains 3,938 sample questions for 228 class labels, and
-    each class label corresponds to a unique answer.
-
-    \item \emph{Amazon-670K}, is a customer product review dataset for
-    text  classification  task  from  the  extreme  classification repository. The
-    complete  dataset  contains 670,091 class labels, 285,176 training samples and
-    150,875   testing   samples   \cite{bhatia2016extreme}.  As  each  sample  may
-    correspond  to  multiple  class labels, we keep only the first one. We further
-    filter  out the class labels that each one is associated with 5 to 15 samples,
-    or  reviews,  to  mimic  the  chatbot scenario. From them, we sample 250 class
-    labels as well as their samples to form a subset with 1,942 + 716 samples.
-
-    \item \emph{HWU64}, is a intention detection dataset designed for
-    home  robot  scenario \cite{liu2019benchmarking}. It aims at the specific task
-    of  capturing  the  intention  for  different  user requests to home robot and
-    finding  the corresponding answer. The raw dataset contains 25,716 data points
-    for 64 class labels through crowdsourcing.
-
-    \item \emph{CLINC150},  is  a dataset designed for task-oriented
-    systems  with  23,700 queries that are short and unstructured for 150 intents,
-    in    the    same   style   made   by   real   users   through   crowdsourcing
-    \cite{larson2019evaluation}.
-
-    \item \emph{BANKING77}, is a intention detection dataset for bank
-    customer  services.  The  raw dataset contains 13,084 data points for 77 class
-    labels \cite{casanueva2020efficient}.
-  \end{enumerate}
-
-  Regarding  the first two datasets, we conduct 3-fold cross validation experiments
-  that   70   percent   as  training,  15  percent  as  validation  and  testing
-  respectively,  and  report  the  averaged  testing results. Regarding the last
-  three datasets, we conduct experiments using a sampling method similar to that
-  in   \cite{casanueva2020efficient}   yet  in  a  more  sophisticated  few-shot
-  settings.  We  fix  a  test  data for each one, and examine their performances
-  using  5,  10,  15,  20,  30,  and 50 samples per class label respectively for
-  training.  This  is important, as in practice, a task-specific chatbot usually
-  starts  with  merely  a  handful of labeled data available in the early stage.
-  Besides,  in  the  active  learning framework, building an effective auxiliary
-  system  with limited resource is also quite important to help developers label
-  data more efficiently.
-
-  \subsection{Baselines}
-  We choose three kinds of system to construct our baselines.
-
-  \begin{enumerate}
-    \item \emph{Pretrained model based classification system}, which consists of
-    BERT \cite{devlin2018bert},  RoBERTa \cite{liu2019roberta},  and  ALBERT  \cite{lan2019albert}  based.  These pretrained
-    models  are  practically  proven  to  achieve  outstanding  performances  in
-    classification task and other NLP tasks.
-
-    \item   \emph{Non-pretrained   model  based  classification  system},  which
-    consists  of  a typical CNN based TextCNN \cite{kim2014convolutional}, and a
-    label-embedding based LEAM \cite{wang2018joint}. Regarding TextCNN, the
-    model is based on output from RoBERTa tokenization, and the kernels are set
-    as 1, 2, 3, 4, 5. Regarding LEAM, a literal class label is required, which
-    is available only in HWU64, CLINC150, BANKING77. Thus, for other two
-    datasets, we have to use its class number instead.  Empirically,
-    a  non-pretrained  model  based  system  are  not  performing  as  well as a
-    pretrained  models  based,  if  both is applicable in some task. Our listing
-    these  non-pretrained model based systems here is to provide a comprehensive
-    performance comparison on our datasets.
-
-    \item   \emph{Pre-trained   model   based   similarity   model}.  We  choose
-    RoBERTa-large  as  our  fundamental  module as our SFC systems are based on
-    RoBERTa  too, and RoBERTa is empirically more effective than other pretrained
-    models  in  the  short  text  classification  task  in  our  experiments. In
-    inference,  we  use  an  elastic search to find a set of potential candidate
-    labels for the similarity model, to guarantee a reasonable running time.
-  \end{enumerate}
-
-  Our SFC systems include two-stage SFC with ablation, trained with two tasks
-  separately and both, and joint SFC with all three tasks.
-
-  \subsection{Implementation Details}
-  For  our  SFC  systems,  we  use RoBERTa-large as the pretrained model for both
-  classification  task  and  sentence-pair similarity task. We fine-tune
-  our  SFC  system  on  our datasets with max sequence length of 128,
-  learning  rate  of 1.5e-5 for RoBERTa-large pretrained model and learning rate
-  of  5e-4  for  task-specific  layer  with polynomial decay and Adam optimizer.
-  Besides,  we  set  the  max number of the epoch to 100 and save the best model on
-  validation  set based on testing result in weighted F1 score
-  \footnote{In the multi-class and multi-label case, this is the average of the
-  F1 score of each class with weighting depending on the numbers in each class.}.
-  We report the F1 score as the main evaluation measure for all experiments.
-
-  In two-stage SFC, in equ. \ref{eq:two-stage_SFC_loss} the weights of two tasks
-  are  set  as  $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting. The reason
-  for  giving  task  2 relatively more weights is that according to the ablation
-  experiments  we  did  in Section \ref{sec:exp}, task 2 contributes more to the
-  overall  performance.  In  joint  SFC,  in  equ.  \ref{eq:joint_SFC_loss}, the
-  weights  of  three  tasks  are  set  as  $\alpha_S=0.25$,  $\alpha_K=0.25$ and
-  $\alpha_C=0.5$  in  our setting. Overall, the task weights are less sensitive
-  in Joint SFC than in two-stage SFC.
-
-  For  the  experiments  in  Table  \ref{tbe:table2},  we  empirically  set  the
-  hyperparameter  to  be  $K=5$  and  $P=10$  for  all  SFC  variants.  In Table
-  \ref{tbe:table3},  we  conduct extensive experiments to see the performance of
-  SFC system under various hyperparameter settings.
-
-  \subsection{Result Analysis}
-  All  results  in  F1  score  on  the  five  datasets with different models and
-  configurations are showed in Table \ref{tbe:table2}.
-
-  The performance of each model is measured in F1 score on the fixed
-  test  set  for  each  dataset.  
-  Overall,  two-stage  SFC systems in multi-task training deliver  moderate 
-  improvements  over  corresponding baselines, and joint SFC deliver more
-  significant and consistent improvements over the best baseline, RoBERTa based
-  classification. In following content, we dive into more details.
-
-  \subsubsection*{Are multi-task and joint training working?} 
-  First, we compare the four  SFC  variants to analyze the improvement
-  brought  by  multi-task  and  joint-model  structure.
-
-  \begin{table}
-    \begin{centering}
-      \begin{tabular}{|c|c|c|c|c|}
-        \hline
-        F1 score & Two-stage SFC & Joint SFC & Gap & \tabularnewline
-        \hline
-        top-1 accuracy  & \textbf{81.50} & 81.07 & -0.47 & \tabularnewline
-        top-5 accuracy & 94.01 & \textbf{94.30} & +0.29 & \tabularnewline
-        \hline
-      \end{tabular}
-      \par
-    \end{centering}
-    \caption{The average classification accuracy in percentage in stage 1 on all five dataset.}
-    \label{tbe:top1_5_accuracy}
-  \end{table}
-
-  Comparing with training two-stage SFC with multi-task, training with only task
-  1,  namely the sentence pair similarity model, degrades by 0.8 percent
-  point  on average, and training with only task 2, namely the top-K based
-  classification  task,  degrades  by  0.45  percent  point  on  average.  These
-  degradation  indicates  multi-task training in two-stage SFC is helpful for the
-  system  performance.  Besides, task 2 plays a relatively more important role in
-  multi-task learning, and this aligns with their optimal weight settings.
-
-  Joint SFC consistently outperforms two-stage SFC with multi-task training  
-  on 5 diverse datasets by 0.95 percents  on  average. 
-  This observation supports the idea that the joint model
-  structure  can  alleviate  the  limitation  brought by the lack of interaction
-  between  two  stages.  In  following analysis, we will focus on the comparison
-  between joint SFC and the other baseline models.
-
-  \subsubsection*{Is  the  fusion of classification and similarity models
-  helpful?}  We  compare  joint SFC with classification and similarity based
-  baselines respectively.
-
-  \begin{table*}
-    \begin{centering}
-
-      \begin{tabular}{|c|c|c|c|c|c|c|}
-        \hline 
-        \multicolumn{1}{|c|}{\multirow{2}*{Dataset}}&\multicolumn{1}{c|}{\multirow{2}*{Model}}& $K=3$ & $K=5$ & $K=10$ & $K=15$ & $K=20$\tabularnewline
-        \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & $P=20$ & $P=10$ & $P=5$ & $P=4$ & $P=3$\tabularnewline
-        \hline
-        \multicolumn{1}{|c|}{\multirow{2}*{ITG}}& two-stage SFC & $0.8034$ & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
-        \cline{2-7}
-        \multicolumn{1}{|c|}{} & joint SFC & $0.7986$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7918$\tabularnewline
-        \hline
-        \multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& two-stage SFC & $0.7278$ & $0.7364$ & $0.7366$ & $0.7328$ & $0.7204$\tabularnewline
-        \cline{2-7}
-        \multicolumn{1}{|c|}{} & joint SFC & $0.7334$ & $0.7445$ & $0.7516$ & $0.7344$ & $0.7373$\tabularnewline
-        \hline
-      \end{tabular}
-      \par
-    \end{centering}
-    \caption{
-      We  show the performances of SFC from different settings of
-      hyperparameters, $K$  denoting the candidate class number from stage 1,
-      $P$ denoting the number of sampled sententence pair in stage 2. 
-    }
-    \label{tbe:table3}
-  \end{table*}
-
-  Regarding the  classification  models,  joint SFC
-  outperforms RoBERTa-large based, the strongest among all baselines, 
-  by 2.04 percent points on average F1 score over 5 datasets.  
-  Especially, ALBERT.xxlarge based is rather unstable  in this senario. Thus, 
-  we did multiple run with different settings and  report the  best  ones here. 
-  Comparatively,  RoBERTa  based is  the  most stable and has the best performance 
-  n almost all experiment settings.
-
-  Regarding  the  similarity  model,  as  analyzed  above,  we  only  choose the
-  RoBERTa-large based implementation as our baseline. Joint SFC achieves more improvement of
-  7.09  percent points  on average F1 score.
-
-  The above analysis illustrates that suitable fusing the two kinds of models
-  can take their advantages.
-
-  \subsubsection*{Does joint SFC improve the classification in stage 1?}
-  We  compare  the  top-1  prediction and top-5 candidate labels in stage 1 from
-  two-stage SFC and joint SFC in Table \ref{tbe:top1_5_accuracy}. We should note
-  that  two-stage  SFC  does not optimize the stage 1 model, which is a RoBERTa
-  based classification model.
-
-  The joint training does not improve the classification performance in stage 1,
-  measured  by  top-1  accuracy.  However,  it  improves  the  quality of top-5
-  candidate  class  labels.  It  can  be  explained that, a classification model
-  inherently optimizes the objective loss, 0-1 error of top-1 here; the sentence
-  pair similairity model in the joint SFC poses more positive effect in optimizing the 
-  candidate labels.
-
-  \subsubsection*{How does training sample size influence SFC?} 
-  We analyze the overall  improvement  trend  of  joint SFC under various few-shot
-  settings, and show results in Fig. \ref{fig:trend}.
-
-  Our main focus  is  to  study  chatbot  building  in common situation during real-world
-  application  where  only  a few sample sentences are available for each class.
-  The  experimental  results  for  the  3  diverse  intention detection datasets
-  (ClINC150,  BANKING77,  HWU64)  under  few-shot  settings, 5 to 50 samples per
-  class,  indicate that our proposed joint SFC can achieve 2.47 percents average
-  improvement   over  one  of  the  most  powerful  baseline  models,  which  is
-  RoBERTa-large  classification  model.  Moreover,  the  improvement  in F1 score
-  becomes  more  and  more prominent with the decrease of data sample number per
-  class.
-
-  \begin{figure}[t]
-    \begin{centering}
-      \includegraphics[scale=0.2]{picture/improvement_trend.jpg} 
-      \par
-    \end{centering}
-    \caption{
-      Improvements  from  Joint  SFC  over  RoBERTa  based  classification  with
-      different size of training data.
-    }
-    \label{fig:trend}
-  \end{figure}
-
-  Especially,  in the most extreme few-shot setting with only 5 training samples
-  per  class  our joint SFC achieves 4.97 percent points improvements on average
-  over  RoBERTa-large classification model. This observation indicates that SFC
-  is  especially  well-performed  when being applied during the initial stage of
-  building  task-specific  chatbot  system,  where the amount of data sample for
-  each class label is extremely scarce.
-
-  Furthermore,  our  proposed  joint  SFC can also achieve 2.04 percents average
-  improvement  over  RoBERTa-large classification model on all the data settings
-  including  the  ones  with  large  scale,  30  to  50  samples per class. This
-  indicates that joint SFC can still steadily outperforms pretrained model based
-  baseline even if the data size grows bigger. However, the improvement is still
-  more prominent when the data is scarce, which makes SFC an excellent model for
-  low-resource chatbot scenario.
-
-  \subsubsection*{How does joint SFC relate to the label  embedding based  LEAM?}
-  LEAM performs consistently better than TextCNN by a large margin in all
-  datasets. TextCNN is practically efficiently in task-specific chat
-  applications, and LEAM shows its power in modeling labeling information.
-
-  LEAM  does not perform as well as SFCs, since the first intuitive reason is it
-  does  not use pretrained model as encoding module; and another critical reason
-  is  in  task-specific  chat applications, it is common to have many intentions
-  that are close to some others with a minor difference, and it is hard and even
-  impossible  to  name  each  intention  with  a short clear name. One candidate
-  solution  is  setting  a most standard sample as the label of that class. When
-  using  non-pretrained  models  base  LEAM,  this is applicable. Yet when using
-  pretrained  model  based, as the all labels can be hundreds of thousands, then
-  this  can not be accommodated in a poplar 32 G Tesla V100 GPU. Actually, joint
-  SFC  can  be  kind  of  understood  as  a  generalization form of LEAM. In the
-  scenario when there is no clear class label, the relationship between a sample
-  and  a class label is implicitly encoded as that between a sample and another
-  sample  from  the  same  class, and this turns into a sentence pair similarity
-  model.
-
-  \subsubsection*{Settings  of  hyperparameters} 
-  Finally, we analyze the effect brought
-  by  different  settings  of  hyperparameters,  see  Table \ref{tbe:table3}.
-
-  We  conduct  experiments on 5 different settings of hyperparameters, which are
-  the  number of candidate class number $K$ and the number of sentence pairs $P$
-  for  each  class,  on  ITG  and Amazon-670K datasets to find the most suitable
-  setting  of  these  2 hyperparameters. We control the total number of sentence
-  pairs  sampled for each user query into about the same level of amount(50-60).
-  Through  analyzing the experimental results shown in Table \ref{tbe:table3}, we
-  find  that the best setting of hyperparameters might be different for datasets
-  of  different  data  size.  The  class label number of ITG and Amazon-670k are
-  similar  in  our  experimental setting, which is around 250. However the total
-  amount of data points of ITG is approximately 2 times larger than Amazon-670k.
-  Therefore,  the  setting of $K=5$ and $P=10$ is good enough for ITG since most
-  of  the  classes  contains  over 10 data points. However, for Amazon-670k, the
-  amount  of  data  sample  for  each  class  is  scarce, thus, we may need more
-  candidate  classes to sample enough effective sentence pairs for sentence-pair
-  model  layer  of  SFC.  In this way, the setting of $K=10$ and $P=5$ becomes a
-  good choice. However, in spite of the effect on evaluation performance brought
-  by different settings of hyperparameters, joint SFC still steadily outperforms
-  two-stage  SFC  by  0.41  percents  in  overall  average  F1 score  on  ITG and
-  Amazon-670k datasets.
-
-  In  conclusion, to the best of our knowledge, these experimental results place
-  joint  SFC as the best performing model on 5 diverse experimental datasets for
-  text   classification   task,   especially   when   it's   under  low-resource
-  task-specific conversational chatbot scenario.
-
-  \bibliographystyle{aaai21}
-  \bibliography{refs}
-
-\end{document}

### 2020-09-10 chatbot_classification/aaai_2021/paper.tex
Reorganized.   modified:   paper.tex
  new file:   abstract.tex
  new file:   introduction.tex
  new file:   related_work.tex
  new file:   methodology.tex
  new file:   experiments.tex
  new file:   conclusion.tex

@@
 
-  \begin{abstract}
-    Task-specific  chatbot systems have gained many important applications, such
-    as  Siri,  Google home, and customer service systems, etc. One essential technique 
-    underlying these applications  is to detect the real intention behind a user's input.
-    The intention detection,  assuming  only  one  intention  in  a  user's input here, can be
-    regarded  as  a  short  text  classification problem.  In  practice,  the  number  of
-    intentions  can  be hundreds of thousands, as opposed to a few number in the
-    traditional text classification problem; creating enough training data from tons of 
-    raw user logs with miscellaneous information is not trivial, 
-    and generally only 10 to 20 samples per intention are available in  the  early  stage.  
-    Thus,  how  to  train  an  effective short-text classification model with
-    limited labeled data  in such a practical  and important application is critical. In this work, we propose a
-    novel  model, called similarity model fused with classification model (SFC),
-    which  combines  a  classification  model  and  a similarity model, and also
-    borrows  the  power  of  multi-task  training  as well. We conduct extensive
-    experiments  on  4  public  and 1 private datasets. Experimental results
-    show that our new model outperforms very strong baselines (i.e., BERT, RoBERTa and
-    ALBERT based pretrained models) by over 2 percentages in average F1 score.
-
-  \end{abstract}
-
-  \section{Introduction}
-  \label{sec:intro}
-
-  Task-specific  conversational  chatbot  \cite{wen2016network}  has been applied
-  into  many practical products. One typical example is the chatbot that shares the working burden of
-  human  customer  service  agents  responsible  for  customers' questions about
-  certain  products  or services. Another one is the speech-based control in
-  devices  like  intelligent  speakers, such as Siri, Google home, Baidu Xiaodu,
-  and smart home equipments, to name a few. Regardless of whether these conversations belong to
-  single or  multi-round, an essential technique underlying this type of chatbot is to
-  identify  the  real  intention  behind  a  user's  question or reply. 
-  The detected intention  with  its  associated  information  is then mapped into a
-  predefined dialog logic graph, from which a suitable response (e.g., conducting 
-  expected actions, replying texts or accomplishing some operations, etc)  is returned.
-  This  is  the  main  difference  from  a  free chatbot.
-
-  Intention detection in task-specific chatbot  is  a  challenging task due to some inherent properties. First,
-  a customer's  utterance  within  a conversation is usually quite short. Since it
-  does  not  contain  enough  information,  short  texts \cite{song2014short} are
-  thought  to  be  more  ambiguous  compared to long texts such as paragraphs or
-  documents,  posing  a  great challenge \cite{chen2019deep} for classification
-  task   \cite{phan2008learning,yan2009dynamic,hua2015short}.   Second,  in  the
-  initial  stage  of  building  a  chatbot  , it is often rather hard to collect
-  sufficient  labeled  data  to  train  a good model. Because developers have to
-  examine tons of real system logs for typical user's utterances, and then label
-  them  with expected intentions. Therefore, to build a task-specific chatbot with
-  high  performance, it is essential to solve the challenge of short-text
-  classification   \cite{sriram2010short}   problem   under   few-shot   setting
-  \cite{yu2018diverse}.
-
-  Generally  there  are  two  kinds  of  approaches  to  address  this  problem,
-  one is the classification model that directly maps an input into a most likely label, and
-  the other one is the similarity  model  that searches a label whose associated data is most similar to
-  an input.
-
-  The   first  one,  \emph{text  classification},  includes  classic  long  text
-  classification  and  short  text  classification  in  this  scenario.  Besides
-  traditional  machine  learning  models  like  SVM \cite{suykens1999least},  
-  boosting  tree \cite{tu2005probabilistic},  many work
-  \cite{wen2016network}  choose  neural  network  such  as  convolutional neural
-  networks (CNNs) \cite{kim2014convolutional,zhang2015character,conneau2016very}
-  and       long       short       term       memory       networks      (LSTMs)
-  \cite{mousa2017contextual,liu2016recurrent}   to   accomplish   the   task  of
-  extracting  semantic  feature from limited amount of words. Their common model
-  structure  is  adding  a  softmax classifier as the final layer and mapping to
-  labels.  Another  two  interesting lines of work, label-word joint models, and
-  joint  NER  and  classification  are  discussed  in  the related work section.
-  Afterwards,   pre-trained   language   models   on   large  corpus  like  BERT
-  \cite{devlin2018bert}  and  RoBERTa \cite{liu2019roberta} has been proven more
-  powerful  in  solving  many  NLP  tasks  including  short-text  classification
-  \cite{madabushi2020cost}.      Especially      for      few-shot     scenarios
-  \cite{yu2018diverse},     pre-trained     model    based    on    transformers
-  \cite{vaswani2017attention} tends to do more
-  help to reducing the negative effects brought by scarcity of training data.
-
-  The  second  one,  \emph{similarity model} is also called sentence-pair model.
-  Its  motivation  originates  from  the idea of Information Retrieval (IR) based
-  chatbot   \cite{jafarpour2010filter,   leuski2011npceditor}.   Having   a  Q-A
-  (Question-Answer)  pairs dataset and user query Q, the IR based conversational
-  system will look up in the Q-A dataset for the pair (Q', A') that best matches
-  query  Q  through  semantic  analysis  and  returns  A'  as  the  answer  to Q
-  \cite{mnasri2019recent}. In this way, sentence-pair model pre-trained on large
-  corpus  of  semantic  similarity  identification task can be applied for being
-  used  as  a  tool  to  identify  the class with highest semantic similarity to
-  customer's    query.    A    common    model    structure    of    pre-trained 
-  sentence-pair model is based on multiple cross-attention
-  mechanism  \cite{barkan2020scalable}. Due to
-  the   fact   that   many   experiment   results   have   shown   that  RoBERTa
-  \cite{liu2019roberta} is an improved version of BERT \cite{devlin2018bert}, and has achieved amazing
-  results  on  both  text  classification and sentence-pairs semantic similarity
-  tasks, we choose RoBERTa as an important baseline approach in this paper.
-
-  Despite  the  success  of  these two kinds of approaches, they still have some
-  limitations   in   task-specific  chatbot  scenario.  As  for  the  \emph{text
-  classification  model},  it  is  quite hard to use data augmentation method to
-  solve  the  data insufficiency challenge since the it is usually unfeasible to
-  get  large amount of domain-specific data when facing a new task. With respect
-  to  the  \emph{similarity model}, though we can obtain a large amount of data
-  from semantically  duplicate  sentence  pair identification domain for transfer
-  learning  \cite{sun2019fine},  it  is  still  quite  hard  to  perform well on
-  a new task-specific dataset,  since their objective losses are totally different.
-
-  The  above limitation motivates us to propose a joint system that is capable of
-  taking  advantages  from  both  classification model and similarity model. We
-  call  it  SFC,  short  for  similairty model fused with classification Model,
-  shown  in  Fig.  \ref{fig:framework}.  To  better train SFC, we further bring in
-  multi-task   learning   \cite{caruana1993multitask,collobert2008unified, liu2019multi}.  Our
-  basic  idea  came  from  two  stages. In the first stage, we use an auxiliary
-  model  to  select top-K most possible labels for a input. This model can be an
-  elastic search  \cite{divya2013elasticsearch}  or  a  text classification model
-  trained on current task-specific chatbot data. In the second stage, we build a
-  classification  model  whose  main modules are similarity models. Then, this
-  structure  derives two goals to train towards, the classification loss for our
-  application,  and the similarity loss for the main modules. When the two stages
-  are  independently  optimized,  we call \emph{two-stage SFC}. We further find,
-  the  the  quality  of  output  from  the  first  stage  might  limit the final
-  performance  of  system,  since  the  candidate  labels for each user query is
-  always  fixed  in  the  whole  multi-task  training  process. This observation
-  motivates  us  to  further  improve  the  two-stage SFC into a joint training,
-  called  \emph{joint  SFC}. In this way, the sentence pairs associated with the
-  top-K  classes  also  become dynamic, and the text classification model in the
-  first  stage  will also be further optimized to provide better top-K result by
-  the final training loss.
-
-  We summarize our contributions as follow:
-  \begin{enumerate}
-    \item We propose a novel joint system to makes full utilization of
-    the advantages from both text classification model and similarity model.
-
-    \item To  better  train such a system, we bring in multi-task training to obtain
-    reasonable performance.
-
-    \item Experiment  results  from 4 public and 1 private short-text classification
-    datasets,  show  that  our  proposed  SFC joint system can achieve significant
-    and consistent improvements over strong baselines, especially in the low resource settings.
-  \end{enumerate}
-
-  \begin{figure*}[t]
-    \begin{centering}
-      \includegraphics[scale=0.72]{picture/picture4} 
-      \par
-    \end{centering}
-    \caption{
-      \textbf{Network Structure of SFC:} two-stage SFC and joint-SFC are sharing
-      the  same  network  from  stage  1  and  stage 2, with the only difference
-      whether two stages being jointly trained.
-    }
-    \label{fig:framework}
-  \end{figure*}
-
-  \section{Related work}
-
-  Another  common  approach  is  text  classification  neural  network  based on
-  label-word     joint     embedding,    such    as    LEAM \cite{wang2018joint},
-  MTLE \cite{zhang2017multi}   and   EXAM \cite{du2019explicit}.   This   approach
-  involves  label  embedding when constructing the text-sequence representation.
-  Take  LEAM  as  an  example,  the  text classification model is implemented by
-  jointly    embedding    the    word    and    label   in   the   same   latent
-  space \cite{wang2018joint}. Afterwards, the text representation are constructed
-  based  on  text-label  compatibility through attention mechanism. In this way,
-  additional  sources  of  semantic  information  from class labels can be fully
-  leveraged, which is quite helpful especially under few-shot scenario.
-
-  As for \emph{label-word joint
-  embedding  approach},  it  poses  noticeable requirements on label information.
-  However,  in  our  cases,  since  we have large amount of class labels without
-  being well-defined for question answering chatbot, the only thing we can do is
-  to  choose  one  of the user utterance as the class label to represent the key
-  information  of  the  whole class. In this way, the label will become not only
-  prolix  but  also  biased,  which  will  bring  some  negative effect to label
-  embedding.
-
-  Another   line   of  interesting  work  is  the  joint  training  of  sentence
-  classification   and  NER  (todo:  reference).  If  both  the  city  and  date
-  information  are  recognized,  then  they  are good indicators that this query
-  might  be  booking  an  ticket. This work can also be combined in our proposed
-  framework.
-
-  \section{Methodology}
-  In  this section, we describe our proposed system, a similarity model fused with
-  a classification  model (SFC). We propose two approaches to implement this idea,
-  two-stage SFC, and its more compact version joint SFC.
-
-  \subsection{Two-stage SFC}
-
-  Two-stage   SFC  is  composed  with  two  independent stages  in  charge of
-  different  jobs.
-
-  \subsubsection*{
-    Stage 1: classification model for providing top-K candidate class labels
-  } 
-  We  can  use any auxiliary text classification model or tool,
-  such as Term Frequency-Inverse Document Frequency (TF-IDF)retrieval, to
-  provide  top-K  most  related  class  labels. These selected class labels will
-  later  be  used to sample sentence pairs of both positive samples and negative
-  samples  for  stage  2.
-
-  In  this  work,  we  choose pretrained models to fine tune on our data.
-  Due to the excellent performance of RoBERTa in this task, compared to other pretrained
-  models, we use RoBERTa as the encoder of classification model in our setting.
-
-  Given   a   data   point   $x_{i}$  with  class  label  $y_{i}$  from  dataset
-  $\mathcal{D}$, we take the final hidden state $h_{i}$ of the first token [CLS]
-  encoded  by  RoBERTa  as the representation for the whole sequence of $x_{i}$.
-  Then  a linear layer is followed to output probabilistic distribution of class
-  labels,  $softmax(W^Ch_{i}+b^C)=softmax({\Phi}^C_{i})$,  where $W^C$ and $b^C$
-  are  trainable  parameters.  Then, the loss in stage 1 classification model is
-  shown in Equ. \ref{eq:classification_loss},
-
-  \begin{equation}
-    \begin{aligned}
-      \mathcal{L}^{C}&=\frac{1}{N}\sum_{i=1}^{N}-log(\frac{exp(\varPhi_{i,y_{i}}^C)}{\sum_{j=1}^{C}exp(\varPhi_{i,j}^C)}) \\
-      \label{eq:classification_loss}
-    \end{aligned}
-  \end{equation}
-
-  \subsubsection*{
-    Stage 2: sentence-pair similarity model based classification with multi-task
-    learning
-  }
-  We  continue choosing RoBERTa as the main module in this stage that identifies
-  the class label with strongest semantic similarity to the user input sentence.
-
-  Suppose  we have a training dataset $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$ of
-  $N$  data  points,  in  which $x_{i}$ is the user input query and $y_{i}$ is a
-  single  class label from a class label set of $C$ classes in total. We 
-  generate            a sentence            pair            dataset
-  $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$ from $\mathcal{D}$,   where   $(x,   x')_{j}$  is
-  a pair of two history queries \footnote{For simplicity, we use query
-  to denote a user's question or a response.}, and $l_{j}\in\{0, 1\}$ denotes the
-  similarity label that only the ones from the same class label are considered
-  similar. The size of $\mathcal{D'}$  would be up to $O(N^2)$ if no any
-  sampling strategy is used.  This is quite time-consuming  for the  training
-  in stage 2 because $N$ can be several hundreds or thousands even under 
-  few shot setting in task-specific chatbot scenario.
-
-  Therefore,  we  adopt  the idea of adversarial negative sampling strategy from
-  the  work  \cite{bamler2020extreme}.  The  key  idea is to train with negative
-  samples  that  are hard to be distinguished from positive samples. Now suppose
-  we  have  a  user  input query $x_{i}$ and top-K most related class labels set
-  $\mathcal{C'}=\{c'_{1},  \dots,  c'_{K}\}$ provided by auxiliary model or tool
-  in  stage  1, where $K$ is a hyperparameter to control candidate class number,
-  we  apply  the  adversarial  negative sampling strategy into our sentence pair
-  sampling process by the following two steps:
-
-  The  first step is \emph{positive sentence pair sampling}. During the training
-  process,  we  first make sure the ground truth class label $y_{i}$ for $x_{i}$
-  is  within  the  candidate  class  label  set  $\mathcal{C'}$. If $y_{i}\notin
-  \mathcal{C'}$,  we  manually  add  $y_{i}$  into  $\mathcal{C'}$  by replacing
-  $c'_{K}$  with  $y_{i}$, since $c'_{K}$ is the least promising candidate label
-  according  to  the  auxiliary  model  in stage 1. Afterwards, we will randomly
-  sample  $P$ sentences $\{x'_{1}, \dots, x'_{P}\}$ with the same class label as
-  $y_{i}$  from  dataset  $\mathcal{D}$  to  form the set of sentence pairs with
-  positive  label  $\mathcal{P'}_{i}=\{[(x_{i},  x'_{1}),  1],  \dots,  [(x_{i},
-  x'_{P}),  1]\}$,  where $P$ is also a hyperparameter set to control the number
-  of sentences we should sample from each class.
-
-  \begin{table*}
-    \begin{centering}
-      \scalebox{0.9}{
-        \begin{tabular}{|c|c|c|c|c|c|}
-          \hline 
-          \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} &
-          \textbf{\#Training Samples} & \textbf{\#Samples/Class} & \textbf{Experimental Settings}\tabularnewline
-          \hline 
-          ITG & FAQ chatbot & 228 & 3938 & 17 & 3-fold\tabularnewline
-          \hline 
-          Amazon-670k & Product review & 250 & 1942 & 8 & 3-fold\tabularnewline
-          \hline 
-          HWU64 & intention detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
-          \hline 
-          CLINC150 & intention detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
-          \hline 
-          BANKING77 & intention detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
-          \hline 
-        \end{tabular}
-      }
-      \par
-    \end{centering}
-    \caption{Statistics for all datasets and few shot settings.}
-
-    \label{tbe:dataset statistic}
-  \end{table*}
-
-  The  second  step  is  \emph{negative sentence pair sampling}: As for negative
-  sentence  pairs,  we will also randomly sample $P$ sentences for each class in
-  the negative candidate class label set $\mathcal{C'}\backslash \{y_{i}\}$. The
-  class  labels  in  $\mathcal{C'}\backslash  \{y_{i}\}$  are  the  set  of most
-  confusing  class  labels comparing to the ground truth ${y_{i}}$, so we assume
-  that  the  sentence  pairs  with  negative  label  grouped by user input query
-  $x_{i}$  and sentences with class labels in $\mathcal{C'}\backslash \{y_{i}\}$
-  are  strong  adversarial  negative  samples for sentence-pair similarity model
-  that  can  help  enhance  the training speed and performance. According to the
-  same  method  as  positive  sentence  pair  sampling, we can obtain the set of
-  sentence  pairs  with  negative label as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{1}),
-  0], ..., [(x_{i}, x'_{P\cdot K}), 0]\}$
-
-  In  this way, we generate the sentence pair dataset $\mathcal{D'}$ for stage 2
-  based  on  the  top-K  class  label  set $\mathcal{C'}$ provided by stage 1 as
-  $\mathcal{D'}=\{\mathcal{P'}_{i}\cup  \mathcal{N'}_{i}\}_{i=1}^{N}$,  in which
-  we have $M=N\cdot K\cdot P$ data points of sentence pairs in total.
-
-  Before starting to fine-tune our sentence-pair model on task-specific dataset,
-  we  first  fine-tune  RoBERTa  on  Quora  dataset  \cite{iyer2017first}, which
-  contains  404,290  potential  duplicate question pairs, for transfer learning.
-  This  is  also  the  merit of similarity based model, as labeled task-specific
-  classification  data  is  hard  to  acquire,  yet  general sentence pairs with
-  similar semantics can be much easier to acquire.
-
-  \subsubsection*{Multi-task based training}
-  We   continue  to  do  multi-task  training  on  sentence-pair  dataset
-  $\mathcal{D'}$ sampled from the top-K candidate class labels provided by stage
-  1. In stage 2, we have two tasks tuning our system.
-
-  The first task is \emph{regular sentence-pair similarity task}.
-  For  sentence  pair semantic similarity task, given a data point $(x, x')_{i}$
-  with       similarity       label       $l_{i}$       from       data      set
-  $\mathcal{D'}=\{[(x,x')_{i},l_{i}]\}_{i=1}^{M}$,   Roberta   takes  the  final
-  hidden  state  $h_{i}$  of the first token [CLS] as the representation for the
-  sequence of packed sentence pair $(x, x')_{i}$. Let's suppose we have a linear
-  layer  as  ${\Phi}^S_{i}=W^Sh_{i}+b^S$,  where  $W^S$  and $b^S$ are trainable
-  parameters,  and  the probability score for $(x, x')_{i}$ can be calculated as
-  $p^S_{i}=softmax({\Phi}^S_{i})$.
-
-  Due  to  the  fact that sentence pairs within the same class is much fewer than
-  that from  different  classes,  the  dataset  $\mathcal{D'}$  is
-  quite imbalanced.  Therefore, we will accommodate a weight variable $w^S = [K-1, 1]$
-  to  the  loss  to eliminate the bias brought by data imbalance, shown in Equ.
-  \ref{eq:similarity_loss}.
-
-  \begin{equation}
-    \begin{aligned}
-      \mathcal{L}^{S}&=\frac{1}{M}\sum_{i=1}^{M}-w^S_{l_i}\cdot log(\frac{exp(\varPhi_{i,l_{i}}^S)}{\sum_{j=0}^{1}exp(\varPhi_{i,j}^S)}) \\
-      \label{eq:similarity_loss}
-    \end{aligned}
-  \end{equation}
-
-  The  second  task  is  \emph{classification  on  top-K classes}. As minimizing
-  similarity  loss  is  not  our  final goal in the intention classification, we
-  bring  back  classification  loss again. In this task, the network is based on
-  sentence  pair  similarity  modules.  The  only  difference  is  that we add a
-  task-specific  average  pooling  layer,  shown  in Fig. \ref{fig:framework} to
-  accomplish the classification task based on sentence-pair model.
-
-  We  already  know  that the size of ${\Phi}^S$ in task 1 is $M\times 2=(N\cdot
-  K\cdot  P)\times  2$, where $N$ is the total number of data points in original
-  training  data $\mathcal{D}$, $K$ is a hyperparameter that controls the number
-  of   candidate   class  labels  provided  by  stage  1,  and  $P$  is  also  a
-  hyperparameter that controls the number of sentences we should randomly sample
-  from each candidate class labels. Now, for the average pooling layer, we first
-  reshape  ${\Phi}^S$  into  the  size  of $N\times K\times P\times 2$, and then
-  split  it  into  ${\Phi}^{K,pos}$  and ${\Phi}^{K,neg}$, and both of them will
-  have  the  size  of  $N\times  K\times  P$.  In this way, ${\Phi}^{K,pos}$ can
-  represent  the  level  of  similarity  for each sentence pair, and in the mean
-  time,  ${\Phi}^{K,neg}$  can  represent  the  level  of dissimilarity for each
-  sentence  pair. Then, we can do average pooling for each candidate class among
-  the  top-K  classes  as  shown  in  Equ.  \ref{eq:average  pooling}.
-
-  \begin{align}
-    {\xi}_{i,j}^{K,pos} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,pos} \ \ \ \ \ \ \ 
-    {\xi}_{i,j}^{K,neg} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,neg}
-    \label{eq:average pooling}
-  \end{align}
-
-  With  the  average pooling result ${\xi}^{K,pos}$ and ${\xi}^{K,neg}$, we also
-  generate   a   top-K   class   label   $l^{K}_i\in   [1,\dots,K]$   for   each
-  ${\xi}^{K,pos}_{i}$ and ${\xi}^{K,neg}_{i}$. The loss for top-K classification
-  task is shown in Equ. \ref{eq:top-k_classification_loss}. In Equ. \ref{eq: pos
-  top-k   loss}   and   Equ.   \ref{eq:   neg   top-k   loss},  the  first  term
-  $\xi_{i,l^{K}_{i}}^{K,pos}$  and  $\xi_{i,l^{K}_{i}}^{K,neg}$  encourage  high
-  level  of  similarity  and  low  level  of dissimilarity for prediction of the
-  correct label $l^{K}_i$ within the top-K candidate classes.
-
-  \begin{align}
-    \mathcal{L}^{K} = \frac{1}{N}\sum_{i=1}^{N}(\mathcal{L}^{K,pos}_{i} - \mathcal{L}^{K,neg}_{i})
-    \label{eq:top-k_classification_loss}
-  \end{align}
-  where
-
-  \begin{equation}
-    \begin{aligned}
-      \mathcal{L}^{K,pos}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,pos})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,pos})})
-      \label{eq: pos top-k loss}
-    \end{aligned}
-  \end{equation}
-
-  \begin{equation}
-    \begin{aligned}
-      \mathcal{L}^{K,neg}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,neg})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,neg})}) \\
-      \label{eq: neg top-k loss}
-    \end{aligned}
-  \end{equation}
-
-  Finally,  the  overall  loss  function for multi-task learning in stage 2 is
-  shown in Equ. \ref{eq:two-stage_SFC_loss}. The training objective of stage 2 is
-  to  minimize  the  weighted  sum  of task-specific losses. Here $\alpha_S$ and
-  $\alpha_K$  are  weights  of  task  1  and  task  2  respectively.
-
-  \begin{align}
-    \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K
-    \label{eq:two-stage_SFC_loss}
-  \end{align}
-
-  \begin{table*}
-    \begin{centering}
-      \scalebox{0.55}{
-        \begin{tabular}{|c|cccccc|cccccc|cccccc|c|c|}
-          \hline 
-          \multicolumn{1}{|c|}{\multirow{2}*{\textbf{Models}} }& \multicolumn{6}{c|}{\textbf{CLINC150}}& \multicolumn{6}{c|}{\textbf{BANKING77}}& \multicolumn{6}{c|}{\textbf{HWU64}}& \ \ \ \textbf{ITG} \ \ \ & \textbf{Amazon-670k}\tabularnewline
-          \cline{2-21}
-          \multicolumn{1}{|c|}{} & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$
-          & $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & $\textbf{5}$ &
-          $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{30}$ &
-          $\textbf{50}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ &
-          $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & \textbf{3-fold} &
-          \textbf{3-fold}\tabularnewline
-          \hline
-          TextCNN & \multirow{2}*{$0.5318$} & \multirow{2}*{$0.6963$} & \multirow{2}*{$0.7609$} & \multirow{2}*{$0.8142$} & \multirow{2}*{$0.8526$} & \multirow{2}*{$0.8867$} & \multirow{2}*{$0.4408$} & \multirow{2}*{$0.6436$} & \multirow{2}*{$0.7366$} & \multirow{2}*{$0.7918$} & \multirow{2}*{$0.8228$} & \multirow{2}*{$0.8619$} & \multirow{2}*{$0.3112$} & \multirow{2}*{$0.4007$} & \multirow{2}*{$0.4823$} & \multirow{2}*{$0.5272$} & \multirow{2}*{$0.5782$} & \multirow{2}*{$0.6262$} & \multirow{2}*{$0.6624$} & \multirow{2}*{$0.4401$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          LEAM & \multirow{2}*{$0.7514$} & \multirow{2}*{$0.8203$} & \multirow{2}*{$0.8612$} & \multirow{2}*{$0.8802$} & \multirow{2}*{$0.9010$} & \multirow{2}*{$0.9180$} & \multirow{2}*{$0.5422$} & \multirow{2}*{$0.7812$} & \multirow{2}*{$0.8129$} & \multirow{2}*{$0.8280$} & \multirow{2}*{$0.8610$} & \multirow{2}*{$0.8727$} & \multirow{2}*{$0.4545$} & \multirow{2}*{$0.5554$} & \multirow{2}*{$0.5936$} & \multirow{2}*{$0.6599$} & \multirow{2}*{$0.6855$} & \multirow{2}*{$0.7046$} & \multirow{2}*{$0.7086$} & \multirow{2}*{$0.6091$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-          BERT-large & \multirow{2}*{$0.8080$} & \multirow{2}*{$0.8904$} & \multirow{2}*{$0.9265$} & \multirow{2}*{$0.9334$} & \multirow{2}*{$0.9497$} & \multirow{2}*{$0.9595$} & \multirow{2}*{$0.5780$} & \multirow{2}*{$0.8004$} & \multirow{2}*{$0.8518$} & \multirow{2}*{$0.8827$} & \multirow{2}*{$0.8858$} & \multirow{2}*{$0.8982$} & \multirow{2}*{$0.4711$} & \multirow{2}*{$0.5963$} & \multirow{2}*{$0.6342$} & \multirow{2}*{$0.7010$} & \multirow{2}*{$0.7117$} & \multirow{2}*{$0.7424$} & \multirow{2}*{$0.7485$} & \multirow{2}*{$0.6658$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          ALBERT-xxlarge & \multirow{2}*{$0.8497$} & \multirow{2}*{$0.9008$} & \multirow{2}*{$0.9296$} & \multirow{2}*{$0.9297$} & \multirow{2}*{$0.9466$} & \multirow{2}*{$0.9578$} & \multirow{2}*{$0.5549$} & \multirow{2}*{$0.7981$} & \multirow{2}*{$0.8231$} & \multirow{2}*{$0.8530$} & \multirow{2}*{$0.8571$} & \multirow{2}*{$0.9096$} & \multirow{2}*{$0.4879$} & \multirow{2}*{$0.6116$} & \multirow{2}*{$0.6135$} & \multirow{2}*{$0.6996$} & \multirow{2}*{$0.7094$} & \multirow{2}*{$0.7376$} & \multirow{2}*{$0.7253$} & \multirow{2}*{$0.6893$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          RoBERTa-base & \multirow{2}*{$0.8732$} & \multirow{2}*{$0.9254$} & \multirow{2}*{$0.9363$} & \multirow{2}*{$0.9482$} & \multirow{2}*{$0.9558$} & \multirow{2}*{$0.9637$} & \multirow{2}*{$0.7305$} & \multirow{2}*{$0.8654$} & \multirow{2}*{$0.8808$} & \multirow{2}*{$0.9080$} & \multirow{2}*{$0.9061$} & \multirow{2}*{$0.9293$} & \multirow{2}*{$0.5831$} & \multirow{2}*{$0.6790$} & \multirow{2}*{$0.7064$} & \multirow{2}*{$0.7100$} & \multirow{2}*{$0.7320$} & \multirow{2}*{$0.7472$} & \multirow{2}*{$0.7734$} & \multirow{2}*{$0.6708$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          RoBERTa-large & \multirow{2}*{$\textbf{0.8974}$} &
-          \multirow{2}*{$\textbf{0.9372}$} & \multirow{2}*{$\textbf{0.9508}$} &
-          \multirow{2}*{$\textbf{0.9584}$} & \multirow{2}*{$\textbf{0.9621}$} & 
-          \multirow{2}*{$\textbf{0.9733}$} & \multirow{2}*{$\textbf{0.7690}$} & 
-          \multirow{2}*{$\textbf{0.8728}$} & \multirow{2}*{$\textbf{0.8966}$} & 
-          \multirow{2}*{$\textbf{0.9099}$} & \multirow{2}*{$\textbf{0.9227}$} & 
-          \multirow{2}*{$\textbf{0.9313}$} & \multirow{2}*{$\textbf{0.6044}$} & 
-          \multirow{2}*{$\textbf{0.7002}$} & \multirow{2}*{$\textbf{0.7129}$} & 
-          \multirow{2}*{$\textbf{0.7436}$} & \multirow{2}*{$\textbf{0.7493}$} & 
-          \multirow{2}*{$\textbf{0.7678}$} & \multirow{2}*{$\textbf{0.7990}$} & 
-          \multirow{2}*{$\textbf{0.7156}$}\tabularnewline
-          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-          RoBERTa-large & \multirow{2}*{$0.8266$} & \multirow{2}*{$0.8861$} & \multirow{2}*{$0.9023$} & \multirow{2}*{$0.9084$} & \multirow{2}*{$0.9090$} & \multirow{2}*{$0.9407$} & \multirow{2}*{$0.757$} & \multirow{2}*{$0.8476$} & \multirow{2}*{$0.8614$} & \multirow{2}*{$0.8743$} & \multirow{2}*{$0.8749$} & \multirow{2}*{$0.8980$} & \multirow{2}*{$0.5425$} & \multirow{2}*{$0.6164$} & \multirow{2}*{$0.6503$} & \multirow{2}*{$0.6729$} & \multirow{2}*{$0.6947$} & \multirow{2}*{$0.7231$} & \multirow{2}*{$0.7418$} & \multirow{2}*{$0.6362$}\tabularnewline
-          (similarity) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-          2-stage SFC & \multirow{2}*{$0.8979$} & \multirow{2}*{$0.9457$} & \multirow{2}*{$0.9517$} & \multirow{2}*{$0.9591$} & \multirow{2}*{$0.9610$} & \multirow{2}*{$0.9664$} & \multirow{2}*{$0.7975$} & \multirow{2}*{$0.8818$} & \multirow{2}*{$0.8962$} & \multirow{2}*{$0.9109$} & \multirow{2}*{$0.9187$} & \multirow{2}*{$0.9198$} & \multirow{2}*{$0.6477$} & \multirow{2}*{$0.7055$} & \multirow{2}*{$0.7200$} & \multirow{2}*{$0.7232$} & \multirow{2}*{$0.7484$} & \multirow{2}*{$0.7653$} & \multirow{2}*{$0.7972$} & \multirow{2}*{$0.7189$}\tabularnewline
-          (task1) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          2-stage SFC & \multirow{2}*{$0.9162$} & \multirow{2}*{$0.9424$} & \multirow{2}*{$0.9530$} & \multirow{2}*{$0.9617$} & \multirow{2}*{$0.9633$} & \multirow{2}*{$0.9690$} & \multirow{2}*{$0.7997$} & \multirow{2}*{$0.8823$} & \multirow{2}*{$0.8945$} & \multirow{2}*{$0.9123$} & \multirow{2}*{$0.9236$} & \multirow{2}*{$0.9317$} & \multirow{2}*{$0.6498$} & \multirow{2}*{$0.6980$} & \multirow{2}*{$0.7202$} & \multirow{2}*{$0.7358$} & \multirow{2}*{$0.7498$} & \multirow{2}*{$0.7657$} & \multirow{2}*{$0.8020$} & \multirow{2}*{$0.7311$}\tabularnewline
-          (task2) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          2-stage SFC & \multirow{2}*{$0.9167$} & \multirow{2}*{$0.9456$} & \multirow{2}*{$0.9571$} & \multirow{2}*{$0.9638$} & \multirow{2}*{$0.9658$} & \multirow{2}*{$0.9753$} & \multirow{2}*{$0.8135$} & \multirow{2}*{$0.8854$} & \multirow{2}*{$0.8931$} & \multirow{2}*{$0.9192$} & \multirow{2}*{$0.9257$} & \multirow{2}*{$0.9339$} & \multirow{2}*{$0.6525$} & \multirow{2}*{$0.7092$} & \multirow{2}*{$0.7168$} & \multirow{2}*{$0.7476$} & \multirow{2}*{$0.7519$} & \multirow{2}*{$0.7696$} & \multirow{2}*{$\textbf{0.8124}$} & \multirow{2}*{$0.7364$}\tabularnewline
-          (task1 + task2) & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-          \multirow{2}*{Joint SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.9669}$} & \multirow{2}*{$\textbf{0.9712}$} & \multirow{2}*{$\textbf{0.9821}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.9323}$} & \multirow{2}*{$\textbf{0.9463}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$\textbf{0.7593}$} & \multirow{2}*{$\textbf{0.7772}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline
-          & & & & & & & & & & & & & & & & & & & &\tabularnewline
-          \hline
-        \end{tabular}
-      }
-      \par
-    \end{centering}
-    \caption{
-      F1 scores  on  five  task-specific  datasets text classification in chatbot
-      under low resource. For ITG, we keep the full dataset. For Amazon-670k, we
-      randomly  sampled  250  classes  with  training sample numbers within 5-15
-      samples  per  class.  For  CLINC150,  BANKING77,  HWU64, we set up various
-      few-shot  settings  (5/10/15/20/30/50 samples per class) while keeping the
-      test  set to be fixed. The highest scores among all the baseline models and SFC variants for each data setting are both marked
-      in bold.
-    }
-    \label{tbe:table2}
-  \end{table*}
-
-  \subsection{Joint SFC}
-  In  two-stage  SFC,  Stage  1  and  stage 2 are separate that there is no deep
-  interaction  with each other during training. In this case, the performance of
-  stage  1  may  limit  the potential of stage 2; meanwhile, stage 2 also cannot
-  give  training feedback back to stage 1 for fine-tuning. Therefore, to further
-  improve  the  overall performance of SFC, we proposed a joint model structure,
-  shown in Fig. \ref{fig:framework}.
-
-  In  joint  SFC,  classification  model is being placed in lower layer level to
-  dynamically  provide  top-K  candidate  class  labels  for  the  sentence-pair
-  similarity  model  placed in higher layer level through a top-K pooling layer.
-  In  this way, classification model and similarity model can be merged into one
-  single  joint-model  for  multi-task training with sentence pairs sampled from
-  varying  candidate  class  labels,  thus  avoiding the limitation brought by 2
-  separate stage structure.
-
-  There  are 3 tasks in total during the training process of joint SFC, shown in
-  Fig. \ref{fig:framework}, and the overall loss is also the weighted sum of all
-  the   task-specific  losses,  shown  in  Equ.  \ref{eq:joint_SFC_loss}.  Here,
-  $\alpha_S$,  $\alpha_K$  and  $\alpha_C$  represent  the  weights  for  task 1
-  sentence-pair  similarity  in  Equ.  \ref{eq:similarity_loss},  task  2  top-K
-  classification  in Equ. \ref{eq:top-k_classification_loss}, and task 3 general
-  single       sentence       classification      respectively      in      Equ.
-  \ref{eq:classification_loss}.
-
-  \begin{align}
-    \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K + \alpha_C \mathcal{L}^C
-    \label{eq:joint_SFC_loss}
-  \end{align}
-
-  \section{Experiments}
-  \label{sec:exp}
-
-  \subsection{Datasets}
-  Our experiments aim to study the short text classification in the low-resource
-  environment  popular  in  the  task-specific conversational chatbot application.
-  Hence we choose and configure set datasets to serve this study. Different from
-  the  datasets from other short text classification research, such as semantics
-  classification  with  very  limited  semantics labels and relatively longer
-  input,   the   datasets  adopted  in  our  experiments  are  typically  having
-  comparatively  large  number  of  class labels, ranging from several dozens to
-  hundreds,  and  each  class  label  is  associated  with  a handful of labeled
-  queries with each  query  being usually  one  sentence. Table \ref{tbe:dataset
-  statistic} displays their statistics.  All settings of four public datasets would 
-  be released to github soon.
-
-  \begin{enumerate}
-    \item \emph{ITG},  is  a proprietory FAQ dataset from real-world
-    chatbot  project,  which is composed of question and answer pairs about online
-    English teaching. It contains 3,938 sample questions for 228 class labels, and
-    each class label corresponds to a unique answer.
-
-    \item \emph{Amazon-670K}, is a customer product review dataset for
-    text  classification  task  from  the  extreme  classification repository. The
-    complete  dataset  contains 670,091 class labels, 285,176 training samples and
-    150,875   testing   samples   \cite{bhatia2016extreme}.  As  each  sample  may
-    correspond  to  multiple  class labels, we keep only the first one. We further
-    filter  out the class labels that each one is associated with 5 to 15 samples,
-    or  reviews,  to  mimic  the  chatbot scenario. From them, we sample 250 class
-    labels as well as their samples to form a subset with 1,942 + 716 samples.
-
-    \item \emph{HWU64}, is a intention detection dataset designed for
-    home  robot  scenario \cite{liu2019benchmarking}. It aims at the specific task
-    of  capturing  the  intention  for  different  user requests to home robot and
-    finding  the corresponding answer. The raw dataset contains 25,716 data points
-    for 64 class labels through crowdsourcing.
-
-    \item \emph{CLINC150},  is  a dataset designed for task-oriented
-    systems  with  23,700 queries that are short and unstructured for 150 intents,
-    in    the    same   style   made   by   real   users   through   crowdsourcing
-    \cite{larson2019evaluation}.
-
-    \item \emph{BANKING77}, is a intention detection dataset for bank
-    customer  services.  The  raw dataset contains 13,084 data points for 77 class
-    labels \cite{casanueva2020efficient}.
-  \end{enumerate}
-
-  Regarding  the first two datasets, we conduct 3-fold cross validation experiments
-  that   70   percent   as  training,  15  percent  as  validation  and  testing
-  respectively,  and  report  the  averaged  testing results. Regarding the last
-  three datasets, we conduct experiments using a sampling method similar to that
-  in   \cite{casanueva2020efficient}   yet  in  a  more  sophisticated  few-shot
-  settings.  We  fix  a  test  data for each one, and examine their performances
-  using  5,  10,  15,  20,  30,  and 50 samples per class label respectively for
-  training.  This  is important, as in practice, a task-specific chatbot usually
-  starts  with  merely  a  handful of labeled data available in the early stage.
-  Besides,  in  the  active  learning framework, building an effective auxiliary
-  system  with limited resource is also quite important to help developers label
-  data more efficiently.
-
-  \subsection{Baselines}
-  We choose three kinds of system to construct our baselines.
-
-  \begin{enumerate}
-    \item \emph{Pretrained model based classification system}, which consists of
-    BERT \cite{devlin2018bert},  RoBERTa \cite{liu2019roberta},  and  ALBERT  \cite{lan2019albert}  based.  These pretrained
-    models  are  practically  proven  to  achieve  outstanding  performances  in
-    classification task and other NLP tasks.
-
-    \item   \emph{Non-pretrained   model  based  classification  system},  which
-    consists  of  a typical CNN based TextCNN \cite{kim2014convolutional}, and a
-    label-embedding based LEAM \cite{wang2018joint}. Regarding TextCNN, the
-    model is based on output from RoBERTa tokenization, and the kernels are set
-    as 1, 2, 3, 4, 5. Regarding LEAM, a literal class label is required, which
-    is available only in HWU64, CLINC150, BANKING77. Thus, for other two
-    datasets, we have to use its class number instead.  Empirically,
-    a  non-pretrained  model  based  system  are  not  performing  as  well as a
-    pretrained  models  based,  if  both is applicable in some task. Our listing
-    these  non-pretrained model based systems here is to provide a comprehensive
-    performance comparison on our datasets.
-
-    \item   \emph{Pre-trained   model   based   similarity   model}.  We  choose
-    RoBERTa-large  as  our  fundamental  module as our SFC systems are based on
-    RoBERTa  too, and RoBERTa is empirically more effective than other pretrained
-    models  in  the  short  text  classification  task  in  our  experiments. In
-    inference,  we  use  an  elastic search to find a set of potential candidate
-    labels for the similarity model, to guarantee a reasonable running time.
-  \end{enumerate}
-
-  Our SFC systems include two-stage SFC with ablation, trained with two tasks
-  separately and both, and joint SFC with all three tasks.
-
-  \subsection{Implementation Details}
-  For  our  SFC  systems,  we  use RoBERTa-large as the pretrained model for both
-  classification  task  and  sentence-pair similarity task. We fine-tune
-  our  SFC  system  on  our datasets with max sequence length of 128,
-  learning  rate  of 1.5e-5 for RoBERTa-large pretrained model and learning rate
-  of  5e-4  for  task-specific  layer  with polynomial decay and Adam optimizer.
-  Besides,  we  set  the  max number of the epoch to 100 and save the best model on
-  validation  set based on testing result in weighted F1 score
-  \footnote{In the multi-class and multi-label case, this is the average of the
-  F1 score of each class with weighting depending on the numbers in each class.}.
-  We report the F1 score as the main evaluation measure for all experiments.
-
-  In two-stage SFC, in equ. \ref{eq:two-stage_SFC_loss} the weights of two tasks
-  are  set  as  $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting. The reason
-  for  giving  task  2 relatively more weights is that according to the ablation
-  experiments  we  did  in Section \ref{sec:exp}, task 2 contributes more to the
-  overall  performance.  In  joint  SFC,  in  equ.  \ref{eq:joint_SFC_loss}, the
-  weights  of  three  tasks  are  set  as  $\alpha_S=0.25$,  $\alpha_K=0.25$ and
-  $\alpha_C=0.5$  in  our setting. Overall, the task weights are less sensitive
-  in Joint SFC than in two-stage SFC.
-
-  For  the  experiments  in  Table  \ref{tbe:table2},  we  empirically  set  the
-  hyperparameter  to  be  $K=5$  and  $P=10$  for  all  SFC  variants.  In Table
-  \ref{tbe:table3},  we  conduct extensive experiments to see the performance of
-  SFC system under various hyperparameter settings.
-
-  \subsection{Result Analysis}
-  All  results  in  F1  score  on  the  five  datasets with different models and
-  configurations are showed in Table \ref{tbe:table2}.
-
-  The performance of each model is measured in F1 score on the fixed
-  test  set  for  each  dataset.  
-  Overall,  two-stage  SFC systems in multi-task training deliver  moderate 
-  improvements  over  corresponding baselines, and joint SFC deliver more
-  significant and consistent improvements over the best baseline, RoBERTa based
-  classification. In following content, we dive into more details.
-
-  \subsubsection*{Are multi-task and joint training working?} 
-  First, we compare the four  SFC  variants to analyze the improvement
-  brought  by  multi-task  and  joint-model  structure.
-
-  \begin{table}
-    \begin{centering}
-      \begin{tabular}{|c|c|c|c|c|}
-        \hline
-        F1 score & Two-stage SFC & Joint SFC & Gap & \tabularnewline
-        \hline
-        top-1 accuracy  & \textbf{81.50} & 81.07 & -0.47 & \tabularnewline
-        top-5 accuracy & 94.01 & \textbf{94.30} & +0.29 & \tabularnewline
-        \hline
-      \end{tabular}
-      \par
-    \end{centering}
-    \caption{The average classification accuracy in percentage in stage 1 on all five dataset.}
-    \label{tbe:top1_5_accuracy}
-  \end{table}
-
-  Comparing with training two-stage SFC with multi-task, training with only task
-  1,  namely the sentence pair similarity model, degrades by 0.8 percent
-  point  on average, and training with only task 2, namely the top-K based
-  classification  task,  degrades  by  0.45  percent  point  on  average.  These
-  degradation  indicates  multi-task training in two-stage SFC is helpful for the
-  system  performance.  Besides, task 2 plays a relatively more important role in
-  multi-task learning, and this aligns with their optimal weight settings.
-
-  Joint SFC consistently outperforms two-stage SFC with multi-task training  
-  on 5 diverse datasets by 0.95 percents  on  average. 
-  This observation supports the idea that the joint model
-  structure  can  alleviate  the  limitation  brought by the lack of interaction
-  between  two  stages.  In  following analysis, we will focus on the comparison
-  between joint SFC and the other baseline models.
-
-  \subsubsection*{Is  the  fusion of classification and similarity models
-  helpful?}  We  compare  joint SFC with classification and similarity based
-  baselines respectively.
-
-  \begin{table*}
-    \begin{centering}
-
-      \begin{tabular}{|c|c|c|c|c|c|c|}
-        \hline 
-        \multicolumn{1}{|c|}{\multirow{2}*{Dataset}}&\multicolumn{1}{c|}{\multirow{2}*{Model}}& $K=3$ & $K=5$ & $K=10$ & $K=15$ & $K=20$\tabularnewline
-        \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & $P=20$ & $P=10$ & $P=5$ & $P=4$ & $P=3$\tabularnewline
-        \hline
-        \multicolumn{1}{|c|}{\multirow{2}*{ITG}}& two-stage SFC & $0.8034$ & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
-        \cline{2-7}
-        \multicolumn{1}{|c|}{} & joint SFC & $0.7986$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7918$\tabularnewline
-        \hline
-        \multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& two-stage SFC & $0.7278$ & $0.7364$ & $0.7366$ & $0.7328$ & $0.7204$\tabularnewline
-        \cline{2-7}
-        \multicolumn{1}{|c|}{} & joint SFC & $0.7334$ & $0.7445$ & $0.7516$ & $0.7344$ & $0.7373$\tabularnewline
-        \hline
-      \end{tabular}
-      \par
-    \end{centering}
-    \caption{
-      We  show the performances of SFC from different settings of
-      hyperparameters, $K$  denoting the candidate class number from stage 1,
-      $P$ denoting the number of sampled sententence pair in stage 2. 
-    }
-    \label{tbe:table3}
-  \end{table*}
-
-  Regarding the  classification  models,  joint SFC
-  outperforms RoBERTa-large based, the strongest among all baselines, 
-  by 2.04 percent points on average F1 score over 5 datasets.  
-  Especially, ALBERT.xxlarge based is rather unstable  in this senario. Thus, 
-  we did multiple run with different settings and  report the  best  ones here. 
-  Comparatively,  RoBERTa  based is  the  most stable and has the best performance 
-  n almost all experiment settings.
-
-  Regarding  the  similarity  model,  as  analyzed  above,  we  only  choose the
-  RoBERTa-large based implementation as our baseline. Joint SFC achieves more improvement of
-  7.09  percent points  on average F1 score.
-
-  The above analysis illustrates that suitable fusing the two kinds of models
-  can take their advantages.
-
-  \subsubsection*{Does joint SFC improve the classification in stage 1?}
-  We  compare  the  top-1  prediction and top-5 candidate labels in stage 1 from
-  two-stage SFC and joint SFC in Table \ref{tbe:top1_5_accuracy}. We should note
-  that  two-stage  SFC  does not optimize the stage 1 model, which is a RoBERTa
-  based classification model.
-
-  The joint training does not improve the classification performance in stage 1,
-  measured  by  top-1  accuracy.  However,  it  improves  the  quality of top-5
-  candidate  class  labels.  It  can  be  explained that, a classification model
-  inherently optimizes the objective loss, 0-1 error of top-1 here; the sentence
-  pair similairity model in the joint SFC poses more positive effect in optimizing the 
-  candidate labels.
-
-  \subsubsection*{How does training sample size influence SFC?} 
-  We analyze the overall  improvement  trend  of  joint SFC under various few-shot
-  settings, and show results in Fig. \ref{fig:trend}.
-
-  Our main focus  is  to  study  chatbot  building  in common situation during real-world
-  application  where  only  a few sample sentences are available for each class.
-  The  experimental  results  for  the  3  diverse  intention detection datasets
-  (ClINC150,  BANKING77,  HWU64)  under  few-shot  settings, 5 to 50 samples per
-  class,  indicate that our proposed joint SFC can achieve 2.47 percents average
-  improvement   over  one  of  the  most  powerful  baseline  models,  which  is
-  RoBERTa-large  classification  model.  Moreover,  the  improvement  in F1 score
-  becomes  more  and  more prominent with the decrease of data sample number per
-  class.
-
-  \begin{figure}[t]
-    \begin{centering}
-      \includegraphics[scale=0.2]{picture/improvement_trend.jpg} 
-      \par
-    \end{centering}
-    \caption{
-      Improvements  from  Joint  SFC  over  RoBERTa  based  classification  with
-      different size of training data.
-    }
-    \label{fig:trend}
-  \end{figure}
-
-  Especially,  in the most extreme few-shot setting with only 5 training samples
-  per  class  our joint SFC achieves 4.97 percent points improvements on average
-  over  RoBERTa-large classification model. This observation indicates that SFC
-  is  especially  well-performed  when being applied during the initial stage of
-  building  task-specific  chatbot  system,  where the amount of data sample for
-  each class label is extremely scarce.
-
-  Furthermore,  our  proposed  joint  SFC can also achieve 2.04 percents average
-  improvement  over  RoBERTa-large classification model on all the data settings
-  including  the  ones  with  large  scale,  30  to  50  samples per class. This
-  indicates that joint SFC can still steadily outperforms pretrained model based
-  baseline even if the data size grows bigger. However, the improvement is still
-  more prominent when the data is scarce, which makes SFC an excellent model for
-  low-resource chatbot scenario.
-
-  \subsubsection*{How does joint SFC relate to the label  embedding based  LEAM?}
-  LEAM performs consistently better than TextCNN by a large margin in all
-  datasets. TextCNN is practically efficiently in task-specific chat
-  applications, and LEAM shows its power in modeling labeling information.
-
-  LEAM  does not perform as well as SFCs, since the first intuitive reason is it
-  does  not use pretrained model as encoding module; and another critical reason
-  is  in  task-specific  chat applications, it is common to have many intentions
-  that are close to some others with a minor difference, and it is hard and even
-  impossible  to  name  each  intention  with  a short clear name. One candidate
-  solution  is  setting  a most standard sample as the label of that class. When
-  using  non-pretrained  models  base  LEAM,  this is applicable. Yet when using
-  pretrained  model  based, as the all labels can be hundreds of thousands, then
-  this  can not be accommodated in a poplar 32 G Tesla V100 GPU. Actually, joint
-  SFC  can  be  kind  of  understood  as  a  generalization form of LEAM. In the
-  scenario when there is no clear class label, the relationship between a sample
-  and  a class label is implicitly encoded as that between a sample and another
-  sample  from  the  same  class, and this turns into a sentence pair similarity
-  model.
-
-  \subsubsection*{Settings  of  hyperparameters} 
-  Finally, we analyze the effect brought
-  by  different  settings  of  hyperparameters,  see  Table \ref{tbe:table3}.
-
-  We  conduct  experiments on 5 different settings of hyperparameters, which are
-  the  number of candidate class number $K$ and the number of sentence pairs $P$
-  for  each  class,  on  ITG  and Amazon-670K datasets to find the most suitable
-  setting  of  these  2 hyperparameters. We control the total number of sentence
-  pairs  sampled for each user query into about the same level of amount(50-60).
-  Through  analyzing the experimental results shown in Table \ref{tbe:table3}, we
-  find  that the best setting of hyperparameters might be different for datasets
-  of  different  data  size.  The  class label number of ITG and Amazon-670k are
-  similar  in  our  experimental setting, which is around 250. However the total
-  amount of data points of ITG is approximately 2 times larger than Amazon-670k.
-  Therefore,  the  setting of $K=5$ and $P=10$ is good enough for ITG since most
-  of  the  classes  contains  over 10 data points. However, for Amazon-670k, the
-  amount  of  data  sample  for  each  class  is  scarce, thus, we may need more
-  candidate  classes to sample enough effective sentence pairs for sentence-pair
-  model  layer  of  SFC.  In this way, the setting of $K=10$ and $P=5$ becomes a
-  good choice. However, in spite of the effect on evaluation performance brought
-  by different settings of hyperparameters, joint SFC still steadily outperforms
-  two-stage  SFC  by  0.41  percents  in  overall  average  F1 score  on  ITG and
-  Amazon-670k datasets.
-
-  In  conclusion, to the best of our knowledge, these experimental results place
-  joint  SFC as the best performing model on 5 diverse experimental datasets for
-  text   classification   task,   especially   when   it's   under  low-resource
-  task-specific conversational chatbot scenario.
+  \input{abstract}
+  \input{introduction}
+  \input{related_work}
+  \input{methodology}
+  \input{experiments}
+  \input{conclusion}
 

### 2020-09-10 chatbot_classification/aaai_2021/related_work.tex
Reorganized.   modified:   paper.tex
  new file:   abstract.tex
  new file:   introduction.tex
  new file:   related_work.tex
  new file:   methodology.tex
  new file:   experiments.tex
  new file:   conclusion.tex

--- 2020-08-30 chatbot_classification/aaai_2021/paper.ver_04.tex
@@
-\def\year{2021}\relax
-%File: formatting-instructions-latex-2021.tex
-%release 2021.1
-\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
-\usepackage{aaai21}  % DO NOT CHANGE THIS
-\usepackage{times}  % DO NOT CHANGE THIS
-\usepackage{helvet} % DO NOT CHANGE THIS
-\usepackage{courier}  % DO NOT CHANGE THIS
-\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
-\usepackage{graphicx} % DO NOT CHANGE THIS
-\urlstyle{rm} % DO NOT CHANGE THIS
-\def\UrlFont{\rm}  % DO NOT CHANGE THIS
-\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\frenchspacing  % DO NOT CHANGE THIS
-\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
-\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
-%\nocopyright
-%PDF Info Is REQUIRED.
-% For /Author, add all authors within the parentheses, separated by commas. No accents or commands.
-% For /Title, add Title in Mixed Case. No accents or commands. Retain the parentheses.
-\pdfinfo{
-  /Title (AAAI Press Formatting Instructions for Authors Using LaTeX -- A Guide)
-  /Author (AAAI Press Staff, Pater Patel Schneider, Sunil Issar, J. Scott Penberthy, George Ferguson, Hans Guesgen, Francisco Cruz, Marc Pujol-Gonzalez)
-  /TemplateVersion (2021.1)
-}
-
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{float}
-\usepackage{subfigure}
-\usepackage{spconf}
-
-\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
-%% Because html converters don't know tabularnewline
-\providecommand{\tabularnewline}{\\}
-%% A simple dot to overcome graphicx limitations
-\newcommand{\lyxdot}{.}
-
-\def\x{{\mathbf x}}
-\def\L{{\cal L}}
-
-\title{     
-  %SFC: Few-Shot Text Classification via Similarity Fused with Classification System
-  Joint training of classification model and similarity model for low-resource
-  text classification in chatbot
-}
-
-\author{
-  %Authors
-  % All authors must be in the same font size and format.
-  Written by AAAI Press Staff\textsuperscript{\rm 1}\thanks{With help from the AAAI Publications Committee.}\\
-  AAAI Style Contributions by Pater Patel Schneider,
-  Sunil Issar,  \\
-  J. Scott Penberthy,
-  George Ferguson,
-  Hans Guesgen,
-  Francisco Cruz,
-  Marc Pujol-Gonzalez
-  \\
-}
-\affiliations{
-  %Afiliations
-
-  \textsuperscript{\rm 1}Association for the Advancement of Artificial Intelligence\\
-  %If you have multiple authors and multiple affiliations
-  % use superscripts in text and roman font to identify them.
-  %For example,
-
-  % Sunil Issar, \textsuperscript{\rm 2}
-  % J. Scott Penberthy, \textsuperscript{\rm 3}
-  % George Ferguson,\textsuperscript{\rm 4}
-  % Hans Guesgen, \textsuperscript{\rm 5}.
-  % Note that the comma should be placed BEFORE the superscript for optimum readability
-
-  2275 East Bayshore Road, Suite 160\\
-  Palo Alto, California 94303\\
-  % email address must be in roman text type, not monospace or sans serif
-  publications21@aaai.org
-
-  % See more examples next
-}
-
-\begin{document}
-  \maketitle
-
-  \begin{abstract}
-    Task-specific  chatbot  systems has gained many important applications, such
-    as  Siri, Google home, customer service systems to allievaite human's labor.
-    In  this  kind  of  systems, one of the core problems is the accurate detection of
-    intention  of  a  user's input. It is then mapped into a predefined chatting
-    logic  graph,  and the chatbot can return reasonable answers easily. This is
-    the  main  difference from a free chatbot. The intention detection, assuming
-    only  one  intention  in  a  sentence,  can  be  modeled  as  a  short  text
-    classification  problem.  In  practice,  the  number  of  intentions  can be
-    hundreads of thousands, as opposed to quite limited in the tradiational text
-    classification  problem,  and  the  labeled  data  is not trivial to acquire
-    plenty,  generally  10  to 20 per intention. Then, how to train an efficient
-    model  in such a resource-intensive practical application in a new domain is
-    critical.  In  this  work, we propose a novel model, called similairty model
-    fused with classification Model (SFC), which combines a classification model
-    and  a  similairty  model,  and  borrows the power of multi-task training as
-    well.  We  conduct extensive experiments on 4 public and 1 private datasets.
-    The  experimental  results  show  that our new model outperforms very strong
-    baselines, BERT, RoBERTa and ALBERT based pretrained models by 2 percentages
-    in average accuracy.
-
-  \end{abstract}
-
-  \section{Introduction}
-  \label{sec:intro}
-
-  Task-specific  conversational  chatbot  \cite{wen2016network}  has been applied
-  into  many practical products. For example, it can share the working burden of
-  human  customer  service  agents  responsible  for  customers' questions about
-  certain  products  or services. Another example is the speech-based control in
-  devices  like  intelligent  speakers, such as Siri, Google home, Baidu Xiaodu,
-  and smart home equipments. Regardless of whether these conversations belong to
-  single-turn or multi-turn, an essential technique underlying the chatbot is to
-  identify  the  real  intention  behind  a  user's  question or reply. Then the
-  chatbot  is caple of conducting expected actions, text reply or accomplish some
-  operations.
-
-  It  is  a  challenging task due to some inherent properties. First,
-  a customer's  utterance  within  a conversation is usually quite short. Since it
-  does  not  contain  enough  information,  short  text \cite{song2014short} are
-  thought  to  be  more  ambiguous  compared to long texts such as paragraphs or
-  documents,  poseing  a  great challenge \cite{chen2019deep} for classification
-  task   \cite{phan2008learning,yan2009dynamic,hua2015short}.   Second,  in  the
-  initial  stage  of  building  a  chatbot  , it is often rather hard to collect
-  sufficient  labeled  data  to  train  a good model. Because developers have to
-  examine tons of real system logs for typical user's utterances, and then label
-  them  with expected intentions. Therefore, the key to building a task-specific
-  chatbot  with  high  performance  becomes  solving the challenge of short-text
-  classification   \cite{sriram2010short}   problem   under   few-shot   setting
-  \cite{yu2018diverse}.
-
-  Generally  there  are  two  kinds  of  approaches  to  address  this  problem,
-  classification model that directly maps an input into a most likely label, and
-  similarity  model  that searches a label whose associated data is most similar to
-  an input.
-
-  The   first  one,  \emph{text  classification},  includes  classic  long  text
-  classification  and  short  text  classification  in  this  scenario.  Besides
-  traditional  machine  learning  models  like  SVM,  boosting  tree,  many work
-  \cite{wen2016network}  choose  neural  network  such  as  convolutional neural
-  networks (CNNs) \cite{kim2014convolutional,zhang2015character,conneau2016very}
-  and       long       short       term       memory       networks      (LSTMs)
-  \cite{mousa2017contextual,liu2016recurrent}   to   accomplish   the   task  of
-  extracting  semantic  feature from limited amount of words. Their common model
-  structure  is  adding  a  softmax classifier as the final layer and mapping to
-  labels.  Another  two  interesting lines of work, label-word joint models, and
-  joint  NER  and  classification  are  discussed  in  the related work section.
-  Afterwards,   pre-trained   language   models   on   large  corpus  like  BERT
-  \cite{devlin2018bert}  and  RoBERTa \cite{liu2019roberta} has been proven more
-  powerful  in  solving  many  NLP  tasks  including  short-text  classification
-  \cite{madabushi2020cost}.      Especially      for      few-shot     scenarios
-  \cite{yu2018diverse},     pre-trained     model    based    on    transformers
-  \cite{vaswani2017attention}, shown in Fig. \ref{Fig.1.sub.1}, tends to do more
-  help to reducing the negative effects brought by scarcity of training data.
-
-  The  second  one,  \emph{similarity model} is also called sentence-pair model.
-  Its  motivation  originates  from  the idea of Information Retrival (IR) based
-  chatbot   \cite{jafarpour2010filter,   leuski2011npceditor}.   Having   a  Q-A
-  (Question-Answer)  pairs dataset and user query Q, the IR based conversational
-  system will look up in the Q-A dataset for the pair (Q', A') that best matches
-  query  Q  through  semantic  analysis  and  returns  A'  as  the  answer  to Q
-  \cite{mnasri2019recent}. In this way, sentence-pair model pre-trained on large
-  corpus  of  semantic  similarity  identification task can be applied for being
-  used  as  a  tool  to  identify  the class with highest semantic similarity to
-  customer's    query.    A    common    model    structure    of    pre-trained
-  \cite{devlin2018bert} sentence-pair model is based on multiple cross-attention
-  mechanism  \cite{barkan2020scalable},  shown in Fig. \ref{Fig.1.sub.2}. Due to
-  the   fact   that   many   experiment   results   have   shown   that  RoBERTa
-  \cite{liu2019roberta} is an improved version of BERT, and has achieved amazing
-  results  on  both  text  classification and sentence-pairs semantic similarity
-  tasks, we choose RoBERTa as an important baseline approach in this paper.
-
-  Despite  the  success  of  these two kinds of approaches, they still have some
-  limitations   in   task-specific  chatbot  scenario.  As  for  the  \emph{text
-  classification  model},  it  is  quite hard to use data augmentation method to
-  solve  the  data insufficiency challenge since the it is usually unfeasible to
-  get  large amount of domain-specific data when facing a new task. With respect
-  to  the  \emph{similarity model}, though we can obtain a large amount of data
-  from semantically  duplicate  sentence  pair identification domain for transfer
-  learning  \cite{sun2019fine},  it  is  still  quite  hard  to  perform well on
-  a new task-specific dataset,  since their objective losses are totally different.
-
-  The  above limitation motivates us to propose a joint system that is capble of
-  taking  advantagges  from  both  classification model and similarity model. We
-  calle  it  SFC,  short  for  similairty model fused with classification Model,
-  shown  in  Fig.  \ref{fig:ver.1.3}.  To  better train SFC, we further bring in
-  multi-task   learning   \cite{caruana1993multitask,collobert2008unified}.  Our
-  basic  idea  cames  from  two  stages. In the first stage, we use an auxiliary
-  model  to  select top-K most possible labels for a input. This model can be an
-  elasticsearch  \cite{divya2013elasticsearch}  or  a  text classification model
-  trained on current task-specific chatbot data. In the second stage, we build a
-  classification  model  whose  main modules are similarity models. Then, this
-  structure  derives two goals to train towards, the classification loss for our
-  application,  and the similarity loss for the main modules. When the two stages
-  are  independently  optimized,  we call \emph{two-stage SFC}. We further find,
-  the  the  quality  of  output  from  the  first  stage  might  limit the final
-  performance  of  system,  since  the  candidate  labels for each user query is
-  always  fixed  in  the  whole  multi-task  training  process. This observation
-  motivates  us  to  further  improve  the  two-stage SFC into a joint training,
-  called  \emph{joint  SFC}. In this way, the sentence pairs associated with the
-  top-K  classes  also  become dynamic, and the text classification model in the
-  first  stage  will also be further optimized to provide better top-K result by
-  the final training loss.
-
-  We summarize our contributions as follow:
-  \begin{enumerate}
-    \item We propose a novel joint system to makes full utilization of
-    the advantages from both text classification model and similarity model.
-
-    \item To  better  train such a system, we bring in multi-task training to obtain
-    expected performance.
-
-    \item Experiment  results  from 4 public and 1 private short-text classification
-    datasets,  show  that  our  proposed  SFC joint system can achieve significant
-    improvements over strong baselines, especially in the low resource settings.
-  \end{enumerate}
-
-  \begin{figure*}[t]
-    \begin{centering}
-      \includegraphics[scale=0.72]{picture/picture4} 
-      \par
-    \end{centering}
-    \caption{
-      \textbf{Network   Structure   of  joint  SFC:}  a  joint  model  of
-      sentence-pair   model   and   text   classification   model  organized  in
-      joint  structure by completing different tasks at different network
-      layers.
-    }
-    \label{fig:framework}
-  \end{figure*}
-
 \section{Related work}
@@
 
-  {Add joint NER and classification problem here.}
-
-  \section{Methodology}
-  In  this  section,  we  will  describe a system of similarity model fused with
-  classification  model,  named  as  SFC, in detail. We come up with 2 different
-  approaches  for  implementation  of SFC system, in which joint SFC is a
-  further improvement of two-stage SFC for better performance.
-
-  \subsection{two-stage SFC with multi-task learning}
-
-  The   detailed   network   structure   of   two-stage   SFC  is  shown  in  Fig.
-  \ref{fig:ver.1.3}.  It  is  composed  with  2  separate  stages  in  charge of
-  different  jobs. In stage 1, we can use any auxiliary model or tool to provide
-  top-K  most  related class labels for sampling sentence pairs of both positive
-  samples  and negative samples for stage 2. Suppose we have a training data set
-  $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$  of  $N$ data points, in which $x_{i}$
-  is the user input query and $y_{i}$ is a single class label from a class label
-  set  of  $C$  classes  in total. If we want to generate sentence pair data set
-  $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$,   where   $(x,   x')_{j}$  is
-  sentence  pair  grouped  by  2  user  input  queries and $l_{j}\in\{0, 1\}$ is
-  similarity class label, see Equ. \ref{eq:similarity label},
-  \begin{align}
-    l_{j}=
-    \begin{cases} \label{eq:similarity label}
-      0 & y_{x}\neq y_{x'}\\
-      1 & y_{x}=y_{x'}
-    \end{cases}
-  \end{align}
-  directly  from  original data set $\mathcal{D}$ without any sampling strategy,
-  then  $\mathcal{D'}$  will  have  $M=N^2$ data points of sentence pairs, which
-  might be too time-consuming for the training process of stage 2 since we often
-  have  hundreds  of class labels under task-specific chatbot scenario. Although
-  we  may  only  have  a  few data points for a single class label, $M$ is still
-  quite a big number.
-
-  Therefore,  we adopt the idea of adversarial negative sampling strategy raised
-  by   \cite{bamler2020extreme}.  The  key  idea  of this sampling strategy is to
-  train  with  negative  samples that are hard to be distinguished from positive
-  samples. Now suppose we have a user input query $x_{i}$ and top-K most related
-  class   labels   set  $\mathcal{C'}=\{c'_{1},  \dots,  c'_{K}\}$  provided  by
-  auxiliary  model  or  tool in stage 1, where $K$ is a hyperparameter set by us
-  that  controls  candidate  class  number,  we  apply  the adversarial negative
-  sampling  strategy  into our sentence pair sampling process by the following 2
-  steps:
-
-  \textbf{1.  positive  sentence pair sampling}: During the training process, we
-  have  to first make sure that the ground truth class label $y_{i}$ for $x_{i}$
-  is  within  the  candidate  class  label  set  $\mathcal{C'}$. If $y_{i}\notin
-  \mathcal{C'}$,  we  will manually add $y_{i}$ into $\mathcal{C'}$ by replacing
-  $c'_{K}$  with  $y_{i}$, since $c'_{K}$ is the least promising candidate label
-  according  to  the  auxiliary  model  in stage 1. Afterwards, we will randomly
-  sample  $P$  sentences  $\{x'_{0},x'_{1}, \dots, x'_{P}\}$ with the same class
-  label as $y_{i}$ from data set $\mathcal{D}$ to form the set of sentence pairs
-  with   positive   label  $\mathcal{P'}_{i}=\{[(x_{i},  x'_{0}),  1],  [(x_{i},
-  x'_{1}),   1],   \dots,   [(x_{i},   x'_{P}),  1]\}$,  where  $P$  is  also  a
-  hyperparameter  set  by  us  that  controls  the number of sentences we should
-  sample from each class.
-
-  \textbf{2.  negative  sentence pair sampling}: As for negative sentence pairs,
-  we  will  also  randomly  sample  $P$ sentences for each class in the negative
-  candidate class label set $\mathcal{C'}\backslash \{y_{i}\}$. The class labels
-  in  $\mathcal{C'}\backslash  \{y_{i}\}$  are  the  set of most confusing class
-  labels comparing to the ground truth ${y_{i}}$, so we assume that the sentence
-  pairs  with  negative  label grouped by user input query $x_{i}$ and sentences
-  with class labels in $\mathcal{C'}\backslash \{y_{i}\}$ are strong adversarial
-  negative  samples for sentence-pair similarity model that can help enhance the
-  training  speed  and  performance.  According  to  the same method as positive
-  sentence  pair sampling, we can obtain the set of sentence pairs with negative
-  label  as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{0}), 0], [(x_{i}, x'_{1}), 0], ...,
-  [(x_{i}, x'_{P\cdot (K-1)}), 0]\}$
-
-  In  this  way,  we  can generate the sentence pair data set $\mathcal{D'}$ for
-  stage  2 based on the top-K class label set $\mathcal{C'}$ provided by stage 1
-  as   $\mathcal{D'}=\{\mathcal{P'}_{i}\cup   \mathcal{N'}_{i}\}_{i=1}^{N}$,  in
-  which we will have $M=N\cdot K\cdot P$ data points of sentence pairs in total.
-
-  After  explaining the data sampling principle for sentence pairs and how the 2
-  stages  in  SFC  system  connect  with  each other, let's go deeper into model
-  structure within these two stages respectively to see how it works.
-
-  \subsubsection*{
-    stage 1: classification model for providing top-K candidate class labels
-  }
-
-  As for  stage  1,  our  SFC  system  can adapt to any auxiliary model or even
-  searching  tool  based  on  Term Frequency-Inverse Document Frequency (TF-IDF)
-  retrieval.  In  this  paper,  however,  we  choose to fine-tune RoBERTa on our
-  task-specific  data set $\mathcal{D}$ by adding a softmax classifier on top of
-  it,  the  same  as  the  structure shown in Fig. \ref{Fig.1.sub.1}, for better
-  overall  performance.  According  to  our  experimental  result,  RoBERTa  can
-  guarantee  that  approximately  95\%  ground  truth label be included in top-5
-  candidate  class  labels  with  highest  probability after being fine-tuned on
-  task-specific  data set with experimental result measured by F-score at around
-  0.75.  So  we use RoBERTa as encoder of classification model in our setting at
-  stage 1 to ensure low limitation for the performance of stage 2.
-
-  For single-sentence text classification tasks, given a data point $x_{i}$ with
-  class  label  $y_{i}$  from  data  set  $\mathcal{D}$, RoBERTa takes the final
-  hidden  state  $h_{i}$  of the first token [CLS] as the representation for the
-  whole   sequence  of  $x_{i}$.  Let's  suppose  we  have  a  linear  layer  as
-  ${\Phi}^C_{i}=W^Ch_{i}+b^C$,  where  $W^C$ and $b^C$ are trainable parameters,
-  the    probability    score    for    $x_{i}$    can    be    calculated    as
-  $p^C_{i}=softmax(W^Ch_{i}+b^C)=softmax({\Phi}^C_{i})$.   Then,  the  loss  for
-  stage 1 classification model is shown in Equ. \ref{eq:classification loss}, in
-  which  the  first  term  $\varPhi_{i,y_{i}}^C$ encourages high probability for
-  prediction of the correct label $y_{i}$.
-
-  \begin{equation}
-    \begin{aligned}
-      \mathcal{L}^{C}&=\frac{1}{N}\sum_{i=1}^{N}-log(\frac{exp(\varPhi_{i,y_{i}}^C)}{\sum_{j=1}^{C}exp(\varPhi_{i,j}^C)}) \\&=\frac{1}{N}\sum_{i=1}^{N}-\varPhi_{i,y_{i}}^C+log(\sum_{j=1}^{C}exp(\varPhi_{i,j}^C))
-      \label{eq:classification loss}
-    \end{aligned}
-  \end{equation}
-
-  \subsubsection*{
-    stage 2: sentence-pair model for multi-task learning
-  }
-
-  As for  stage 2, we also choose RoBERTa as the encoder for sentence pairs, as
-  shown  in Fig. \ref{fig:ver.1.3}. Before sending sentence pairs to Roberta, we
-  pack  sentence  pairs  into a single sequence and separate them with a special
-  token  [SEP].  Roberta  will  also  add  a  learned  embedding  to every token
-  indicating  whether  it belongs to the first sentence or the second one. Then,
-  we  utilize  the  cross-attention  mechanism  inside RoBERTa, and then extract
-  semantic relationship between 2 sentences from the output softmax layer, which
-  is placed on top of the last hidden representation of the [CLS] token.
-
-  Before we start to fine-tune our sentence-pair model on task-specific dataset,
-  we   first  fine-tune  RoBERTa  on  Quora  dataset \cite{iyer2017first},  which
-  contains  404,290  potential  duplicate question pairs, for transfer learning.
-  Then   we   continue  to  do  multi-task  training  on  sentence-pair  dataset
-  $\mathcal{D'}$ sampled from the top-K candidate class labels provided by stage
-  1.
-
-  The 2 tasks for stage 2 training process are listed below.
-
-  $\bullet$ \textbf{Task 1: Regular sentence-pair similarity task}
-
-  For  sentence  pair semantic similarity task, given a data point $(x, x')_{i}$
-  with       similarity       label       $l_{i}$       from       data      set
-  $\mathcal{D'}=\{[(x,x')_{i},l_{i}]\}_{i=1}^{M}$,   Roberta   takes  the  final
-  hidden  state  $h_{i}$  of the first token [CLS] as the representation for the
-  sequence of packed sentence pair $(x, x')_{i}$. Let's suppose we have a linear
-  layer  as  ${\Phi}^S_{i}=W^Sh_{i}+b^S$,  where  $W^S$  and $b^S$ are trainable
-  parameters,  and  the probability score for $(x, x')_{i}$ can be calculated as
-  $p^S_{i}=softmax({\Phi}^S_{i})$.
-
-  Due  to  the  fact that sentence pairs within the same class is much less than
-  sentence  pairs  from  different  classes,  the  data  set  $\mathcal{D'}$  is
-  imbalanced.  Therefore, we will accommodate a weight variable $w^S = [K-1, 1]$
-  to  the  loss  to eliminate the bias brought by imbalanced data, shown in Equ.
-  \ref{eq:similarity loss}.
-
-  \begin{equation}
-    \begin{aligned}
-      \mathcal{L}^{S}&=\frac{1}{M}\sum_{i=1}^{M}-w^S_{l_i}\cdot log(\frac{exp(\varPhi_{i,l_{i}}^S)}{\sum_{j=0}^{1}exp(\varPhi_{i,j}^S)}) \\&=\frac{1}{M}\sum_{i=1}^{M}-w^S_{l_i}\cdot \varPhi_{i,l_{i}}^S+w^S_{l_i}\cdot log(\sum_{j=0}^{1}exp(\varPhi_{i,j}^S))
-      \label{eq:similarity loss}
-    \end{aligned}
-  \end{equation}
-
-  $\bullet$ \textbf{Task 2: Classification task on top-K classes based on sentence-pair model}
-
-  As  for top-K classification task, it shares the same sentence-pair similarity
-  model   structure  with  task  1.  The  only  difference  is  that  we  add  a
-  task-specific  average  pooling  layer,  shown  in  Fig.  \ref{fig:ver.1.3} to
-  implement the classification task based on sentence-pair model.
-
-  We  already  know  that the size of ${\Phi}^S$ in task 1 is $M\times 2=(N\cdot
-  K\cdot  P)\times  2$, where $N$ is the total number of data points in original
-  training  data $\mathcal{D}$, $K$ is a hyperparameter that controls the number
-  of   candidate   class  labels  provided  by  stage  1,  and  $P$  is  also  a
-  hyperparameter that controls the number of sentences we should randomly sample
-  from each candidate class labels. Now, for the average pooling layer, we first
-  reshape  ${\Phi}^S$  into  the  size  of $N\times K\times P\times 2$, and then
-  split  it  into  ${\Phi}^{K,pos}$  and ${\Phi}^{K,neg}$, and both of them will
-  have  the  size  of  $N\times  K\times  P$.  In this way, ${\Phi}^{K,pos}$ can
-  represent  the  level  of  similarity  for each sentence pair, and in the mean
-  time,  ${\Phi}^{K,neg}$  can  represent  the  level  of dissimilarity for each
-  sentence  pair. Then, we can do average pooling for each candidate class among
-  the  top-K  classes  as  shown  in  Equ.  \ref{eq:average  pooling:1} and Equ.
-  \ref{eq:average pooling:2}.
-
-  \begin{align}
-    {\xi}_{i,j}^{K,pos} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,pos} \label{eq:average pooling:1}\\
-    {\xi}_{i,j}^{K,neg} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,neg}
-    \label{eq:average pooling:2}
-  \end{align}
-
-  With  the  average pooling result ${\xi}^{K,pos}$ and ${\xi}^{K,neg}$, we also
-  generate   a   top-K   class   label   $l^{K}_i\in   [1,\dots,K]$   for   each
-  ${\xi}^{K,pos}_{i}$ and ${\xi}^{K,neg}_{i}$. The loss for top-K classification
-  task is shown in Equ. \ref{eq:top-k classification loss}. In Equ. \ref{eq: pos
-  top-k   loss}   and   Equ.   \ref{eq:   neg   top-k   loss},  the  first  term
-  $\xi_{i,l^{K}_{i}}^{K,pos}$  and  $\xi_{i,l^{K}_{i}}^{K,neg}$  encourage  high
-  level  of  similarity  and  low  level  of dissimilarity for prediction of the
-  correct label $l^{K}_i$ within the top-K candidate classes.
-
-  \begin{align}
-    \mathcal{L}^{K} = \frac{1}{N}\sum_{i=1}^{N}(\mathcal{L}^{K,pos}_{i} - \mathcal{L}^{K,neg}_{i})
-    \label{eq:top-k classification loss}
-  \end{align}
-  where,
-
-  \begin{equation}
-    \begin{aligned}
-      \mathcal{L}^{K,pos}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,pos})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,pos})}) \\
-      &= -\xi_{i,l^{K}_{i}}^{K,pos} + log(\sum_{j=1}^{K}exp(\xi_{i,j}^{K,pos}))
-      \label{eq: pos top-k loss}
-    \end{aligned}
-  \end{equation}
-
-  \begin{equation}
-    \begin{aligned}
-      \mathcal{L}^{K,neg}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,neg})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,neg})}) \\
-      &= -\xi_{i,l^{K}_{i}}^{K,neg} + log(\sum_{j=1}^{K}exp(\xi_{i,j}^{K,neg}))
-      \label{eq: neg top-k loss}
-    \end{aligned}
-  \end{equation}
-
-  Therefore,  the  overall  loss  function for multi-task learning in stage 2 is
-  shown in Equ. \ref{eq: two-stage SFC loss}. The training objective of stage 2 is
-  to  minimize  the  weighted  sum  of task-specific losses. Here $\alpha_S$ and
-  $\alpha_K$  are  weights  of  task  1  and  task  2  respectively,  which  are
-  $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting.
-
-  \begin{align}
-    \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K
-    \label{eq: two-stage SFC loss}
-  \end{align}
-
-  \begin{table*}
-    \begin{centering}
-
-      \begin{tabular}{|c|c|c|c|c|c|}
-        \hline 
-        Dataset & Domain & \#Class & \#Samples & \#Samples/Class & Experimental Settings\tabularnewline
-        \hline 
-        ITG & FAQ chatbot & 228 & 3938 & 17 & 3-fold\tabularnewline
-        \hline 
-        Amazon-670k & Product review & 250 & 1942 & 8 & class sampling\tabularnewline
-        \hline 
-        HWU64 & intention detection & 64 & [320, 640, 960, 1280] & [5, 10, 15, 20] & data sampling\tabularnewline
-        \hline 
-        CLINC150 & intention detection & 150 & [750, 1500, 2250] & [5, 10, 15] & data sampling\tabularnewline
-        \hline 
-        BANKING77 & intention detection & 77 & [385, 770, 1155, 1540] & [5, 10, 15, 20] & data sampling\tabularnewline
-        \hline 
-      \end{tabular}
-      \par
-    \end{centering}
-    \caption{Key statistics for experimental datasets and few shot settings}
-
-    \label{tbe:dataset statistic}
-  \end{table*}
-
-  \subsection{joint SFC with joint model structure}
-  Despite  the  outstanding experimental result of two-stage SFC on various tasks,
-  we still find a limitation brought by the two-stage system structure. In two-stage
-  SFC, Stage 1 and stage 2 are separate, so they do not interact with each other
-  during  training.  In  this  case,  the  performance  of stage 1 can limit the
-  potential  of  stage  2, meanwhile, stage 2 also cannot give training feedback
-  back to stage 1 for fine-tuning.
-
-  Therefore,  to  further  improve the overall performance of SFC, we proposed a
-  joint  model  structure,  shown  in Fig. \ref{fig:framework}. In
-  joint SFC, classification model is being placed in lower layer level to
-  dynamically  provide  top-K  candidate  class  labels  for  the  sentence-pair
-  similarity  model  placed in higher layer level through a top-K pooling layer.
-  In  this way, classification model and similarity model can be merged into one
-  single  joint-model  for  multi-task training with sentence pairs sampled from
-  varying  candidate  class  labels,  thus  avoiding the limitation brought by 2
-  separate stage structure.
-
-  There  are  3  tasks in total during the training process of joint SFC,
-  shown  in  Fig. \ref{fig:framework}, and the overall loss is also the weighted
-  sum  of  all  the task-specific losses, shown in Equ. \ref{eq: hierachical SFC
-  loss}. Here, $\alpha_S$, $\alpha_K$ and $\alpha_C$ are the weights for task 1:
-  sentence-pair  similarity,  task  2:  top-K classification and task 3: general
-  single   sentence  classification  respectively,  which  are  $\alpha_S=0.25$,
-  $\alpha_K=0.25$ and $\alpha_C=0.5$ in our setting.
-
-  \begin{align}
-    \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K + \alpha_C \mathcal{L}^C
-    \label{eq: hierachical SFC loss}
-  \end{align}
-
-  Finally,  when  doing inference, for each user input query $x$, we will choose
-  the  class label that contains the sentence $x'$ with highest similarity score
-  $\varPhi$,  after  being packed into a sentence pair $(x, x')$ with query $x$,
-  as our final result for prediction.
-
-  \section{Experiments}
-  In  this  section,  we  conduct  extensive  experiments  over  5 task-specific
-  datasets  to  evaluate  the  performance  of  our  proposed SFC system and the
-  effectiveness  of  the  methodology  of  multi-task  learning  and hierachical
-  joint-model structure under low-data settings.
-
-  \subsection{Datasets}
-  The  datasets  used in our experiments aims to help us study low-resource text
-  classification  problem  under  task-specific conversational chatbot scenario.
-  Therefore,  we keep all the dataset under low-resource chatbot corpus setting,
-  which  is a large number of class labels (50-250) with a few examples(5-20) in
-  short  text  for  each  class, by sampling smaller subsets from the full scale
-  when the raw datasets are oversized, see Table \ref{tbe:dataset statistic}.
-
-  According to the task and domain, we categorize our experimental datasets into
-  the following 3 categories:
-
-  $\bullet$ \textbf{Full-scale real-world task-specific faq chatbot dataset}
-
-  \textbf{ITG}  is  a  real-world  FAQ  chatbot dataset composed of question and
-  answer pairs about online English teaching. It contains 3,938 sample questions
-  for  228  class labels, where each class label corresponds to an unique answer
-  for a bunch of similar sample questions.
-
-  We  divide the whole dataset into 3 folds randomly with approximately the same
-  amount  of data within each fold, and then choose 2 folds as the training set,
-  the  remaing  1  fold  as  the  test  set for our experiments. We can obtain 3
-  different  combinations  among  the  3  folds,  and  we  will  use the average
-  experimental  results  of  these 3 combinations as the final evaluation result
-  for this dataset.
-
-  $\bullet$ \textbf{Subset of customer review dataset for extreme classification}
-
-  \textbf{Amazon-670K}   is   a   customer   product  review  dataset  for  text
-  classification  task from the extreme classification repository with full data
-  containing  670,091  class  labels,  285,176  training samples and 150875 test
-  samples \cite{bhatia2016extreme}.  As  the  data  set  contains  multiple class
-  labels  per  training sample, we keep only the first class label for each data
-  point. Besides, we also randomly sampled 250 class labels from all the classes
-  that  contain only 5-15 data points. In this way, we simulate the low-resource
-  chatbot  corpus setting with the subset of 1,942 training samples and 716 test
-  samples for 250 class labels.
-
-  $\bullet$ \textbf{Subset of recently-released intention detection datasets}.
-
-  From our point of view, task-specific chatbot usually starts with small amount
-  of  data at the initial stage. As more and more customers start to communicate
-  with  the  chatbot,  more data can be extracted from conversation log. Base on
-  these  assumptions,  we  do  experiments  on  the following 3 intention detection
-  dataset    under    sampling    method    similar    to    the   approach   in
-  \cite{casanueva2020efficient}  but  in  more  sophisticated few-shot settings,
-  while  keeping the same test sets for each experiment to see the change of the
-  improvement scale with decreasing data amount.
-
-  \begin{table*}
-    \begin{centering}
-      \scalebox{0.8}{
-        \begin{tabular}{|c|ccc|cccc|cccc|c|c|}
-          \hline 
-          \multicolumn{1}{|c|}{\multirow{2}*{\textbf{Models}} }& \multicolumn{3}{c|}{\textbf{CLINC150}}& \multicolumn{4}{c|}{\textbf{BANKING77}}& \multicolumn{4}{c|}{\textbf{HWU64}}& \ \ \ \textbf{ITG} \ \ \ & \textbf{Amazon-670k}\tabularnewline
-          \cline{2-14}
-          \multicolumn{1}{|c|}{} & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & \textbf{Full} & \textbf{Full}\tabularnewline
-          \hline
-          TextCNN & \multirow{2}*{$0.5318$} & \multirow{2}*{$0.6963$} & \multirow{2}*{$0.7609$} & \multirow{2}*{$0.4408$} & \multirow{2}*{$0.6436$} & \multirow{2}*{$0.7366$} & \multirow{2}*{$0.7918$} & \multirow{2}*{$0.3112$} & \multirow{2}*{$0.4007$} & \multirow{2}*{$0.4823$} & \multirow{2}*{$0.5272$} & \multirow{2}*{$0.6624$} & \multirow{2}*{$0.4401$}\tabularnewline
-          (classification) & & & & & & & & & & & & &\tabularnewline
-          \hline
-          LEAM & \multirow{2}*{$0.7514$} & \multirow{2}*{$0.8203$} & \multirow{2}*{$0.8612$} & \multirow{2}*{$0.5422$} & \multirow{2}*{$0.7812$} & \multirow{2}*{$0.8129$} & \multirow{2}*{$0.8280$} & \multirow{2}*{$0.4545$} & \multirow{2}*{$0.5554$} & \multirow{2}*{$0.5936$} & \multirow{2}*{$0.6599$} & \multirow{2}*{$0.7086$} & \multirow{2}*{$0.6091$}\tabularnewline
-          (classification) & & & & & & & & & & & & &\tabularnewline
-          \hline
-          BERT-large & \multirow{2}*{$0.8080$} & \multirow{2}*{$0.8904$} & \multirow{2}*{$0.9265$} & \multirow{2}*{$0.578$} & \multirow{2}*{$0.8004$} & \multirow{2}*{$0.8518$} & \multirow{2}*{$0.8827$} & \multirow{2}*{$0.4711$} & \multirow{2}*{$0.5963$} & \multirow{2}*{$0.6342$} & \multirow{2}*{$0.7010$} & \multirow{2}*{$0.7485$} & \multirow{2}*{$0.6658$}\tabularnewline
-          (classification) & & & & & & & & & & & & &\tabularnewline
-          \hline
-          ALBERT-xxlarge & \multirow{2}*{$0.8497$} & \multirow{2}*{$0.9008$} & \multirow{2}*{$0.9296$} & \multirow{2}*{$0.5549$} & \multirow{2}*{$0.7981$} & \multirow{2}*{$0.8231$} & \multirow{2}*{$0.8530$} & \multirow{2}*{$0.4879$} & \multirow{2}*{$0.6116$} & \multirow{2}*{$0.6135$} & \multirow{2}*{$0.6996$} & \multirow{2}*{$0.7253$} & \multirow{2}*{$0.6893$}\tabularnewline
-          (classification) & & & & & & & & & & & & &\tabularnewline
-          \hline
-          RoBERTa-base & \multirow{2}*{$0.8732$} & \multirow{2}*{$0.9254$} & \multirow{2}*{$0.9363$} & \multirow{2}*{$0.7305$} & \multirow{2}*{$0.8654$} & \multirow{2}*{$0.8808$} & \multirow{2}*{$0.9080$} & \multirow{2}*{$0.5831$} & \multirow{2}*{$0.6790$} & \multirow{2}*{$0.7064$} & \multirow{2}*{$0.7100$} & \multirow{2}*{$0.7734$} & \multirow{2}*{$0.6708$}\tabularnewline
-          (classification) & & & & & & & & & & & & &\tabularnewline
-          \hline
-          RoBERTa-large & \multirow{2}*{$0.8974$} & \multirow{2}*{$0.9372$} & \multirow{2}*{$0.9508$} & \multirow{2}*{$0.7690$} & \multirow{2}*{$0.8728$} & \multirow{2}*{$0.8966$} & \multirow{2}*{$0.9099$} & \multirow{2}*{$0.6044$} & \multirow{2}*{$0.7002$} & \multirow{2}*{$0.7129$} & \multirow{2}*{$0.7436$} & \multirow{2}*{$0.7990$} & \multirow{2}*{$0.7156$}\tabularnewline
-          (classification) & & & & & & & & & & & & &\tabularnewline
-          \hline
-          RoBERTa-large & \multirow{2}*{$0.8266$} & \multirow{2}*{$0.8861$} & \multirow{2}*{$0.9023$} & \multirow{2}*{$0.757$} & \multirow{2}*{$0.8476$} & \multirow{2}*{$0.8614$} & \multirow{2}*{$0.8743$} & \multirow{2}*{$0.5425$} & \multirow{2}*{$0.6164$} & \multirow{2}*{$0.6503$} & \multirow{2}*{$0.6729$} & \multirow{2}*{$0.7418$} & \multirow{2}*{$0.6362$}\tabularnewline
-          (similarity) & & & & & & & & & & & & &\tabularnewline
-          \hline
-          two-stage SFC & \multirow{2}*{$0.8979$} & \multirow{2}*{$0.9457$} & \multirow{2}*{$0.9517$} & \multirow{2}*{$0.7975$} & \multirow{2}*{$0.8818$} & \multirow{2}*{$0.8962$} & \multirow{2}*{$0.9109$} & \multirow{2}*{$0.6477$} & \multirow{2}*{$0.7055$} & \multirow{2}*{$0.7200$} & \multirow{2}*{$0.7232$} & \multirow{2}*{$0.7972$} & \multirow{2}*{$0.7189$}\tabularnewline
-          (task1 only) & & & & & & & & & & & & &\tabularnewline
-          \hline
-          two-stage SFC & \multirow{2}*{$0.9162$} & \multirow{2}*{$0.9424$} & \multirow{2}*{$0.9530$} & \multirow{2}*{$0.7997$} & \multirow{2}*{$0.8823$} & \multirow{2}*{$0.8945$} & \multirow{2}*{$0.9123$} & \multirow{2}*{$0.6498$} & \multirow{2}*{$0.6980$} & \multirow{2}*{$0.7202$} & \multirow{2}*{$0.7358$} & \multirow{2}*{$0.8020$} & \multirow{2}*{$0.7311$}\tabularnewline
-          (task2 only) & & & & & & & & & & & & &\tabularnewline
-          \hline
-          two-stage SFC & \multirow{2}*{$0.9167$} & \multirow{2}*{$0.9456$} & \multirow{2}*{$0.9571$} & \multirow{2}*{$0.7954$} & \multirow{2}*{$0.8854$} & \multirow{2}*{$0.8931$} & \multirow{2}*{$0.9192$} & \multirow{2}*{$0.6525$} & \multirow{2}*{$0.7001$} & \multirow{2}*{$0.7168$} & \multirow{2}*{$0.7476$} & \multirow{2}*{$\textbf{0.8124}$} & \multirow{2}*{$0.7364$}\tabularnewline
-          (task1 + task2) & & & & & & & & & & & & &\tabularnewline
-          \hline
-          \multirow{2}*{joint SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline
-          & & & & & & & & & & & & &\tabularnewline
-          \hline
-        \end{tabular}
-      }
-      \par
-    \end{centering}
-    \caption{
-      F-scores  on five task-specific dataset for text classification in chatbot
-      under low resource. For ITG, we keep the full dataset. For Amazon-670k, we
-      randomly  sampled  250  classes  with  training sample numbers within 5-15
-      samples  per  class.  For  CLINC150,  BANKING77,  HWU64, we set up various
-      few-shot  settings  (5/10/15/20  samples per class) while keeping the test
-      set  to  be  fixed. The highest scores for each data setting are marked in
-      bold.
-    }
-
-    \label{tbe:table2}
-  \end{table*}
-
-  \textbf{HWU64}   is  a  intention  detection  dataset  designed  for  home  robot
-  scenario \cite{liu2019benchmarking}.  It aims at the specific task of capturing
-  the  intention  for  different  user  requests  to  home  robot  and  finding the
-  corresponding answer. The raw dataset contains 25,716 data points for 64 class
-  labels  through  crowdsourcing,  which  raises  much  more  data  than  common
-  real-world  circumstances. Therefore, we experiment with the setups where only
-  5,  10,  15  and 20 training data points are available for each class label by
-  random sampling.
-
-  \textbf{CLINC150}  is a dataset designed for task-oriented systems with 23,700
-  queries  that  are  short  and unstructured for 150 intents, in the same style
-  made  by real users through crowdsourcing \cite{larson2019evaluation}. Here, we
-  sample 5, 10 and 15 training data points for each intention class label by random
-  sampling for our experimental setup.
-
-  \textbf{BANKING77}  is  a intention detection dataset for bank customer services.
-  The    raw    dataset    contains    13,084   data   points   for   77   class
-  labels \cite{casanueva2020efficient}.  Here,  we  sample 5, 10, 15, 20 training
-  data  points  for  each  class  label  by random sampling for our experimental
-  setup.
-
-  \subsection{Baselines}
-  We choose 3 groups of representative baselines:
-
-  \textbf{Group  1:  single-task  classification  model.} This group of baseline
-  models  are  based  on the network structure for classification model shown in
-  \ref{Fig.1.sub.1}.   As   for   non-pretrained   neural   network,  we  choose
-  TextCNN \cite{kim2014convolutional}  as  a  representative baseline. As for the
-  pretrained  model,  we choose RoBERTa, BERT and ALBERT, all of which are among
-  the  most  powerful pretrained models that achieve outstanding results in many
-  NLP  tasks,  in  our  experimental  setting. Since we apply RoBERTa in our SFC
-  system,   we   naturally  adopt  single-task  classification  model  based  on
-  RoBERTa-large  and RoBERTa-base as our baseline models. Besides, we also adopt
-  the       recently       released       baseline       pre-trained       model
-  ALBERT-xxlarge \cite{lan2019albert}  for  comparison.  Since  we  use different
-  few-shot   settings   from    \cite{casanueva2020efficient}  for  those
-  intention
-  detection  datasets,  we also use BERT-large tuned on our few-shot settings as
-  an essential reference for experimental results.
-
-  \textbf{Group  2: single-task similarity model.} This group of baseline models
-  are   based   on   network   structure   for   similarity   model   shown   in
-  \ref{Fig.1.sub.2}. We choose RoBERTa-large for the pretrained model part as an
-  powerful baseline. But during the evaluation step, we use elastic search to do
-  a  rough  filter  for  candidate  sentence  pairs  to  guarantee  a reasonable
-  inference time for each user query.
-
-  \textbf{Group  3:  SFC  system with ablation study.} This group of baseline is
-  based  on  the network structure of two-stage SFC shown in \ref{fig:ver.1.3}. We
-  conduct  ablation study by introducing single task SFC system with only Task 1
-  or  Task  2  to  investigate  the influence of each component within the total
-  loss.
-
-  \subsection{Implementation Details}
-  For  our  SFC  system,  we  use RoBERTa-large as the pretrained model for both
-  classification  task  and  sentence-pair similarity task. We further fine-tune
-  our  SFC  system  on  task-specific  datasets with max sequence length of 128,
-  learning  rate  of 1.5e-5 for RoBERTa-large pretrained model and learning rate
-  of  5e-4  for  task-specific  layer  with polynomial decay and Adam optimizer.
-  Also,  we  set  the  max number of the epoch to 100 and save the best model on
-  validation  set based on test result in F-score. We also report the F-score as
-  the main evaluation measure for all experimental results.
-
-  For  the  experiments  in  Table  \ref{tbe:table2},  we  empirically  set  the
-  hyperparameter  to  be  $K=5$  and  $P=10$  for  all  SFC  variants.  In Table
-  \ref{tbe:table3},  we  conduct extensive experiments to see the performance of
-  SFC system under various hyperparameter settings.
-
-  \begin{table*}
-    \begin{centering}
-
-      \begin{tabular}{|c|c|c|c|c|c|c|}
-        \hline 
-        \multicolumn{1}{|c|}{\multirow{2}*{Dataset}}&\multicolumn{1}{c|}{\multirow{2}*{Model}}& $K=3$ & $K=5$ & $K=10$ & $K=15$ & $K=20$\tabularnewline
-        \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & $P=20$ & $P=10$ & $P=5$ & $P=4$ & $P=3$\tabularnewline
-        \hline
-        \multicolumn{1}{|c|}{\multirow{2}*{ITG}}& two-stage SFC & $0.8034$ & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
-        \cline{2-7}
-        \multicolumn{1}{|c|}{} & joint SFC & $0.7986$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7918$\tabularnewline
-        \hline
-        \multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& two-stage SFC & $0.7278$ & $0.7364$ & $0.7366$ & $0.7328$ & $0.7204$\tabularnewline
-        \cline{2-7}
-        \multicolumn{1}{|c|}{} & joint SFC & $0.7334$ & $0.7445$ & $0.7516$ & $0.7344$ & $0.7373$\tabularnewline
-        \hline
-      \end{tabular}
-      \par
-    \end{centering}
-    \caption{
-      We  show the performance of SFC from different settings of hyperparameters
-      for  $K$,  the candidate class number, and $P$, the sample number for each
-      class.
-    }
-
-    \label{tbe:table3}
-  \end{table*}
-
-  \subsection{Result Analysis}
-
-  Table  \ref{tbe:table2}  presents  the  results for each experimental data and
-  model  set-up  in detail. The performance of each model is measured in F-score
-  on the fixed test set for each data set. The overall performance of SFC system
-  is  better  than  all  the  competitive  single-model  baseline models on five
-  experimental   datasets.  This  observation  gives  us  a  general  idea  that
-  classification model and similarity model can actually provide each other with
-  complementary information, and combining them together into a joint system can
-  effectively  enhance the overall capability based on richer extracted semantic
-  information.  However  the  relative performance among all the variants of SFC
-  also  seems  to  depend  on  some  specific  charateristic  of  each data set.
-  Therefore,  we did the following more detailed analysis from several different
-  aspect.
-
-  \textbf{Comparison  among  SFC  variants.} First, we turn to compare among the
-  four  SFC  variants shown in Table \ref{tbe:table2} to analyze the improvement
-  brought  by  multi-task  and  joint-model  structure. We conduct
-  ablation  experiments  to study the benefits brought by multi-task training by
-  comparing multi-task two-stage SFC with single-task two-stage SFC. We can see from
-  Table  \ref{tbe:table2}  that  two-stage  SFC  with  only  task 1 (sentence-pair
-  similarity task) degrades by 0.65 percent on average and two-stage SFC with only
-  task  2  (top-K  classification  task) degrades by 0.32 percent on average. The
-  degradation  indicates  that  training  with these 2 tasks together in SFC can
-  effectively  help  the  sentence-pair  model  extract  more knowledge from the
-  limited  amount  of data. Besides, task 2 degrades 0.33 percent less than task
-  1.  This observation suggests that task 2 may play a relatively more important
-  role  in multi-task learning, which leads us to put larger weight $\alpha_{K}$
-  to  the  loss  $\mathcal{L}^{K}$  of  task  2  when calculating the total loss
-  $\mathcal{L}$.  Also, we can see that the joint SFC steadily outperforms
-  two-stage  SFC  on  5  diverse  datasets  by  1.17  percents  on  average.  This
-  observation  supports  the idea that the joint model structure can
-  alleviate the limitation brought by the lack of interaction between similarity
-  model  and  classification  model in two-stage SFC. Therefore, for the following
-  analysis,  we  will  focus  on  the comparison between joint SFC and the
-  other baseline models.
-
-  \textbf{Analysis  under  few-shot  scenarios.}  Next,  we  analyze the overall
-  improvement trend of SFC under various few-shot settings. Our main focus is to
-  study chatbot building in common situation during real-world application where
-  only  a  few  sample  sentences are available for each class. The experimental
-  results  for  the  3  diverse  intention detection datasets (ClINC150, BANKING77,
-  HWU64) under few-shot settings indicate that our proposed joint SFC can
-  achieve  2.47  percents  average  improvement  over  one  of the most powerful
-  baseline  models,  which  is  RoBERTa-large classification model, on all these
-  few-shot  settings. Moreover, the improvement in F-score becomes more and more
-  prominent  with the decrease of data sample number per class. Our joint
-  SFC   can  achieve  4.97  percents  average  improvements  over  RoBERTa-large
-  classification model in the most extreme few-shot setting with only 5 training
-  samples  per class. This observation indicates that SFC is especially suitable
-  for  being  applied during the initial stage of building task-specific chatbot
-  system,  where  the  amount  of  data sample for each class label is extremely
-  scarce.
-
-  \textbf{Comparison  between  label  embedding  and  sentence  pair embedding.}
-  Afterwards,  we  start  to  compare the performance of SFC with the text-label
-  joint  embedding  baseline  named as LEAM. As shown in Table \ref{tbe:table2},
-  joint  SFC outperforms LEAM by 14.25 percents on average F-score over 5
-  datasets.  Besides,  although the labels within the 3 diverse intention detection
-  datasets  (CLINC150,  BANKING77,  HWU64)  are  all  being  well-defined as the
-  semantic  summary  of  each intention, joint SFC still outperforms LEAM by
-  14.69  percents  on  average  F-score.  This  observation  indicates that it is
-  usually  quite  hard  to  use  a  fixed  label  with  only  a few words as the
-  representative  of  all  the  sentences  within a class since there are always
-  plenty of ways for people to express questions or queries about the same topic
-  during   a   conversation  with  chatbot.  Therefore,  learning  the  semantic
-  similarity  between  user  query  and  sample  sentences through sentence pair
-  embedding  can be more reliable than making decision according to the semantic
-  relationship between user query and class labels through label embedding.
-
-  \textbf{Fusion  of  classification  and  similarity  model.} Then, we begin to
-  compare  the  general  performance  of SFC with single-task classification and
-  similarity  baselines.  As  for  the  classification  model,  joint SFC
-  outperforms    TextCNN    by   26.19   percents,   ALBERT-xxlarge   by   9.95
-  percents\footnote{We found that the performance of ALBERT.xxlarge is extremely
-  unstable  for  classification  task.  Here, we did multiple run with different
-  settings  of parameters such as learning rate and batch size for each dataset,
-  and  record  the  best  result  we  can  obtain  in  Table \ref{tbe:table2}.},
-  BERT-large  by  9.81 percents, RoBERTa-base by 4.52 percents, RoBERTa-large by
-  2.47 percents on average F-score over 5 datasets. In this way, we can see that
-  RoBERTa  is  the  best  baseline  pre-trained  model for the low-resource text
-  classification  task  we  are  studying.  As for the similarity model, we only
-  choose  the  strongest  pretrained  model  RoBERTa-large  as our baseline, and
-  joint  SFC  achieves  the  improvement  of  7.81  percents  on average.
-  Moreover,  joint  SFC's  result on 2 datasets without data sampling for
-  few-shot  settings,  which  are  ITG  and  Amazon-670k, are also 1.24 and 2.89
-  percents  higher  than  Roberta-large  classification  model, and are 6.96 and
-  10.77  percents higher than Roberta-large similarity model. These improvements
-  illustrate that putting classification model and similarity model at different
-  network  layers  to  cooperate  with  each  other  is  a  successful design of
-  joint network structure for joint model, which enables these two models
-  assist each other for better overall results.
-
-  \textbf{Settings  of  hyperparameters.} Finally, we analyze the effect brought
-  by  different  settings  of  hyperparameters,  see  Table \ref{tbe:table3}. We
-  conduct  experiments on 5 different settings of hyperparameters, which are the
-  number  of candidate class number $K$ and the number of sentence pairs $P$ for
-  each  class, on ITG and Amazon-670K datasets to find the most suitable setting
-  of  these  2  hyperparameters.  We  control the total number of sentence pairs
-  sampled  for  each  user  query  into  about  the same level of amount(50-60).
-  Through  analyzing the experimenal results shown in Table \ref{tbe:table3}, we
-  find  that the best setting of hyperparameters might be different for
-  datasets of different data size. The class label number of ITG and Amazon-670k
-  are  similar  in  our  experimental  setting, which is around 250. However the
-  total  amount  of  data  points  of  ITG  is approximately 2 times larger than
-  Amazon-670k. Therefore, the setting of $K=5$ and $P=10$ is good enough for ITG
-  since  most  of  the  classes  contains  over  10  data  points.  However, for
-  Amazon-670k,  the amount of data sample for each class is scarce, thus, we may
-  need  more  candidate  classes  to  sample enough effective sentence pairs for
-  sentence-pair model layer of SFC. In this way, the setting of $K=10$ and $P=5$
-  becomes a good choice.
-However, in spite of the effect on evaluation performance brought by different settings of hyperparameters, joint SFC still steadily outperforms two-stage SFC by 0.41 percents in overall average F-score on ITG and Amazon-670k datasets.
-
-  In  conclusion,  to  the best of our knowledge, these experimental results place joint SFC as the
-  best   performing   model   on   5  diverse  experimental  datasets  for  text
-  classification  task  under  low-resource task-specific conversational chatbot
-  scenario.
-
-  \section{Conclusion}
-  In  this  work, we successfully proposed SFC, a joint system of classification
-  model  and  sentence-pair similarity model with multi-task learning, which can
-  effectively  alleviate  the  limitation of classification model and similarity
-  model   for  low-resource  text  classification  tasks.  Experimental  results
-  illustrate that our proposed system can achieve great improvement on 5 diverse
-  datasets for task-specific chatbot system over several competitive single-task
-  baseline  models. Furthermore, we especially analyze the excellent performance
-  of SFC when facing the challenge brought by few-shot scenarios, which is quite
-  common in real-world application of chatbot system.
-
-  \bibliographystyle{aaai21}
-  \bibliography{refs}
-
-\end{document}
+Another   line   of  interesting  work  is  the  joint  training  of  sentence
+classification   and  NER  (todo:  reference).  If  both  the  city  and  date
+information  are  recognized,  then  they  are good indicators that this query
+might  be  booking  an  ticket. This work can also be combined in our proposed
+framework.

### 2020-09-10 chatbot_classification/aaai_2021/experiments.tex
modified:   experiments.tex

@@
 of  5e-4  for  task-specific  layer  with polynomial decay and Adam optimizer.
-Besides,  we  set  the  max number of the epoch to 100 and save the best model on
-validation  set based on testing result in weighted F1 score
-\footnote{In the multi-class and multi-label case, this is the average of the
-F1 score of each class with weighting depending on the numbers in each class.}.
-We report the F1 score as the main evaluation measure for all experiments.
 
@@
 \subsection{Result Analysis}
-All  results  in  F1  score  on  the  five  datasets with different models and
-configurations are showed in Table \ref{tbe:table2}.
+We  report  the F1 score \footnote{In the multi-class and multi-label case, this
+is  the  average  of  the F1 score of each class with weighting depending on the
+numbers  in  each class.}. as the main evaluation measure for all experiments in
+Table \ref{tbe:table2}.
 
@@
 \subsubsection*{Settings  of  hyperparameters} 
-Finally, we analyze the effect brought
-by  different  settings  of  hyperparameters,  see  Table \ref{tbe:table3}.
+In  Table \ref{tbe:table3}, we explore the influence from hyperparameters, which
+are  the  number  of  candidate  class  labels $K$ in stage 1, and the number of
+sampled  sentence  pairs  for  each class $P$ in stage 2, on ITG and Amazon-670K
+datasets.  As we control the total number of sampled sentence pairs to about 50 to 60, we
+roughly obatin five combinations of hyperparameters.
 
-We  conduct  experiments on 5 different settings of hyperparameters, which are
-the  number of candidate class number $K$ and the number of sentence pairs $P$
-for  each  class,  on  ITG  and Amazon-670K datasets to find the most suitable
-setting  of  these  2 hyperparameters. We control the total number of sentence
-pairs  sampled for each user query into about the same level of amount(50-60).
-Through  analyzing the experimental results shown in Table \ref{tbe:table3}, we
-find  that the best setting of hyperparameters might be different for datasets
+We find  that the best setting of hyperparameters is different from datasets
 of  different  data  size.  The  class label number of ITG and Amazon-670k are
@@
 model  layer  of  SFC.  In this way, the setting of $K=10$ and $P=5$ becomes a
-good choice. However, in spite of the effect on evaluation performance brought
-by different settings of hyperparameters, joint SFC still steadily outperforms
-two-stage  SFC  by  0.41  percents  in  overall  average  F1 score  on  ITG and
-Amazon-670k datasets.
+good choice.
 
-In  conclusion, to the best of our knowledge, these experimental results place
-joint  SFC as the best performing model on 5 diverse experimental datasets for
-text   classification   task,   especially   when   it's   under  low-resource
-task-specific conversational chatbot scenario.
+However,  in  spite of the effect on evaluation performance brought by different
+settings  of hyperparameters, joint SFC still steadily outperforms two-stage SFC
+by  0.41  percent  points  in  overall  average  F1 score on ITG and Amazon-670k
+datasets.

### 2020-09-10 chatbot_classification/aaai_2021/experiments.tex
modified:   experiments.tex

@@
 is  the  average  of  the F1 score of each class with weighting depending on the
-numbers  in  each class.}. as the main evaluation measure for all experiments in
+numbers  in  each class.} as the main evaluation measure for all experiments in
 Table \ref{tbe:table2}.

### 2020-09-10 chatbot_classification/aaai_2021/introduction.tex
modify introduction and methodology

@@
 Generally  there  are  two  kinds  of  approaches  to  address  this  problem,
-one is the classification model that directly maps an input into a most likely label, and
-the other one is the similarity  model  that searches a label whose associated data is most similar to
+one is based on the \emph{(text) classification model} that directly maps an input into a most likely label, and
+the other one is based on the \emph{(text) similarity  model}  that searches a label whose associated data is most similar to
 an input.
 
-The   first  one,  \emph{text  classification},  includes  classic  long  text
+The   first  one,  \emph{classification model},  includes  classic  long  text
 classification  and  short  text  classification  in  this  scenario.  Besides
@@
 \cite{mousa2017contextual,liu2016recurrent}   to   accomplish   the   task  of
-extracting  semantic  feature from limited amount of words. Their common model
+extracting  semantic  features from limited amount of words. Their common model
 structure  is  adding  a  softmax classifier as the final layer and mapping to
@@
 \cite{yu2018diverse},     pre-trained     model    based    on    transformers
-\cite{vaswani2017attention} tends to do more
-help to reducing the negative effects brought by scarcity of training data.
+\cite{vaswani2017attention} tends to be more helpful to reduce the negative effects brought by scarcity of training data.
 
-The  second  one,  \emph{similarity model} is also called sentence-pair model.
-Its  motivation  originates  from  the idea of Information Retrieval (IR) based
-chatbot   \cite{jafarpour2010filter,   leuski2011npceditor}.   Having   a  Q-A
-(Question-Answer)  pairs dataset and user query Q, the IR based conversational
-system will look up in the Q-A dataset for the pair (Q', A') that best matches
-query  Q  through  semantic  analysis  and  returns  A'  as  the  answer  to Q
+The  second  one,  \emph{similarity model},  is also called sentence-pair model.
+Its  motivation  originates  from  the idea of retrieval based
+chatbot   \cite{jafarpour2010filter,   leuski2011npceditor}.   Given  a  Q-A
+(Question-Answer)  pairs dataset and a user query Q, the retrieval based conversational
+system will search from the Q-A dataset  the most matched pair (Q', A') 
+through  semantic  analysis  and  return  A'  as  the  answer  to Q
 \cite{mnasri2019recent}. In this way, sentence-pair model pre-trained on large
-corpus  of  semantic  similarity  identification task can be applied for being
-used  as  a  tool  to  identify  the class with highest semantic similarity to
+corpus  can be employed  to  identify  the class with highest semantic similarity to
 customer's    query.    A    common    model    structure    of    pre-trained 
@@
 results  on  both  text  classification and sentence-pairs semantic similarity
-tasks, we choose RoBERTa as an important baseline approach in this paper.
+tasks, we choose RoBERTa as one of the baselines in this paper.
 

### 2020-09-10 chatbot_classification/aaai_2021/methodology.tex
modified:   experiments.tex   modified:   methodology.tex
modify introduction and methodology

@@
 \section{Methodology}
-In  this section, we describe our proposed system, a similarity model fused with
-a classification  model (SFC). We propose two approaches to implement this idea,
+In  this section, we describe our proposed SFC. We propose two approaches to implement this idea,
 two-stage SFC, and its more compact version joint SFC.
@@
 provide  top-K  most  related  class  labels. These selected class labels will
-later  be  used to sample sentence pairs of both positive samples and negative
+later  be  used to sample sentence pairs of both positive and negative
 samples  for  stage  2.
@@
         \hline 
-        ITG & FAQ chatbot & 228 & 3938 & 17 & 3-fold\tabularnewline
+        ITG & FAQ chatbot & 228 & 3938 * 0.7 & 17 & 3-fold\tabularnewline
         \hline 
-        Amazon-670k & Product review & 250 & 1942 & 8 & 3-fold\tabularnewline
+        Amazon-670k & Product review & 250 & 2658 * 0.7 & 8 & 3-fold\tabularnewline
         \hline 

### 2020-09-10 chatbot_classification/aaai_2021/experiments.tex

@@
   correspond  to  multiple  class labels, we keep only the first one. We further
-  filter  out the class labels that each one is associated with 5 to 15 samples,
+  filter  out the class labels that each one is associated with only 5 to 15 samples,
   or  reviews,  to  mimic  the  chatbot scenario. From them, we sample 250 class
-  labels as well as their samples to form a subset with 1,942 + 716 samples.
+  labels as well as their samples to form a subset with 2658 samples.
 

### 2020-09-10 chatbot_classification/aaai_2021/introduction.tex
modify several *.tex files to create the final submitted paper.ver10.pdf for review

@@
 into  many practical products. One typical example is the chatbot that shares the working burden of
-human  customer  service  agents  responsible  for  customers' questions about
-certain  products  or services. Another one is the speech-based control in
+human  customer  service  agents  responsible  for  customers' questions. 
+Another one is the speech-based control in
 devices  like  intelligent  speakers, such as Siri, Google home, Baidu Xiaodu,
@@
 
-Intention detection in task-specific chatbot  is  a  challenging task due to some inherent properties. First,
+Intention detection in task-specific chatbot  is  a  challenging task due to its inherent properties. First,
 a customer's  utterance  within  a conversation is usually quite short. Since it
@@
 initial  stage  of  building  a  chatbot , it is often rather hard to collect
-sufficient  labeled  data  to  train  a good model. Because developers have to
+sufficient  labeled  data  to  train  a good model. Developers have to
 examine tons of real system logs for typical user's utterances, and then label
@@
 Generally  there  are  two  kinds  of  approaches  to  address  this  problem,
-one is based on the \emph{(text) classification model} that directly maps an input into a most likely label, and
-the other one is based on the \emph{(text) similarity  model}  that searches a label whose associated data is most similar to
-an input.
+one is based on the \emph{text classification model} that directly maps an input text into a most likely label, and
+the other one is based on the \emph{text similarity  model}  that searches the most similar text to the input and returns the associated label.
 
-The   first  one,  \emph{classification model},  includes  classic  long  text
+\emph{Text classification}  includes  classic  long  text
 classification  and  short  text  classification  in  this  scenario.  Besides
@@
 extracting  semantic  features from limited amount of words. Their common model
-structure  is  adding  a  softmax classifier as the final layer and mapping to
+structure  is  adding  a  softmax classifier as the final layer to predict the
 labels.  Another  two  interesting lines of work, label-word joint models, and
 joint  NER  and  classification  are  discussed  in  the related work section.
-Afterwards,   pre-trained   language   models   on   large  corpus  like  BERT
+Recently,   pre-trained   language   models   on   large  corpus  like  BERT
 \cite{devlin2018bert}  and  RoBERTa \cite{liu2019roberta} has been proven more
@@
 \cite{madabushi2020cost}.      Especially      for      few-shot     scenarios
-\cite{yu2018diverse},     pre-trained     model    based    on    transformers
-\cite{vaswani2017attention} tends to be more helpful to reduce the negative effects brought by scarcity of training data.
+\cite{yu2018diverse},     pre-trained     models    based    on    transformers
+\cite{vaswani2017attention} tends to be more helpful to alleviate the dearth of training data.
 
-The  second  one,  \emph{similarity model},  is also called sentence-pair model.
-Its  motivation  originates  from  the idea of retrieval based
-chatbot   \cite{jafarpour2010filter,   leuski2011npceditor}.   Given  a  Q-A
-(Question-Answer)  pairs dataset and a user query Q, the retrieval based conversational
-system will search from the Q-A dataset  the most matched pair (Q', A') 
-through  semantic  analysis  and  return  A'  as  the  answer  to Q
-\cite{mnasri2019recent}. In this way, sentence-pair model pre-trained on large
-corpus  can be employed  to  identify  the class with highest semantic similarity to
-customer's    query.    A    common    model    structure    of    pre-trained 
-sentence-pair model is based on multiple cross-attention
-mechanism  \cite{barkan2020scalable}. Due to
-the   fact   that   many   experiment   results   have   shown   that  RoBERTa
+\emph{Text similarity model}  is usually employed to calculate the similarities between an input text 
+and historical texts in the repository, and returns the associated label of the historical
+text with highest similarity score. 
+One of the state-of-the-art similarity models is based on multiple cross-attention
+mechanism  \cite{barkan2020scalable}.
+Due to the   fact   that   many   experiment   results   have   shown   that  RoBERTa
 \cite{liu2019roberta} is an improved version of BERT \cite{devlin2018bert}, and has achieved amazing
-results  on  both  text  classification and sentence-pairs semantic similarity
+results  on  both  text  classification and text similarity-related
 tasks, we choose RoBERTa as one of the baselines in this paper.
+
+%\emph{Text similarity model}  is also called sentence-pair model. 
+%Its  motivation  originates  from  the idea of retrieval based
+%chatbot   \cite{jafarpour2010filter,   leuski2011npceditor}.   Given  a dataset consists of
+%Question-Answer (QA)  pairs and a user query Q, the retrieval based conversational
+%system will search from the dataset  the most matched pair (Q', A') 
+%through  semantic  analysis  and  return  A'  as  the  answer  to Q
+%\cite{mnasri2019recent}. In this way, sentence-pair model pre-trained on large
+%corpus  can be employed  to  identify  the class with highest semantic similarity to
+%customer's    query.    A    common    model    structure    of    pre-trained 
+%sentence-pair model is based on multiple cross-attention
+%mechanism  \cite{barkan2020scalable}. Due to
+%the   fact   that   many   experiment   results   have   shown   that  RoBERTa
+%\cite{liu2019roberta} is an improved version of BERT \cite{devlin2018bert}, and has achieved amazing
+%results  on  both  text  classification and sentence-pairs semantic similarity
+%tasks, we choose RoBERTa as one of the baselines in this paper.
 
@@
 limitations   in   task-specific  chatbot  scenario.  As  for  the  \emph{text
-classification  model},  it  is  quite hard to use data augmentation method to
-solve  the  data insufficiency challenge since the it is usually unfeasible to
+classification  model},  it  is  not  easy to use data augmentation method to
+solve  the  data insufficiency challenge. It is usually unfeasible to
 get  large amount of domain-specific data when facing a new task. With respect
 to  the  \emph{similarity model}, though we can obtain a large amount of data
-from semantically  duplicate  sentence  pair identification domain for transfer
-learning  \cite{sun2019fine},  it  is  still  quite  hard  to  perform well on
+through similar sentence detection  \cite{sun2019fine},  it  is  still  quite  hard  to  perform well on
 a new task-specific dataset,  since their objective losses are totally different.
 
-The  above  limitation motivates us to propose a joint system that is capable of
-taking  advantages  from both classification model and similarity model. We call
-it  SFC,  short  for  similairty model fused with classification Model, shown in
-Fig.  \ref{fig:framework}.  To  better train SFC, we further bring in multi-task
-learning   \cite{caruana1993multitask,collobert2008unified,  liu2019multi}.  Our
-basic  idea  came from two stages. In the first stage, we use an auxiliary model
-to  select  top-K most possible labels for a input. This model can be an elastic
+The  above  limitations motivate us to propose a joint system that is capable of
+taking  advantages  from both the classification and similarity models. We call
+it  as SFC,  short  for  similarity model fused with classification model, shown in
+Fig.  \ref{fig:framework}.  We further bring in multi-task learning   \cite{caruana1993multitask,collobert2008unified,  liu2019multi} to train SFC.  
+Our basic  idea  consists of two stages. In the first stage, we use an auxiliary model
+to  select  top-K most possible labels for an input. This model can be an elastic
 search  \cite{divya2013elasticsearch}  or a text classification model trained on
@@
 application,  and  the similarity loss for the main modules. When the two stages
-are  independently optimized, we call \emph{two-stage SFC}. We further find, the
-the  quality of output from the first stage might limit the final performance of
+are  independently optimized, we call \emph{two-stage SFC}. We further find that
+the  quality of the output from the first stage might limit the final performance of the
 system,  since  the  candidate labels for each user query is always fixed in the
 whole  multi-task  training  process.  This  observation motivates us to further
-improve  the  two-stage  SFC  into a joint training, called \emph{joint SFC}. In
-this  way,  the  sentence  pairs  associated  with the top-K classes also become
+improve  the  two-stage  SFC  into a joint training setting, called \emph{joint SFC}. In
+this  way,  the  candidate texts associated  with the top-K classes also become
 dynamic,  and  the  text  classification  model  in the first stage will also be
-further optimized to provide better top-K result by the final training loss.
+further optimized to provide better top-K results by the final training loss.
 
-We summarize our contributions as follow:
+We summarize our contributions as follows:
 \begin{enumerate}
-  \item We propose a novel joint system to makes full utilization of
-  the advantages from both text classification model and similarity model.
+  \item We propose a novel joint system to makes full use of
+  the advantages from both the text classification and similarity models.
 

### 2020-11-06 chatbot_classification/aaai_2021/rebuttal.txt
renamed:    aaai reviews for rebuttal.pdf -> aaai_reviews_for_rebuttal.pdf   new file:   rebuttal.txt

----------------------------- * For Reviewer #3 * ------------------------------

### Question 1: Was the pre-trained model used in baseline were fine-tuned …

Response:
Thanks  for  your invaluable question. All pre-trained model based baselines are
fine-tuned. Sorry for our careless assumption that in NLP almost all pre-trained
model based systems have to be fine-tuned.

Usually  in our experiments, RoBERTa and BERT model layers are tuned, regardless
of  being  in  baselines or SFC, with a learning rate of 5e-4, and task-specific
layers with a learning rate of 1e-4. This setting is empirically efficient.

Besides, all other settings, like the polynomial decay, Adam optimize, and using
a development set, are the same.

#####  Question  2:  the baseline can be stronger, such as joint-training of NER
and intent detection using BERT.

Response:
Thanks  for such a nice question. We did notice this line of work, introduced in
line 154. We can put the analysis below in our next version. Appreciate.

First,  the  datasets,  usually used for both intent and NER tasks, namely Snips
and ATIS, have quite limited intent number, 7 and 21 respectively. However, they
define  quite  rich  NER  labels,  72  and  120  respectively. In our researched
applications,  the available labeled data is often limited, then NER module in a
joint  model  might not be sufficiently trained. However, for some popular NERs,
address, person, time, city, there are more available data for better training.

Now  considering  a  joint  model,  our  framework  is  still  supportive of NER
training. In the first stage of SFCs, which is a BERT-like classification model,
we  can  trivially develop a fourth objective, as NER. This is a clear effective
idea. Refer to "BERT for Joint Intent Classification and Slot Filling".

However,  the  four  public datasets and one private dataset do not have any NER
information.  Thus,  in  this  work,  we  exclusively compare the classification
performance.

#####  Question  3:  -  There  is  not  much  what  ...  exactly was improved by
introducing the similarity model.

Response: 
Sorry  for  the  unclear explanation. This is really difficult to exactly answer
why.   We   tried  to  explain  this  point  in  "Does  joint  SFC  improve  the
classification  in  stage  1" in the experimental part. Our experiment, table 3,
show  that  SFC  improves  the top-5 accuracy in the first stage, at the cost of
top-1 accuracy, to improve the final performance.

Hope this kind of clarify this issue. Appreciate!

----------------------------- * For Reviewer #4 *  -----------------------------

###  Question  1: "classification model cannot use data augmentation method" and
"similarity  model  doesn't  perform  well  on a new task-specific dataset". Why
putting ... together ...?

Response:
Thanks  for  your  question.  This  is an invaluable opinion that we should have
spent effort to clarify it.

In  the  classification  model,  let  (x, y) be the input feature and label of a
sample.  In  our target application, we need enough labeled data like such pairs
(x,  y).  However, we are lacking of those pairs, except spending lots of effort
labeling them manually. Even though in a second application, we have enough data
like  (x,  y), and because the label definitions of two applications are totally
different,  then  we  have no way to bring the data in the second application to
the first application.

This  is  quite  different  in  the similarity model which only models two x’s
similarity, and this definition is more general. In inference, given a x_new, we
target at searching the most similar x, modeled by similarity(x_new, x), and use
the  label  of  this  x as the label of x_new. Let’s continue with the example
above.  In  the  third application, though its training data is from a different
domain,  yet the similarity model (x1, x2) can be used in the first application,
as the label definitions do not matter here.

I hope this explanation can provide more information for you. Appreciate!

###  Question  2:  How  to solve the error propagation problem?

Response:
Thanks  for  you  in-depth  question.  The  multi-stage  modeling is popular and
inevitable  in  NLP.  Hence  a  general  idea is joint modeling which trains all
stages simultaneously.

Our  two-stage  SFC  does  have  the  issue pointed out by you. Thus, we further
propose  joint  SFC  to  alleviate  this  issues. However, this issue can not be
solved ideally.

Our  table 3 explores the intermediate result in the joint SFC. We can see that,
the  top-5  accuracy  in  the  first  stage  got  improved, at the cost of top-1
accuracy, in exchange of the final improved performance.

I hope this looks a bit clearer for you. Appreciate!

### Question 2: The authors simply putting a classification model and a matching
model together, and the authors haven't made any improvement.

Response: Sorry for confusing you. 
First,  the combination of two rather different models are not trivial, as their
structures  are  hard  to combine efficiently. In comparison, the two losses are
trivial to combine.

In  our practical applications, such as chatbot, we are often facing the problem
of  lacking  sufficient  labeled  data.  The  classification  model  has  a high
accuracy,  while  quite  hard to utilize external data; the similarity is on the
contrary. This is the motivation of combing two models.

I hope this can help you understand better. Appreciate!

----------------------------- * For Reviewer #5 * ------------------------------

###  Question  1: Can you explain the impact of the fine-tuning process on Quora
dataset?

Response:  This  is a really interesting problem. We did notice this issue, yet we
think  this is not influencing the fairness of our model over ALL baselines. Due
to the target workload of experiments, we did not explain much about this issue.
Let's clarify in-depth now.

First the merit of a similarity model is that we can expand our training data.
Due to page limit, could refer to the response to the first question of reviewer
#4?

As  our  researched  problem  is  the  application  without sufficient data, the
similarity  model baseline is also influenced due to insufficient in-domain data
to  a  great extent. Thus, generally the similarity baseline has to use external
data.

Then this merit is naturally inherited in our SFC models. When comparing SFCs to
a  similarity model baseline, our experiments are fair; when comparing SFCs to a
classification, supporting external data is also our advance, which is fair too.
Hence, in order to reduce the explanation workload, we just use this setting.

### Question 2: Will you release you code if your paper were accepted?

Definitely! I am stilling considering how to release the codes without violating
the rule of releasing author information.

----------------------------- * For Reviewer #6 *  -----------------------------

###  Question  1:  The method seems time-consuming, especially the second stage.

Response: thanks for this good question.

Regarding  the  training time: the time of SFCs is actually the summation of the
classification  model  baseline  and  the  similarity  model  baseline.  In  our
settings,  the  classification  model  needs  about  5  hours in a single Nvidia
RTX8000 GPU; the similarity model needs about 12 hours; our model needs about 14
hours due to faster convergence.

Regarding the inference time, the classification model baseline is about 0.2 ms;
the  similarity  model  baseline  is  about  0.5 ms; our joint SFC needs 0.6 ms.
Actually  both  the  similarity  model  baseline  and  our  joint SFC can be GPU
parallelized in the similarity computation, if we need pretty fast response time
in a real product.

As  our  researched problem is the application without sufficient training data,
hence, the extra training cost from the external data might not be a problem.

Thanks for pointing out. We should have included in our paper!

### 2020-11-06 chatbot_classification/aaai_2021/rebuttal.txt
modified:   rebuttal.txt

@@
 
-### Question 2: The authors simply putting a classification model and a matching
+### Question 3: The authors simply putting a classification model and a matching
 model together, and the authors haven't made any improvement.
@@
 
-Response: thanks for this good question.
+Response: Thanks for this good question.  We should have included in our paper!
 
@@
 hence, the extra training cost from the external data might not be a problem.
-
-Thanks for pointing out. We should have included in our paper!

### 2020-11-18 chatbot_classification/naacl_2021/experiments.tex
paper code for naacl

--- 2020-09-10 chatbot_classification/aaai_2021/experiments.tex
@@
 
-The performance of each model is measured in F1 score on the fixed
-test  set  for  each  dataset.  
-Overall,  two-stage  SFC systems in multi-task training deliver  moderate 
-improvements  over  corresponding baselines, and joint SFC deliver more
-significant and consistent improvements over the best baseline, RoBERTa based
-classification. In following content, we dive into more details.
+%The performance of each model is measured in F1 score on the fixed
+%test  set  for  each  dataset.  
+%Overall,  two-stage  SFC systems in multi-task training deliver  moderate 
+%improvements  over  corresponding baselines, and joint SFC deliver more
+%significant and consistent improvements over the best baseline, RoBERTa based
+%classification. In following content, we dive into more details.
 
@@
   \begin{centering}
-    \begin{tabular}{|c|c|c|c|c|}
+    \scalebox{0.85}{
+        \begin{tabular}{|c|c|c|c|}
         \hline
-      F1 score & Two-stage SFC & Joint SFC & Gap & \tabularnewline
+        F1 score & Two-stage SFC & Joint SFC & Gap \tabularnewline
         \hline
-      top-1 accuracy  & \textbf{81.50} & 81.07 & -0.47 & \tabularnewline
-      top-5 accuracy & 94.01 & \textbf{94.30} & +0.29 & \tabularnewline
+        top-1 accuracy  & \textbf{81.50} & 81.07 & -0.47 \tabularnewline
+        top-5 accuracy & 94.01 & \textbf{94.30} & +0.29 \tabularnewline
         \hline
       \end{tabular}
+    }
     \par

### 2020-11-18 chatbot_classification/naacl_2021/methodology.tex
paper code for naacl

--- 2020-09-10 chatbot_classification/aaai_2021/methodology.tex
@@
 \section{Methodology}
-In  this section, we describe our proposed SFC. We propose two approaches to implement this idea,
-two-stage SFC, and its more compact version joint SFC.
+In  this section, we describe our proposed SFC method, which includes the basic two-stage SFC and its more compact version joint SFC.
 
@@
 
-Two-stage   SFC  is  composed  with  two  independent stages  in  charge of
-different  jobs.
+It consists of the following  two  independent stages  in  charge of different  jobs.
 
@@
   \begin{centering}
-    \scalebox{0.9}{
+    \scalebox{0.75}{
       \begin{tabular}{|c|c|c|c|c|c|}
@@
         \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} &
-        \textbf{\#Training Samples} & \textbf{\#Samples/Class} & \textbf{Experimental Settings}\tabularnewline
+        \textbf{\#Training Samples} & \textbf{\#Samples/Class} & \textbf{Settings}\tabularnewline
         \hline 
-        ITG & FAQ chatbot & 228 & 3938 * 0.7 & 17 & 3-fold\tabularnewline
+        ITG & FAQ chatbot & 228 & 3938 * 0.7 & 12 & 3-fold\tabularnewline
         \hline 
@@
   \begin{centering}
-    \scalebox{0.55}{
+    \scalebox{0.45}{
       \begin{tabular}{|c|cccccc|cccccc|cccccc|c|c|}

### 2020-11-18 chatbot_classification/naacl_2021/related_work.tex
paper code for naacl

\section{Related work}
We supplement some work that is very different from classic classification models.

One  line  of  work  is  based  on  label-word  joint  embedding,  such  as LEAM
\cite{wang2018joint}, MTLE \cite{zhang2017multi} and EXAM \cite{du2019explicit}.
It  poses  extral  requirements  on label information. However in our case, many
class  labels  are  close  to  each  other,  and not well-defined. Though we can
present the class label with one of user's utterances from that class, the label
will  become  not  only prolix but also biased.

Another   line   of   interesting   work  is  the  joint  training  of  sentence
classification     and     NER,     such    as    
\cite{kruengkrai2020improving,zhang2020graph,hakkani2016multi,liu2016attention,goo2018slot}.  
For  example,  If  both  the  city and date information are
recognized,  then  they  are good indicators that this query might be booking an
ticket.

### 2020-11-21 chatbot_classification/naacl_2021/experiments.tex
upload ver01

@@
 \subsection{Baselines}
-We choose three kinds of system to construct our baselines.
+We choose three kinds of system to construct our baselines. All our pretrained 
+model baselines are being fine-tuned on all the experimental datasets. Additionally, 
+the similarity model baseline will use the same fine-tuning process on Quora dataset  \cite{iyer2017first} as all our SFC models.
+As our researched problem is the application without sufficient data, the similarity model baseline is influenced due to insufficient in-domain data to a great extent.
+Thus, generally the similarity model baseline has to use external data.
 
@@
 SFC system under various hyperparameter settings.
+
+As for the training time, in our settings, our joint SFC model needs about 14
+hours to reach convergence using a single Nvidia RTX8000 GPU. In comparison, the classification baseline model needs about 5 hours and the similarity baseline model
+needs about 12 hours, which indicates that our joint SFC model spends less training
+time than the summation of two baseline models due to faster convergence.
+
+As for the inference time, the classification model baseline is about 0.2 ms;
+the similarity model baseline is about 0.5 ms and our joint SFC model takes only 0.6 ms.
+Actually both the similarity model baseline and our joint SFC can be GPU
+parallelized in the similarity computation, if we need pretty fast response time
+in a real product.
 
@@
 measured  by  top-1  accuracy.  However,  it  improves  the  quality of top-5
-candidate  class  labels.  It  can  be  explained that, a classification model
+candidate  class  labels, which can further improve the effect of sentence pair
+similarity training. The reason is that, a classification model
 inherently optimizes the objective loss, 0-1 error of top-1 here; the sentence

### 2020-11-21 chatbot_classification/naacl_2021/introduction.tex
paper code for naacl
upload ver01

--- 2020-09-10 chatbot_classification/aaai_2021/introduction.tex
@@
 The  above  limitations motivate us to propose a joint system that is capable of
-taking  advantages  from both the classification and similarity models. We call
-it  as SFC,  short  for  similarity model fused with classification model, shown in
+taking  advantages  from both the classification and similarity models. The similarity
+model can help us involve the data augmentation method to overcome the data insufficiency
+challenge. In the meantime, the candidate labels provided by classification model can 
+effectively reduce the noise for sentence pair semantic similarity task. We call
+our system as SFC,  short  for  similarity model fused with classification model, shown in
 Fig.  \ref{fig:framework}.  We further bring in multi-task learning   \cite{caruana1993multitask,collobert2008unified,  liu2019multi} to train SFC.  
@@
   \begin{centering}
-    \includegraphics[scale=0.72]{picture/picture4} 
+    \includegraphics[scale=0.66]{picture/picture4} 
     \par

### 2020-11-21 chatbot_classification/naacl_2021/related_work.tex
upload ver01

@@
 recognized,  then  they  are good indicators that this query might be booking an
-ticket.
+ticket. Considering a joint model, our framework is supportive of NER
+training using the same method as mentioned in \cite{chen2019bert}. 
+However in our case, the four public datasets and one private dataset we are using
+do not have any NER information. Thus, in this work, we exclusively compare the classification
+performance.

### 2020-11-24 chatbot_classification/naacl_2021/clear.sh
new file:   build.sh   new file:   clear.sh   new file:   compile.sh   new file:   open.sh

@@ -1,0 +1,12 @@
+find . -iregex ".*\.aux" -exec rm -v {} \;
+find . -iregex ".*\.blg" -exec rm -v {} \;
+find . -iregex ".*\.bbl" -exec rm -v {} \;
+find . -iregex ".*\.brf" -exec rm -v {} \;
+find . -iregex ".*\.idx" -exec rm -v {} \;
+find . -iregex ".*\.loa" -exec rm -v {} \;
+find . -iregex ".*\.lof" -exec rm -v {} \;
+find . -iregex ".*\.log" -exec rm -v {} \;
+find . -iregex ".*\.lot" -exec rm -v {} \;
+find . -iregex ".*\.out" -exec rm -v {} \;
+find . -iregex ".*\.toc" -exec rm -v {} \;
+find . -iregex ".*\.pdfsync" -exec rm -v {} \;

### 2020-11-24 chatbot_classification/naacl_2021/open.sh

@@ -1,0 +1,1 @@
+vim paper.tex abstract.tex introduction.tex related_work.tex methodology.tex experiments.tex conclusion.tex refs.bib

### 2020-11-24 chatbot_classification/naacl_2021/introduction.tex
modified:   introduction.tex   modified:   paper.tex

@@
 human  customer  service  agents  responsible  for  customers' questions. 
-Another one is the speech-based control in
-devices  like  intelligent  speakers, such as Siri, Google home, Baidu Xiaodu,
-and smart home equipments, to name a few. Regardless of whether these conversations belong to
+Another one is intelligent  speakers, e.g. Siri, Google home. 
+Regardless of whether these conversations belong to
 single or  multi-round, an essential technique underlying this type of chatbot is to
@@
 The detected intention  with  its  associated  information  is then mapped into a
-predefined dialog logic graph, from which a suitable response (e.g., conducting 
-expected actions, replying texts or accomplishing some operations, etc)  is returned.
+predefined dialog logic graph, from which a suitable response is returned.
 This  is  the  main  difference  from  a  free chatbot.
@@
 
-Generally  there  are  two  kinds  of  approaches  to  address  this  problem,
-one is based on the \emph{text classification model} that directly maps an input text into a most likely label, and
-the other one is based on the \emph{text similarity  model}  that searches the most similar text to the input and returns the associated label.
+Generally  there  are  two  kinds  of  approaches  to  address  this  problem.
 
-\emph{Text classification}  includes  classic  long  text
+The   first   one,   \emph{text  classification},  includes  classic  long  text
 classification   and   short  text  classification  in  this  scenario.  Besides
-traditional  machine  learning  models  like  SVM \cite{suykens1999least},  
-boosting  tree \cite{tu2005probabilistic},  many work
-\cite{wen2016network}  choose  neural  network  such  as  convolutional neural
-networks (CNNs) \cite{kim2014convolutional,zhang2015character,conneau2016very}
-and       long       short       term       memory       networks      (LSTMs)
-\cite{mousa2017contextual,liu2016recurrent}   to   accomplish   the   task  of
-extracting  semantic  features from limited amount of words. Their common model
-structure  is  adding  a  softmax classifier as the final layer to predict the
-labels.  Another  two  interesting lines of work, label-word joint models, and
-joint  NER  and  classification  are  discussed  in  the related work section.
-Recently,   pre-trained   language   models   on   large  corpus  like  BERT
+traditional  machine  learning models like SVM \cite{suykens1999least}, boosting
+tree  \cite{tu2005probabilistic},  many work \cite{wen2016network} choose neural
+network      such      as      convolutional      neural     networks     (CNNs)
+\cite{kim2014convolutional,zhang2015character,conneau2016very}  and  long  short
+term  memory  networks  (LSTMs)  \cite{mousa2017contextual,liu2016recurrent}  to
+accomplish  the  task  of  extracting  semantic  features from limited amount of
+words.  Another two interesting lines of work, label-word
+joint models, and joint NER and classification are discussed in the related work
+section.  Recently,  pre-trained  language  models  on  large  corpus  like BERT
 \cite{devlin2018bert}  and  RoBERTa  \cite{liu2019roberta}  has been proven more
@@
 \cite{yu2018diverse},     pre-trained     models     based    on    transformers
-\cite{vaswani2017attention} tends to be more helpful to alleviate the dearth of training data.
+\cite{vaswani2017attention}  tends to be more helpful to alleviate the dearth of
+training data.
 
-\emph{Text similarity model}  is usually employed to calculate the similarities between an input text 
-and historical texts in the repository, and returns the associated label of the historical
-text with highest similarity score. 
-One of the state-of-the-art similarity models is based on multiple cross-attention
-mechanism  \cite{barkan2020scalable}.
-Due to the   fact   that   many   experiment   results   have   shown   that  RoBERTa
-\cite{liu2019roberta} is an improved version of BERT \cite{devlin2018bert}, and has achieved amazing
-results  on  both  text  classification and text similarity-related
-tasks, we choose RoBERTa as one of the baselines in this paper.
+The  second  one, \emph{text similarity model}, is usually employed to calculate
+how  similar  between an input text and a historical text in the repository. The
+associated label of the most similar historical text is returned as the label of
+the  text  to  query \cite{jafarpour2010filter,   leuski2011npceditor}.  
+A  popular  and  effective  methodology  is adopting BERT
+\cite{devlin2018bert} and other pretrained models \cite{liu2019roberta} to model
+the similarity model as a binary classification problem.
 
-%\emph{Text similarity model}  is also called sentence-pair model. 
-%Its  motivation  originates  from  the idea of retrieval based
-%chatbot   \cite{jafarpour2010filter,   leuski2011npceditor}.   Given  a dataset consists of
-%Question-Answer (QA)  pairs and a user query Q, the retrieval based conversational
-%system will search from the dataset  the most matched pair (Q', A') 
-%through  semantic  analysis  and  return  A'  as  the  answer  to Q
-%\cite{mnasri2019recent}. In this way, sentence-pair model pre-trained on large
-%corpus  can be employed  to  identify  the class with highest semantic similarity to
-%customer's    query.    A    common    model    structure    of    pre-trained 
-%sentence-pair model is based on multiple cross-attention
-%mechanism  \cite{barkan2020scalable}. Due to
-%the   fact   that   many   experiment   results   have   shown   that  RoBERTa
-%\cite{liu2019roberta} is an improved version of BERT \cite{devlin2018bert}, and has achieved amazing
-%results  on  both  text  classification and sentence-pairs semantic similarity
-%tasks, we choose RoBERTa as one of the baselines in this paper.
+Despite  the  success  of  these two approaches, they still have some
+limitations.  
+Regarding  the  \emph{text  classification  model}, when the labeled data in current
+domain  is  insufficient,  it  is  quite  hard  to adopt labeled data from other
+domains, as their label definitions are often incompatible to each other. Though
+we can use some paraphrasing methods, e.g., machine translation based, to expand
+the labeled data, the resulting benenift is still limited.
+Regarding the  \emph{similarity model}, the foremost advantage is it does not pose
+any restriction on label definition in a domain, as it merely models the
+similarity of two input texts. Thus, we may borrow plenty of extra data to help
+the similarity model training in current domain \cite{sun2019fine}. 
+Yet, its biggest disadvantage is its optimization loss differs from that in a
+specific task. This always lead to a suboptimial model.
 
-Despite  the  success  of  these two kinds of approaches, they still have some
-limitations   in   task-specific  chatbot  scenario.  As  for  the  \emph{text
-classification  model},  it  is  not  easy to use data augmentation method to
-solve  the  data insufficiency challenge. It is usually unfeasible to
-get  large amount of domain-specific data when facing a new task. With respect
-to  the  \emph{similarity model}, though we can obtain a large amount of data
-through similar sentence detection  \cite{sun2019fine},  it  is  still  quite  hard  to  perform well on
-a new task-specific dataset,  since their objective losses are totally different.
-
-The  above  limitations motivate us to propose a joint system that is capable of
-taking  advantages  from both the classification and similarity models. The similarity
-model can help us involve the data augmentation method to overcome the data insufficiency
-challenge. In the meantime, the candidate labels provided by classification model can 
-effectively reduce the noise for sentence pair semantic similarity task. We call
-our system as SFC,  short  for  similarity model fused with classification model, shown in
+The  above  limitations motivate us to propose a system that 
+takes both the performance of a classification model and the ability of
+supporting out-of-domain data from a similarity model.
+We call our system as SFC,  short  for  similarity model fused with classification model, shown in
 Fig.  \ref{fig:framework}.  We further bring in multi-task learning   \cite{caruana1993multitask,collobert2008unified,  liu2019multi} to train SFC.  
@@
 application,  and  the similarity loss for the main modules. When the two stages
-are  independently optimized, we call \emph{two-stage SFC}. We further find that
+are  independently optimized, we call \emph{two-stage SFC}.
+
+We further find that
 the  quality of the output from the first stage might limit the final performance of the
-system,  since  the  candidate labels for each user query is always fixed in the
+system,  since  the  candidate labels for an input is fixed in the
 whole  multi-task  training  process.  This  observation motivates us to further
@@
 
-We summarize our contributions as follows:
-\begin{enumerate}
-  \item We propose a novel joint system to makes full use of
-  the advantages from both the text classification and similarity models.
-
-  \item To  better  train such a system, we bring in multi-task training to obtain
-  reasonable performance.
-
-  \item Experiment  results  from 4 public and 1 private short-text classification
-  datasets,  show  that  our  proposed  SFC joint system can achieve significant
-  and consistent improvements over strong baselines, especially in the low resource settings.
-\end{enumerate}
+Experiment  results  from  4  public  and  1  private  short-text classification
+datasets,  show  that  our proposed SFC joint system can achieve significant and
+consistent  improvements  over  strong baselines, especially in the low resource
+settings.
 

### 2020-11-24 chatbot_classification/naacl_2021/abstract.tex
paper code for naacl
ver 02

--- 2020-09-10 chatbot_classification/aaai_2021/abstract.tex
@@
   underlying these applications  is to detect the real intention behind a user's input.
-  The intention detection,  assuming  only  one  intention  in  a  user's input here, can be
+  Intention detection,  assuming  only  one  intention  in  a  user's input here, can be
   regarded  as  a  short  text  classification problem.  In  practice,  the  number  of
@@
   novel  model, called similarity model fused with classification model (SFC),
-  which  combines  a  classification  model  and  a similarity model, and also
-  borrows  the  power  of  multi-task  training  as well. We conduct extensive
+  which combines both the performance of a classification model and the ability of supporting out-of-domain data from a similarity model
+  in the framework of multi-task  training. We conduct extensive
   experiments  on  4  public  and 1 private datasets. Experimental results

### 2020-11-24 chatbot_classification/naacl_2021/open.sh

@@ -1,1 +1,1 @@
-vim paper.tex abstract.tex introduction.tex related_work.tex methodology.tex experiments.tex conclusion.tex refs.bib
+vim paper.tex abstract.tex introduction.tex related_work.tex methodology.tex experiments.tex conclusion.tex appendix.tex refs.bib 

### 2021-01-23 chatbot_classification/acl_2021/experiments.tex
upload paper in acl_2021 format

--- 2020-11-18 chatbot_classification/naacl_2021/experiments.tex
@@
 \begin{enumerate}
-  \item \emph{ITG},  is  a proprietory FAQ dataset from real-world
+  \item \emph{ITG},  is  a proprietary FAQ dataset from real-world
   chatbot  project,  which is composed of question and answer pairs about online
@@
   labels \cite{casanueva2020efficient}.
+
+  \item \emph{FRAMES}, is a collection of multi-domain dialogues dealing with
+hotel bookings. The raw data is consists of 1369 human-human
+dialogues with slot filling information. There are 30,522 utterances in total for 21 intents and 49 slots \cite{asri2017frames}.
+
+  \item \emph{ATIS}, is a popular dataset for intent detection of flight reservations with slot filling\cite{tur2010left}.
+The raw data's training, development and test sets contain 4,478, 500 and 893 utterances, respectively.
+There are 120 slot labels and 21 intent types for the training set.
+
 \end{enumerate}
@@
 respectively,  and  report  the  averaged  testing results. Regarding the last
-three datasets, we conduct experiments using a sampling method similar to that
+five datasets, we conduct experiments using a sampling method similar to that
 in   \cite{casanueva2020efficient}   yet  in  a  more  sophisticated  few-shot
 settings.  We  fix  a  test  data for each one, and examine their performances
-using  5,  10,  15,  20,  30,  and 50 samples per class label respectively for
+using  5,  10,  15,  20,  30,  or 50 samples per class label respectively for
 training.  This  is important, as in practice, a task-specific chatbot usually
@@
 \subsection{Baselines}
-We choose three kinds of system to construct our baselines.
+We  choose  three kinds of system as our baselines. All our pretrained
+model   baselines  are  fine-tuned  on  our datasets.
+Especially, the similarity  model  baseline  and all similarity modules in SFCs
+use extra Quora  dataset  \cite{iyer2017first}  to enhance system performance.
 
@@
   labels for the similarity model, to guarantee a reasonable running time.
+
+  \item \emph{Pre-trained model based text classification and NER joint model}.
+Considering  a  joint  model,  our  SFC framework  is also supportive of NER task.
+That  is  in  stage  1,  based on the  output  states from a
+pretrained model, we can derive a fourth task for NER loss.
+For performance comparison, we choose the state-of-the-art model, which is RoBERTa-large with NER loss, using the same model structure with \cite{chen2019bert}, as our baseline.
 \end{enumerate}
@@
 Our SFC systems include two-stage SFC with ablation, trained with two tasks
-separately and both, and joint SFC with all three tasks.
-
-\subsection{Implementation Details}
-For  our  SFC  systems,  we  use RoBERTa-large as the pretrained model for both
-classification  task  and  sentence-pair similarity task. We fine-tune
-our  SFC  system  on  our datasets with max sequence length of 128,
-learning  rate  of 1.5e-5 for RoBERTa-large pretrained model and learning rate
-of  5e-4  for  task-specific  layer  with polynomial decay and Adam optimizer.
-
-In two-stage SFC, in equ. \ref{eq:two-stage_SFC_loss} the weights of two tasks
-are  set  as  $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting. The reason
-for  giving  task  2 relatively more weights is that according to the ablation
-experiments  we  did  in Section \ref{sec:exp}, task 2 contributes more to the
-overall  performance.  In  joint  SFC,  in  equ.  \ref{eq:joint_SFC_loss}, the
-weights  of  three  tasks  are  set  as  $\alpha_S=0.25$,  $\alpha_K=0.25$ and
-$\alpha_C=0.5$  in  our setting. Overall, the task weights are less sensitive
-in Joint SFC than in two-stage SFC.
-
-For  the  experiments  in  Table  \ref{tbe:table2},  we  empirically  set  the
-hyperparameter  to  be  $K=5$  and  $P=10$  for  all  SFC  variants.  In Table
-\ref{tbe:table3},  we  conduct extensive experiments to see the performance of
-SFC system under various hyperparameter settings.
+separately and both, and joint SFC with all three tasks. All setting details can
+be found in the appendix due to the space limitation.
 
@@
 
-%The performance of each model is measured in F1 score on the fixed
-%test  set  for  each  dataset.  
-%Overall,  two-stage  SFC systems in multi-task training deliver  moderate 
-%improvements  over  corresponding baselines, and joint SFC deliver more
-%significant and consistent improvements over the best baseline, RoBERTa based
-%classification. In following content, we dive into more details.
-
 \subsubsection*{Are multi-task and joint training working?} 
@@
 brought  by  multi-task  and  joint-model  structure.
+
+\begin{table}
+  \begin{centering}
+    \scalebox{0.58}{
+      \begin{tabular}{|c|ccc|ccc|}
+        \hline
+        \multicolumn{1}{|c|}{\multirow{2}*{\textbf{Models}} }& \multicolumn{3}{c|}{\textbf{FRAMES}}& \multicolumn{3}{c|}{\textbf{ATIS}}\tabularnewline
+        \cline{2-7}
+        \multicolumn{1}{|c|}{} & $\textbf{10}$ & $\textbf{20}$ & $\textbf{50}$
+        & $\textbf{10}$ & $\textbf{20}$ & $\textbf{50}$\tabularnewline
+        \hline
+        RoBERTa-large & \multirow{2}*{${0.3456}$} &
+        \multirow{2}*{${0.4043}$} & \multirow{2}*{${0.4262}$} &
+        \multirow{2}*{${0.9349}$} & \multirow{2}*{${0.9757}$} & 
+        \multirow{2}*{${0.9800}$}\tabularnewline
+        (classification) & & & & & & \tabularnewline
+        \hline
+        RoBERTa-large & \multirow{2}*{${0.3520}$} &
+        \multirow{2}*{${0.4088}$} & \multirow{2}*{${0.4353}$} &
+        \multirow{2}*{${0.9560}$} & \multirow{2}*{${0.9706}$} & 
+        \multirow{2}*{${0.9832}$}\tabularnewline
+        (classification w/ NER) & & & & & & \tabularnewline
+        \hline
+        Joint SFC & \multirow{2}*{${0.3843}$} &
+        \multirow{2}*{${0.4130}$} & \multirow{2}*{${0.4390}$} &
+        \multirow{2}*{${0.9404}$} & \multirow{2}*{${0.9761}$} & 
+        \multirow{2}*{${0.9825}$}\tabularnewline
+        (w/o NER) & & & & & & \tabularnewline
+        \hline
+        Joint SFC & \multirow{2}*{$\textbf{0.3925}$} &
+        \multirow{2}*{$\textbf{0.4420}$} & \multirow{2}*{$\textbf{0.4456}$} &
+        \multirow{2}*{${0.9442}$} & \multirow{2}*{${0.9729}$} & 
+        \multirow{2}*{${0.9826}$}\tabularnewline
+        (w/ NER) & & & & & & \tabularnewline
+        \hline
+      \end{tabular}
+    }
+
+  \end{centering}
+  \caption{F1 scores on two task-specific datasets for joint training of sentence classification and NER in chatbot domain under low resource.
+For both FRAMES and ATIS, we set up various few-shot settings(10/20/50 samples per intent) while keeping the original test set.}
+  \label{tbe:addtional ner experiments}
+\end{table}
 
@@
 \subsubsection*{Is  the  fusion of classification and similarity models
-helpful?}  We  compare  joint SFC with classification and similarity based
-baselines respectively.
+helpful?}  We  compare  joint SFC with classification, similarity and NER joint model based baselines respectively.
 
@@
     hyperparameters, $K$  denoting the candidate class number from stage 1,
-    $P$ denoting the number of sampled sententence pair in stage 2. 
+    $P$ denoting the number of sampled sentence pair in stage 2. 
   }
@@
 by 2.04 percent points on average F1 score over 5 datasets.  
-Especially, ALBERT.xxlarge based is rather unstable  in this senario. Thus, 
+Especially, ALBERT.xxlarge based is rather unstable  in this scenario. Thus, 
 we did multiple run with different settings and  report the  best  ones here. 
@@
 
-The above analysis illustrates that suitable fusing the two kinds of models
+As for the intent classification and NER joint model, we choose the state-of-the-art RoBERTa-large model with NER loss as our baseline.
+For ablation study, we did experiments on Joint SFC model with and without NER loss respectively.
+Our Joint SFC without NER loss still outperforms RoBERTa with NER loss baseline by 1.34 percent points on average.
+This indicates that the fusion of classification and similarity can even works better than utilizing additional NER information under few-shot chatbot scenario.
+Moreover, our Joint SFC with NER loss achieves further improvement by 2.80 percent points over RoBERTa with NER loss baseline.
+In this way, we show the compatibility of our Joint SFC model with extra semantic information.
+
+The above analysis illustrates that suitable fusing these two kinds of models
 can take their advantages.
@@
 measured  by  top-1  accuracy.  However,  it  improves  the  quality of top-5
-candidate  class  labels.  It  can  be  explained that, a classification model
+candidate  class  labels, which can further improve the effect of sentence pair
+similarity training. The reason is that, a classification model
 inherently optimizes the objective loss, 0-1 error of top-1 here; the sentence
-pair similairity model in the joint SFC poses more positive effect in optimizing the 
+pair similarity model in the joint SFC poses more positive effect in optimizing the 
 candidate labels.
@@
 model.
-
-\subsubsection*{Settings  of  hyperparameters} 
-In  Table \ref{tbe:table3}, we explore the influence from hyperparameters, which
-are  the  number  of  candidate  class  labels $K$ in stage 1, and the number of
-sampled  sentence  pairs  for  each class $P$ in stage 2, on ITG and Amazon-670K
-datasets.  As we control the total number of sampled sentence pairs to about 50 to 60, we
-roughly obatin five combinations of hyperparameters.
-
-We find  that the best setting of hyperparameters is different from datasets
-of  different  data  size.  The  class label number of ITG and Amazon-670k are
-similar  in  our  experimental setting, which is around 250. However the total
-amount of data points of ITG is approximately 2 times larger than Amazon-670k.
-Therefore,  the  setting of $K=5$ and $P=10$ is good enough for ITG since most
-of  the  classes  contains  over 10 data points. However, for Amazon-670k, the
-amount  of  data  sample  for  each  class  is  scarce, thus, we may need more
-candidate  classes to sample enough effective sentence pairs for sentence-pair
-model  layer  of  SFC.  In this way, the setting of $K=10$ and $P=5$ becomes a
-good choice.
-
-However,  in  spite of the effect on evaluation performance brought by different
-settings  of hyperparameters, joint SFC still steadily outperforms two-stage SFC
-by  0.41  percent  points  in  overall  average  F1 score on ITG and Amazon-670k
-datasets.

### 2021-01-23 chatbot_classification/acl_2021/methodology.tex
upload paper in acl_2021 format

--- 2020-11-18 chatbot_classification/naacl_2021/methodology.tex
@@
         \hline 
-        HWU64 & intention detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
+        HWU64 & intent detect & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
         \hline 
-        CLINC150 & intention detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
+        CLINC150 & intent detect & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
         \hline 
-        BANKING77 & intention detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
+        BANKING77 & intent detect & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
+        \hline 
+        FRAMES & intent detect with ner & 21 & [208, 408, 984] & [10, 20, 50] & data sampling\tabularnewline
+        \hline
+        ATIS & inent detect with ner & 21 & [168, 303, 544] & [10, 20, 50] & data sampling\tabularnewline
         \hline
@@
   \caption{
-    F1 scores  on  five  task-specific  datasets text classification in chatbot
+    F1 scores  on  five  task-specific  datasets for text classification in chatbot
     under low resource. For ITG, we keep the full dataset. For Amazon-670k, we

### 2021-01-26 chatbot_classification/acl_2021/experiments.tex
update result analysis for ATIS

@@
 numbers  in  each class.} as the main evaluation measure for all experiments in
-Table \ref{tbe:table2}.
+Table \ref{tbe:table2} and Table \ref{tbe:addtional ner experiments}.
 
@@
         \multirow{2}*{${0.9560}$} & \multirow{2}*{${0.9706}$} & 
-        \multirow{2}*{${0.9832}$}\tabularnewline
+        \multirow{2}*{$\textbf{0.9832}$}\tabularnewline
         (classification w/ NER) & & & & & & \tabularnewline
@@
         \multirow{2}*{${0.4130}$} & \multirow{2}*{${0.4390}$} &
-        \multirow{2}*{${0.9404}$} & \multirow{2}*{${0.9761}$} & 
+        \multirow{2}*{${0.9618}$} & \multirow{2}*{${0.9761}$} & 
         \multirow{2}*{${0.9825}$}\tabularnewline
@@
         \multirow{2}*{$\textbf{0.4420}$} & \multirow{2}*{$\textbf{0.4456}$} &
-        \multirow{2}*{${0.9442}$} & \multirow{2}*{${0.9729}$} & 
+        \multirow{2}*{$\textbf{0.9639}$} & \multirow{2}*{$\textbf{0.9784}$} & 
         \multirow{2}*{${0.9826}$}\tabularnewline
@@
 
-As for the intent classification and NER joint model, we choose the state-of-the-art RoBERTa-large model with NER loss as our baseline.
+As for the intent classification and NER joint model, we choose the state-of-the-art RoBERTa-large model with NER loss as our strongest baseline.
 For ablation study, we did experiments on Joint SFC model with and without NER loss respectively.
-Our Joint SFC without NER loss still outperforms RoBERTa with NER loss baseline by 1.34 percent points on average.
-This indicates that the fusion of classification and similarity can even works better than utilizing additional NER information under few-shot chatbot scenario.
-Moreover, our Joint SFC with NER loss achieves further improvement by 2.80 percent points over RoBERTa with NER loss baseline.
-In this way, we show the compatibility of our Joint SFC model with extra semantic information.
+From Table \ref{tbe:addtional ner experiments}, we can see that our Joint SFC without NER loss still outperforms RoBERTa with NER loss baseline by 0.86 percent points on average.
+This indicates that the fusion of classification and similarity can even works better than fusing with additional NER information under few-shot chatbot scenario.
+Moreover, after adding NER loss to Joint SFC, it achieves further improvement by 1.66 percent points over RoBERTa with NER loss baseline.
+Especially for FRAMES dataset, which is a much more difficult task in comparison with ATIS, our Joint SFC with NER loss achieves a bigger improvement of 2.8 percent points on average.
+In this way, we show the compatibility of our Joint SFC model with extra semantic information, as well as the stable outstanding performance of Joint SFC when facing hard tasks with few training data.
 

### 2021-01-28 chatbot_classification/acl_2021/experiments.tex
update Experiments part

@@
 environment  popular  in  the  task-specific conversational chatbot application.
-Hence we choose and configure set datasets to serve this study. Different from
+Hence we choose and configure datasets to serve this study. Different from
 the  datasets from other short text classification research, such as semantics
 classification  with  very  limited  semantics labels and relatively longer
-input,   the   datasets  adopted  in  our  experiments  are  typically  having
+input,   the   datasets  adopted  in  our  experiments   typically  contain
 comparatively  large  number  of  class labels, ranging from several dozens to
@@
 queries with each  query  being usually  one  sentence. Table \ref{tbe:dataset
-statistic} displays their statistics.  All settings of four public datasets would 
+statistic} displays their statistics.  All settings of six public datasets would 
 be released to github soon.
@@
   correspond  to  multiple  class labels, we keep only the first one. We further
-  filter  out the class labels that each one is associated with only 5 to 15 samples,
-  or  reviews,  to  mimic  the  chatbot scenario. From them, we sample 250 class
-  labels as well as their samples to form a subset with 2658 samples.
+  filter  out the class labels that only associated to training samples within the amount of 5 to 15 to  mimic  the  few-shot chatbot scenario. From them, we sample 250 class
+  labels as well as their training samples to form a subset with 2658 samples.
 
-  \item \emph{HWU64}, is a intention detection dataset designed for
+  \item \emph{HWU64}, is an intention detection dataset designed for
   home  robot  scenario \cite{liu2019benchmarking}. It aims at the specific task
@@
 
-  \item \emph{BANKING77}, is a intention detection dataset for bank
+  \item \emph{BANKING77}, is an intention detection dataset for bank
   customer  services.  The  raw dataset contains 13,084 data points for 77 class
@@
 \subsection{Baselines}
-We  choose  three kinds of system as our baselines. All our pretrained
+We  choose  four kinds of system as our baselines. All our pretrained
 model   baselines  are  fine-tuned  on  our datasets.
@@
 \subsubsection*{Are multi-task and joint training working?} 
-First, we compare the four  SFC  variants to analyze the improvement
+First, we compare the four  SFC  variants shown in Table \ref{tbe:table2} to analyze the improvement
 brought  by  multi-task  and  joint-model  structure.

### 2021-01-29 chatbot_classification/acl_2021/abstract.tex
modified:   abstract.tex   new file:   open.sh   modified:   paper.ver00.pdf

\begin{abstract}
  Task-specific chatbot systems have gained many important applications, such as
  smart  speaker,  customer  service systems. One essential technique, detecting
  intention behind a user's input, can be modeled as a short text classification
  problem.  In  the early stage of buidling a chatbot, collecting enough labeled
  data  for  hundreds  of  thousands  of  user  intention  is expensive. Popular
  classfication models, direct mapping query to intention, have a high precsion,
  while depending on enough task-specific labels information. Similarity models,
  modeling  similarity  of two queries instead, can utilize out-of-domain data,
  while  having  a  relatively  lower  precision,  due  to  the  discrepency  of
  similairty loss and real classification loss. In this work, we propose a novel
  model,  called  similarity  model  fused  with  classification model (SFC), to
  combine  the  merits of the two kinds of models in the framework of multi-task
  training.  Our  extensive  experiments  on  6  public  and  1 private datasets
  demostrate  that  our  systems outperform very strong baselines (i.e., RoBERTa
  based  pretrained  model,  joint model with NER), espeically with insufficient
  data.

\end{abstract}

### 2021-01-29 chatbot_classification/acl_2021/open.sh

@@ -1,0 +1,1 @@
+vim paper.tex abstract.tex introduction.tex related_work.tex methodology.tex experiments.tex conclusion.tex appendix.tex refs.bib 

### 2021-01-29 chatbot_classification/acl_2021/abstract.tex
modified:   abstract.tex   new file:   build.sh   new file:   clear.sh   new file:   compile.sh   modified:   experiments.tex   modified:   introduction.tex   modified:   methodology.tex   modified:   open.sh   modified:   paper.tex

@@
   Task-specific chatbot systems have gained many important applications, such as
-  smart  speaker,  customer  service systems. One essential technique, detecting
-  intention behind a user's input, can be modeled as a short text classification
-  problem.  In  the early stage of buidling a chatbot, collecting enough labeled
-  data  for  hundreds  of  thousands  of  user  intention  is expensive. Popular
-  classfication models, direct mapping query to intention, have a high precsion,
-  while depending on enough task-specific labels information. Similarity models,
+  smart  speaker,  customer  service system. One fundermental module behind them, detecting
+  intent of a user's input, can be modeled as a short text classification
+  problem.  However, in  the early stage of buidling a chatbot, collecting enough labeled
+  data  for  hundreds  of  thousands  of  user  intents is expensive. Popular
+  classfication models, direct mapping a query to an intent, have a high precsion,
+  while depending on enough task-specific labels information. In comparison, similarity models,
   modeling  similarity  of two queries instead, can utilize out-of-domain data,

### 2021-01-29 chatbot_classification/acl_2021/introduction.tex
modified:   abstract.tex   new file:   build.sh   new file:   clear.sh   new file:   compile.sh   modified:   experiments.tex   modified:   introduction.tex   modified:   methodology.tex   modified:   open.sh   modified:   paper.tex

--- 2020-11-24 chatbot_classification/naacl_2021/introduction.tex
@@
 single or  multi-round, an essential technique underlying this type of chatbot is to
-identify  the  real  intention  behind  a  user's  question or reply. 
-The detected intention  with  its  associated  information  is then mapped into a
+identify  the  real  intent  behind  a  user's  question or reply. 
+The detected intent  with  its  associated  information  is then mapped into a
 predefined dialog logic graph, from which a suitable response is returned.
@@
 
-Intention detection in task-specific chatbot  is  a  challenging task due to its inherent properties. First,
+intent detection in task-specific chatbot  is  a  challenging task due to its inherent properties. First,
 a customer's  utterance  within  a conversation is usually quite short. Since it
@@
 examine tons of real system logs for typical user's utterances, and then label
-them  with expected intentions. Therefore, to build a task-specific chatbot with
+them  with expected intents. Therefore, to build a task-specific chatbot with
 high  performance, it is essential to solve the challenge of short-text
@@
 joint models, and joint NER and classification are discussed in the related work
-section.  Recently,  pre-trained  language  models  on  large  corpus  like BERT
+of appendix.  Recently,  pre-trained  language  models  on  large  corpus  like BERT
 \cite{devlin2018bert}  and  RoBERTa  \cite{liu2019roberta}  has been proven more
@@
 we can use some paraphrasing methods, e.g., machine translation based, to expand
-the labeled data, the resulting benenift is still limited.
+the labeled data, the resulting benefit is still limited.
 Regarding the  \emph{similarity model}, the foremost advantage is it does not pose
@@
 Yet, its biggest disadvantage is its optimization loss differs from that in a
-specific task. This always lead to a suboptimial model.
+specific task. This always lead to a suboptimal model.
 

### 2021-01-29 chatbot_classification/acl_2021/compile.sh

@@ -1,0 +1,2 @@
+pdflatex paper 
+open paper.pdf

### 2021-01-29 chatbot_classification/acl_2021/open.sh

@@ -1,1 +1,1 @@
-vim paper.tex abstract.tex introduction.tex related_work.tex methodology.tex experiments.tex conclusion.tex appendix.tex refs.bib 
+vim paper.tex abstract.tex introduction.tex related_work.tex methodology.tex experiments.tex conclusion.tex refs.bib

### 2021-05-10 chatbot_classification/00.aaai_2021/paper.tex
Added indexes.   #renamed:    aaai_2021/README.md -> 00.aaai_2021/README.md

--- 2020-09-10 chatbot_classification/aaai_2021/paper.tex
@@
 \usepackage[switch]{lineno}
-\usepackage{spconf}
+%\usepackage{spconf}
 \usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
@@
 \pdfinfo{
-  /title (Joint training of classification model and similarity model for
-  low-resource text classification in chatbot)
+  /Title (Joint Training of Classification and Similarity Models for Intention Detection in Task-specific Chatbot)
   /Author (no author informmation)

### 2021-05-10 chatbot_classification/01.naacl_2021/appendix.tex
Added indexes.   #renamed:    aaai_2021/README.md -> 00.aaai_2021/README.md

--- 2020-11-21 chatbot_classification/naacl_2021/experiments.tex
@@
-\section{Experiments}
-\label{sec:exp}
+\appendix
 
-\subsection{Datasets}
-Our experiments aim to study the short text classification in the low-resource
-environment  popular  in  the  task-specific conversational chatbot application.
-Hence we choose and configure set datasets to serve this study. Different from
-the  datasets from other short text classification research, such as semantics
-classification  with  very  limited  semantics labels and relatively longer
-input,   the   datasets  adopted  in  our  experiments  are  typically  having
-comparatively  large  number  of  class labels, ranging from several dozens to
-hundreds,  and  each  class  label  is  associated  with  a handful of labeled
-queries with each  query  being usually  one  sentence. Table \ref{tbe:dataset
-statistic} displays their statistics.  All settings of four public datasets would 
-be released to github soon.
+\newpage
+\section{Appendix}
 
-\begin{enumerate}
-  \item \emph{ITG},  is  a proprietory FAQ dataset from real-world
-  chatbot  project,  which is composed of question and answer pairs about online
-  English teaching. It contains 3,938 sample questions for 228 class labels, and
-  each class label corresponds to a unique answer.
+\subsection{Related work}
+We supplement some work that is very different from classic classification models.
 
-  \item \emph{Amazon-670K}, is a customer product review dataset for
-  text  classification  task  from  the  extreme  classification repository. The
-  complete  dataset  contains 670,091 class labels, 285,176 training samples and
-  150,875   testing   samples   \cite{bhatia2016extreme}.  As  each  sample  may
-  correspond  to  multiple  class labels, we keep only the first one. We further
-  filter  out the class labels that each one is associated with only 5 to 15 samples,
-  or  reviews,  to  mimic  the  chatbot scenario. From them, we sample 250 class
-  labels as well as their samples to form a subset with 2658 samples.
+One  line  of  work  is  based  on  label-word  joint  embedding,  such  as LEAM
+\cite{wang2018joint}, MTLE \cite{zhang2017multi} and EXAM \cite{du2019explicit}.
+It  poses  extral  requirements  on label information. However in our case, many
+class  labels  are  close  to  each  other,  and not well-defined. Though we can
+present the class label with one of user's utterances from that class, the label
+will  become  not  only prolix but also biased.
 
-  \item \emph{HWU64}, is a intention detection dataset designed for
-  home  robot  scenario \cite{liu2019benchmarking}. It aims at the specific task
-  of  capturing  the  intention  for  different  user requests to home robot and
-  finding  the corresponding answer. The raw dataset contains 25,716 data points
-  for 64 class labels through crowdsourcing.
+Another   line   of   interesting   work  is  the  joint  training  of  sentence
+classification     and     NER,     such    as    
+\cite{kruengkrai2020improving,zhang2020graph,hakkani2016multi,liu2016attention,goo2018slot}.  
+For  example,  If  both  the  city and date information are
+recognized,  then  they  are good indicators that this query might be booking an
+ticket.
 
-  \item \emph{CLINC150},  is  a dataset designed for task-oriented
-  systems  with  23,700 queries that are short and unstructured for 150 intents,
-  in    the    same   style   made   by   real   users   through   crowdsourcing
-  \cite{larson2019evaluation}.
+\subsection{Settings  of  hyperparameters} 
+In  Table \ref{tbe:table3}, we explore the influence from hyperparameters, which
+are  the  number  of  candidate  class  labels $K$ in stage 1, and the number of
+sampled  sentence  pairs  for  each class $P$ in stage 2, on ITG and Amazon-670K
+datasets.  As we control the total number of sampled sentence pairs to about 50 to 60, we
+roughly obatin five combinations of hyperparameters.
 
-  \item \emph{BANKING77}, is a intention detection dataset for bank
-  customer  services.  The  raw dataset contains 13,084 data points for 77 class
-  labels \cite{casanueva2020efficient}.
-\end{enumerate}
+We find  that the best setting of hyperparameters is different from datasets
+of  different  data  size.  The  class label number of ITG and Amazon-670k are
+similar  in  our  experimental setting, which is around 250. However the total
+amount of data points of ITG is approximately 2 times larger than Amazon-670k.
+Therefore,  the  setting of $K=5$ and $P=10$ is good enough for ITG since most
+of  the  classes  contains  over 10 data points. However, for Amazon-670k, the
+amount  of  data  sample  for  each  class  is  scarce, thus, we may need more
+candidate  classes to sample enough effective sentence pairs for sentence-pair
+model  layer  of  SFC.  In this way, the setting of $K=10$ and $P=5$ becomes a
+good choice.
 
-Regarding  the first two datasets, we conduct 3-fold cross validation experiments
-that   70   percent   as  training,  15  percent  as  validation  and  testing
-respectively,  and  report  the  averaged  testing results. Regarding the last
-three datasets, we conduct experiments using a sampling method similar to that
-in   \cite{casanueva2020efficient}   yet  in  a  more  sophisticated  few-shot
-settings.  We  fix  a  test  data for each one, and examine their performances
-using  5,  10,  15,  20,  30,  and 50 samples per class label respectively for
-training.  This  is important, as in practice, a task-specific chatbot usually
-starts  with  merely  a  handful of labeled data available in the early stage.
-Besides,  in  the  active  learning framework, building an effective auxiliary
-system  with limited resource is also quite important to help developers label
-data more efficiently.
-
-\subsection{Baselines}
-We choose three kinds of system to construct our baselines. All our pretrained 
-model baselines are being fine-tuned on all the experimental datasets. Additionally, 
-the similarity model baseline will use the same fine-tuning process on Quora dataset  \cite{iyer2017first} as all our SFC models.
-As our researched problem is the application without sufficient data, the similarity model baseline is influenced due to insufficient in-domain data to a great extent.
-Thus, generally the similarity model baseline has to use external data.
-
-\begin{enumerate}
-  \item \emph{Pretrained model based classification system}, which consists of
-  BERT \cite{devlin2018bert},  RoBERTa \cite{liu2019roberta},  and  ALBERT  \cite{lan2019albert}  based.  These pretrained
-  models  are  practically  proven  to  achieve  outstanding  performances  in
-  classification task and other NLP tasks.
-
-  \item   \emph{Non-pretrained   model  based  classification  system},  which
-  consists  of  a typical CNN based TextCNN \cite{kim2014convolutional}, and a
-  label-embedding based LEAM \cite{wang2018joint}. Regarding TextCNN, the
-  model is based on output from RoBERTa tokenization, and the kernels are set
-  as 1, 2, 3, 4, 5. Regarding LEAM, a literal class label is required, which
-  is available only in HWU64, CLINC150, BANKING77. Thus, for other two
-  datasets, we have to use its class number instead.  Empirically,
-  a  non-pretrained  model  based  system  are  not  performing  as  well as a
-  pretrained  models  based,  if  both is applicable in some task. Our listing
-  these  non-pretrained model based systems here is to provide a comprehensive
-  performance comparison on our datasets.
-
-  \item   \emph{Pre-trained   model   based   similarity   model}.  We  choose
-  RoBERTa-large  as  our  fundamental  module as our SFC systems are based on
-  RoBERTa  too, and RoBERTa is empirically more effective than other pretrained
-  models  in  the  short  text  classification  task  in  our  experiments. In
-  inference,  we  use  an  elastic search to find a set of potential candidate
-  labels for the similarity model, to guarantee a reasonable running time.
-\end{enumerate}
-
-Our SFC systems include two-stage SFC with ablation, trained with two tasks
-separately and both, and joint SFC with all three tasks.
+However,  in  spite of the effect on evaluation performance brought by different
+settings  of hyperparameters, joint SFC still steadily outperforms two-stage SFC
+by  0.41  percent  points  in  overall  average  F1 score on ITG and Amazon-670k
+datasets.
 
@@
 in a real product.
-
-\subsection{Result Analysis}
-We  report  the F1 score \footnote{In the multi-class and multi-label case, this
-is  the  average  of  the F1 score of each class with weighting depending on the
-numbers  in  each class.} as the main evaluation measure for all experiments in
-Table \ref{tbe:table2}.
-
-%The performance of each model is measured in F1 score on the fixed
-%test  set  for  each  dataset.  
-%Overall,  two-stage  SFC systems in multi-task training deliver  moderate 
-%improvements  over  corresponding baselines, and joint SFC deliver more
-%significant and consistent improvements over the best baseline, RoBERTa based
-%classification. In following content, we dive into more details.
-
-\subsubsection*{Are multi-task and joint training working?} 
-First, we compare the four  SFC  variants to analyze the improvement
-brought  by  multi-task  and  joint-model  structure.
-
-\begin{table}
-  \begin{centering}
-    \scalebox{0.85}{
-        \begin{tabular}{|c|c|c|c|}
-        \hline
-        F1 score & Two-stage SFC & Joint SFC & Gap \tabularnewline
-        \hline
-        top-1 accuracy  & \textbf{81.50} & 81.07 & -0.47 \tabularnewline
-        top-5 accuracy & 94.01 & \textbf{94.30} & +0.29 \tabularnewline
-        \hline
-      \end{tabular}
-    }
-    \par
-  \end{centering}
-  \caption{The average classification accuracy in percentage in stage 1 on all five dataset.}
-  \label{tbe:top1_5_accuracy}
-\end{table}
-
-Comparing with training two-stage SFC with multi-task, training with only task
-1,  namely the sentence pair similarity model, degrades by 0.8 percent
-point  on average, and training with only task 2, namely the top-K based
-classification  task,  degrades  by  0.45  percent  point  on  average.  These
-degradation  indicates  multi-task training in two-stage SFC is helpful for the
-system  performance.  Besides, task 2 plays a relatively more important role in
-multi-task learning, and this aligns with their optimal weight settings.
-
-Joint SFC consistently outperforms two-stage SFC with multi-task training  
-on 5 diverse datasets by 0.95 percents  on  average. 
-This observation supports the idea that the joint model
-structure  can  alleviate  the  limitation  brought by the lack of interaction
-between  two  stages.  In  following analysis, we will focus on the comparison
-between joint SFC and the other baseline models.
-
-\subsubsection*{Is  the  fusion of classification and similarity models
-helpful?}  We  compare  joint SFC with classification and similarity based
-baselines respectively.
-
-\begin{table*}
-  \begin{centering}
-
-    \begin{tabular}{|c|c|c|c|c|c|c|}
-      \hline 
-      \multicolumn{1}{|c|}{\multirow{2}*{Dataset}}&\multicolumn{1}{c|}{\multirow{2}*{Model}}& $K=3$ & $K=5$ & $K=10$ & $K=15$ & $K=20$\tabularnewline
-      \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & $P=20$ & $P=10$ & $P=5$ & $P=4$ & $P=3$\tabularnewline
-      \hline
-      \multicolumn{1}{|c|}{\multirow{2}*{ITG}}& two-stage SFC & $0.8034$ & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
-      \cline{2-7}
-      \multicolumn{1}{|c|}{} & joint SFC & $0.7986$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7918$\tabularnewline
-      \hline
-      \multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& two-stage SFC & $0.7278$ & $0.7364$ & $0.7366$ & $0.7328$ & $0.7204$\tabularnewline
-      \cline{2-7}
-      \multicolumn{1}{|c|}{} & joint SFC & $0.7334$ & $0.7445$ & $0.7516$ & $0.7344$ & $0.7373$\tabularnewline
-      \hline
-    \end{tabular}
-    \par
-  \end{centering}
-  \caption{
-    We  show the performances of SFC from different settings of
-    hyperparameters, $K$  denoting the candidate class number from stage 1,
-    $P$ denoting the number of sampled sententence pair in stage 2. 
-  }
-  \label{tbe:table3}
-\end{table*}
-
-Regarding the  classification  models,  joint SFC
-outperforms RoBERTa-large based, the strongest among all baselines, 
-by 2.04 percent points on average F1 score over 5 datasets.  
-Especially, ALBERT.xxlarge based is rather unstable  in this senario. Thus, 
-we did multiple run with different settings and  report the  best  ones here. 
-Comparatively,  RoBERTa  based is  the  most stable and has the best performance 
-n almost all experiment settings.
-
-Regarding  the  similarity  model,  as  analyzed  above,  we  only  choose the
-RoBERTa-large based implementation as our baseline. Joint SFC achieves more improvement of
-7.09  percent points  on average F1 score.
-
-The above analysis illustrates that suitable fusing the two kinds of models
-can take their advantages.
-
-\subsubsection*{Does joint SFC improve the classification in stage 1?}
-We  compare  the  top-1  prediction and top-5 candidate labels in stage 1 from
-two-stage SFC and joint SFC in Table \ref{tbe:top1_5_accuracy}. We should note
-that  two-stage  SFC  does not optimize the stage 1 model, which is a RoBERTa
-based classification model.
-
-The joint training does not improve the classification performance in stage 1,
-measured  by  top-1  accuracy.  However,  it  improves  the  quality of top-5
-candidate  class  labels, which can further improve the effect of sentence pair
-similarity training. The reason is that, a classification model
-inherently optimizes the objective loss, 0-1 error of top-1 here; the sentence
-pair similairity model in the joint SFC poses more positive effect in optimizing the 
-candidate labels.
-
-\subsubsection*{How does training sample size influence SFC?} 
-We analyze the overall  improvement  trend  of  joint SFC under various few-shot
-settings, and show results in Fig. \ref{fig:trend}.
-
-Our main focus  is  to  study  chatbot  building  in common situation during real-world
-application  where  only  a few sample sentences are available for each class.
-The  experimental  results  for  the  3  diverse  intention detection datasets
-(ClINC150,  BANKING77,  HWU64)  under  few-shot  settings, 5 to 50 samples per
-class,  indicate that our proposed joint SFC can achieve 2.47 percents average
-improvement   over  one  of  the  most  powerful  baseline  models,  which  is
-RoBERTa-large  classification  model.  Moreover,  the  improvement  in F1 score
-becomes  more  and  more prominent with the decrease of data sample number per
-class.
-
-\begin{figure}[t]
-  \begin{centering}
-    \includegraphics[scale=0.2]{picture/improvement_trend.jpg} 
-    \par
-  \end{centering}
-  \caption{
-    Improvements  from  Joint  SFC  over  RoBERTa  based  classification  with
-    different size of training data.
-  }
-  \label{fig:trend}
-\end{figure}
-
-Especially,  in the most extreme few-shot setting with only 5 training samples
-per  class  our joint SFC achieves 4.97 percent points improvements on average
-over  RoBERTa-large classification model. This observation indicates that SFC
-is  especially  well-performed  when being applied during the initial stage of
-building  task-specific  chatbot  system,  where the amount of data sample for
-each class label is extremely scarce.
-
-Furthermore,  our  proposed  joint  SFC can also achieve 2.04 percents average
-improvement  over  RoBERTa-large classification model on all the data settings
-including  the  ones  with  large  scale,  30  to  50  samples per class. This
-indicates that joint SFC can still steadily outperforms pretrained model based
-baseline even if the data size grows bigger. However, the improvement is still
-more prominent when the data is scarce, which makes SFC an excellent model for
-low-resource chatbot scenario.
-
-\subsubsection*{How does joint SFC relate to the label  embedding based  LEAM?}
-LEAM performs consistently better than TextCNN by a large margin in all
-datasets. TextCNN is practically efficiently in task-specific chat
-applications, and LEAM shows its power in modeling labeling information.
-
-LEAM  does not perform as well as SFCs, since the first intuitive reason is it
-does  not use pretrained model as encoding module; and another critical reason
-is  in  task-specific  chat applications, it is common to have many intentions
-that are close to some others with a minor difference, and it is hard and even
-impossible  to  name  each  intention  with  a short clear name. One candidate
-solution  is  setting  a most standard sample as the label of that class. When
-using  non-pretrained  models  base  LEAM,  this is applicable. Yet when using
-pretrained  model  based, as the all labels can be hundreds of thousands, then
-this  can not be accommodated in a poplar 32 G Tesla V100 GPU. Actually, joint
-SFC  can  be  kind  of  understood  as  a  generalization form of LEAM. In the
-scenario when there is no clear class label, the relationship between a sample
-and  a class label is implicitly encoded as that between a sample and another
-sample  from  the  same  class, and this turns into a sentence pair similarity
-model.
-
-\subsubsection*{Settings  of  hyperparameters} 
-In  Table \ref{tbe:table3}, we explore the influence from hyperparameters, which
-are  the  number  of  candidate  class  labels $K$ in stage 1, and the number of
-sampled  sentence  pairs  for  each class $P$ in stage 2, on ITG and Amazon-670K
-datasets.  As we control the total number of sampled sentence pairs to about 50 to 60, we
-roughly obatin five combinations of hyperparameters.
-
-We find  that the best setting of hyperparameters is different from datasets
-of  different  data  size.  The  class label number of ITG and Amazon-670k are
-similar  in  our  experimental setting, which is around 250. However the total
-amount of data points of ITG is approximately 2 times larger than Amazon-670k.
-Therefore,  the  setting of $K=5$ and $P=10$ is good enough for ITG since most
-of  the  classes  contains  over 10 data points. However, for Amazon-670k, the
-amount  of  data  sample  for  each  class  is  scarce, thus, we may need more
-candidate  classes to sample enough effective sentence pairs for sentence-pair
-model  layer  of  SFC.  In this way, the setting of $K=10$ and $P=5$ becomes a
-good choice.
-
-However,  in  spite of the effect on evaluation performance brought by different
-settings  of hyperparameters, joint SFC still steadily outperforms two-stage SFC
-by  0.41  percent  points  in  overall  average  F1 score on ITG and Amazon-670k
-datasets.

### 2021-05-10 chatbot_classification/01.naacl_2021/experiments.tex
Added indexes.   #renamed:    aaai_2021/README.md -> 00.aaai_2021/README.md

--- 2020-11-18 chatbot_classification/naacl_2021/experiments.tex
@@
 
+Considering  a  joint  model,  our  framework  is supportive of NER task same as
+\cite{chen2019bert}.  That  is  in  stage  1,  based  the  output  states from a
+pretrained model, we can derive a fourth task for NER loss. However in our case,
+the  four  public  datasets and one private dataset we are using do not have any
+NER  information.  Thus, in this work, we exclusively compare the classification
+performance.
+
 Our SFC systems include two-stage SFC with ablation, trained with two tasks
-separately and both, and joint SFC with all three tasks.
-
-\subsection{Implementation Details}
-For  our  SFC  systems,  we  use RoBERTa-large as the pretrained model for both
-classification  task  and  sentence-pair similarity task. We fine-tune
-our  SFC  system  on  our datasets with max sequence length of 128,
-learning  rate  of 1.5e-5 for RoBERTa-large pretrained model and learning rate
-of  5e-4  for  task-specific  layer  with polynomial decay and Adam optimizer.
-
-In two-stage SFC, in equ. \ref{eq:two-stage_SFC_loss} the weights of two tasks
-are  set  as  $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting. The reason
-for  giving  task  2 relatively more weights is that according to the ablation
-experiments  we  did  in Section \ref{sec:exp}, task 2 contributes more to the
-overall  performance.  In  joint  SFC,  in  equ.  \ref{eq:joint_SFC_loss}, the
-weights  of  three  tasks  are  set  as  $\alpha_S=0.25$,  $\alpha_K=0.25$ and
-$\alpha_C=0.5$  in  our setting. Overall, the task weights are less sensitive
-in Joint SFC than in two-stage SFC.
-
-For  the  experiments  in  Table  \ref{tbe:table2},  we  empirically  set  the
-hyperparameter  to  be  $K=5$  and  $P=10$  for  all  SFC  variants.  In Table
-\ref{tbe:table3},  we  conduct extensive experiments to see the performance of
-SFC system under various hyperparameter settings.
+separately and both, and joint SFC with all three tasks. All setting details can
+be found in the appendix due to the space limitation.
 
@@
 Table \ref{tbe:table2}.
-
-%The performance of each model is measured in F1 score on the fixed
-%test  set  for  each  dataset.  
-%Overall,  two-stage  SFC systems in multi-task training deliver  moderate 
-%improvements  over  corresponding baselines, and joint SFC deliver more
-%significant and consistent improvements over the best baseline, RoBERTa based
-%classification. In following content, we dive into more details.
 

### 2021-05-10 chatbot_classification/02.acl_2021/abstract.tex
Added indexes.   #renamed:    aaai_2021/README.md -> 00.aaai_2021/README.md

--- 2021-01-29 chatbot_classification/acl_2021/abstract.tex
@@
 \begin{abstract}
-  Task-specific chatbot systems have gained many important applications, such as
-  smart  speaker,  customer  service system. One fundermental module behind them, detecting
-  intent of a user's input, can be modeled as a short text classification
-  problem.  However, in  the early stage of buidling a chatbot, collecting enough labeled
-  data  for  hundreds  of  thousands  of  user  intents is expensive. Popular
-  classfication models, direct mapping a query to an intent, have a high precsion,
-  while depending on enough task-specific labels information. In comparison, similarity models,
-  modeling  similarity  of two queries instead, can utilize out-of-domain data,
-  while  having  a  relatively  lower  precision,  due  to  the  discrepency  of
-  similairty loss and real classification loss. In this work, we propose a novel
-  model,  called  similarity  model  fused  with  classification model (SFC), to
-  combine  the  merits of the two kinds of models in the framework of multi-task
-  training.  Our  extensive  experiments  on  6  public  and  1 private datasets
-  demostrate  that  our  systems outperform very strong baselines (i.e., RoBERTa
-  based  pretrained  model,  joint model with NER), espeically with insufficient
-  data.
+  Task-specific chatbot systems have gained many important applications, such as smart  speaker,  customer  service system. 
+  One fundermental module behind them is detecting intent of a user's input, and can be modeled as a short text classification problem.  
+  However, in  the early stage of buidling a chatbot, collecting enough labeled data  for  hundreds  of  thousands  of  user  intents is expensive. 
+  Popular classfication models, direct mapping a query to an intent, have a high precsion, while depending on enough task-specific labels information. 
+  In comparison, similarity models, modeling  similarity  of two queries instead, can utilize additional out-of-domain data, while  having  a  relatively  lower  precision,  due  to  the  discrepency  of similairty loss and real classification loss.
+  In this work, we propose a novel model,  called  similarity  model  fused  with  classification model (SFC), to combine  the  merits of the two kinds of models in the framework of multi-task training.
+  Our  extensive  experiments  on  6  public  and  1 private datasets demostrate  that  our  systems outperform very strong baselines (i.e., RoBERTa based  pretrained  model,  joint model with NER), espeically with insufficient data.
 

### 2021-05-10 chatbot_classification/02.acl_2021/experiments.tex
Added indexes.   #renamed:    aaai_2021/README.md -> 00.aaai_2021/README.md

--- 2021-01-28 chatbot_classification/acl_2021/experiments.tex
@@
 
-  \item \emph{HWU64}, is an intention detection dataset designed for
+  \item \emph{HWU64}, is an intent detection dataset designed for
   home  robot  scenario \cite{liu2019benchmarking}. It aims at the specific task
-  of  capturing  the  intention  for  different  user requests to home robot and
+  of  capturing  the  intent  for  different  user requests to home robot and
   finding  the corresponding answer. The raw dataset contains 25,716 data points
@@
 
-  \item \emph{BANKING77}, is an intention detection dataset for bank
+  \item \emph{BANKING77}, is an intent detection dataset for bank
   customer  services.  The  raw dataset contains 13,084 data points for 77 class
@@
 application  where  only  a few sample sentences are available for each class.
-The  experimental  results  for  the  3  diverse  intention detection datasets
+The  experimental  results  for  the  3  diverse  intent detection datasets
 (ClINC150,  BANKING77,  HWU64)  under  few-shot  settings, 5 to 50 samples per
@@
 does  not use pretrained model as encoding module; and another critical reason
-is  in  task-specific  chat applications, it is common to have many intentions
+is  in  task-specific  chat applications, it is common to have many intents
 that are close to some others with a minor difference, and it is hard and even
-impossible  to  name  each  intention  with  a short clear name. One candidate
+impossible  to  name  each  intent  with  a short clear name. One candidate
 solution  is  setting  a most standard sample as the label of that class. When

### 2021-05-10 chatbot_classification/02.acl_2021/introduction.tex
Added indexes.   #renamed:    aaai_2021/README.md -> 00.aaai_2021/README.md

\section{Introduction}
\label{sec:intro}

Task-specific  conversational  chatbot  \cite{wen2016network}  has been applied into  many practical products. 
A popular one is the smart speaker, e.g. Alex, Siri, Google home. 
Another important one is the customer service system, which greatly help human agents handle miscellanious customer's questions.
No matter these applications involves single- or  multi-round conversations, a critical step is to identify  the  intent  behind  a  user's  question or response. 
The detected intent  with  its  associated  attributes is then mapped into a predefined dialog logic to obtain a suitable response to return to customers.

In  the early stage  of  building  a  chatbot , sufficient  labeled  data is often expensive to obtain to render the system to achieve a strong performance.
People thus have to filter out enough typical users' utterances from tons of real conversation logs, and label them  with proper intents. 
In practice, this procedure can be improved by active-learning like operations. 
A basic intent detection system with very limited manually labeled data can be built first, and then it filters out a set of potential data with high confidences for humans to label.
The new data is added to train a better system again. 
This procedure iterates until the system reach a high performance.
Therefore, it is meaningful to address the challenge of short-text classification   \cite{sriram2010short, chen2019deep, phan2008learning,yan2009dynamic,hua2015short}   problem   under the few-shot   setting \cite{yu2018diverse}.

Existent approaches for intent detection can be roughly categorized as text classfication model and text similarity model.

The first one,  \emph{text  classification model},  includes a variety of work.
From  traditional  machine  learning models like SVM \cite{suykens1999least}, boosting tree  \cite{tu2005probabilistic},  to neural networks \cite{wen2016network}, such as   convolutional      neural     networks (CNNs) \cite{kim2014convolutional,zhang2015character,conneau2016very}  and  long  short term  memory  networks  (LSTMs)  \cite{mousa2017contextual,liu2016recurrent}, and then to the most popular pretrained language models based, such as BERT \cite{devlin2018bert}, RoBERTa  \cite{liu2019roberta} and etc. 
Especiallaly, pretrained     models     based    \cite{vaswani2017attention}  tends to be more helpful in the few-shot scenario \cite{yu2018diverse, madabushi2020cost}  to alleviate the dearth of training data.
Another two interesting lines of work, label-word joint models, and joint NER and classification are discussed in the related work of appendix.

The  second  one, \emph{text similarity model}, is usually employed to calculate how  similar  between an input text and a historical text in the repository. 
The associated label of the most similar historical text is returned as the label of the  text  to  query \cite{jafarpour2010filter,   leuski2011npceditor}.  
A  popular  and  effective  methodology  is adopting pretrained models to model the similarity calculation as a binary classification problem.

Despite  plenty of success  of  these two methodologies, they still have some limitations in this task especially when data is insufficient.
Regarding  the  \emph{text  classification  model}, it learns a function that directly maps an input query into its expected label.
Its training requires data in the form of a pair of  a query and a task dependent label. 
It is quite hard to adopt labeled data from other domains, as their label definitions are often incompatible to each other. 
Though we can use some data augmentation methods to alleivate the paucity of data,  e.g., translation based paraphrasing methods, the resulting benefit is still limited because of the data being homogeneous, in the case that our labeled data is very insufficient.
Regarding the  \emph{similarity model}, the foremost advantage is it does not pose any restriction on the label definition of user intents, but aims to learn a function that measure how similar of two sentences are. 
Then in the intent detection task, we are only concerned which labeled query is the most similary one to the current input, and then use its label as the output.
This results in a possibility that even though the labeled data in current domain is scarce, we may borrow additional data from another domain to help enhance the similarity model to make a better intent prediction.
Nevertheless, just as every coin has two sides, the high flexibility of similarity model leads to its worse performance compared to a classification model,  because its training loss differs from a classification loss corresponding to the intent detection goal.
More, it requires an auxiliary model to narrow down candidate labeled queries to speed up the calculation, which makes it slow in the speed and tricky in the auxiliary model selection.

The  above  limitations motivate us to propose a system that may take both the high performance from a classification model and the ability of supporting out-of-domain data from a similarity model.
We call our system as SFC,  short  for  similarity model fused with classification model, shown in Fig.  \ref{fig:framework}.  
In order to train effectively, we further borrow the multi-task learning   \cite{caruana1993multitask,collobert2008unified,  liu2019multi}.
Our basic  idea  come naturally, and the first impementation consists of two stages. 
In the first stage, we use an auxiliary model to  select  top-K most possible labels for an input. 
This model can be an elastic search  \cite{divya2013elasticsearch}  or a text classification model trained on current domain.  
In  the  second  stage,  we  build  a classification  model  which is composed of several similarity  modules. 
Then, this structure  derives  two  goals to train towards, the task-specific classification loss ,  and  the similarity loss on both in-domain and out-of-domain data. 
In this version, the two stages are  independently optimized, so we call it \emph{two-stage SFC}.

We further find that the  quality of outputs from the first stage might limit the final performance of the system,  since  those outputs are fixed in the whole system training  procedure.  
This  observation motivates us to continue improving  the  above two-stage  SFC  into a joint training setting, and we call this second version as \emph{joint SFC}. 
In this  way, the first stage model can be optimized by the optimization in the second stage so that it can provide better candidates to improve the performance of the second stage in turn.

Experiment  results  from  6  public  and  1  private  short-text classification datasets,  show  that  our proposed SFC joint system can achieve significant and consistent  improvements  over  strong baselines, especially in the low resource settings.

\begin{figure*}[t]
  \begin{centering}
    \includegraphics[scale=0.66]{picture/picture4} 
    \par
  \end{centering}
  \caption{
    \textbf{Network Structure of SFC:} two-stage SFC and joint-SFC are sharing
    the  same  network  from  stage  1  and  stage 2, with the only difference
    whether two stages being jointly trained.
  }
  \label{fig:framework}
\end{figure*}

### 2021-05-15 chatbot_classification/03.emnlp_2021/build.sh
new file:   03.emnlp_2021

@@ -1,0 +1,4 @@
+pdflatex paper 
+pdflatex paper
+bibtex   paper
+open     paper.pdf

### 2021-05-16 chatbot_classification/03.emnlp_2021/abstract.tex
modified:   abstract.tex   modified:   experiments.tex   modified:   paper.ver00.pdf

\begin{abstract}
  Task-specific chatbot systems have gained many important applications, such as smart  speaker,  customer  service system. 
  One fundamental module behind them is detecting intent of a user's input, and can be modeled as a short text classification problem.  
  However, in  the early stage of building a chatbot, collecting enough labeled data  for  hundreds  of  thousands  of  user  intents is expensive. 
  Popular classification models, direct mapping a query to an intent, have a high precision, while depending on enough task-specific labels information. 
  In comparison, similarity models, modeling  similarity  of two queries instead, can utilize additional out-of-domain data, while  having  a  relatively  lower  precision,  due  to  the  discrepancy  of similarity loss and real classification loss. 
  In this work, we propose a novel model,  called  similarity  model  fused  with  classification model (SFC), to combine  the  merits of the two kinds of models in the framework of multi-task training.  
  Our  extensive  experiments  on  6  public  and  1 private datasets demonstrate  that  our  systems outperform very strong baselines (i.e., RoBERTa based  pretrained  model,  joint model with NER), especially with insufficient data.

\end{abstract}

### 2021-05-16 chatbot_classification/03.emnlp_2021/appendix.tex
modified:   appendix.tex   modified:   experiments.tex   modified:   introduction.tex   modified:   methodology.tex

--- 2021-05-10 chatbot_classification/01.naacl_2021/appendix.tex
@@
 However,  in  spite of the effect on evaluation performance brought by different
-settings  of hyperparameters, joint SFC still steadily outperforms two-stage SFC
+settings  of hyperparameters, joint-SFC still steadily outperforms two-stage SFC
 by  0.41  percent  points  in  overall  average  F1 score on ITG and Amazon-670k
@@
 experiments  we  did  in Section \ref{sec:exp}, task 2 contributes more to the
-overall  performance.  In  joint  SFC,  in  equ.  \ref{eq:joint_SFC_loss}, the
+overall  performance.  In  joint-SFC,  in  equ.  \ref{eq:joint_SFC_loss}, the
 weights  of  three  tasks  are  set  as  $\alpha_S=0.25$,  $\alpha_K=0.25$ and
 $\alpha_C=0.5$  in  our setting. Overall, the task weights are less sensitive
-in Joint SFC than in two-stage SFC.
+in joint-SFC than in two-stage SFC.
 
@@
 
-As for the training time, in our settings, our joint SFC model needs about 14
+As for the training time, in our settings, our joint-SFC model needs about 14
 hours to reach convergence using a single Nvidia RTX8000 GPU. In comparison, the classification baseline model needs about 5 hours and the similarity baseline model
-needs about 12 hours, which indicates that our joint SFC model spends less training
+needs about 12 hours, which indicates that our joint-SFC model spends less training
 time than the summation of two baseline models due to faster convergence.
@@
 As for the inference time, the classification model baseline is about 0.2 ms;
-the similarity model baseline is about 0.5 ms and our joint SFC model takes only 0.6 ms.
-Actually both the similarity model baseline and our joint SFC can be GPU
+the similarity model baseline is about 0.5 ms and our joint-SFC model takes only 0.6 ms.
+Actually both the similarity model baseline and our joint-SFC can be GPU
 parallelized in the similarity computation, if we need pretty fast response time

### 2021-05-16 chatbot_classification/03.emnlp_2021/experiments.tex
modified:   abstract.tex   modified:   experiments.tex   modified:   paper.ver00.pdf
modified:   appendix.tex   modified:   experiments.tex   modified:   introduction.tex   modified:   methodology.tex

--- 2021-05-10 chatbot_classification/02.acl_2021/experiments.tex
@@
 \subsection{Datasets}
-Our experiments aim to study the short text classification in the low-resource
-environment  popular  in  the  task-specific conversational chatbot application.
-Hence we choose and configure datasets to serve this study. Different from
-the  datasets from other short text classification research, such as semantics
-classification  with  very  limited  semantics labels and relatively longer
-input,   the   datasets  adopted  in  our  experiments   typically  contain
-comparatively  large  number  of  class labels, ranging from several dozens to
-hundreds,  and  each  class  label  is  associated  with  a handful of labeled
-queries with each  query  being usually  one  sentence. Table \ref{tbe:dataset
-statistic} displays their statistics.  All settings of six public datasets would 
-be released to github soon.
+Our experiments aim to study the short text classification in the low-resource environment  popular  in  the  task-specific conversational chatbot application.
+The   datasets  adopted  in  our  experiments, showed in \ref{tbe:dataset statistic} \footnote{All settings of six public datasets would be released to github soon.}, typically  contain comparatively  large  number  of  class labels, ranging from several dozens to hundreds,  and  each  class  label  is  associated  with  a handful of labeled queries with each  query  being usually  one  sentence.
 
@@
 
-Regarding  the first two datasets, we conduct 3-fold cross validation experiments
-that   70   percent   as  training,  15  percent  as  validation  and  testing
-respectively,  and  report  the  averaged  testing results. Regarding the last
-five datasets, we conduct experiments using a sampling method similar to that
-in   \cite{casanueva2020efficient}   yet  in  a  more  sophisticated  few-shot
-settings.  We  fix  a  test  data for each one, and examine their performances
-using  5,  10,  15,  20,  30,  or 50 samples per class label respectively for
-training.  This  is important, as in practice, a task-specific chatbot usually
-starts  with  merely  a  handful of labeled data available in the early stage.
-Besides,  in  the  active  learning framework, building an effective auxiliary
-system  with limited resource is also quite important to help developers label
-data more efficiently.
+Regarding  the first two datasets, we conduct 3-fold cross validation experiments that treat 70   percent   as  training,  15  percent  as  validation  and  testing respectively,  and  report  the  averaged  testing results.
+Regarding the last five datasets, we use a sampling method similar to that from \cite{casanueva2020efficient}   yet  in  a  more  sophisticated  few-shot settings.  
+We  fix  a  test  data for each one, and examine their performances using  5,  10,  15,  20,  30,  or 50 samples per class label respectively for training.  
+This  is important, as in practice a task-specific chatbot usually starts  with  merely  a  handful of labeled data available in the early stage.
+Besides,  in  the  active  learning framework, building an effective auxiliary system  with limited resource is also quite important to help developers label new data more efficiently.
 
 \subsection{Baselines}
-We  choose  four kinds of system as our baselines. All our pretrained
-model   baselines  are  fine-tuned  on  our datasets.
-Especially, the similarity  model  baseline  and all similarity modules in SFCs
-use extra Quora  dataset  \cite{iyer2017first}  to enhance system performance.
+Our baselines comprise of four styles of systems.
 
 \begin{enumerate}
-  \item \emph{Pretrained model based classification system}, which consists of
-  BERT \cite{devlin2018bert},  RoBERTa \cite{liu2019roberta},  and  ALBERT  \cite{lan2019albert}  based.  These pretrained
-  models  are  practically  proven  to  achieve  outstanding  performances  in
-  classification task and other NLP tasks.
+  \item   
+  \emph{Non-pretrained   model  based  classification  system},  which consists  of  a typical CNN based TextCNN \cite{kim2014convolutional}, and a label-embedding based LEAM \cite{wang2018joint}. 
+  Regarding TextCNN, the input is from RoBERTa tokenization, and the kernels are set as 1, 2, 3, 4, 5. 
+  Regarding LEAM, a literal class label is required, which is available only in HWU64, CLINC150, BANKING77. 
+  Thus, for other two datasets, we have to use its class number instead.  
+  Empirically, a  non-pretrained  model  based  system  are  not  performing  as  well as a pretrained  models  based in many NLP tasks.
+  Our listing these  non-pretrained model based systems here is serving a comprehensive performance comparison on our datasets.
 
-  \item   \emph{Non-pretrained   model  based  classification  system},  which
-  consists  of  a typical CNN based TextCNN \cite{kim2014convolutional}, and a
-  label-embedding based LEAM \cite{wang2018joint}. Regarding TextCNN, the
-  model is based on output from RoBERTa tokenization, and the kernels are set
-  as 1, 2, 3, 4, 5. Regarding LEAM, a literal class label is required, which
-  is available only in HWU64, CLINC150, BANKING77. Thus, for other two
-  datasets, we have to use its class number instead.  Empirically,
-  a  non-pretrained  model  based  system  are  not  performing  as  well as a
-  pretrained  models  based,  if  both is applicable in some task. Our listing
-  these  non-pretrained model based systems here is to provide a comprehensive
-  performance comparison on our datasets.
+  \item 
+  \emph{Pretrained model based classification system}, which consists of BERT \cite{devlin2018bert},  RoBERTa \cite{liu2019roberta},  and  ALBERT  \cite{lan2019albert}  based.  
+  These pretrained models  are  practically  proven  to  achieve  outstanding  performances  in classification task and other NLP tasks.
 
-  \item   \emph{Pre-trained   model   based   similarity   model}.  We  choose
-  RoBERTa-large  as  our  fundamental  module as our SFC systems are based on
-  RoBERTa  too, and RoBERTa is empirically more effective than other pretrained
-  models  in  the  short  text  classification  task  in  our  experiments. In
-  inference,  we  use  an  elastic search to find a set of potential candidate
-  labels for the similarity model, to guarantee a reasonable running time.
+  \item   
+  \emph{Pre-trained   model   based   similarity   model}.  
+  As RoBERTa is empirically found more effective than other pretrained models  in  the  short  text  classification  task  in  our  experiments, we  choose RoBERTa-large  based implementation.
+  In inference,  we  use  an  elastic search to find a set of potential candidate labels for the similarity model, to guarantee a reasonable running time.
 
-  \item \emph{Pre-trained model based text classification and NER joint model}.
-Considering  a  joint  model,  our  SFC framework  is also supportive of NER task.
-That  is  in  stage  1,  based on the  output  states from a
-pretrained model, we can derive a fourth task for NER loss.
-For performance comparison, we choose the state-of-the-art model, which is RoBERTa-large with NER loss, using the same model structure with \cite{chen2019bert}, as our baseline.
+  \item 
+  \emph{Pre-trained model based joint text classification and NER model}. 
+  We choose the work from \cite{chen2019bert}, which utilizes a RoBERTa-large model to jointly train two losses, as our baseline system.
+  Our  SFC framework  is also conveniently supportive of extra NER loss that in  stage  1 a fourth task for NER loss is trivially derived  based on the  output states from a pretrained model.
+
 \end{enumerate}
 
-Our SFC systems include two-stage SFC with ablation, trained with two tasks
-separately and both, and joint SFC with all three tasks. All setting details can
-be found in the appendix due to the space limitation.
+All our pretrained model   baselines  are  fine-tuned  on  our datasets.
+Especially, the similarity  model  baseline  and all similarity modules in SFCs use extra Quora  dataset  \cite{iyer2017first}  to enhance system performance. 
+This is also one of merits in SFC as it support adopting out-of-domain data in comparison to a classification based model.
+
+Our SFC implementations include three 2-stage SFCs, which uses task 1 and 2 with ablation in Table \ref{tbe:table2} ; one joint-SFC which is trained jointly on all three tasks in Table \ref{tbe:table2}; one joint-SFC with an additional fourth NER task in Table \ref{tbe:addtional ner experiments}.
+
+All setting details can be found in the appendix due to the space limitation.
 
@@
         \hline
-        RoBERTa-large & \multirow{2}*{${0.3456}$} &
-        \multirow{2}*{${0.4043}$} & \multirow{2}*{${0.4262}$} &
-        \multirow{2}*{${0.9349}$} & \multirow{2}*{${0.9757}$} & 
-        \multirow{2}*{${0.9800}$}\tabularnewline
+        RoBERTa-large & \multirow{2}*{${0.3456}$} & \multirow{2}*{${0.4043}$} & \multirow{2}*{${0.4262}$} & \multirow{2}*{${0.9349}$} & \multirow{2}*{${0.9757}$} & \multirow{2}*{${0.9800}$}\tabularnewline
         (classification) & & & & & & \tabularnewline
         \hline
-        RoBERTa-large & \multirow{2}*{${0.3520}$} &
-        \multirow{2}*{${0.4088}$} & \multirow{2}*{${0.4353}$} &
-        \multirow{2}*{${0.9560}$} & \multirow{2}*{${0.9706}$} & 
-        \multirow{2}*{$\textbf{0.9832}$}\tabularnewline
-        (classification w/ NER) & & & & & & \tabularnewline
+        RoBERTa-large & \multirow{3}*{${0.3520}$} & \multirow{3}*{${0.4088}$} & \multirow{3}*{${0.4353}$} & \multirow{3}*{${0.9560}$} & \multirow{3}*{${0.9706}$} & \multirow{3}*{$\textbf{0.9832}$}\tabularnewline
+        (classification & & & & & & \tabularnewline
+        w/ NER) & & & & & & \tabularnewline
         \hline
-        Joint SFC & \multirow{2}*{${0.3843}$} &
+        Joint-SFC & \multirow{2}*{${0.3843}$} &
         \multirow{2}*{${0.4130}$} & \multirow{2}*{${0.4390}$} &
@@
         \hline
-        Joint SFC & \multirow{2}*{$\textbf{0.3925}$} &
+        Joint-SFC & \multirow{2}*{$\textbf{0.3925}$} &
         \multirow{2}*{$\textbf{0.4420}$} & \multirow{2}*{$\textbf{0.4456}$} &
@@
   \end{centering}
-  \caption{F1 scores on two task-specific datasets for joint training of sentence classification and NER in chatbot domain under low resource.
-For both FRAMES and ATIS, we set up various few-shot settings(10/20/50 samples per intent) while keeping the original test set.}
+  \caption{
+    F1 scores for joint sentence classification and NER training. 
+    Regarding both FRAMES and ATIS dataset, we set up various few-shot settings (10/20/50 samples per intent) while fixing the original test set.
+  }
   \label{tbe:addtional ner experiments}
@@
         \hline
-        F1 score & Two-stage SFC & Joint SFC & Gap \tabularnewline
+        F1 score & 2-stage SFC & joint-SFC & Gap \tabularnewline
         \hline
@@
 
-Comparing with training two-stage SFC with multi-task, training with only task
+Comparing with training 2-stage SFC with multi-task, training with only task
 1,  namely the sentence pair similarity model, degrades by 0.8 percent
@@
 classification  task,  degrades  by  0.45  percent  point  on  average.  These
-degradation  indicates  multi-task training in two-stage SFC is helpful for the
+degradation  indicates  multi-task training in 2-stage SFC is helpful for the
 system  performance.  Besides, task 2 plays a relatively more important role in
@@
 
-Joint SFC consistently outperforms two-stage SFC with multi-task training  
+Joint-SFC consistently outperforms 2-stage SFC with multi-task training  
 on 5 diverse datasets by 0.95 percents  on  average. 
@@
 between  two  stages.  In  following analysis, we will focus on the comparison
-between joint SFC and the other baseline models.
+between joint-SFC and the other baseline models.
 
 \subsubsection*{Is  the  fusion of classification and similarity models
-helpful?}  We  compare  joint SFC with classification, similarity and NER joint model based baselines respectively.
+helpful?}  We  compare  joint-SFC with classification, similarity and NER joint model based baselines respectively.
 
-\begin{table*}
+\begin{table}
   \begin{centering}
-
+  \scalebox{0.58}{
     \begin{tabular}{|c|c|c|c|c|c|c|}
@@
       \hline
-      \multicolumn{1}{|c|}{\multirow{2}*{ITG}}& two-stage SFC & $0.8034$ & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
+      \multicolumn{1}{|c|}{\multirow{2}*{ITG}}& 2-stage SFC & $0.8034$ & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
       \cline{2-7}
-      \multicolumn{1}{|c|}{} & joint SFC & $0.7986$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7918$\tabularnewline
+      \multicolumn{1}{|c|}{} & joint-SFC & $0.7986$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7918$\tabularnewline
       \hline
-      \multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& two-stage SFC & $0.7278$ & $0.7364$ & $0.7366$ & $0.7328$ & $0.7204$\tabularnewline
+      \multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& 2-stage SFC & $0.7278$ & $0.7364$ & $0.7366$ & $0.7328$ & $0.7204$\tabularnewline
       \cline{2-7}
-      \multicolumn{1}{|c|}{} & joint SFC & $0.7334$ & $0.7445$ & $0.7516$ & $0.7344$ & $0.7373$\tabularnewline
+      \multicolumn{1}{|c|}{} & joint-SFC & $0.7334$ & $0.7445$ & $0.7516$ & $0.7344$ & $0.7373$\tabularnewline
       \hline
@@
     \par
+  }
   \end{centering}
@@
   \label{tbe:table3}
-\end{table*}
+\end{table}
 
-Regarding the  classification  models,  joint SFC
+Regarding the  classification  models,  joint-SFC
 outperforms RoBERTa-large based, the strongest among all baselines, 
@@
 Regarding  the  similarity  model,  as  analyzed  above,  we  only  choose the
-RoBERTa-large based implementation as our baseline. Joint SFC achieves more improvement of
+RoBERTa-large based implementation as our baseline. Joint-SFC achieves more improvement of
 7.09  percent points  on average F1 score.
@@
 As for the intent classification and NER joint model, we choose the state-of-the-art RoBERTa-large model with NER loss as our strongest baseline.
-For ablation study, we did experiments on Joint SFC model with and without NER loss respectively.
-From Table \ref{tbe:addtional ner experiments}, we can see that our Joint SFC without NER loss still outperforms RoBERTa with NER loss baseline by 0.86 percent points on average.
+For ablation study, we did experiments on joint-SFC model with and without NER loss respectively.
+From Table \ref{tbe:addtional ner experiments}, we can see that our joint-SFC without NER loss still outperforms RoBERTa with NER loss baseline by 0.86 percent points on average.
 This indicates that the fusion of classification and similarity can even works better than fusing with additional NER information under few-shot chatbot scenario.
-Moreover, after adding NER loss to Joint SFC, it achieves further improvement by 1.66 percent points over RoBERTa with NER loss baseline.
-Especially for FRAMES dataset, which is a much more difficult task in comparison with ATIS, our Joint SFC with NER loss achieves a bigger improvement of 2.8 percent points on average.
-In this way, we show the compatibility of our Joint SFC model with extra semantic information, as well as the stable outstanding performance of Joint SFC when facing hard tasks with few training data.
+Moreover, after adding NER loss to joint-SFC, it achieves further improvement by 1.66 percent points over RoBERTa with NER loss baseline.
+Especially for FRAMES dataset, which is a much more difficult task in comparison with ATIS, our joint-SFC with NER loss achieves a bigger improvement of 2.8 percent points on average.
+In this way, we show the compatibility of our joint-SFC model with extra semantic information, as well as the stable outstanding performance of joint-SFC when facing hard tasks with few training data.
 
@@
 
-\subsubsection*{Does joint SFC improve the classification in stage 1?}
+\subsubsection*{Does joint-SFC improve the classification in stage 1?}
 We  compare  the  top-1  prediction and top-5 candidate labels in stage 1 from
-two-stage SFC and joint SFC in Table \ref{tbe:top1_5_accuracy}. We should note
-that  two-stage  SFC  does not optimize the stage 1 model, which is a RoBERTa
+2-stage SFC and joint-SFC in Table \ref{tbe:top1_5_accuracy}. We should note
+that  2-stage  SFC  does not optimize the stage 1 model, which is a RoBERTa
 based classification model.
@@
 inherently optimizes the objective loss, 0-1 error of top-1 here; the sentence
-pair similarity model in the joint SFC poses more positive effect in optimizing the 
+pair similarity model in the joint-SFC poses more positive effect in optimizing the 
 candidate labels.
@@
 \subsubsection*{How does training sample size influence SFC?} 
-We analyze the overall  improvement  trend  of  joint SFC under various few-shot
+We analyze the overall  improvement  trend  of  joint-SFC under various few-shot
 settings, and show results in Fig. \ref{fig:trend}.
@@
 (ClINC150,  BANKING77,  HWU64)  under  few-shot  settings, 5 to 50 samples per
-class,  indicate that our proposed joint SFC can achieve 2.47 percents average
+class,  indicate that our proposed joint-SFC can achieve 2.47 percents average
 improvement   over  one  of  the  most  powerful  baseline  models,  which  is
@@
 Especially,  in the most extreme few-shot setting with only 5 training samples
-per  class  our joint SFC achieves 4.97 percent points improvements on average
+per  class  our joint-SFC achieves 4.97 percent points improvements on average
 over  RoBERTa-large classification model. This observation indicates that SFC
@@
 including  the  ones  with  large  scale,  30  to  50  samples per class. This
-indicates that joint SFC can still steadily outperforms pretrained model based
+indicates that joint-SFC can still steadily outperforms pretrained model based
 baseline even if the data size grows bigger. However, the improvement is still
@@
 
-\subsubsection*{How does joint SFC relate to the label  embedding based  LEAM?}
+\subsubsection*{How does joint-SFC relate to the label  embedding based  LEAM?}
 LEAM performs consistently better than TextCNN by a large margin in all

### 2021-05-16 chatbot_classification/03.emnlp_2021/introduction.tex
modified:   appendix.tex   modified:   experiments.tex   modified:   introduction.tex   modified:   methodology.tex

--- 2021-05-10 chatbot_classification/02.acl_2021/introduction.tex
@@
 Then, this structure  derives  two  goals to train towards, the task-specific classification loss ,  and  the similarity loss on both in-domain and out-of-domain data. 
-In this version, the two stages are  independently optimized, so we call it \emph{two-stage SFC}.
+In this version, the two stages are  independently optimized, so we call it \emph{2-stage SFC}.
 
 We further find that the  quality of outputs from the first stage might limit the final performance of the system,  since  those outputs are fixed in the whole system training  procedure.  
-This  observation motivates us to continue improving  the  above two-stage  SFC  into a joint training setting, and we call this second version as \emph{joint SFC}. 
+This  observation motivates us to continue improving  the  above 2-stage  SFC  into a joint training setting, and we call this second version as \emph{joint-SFC}. 
 In this  way, the first stage model can be optimized by the optimization in the second stage so that it can provide better candidates to improve the performance of the second stage in turn.
+
+Since SFC is in the framework of multi-task training, its inheriently supports adding additional tasks, such as NER, to gain further improvement.
 
@@
   \caption{
-    \textbf{Network Structure of SFC:} two-stage SFC and joint-SFC are sharing
+    \textbf{Network Structure of SFC:} 2-stage SFC and joint-SFC are sharing
     the  same  network  from  stage  1  and  stage 2, with the only difference

### 2021-05-16 chatbot_classification/03.emnlp_2021/methodology.tex
modified:   appendix.tex   modified:   experiments.tex   modified:   introduction.tex   modified:   methodology.tex

--- 2020-11-18 chatbot_classification/naacl_2021/methodology.tex
@@
 \section{Methodology}
-In  this section, we describe our proposed SFC method, which includes the basic two-stage SFC and its more compact version joint SFC.
+In  this section, we describe our proposed SFC method, which includes the basic 2-stage SFC and its more compact version joint-SFC.
 
-\subsection{Two-stage SFC}
+\subsection{2-stage SFC}
 
@@
 
+\vspace{-2em}
 \begin{equation}
@@
 \end{equation}
+\vspace{-2.5em}
 
@@
         \hline 
-        HWU64 & intention detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
+        HWU64 & Intent detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
         \hline 
-        CLINC150 & intention detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
+        CLINC150 & Intent detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
         \hline 
-        BANKING77 & intention detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
+        BANKING77 & Intent detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
+        \hline 
+        FRAMES & Intent detection with NER & 21 & [208, 408, 984] & [10, 20, 50] & data sampling\tabularnewline
+        \hline
+        ATIS & Intent detection with NER & 21 & [168, 303, 544] & [10, 20, 50] & data sampling\tabularnewline
         \hline
@@
 
+\vspace{-1.5em}
 \begin{equation}
@@
 \end{equation}
+\vspace{-2em}
 
 The  second  task  is  \emph{classification  on  top-K classes}. As minimizing
-similarity  loss  is  not  our  final goal in the intention classification, we
+similarity  loss  is  not  our  final goal in the intent classification, we
 bring  back  classification  loss again. In this task, the network is based on
@@
 
+\vspace{-2em}
 \begin{align}
@@
 
+\vspace{-1em}
 \begin{align}
@@
 where
-
 \begin{equation}
@@
 \end{equation}
+\vspace{-1.25em}
 
@@
 \end{align}
+\vspace{-2em}
 
@@
   \begin{centering}
-    \scalebox{0.45}{
+    \scalebox{0.475}{
       \begin{tabular}{|c|cccccc|cccccc|cccccc|c|c|}
@@
         \hline
-        \multirow{2}*{Joint SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.9669}$} & \multirow{2}*{$\textbf{0.9712}$} & \multirow{2}*{$\textbf{0.9821}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.9323}$} & \multirow{2}*{$\textbf{0.9463}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$\textbf{0.7593}$} & \multirow{2}*{$\textbf{0.7772}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline
+        \multirow{2}*{Joint-SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.9669}$} & \multirow{2}*{$\textbf{0.9712}$} & \multirow{2}*{$\textbf{0.9821}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.9323}$} & \multirow{2}*{$\textbf{0.9463}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$\textbf{0.7593}$} & \multirow{2}*{$\textbf{0.7772}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline
         & & & & & & & & & & & & & & & & & & & &\tabularnewline
@@
 
-\subsection{Joint SFC}
-In  two-stage  SFC,  Stage  1  and  stage 2 are separate that there is no deep
+\subsection{Joint-SFC}
+In  2-stage  SFC,  Stage  1  and  stage 2 are separate that there is no deep
 interaction  with each other during training. In this case, the performance of
@@
 
-In  joint  SFC,  classification  model is being placed in lower layer level to
+In  joint-SFC,  classification  model is being placed in lower layer level to
 dynamically  provide  top-K  candidate  class  labels  for  the  sentence-pair
@@
 
-There  are 3 tasks in total during the training process of joint SFC, shown in
+There  are 3 tasks in total during the training process of joint-SFC, shown in
 Fig. \ref{fig:framework}, and the overall loss is also the weighted sum of all
@@
 
+\vspace{-1.5em}
 \begin{align}
@@
 \end{align}
+\vspace{-1.5em}

### 2021-05-17 chatbot_classification/03.emnlp_2021/experiments.tex
modified:   experiments.tex

@@
 
-\begin{enumerate}
-  \item \emph{ITG},  is  a proprietary FAQ dataset from real-world
+\emph{ITG}, is a proprietary FAQ dataset from real-world
 chatbot project, which is composed of question and answer pairs about online
@@
 
-  \item \emph{Amazon-670K}, is a customer product review dataset for
+\emph{Amazon-670K}, is a customer product review dataset for
 text classification task from the extreme classification repository. The
@@
 
-  \item \emph{HWU64}, is an intent detection dataset designed for
+\emph{HWU64}, is an intent detection dataset designed for
 home robot scenario \cite{liu2019benchmarking}. It aims at the specific task
@@
 
-  \item \emph{CLINC150},  is  a dataset designed for task-oriented
+\emph{CLINC150}, is a dataset designed for task-oriented
 systems with 23,700 queries that are short and unstructured for 150 intents,
@@
 
-  \item \emph{BANKING77}, is an intent detection dataset for bank
+\emph{BANKING77}, is an intent detection dataset for bank
 customer services. The raw dataset contains 13,084 data points for 77 class
@@
 
-  \item \emph{FRAMES}, is a collection of multi-domain dialogues dealing with
+\emph{FRAMES}, is a collection of multi-domain dialogues dealing with
 hotel bookings. The raw data is consists of 1369 human-human
@@
 
-  \item \emph{ATIS}, is a popular dataset for intent detection of flight reservations with slot filling\cite{tur2010left}.
+\emph{ATIS}, is a popular dataset for intent detection of flight reservations with slot filling\cite{tur2010left}.
 The raw data's training, development and test sets contain 4,478, 500 and 893 utterances, respectively.
 There are 120 slot labels and 21 intent types for the training set.
-
-\end{enumerate}
 
@@
 \subsection{Baselines}
-Our baselines comprise of four styles of systems.
+Our baselines comprise of \emph{four} styles of systems.
 
-\begin{enumerate}
-  \item   
-  \emph{Non-pretrained   model  based  classification  system},  which consists  of  a typical CNN based TextCNN \cite{kim2014convolutional}, and a label-embedding based LEAM \cite{wang2018joint}. 
+The first one, \emph{Non-pretrained model based classification system}, which consists of a typical CNN based TextCNN \cite{kim2014convolutional}, and a label-embedding based LEAM \cite{wang2018joint}.
 Regarding TextCNN, the input is from RoBERTa tokenization, and the kernels are set as 1, 2, 3, 4, 5. 
@@
 
-  \item 
-  \emph{Pretrained model based classification system}, which consists of BERT \cite{devlin2018bert},  RoBERTa \cite{liu2019roberta},  and  ALBERT  \cite{lan2019albert}  based.  
+The second one, \emph{pretrained model based classification system}, which consists of BERT \cite{devlin2018bert}, RoBERTa \cite{liu2019roberta}, and ALBERT \cite{lan2019albert} based. 
 These pretrained models are practically proven to achieve outstanding performances in classification task and other NLP tasks.
 
-  \item   
-  \emph{Pre-trained   model   based   similarity   model}.  
+The third one, \emph{pretrained model based similarity model}. 
 As RoBERTa is empirically found more effective than other pretrained models in the short text classification task in our experiments, we choose RoBERTa-large based implementation.
@@
 
-  \item 
-  \emph{Pre-trained model based joint text classification and NER model}. 
-  We choose the work from \cite{chen2019bert}, which utilizes a RoBERTa-large model to jointly train two losses, as our baseline system.
-  Our  SFC framework  is also conveniently supportive of extra NER loss that in  stage  1 a fourth task for NER loss is trivially derived  based on the  output states from a pretrained model.
+The fouth one, \emph{pretrained model based joint text classification and NER model}. 
+We choose the work from \cite{chen2019bert} as our baseline system, which utilizes a strong RoBERTa-large model to jointly train two losses.
+Our SFC framework is also conveniently supportive of extra NER loss that in stage 1 a fourth task with a NER loss is trivially derived based on the output states from a pretrained model.
 
-\end{enumerate}
+All pretrained model baselines are fine-tuned on our datasets.
+Especially, the similarity model baseline and all similarity layers in SFCs use extra Quora dataset \cite{iyer2017first} to enhance system performance. 
+This is also one of merits in SFC, as it support adopting out-of-domain data in comparison to a classification based model.
 
-All our pretrained model   baselines  are  fine-tuned  on  our datasets.
-Especially, the similarity  model  baseline  and all similarity modules in SFCs use extra Quora  dataset  \cite{iyer2017first}  to enhance system performance. 
-This is also one of merits in SFC as it support adopting out-of-domain data in comparison to a classification based model.
-
-Our SFC implementations include three 2-stage SFCs, which uses task 1 and 2 with ablation in Table \ref{tbe:table2} ; one joint-SFC which is trained jointly on all three tasks in Table \ref{tbe:table2}; one joint-SFC with an additional fourth NER task in Table \ref{tbe:addtional ner experiments}.
+Our SFC implementations include three 2-stage SFCs using task 1 and 2 with ablation in Table \ref{tbe:table2}; one joint-SFC trained on all three tasks in Table \ref{tbe:table2}; one joint-SFC with an additional fourth NER task in Table \ref{tbe:addtional ner experiments}.
 
@@
   \begin{centering}
-    \scalebox{0.58}{
+    \scalebox{0.65}{
       \begin{tabular}{|c|ccc|ccc|}
@@
     }
+  \end{centering}
 
-  \end{centering}
   \caption{
     F1 scores for joint sentence classification and NER training. 
-    Regarding both FRAMES and ATIS dataset, we set up various few-shot settings (10/20/50 samples per intent) while fixing the original test set.
+    We iterate various sample number per intent and test on original test set.
   }

### 2021-05-17 chatbot_classification/03.emnlp_2021/experiments.tex
modified:   experiments.tex   modified:   methodology.tex

@@
 \label{sec:exp}
+
+\begin{table*}
+  \begin{centering}
+    \scalebox{0.75}{
+      \begin{tabular}{|c|c|c|c|c|c|}
+        \hline 
+        \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} &
+        \textbf{\#Training Samples} & \textbf{\#Samples/Class} & \textbf{Settings}\tabularnewline
+        \hline 
+        ITG & FAQ chatbot & 228 & 3938 * 0.7 & 12 & 3-fold\tabularnewline
+        \hline 
+        Amazon-670k & Product review & 250 & 2658 * 0.7 & 8 & 3-fold\tabularnewline
+        \hline 
+        HWU64 & Intent detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
+        \hline 
+        CLINC150 & Intent detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
+        \hline 
+        BANKING77 & Intent detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
+        \hline 
+        FRAMES & Intent detection with NER & 21 & [208, 408, 984] & [10, 20, 50] & data sampling\tabularnewline
+        \hline
+        ATIS & Intent detection with NER & 21 & [168, 303, 544] & [10, 20, 50] & data sampling\tabularnewline
+        \hline
+      \end{tabular}
+    }
+    \par
+  \end{centering}
+  \caption{Statistics for all datasets and few shot settings.}
+
+  \label{tbe:dataset statistic}
+\end{table*}
 
@@
 
-The first one, \emph{Non-pretrained model based classification system}, which consists of a typical CNN based TextCNN \cite{kim2014convolutional}, and a label-embedding based LEAM \cite{wang2018joint}.
+The first one, \emph{non-pretrained model based classification system}, which consists of a typical CNN based TextCNN \cite{kim2014convolutional}, and a label-embedding based LEAM \cite{wang2018joint}.
 Regarding TextCNN, the input is from RoBERTa tokenization, and the kernels are set as 1, 2, 3, 4, 5. 

### 2021-05-17 chatbot_classification/03.emnlp_2021/experiments.tex
modified:   experiments.tex

@@
 
-\subsubsection*{Are multi-task and joint training working?} 
-First, we compare the four SFC variants shown in Table \ref{tbe:table2} to analyze the improvement
-brought by multi-task and joint-model structure.
-
+\subsubsection*{Multi-task and joint training} 
 \begin{table}
@@
 
-Comparing with training 2-stage SFC with multi-task, training with only task
-1, namely the sentence pair similarity model, degrades by 0.8 percent
-point on average, and training with only task 2, namely the top-K based
-classification task, degrades by 0.45 percent point on average. These
-degradation indicates multi-task training in 2-stage SFC is helpful for the
-system performance. Besides, task 2 plays a relatively more important role in
-multi-task learning, and this aligns with their optimal weight settings.
+Comparing with training 2-stage SFC with multi-task Table \ref{tbe:table2}, training with only task 1, namely the sentence pair similarity model, degrades by 0.8 percentage point on average, and training with only task 2, namely the top-K based classification task, degrades by 0.45 percentage point on average.
+These degradation indicates multi-task training in 2-stage SFC is helpful for the system performance.
+Besides, task 2 plays a relatively more important role in multi-task learning, and this aligns with their optimal weight settings.
 
-Joint-SFC consistently outperforms 2-stage SFC with multi-task training 
-on 5 diverse datasets by 0.95 percents on average. 
-This observation supports the idea that the joint model
-structure can alleviate the limitation brought by the lack of interaction
-between two stages. In following analysis, we will focus on the comparison
-between joint-SFC and the other baseline models.
+Joint-SFC consistently outperforms 2-stage SFC with multi-task training on 5 diverse datasets by 0.95 percentage point on average. 
+Though a joint model structure may bring extra complexity to the system, it does alleviate the error propagation from the first stage and improves the final performance.
 
-\subsubsection*{Is the fusion of classification and similarity models
-helpful?} We compare joint-SFC with classification, similarity and NER joint model based baselines respectively.
+In following analysis, we will focus on the comparison between joint-SFC and the other baseline models.
+
+\subsubsection*{Fusion of classification and similarity models} 
+%We compare joint-SFC with classification, similarity and NER joint model based baselines respectively.
 
@@
   \caption{
-    We show the performances of SFC from different settings of
-    hyperparameters, $K$ denoting the candidate class number from stage 1,
+    We show the performances of SFC from different settings of hyperparameters, $K$ denoting the candidate class number from stage 1,
     $P$ denoting the number of sampled sentence pair in stage 2. 
@@
 
-Regarding the classification models, joint-SFC
-outperforms RoBERTa-large based, the strongest among all baselines, 
-by 2.04 percent points on average F1 score over 5 datasets. 
-Especially, ALBERT.xxlarge based is rather unstable in this scenario. Thus, 
-we did multiple run with different settings and report the best ones here. 
-Comparatively, RoBERTa based is the most stable and has the best performance 
-n almost all experiment settings.
+Regarding the classification models, joint-SFC outperforms RoBERTa-large based, the strongest among all baselines, by 2.04 percentage points on average F1 score over 5 datasets. 
+Especially, ALBERT.xxlarge based is rather unstable in this short sentence task. 
+Thus, we run multiple times with different settings and report the best ones here. 
+Comparatively, RoBERTa based is the most stable and has the best performance almost all experiment settings.
 
-Regarding the similarity model, as analyzed above, we only choose the
-RoBERTa-large based implementation as our baseline. Joint-SFC achieves more improvement of
-7.09 percent points on average F1 score.
+Regarding the similarity model, as analyzed above, we only choose the RoBERTa-large based implementation as our baseline. 
+Joint-SFC achieves more improvement of 7.09 percentage points on average F1 score. 
+This is also understandable, since RoBERTa-large based similarity model does not and also can not train towards the task specific goal.
 
-As for the intent classification and NER joint model, we choose the state-of-the-art RoBERTa-large model with NER loss as our strongest baseline.
-For ablation study, we did experiments on joint-SFC model with and without NER loss respectively.
-From Table \ref{tbe:addtional ner experiments}, we can see that our joint-SFC without NER loss still outperforms RoBERTa with NER loss baseline by 0.86 percent points on average.
-This indicates that the fusion of classification and similarity can even works better than fusing with additional NER information under few-shot chatbot scenario.
-Moreover, after adding NER loss to joint-SFC, it achieves further improvement by 1.66 percent points over RoBERTa with NER loss baseline.
-Especially for FRAMES dataset, which is a much more difficult task in comparison with ATIS, our joint-SFC with NER loss achieves a bigger improvement of 2.8 percent points on average.
-In this way, we show the compatibility of our joint-SFC model with extra semantic information, as well as the stable outstanding performance of joint-SFC when facing hard tasks with few training data.
+The above analysis illustrates that suitable fusing these two kinds of models can take their advantages.
 
-The above analysis illustrates that suitable fusing these two kinds of models
-can take their advantages.
+\subsubsection*{Joint-SFC improves stage 1?}
+We explore the quality of predicted candidate labels in stage 1 from 2-stage SFC and joint-SFC respectively. 
+We should note that 2-stage SFC does not optimize the stage 1 model, namely a RoBERTa based classification model.
 
-\subsubsection*{Does joint-SFC improve the classification in stage 1?}
-We compare the top-1 prediction and top-5 candidate labels in stage 1 from
-2-stage SFC and joint-SFC in Table \ref{tbe:top1_5_accuracy}. We should note
-that 2-stage SFC does not optimize the stage 1 model, which is a RoBERTa
-based classification model.
+From Table \ref{tbe:top1_5_accuracy}, the joint training does not improve the top-1 classification accuracy in stage 1, yet it improves the top-5 accuracy.
+The reason is that, a classification model inherently optimizes the objective loss, 0-1 error of top-1 here; the sentence pair similarity model in joint-SFC poses more positive effect in optimizing the candidate labels.
 
-The joint training does not improve the classification performance in stage 1,
-measured by top-1 accuracy. However, it improves the quality of top-5
-candidate class labels, which can further improve the effect of sentence pair
-similarity training. The reason is that, a classification model
-inherently optimizes the objective loss, 0-1 error of top-1 here; the sentence
-pair similarity model in the joint-SFC poses more positive effect in optimizing the 
-candidate labels.
+\subsubsection*{Supportive of extra NER loss}
+Many previous work shows joint training with a NER loss improves the intent classification task as well, observed again in our baselines and SFCs in Table \ref{tbe:addtional ner experiments}.
+We choose the state-of-the-art RoBERTa-large model with NER loss as a strong baseline.
 
-\subsubsection*{How does training sample size influence SFC?} 
-We analyze the overall improvement trend of joint-SFC under various few-shot
-settings, and show results in Fig. \ref{fig:trend}.
+We can see that our joint-SFC without NER loss still outperforms RoBERTa with NER loss baseline by 0.86 percentage points on average. 
+This indicates that the fusion of classification and similarity models can even works better than fusing with additional NER information under few-shot chatbot scenario.
 
-Our main focus is to study chatbot building in common situation during real-world
-application where only a few sample sentences are available for each class.
-The experimental results for the 3 diverse intent detection datasets
-(ClINC150, BANKING77, HWU64) under few-shot settings, 5 to 50 samples per
-class, indicate that our proposed joint-SFC can achieve 2.47 percents average
-improvement over one of the most powerful baseline models, which is
-RoBERTa-large classification model. Moreover, the improvement in F1 score
-becomes more and more prominent with the decrease of data sample number per
-class.
+Moreover, the adding NER loss to joint-SFC further achieves improvement of 1.66 percentage points over RoBERTa with NER loss baseline. 
+Especially on FRAMES dataset, which is a much more difficult task in comparison with ATIS based on performance of all systems on it, our joint-SFC with NER loss achieves a bigger improvement of 2.8 percentage points on average.
+
+\subsubsection*{Different training sample size} 
+We analyze the overall improvement trend of joint-SFC under various few-shot settings, and show results in Fig. \ref{fig:trend}.
+
+Our main focus is on studying chatbot construction in real world applications, where each class has only a small number of example sentences.
+The experimental results for the 3 diverse intent detection datasets (ClINC150, BANKING77, HWU64) under few-shot settings, 5 to 50 samples per class, indicate that our proposed joint-SFC can achieve average 2.47 percentage points improvement over one of the most powerful baseline models, which is RoBERTa-large classification model.
+Moreover, the improvement in F1 score becomes more and more prominent with the decrease of data sample number per class.
 
@@
   \caption{
-    Improvements from Joint SFC over RoBERTa based classification with
-    different size of training data.
+    Improvements from joint SFC over RoBERTa based classification with different training size.
   }
@@
 
-Especially, in the most extreme few-shot setting with only 5 training samples
-per class our joint-SFC achieves 4.97 percent points improvements on average
-over RoBERTa-large classification model. This observation indicates that SFC
-is especially well-performed when being applied during the initial stage of
-building task-specific chatbot system, where the amount of data sample for
-each class label is extremely scarce.
+Especially, in the most extreme setting with only 5 training samples per class, joint-SFC achieves 4.97 percentage points improvements on average over RoBERTa-large classification model. 
+Joint SFC is a better choice applied into the early stage of building a task-specific chatbot system, since label data is extremely scarce.
 
-Furthermore, our proposed joint SFC can also achieve 2.04 percents average
-improvement over RoBERTa-large classification model on all the data settings
-including the ones with large scale, 30 to 50 samples per class. This
-indicates that joint-SFC can still steadily outperforms pretrained model based
-baseline even if the data size grows bigger. However, the improvement is still
-more prominent when the data is scarce, which makes SFC an excellent model for
-low-resource chatbot scenario.
+Furthermore, joint SFC also achieves average 2.04 percentage points improvement over RoBERTa-large classification model on all the data settings. 
+However, the improvement is still more prominent when the data is scarce, which makes SFC an excellent model for low-resource chatbot scenario.
 
-\subsubsection*{How does joint-SFC relate to the label embedding based LEAM?}
-LEAM performs consistently better than TextCNN by a large margin in all
-datasets. TextCNN is practically efficiently in task-specific chat
-applications, and LEAM shows its power in modeling labeling information.
+\subsubsection*{Relation to the label embedding based LEAM}
+LEAM shows its superiority over TextCNN in all datasets in our experiments, by modeling labeling information.
 
-LEAM does not perform as well as SFCs, since the first intuitive reason is it
-does not use pretrained model as encoding module; and another critical reason
-is in task-specific chat applications, it is common to have many intents
-that are close to some others with a minor difference, and it is hard and even
-impossible to name each intent with a short clear name. One candidate
-solution is setting a most standard sample as the label of that class. When
-using non-pretrained models base LEAM, this is applicable. Yet when using
-pretrained model based, as the all labels can be hundreds of thousands, then
-this can not be accommodated in a poplar 32 G Tesla V100 GPU. Actually, joint
-SFC can be kind of understood as a generalization form of LEAM. In the
-scenario when there is no clear class label, the relationship between a sample
-and a class label is implicitly encoded as that between a sample and another
-sample from the same class, and this turns into a sentence pair similarity
-model.
+LEAM does not perform as well as SFCs, since the first intuitive reason is it does not use a pretrained model as its input encoding module; 
+another critical reason is in task-specific chat applications, it is common to have many similar intents, and it becomes hard and even impossible to name each intent with a short clear name to feed into LEAM model.
+One candidate solution is setting a most standard sample as the label of the class. 
+When using non-pretrained models base LEAM, this is applicable. 
+Yet when using a pretrained model based, as all labels can be hundreds of thousands, then the training can not be accommodated in a poplar 32 G Tesla V100 GPU.
+
+Actually, joint SFC can be kind of understood as a generalization form of LEAM. 
+When there is no clear class labels, the relationship between a sample and a class label is implicitly encoded as that between a sample and another sample from the same class, and this turns into a sentence pair similarity model.

### 2021-05-18 chatbot_classification/03.emnlp_2021/experiments.tex
modified:   experiments.tex   modified:   methodology.tex
  new file:   paper.ver03.pdf

@@
 All pretrained model baselines are fine-tuned on our datasets.
-Especially, the similarity model baseline and all similarity layers in SFCs use extra Quora dataset \cite{iyer2017first} to enhance system performance. 
+Especially, the similarity model baseline and all similarity layers in SFCs use extra Quora dataset \cite{iyer2017first} \footnote{which contains 404,290 potential duplicate question pairs} to enhance system performance.
 This is also one of merits in SFC, as it support adopting out-of-domain data in comparison to a classification based model.

### 2021-05-18 chatbot_classification/03.emnlp_2021/methodology.tex
modified:   experiments.tex   modified:   methodology.tex
modified:   experiments.tex   modified:   methodology.tex
  new file:   paper.ver03.pdf

@@
 \section{Methodology}
-In  this section, we describe our proposed SFC method, which includes the basic 2-stage SFC and its more compact version joint-SFC.
+In this section, we describe our proposed SFC method, which includes a basic 2-stage SFC implementation and a more compact version called joint SFC.
 
@@
 
-It consists of the following  two  independent stages  in  charge of different  jobs.
+We first introduce this most intuitive implementation.
+The outputs of the first stage are fed into the second stage, yet its parameters can not be tuned based on feedback of the second stage.
 
-\subsubsection*{
-  Stage 1: classification model for providing top-K candidate class labels
-} 
-We  can  use any auxiliary text classification model or tool,
-such as Term Frequency-Inverse Document Frequency (TF-IDF)retrieval, to
-provide  top-K  most  related  class  labels. These selected class labels will
-later  be  used to sample sentence pairs of both positive and negative
-samples  for  stage  2.
+\subsubsection*{Stage 1: top-K candidate class labels generation} 
+Any model that generates top-K most related class labels can be adopted in stage 1, such as classification models, term frequency-inverse document Frequency (TF-IDF) based retrieval models.
+Due to the excellent performance of RoBERTa in practice, we use RoBERTa to construct a classification model in this stage.
 
-In  this  work,  we  choose pretrained models to fine tune on our data.
-Due to the excellent performance of RoBERTa in this task, compared to other pretrained
-models, we use RoBERTa as the encoder of classification model in our setting.
-
-Given   a   data   point   $x_{i}$  with  class  label  $y_{i}$  from  dataset
-$\mathcal{D}$, we take the final hidden state $h_{i}$ of the first token [CLS]
-encoded  by  RoBERTa  as the representation for the whole sequence of $x_{i}$.
-Then  a linear layer is followed to output probabilistic distribution of class
-labels,  $softmax(W^Ch_{i}+b^C)=softmax({\Phi}^C_{i})$,  where $W^C$ and $b^C$
-are  trainable  parameters.  Then, the loss in stage 1 classification model is
-shown in Equ. \ref{eq:classification_loss},
+Suppose we have a training dataset $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$, in which $x_{i}$ is the user input query and $y_{i}$ is a single class label in $\{1, \ldots, J\}$. 
+Given $x_i$, we take the final hidden state $h_i$ of the first token [CLS] encoded by RoBERTa as the representation for the whole sequence of $x_i$.
+A linear layer is followed to output unnormalized probabilistic distribution of class labels, ${\Phi}_i^C=W^C h_i + b^C$, where $W^C$ and $b^C$ are class label related trainable parameters. 
+Then, the loss in stage 1 classification model is shown in Equ. \ref{eq:classification_loss},
 
@@
   \begin{aligned}
-    \mathcal{L}^{C}&=\frac{1}{N}\sum_{i=1}^{N}-log(\frac{exp(\varPhi_{i,y_{i}}^C)}{\sum_{j=1}^{C}exp(\varPhi_{i,j}^C)}) \\
+    \mathcal{L}^{C}&=\frac{1}{N} \sum_{i=1}^{N}-log(\frac{exp(\varPhi_{i,y_{i}}^C)}{\sum_{j=1}^{J}exp(\varPhi_{i,j}^C)}) \\
     \label{eq:classification_loss}
@@
 
-\subsubsection*{
-  Stage 2: sentence-pair similarity model based classification with multi-task
-  learning
-}
-We  continue choosing RoBERTa as the main module in this stage that identifies
-the class label with strongest semantic similarity to the user input sentence.
+\subsubsection*{Stage 2: sentence-pair similarity model based multi-task learning}
+We continue choosing RoBERTa to construct main modules in this stage.
 
-Suppose  we have a training dataset $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$ of
-$N$  data  points,  in  which $x_{i}$ is the user input query and $y_{i}$ is a
-single  class label from a class label set of $C$ classes in total. We 
-generate            a sentence            pair            dataset
-$\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$ from $\mathcal{D}$,   where   $(x,   x')_{j}$  is
-a pair of two history queries \footnote{For simplicity, we use query
-to denote a user's question or a response.}, and $l_{j}\in\{0, 1\}$ denotes the
-similarity label that only the ones from the same class label are considered
-similar. The size of $\mathcal{D'}$  would be up to $O(N^2)$ if no any
-sampling strategy is used.  This is quite time-consuming  for the  training
-in stage 2 because $N$ can be several hundreds or thousands even under 
-few shot setting in task-specific chatbot scenario.
+We generate a sentence pair dataset $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$ from $\mathcal{D}$, where $(x, x')_{j}$ is a pair of two history queries \footnote{For simplicity, we use query to denote a user's question or a response.}, and $l_{j}\in\{0, 1\}$ denotes the similarity that only the pair from the same class label is considered similar.
+The size of $\mathcal{D'}$ would be up to $N^2$ without a sampling strategy. 
+This is prohibitively large and time-consuming for model training in stage 2, because $N$ can be several hundreds or thousands even under few shot setting in our scenario.
 
-Therefore,  we  adopt  the idea of adversarial negative sampling strategy from
-the  work  \cite{bamler2020extreme}.  The  key  idea is to train with negative
-samples  that  are hard to be distinguished from positive samples. Now suppose
-we  have  a  user  input query $x_{i}$ and top-K most related class labels set
-$\mathcal{C'}=\{c'_{1},  \dots,  c'_{K}\}$ provided by auxiliary model or tool
-in  stage  1, where $K$ is a hyperparameter to control candidate class number,
-we  apply  the  adversarial  negative sampling strategy into our sentence pair
-sampling process by the following two steps:
+Therefore, we adopt the idea of adversarial negative sampling strategy from the work \cite{bamler2020extreme}. 
+The key idea is to train with negative samples that are hard to be distinguished from positive samples. 
+Now suppose we have a user input query $x_{i}$ and top-$K$ most related class label set $\mathcal{C'}=\{c'_{1}, \dots, c'_{K}\}$ from stage 1, where $K$ is a hyperparameter, we apply the adversarial negative sampling strategy into our sentence pair sampling in two steps:
 
-The  first step is \emph{positive sentence pair sampling}. During the training
-process,  we  first make sure the ground truth class label $y_{i}$ for $x_{i}$
-is  within  the  candidate  class  label  set  $\mathcal{C'}$. If $y_{i}\notin
-\mathcal{C'}$,  we  manually  add  $y_{i}$  into  $\mathcal{C'}$  by replacing
-$c'_{K}$  with  $y_{i}$, since $c'_{K}$ is the least promising candidate label
-according  to  the  auxiliary  model  in stage 1. Afterwards, we will randomly
-sample  $P$ sentences $\{x'_{1}, \dots, x'_{P}\}$ with the same class label as
-$y_{i}$  from  dataset  $\mathcal{D}$  to  form the set of sentence pairs with
-positive  label  $\mathcal{P'}_{i}=\{[(x_{i},  x'_{1}),  1],  \dots,  [(x_{i},
-x'_{P}),  1]\}$,  where $P$ is also a hyperparameter set to control the number
-of sentences we should sample from each class.
+The first step is \emph{positive sentence pair sampling}. 
+In training, we make sure the ground truth class label $y_{i}$ of $x_{i}$ exists in the candidate class label set $\mathcal{C'}$. 
+Otherwise, we have it substitute for the least relevant class label $c'_{K}$. 
+Then, we randomly sample $P$ sentences $\{x'_{1}, \dots, x'_{P}\}$ with the same class label as $y_{i}$ from dataset $\mathcal{D}$ to form the set of sentence pairs with positive label $\mathcal{P'}_{i}=\{[(x_{i}, x'_{1}), 1], \dots, [(x_{i}, x'_{P}), 1]\}$, where $P$ is also a hyperparameter.
 
-\begin{table*}
-  \begin{centering}
-    \scalebox{0.75}{
-      \begin{tabular}{|c|c|c|c|c|c|}
-        \hline 
-        \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} &
-        \textbf{\#Training Samples} & \textbf{\#Samples/Class} & \textbf{Settings}\tabularnewline
-        \hline 
-        ITG & FAQ chatbot & 228 & 3938 * 0.7 & 12 & 3-fold\tabularnewline
-        \hline 
-        Amazon-670k & Product review & 250 & 2658 * 0.7 & 8 & 3-fold\tabularnewline
-        \hline 
-        HWU64 & Intent detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
-        \hline 
-        CLINC150 & Intent detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
-        \hline 
-        BANKING77 & Intent detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
-        \hline 
-        FRAMES & Intent detection with NER & 21 & [208, 408, 984] & [10, 20, 50] & data sampling\tabularnewline
-        \hline
-        ATIS & Intent detection with NER & 21 & [168, 303, 544] & [10, 20, 50] & data sampling\tabularnewline
-        \hline
-      \end{tabular}
-    }
-    \par
-  \end{centering}
-  \caption{Statistics for all datasets and few shot settings.}
+The second step is \emph{negative sentence pair sampling}.
+We also randomly sample $P$ sentences for each class in the negative candidate class label set $\mathcal{C'}\backslash \{y_{i}\}$, which is the more confusing to the expected class label compared to those out of top-$K$ candidate set.
+The resulting sentence pairs are strong adversarial negative samples for sentence-pair similarity model, and they significantly enhance the training speed and performance. 
+We denote them as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{1}), 0], ..., [(x_{i}, x'_{P\cdot K}), 0]\}$
 
-  \label{tbe:dataset statistic}
-\end{table*}
+In this way, we generate the sentence pair dataset $\mathcal{D'}$ for stage 2, based on the top-K class label set $\mathcal{C'}$ from by stage 1, as $\mathcal{D'}=\{\mathcal{P'}_{i}\cup \mathcal{N'}_{i}\}_{i=1}^{N}$, and its size is $M=N\times K\times P$.
 
-The  second  step  is  \emph{negative sentence pair sampling}: As for negative
-sentence  pairs,  we will also randomly sample $P$ sentences for each class in
-the negative candidate class label set $\mathcal{C'}\backslash \{y_{i}\}$. The
-class  labels  in  $\mathcal{C'}\backslash  \{y_{i}\}$  are  the  set  of most
-confusing  class  labels comparing to the ground truth ${y_{i}}$, so we assume
-that  the  sentence  pairs  with  negative  label  grouped by user input query
-$x_{i}$  and sentences with class labels in $\mathcal{C'}\backslash \{y_{i}\}$
-are  strong  adversarial  negative  samples for sentence-pair similarity model
-that  can  help  enhance  the training speed and performance. According to the
-same  method  as  positive  sentence  pair  sampling, we can obtain the set of
-sentence  pairs  with  negative label as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{1}),
-0], ..., [(x_{i}, x'_{P\cdot K}), 0]\}$
-
-In  this way, we generate the sentence pair dataset $\mathcal{D'}$ for stage 2
-based  on  the  top-K  class  label  set $\mathcal{C'}$ provided by stage 1 as
-$\mathcal{D'}=\{\mathcal{P'}_{i}\cup  \mathcal{N'}_{i}\}_{i=1}^{N}$,  in which
-we have $M=N\cdot K\cdot P$ data points of sentence pairs in total.
-
-Before starting to fine-tune our sentence-pair model on task-specific dataset,
-we  first  fine-tune  RoBERTa on Quora dataset  \cite{iyer2017first}, which
-contains  404,290  potential  duplicate question pairs, for transfer learning.
-This  is  also  the  merit of similarity based model, as labeled task-specific
-classification  data  is  hard  to  acquire,  yet  general sentence pairs with
-similar semantics can be much easier to acquire.
+As analyzed before, one advantage of similarity based model is its potential to use out-of-domain data.
+We take this advantage and use extra Quora dataset \cite{iyer2017first} to enhance performance of both baseline and our SFCs.
 
 \subsubsection*{Multi-task based training}
-We   continue  to  do  multi-task  training  on  sentence-pair  dataset
-$\mathcal{D'}$ sampled from the top-K candidate class labels provided by stage
-1. In stage 2, we have two tasks tuning our system.
+We have our stage 2 model train on two tasks in the framework of multi-task training.
 
 The first task is \emph{regular sentence-pair similarity task}.
-For  sentence  pair semantic similarity task, given a data point $(x, x')_{i}$
-with       similarity       label       $l_{i}$       from       data      set
-$\mathcal{D'}=\{[(x,x')_{i},l_{i}]\}_{i=1}^{M}$,   Roberta   takes  the  final
-hidden  state  $h_{i}$  of the first token [CLS] as the representation for the
-sequence of packed sentence pair $(x, x')_{i}$. Let's suppose we have a linear
-layer  as  ${\Phi}^S_{i}=W^Sh_{i}+b^S$,  where  $W^S$  and $b^S$ are trainable
-parameters,  and  the probability score for $(x, x')_{i}$ can be calculated as
-$p^S_{i}=softmax({\Phi}^S_{i})$.
+For sentence pair semantic similarity task, given a data point $(x, x')_{i}$ with similarity label $l_{i}$ from data set $\mathcal{D'}$, Roberta takes the concatenation of $x, x'$ and outputs hidden state $h_{i}$ of the first token [CLS] as its representation.
+A linear layer is followed as ${\Phi}^S_{i}=W^Sh_{i}+b^S$ to generate unnormalized probabilities, where $W^S$ and $b^S$ are trainable parameters.
 
-Due  to  the  fact that sentence pairs within the same class is much fewer than
-that from  different  classes,  the  dataset  $\mathcal{D'}$  is
-quite imbalanced.  Therefore, we will accommodate a weight variable $w^S = [K-1, 1]$
-to  the  loss  to eliminate the bias brought by data imbalance, shown in Equ.
-\ref{eq:similarity_loss}.
+We note that the dataset $\mathcal{D'}$ is unbalanced, as negative samples are $K - 1$ times as many as positive samples.
+Therefore, we add a weight $w^S \in \{K-1, 1\} $ to the loss of positive and negative samples respectively to eliminate the bias, shown in Equ. \ref{eq:similarity_loss}.
+This weighting strategy is quite effective in practice.
 
@@
 
-The  second  task  is  \emph{classification  on  top-K classes}. As minimizing
-similarity  loss  is  not  our  final goal in the intent classification, we
-bring  back  classification  loss again. In this task, the network is based on
-sentence  pair  similarity  modules.  The  only  difference  is  that we add a
-task-specific  average  pooling  layer,  shown  in Fig. \ref{fig:framework} to
-accomplish the classification task based on sentence-pair model.
+The second task is \emph{classification on top-K classes}. 
+As minimizing similarity loss is not our final goal of the chatbot application, we bring back classification loss again. 
+In this task, the network structure is based on sentence pair similarity modules. 
+We then add a task-specific average pooling layer, shown in Fig. \ref{fig:framework} to accomplish the classification task based on sentence-pair model.
 
-We  already  know  that the size of ${\Phi}^S$ in task 1 is $M\times 2=(N\cdot
-K\cdot  P)\times  2$, where $N$ is the total number of data points in original
-training  data $\mathcal{D}$, $K$ is a hyperparameter that controls the number
-of   candidate   class  labels  provided  by  stage  1,  and  $P$  is  also  a
-hyperparameter that controls the number of sentences we should randomly sample
-from each candidate class labels. Now, for the average pooling layer, we first
-reshape  ${\Phi}^S$  into  the  size  of $N\times K\times P\times 2$, and then
-split  it  into  ${\Phi}^{K,pos}$  and ${\Phi}^{K,neg}$, and both of them will
-have  the  size  of  $N\times  K\times  P$.  In this way, ${\Phi}^{K,pos}$ can
-represent  the  level  of  similarity  for each sentence pair, and in the mean
-time,  ${\Phi}^{K,neg}$  can  represent  the  level  of dissimilarity for each
-sentence  pair. Then, we can do average pooling for each candidate class among
-the  top-K  classes  as  shown  in  Equ.  \ref{eq:average  pooling}.
+The size of ${\Phi}^S$ in task 1, namely unnormalized probabilistic distribution, is $2 \times M$, as $M$ sentence pairs corresponds two class labels.
+Further, it equals $(N\cdot K\cdot P)\times 2$, where $N$ is the total number of data points in original training data $\mathcal{D}$, $K$ is a hyperparameter that controls the number
+of candidate class labels provided by stage 1, and $P$ is also a hyperparameter that controls the number of sentences we should randomly sample from each candidate class labels. 
+Now, for the average pooling layer, we first reshape ${\Phi}^S$ into the size of $N\times K\times P\times 2$, and then split it into ${\Phi}^{K,pos}$ and ${\Phi}^{K,neg}$, and both of them will have the size of $N\times K\times P$.
+In this way, ${\Phi}^{K,pos}$ represents the level of similarity for each sentence pair, and ${\Phi}^{K,neg}$ represents the level of dissimilarity for each sentence pair. 
+Then, we can do average pooling for each candidate class among the top-K classes as shown in Equ. \ref{eq:average pooling}.
 
@@
 correct label $l^{K}_i$ within the top-K candidate classes.
-
-\vspace{-1em}
-\begin{align}
-  \mathcal{L}^{K} = \frac{1}{N}\sum_{i=1}^{N}(\mathcal{L}^{K,pos}_{i} - \mathcal{L}^{K,neg}_{i})
-  \label{eq:top-k_classification_loss}
-\end{align}
-where
-\begin{equation}
-  \begin{aligned}
-    \mathcal{L}^{K,pos}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,pos})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,pos})})
-    \label{eq: pos top-k loss}
-  \end{aligned}
-\end{equation}
-
-\begin{equation}
-  \begin{aligned}
-    \mathcal{L}^{K,neg}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,neg})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,neg})}) \\
-    \label{eq: neg top-k loss}
-  \end{aligned}
-\end{equation}
-\vspace{-1.25em}
-
-Finally,  the  overall  loss  function for multi-task learning in stage 2 is
-shown in Equ. \ref{eq:two-stage_SFC_loss}. The training objective of stage 2 is
-to  minimize  the  weighted  sum  of task-specific losses. Here $\alpha_S$ and
-$\alpha_K$  are  weights  of  task  1  and  task  2  respectively.
-
-\begin{align}
-  \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K
-  \label{eq:two-stage_SFC_loss}
-\end{align}
-\vspace{-2em}
 
@@
 
-\subsection{Joint-SFC}
+\vspace{-1em}
+\begin{align}
+  \mathcal{L}^{K} = \frac{1}{N}\sum_{i=1}^{N}(\mathcal{L}^{K,pos}_{i} - \mathcal{L}^{K,neg}_{i})
+  \label{eq:top-k_classification_loss}
+\end{align}
+where
+\begin{equation}
+  \begin{aligned}
+    \mathcal{L}^{K,pos}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,pos})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,pos})})
+    \label{eq: pos top-k loss}
+  \end{aligned}
+\end{equation}
+
+\begin{equation}
+  \begin{aligned}
+    \mathcal{L}^{K,neg}_{i} &= -log(\frac{exp(\xi_{i,l^{K}_{i}}^{K,neg})}{\sum_{j=1}^{K}exp(\xi_{i,j}^{K,neg})}) \\
+    \label{eq: neg top-k loss}
+  \end{aligned}
+\end{equation}
+\vspace{-1.25em}
+
+Finally, the overall loss function for multi-task learning in stage 2 is
+shown in Equ. \ref{eq:two-stage_SFC_loss}. The training objective of stage 2 is
+to minimize the weighted sum of task-specific losses. Here $\alpha_S$ and
+$\alpha_K$ are weights of task 1 and task 2 respectively.
+
+\begin{align}
+  \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K
+  \label{eq:two-stage_SFC_loss}
+\end{align}
+\vspace{-2em}
+
+\subsection{Joint SFC}
 In 2-stage SFC, Stage 1 and stage 2 are separate that there is no deep

### 2021-05-18 chatbot_classification/03.emnlp_2021/appendix.tex
modified:   abstract.tex   modified:   appendix.tex   modified:   experiments.tex   modified:   introduction.tex   modified:   open.sh   modified:   paper.tex

@@
+\newpage
+
 \appendix
 
-\newpage
 \section{Appendix}
-
 \subsection{Related work}
@@
 ticket.
-
-\subsection{Settings  of  hyperparameters} 
-In  Table \ref{tbe:table3}, we explore the influence from hyperparameters, which
-are  the  number  of  candidate  class  labels $K$ in stage 1, and the number of
-sampled  sentence  pairs  for  each class $P$ in stage 2, on ITG and Amazon-670K
-datasets.  As we control the total number of sampled sentence pairs to about 50 to 60, we
-roughly obatin five combinations of hyperparameters.
-
-We find  that the best setting of hyperparameters is different from datasets
-of  different  data  size.  The  class label number of ITG and Amazon-670k are
-similar  in  our  experimental setting, which is around 250. However the total
-amount of data points of ITG is approximately 2 times larger than Amazon-670k.
-Therefore,  the  setting of $K=5$ and $P=10$ is good enough for ITG since most
-of  the  classes  contains  over 10 data points. However, for Amazon-670k, the
-amount  of  data  sample  for  each  class  is  scarce, thus, we may need more
-candidate  classes to sample enough effective sentence pairs for sentence-pair
-model  layer  of  SFC.  In this way, the setting of $K=10$ and $P=5$ becomes a
-good choice.
-
-However,  in  spite of the effect on evaluation performance brought by different
-settings  of hyperparameters, joint-SFC still steadily outperforms two-stage SFC
-by  0.41  percent  points  in  overall  average  F1 score on ITG and Amazon-670k
-datasets.
 

### 2021-05-18 chatbot_classification/03.emnlp_2021/experiments.tex
modified:   abstract.tex   modified:   appendix.tex   modified:   experiments.tex   modified:   introduction.tex   modified:   open.sh   modified:   paper.tex

@@
 All setting details can be found in the appendix due to the space limitation.
+
+\subsection{Settings  of  hyperparameters} 
+In  Table \ref{tbe:table3}, we explore the influence from hyperparameters, which
+are  the  number  of  candidate  class  labels $K$ in stage 1, and the number of
+sampled  sentence  pairs  for  each class $P$ in stage 2, on ITG and Amazon-670K
+datasets.  As we control the total number of sampled sentence pairs to about 50 to 60, we
+roughly obatin five combinations of hyperparameters.
+
+We find  that the best setting of hyperparameters is different from datasets
+of  different  data  size.  The  class label number of ITG and Amazon-670k are
+similar  in  our  experimental setting, which is around 250. However the total
+amount of data points of ITG is approximately 2 times larger than Amazon-670k.
+Therefore,  the  setting of $K=5$ and $P=10$ is good enough for ITG since most
+of  the  classes  contains  over 10 data points. However, for Amazon-670k, the
+amount  of  data  sample  for  each  class  is  scarce, thus, we may need more
+candidate  classes to sample enough effective sentence pairs for sentence-pair
+model  layer  of  SFC.  In this way, the setting of $K=10$ and $P=5$ becomes a
+good choice.
+
+However,  in  spite of the effect on evaluation performance brought by different
+settings  of hyperparameters, joint-SFC still steadily outperforms two-stage SFC
+by  0.41  percent  points  in  overall  average  F1 score on ITG and Amazon-670k
+datasets.
 

### 2021-05-18 chatbot_classification/03.emnlp_2021/introduction.tex
modified:   introduction.tex
modified:   abstract.tex   modified:   appendix.tex   modified:   experiments.tex   modified:   introduction.tex   modified:   open.sh   modified:   paper.tex

@@
 
-Experiment  results  from  6  public  and  1  private  short-text classification datasets,  show  that  our proposed SFC joint system can achieve significant and consistent  improvements  over  strong baselines, especially in the low resource settings.
-
 \begin{figure*}[t]
@@
   \caption{
-    \textbf{Network Structure of SFC:} 2-stage SFC and joint-SFC are sharing
-    the  same  network  from  stage  1  and  stage 2, with the only difference
-    whether two stages being jointly trained.
+    \textbf{Network Structure of SFC:} 2-stage SFC and joint-SFC are sharing the same network, with the only difference whether the two stages being jointly trained.
   }

### 2021-05-18 chatbot_classification/03.emnlp_2021/open.sh

@@ -1,1 +1,1 @@
-vim paper.tex abstract.tex introduction.tex related_work.tex methodology.tex experiments.tex conclusion.tex refs.bib
+vim paper.tex abstract.tex introduction.tex related_work.tex methodology.tex experiments.tex conclusion.tex refs.bib appendix.tex

### 2021-05-18 chatbot_classification/03.emnlp_2021/appendix.tex
modified:   appendix.tex   modified:   experiments.tex

@@
 
-\subsection{Implementation Details}
-For  our  SFC  systems,  we  use RoBERTa-large as the pretrained model for both
-classification  task  and  sentence-pair similarity task. We fine-tune
-our  SFC  system  on  our datasets with max sequence length of 128,
-learning  rate  of 1.5e-5 for RoBERTa-large pretrained model and learning rate
-of  5e-4  for  task-specific  layer  with polynomial decay and Adam optimizer.
+\subsection*{Relation to the label embedding based LEAM}
+LEAM shows its superiority over TextCNN in all datasets in our experiments, by modeling labeling information.
 
-In two-stage SFC, in equ. \ref{eq:two-stage_SFC_loss} the weights of two tasks
-are  set  as  $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting. The reason
-for  giving  task  2 relatively more weights is that according to the ablation
-experiments  we  did  in Section \ref{sec:exp}, task 2 contributes more to the
-overall  performance.  In  joint-SFC,  in  equ.  \ref{eq:joint_SFC_loss}, the
-weights  of  three  tasks  are  set  as  $\alpha_S=0.25$,  $\alpha_K=0.25$ and
-$\alpha_C=0.5$  in  our setting. Overall, the task weights are less sensitive
-in joint-SFC than in two-stage SFC.
+LEAM does not perform as well as SFCs, since the first intuitive reason is it does not use a pretrained model as its input encoding module; 
+another critical reason is in task-specific chat applications, it is common to have many similar intents, and it becomes hard and even impossible to name each intent with a short clear name to feed into LEAM model.
+One candidate solution is setting a most standard sample as the label of the class. 
+When using non-pretrained models base LEAM, this is applicable. 
+Yet when using a pretrained model based, as all labels can be hundreds of thousands, then the training can not be accommodated in a poplar 32 G Tesla V100 GPU.
 
-For  the  experiments  in  Table  \ref{tbe:table2},  we  empirically  set  the
-hyperparameter  to  be  $K=5$  and  $P=10$  for  all  SFC  variants.  In Table
-\ref{tbe:table3},  we  conduct extensive experiments to see the performance of
-SFC system under various hyperparameter settings.
-
-As for the training time, in our settings, our joint-SFC model needs about 14
-hours to reach convergence using a single Nvidia RTX8000 GPU. In comparison, the classification baseline model needs about 5 hours and the similarity baseline model
-needs about 12 hours, which indicates that our joint-SFC model spends less training
-time than the summation of two baseline models due to faster convergence.
-
-As for the inference time, the classification model baseline is about 0.2 ms;
-the similarity model baseline is about 0.5 ms and our joint-SFC model takes only 0.6 ms.
-Actually both the similarity model baseline and our joint-SFC can be GPU
-parallelized in the similarity computation, if we need pretty fast response time
-in a real product.
+Actually, joint SFC can be kind of understood as a generalization form of LEAM. 
+When there is no clear class labels, the relationship between a sample and a class label is implicitly encoded as that between a sample and another sample from the same class, and this turns into a sentence pair similarity model.

### 2021-05-18 chatbot_classification/03.emnlp_2021/experiments.tex
modified:   appendix.tex   modified:   experiments.tex

@@
 
-\subsubsection*{Relation to the label embedding based LEAM}
-LEAM shows its superiority over TextCNN in all datasets in our experiments, by modeling labeling information.
+\subsection{Implementation Details}
+For  our  SFC  systems,  we  use RoBERTa-large as the pretrained model for both
+classification  task  and  sentence-pair similarity task. We fine-tune
+our  SFC  system  on  our datasets with max sequence length of 128,
+learning  rate  of 1.5e-5 for RoBERTa-large pretrained model and learning rate
+of  5e-4  for  task-specific  layer  with polynomial decay and Adam optimizer.
 
-LEAM does not perform as well as SFCs, since the first intuitive reason is it does not use a pretrained model as its input encoding module; 
-another critical reason is in task-specific chat applications, it is common to have many similar intents, and it becomes hard and even impossible to name each intent with a short clear name to feed into LEAM model.
-One candidate solution is setting a most standard sample as the label of the class. 
-When using non-pretrained models base LEAM, this is applicable. 
-Yet when using a pretrained model based, as all labels can be hundreds of thousands, then the training can not be accommodated in a poplar 32 G Tesla V100 GPU.
+In two-stage SFC, in equ. \ref{eq:two-stage_SFC_loss} the weights of two tasks
+are  set  as  $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting. The reason
+for  giving  task  2 relatively more weights is that according to the ablation
+experiments  we  did  in Section \ref{sec:exp}, task 2 contributes more to the
+overall  performance.  In  joint-SFC,  in  equ.  \ref{eq:joint_SFC_loss}, the
+weights  of  three  tasks  are  set  as  $\alpha_S=0.25$,  $\alpha_K=0.25$ and
+$\alpha_C=0.5$  in  our setting. Overall, the task weights are less sensitive
+in joint-SFC than in two-stage SFC.
 
-Actually, joint SFC can be kind of understood as a generalization form of LEAM. 
-When there is no clear class labels, the relationship between a sample and a class label is implicitly encoded as that between a sample and another sample from the same class, and this turns into a sentence pair similarity model.
+For  the  experiments  in  Table  \ref{tbe:table2},  we  empirically  set  the
+hyperparameter  to  be  $K=5$  and  $P=10$  for  all  SFC  variants.  In Table
+\ref{tbe:table3},  we  conduct extensive experiments to see the performance of
+SFC system under various hyperparameter settings.
+
+As for the training time, in our settings, our joint-SFC model needs about 14
+hours to reach convergence using a single Nvidia RTX8000 GPU. In comparison, the classification baseline model needs about 5 hours and the similarity baseline model
+needs about 12 hours, which indicates that our joint-SFC model spends less training
+time than the summation of two baseline models due to faster convergence.
+
+As for the inference time, the classification model baseline is about 0.2 ms;
+the similarity model baseline is about 0.5 ms and our joint-SFC model takes only 0.6 ms.
+Actually both the similarity model baseline and our joint-SFC can be GPU
+parallelized in the similarity computation, if we need pretty fast response time
+in a real product.

### 2021-05-18 chatbot_classification/03.emnlp_2021/experiments.tex
modified:   experiments.tex   modified:   methodology.tex

--- 2021-05-18 chatbot_classification/03.emnlp_2021/experiments.tex
@@
 Our experiments aim to study the short text classification in the low-resource environment popular in the task-specific conversational chatbot application.
-The datasets adopted in our experiments, showed in \ref{tbe:dataset statistic} \footnote{All settings of six public datasets would be released to github soon.}, typically contain comparatively large number of class labels, ranging from several dozens to hundreds, and each class label is associated with a handful of labeled queries with each query being usually one sentence.
+The datasets adopted in our experiments, showed in Table \ref{tbe:dataset statistic} \footnote{All settings of six public datasets would be released to github soon.}, typically contain comparatively large number of class labels, ranging from several dozens to hundreds, and each class label is associated with a handful of labeled queries with each query being usually one sentence.
 
@@
 
-Our SFC implementations include three 2-stage SFCs using task 1 and 2 with ablation in Table \ref{tbe:table2}; one joint-SFC trained on all three tasks in Table \ref{tbe:table2}; one joint-SFC with an additional fourth NER task in Table \ref{tbe:addtional ner experiments}.
+Our SFC implementations include three 2-stage SFCs using task 1 and 2 with ablation in Table \ref{tbe:table2}; one joint SFC trained on all three tasks in Table \ref{tbe:table2}; one joint SFC with an additional fourth NER task in Table \ref{tbe:addtional ner experiments}.
 
@@
         \hline
-        Joint-SFC & \multirow{2}*{${0.3843}$} &
+        Joint SFC & \multirow{2}*{${0.3843}$} &
         \multirow{2}*{${0.4130}$} & \multirow{2}*{${0.4390}$} &
@@
         \hline
-        Joint-SFC & \multirow{2}*{$\textbf{0.3925}$} &
+        Joint SFC & \multirow{2}*{$\textbf{0.3925}$} &
         \multirow{2}*{$\textbf{0.4420}$} & \multirow{2}*{$\textbf{0.4456}$} &
@@
         \hline
-        F1 score & 2-stage SFC & joint-SFC & Gap \tabularnewline
+        F1 score & 2-stage SFC & joint SFC & Gap \tabularnewline
         \hline
@@
 
-Joint-SFC consistently outperforms 2-stage SFC with multi-task training on 5 diverse datasets by 0.95 percentage point on average. 
+Joint SFC consistently outperforms 2-stage SFC with multi-task training on 5 diverse datasets by 0.95 percentage point on average. 
 Though a joint model structure may bring extra complexity to the system, it does alleviate the error propagation from the first stage and improves the final performance.
 
-In following analysis, we will focus on the comparison between joint-SFC and the other baseline models.
+In following analysis, we will focus on the comparison between joint SFC and the other baseline models.
 
 \subsubsection*{Fusion of classification and similarity models} 
-%We compare joint-SFC with classification, similarity and NER joint model based baselines respectively.
+%We compare joint SFC with classification, similarity and NER joint model based baselines respectively.
 
@@
         \cline{2-7}
-        \multicolumn{1}{|c|}{} & joint-SFC & $0.7986$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7918$\tabularnewline
+        \multicolumn{1}{|c|}{} & joint SFC & $0.7986$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7918$\tabularnewline
         \hline
@@
         \cline{2-7}
-        \multicolumn{1}{|c|}{} & joint-SFC & $0.7334$ & $0.7445$ & $0.7516$ & $0.7344$ & $0.7373$\tabularnewline
+        \multicolumn{1}{|c|}{} & joint SFC & $0.7334$ & $0.7445$ & $0.7516$ & $0.7344$ & $0.7373$\tabularnewline
         \hline
@@
   \caption{
-    We show the performances of SFC from different settings of hyperparameters, $K$ denoting the candidate class number from stage 1,
+    The performances of SFC from different settings of hyperparameters, $K$ denoting the candidate class number from stage 1,
     $P$ denoting the number of sampled sentence pair in stage 2. 
@@
 
-Regarding the classification models, joint-SFC outperforms RoBERTa-large based, the strongest among all baselines, by 2.04 percentage points on average F1 score over 5 datasets. 
+Regarding the classification models, joint SFC outperforms RoBERTa-large based, the strongest among all baselines, by 2.04 percentage points on average F1 score over 5 datasets. 
 Especially, ALBERT.xxlarge based is rather unstable in this short sentence task. 
@@
 Regarding the similarity model, as analyzed above, we only choose the RoBERTa-large based implementation as our baseline. 
-Joint-SFC achieves more improvement of 7.09 percentage points on average F1 score. 
+Joint SFC achieves more improvement of 7.09 percentage points on average F1 score. 
 This is also understandable, since RoBERTa-large based similarity model does not and also can not train towards the task specific goal.
@@
 
-\subsubsection*{Joint-SFC improves stage 1?}
-We explore the quality of predicted candidate labels in stage 1 from 2-stage SFC and joint-SFC respectively. 
+\subsubsection*{Joint SFC improves stage 1?}
+We explore the quality of predicted candidate labels in stage 1 from 2-stage SFC and joint SFC respectively. 
 We should note that 2-stage SFC does not optimize the stage 1 model, namely a RoBERTa based classification model.
@@
 From Table \ref{tbe:top1_5_accuracy}, the joint training does not improve the top-1 classification accuracy in stage 1, yet it improves the top-5 accuracy.
-The reason is that, a classification model inherently optimizes the objective loss, 0-1 error of top-1 here; the sentence pair similarity model in joint-SFC poses more positive effect in optimizing the candidate labels.
+The reason is that, a classification model inherently optimizes the objective loss, 0-1 error of top-1 here; the sentence pair similarity model in joint SFC poses more positive effect in optimizing the candidate labels.
 
-\subsubsection*{Supportive of extra NER loss}
+\subsubsection*{Supportive of extra NER task}
 Many previous work shows joint training with a NER loss improves the intent classification task as well, observed again in our baselines and SFCs in Table \ref{tbe:addtional ner experiments}.
@@
 
-We can see that our joint-SFC without NER loss still outperforms RoBERTa with NER loss baseline by 0.86 percentage points on average. 
+We can see that our joint SFC without NER loss still outperforms RoBERTa with NER loss baseline by 0.86 percentage points on average. 
 This indicates that the fusion of classification and similarity models can even works better than fusing with additional NER information under few-shot chatbot scenario.
 
-Moreover, the adding NER loss to joint-SFC further achieves improvement of 1.66 percentage points over RoBERTa with NER loss baseline. 
-Especially on FRAMES dataset, which is a much more difficult task in comparison with ATIS based on performance of all systems on it, our joint-SFC with NER loss achieves a bigger improvement of 2.8 percentage points on average.
+Moreover, the adding NER loss to joint SFC further achieves improvement of 1.66 percentage points over RoBERTa with NER loss baseline. 
+Especially on FRAMES dataset, which is a much more difficult task in comparison with ATIS based on performance of all systems on it, our joint SFC with NER loss achieves a bigger improvement of 2.8 percentage points on average.
 
 \subsubsection*{Different training sample size} 
-We analyze the overall improvement trend of joint-SFC under various few-shot settings, and show results in Fig. \ref{fig:trend}.
+We analyze the overall improvement trend of joint SFC under various few-shot settings, and show results in Fig. \ref{fig:trend}.
 
 Our main focus is on studying chatbot construction in real world applications, where each class has only a small number of example sentences.
-The experimental results for the 3 diverse intent detection datasets (ClINC150, BANKING77, HWU64) under few-shot settings, 5 to 50 samples per class, indicate that our proposed joint-SFC can achieve average 2.47 percentage points improvement over one of the most powerful baseline models, which is RoBERTa-large classification model.
+The experimental results for the 3 diverse intent detection datasets (ClINC150, BANKING77, HWU64) under few-shot settings, 5 to 50 samples per class, indicate that our proposed joint SFC can achieve average 2.47 percentage points improvement over one of the most powerful baseline models, which is RoBERTa-large classification model.
 Moreover, the improvement in F1 score becomes more and more prominent with the decrease of data sample number per class.
@@
 
-Especially, in the most extreme setting with only 5 training samples per class, joint-SFC achieves 4.97 percentage points improvements on average over RoBERTa-large classification model. 
+Especially, in the most extreme setting with only 5 training samples per class, joint SFC achieves 4.97 percentage points improvements on average over RoBERTa-large classification model. 
 Joint SFC is a better choice applied into the early stage of building a task-specific chatbot system, since label data is extremely scarce.
@@
 
-\subsubsection*{Relation to the label embedding based LEAM}
-LEAM shows its superiority over TextCNN in all datasets in our experiments, by modeling labeling information.
+\subsection{Settings of hyperparameters} 
+In Table \ref{tbe:table3}, we explore the influence from hyperparameters on ITG and Amazon-670K datasets. 
+We control the total number of sampled sentence pairs to about 50 to 60, and obatin about five combinations of hyperparameters.
 
-LEAM does not perform as well as SFCs, since the first intuitive reason is it does not use a pretrained model as its input encoding module; 
-another critical reason is in task-specific chat applications, it is common to have many similar intents, and it becomes hard and even impossible to name each intent with a short clear name to feed into LEAM model.
-One candidate solution is setting a most standard sample as the label of the class. 
-When using non-pretrained models base LEAM, this is applicable. 
-Yet when using a pretrained model based, as all labels can be hundreds of thousands, then the training can not be accommodated in a poplar 32 G Tesla V100 GPU.
+We find that the best setting of hyperparameters is different with different datasets. 
+The class label number of ITG and Amazon-670k are similar in our experiments, around 250. 
+However the number of data points in ITG is approximately 2 times as many as that in Amazon-670k.
+Therefore, the setting of $K=5$ and $P=10$ is good enough for ITG since most of the classes contains over 10 data points. 
+However, in Amazon-670k, the data per each class is scarce, and, we may need more candidate classes to sample enough effective sentence pairs for the stage 2 traininig of SFC. 
+Thus, the setting of $K=10$ and $P=5$ becomes a good choice.
 
-Actually, joint SFC can be kind of understood as a generalization form of LEAM. 
-When there is no clear class labels, the relationship between a sample and a class label is implicitly encoded as that between a sample and another sample from the same class, and this turns into a sentence pair similarity model.
+However, despite the effect on evaluation performance brought by different settings of hyperparameters, joint SFC still steadily outperforms two-stage SFC by 0.41 percent points in overall average F1 score on ITG and Amazon-670k datasets.
+
+For the experiments in Table \ref{tbe:table2}, we empirically set the hyperparameter to be $K=5$ and $P=10$ for all SFC variants.
+
+\subsection{Other settings}
+We fine-tune all SFC systems with the maximum sequence length of 128, learning rate of 1.5e-5 for RoBERTa-large pretrained model and 5e-4 for task-specific layer with a linear decay, and use Adam optimizer.
+
+In two-stage SFC, in equ. \ref{eq:two-stage_SFC_loss} the weights of two tasks are set as $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting. 
+In joint SFC, in equ. \ref{eq:joint_SFC_loss}, the weights of three tasks are set as $\alpha_S=0.25$, $\alpha_K=0.25$ and $\alpha_C=0.5$. 
+Overall, the task weights are less sensitive in joint SFC than in two-stage SFC.
+
+As for the training time, in our settings, our joint SFC model needs about 14 hours to reach convergence using a single Nvidia RTX8000 GPU. 
+In comparison, the classification baseline model needs about 5 hours and the similarity baseline model needs about 12 hours.

### 2021-05-18 chatbot_classification/03.emnlp_2021/methodology.tex
modified:   experiments.tex   modified:   methodology.tex

@@
 
-The size of ${\Phi}^S$ in task 1, namely unnormalized probabilistic distribution, is $2 \times M$, as $M$ sentence pairs corresponds two class labels.
-Further, it equals $(N\cdot K\cdot P)\times 2$, where $N$ is the total number of data points in original training data $\mathcal{D}$, $K$ is a hyperparameter that controls the number
-of candidate class labels provided by stage 1, and $P$ is also a hyperparameter that controls the number of sentences we should randomly sample from each candidate class labels. 
+The size of ${\Phi}^S$ in task 1, namely unnormalized probabilistic distribution, is $2 \times M$, as one sentence pair correspond to two class labels.
+Further, it equals $(N\cdot K\cdot P)\times 2$, where $N$ is the size of original training data $\mathcal{D}$, $K$ the number of candidate class labels from stage 1, and $P$ is the number of sentences randomly sampled from each candidate class label.
 Now, for the average pooling layer, we first reshape ${\Phi}^S$ into the size of $N\times K\times P\times 2$, and then split it into ${\Phi}^{K,pos}$ and ${\Phi}^{K,neg}$, and both of them will have the size of $N\times K\times P$.
@@
         \hline
-        \multirow{2}*{Joint-SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.9669}$} & \multirow{2}*{$\textbf{0.9712}$} & \multirow{2}*{$\textbf{0.9821}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.9323}$} & \multirow{2}*{$\textbf{0.9463}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$\textbf{0.7593}$} & \multirow{2}*{$\textbf{0.7772}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline
+        \multirow{2}*{Joint SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.9669}$} & \multirow{2}*{$\textbf{0.9712}$} & \multirow{2}*{$\textbf{0.9821}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.9323}$} & \multirow{2}*{$\textbf{0.9463}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$\textbf{0.7593}$} & \multirow{2}*{$\textbf{0.7772}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline
         & & & & & & & & & & & & & & & & & & & &\tabularnewline
@@
 \subsection{Joint SFC}
-In 2-stage SFC, Stage 1 and stage 2 are separate that there is no deep
-interaction with each other during training. In this case, the performance of
-stage 1 may limit the potential of stage 2; meanwhile, stage 2 also cannot
-give training feedback back to stage 1 for fine-tuning. Therefore, to further
-improve the overall performance of SFC, we proposed a joint model structure,
-shown in Fig. \ref{fig:framework}.
+In 2-stage SFC, two stages are separate that there is no deep interaction with each other during training. 
+In this case, the performance of stage 1 may limit the model potential in stage 2; 
+meanwhile, stage 2 also cannot loop feedback back to stage 1 in trainig for improvement. 
+Therefore, we propose to jointly train all stages, shown in Fig. \ref{fig:framework}.
 
-In joint-SFC, classification model is being placed in lower layer level to
-dynamically provide top-K candidate class labels for the sentence-pair
-similarity model placed in higher layer level through a top-K pooling layer.
-In this way, classification model and similarity model can be merged into one
-single joint-model for multi-task training with sentence pairs sampled from
-varying candidate class labels, thus avoiding the limitation brought by 2
-separate stage structure.
+In joint SFC, a classification model is placed in stage 1 to dynamically provide top-K candidate class labels for the sentence-pair similarity model in stage 2 through a top-K pooling layer.
+In this way, classification model and similarity model can be merged into one single model for multi-task training with sentence pairs sampled from varying candidate class labels.
 
-There are 3 tasks in total during the training process of joint-SFC, shown in
-Fig. \ref{fig:framework}, and the overall loss is also the weighted sum of all
-the task-specific losses, shown in Equ. \ref{eq:joint_SFC_loss}. Here,
-$\alpha_S$, $\alpha_K$ and $\alpha_C$ represent the weights for task 1
-sentence-pair similarity in Equ. \ref{eq:similarity_loss}, task 2 top-K
-classification in Equ. \ref{eq:top-k_classification_loss}, and task 3 general
-single sentence classification respectively in Equ.
+There are 3 tasks in total during the training of joint SFC, shown in Fig. \ref{fig:framework}. 
+The overall loss is a linear combination of them, shown in Equ. \ref{eq:joint_SFC_loss}. 
+Here, $\alpha_S$, $\alpha_K$ and $\alpha_C$ represent the weights for task 1 sentence-pair similarity in Equ.
+\ref{eq:similarity_loss}, task 2 top-K classification in Equ.
+\ref{eq:top-k_classification_loss}, and task 3 general single sentence classification respectively in Equ.
 \ref{eq:classification_loss}.

### 2021-05-18 chatbot_classification/03.emnlp_2021/experiments.tex
modified:   experiments.tex   new file:   picture/picture4.key   modified:   picture/picture4.pdf
modified:   conclusion.tex   modified:   experiments.tex   modified:   introduction.tex   modified:   methodology.tex   modified:   paper.tex   new file:   paper.ver06.appendix.pdf   new file:   paper.ver06.pdf   modified:   picture/picture4.key   modified:   picture/picture4.pdf

@@
 
-The fouth one, \emph{pretrained model based joint text classification and NER model}. 
+The fourth one, \emph{pretrained model based joint text classification and NER model}. 
 We choose the work from \cite{chen2019bert} as our baseline system, which utilizes a strong RoBERTa-large model to jointly train two losses.
@@
 Our SFC implementations include three 2-stage SFCs using task 1 and 2 with ablation in Table \ref{tbe:table2}; one joint SFC trained on all three tasks in Table \ref{tbe:table2}; one joint SFC with an additional fourth NER task in Table \ref{tbe:addtional ner experiments}.
-
-All setting details can be found in the appendix due to the space limitation.
 
@@
   \end{centering}
-  \caption{The average classification accuracy in percentage in stage 1 on all five dataset.}
+  \caption{The average classification accuracy in percentage in stage 1 on the first five datasets.}
   \label{tbe:top1_5_accuracy}
@@
 In Table \ref{tbe:table3}, we explore the influence from hyperparameters on ITG and Amazon-670K datasets. 
-We control the total number of sampled sentence pairs to about 50 to 60, and obatin about five combinations of hyperparameters.
+We control the total number of sampled sentence pairs to about 50 to 60, and obtain about five combinations of hyperparameters.
 
@@
 Therefore, the setting of $K=5$ and $P=10$ is good enough for ITG since most of the classes contains over 10 data points. 
-However, in Amazon-670k, the data per each class is scarce, and, we may need more candidate classes to sample enough effective sentence pairs for the stage 2 traininig of SFC. 
+However, in Amazon-670k, the data per each class is scarce, and, we may need more candidate classes to sample enough effective sentence pairs for the stage 2 training of SFC. 
 Thus, the setting of $K=10$ and $P=5$ becomes a good choice.

### 2021-05-18 chatbot_classification/03.emnlp_2021/introduction.tex
modified:   conclusion.tex   modified:   experiments.tex   modified:   introduction.tex   modified:   methodology.tex   modified:   paper.tex   new file:   paper.ver06.appendix.pdf   new file:   paper.ver06.pdf   modified:   picture/picture4.key   modified:   picture/picture4.pdf

@@
 A popular one is the smart speaker, e.g. Alex, Siri, Google home. 
-Another important one is the customer service system, which greatly help human agents handle miscellanious customer's questions.
+Another important one is the customer service system, which greatly help human agents handle miscellaneous customer's questions.
 No matter these applications involves single- or multi-round conversations, a critical step is to identify the intent behind a user's question or response. 
@@
 
-Existent approaches for intent detection can be roughly categorized as text classfication model and text similarity model.
+Existent approaches for intent detection can be roughly categorized as text classification model and text similarity model.
 
@@
 From traditional machine learning models like SVM \cite{suykens1999least}, boosting tree \cite{tu2005probabilistic}, to neural networks \cite{wen2016network}, such as convolutional neural networks (CNNs) \cite{kim2014convolutional,zhang2015character,conneau2016very} and long short term memory networks (LSTMs) \cite{mousa2017contextual,liu2016recurrent}, and then to the most popular pretrained language models based, such as BERT \cite{devlin2018bert}, RoBERTa \cite{liu2019roberta} and etc.
-Especiallaly, pretrained models based \cite{vaswani2017attention} tends to be more helpful in the few-shot scenario \cite{yu2018diverse, madabushi2020cost} to alleviate the dearth of training data.
+Especially, pretrained models based \cite{vaswani2017attention} tends to be more helpful in the few-shot scenario \cite{yu2018diverse, madabushi2020cost} to alleviate the dearth of training data.
 Another two interesting lines of work, label-word joint models, and joint NER and classification are discussed in the related work of appendix.
@@
 It is quite hard to adopt labeled data from other domains, as their label definitions are often incompatible to each other. 
-Though we can use some data augmentation methods to alleivate the paucity of data, e.g., translation based paraphrasing methods, the resulting benefit is still limited because of the data being homogeneous, in the case that our labeled data is very insufficient.
+Though we can use some data augmentation methods to alleviate the paucity of data, e.g., translation based paraphrasing methods, the resulting benefit is still limited because of the data being homogeneous, in the case that our labeled data is very insufficient.
 Regarding the \emph{similarity model}, the foremost advantage is it does not pose any restriction on the label definition of user intents, but aims to learn a function that measure how similar of two sentences are.
-Then in the intent detection task, we are only concerned which labeled query is the most similary one to the current input, and then use its label as the output.
+Then in the intent detection task, we are only concerned which labeled query is the most similar one to the current input, and then use its label as the output.
 This results in a possibility that even though the labeled data in current domain is scarce, we may borrow additional data from another domain to help enhance the similarity model to make a better intent prediction.
@@
 In order to train effectively, we further borrow the multi-task learning \cite{caruana1993multitask,collobert2008unified, liu2019multi}.
-Our basic idea come naturally, and the first impementation consists of two stages. 
+Our basic idea come naturally, and the first implementation consists of two stages. 
 In the first stage, we use an auxiliary model to select top-K most possible labels for an input. 
@@
 
-Since SFC is in the framework of multi-task training, its inheriently supports adding additional tasks, such as NER, to gain further improvement.
+Since SFC is in the framework of multi-task training, its inherently supports adding additional tasks, such as NER, to gain further improvement.
 

### 2021-05-18 chatbot_classification/03.emnlp_2021/methodology.tex
modified:   conclusion.tex   modified:   experiments.tex   modified:   introduction.tex   modified:   methodology.tex   modified:   paper.tex   new file:   paper.ver06.appendix.pdf   new file:   paper.ver06.pdf   modified:   picture/picture4.key   modified:   picture/picture4.pdf

@@
 In this case, the performance of stage 1 may limit the model potential in stage 2; 
-meanwhile, stage 2 also cannot loop feedback back to stage 1 in trainig for improvement. 
+meanwhile, stage 2 also cannot loop feedback back to stage 1 in training for improvement. 
 Therefore, we propose to jointly train all stages, shown in Fig. \ref{fig:framework}.

### 2021-05-18 chatbot_classification/03.emnlp_2021/experiments.tex
modified:   experiments.tex   modified:   introduction.tex   modified:   methodology.tex   new file:   paper.ver07.pdf

@@
 We choose the work from \cite{chen2019bert} as our baseline system, which utilizes a strong RoBERTa-large model to jointly train two losses.
-Our SFC framework is also conveniently supportive of extra NER loss that in stage 1 a fourth task with a NER loss is trivially derived based on the output states from a pretrained model.
 
@@
 \subsubsection*{Supportive of extra NER task}
-Many previous work shows joint training with a NER loss improves the intent classification task as well, observed again in our baselines and SFCs in Table \ref{tbe:addtional ner experiments}.
-We choose the state-of-the-art RoBERTa-large model with NER loss as a strong baseline.
+Many previous work shows joint training with a NER task improves the intent classification task as well, observed again in our baselines and SFCs in Table \ref{tbe:addtional ner experiments}.
+Our SFC systems set the weight of the fourth NER task as 0.25 throughout this part.
 
-We can see that our joint SFC without NER loss still outperforms RoBERTa with NER loss baseline by 0.86 percentage points on average. 
+We can see that our joint SFC without a NER task still outperforms RoBERTa baseline with a NER task by 0.86 percentage points on average. 
 This indicates that the fusion of classification and similarity models can even works better than fusing with additional NER information under few-shot chatbot scenario.
 
-Moreover, the adding NER loss to joint SFC further achieves improvement of 1.66 percentage points over RoBERTa with NER loss baseline. 
-Especially on FRAMES dataset, which is a much more difficult task in comparison with ATIS based on performance of all systems on it, our joint SFC with NER loss achieves a bigger improvement of 2.8 percentage points on average.
+Moreover, the adding NER task to joint SFC further achieves improvement of 1.66 percentage points over RoBERTa baseline with a NER task. 
+Especially on FRAMES dataset, which is a much more difficult task in comparison with ATIS based on performance of all systems on it, our joint SFC with a NER task achieves a bigger improvement of 2.8 percentage points on average.
 

### 2021-05-18 chatbot_classification/03.emnlp_2021/introduction.tex
modified:   experiments.tex   modified:   introduction.tex   modified:   methodology.tex   new file:   paper.ver07.pdf

@@
 Despite plenty of success of these two methodologies, they still have some limitations in this task especially when data is insufficient.
+
 Regarding the \emph{text classification model}, it learns a function that directly maps an input query into its expected label.
-Its training requires data in the form of a pair of a query and a task dependent label. 
-It is quite hard to adopt labeled data from other domains, as their label definitions are often incompatible to each other. 
-Though we can use some data augmentation methods to alleviate the paucity of data, e.g., translation based paraphrasing methods, the resulting benefit is still limited because of the data being homogeneous, in the case that our labeled data is very insufficient.
+The training requires data in the form of a pair of a query and a task dependent label. 
+Yet it is quite hard to adopt existent labeled data from other domains, since their label definitions are often incompatible to each other. 
+Though we can use some data augmentation methods to alleviate the paucity of data, e.g., translation based paraphrasing methods, the resulting benefit is still limited because of the data being homogeneous, in the cases that labeled data is rather insufficient.
+
 Regarding the \emph{similarity model}, the foremost advantage is it does not pose any restriction on the label definition of user intents, but aims to learn a function that measure how similar of two sentences are.
-Then in the intent detection task, we are only concerned which labeled query is the most similar one to the current input, and then use its label as the output.
+Then in the intent detection task, we are only concerned which labeled query is the most similar to the current input, and then use its label as the output.
 This results in a possibility that even though the labeled data in current domain is scarce, we may borrow additional data from another domain to help enhance the similarity model to make a better intent prediction.
-Nevertheless, just as every coin has two sides, the high flexibility of similarity model leads to its worse performance compared to a classification model, because its training loss differs from a classification loss corresponding to the intent detection goal.
-More, it requires an auxiliary model to narrow down candidate labeled queries to speed up the calculation, which makes it slow in the speed and tricky in the auxiliary model selection.
+Nevertheless, just as every coin has two sides, the high flexibility of similarity model leads to its worse performance compared to a classification model, as it is not trained towards the goal in the intent detection task which is actually a 0-1 loss minimization.
+More, it requires an auxiliary model to narrow down candidate class labels to speed up the similarity calculation next step, and this auxiliary model should be of a good balance in precision and recall.
 
